### 2017-04-03 Writeup/PERT_Report.tex
Updated the summary to include only Scenario 1
Updated the summary to include only Scenario 1

\documentclass[11pt]{article}
\usepackage[small]{titlesec}
\usepackage[top = 0.66in,textwidth = 6.5in, textheight=9.1in]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage{natbib}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}

\def\qed{\hfill{\(\vcenter{\hrule height1pt \hbox{\vrule width1pt height5pt
     \kern5pt \vrule width1pt} \hrule height1pt}\)} \medskip}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\renewcommand{\textfraction}{0.0}
\newcommand{\dst}{\displaystyle}
\newcommand{\minx}{\mbox{\( \dst \min_{x \in X} \)}}
\newcommand{\Efx}{\mbox{\( \dst E f (x, \xi) \)}}
\newcommand{\Efxhat}{\mbox{\( \dst E f (\hat{x}, \xi) \)}}
\newcommand{\hxx}{\mbox{\( \hat{x} \)}}
\newcommand{\bpi}{\bar{\pi}}
\newcommand{\xx}{\mbox{\( x \)}}
\newcommand{\txxi}{\mbox{\(\xi\)}}
\newcommand{\var}{\mbox{var}}
\newcommand{\cF}{{\cal F}}
\newcommand{\cG}{{\cal G}}
\newcommand{\cN}{{\cal N}}
\newcommand{\cO}{{\cal O}}
\newcommand{\txi}{{\xi}}
\newcommand{\PP}{\mbox{\(SP\)}}
\newcommand{\PPn}{\mbox{\(SP_n\)}}
\newcommand{\PPnx}{\mbox{\(SP_{n_x}\)}}
\newcommand{\noi}{\noindent}
\renewcommand{\ss}{\smallskip}
\newcommand{\ms}{\medskip}
\newcommand{\bs}{\bigskip}
\newcommand{\st}{\mbox{s.t.}}
\newcommand{\wpo}{\mbox{wp1}}
\newcommand{\iid}{\mbox{i.i.d.\ }}
\newcommand{\vsmo}{\vspace*{-0.1in}}
\newcommand{\vsmt}{\vspace*{-0.2in}}
\newcommand{\vso}{\vspace*{0.1in}}
\newcommand{\vst}{\vspace*{0.2in}}
\newcommand{\mc}{\multicolumn}
\newcommand{\cP}{{\cal P}}
\newcommand{\underv}{\mbox{$\underbar{$v$}$}}
%\allowdisplaybreaks

\renewcommand{\P}{{\mathbb P}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\renewcommand{\Re}{{\mathbb R}}

\bibliographystyle{plain}

\begin{document}
%0.27
\baselineskip0.25in

\begin{center}
\begin{large}
\begin{bf}

Optimizing Crashing Decisions in Project Management Problem with Disruptions \ms

Haoxiang Yang \ms

\today \ms
\end{bf}
\end{large}
\end{center}

\section{Introduction to the Project Management Problem with Disruptions}
A project could be viewed as a collection of activities, each of which will consume some time and resources. There will be precedence relationships between activities due to logical or technological considerations. The objective is to find the smallest amount of time needed to finish all activities. The project could be represented as an activity network where the length of each link shows the duration of an activity, and the direction of it shows the precedence relationship. An activity cannot start until all its predecessors are completed. Two dummy nodes \((S,T)\) are created in the network to represent the start and the end of the project. In the network setting with no uncertainty, finding the shortest project span is equivalent to finding the longest path from \(S\) to \(T\). Since the activity network is usually acyclic, it is easy to use shortest path algorithms to find a longest path in polynomial time. More details about the activity network are discussed in \cite{Elmaghraby77}.\\
\newline In the planning stage of a project, a set of decisions can be made to crash a certain set of activities. Here crashing an activity means accelerating its progress or compress its duration. In this paper, a discrete set of crashing options will be given to the decision makers, each with a fractional number which equals to the crashed duration divided by the original duration. One project can only be crashed once with one specific option. Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget.\\
\newline In this paper, we focus on the perspective of time and we assume that multiple projects can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied. A disruption is an event that may occur any time in the time horizon and will significantly affect the duration of all activities. The number of disruption is limited to one for this paper. We assume before the disruption the original duration of all activities are deterministic and given. The distribution of the timing for the disruption is known as well. Once the disruption occurs, the duration of all unfinished activities will be revealed.

\section{A Motivating Example}
V-42 problem goes here.

\section{Stochastic Program Formulations} \label{formulation}
In this section we will discuss a scenario in which the disruption does not affect the activities that have already started. Under this scenario, if an activity starts before the disruption time, the duration of that activity is deterministic and known as the original activity duration. If an activity is started after the disruption, the activity will have a new duration, which is a random number according to a known distribution. Additionally, we are considering a finite discrete distribution for the duration after disruption of every activity. The decision of crashing has to be made the same time when the activity starts and cannot be changed after that.\\
\newline The notation for the model is displayed as follows:
\begin{table}[H]
	\begin{tabular}{ l l l l }
		\multicolumn{4}{l}{Indices and index sets} \\
		\\
		\(I\) & \(\qquad\) & the set of activities;&\\
		\(J\) & \(\qquad\) & the set of crashing options;&\\
		\(\Omega\) & \(\qquad\) & the set of possible realizations of disruption;&\\
		\\
		\multicolumn{4}{l}{Parameters} \\
		\\
		\(D_{i}\)& \(\qquad\) & original duration of activity \(i\), \(i \in I\);&\\
		\(e_{j}\) & \(\qquad\) & effectiveness of crashing option \(j\), \(j \in J\);&\\
		\(B\) & \(\qquad\) & total budget;&\\
		\(b_{j}\) & \(\qquad\) & cost of crashing option \(j\), \(j \in J\);&\\
		\(\mathcal{A}\) &\(\qquad\) & set of arcs which represents the precedence relationship;&\\
		\(H^\omega\) &\(\qquad\) & disruption time in realization \(\omega\), \(\omega \in \Omega\);&\\
		\\
		\multicolumn{4}{l}{Decision Variables}\\
		\\
		\(t_{i}\) & \(\qquad\) & original starting time of activity \(i\);&\\
		\(x_{ij}\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) in the original plan; &\\
		\(F_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts before disruption in realization \(\omega\);&\\
		\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\);&\\
		\(\tilde{F}_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) ends when disruption occurs in realization \(\omega\); &\\
		\(\tilde{G}_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) ends when disruption occurs in realization \(\omega\); &\\
	\end{tabular}
\end{table}

\noi Given the assumption that only one disruption will occur, we can model the problem as a two stage stochastic mixed integer program. We assume after disruption the duration of activity \(i\) will be \(D_i + d_i^\omega \geq 0\) in realization \(\omega\). The master program can be displayed as follows:
	\begin{subequations}
		\begin{align}
			\min \quad & \sum_{\omega \in \Omega} f^\omega(t,x) &\\
			\text{s.t.} \quad & t_k - t_i \geq D_i(1 - \sum_{j \in J} e_jx_{ij}) & \forall (i,k) \in \mathcal{A}\\
			& \sum_{j \in J} x_{ij} \leq 1 & \forall i \in I\\
			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij} \leq B &\\
			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J
		\end{align}
		\label{masterOrigin}
	\end{subequations}
And the subproblem is formed in the following way. Here we set up two status variables \(F_i^\omega, G_i^\omega\) for each activity under every circumstance to indicator whether it starts before or after the disruption, since the relationship between the starting time and the disruption time decides the length of that activity.
	\begin{subequations}
		\begin{align}
			f^\omega(t,x) = \min \quad & t_N^\omega &\\
			\text{s.t.} \quad & H^\omega - F_i^\omega M \leq t_i & \forall i \in I\\
			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I\\
			& F_i^\omega + G_i^\omega = 1 & \forall i \in I\\
			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I\\
			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I\\
			& x_{ij}^\omega + (1 - F_i^\omega) \geq x_{ij} & \forall i \in I, j \in J \\
			& x_{ij}^\omega - (1 - F_i^\omega) \leq x_{ij} & \forall i \in I, j \in J \\
			& t_N^\omega \geq t_i^\omega & \forall i \in I\\
			& t_k^\omega - t_i^\omega \geq (D_i + d_i^\omega G_i^\omega)(\sum_{j \in J} e_jx_{ij}^\omega) & \forall i \in I, j \in J \label{constr:Duration}\\
			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I \\
			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega\\
			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J\\
			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J
		\end{align}
	\end{subequations}
In this formulation, the right hand side of constraint (\ref{constr:Duration}) is not a linear expression of the decision variables. However, since both \(G_i^\omega\) and \(x_{ij}^\omega\) are binary variables, it is possible to linearize this constraint by letting \(Z_{ij}^\omega\) represent \(G_i^\omega x_{ij}^\omega\):
	\begin{subequations}
		\begin{align*}
		& Z_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J\\
		& Z_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J\\
		& Z_{ij}^\omega \geq x_{ij}^\omega + G_i^\omega - 1 & \forall i \in I, j \in J
		\end{align*}
	\end{subequations}

\section{Decomposition Method to Solve the Stochastic Program}
In this section we create a decomposition method for the problem in Section~\ref{formulation}, where the disruption affects the unfinished part of the activities that have started by the time of disruption. Same procedure can be applied to the other two cases.\\
\newline 
The second stage problem, as stated in Section~\ref{formulation}, is a mixed integer program (MIP) with both binary variables and continuous variables passing down from the master problem. This problem is neither convex nor continuous. This type of stochastic mixed integer problem has been studied by many researchers. Primal methods are derived using Benders-like cuts to characterize the second stage function. \cite{laporte1993integer} developed an integer L-shaped method to solve two stage stochastic programs with only binary first stage variables and complete recourse. More recently, \cite{zou2016nested} proposed a type of Lagrangian cuts and strengthened Benders cuts to solve multi-stage stochastic integer programs with binary state variables. The Lagrangian cuts are tight at the feasible previous stage solution, valid globally and finite. On the other side, dual methods are also widely used, especially in solving multi-stage stochastic mixed integer problems. Progressive hedging method has been successfully used in many occasions \textcolor{blue}{(add citations here about the dual method)}. In general, it is hard to come up with a lower approximation tight at the solution, especially when our state variables contain both binary ones and continuous ones. However, it is possible to come up with a lower approximation scheme based on dualization.\\
\newline 
Here we write down the master program again, with linear constraints (\ref{cuts}) that form a lower approximation of the second stage problem. 
	\begin{subequations}
		\begin{align}
			\min \quad & \sum_{\omega \in \Omega} \theta^\omega &\\
			\text{s.t.} \quad & t_k - t_i \geq D_i(\sum_{j \in J} e_jx_{ij}) & \forall (i,k) \in \mathcal{A}\\
			& \sum_{j \in J} x_{ij} \leq 1 & \forall i \in I\\
			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij} \leq B &\\
			& \theta^{\omega} \geq v_{s}^\omega + \sum_{i \in I}\sum_{j \in J}\lambda_{ij,s}^\omega (x_{ij} - \hat{x}_{ij,s}) + \sum_{i \in I} \pi_{i,s}^\omega(t_i - \hat{t}_i)& s = 1,2,\dots \label{cuts}\\
			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J
		\end{align}
		\label{master}
	\end{subequations}
Solving this master program will yield a lower bound of the original problem (\ref{masterOrigin}). If the cuts can characterize the function, that is, if \[f^\omega(t,x) = \max_{s} v_{s}^\omega + \sum_{i \in I}\sum_{j \in J}\lambda_{ij,s}^\omega (x_{ij} - \hat{x}_{ij,s}) + \sum_{i \in I} \pi_{i,s}^\omega(t_i - \hat{t}_i) \qquad \forall \omega \in \Omega\]
for all feasible \(x\) and \(t\), then solving problem (\ref{master}) will be equivalent to solving the original problem. However, since \(t\) is continuous and \(f^\omega\) is a non-convex function in \(t\), it is impossible to use a set of linear cuts to approximate \(f^\omega\). So the optimal value of problem (\ref{master}) is strictly less than that of problem (\ref{masterOrigin}).\\
\newline 
Although solving the transformation of the original problem only provides a lower bound, it might still lead to an optimal solution. \textcolor{blue}{We would like to derive an algorithm that terminates in finite number of iterations to one optimal solution.}\\
\textcolor{blue}{Remaining Points:
	\begin{itemize}
		\item write down the algorithm to generate a good solution
		\item describe the computational result of the optimality gap
		\item describe the comparison between the disruption model and the deterministic model
		\item prove how loose the lagrangian cut method can be
		\item assume if every activity needs to start as soon as all its prerequisites have finished
		\item assume continuous x: could we get rid of all binary variables?
	\end{itemize}
}

\bibliographystyle{plain}
\bibliography{PERT_Bib}

\end{document}

### 2017-05-22 PERT.tex
Added the paper structure
Added the paper structure

--- 2017-04-03 Writeup/PERT_Report.tex
@@
 Once the disruption occurs, the duration of all unfinished activities will be revealed.
-
+\\
 \section{A Motivating Example}
 	V-42 problem goes here.
-
-\section{Stochastic Program Formulations} \label{formulation}
-In this section we will discuss a scenario in which the disruption does not affect the activities that have already started.
-Under this scenario, if an activity starts before the disruption time, the duration of that activity is deterministic and known as the original activity duration.
+\section{Stochastic Program Formulations}
+	In this section we will discuss three different scenarios when a disruption occurs.
+Under all scenarios, if an activity is finished before the disruption, the duration of that activity is deterministic and known as the original activity duration.
 If an activity is started after the disruption, the activity will have a new duration, which is a random number according to a known distribution.
-Additionally, we are considering a finite discrete distribution for the duration after disruption of every activity.
-The decision of crashing has to be made the same time when the activity starts and cannot be changed after that.\\
+The key difference between three scenarios is for the activities which have been started but not finished when the disruption occurs.
+\\
 	\newline The notation for the model is displayed as follows:
@@
 
-\noi Given the assumption that only one disruption will occur, we can model the problem as a two stage stochastic mixed integer program.
+	\subsection{Activities already started are not affected by the disruption} \label{scen1}
+		In the first part we consider a scenario where the disruption will not affect the activities that have already started.
+Additionally, we are considering a finite discrete distribution for the duration after disruption of every activity.
+The decision of crashing has to be made the same time when the activity starts and cannot be changed after that.
+\\
+		\newline Given the assumption that only one disruption will occur, we can model the problem as a two stage stochastic mixed integer program.
 We assume after disruption the duration of activity \(i\) will be \(D_i + d_i^\omega \geq 0\) in realization \(\omega\).
 The master program can be displayed as follows:
-	\begin{subequations}
 		\begin{align}
 			\min \quad & \sum_{\omega \in \Omega} f^\omega(t,x) &\\
-			\text{s.t.} \quad & t_k - t_i \geq D_i(1 - \sum_{j \in J} e_jx_{ij}) & \forall (i,k) \in \mathcal{A}\\
+			\text{s.t.} \quad & t_k - t_i \geq D_i(\sum_{j \in J} e_jx_{ij}) & \forall (i,k) \in \mathcal{A}\\
 			& \sum_{j \in J} x_{ij} \leq 1 & \forall i \in I\\
@@
 		\end{align}
-		\label{masterOrigin}
-	\end{subequations}
 		And the subproblem is formed in the following way.
 Here we set up two status variables \(F_i^\omega, G_i^\omega\) for each activity under every circumstance to indicator whether it starts before or after the disruption, since the relationship between the starting time and the disruption time decides the length of that activity.
-	\begin{subequations}
 		\begin{align}
 			f^\omega(t,x) = \min \quad & t_N^\omega &\\
-			\text{s.t.} \quad & H^\omega - F_i^\omega M \leq t_i & \forall i \in I\\
-			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I\\
-			& F_i^\omega + G_i^\omega = 1 & \forall i \in I\\
-			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I\\
-			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I\\
-			& x_{ij}^\omega + (1 - F_i^\omega) \geq x_{ij} & \forall i \in I, j \in J \\
-			& x_{ij}^\omega - (1 - F_i^\omega) \leq x_{ij} & \forall i \in I, j \in J \\
-			& t_N^\omega \geq t_i^\omega & \forall i \in I\\
-			& t_k^\omega - t_i^\omega \geq (D_i + d_i^\omega G_i^\omega)(\sum_{j \in J} e_jx_{ij}^\omega) & \forall i \in I, j \in J \label{constr:Duration}\\
-			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I \\
+			\text{s.t.} \quad & H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega\\
+			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega\\
+			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega\\
+			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega\\
+			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \\
+			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \\
+			& t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega\\
+			& t_k^\omega - t_i^\omega \geq (D_i + d_i^\omega G_i^\omega)(\sum_{j \in J} e_jx_{ij}^\omega) & \forall i \in I, j \in J, \omega \in \Omega\\
+			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega\\
 			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega\\
-			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J\\
-			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J
+			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J, \omega \in \Omega\\
+			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J, \omega \in \Omega
 		\end{align}
-	\end{subequations}
-In this formulation, the right hand side of constraint (\ref{constr:Duration}) is not a linear expression of the decision variables.
+		In this formulation, the right hand side of constraint (15) is not a linear expression of the decision variables.
 However, since both \(G_i^\omega\) and \(x_{ij}^\omega\) are binary variables, it is possible to linearize this constraint by letting \(Z_{ij}^\omega\) represent \(G_i^\omega x_{ij}^\omega\):
-	\begin{subequations}
 		\begin{align*}
-		& Z_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J\\
-		& Z_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J\\
-		& Z_{ij}^\omega \geq x_{ij}^\omega + G_i^\omega - 1 & \forall i \in I, j \in J
+			& Z_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J, \omega \in \Omega\\
+			& Z_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J, \omega \in \Omega\\
+			& Z_{ij}^\omega \geq x_{ij}^\omega + G_i^\omega - 1 & \forall i \in I, j \in J, \omega \in \Omega
 		\end{align*}
-	\end{subequations}
+	\subsection{Unfinished part of the activities already started are affected by the disruption} \label{scen2}
+		In this part we consider that the disruption will change only the unfinished part of activities which are not finished at the time of disruption.
+For example, if the disruption time is \(H\), activity \(i\) starts at \(t_i \leq H\), the original duration is \(D_i\), and \(t_i + D_i \geq H\), then the disruption will only affect the part after it, which has a length of \(t_i + D_i - H\), by multiplying it by a random coefficient \(r_i\).
+Therefore, the total time to finish activity \(i\) is \(H - t_i + r_i(t_i + D_i - H)\).
+If an activity is crashed by option \(j\), which will bring down the original duration to a fraction \(e_j\) of \(D_i\), while it still starts before the disruption and ends after the disruption, the total time to finish activity \(i\) is \(H - t_i + r_i(t_i + D_ie_j - H)\), where \(t_i + D_ie_j \geq H\).
+Same as stated in Section~\ref{scen1}, the crashing decisions need to be made as soon as an activity is started and cannot be changed afterwards.\\
+		\newline For each activity, there are only three types of position relative to the disruption time.
+An activity could be finished before disruption, started before disruption but not finished at disruption, and not yet started at disruption.
+Different from Section~\ref{scen1}, here whether each activity is finished at disruption needs to be recorded as well because it is necessary to distinguish which case matches the situation of each activity.
+For simplicity, we introduce more status variables \(\tilde{F}_i^\omega, \tilde{G}_i^\omega\) to indicator whether, according to the original plan, activity \(i\) is finished or not by disruption.
+We further set up three indicator variables \(S_{i1}^\omega, S_{i2}^\omega, S_{i3}^\omega\) to indicate which case is activity \(i\).
+\(S_{i1}^\omega, S_{i2}^\omega, S_{i3}^\omega\) can be directly derived from \(F_i^\omega, G_i^\omega, \tilde{F}_i^\omega, \tilde{G}_i^\omega\).
+\\
+		\newline Since properties of the problem before disruption do not change across scenarios, we could use the same master program as Section~\ref{scen1}.
+The subproblem of this scenario is formulated as follows:
+		\begin{align}
+			f^\omega(t,x)& = \min \quad t_N^\omega &\\
+			\text{s.t.} \quad & H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega\\
+			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega\\
+			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& H^\omega - \tilde{F}_i^\omega M \leq t_i + D_i(\sum_{j \in J}e_jx_{ij}) & \forall i \in I, \omega \in \Omega\\
+			& H^\omega + \tilde{G}_i^\omega M \geq t_i + D_i(\sum_{j \in J}e_jx_{ij}) & \forall i \in I, \omega \in \Omega\\
+			& \tilde{F}_i^\omega + \tilde{G}_i^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega\\
+			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega\\
+			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \\
+			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \\
+			& t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega\\
+			& F_i^\omega + \tilde{G}_i^\omega \leq 1 + S_{i1}^\omega & \forall i \in I, \omega \in \Omega \\
+			& F_i^\omega + \tilde{F}_i^\omega \leq 1 + S_{i2}^\omega & \forall i \in I, \omega \in \Omega \\
+			& G_i^\omega + \tilde{G}_i^\omega \leq 1 + S_{i3}^\omega & \forall i \in I, \omega \in \Omega \\
+			& S_{i1}^\omega + S_{i2}^\omega + S_{i3}^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& t_k^\omega - t_i^\omega \geq \left[\left[t_i^\omega + (\sum_{j \in J} e_jx_{ij}^\omega)D_i - H^\omega\right] r_i^\omega +(H^\omega - t_i^\omega) \right]S_{i1}^\omega & \notag \\&\qquad \qquad + D_i(\sum_{j \in J} e_jx_{ij}^\omega)S_{i2}^\omega + \left[D_i (\sum_{j \in J} e_j x_{ij}^\omega) r_i^\omega \right] S_{i3}^\omega & \forall i \in I, j \in J, \omega \in \Omega\\
+			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega\\
+			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega\\
+			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J, \omega \in \Omega\\
+			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J, \omega \in \Omega
+		\end{align}
+		Similar linearization technique could be applied here for constraint (36).
+The difference here is that \(t_i^\omega\) is a continuous variable so the linearization applied is different from Section~\ref{scen2}.
+For example, suppose we denote \(t_{i}^\omega S_{i1}^\omega\) as \(Y_{i1}^\omega\), \(Y_{i1}^\omega = t_{i}^\omega S_{i1}^\omega\) is equivalent to the following set of constraints:
+		\begin{align*}
+			& Y_{i1}^\omega \leq MS_{i1}^\omega & \forall i \in I, \omega \in \Omega\\
+			& Y_{i1}^\omega \geq 0 & \forall i \in I, \omega \in \Omega\\
+			& Y_{i1}^\omega \leq t_i^\omega & \forall i \in I, \omega \in \Omega\\
+			& Y_{i1}^\omega \geq t_i^\omega - M(1-S_{i1}^\omega) & \forall i \in I, \omega \in \Omega
+		\end{align*}
+	\subsection{The unfinished activities at the disruption will start from scratch} \label{scen3}
+		In the last part we consider a case where the disruption will cancel all the work that has been done for all unfinished activities at the time of disruption.
+All finished activities remain intact.
+Suppose activity \(i\), with starting time \(t_i\) and original duration \(D_i\) and no crashing, has not been finished at the disruption time \(H\), it will take another \(r_iD_i\) to finish the activity, making the total duration of it \(H - t_i + r_iD_i\), where \(t_i \leq H\) and \(t_i + D_i \geq H\).
+If the activity \(i\) is crashed by option \(j\), it will follow the same logic as in Section~\ref{scen2} and the total elapse time for activity \(i\) will be \(H - t_i + r_iD_ie_j\).\\
+		\newline Following the setup of Section~\ref{scen2}, the subproblem of this scenario can be formulated as follows:
+		\begin{align}
+			f^\omega(t,x)& = \min \quad t_N^\omega &\\
+			\text{s.t.} \quad & H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega\\
+			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega\\
+			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& H^\omega - \tilde{F}_i^\omega M \leq t_i + D_i(\sum_{j \in J}e_jx_{ij}) & \forall i \in I, \omega \in \Omega\\
+			& H^\omega + \tilde{G}_i^\omega M \geq t_i + D_i(\sum_{j \in J}e_jx_{ij}) & \forall i \in I, \omega \in \Omega\\
+			& \tilde{F}_i^\omega + \tilde{G}_i^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega\\
+			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega\\
+			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \\
+			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \\
+			& t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega\\
+			& F_i^\omega + \tilde{G}_i^\omega \leq 1 + S_{i1}^\omega & \forall i \in I, \omega \in \Omega \\
+			& F_i^\omega + \tilde{F}_i^\omega \leq 1 + S_{i2}^\omega & \forall i \in I, \omega \in \Omega \\
+			& G_i^\omega + \tilde{G}_i^\omega \leq 1 + S_{i3}^\omega & \forall i \in I, \omega \in \Omega \\
+			& S_{i1}^\omega + S_{i2}^\omega + S_{i3}^\omega = 1 & \forall i \in I, \omega \in \Omega \\
+			& t_k^\omega - t_i^\omega \geq \left[(\sum_{j \in J} e_jx_{ij}^\omega) D_i r_i^\omega +(H^\omega - t_i^\omega) \right]S_{i1}^\omega & \notag \\&\qquad \qquad + D_i(\sum_{j \in J} e_jx_{ij}^\omega)S_{i2}^\omega + \left[D_i (\sum_{j \in J} e_j x_{ij}^\omega) r_i^\omega \right] S_{i3}^\omega & \forall i \in I, j \in J, \omega \in \Omega\\
+			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega\\
+			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega\\
+			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J, \omega \in \Omega\\
+			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J, \omega \in \Omega
+		\end{align}
+		The linearization technique applied here is same as those in Section~\ref{scen1} and Section~\ref{scen2}.
 
 \section{Decomposition Method to Solve the Stochastic Program}
-In this section we create a decomposition method for the problem in Section~\ref{formulation}, where the disruption affects the unfinished part of the activities that have started by the time of disruption.
+	In this section we focus on the problem formulation of Section~\ref{scen2}, where the disruption affects the unfinished part of the activities that have started by the time of disruption.
 Same procedure can be applied to the other two cases.\\
-\newline 
-The second stage problem, as stated in Section~\ref{formulation}, is a mixed integer program (MIP) with both binary variables and continuous variables passing down from the master problem.
+	\newline The second stage problem, as stated in Section~\ref{scen2}, is a mixed integer program (MIP) with both binary variables and continuous variables passing down from the master problem.
 This problem is neither convex nor continuous.
@@
 However, it is possible to come up with a lower approximation scheme based on dualization.\\
-\newline 
-Here we write down the master program again, with linear constraints (\ref{cuts}) that form a lower approximation of the second stage problem. 
-	\begin{subequations}
+	\newline Here we write down the master program again, with linear constraints (\ref{cuts}) that form a lower approximation of the second stage problem. 
 	\begin{align}
@@
 	\end{align}
-		\label{master}
-	\end{subequations}
-Solving this master program will yield a lower bound of the original problem (\ref{masterOrigin}).
+	Solving this master program will yield a lower bound of the original problem (1) - (5).
 If the cuts can characterize the function, that is, if \[f^\omega(t,x) = \max_{s} v_{s}^\omega + \sum_{i \in I}\sum_{j \in J}\lambda_{ij,s}^\omega (x_{ij} - \hat{x}_{ij,s}) + \sum_{i \in I} \pi_{i,s}^\omega(t_i - \hat{t}_i) \qquad \forall \omega \in \Omega\]
-for all feasible \(x\) and \(t\), then solving problem (\ref{master}) will be equivalent to solving the original problem.
+	for all feasible \(x\) and \(t\), then solving problem (62) - (67) will be equivalent to solving the original problem.
 However, since \(t\) is continuous and \(f^\omega\) is a non-convex function in \(t\), it is impossible to use a set of linear cuts to approximate \(f^\omega\).
-So the optimal value of problem (\ref{master}) is strictly less than that of problem (\ref{masterOrigin}).\\
-\newline 
-Although solving the transformation of the original problem only provides a lower bound, it might still lead to an optimal solution.
-\textcolor{blue}{We would like to derive an algorithm that terminates in finite number of iterations to one optimal solution.}\\
+So the optimal value of problem (62) -(67) is strictly less than that of (1) - (5).\\
+	\newline Although solving the transformation of the original problem only provides a lower bound, it might still lead to an optimal solution.
+\textcolor{blue}{We would like to derive an algorithm that terminates in finite number of iterations to one optimal solution.}
+
 	\textcolor{blue}{Remaining Points:

### 2017-05-22 Paper.tex
Added the paper structure
Added the paper structure

--- 2017-04-03 Writeup/PERT_Report.tex
@@
 \usepackage{pbox}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
      \kern5pt \vrule width1pt} \hrule height1pt}\)} \medskip}
-\allowdisplaybreaks
 
@@
 \newtheorem{example}{Example}
+\newtheorem{definition}{Definition}
 \renewcommand{\textfraction}{0.0}
@@
 \renewcommand{\Re}{{\mathbb R}}
+\newcommand{\mbf}{\mathbf}
 
@@
 
-Haoxiang Yang \ms
-
 \today \ms
@@
 
-\section{Introduction to the Project Management Problem with Disruptions}
-A project could be viewed as a collection of activities, each of which will consume some time and resources.
-There will be precedence relationships between activities due to logical or technological considerations.
-The objective is to find the smallest amount of time needed to finish all activities.
-The project could be represented as an activity network where the length of each link shows the duration of an activity, and the direction of it shows the precedence relationship.
-An activity cannot start until all its predecessors are completed.
-Two dummy nodes \((S,T)\) are created in the network to represent the start and the end of the project.
-In the network setting with no uncertainty, finding the shortest project span is equivalent to finding the longest path from \(S\) to \(T\).
-Since the activity network is usually acyclic, it is easy to use shortest path algorithms to find a longest path in polynomial time.
-More details about the activity network are discussed in \cite{Elmaghraby77}.\\
-\newline In the planning stage of a project, a set of decisions can be made to crash a certain set of activities.
-Here crashing an activity means accelerating its progress or compress its duration.
-In this paper, a discrete set of crashing options will be given to the decision makers, each with a fractional number which equals to the crashed duration divided by the original duration.
-One project can only be crashed once with one specific option.
-Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget.\\
-\newline In this paper, we focus on the perspective of time and we assume that multiple projects can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
-A disruption is an event that may occur any time in the time horizon and will significantly affect the duration of all activities.
-The number of disruption is limited to one for this paper.
-We assume before the disruption the original duration of all activities are deterministic and given.
-The distribution of the timing for the disruption is known as well.
-Once the disruption occurs, the duration of all unfinished activities will be revealed.
-
-\section{A Motivating Example}
-V-42 problem goes here.
-
-\section{Stochastic Program Formulations} \label{formulation}
-In this section we will discuss a scenario in which the disruption does not affect the activities that have already started.
-Under this scenario, if an activity starts before the disruption time, the duration of that activity is deterministic and known as the original activity duration.
-If an activity is started after the disruption, the activity will have a new duration, which is a random number according to a known distribution.
-Additionally, we are considering a finite discrete distribution for the duration after disruption of every activity.
-The decision of crashing has to be made the same time when the activity starts and cannot be changed after that.\\
-\newline The notation for the model is displayed as follows:
-\begin{table}[H]
-	\begin{tabular}{ l l l l }
-		\multicolumn{4}{l}{Indices and index sets} \\
-		\\
-		\(I\) & \(\qquad\) & the set of activities;&\\
-		\(J\) & \(\qquad\) & the set of crashing options;&\\
-		\(\Omega\) & \(\qquad\) & the set of possible realizations of disruption;&\\
-		\\
-		\multicolumn{4}{l}{Parameters} \\
-		\\
-		\(D_{i}\)& \(\qquad\) & original duration of activity \(i\), \(i \in I\);&\\
-		\(e_{j}\) & \(\qquad\) & effectiveness of crashing option \(j\), \(j \in J\);&\\
-		\(B\) & \(\qquad\) & total budget;&\\
-		\(b_{j}\) & \(\qquad\) & cost of crashing option \(j\), \(j \in J\);&\\
-		\(\mathcal{A}\) &\(\qquad\) & set of arcs which represents the precedence relationship;&\\
-		\(H^\omega\) &\(\qquad\) & disruption time in realization \(\omega\), \(\omega \in \Omega\);&\\
-		\\
-		\multicolumn{4}{l}{Decision Variables}\\
-		\\
-		\(t_{i}\) & \(\qquad\) & original starting time of activity \(i\);&\\
-		\(x_{ij}\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) in the original plan; &\\
-		\(F_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts before disruption in realization \(\omega\);&\\
-		\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\);&\\
-		\(\tilde{F}_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) ends when disruption occurs in realization \(\omega\); &\\
-		\(\tilde{G}_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) ends when disruption occurs in realization \(\omega\); &\\
-	\end{tabular}
-\end{table}
-
-\noi Given the assumption that only one disruption will occur, we can model the problem as a two stage stochastic mixed integer program.
-We assume after disruption the duration of activity \(i\) will be \(D_i + d_i^\omega \geq 0\) in realization \(\omega\).
-The master program can be displayed as follows:
-	\begin{subequations}
-		\begin{align}
-			\min \quad & \sum_{\omega \in \Omega} f^\omega(t,x) &\\
-			\text{s.t.} \quad & t_k - t_i \geq D_i(1 - \sum_{j \in J} e_jx_{ij}) & \forall (i,k) \in \mathcal{A}\\
-			& \sum_{j \in J} x_{ij} \leq 1 & \forall i \in I\\
-			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij} \leq B &\\
-			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J
-		\end{align}
-		\label{masterOrigin}
-	\end{subequations}
-And the subproblem is formed in the following way.
-Here we set up two status variables \(F_i^\omega, G_i^\omega\) for each activity under every circumstance to indicator whether it starts before or after the disruption, since the relationship between the starting time and the disruption time decides the length of that activity.
-	\begin{subequations}
-		\begin{align}
-			f^\omega(t,x) = \min \quad & t_N^\omega &\\
-			\text{s.t.} \quad & H^\omega - F_i^\omega M \leq t_i & \forall i \in I\\
-			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I\\
-			& F_i^\omega + G_i^\omega = 1 & \forall i \in I\\
-			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I\\
-			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I\\
-			& x_{ij}^\omega + (1 - F_i^\omega) \geq x_{ij} & \forall i \in I, j \in J \\
-			& x_{ij}^\omega - (1 - F_i^\omega) \leq x_{ij} & \forall i \in I, j \in J \\
-			& t_N^\omega \geq t_i^\omega & \forall i \in I\\
-			& t_k^\omega - t_i^\omega \geq (D_i + d_i^\omega G_i^\omega)(\sum_{j \in J} e_jx_{ij}^\omega) & \forall i \in I, j \in J \label{constr:Duration}\\
-			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I \\
-			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega\\
-			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J\\
-			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J
-		\end{align}
-	\end{subequations}
-In this formulation, the right hand side of constraint (\ref{constr:Duration}) is not a linear expression of the decision variables.
-However, since both \(G_i^\omega\) and \(x_{ij}^\omega\) are binary variables, it is possible to linearize this constraint by letting \(Z_{ij}^\omega\) represent \(G_i^\omega x_{ij}^\omega\):
-	\begin{subequations}
-		\begin{align*}
-		& Z_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J\\
-		& Z_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J\\
-		& Z_{ij}^\omega \geq x_{ij}^\omega + G_i^\omega - 1 & \forall i \in I, j \in J
-		\end{align*}
-	\end{subequations}
-
-\section{Decomposition Method to Solve the Stochastic Program}
-In this section we create a decomposition method for the problem in Section~\ref{formulation}, where the disruption affects the unfinished part of the activities that have started by the time of disruption.
-Same procedure can be applied to the other two cases.\\
-\newline 
-The second stage problem, as stated in Section~\ref{formulation}, is a mixed integer program (MIP) with both binary variables and continuous variables passing down from the master problem.
-This problem is neither convex nor continuous.
-This type of stochastic mixed integer problem has been studied by many researchers.
-Primal methods are derived using Benders-like cuts to characterize the second stage function.
-\cite{laporte1993integer} developed an integer L-shaped method to solve two stage stochastic programs with only binary first stage variables and complete recourse.
-More recently, \cite{zou2016nested} proposed a type of Lagrangian cuts and strengthened Benders cuts to solve multi-stage stochastic integer programs with binary state variables.
-The Lagrangian cuts are tight at the feasible previous stage solution, valid globally and finite.
-On the other side, dual methods are also widely used, especially in solving multi-stage stochastic mixed integer problems.
-Progressive hedging method has been successfully used in many occasions \textcolor{blue}{(add citations here about the dual method)}.
-In general, it is hard to come up with a lower approximation tight at the solution, especially when our state variables contain both binary ones and continuous ones.
-However, it is possible to come up with a lower approximation scheme based on dualization.\\
-\newline 
-Here we write down the master program again, with linear constraints (\ref{cuts}) that form a lower approximation of the second stage problem. 
-	\begin{subequations}
-		\begin{align}
-			\min \quad & \sum_{\omega \in \Omega} \theta^\omega &\\
-			\text{s.t.} \quad & t_k - t_i \geq D_i(\sum_{j \in J} e_jx_{ij}) & \forall (i,k) \in \mathcal{A}\\
-			& \sum_{j \in J} x_{ij} \leq 1 & \forall i \in I\\
-			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij} \leq B &\\
-			& \theta^{\omega} \geq v_{s}^\omega + \sum_{i \in I}\sum_{j \in J}\lambda_{ij,s}^\omega (x_{ij} - \hat{x}_{ij,s}) + \sum_{i \in I} \pi_{i,s}^\omega(t_i - \hat{t}_i)& s = 1,2,\dots \label{cuts}\\
-			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J
-		\end{align}
-		\label{master}
-	\end{subequations}
-Solving this master program will yield a lower bound of the original problem (\ref{masterOrigin}).
-If the cuts can characterize the function, that is, if \[f^\omega(t,x) = \max_{s} v_{s}^\omega + \sum_{i \in I}\sum_{j \in J}\lambda_{ij,s}^\omega (x_{ij} - \hat{x}_{ij,s}) + \sum_{i \in I} \pi_{i,s}^\omega(t_i - \hat{t}_i) \qquad \forall \omega \in \Omega\]
-for all feasible \(x\) and \(t\), then solving problem (\ref{master}) will be equivalent to solving the original problem.
-However, since \(t\) is continuous and \(f^\omega\) is a non-convex function in \(t\), it is impossible to use a set of linear cuts to approximate \(f^\omega\).
-So the optimal value of problem (\ref{master}) is strictly less than that of problem (\ref{masterOrigin}).\\
-\newline 
-Although solving the transformation of the original problem only provides a lower bound, it might still lead to an optimal solution.
-\textcolor{blue}{We would like to derive an algorithm that terminates in finite number of iterations to one optimal solution.}\\
-\textcolor{blue}{Remaining Points:
+\section{Introduction}
 	\begin{itemize}
-		\item write down the algorithm to generate a good solution
-		\item describe the computational result of the optimality gap
-		\item describe the comparison between the disruption model and the deterministic model
-		\item prove how loose the lagrangian cut method can be
-		\item assume if every activity needs to start as soon as all its prerequisites have finished
-		\item assume continuous x: could we get rid of all binary variables?
+		\item Literature review: PERT set up, applications.
+		\item Literature review: stochastic disruptions.
+		\item Paper structure.
 	\end{itemize}
-}
+\section{Problem Formulation}
+	\begin{itemize}
+		\item Static PERT problem formulation/ Stochastic PERT literature review: simulation optimization/ Distributionally robust: Natarajan
+		\item Assumptions: not affected by the disruption once started.
+		\item Formulation: extensive, master, sub
+	\end{itemize}
+\section{Decomposition Method}
+	\begin{itemize}
+		\item Cut generation
+		\item Branch and bound method
+	\end{itemize}
+\section{Computational Results}
+\section{Conclusions}
+	\begin{itemize}
+		\item Contributions
+		\item Further directions
+	\end{itemize}
 

### 2017-05-23 Paper.tex
Added introduction
Added introduction

@@
 
-\section{Introduction}
+\section{Introduction} \label{sec:intro}
 	\begin{itemize}
@@
 	\end{itemize}
-\section{Problem Formulation}
+	\textcolor{blue}{One sentence background/history on project management.} A project could be viewed as a collection of activities, each of which will consume some time and resources.
+There will be precedence relationships between activities due to logical or technological considerations.
+The objective is to find the smallest amount of time needed to finish all activities.
+The project could be represented as an activity network where the length of each link shows the duration of an activity, and the direction of it shows the precedence relationship.
+An activity cannot start until all its predecessors are completed.
+Two dummy nodes \((S,T)\) are created in the network to represent the start and the end of the project.
+In the network setting with no uncertainty, finding the shortest project span is equivalent to finding the longest path from \(S\) to \(T\).
+Since the activity network is usually acyclic, it is easy to use shortest path algorithms to find a longest path in polynomial time.
+Multiple projects can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
+More details about the activity network are discussed in \cite{Elmaghraby77}.\\
+	\newline 
+	In the planning stage of a project, decisions can be made to crash a certain set of activities in order to achieve the shortest project span.
+Here crashing an activity means accelerating its progress or compress its duration.
+In this paper, a discrete set of crashing options will be given to the decision makers, each with a fractional number which equals to the crashed duration divided by the original duration.
+One project can only be crashed once with one specific option.
+Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget.
+Static crashing optimization problem is first researched in \textcolor{blue}{list the original crashing problem literature} and then extended to incorporate uncertainty of activity durations in \textcolor{blue}{list the stochastic crashing optimization problems.}\\
+	\newline
+	The uncertainty in our paper lies in the timing and the magnitude of the stochastic disruption, which is modeled in a different way from the random variable distribution in the stochastic programming setting, or from the uncertainty set in the robust optimization setting.
+A stochastic disruption is an event that may occur any time in the time horizon and change the system parameters significantly.
+\textcolor{blue}{list the past papers about the (lacked) work in the stochastic disruption}.\\
+	\newline
+	Since it is a new model of uncertainty, we first formally describe the crashing optimization problem with disruptions.
+Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}.
+The large scale and the discrete non-convex nature of the extended formulation means it may not be solved efficiently to desirable tolerance level.
+In Section~\ref{sec:decomposition}, a branch-and-bound method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
+We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.
+\\
+	\newline
+	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the static solution obtained by solving the crashing optimization, and the time improvement by using the decomposition method in Section~\ref{sec:decomposition} compared to solving the extensive formulation.
+The experiment result shows \textcolor{blue}{append summary of the experiment results here.} We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
+
+\section{Problem Formulation} \label{sec:formulation}
 	\begin{itemize}
@@
 		\item Assumptions: not affected by the disruption once started.
+	\end{itemize}
+	Suppose at most one stochastic disruption will occur in the entire project span. When the disruption happens is a random variable, of which the distribution is known to us. The stochastic disruption
+
+\section{Decomposition Method} \label{sec:decomposition}
+	\begin{itemize}
 		\item Formulation: extensive, master, sub
-	\end{itemize}
-\section{Decomposition Method}
-	\begin{itemize}
 		\item Cut generation
@@
 	\end{itemize}
-\section{Computational Results}
-\section{Conclusions}
+
+\section{Computational Results} \label{sec:results}
+
+\section{Conclusions} \label{sec:conclusions}
 	\begin{itemize}

### 2017-06-06 Paper.tex
Small change in writeup

@@
 	\newline
-	Since it is a new model of uncertainty, we first formally describe the crashing optimization problem with disruptions.
+	We first formally describe the crashing optimization problem with disruptions.
 Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}.
@@
 	\end{itemize}
-	Suppose at most one stochastic disruption will occur in the entire project span. When the disruption happens is a random variable, of which the distribution is known to us. The stochastic disruption
+	\textcolor{blue}{list the literature of static PERT}
 

### 2017-06-06 Paper.tex
Updated Writeup with the deterministic formulation

--- 2017-05-23 Paper.tex
@@
 Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget.
-Static crashing optimization problem is first researched in \textcolor{blue}{list the original crashing problem literature} and then extended to incorporate uncertainty of activity durations in \textcolor{blue}{list the stochastic crashing optimization problems.}\\
+Static crashing optimization problem is first researched in \cite{fulkerson1961network, kelley1961criticalpath}.
+If we assume a finite set of crashing options, the problem could be modeled as a mixed integer program.
+\textcolor{blue}{list the original crashing problem literature} The static model can be extended to incorporate uncertainty of activity durations.
+Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is really possible to provide an analytical expression of the true expected project span.
+\textcolor{blue}{list the literature of stochastic crashing optimization problems.} Another approach to handle the uncertainty is the robust optimization method.
+In the robust optimization setting, the objective is to minimize the worst case project span within the uncertainty set.
+\textcolor{blue}{list the literature of robust crashing optimization problems}\\
 	\newline
@@
 A stochastic disruption is an event that may occur any time in the time horizon and change the system parameters significantly.
+Yu and Qi \cite{yu2004disruptionmgt} introduced scenario-based optimization models and applied it to solve airline scheduling problems.
+Morton et al.
+\cite{morton2009sealift} introduced the modeling of a sealift scheduling problem under finite number of stochastic disruptions within a stochastic programming structure.
+This structure ``falls between standard two-stage and multi-stage stochastic programs for a multi-period problem" and reduces the size of the problem to a quadratic growth in the number of time periods.
+Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing continuous disruption time instead of the fixed stages.
 \textcolor{blue}{list the past papers about the (lacked) work in the stochastic disruption}.\\
@@
 	\end{itemize}
-	Suppose at most one stochastic disruption will occur in the entire project span. When the disruption happens is a random variable, of which the distribution is known to us. The stochastic disruption
+	The deterministic project crashing optimization problem is widely researched since 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
+Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\).
+The budget limit \(B\) and the nominal length of each activity \(D_i\) are given.
+For each activity \(i \in I\), there is a finite set of crashing options \(j \in J_i\) and each of them will incur a cost of \(b_{ij}\) while cutting down the nominal activity length to \(1 - e_{ij}\) of the nominal length.
+We assume each activity could be crashed at most once and the problem could be formulated as follows.
+	\begin{subequations} \label{prob:static}
+		\begin{align}
+			\min \quad & t_N &\\
+			\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} y_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
+			& t_i \geq 0 & \forall i \in I\\
+			& t_N \geq t_i & \forall i \in I \\
+			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}y_{ij} \leq B & \\
+			& \sum_{j \in J_i} y_{ij} \leq 1 & \forall i \in I\\
+			& y_{ij} \in \{0,1\} & \forall i \in I, j \in J_i&
+		\end{align}
+	\end{subequations}
+	Based on this formulation, we can derive the stochastic optimization and the robust optimization models with reference to \textcolor{blue}{list the literature of stochastic/robust crashing optimization problems}.
+We omit these formulations in this paper since our uncertainty model is different from the literature listed above.\\
+	\newline
+	We assume at most one stochastic disruption will occur in the project span.
+The disruption will not affect the activities that have already started but will change the length of activities starting after it according to some given finite discrete distributions.
+The decision of crashing has to be made the same time when the activity starts and cannot be changed after that.
+Since there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
+Notice that the definition of the first stage is different from the traditional stochastic program setting.
+Here the first stage contains all the decisions if no disruption occurs and the second stage will characterize the decisions for each realization of the disruption.
+This means that the first stage decision variables are not limited to a certain time period but can be all over the entire time horizon, which allows us to model continuous disruption time.\\
+	\newline
+	The notation for the model is displayed as follows:
+	\begin{table}[H]
+		\begin{tabular}{ l l l l }
+			\multicolumn{4}{l}{Indices and index sets} \\
+			\\
+			\(I\) & \(\qquad\) & the set of activities;&\\
+			\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i\), \(i \in I\);&\\
+			\(\Omega\) & \(\qquad\) & the set of possible realizations of disruption;&\\
+			\(\mathcal{A}\) &\(\qquad\) & set of arcs which represents the precedence relationship;&\\
+			\\
+			\multicolumn{4}{l}{Parameters} \\
+			\\
+			\(D_{i}\)& \(\qquad\) & original duration of activity \(i\), \(i \in I\);&\\
+			\(e_{ij}\) & \(\qquad\) & effectiveness of crashing option \(j\), \(i \in I, j \in J_i\);&\\
+			\(B\) & \(\qquad\) & total budget;&\\
+			\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j\), \(i \in I, j \in J_i\);&\\
+			\(H^\omega\) &\(\qquad\) & disruption time in scenario \(\omega\), \(\omega \in \Omega\);&\\
+			\(d_{i}^\omega\) & \(\qquad\)&the change of duration of activity \(i\) in realization \(\omega\), &\\
+			& \(\qquad\) & if the activity is started after the disruption, \(i \in I, \omega \in \Omega\);& \\
+			\(p^\omega\) & \(\qquad\) & the probability of scenario \(\omega\), \(\omega \in \Omega\);& \\
+			\(p^0\) & \(\qquad\) & the probability of no disruption;& \\
+			\\
+			\multicolumn{4}{l}{Decision Variables}\\
+			\\
+			\(t_{i}\) & \(\qquad\) & nominal starting time of activity \(i\), \(i \in I\);&\\
+			\(x_{ij}\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) in the nominal plan, \(i \in I, j \in J_i\); &\\
+			\(t_{i}^\omega\) & \(\qquad\) & starting time of activity \(i\) under scenario \(\omega\), \(i \in I, \omega \in \Omega\);&\\
+			\(x_{ij}^\omega\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) under scenario \(\omega\), \(i \in I, j \in J_i, \omega \in \Omega \); &\\
+			\(F_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts before disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
+			\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\).&\\
+		\end{tabular}
+	\end{table}
+	\noi The extensive formulation of the two-stage stochastic program is shown as Formulation~(\ref{prob:extensive}).
+Here \(M\) is a large number to enforce the logic relationships.
+In this problem, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
+Variables \(F^\omega_i\) and \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:f}) - (\ref{cons:fg})).
+This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
+\\
+	\newline
+	We have to use a set of non-anticipativity constraints (\ref{cons:tf1}) - (\ref{cons:xf2}), different from the one used in a traditional stochastic programming setting, since the first stage decision variables here spans the entire time horizon.
+These logic constraints ensure the decisions made before the disruption time in each scenario should be the same as the nominal decisions before the same time point, because decisions made with the same amount information should be the same.\\
+	\begin{subequations} \label{prob:extensive}
+		\begin{align}
+			\min \quad & \sum_{\omega \in \Omega} p^\omega t_N^\omega + p^0 t_N& \\
+			\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega \\
+			& t_N \geq t_i & \\
+			& t_i^\omega \geq 0 & \forall i \in I, \omega \in \Omega\\
+			& t_i \geq 0 & \forall i \in I\\
+			& H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:f}\\
+			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:g}\\
+			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \label{cons:fg}\\
+			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf1}\\
+			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf2}\\
+			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \label{cons:xf1}\\
+			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \label{cons:xf2}\\
+			& t_k^\omega - t_i^\omega \geq (D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J} e_jx_{ij}^\omega) & \forall i \in I, j \in J, \omega \in \Omega \label{cons:duration}\\
+			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega \label{cons:crashLim}\\
+			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega \label{cons:budget}\\
+			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J, \omega \in \Omega\\
+			& F_i^\omega, G_i^\omega \in \{0,1\} & \forall i \in I, \omega \in \Omega\\
+			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J, \omega \in \Omega
+		\end{align}
+	\end{subequations}
 
@@
 	\begin{itemize}
-		\item Formulation: extensive, master, sub
+		\item Formulation: master, sub
 		\item Cut generation
@@
 	\end{itemize}
+	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary and continuous state variables.
+A state variable here is a variable whose value is passed from the first stage to the second stage.
+Two-stage stochastic linear program could be solved nicely using Benders decomposition (\textcolor{blue}{cite Benders decomposition}).
+However, it is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly.
+\textcolor{blue}{cite literature about the stochastic integer programs}.
+\\
+	\newline 
+	Recently Zou et al.
+\cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables.
+Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts.
+Although this result could not be directly applied in our problem due to the continuous state variable \(t\), it provides a pivotal theoretical basis for our decomposition method.\\
+	\newline
+	First we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems.
+It is difficult to solve the master problem because the function \(f^\omega(x,t)\) is non-convex and it is hard to derive its analytical form.
 

### 2017-06-12 Paper.tex
Debugged version of Exec and Func

@@
 			\min \quad & t_N &\\
-			\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} y_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
+			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \\
+			& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
+			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \\
+			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
 			& t_i \geq 0 & \forall i \in I\\
-			& t_N \geq t_i & \forall i \in I \\
-			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}y_{ij} \leq B & \\
-			& \sum_{j \in J_i} y_{ij} \leq 1 & \forall i \in I\\
-			& y_{ij} \in \{0,1\} & \forall i \in I, j \in J_i&
+			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J_i&
 		\end{align}
@@
 			\(F_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts before disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
-			\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\).&\\
+			\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
+			\(S_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\
 		\end{tabular}
@@
 This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
-\\
+For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\).
+This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints (\ref{cons:linearize1}) - (\ref{cons:linearize3}).\\
 	\newline
@@
 			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf2}\\
-			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \label{cons:xf1}\\
-			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J, \omega \in \Omega \label{cons:xf2}\\
-			& t_k^\omega - t_i^\omega \geq (D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J} e_jx_{ij}^\omega) & \forall i \in I, j \in J, \omega \in \Omega \label{cons:duration}\\
-			& \sum_{j \in J} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega \label{cons:crashLim}\\
-			& \sum_{i \in I}\sum_{j \in J} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega \label{cons:budget}\\
-			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J, \omega \in \Omega\\
+			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
+			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
+			& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
+			& \sum_{j \in J_i} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega \label{cons:crashLim}\\
+			& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega \label{cons:budget}\\
+			& S_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
+			& S_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
+			& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
+			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J_i, \omega \in \Omega\\
 			& F_i^\omega, G_i^\omega \in \{0,1\} & \forall i \in I, \omega \in \Omega\\
-			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J, \omega \in \Omega
+			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J_i, \omega \in \Omega
 		\end{align}
@@
 	\end{itemize}
-	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary and continuous state variables.
+	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary (\(x\)) and continuous (\(t\)) state variables.
 A state variable here is a variable whose value is passed from the first stage to the second stage.
@@
 	\newline
-	First we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems.
-It is difficult to solve the master problem because the function \(f^\omega(x,t)\) is non-convex and it is hard to derive its analytical form.
+	First we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}).
+Notice that it is difficult to directly solve the master problem because the function \(f^\omega\) is non-convex and it is hard to derive its analytical form.
+	\begin{subequations}
+		\label{prob:master}
+		\begin{align}
+		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega f^\omega(x,t) & \\
+		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I\\
+		& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
+		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \\
+		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
+		& t_i \geq 0 & \forall i \in I\\
+		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i&
+		\end{align}
+	\end{subequations}
+	\begin{subequations}
+		\label{prob:sub}
+		\begin{align}
+			(S^\omega) \quad f^\omega(\hat{x},\hat{t}) = \min \quad & t_N & \\
+			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \\
+			& H^\omega - F_i M \leq t_i & \forall i \in I \\
+			& H^\omega + G_i M \geq t_i & \forall i \in I \\
+			& F_i + G_i = 1 & \forall i \in I \\
+			& t_i + (1-F_i) M \geq \hat{t}_i & \forall i \in I\\
+			& t_i - (1-F_i) M \leq \hat{t}_i & \forall i \in I \\
+			& x_{ij} + (1-F_i) \geq \hat{x}_{ij} & \forall i \in I, j \in J_i \\
+			& x_{ij} - (1-F_i) \leq \hat{x}_{ij} & \forall i \in I, j \in J_i \\
+			& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij} & \forall i \in I, (i,k) \in \mathcal{A}\\
+			&\sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B &\\
+			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
+			& S_{ij} \leq G_i & \forall i \in I, j \in J_i \\
+			& S_{ij} \leq x_{ij} & \forall i \in I, j \in J_i\\
+			& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i\\
+			& t_i \geq 0 & \forall i \in I \\
+			& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i
+		\end{align}
+	\end{subequations}
+	\textcolor{blue}{Introduce the Lagrangian cut and how it is generated.}
+	Since our state variable contains both continuous variables \(t\) and binary variables \(x\), the Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed.
+This means that if we carry out a cutting plane scheme using the Lagrangian cuts, we will not solve the problem to the exactness but will only obtain a lower bound.
+\\
+	\newline
+	One important observation to help with this issue is that if we can determine the temporal relationship between every activity and the disruption, the restricted version of the function \(f^\omega\) will be convex in \(t\), and we could find a tight and valid Lagrangian cut similar to those in \cite{zou2016nested}.
+This means, for example, if for a specific scenario \(\omega\), \(H^\omega = 5\), and for each activity \(i \in I\) we know whether its starting time \(t_i\) is less than, larger than or equal to \(H^\omega = 5\), then there is a finite set of linear constraints that could be generated to fully characterize \(f^\omega(x,t)\) in formulation~(\ref{prob:master}).
+This property is true mainly because once we know the temporal relationship between the starting time of each activity and the disruption time, it is always optimal to start the activity at its earliest possible time.
+We will prove this property as follows.
+\\
+	\newline
+	\textcolor{blue}{State the Proofs of the tightness/validity of the Lagrangian cuts}\\
+	\newline
+	The temporal relationship could be determined by a branch-and-bound scheme.
+Although theoretically for each scenario there are exponential number of possible temporal relationships because each activity can either be before the disruption time or after that, there are only a small number of activities, of which the optimal starting time of the deterministic problem (\ref{prob:static}) is close to the disruption time, that really matter.
+If an activity should be starting much earlier than the disruption time in the deterministic problem, it usually will significantly increase the length of the project span by delaying the start of such activity.
+If an activity cannot start until a time much later than the disruption time, it is usually not possible to make it start before the disruption time without committing crashing resources heavily on its precedent activities, which may likely lead to an inferior solution.
 

### 2017-06-12 src/Case1Exec.jl

@@ -55,7 +55,7 @@ while nodeList != []
     end
 
     # for each subproblem, solve the subproblem corresponding to the current node
-    tempUB = p*mpObj;
+    tempUB = mpObj;
     zDiff = Dict();
     zDiffMax = -Inf;
     zDiffMaxIndex = 1;

### 2017-06-12 src/Case1Func.jl

@@ -130,9 +130,9 @@ end
 
 # function to create the basic version of the master program
 function createMaster(D,d,b,B,ee,II,JJ,SS,GG,p)
-  mp = Model(solver = CplexSolver(CPXPARAM_ScreenOutput = 0));
+  mp = Model(solver = CplexSolver());
   @variables(mp, begin
-    θ[s in SS;s >= 2]
+    θ[s in SS;s >= 2] >= 0
     x[i in II,j in JJ], Bin
     t[i in II] >= 0
     tN >= 0
@@ -141,7 +141,7 @@ function createMaster(D,d,b,B,ee,II,JJ,SS,GG,p)
   @constraint(mp, durationConstr[g in GG], t[g[2]] - t[g[1]] >= D[g[1]]*(1-sum(ee[j]*x[g[1],j] for j in JJ)));
   @constraint(mp, tNConstr[i in II], tN >= t[i]);
   @constraint(mp, xConstr[i in II], sum(x[i,j] for j in JJ) <= 1);
-  @objective(mp,Min,p*tN + sum(1/(length(SS)-1)*θ[s] for s in SS if s >= 2));
+  @objective(mp,Min,p*tN + sum((1 - p)/(length(SS)-1)*θ[s] for s in SS if s >= 2));
 
   return mp;
 end
@@ -188,13 +188,15 @@ function subInt(xs,ts,D,b,B,ee,II,I1,I2,dscen,JJ,GG)
     t[i in II] >= 0
     tN >= 0
   end);
-  @constraint(mp, budgetConstr, sum(sum(b[i,j]*x[i,j] for j in JJ) for i in II) <= B);
-  @constraint(mp, durationConstr1[g in GG;g[1] in I1], t[g[2]] - t[g[1]] >= D[g[1]]*(1-sum(ee[j]*x[g[1],j] for j in JJ)));
-  @constraint(mp, durationConstr2[g in GG;g[1] in I2], t[g[2]] - t[g[1]] >= (D[g[1]]+dscen[g[1]])*(1-sum(ee[j]*x[g[1],j] for j in JJ)));
-  @constraint(mp, tNConstr[i in II], tN >= t[i]);
-  @constraint(mp, xConstr[i in II], sum(x[i,j] for j in JJ) <= 1);
-  @constraint(mp, tConstant[i in I1], t[i] == ts[i]);
[…]

### 2017-06-20 src/Case1Exec.jl
Updated the formulation and added the extensive formulation

@@ -3,7 +3,10 @@
 include("Case1Func.jl");
 include("def.jl");
 # read in data of scenarios and the activity network
-InputAdd = "test_Input_graph_Semi1.csv";
+# Semi1 is the one with fixed disruption time
+# Semi2 is the one with fixed disruption magnitude
+# Fixed is the one with both disruption time and disruption magnitude fixed
+InputAdd = "test_Input_graph_Fixed.csv";
 D,d,H,b,B,ee,II,JJ,M,SS,GG,dH,dR,p = readIn(InputAdd);
 
 # prepare the scenario data: each scenario's information with each activity's duration after disruption

### 2017-06-20 src/Case1Func.jl

@@ -425,3 +425,42 @@ function generateCut(s,πg,λg,zlag,xSol,tSol,II,JJ)
   lc = LagCut(s,πg,λg,zlag - sum(πg[i]*tSol[i] for i in II) - sum(sum(λg[i,j]*xSol[i,j] for j in JJ) for i in II));
   return lc;
 end
+
+# function to build the extensive formulation
+function fullExt(D,dscen,H,b,B,ee,II,JJ,M,SS,GG,p)
+  mext = Model(solver = CplexSolver());
+
+  @variable(mext,tN0 >= 0);
+  @variable(mext,tN[s in SS] >= 0);
+  @variable(mext,t[i in II, s in SS] >= 0);
+  @variable(mext,x[i in II, j in JJ, s in SS], Bin);
+  @variable(mext,t0[i in II] >= 0);
+  @variable(mext,x0[i in II, j in JJ], Bin);
+  @variable(mext,F[i in II, s in SS], Bin);
+  @variable(mext,G[i in II, s in SS], Bin);
+  @variable(mext,S[i in II, j in JJ, s in SS], Bin);
+
+  @constraint(mext, tN0Constr[i in II], tN0 >= t0[i]);
+  @constraint(mext, tNConstr[i in II, s in SS], tN[s] >= t[i,s]);
+  @constraint(mext, FConstr[i in II, s in SS], H[s] - F[i,s]*M[s] <= t0[i]);
+  @constraint(mext, GConstr[i in II, s in SS], H[s] + G[i,s]*M[s] >= t0[i]);
+  @constraint(mext, FGConstr[i in II, s in SS], F[i,s] + G[i,s] == 1);
+  @constraint(mext, tConstr1[i in II, s in SS], t[i,s] + (1 - F[i,s])*M[s] >= t0[i]);
+  @constraint(mext, tConstr2[i in II, s in SS], t[i,s] - (1 - F[i,s])*M[s] <= t0[i]);
+  @constraint(mext, xConstr1[i in II, j in JJ, s in SS], x[i,j,s] + (1 - F[i,s]) >= x0[i,j]);
+  @constraint(mext, xConstr2[i in II, j in JJ, s in SS], x[i,j,s] - (1 - F[i,s]) <= x0[i,j]);
[…]

### 2017-07-13 Paper.tex
Updated the formulation and added the extensive formulation
Added the upper bound record and changed the solver

@@
 			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J_i, \omega \in \Omega\\
-			& F_i^\omega, G_i^\omega \in \{0,1\} & \forall i \in I, \omega \in \Omega\\
-			& t_{i}^\omega \geq 0 & \forall i \in I, j \in J_i, \omega \in \Omega
+			& F_i^\omega, G_i^\omega \in \{0,1\}. & \forall i \in I, \omega \in \Omega
 		\end{align}
@@
 Two-stage stochastic linear program could be solved nicely using Benders decomposition (\textcolor{blue}{cite Benders decomposition}).
-However, it is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly.
-\textcolor{blue}{cite literature about the stochastic integer programs}.
 \\
 	\newline 
-	Recently Zou et al.
-\cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables.
-Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts.
-Although this result could not be directly applied in our problem due to the continuous state variable \(t\), it provides a pivotal theoretical basis for our decomposition method.\\
-	\newline
-	First we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}).
-Notice that it is difficult to directly solve the master problem because the function \(f^\omega\) is non-convex and it is hard to derive its analytical form.
+	For our crashing optimization problem, we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}).
+Constraint (\ref{cons:linearCuts}) are generated by solving the sub-problems iteratively for the optimal multipliers \(\pi\) and \(\lambda\).
+In a regular multi-cut Benders decomposition case, the sub problem is a convex optimization problem, usually a linear program.
+This means a finite number of constraints on \(\theta^\omega\) can fully characterize the function \(f^\omega(x,t)\).
+However, in this case \(f^\omega(x,t)\) is a mixed integer linear program.
+It is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly.
+\textcolor{blue}{cite literature about the stochastic integer programs}.
 	\begin{subequations}
@@
 		\begin{align}
-		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega f^\omega(x,t) & \\
+		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega \theta^\omega & \\
 		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I\\
@@
 		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
+		& \theta^\omega \geq \sum_{i \in I} \pi_i^{\omega,k^\omega} t_i + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,k^\omega} x_{ij} + v^{\omega,k^\omega} x_{ij} & \forall \omega \in \Omega, k^\omega = 1,2, \dots \label{cons:linearCuts}\\
 		& t_i \geq 0 & \forall i \in I\\
@@
 	\end{subequations}
-	\textcolor{blue}{Introduce the Lagrangian cut and how it is generated.}
-	Since our state variable contains both continuous variables \(t\) and binary variables \(x\), the Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed.
-This means that if we carry out a cutting plane scheme using the Lagrangian cuts, we will not solve the problem to the exactness but will only obtain a lower bound.
+	Recently Zou et al.
+\cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables.
+Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts.
+To generate the Lagrangian multipliers, a local copy (\(\tau\) and \(z\)) of the state variable (\(\hat{t}\) and \(\hat{x}\)) is first created as in constraint (\ref{cons:local1}) and (\ref{cons:local2}) of formulation (\ref{prob:subLocal}).
+We can then relax the constraint (\ref{cons:local1}) and (\ref{cons:local2}) to create a Lagrangian dual problem (\ref{prob:LagDual}).
+The optimal solution  \(\pi^*\) and \(\lambda^*\) to the Lagrangian dual problem will be used in the Lagrangian cuts as in constraint (\ref{cons:linearCuts}).
+Problem (\ref{prob:LagDual}) can be solved by a subgradient method \textcolor{blue}{cite Fisher's tutorial for solving the Lagrangian Relaxation problem}.\\
+	\begin{subequations}
+		\label{prob:subLocal}
+		\begin{align}
+		(S^\omega_L) \quad \min \quad & t_N & \\
+		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:tN}\\
+		& H^\omega - F_i M \leq t_i & \forall i \in I \\
+		& H^\omega + G_i M \geq t_i & \forall i \in I \\
+		& F_i + G_i = 1 & \forall i \in I \\
+		& t_i + (1-F_i) M \geq \tau_i & \forall i \in I\\
+		& t_i - (1-F_i) M \leq \tau_i & \forall i \in I \\
+		& x_{ij} + (1-F_i) \geq z_{ij} & \forall i \in I, j \in J_i \\
+		& x_{ij} - (1-F_i) \leq z_{ij} & \forall i \in I, j \in J_i \\
+		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij} & \forall i \in I, (i,k) \in \mathcal{A}\\
+		&\sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B &\\
+		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
+		& S_{ij} \leq G_i & \forall i \in I, j \in J_i \\
+		& S_{ij} \leq x_{ij} & \forall i \in I, j \in J_i\\
+		& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i \label{cons:s3}\\
+		& z_{ij} = \hat{x}_{ij} & \forall i \in I, j \in J_i \label{cons:local1}\\
+		& \tau_{i} = \hat{t}_{i} & \forall i \in I \label{cons:local2}\\
+		& t_i \geq 0 & \forall i \in I \label{cons:tPos}\\
+		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i\\
+		& \tau_i \geq 0 & \forall i \in I \\
+		& 0 \leq z_{ij} \leq 1 . & \forall i \in I, j \in J_i \label{cons:zRange}
+		\end{align}
+	\end{subequations}
+	\begin{subequations}
+		\label{prob:LagDual}
+		\begin{align}
+		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N - \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) - \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
+		\text{s.t.} \quad & (\ref{cons:tN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange})
+		\end{align}
+	\end{subequations}
+	The result from \cite{zou2016nested} could not be directly applied in our problem since our state variable contains both continuous variables \(t\) and binary variables \(x\).
+The Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed.
+This means that if we carry out a cutting plane scheme using the Lagrangian cuts, solving the master problem (\ref{prob:master}) will only obtain a lower bound.
 \\

### 2017-07-13 src/Case1Func.jl

@@ -1,5 +1,5 @@
 # This is a collections of all functions
-using JuMP,Distributions,CPLEX;
+using JuMP,Distributions,Gurobi,HDF5,JLD;
 
 function readIn(InputAdd)
     # no of activities
@@ -130,7 +130,7 @@ end
 
 # function to create the basic version of the master program
 function createMaster(D,d,b,B,ee,II,JJ,SS,GG,p)
-  mp = Model(solver = CplexSolver());
+  mp = Model(solver = GurobiSolver());
   @variables(mp, begin
     θ[s in SS;s >= 2] >= 0
     x[i in II,j in JJ], Bin
@@ -182,7 +182,7 @@ end
 
 # function to build the MIP sub problem
 function subInt(xs,ts,D,b,B,ee,II,I1,I2,dscen,JJ,GG)
-  sip = Model(solver = CplexSolver());
+  sip = Model(solver = GurobiSolver());
   @variables(sip, begin
     x[i in II,j in JJ], Bin
     t[i in II] >= 0
@@ -203,7 +203,7 @@ end
 # function to solve for the coefficents used in Lagrangian cuts
 # the easier version of the sub problem: without big M
 function subLagP(D,dscen,b,B,ee,II,I1,I2,JJ,GG)
-  spLp = Model(solver = CplexSolver());
+  spLp = Model(solver = GurobiSolver());
   @variables(spLp, begin
     tN >= 0
     t[i in II] >= 0
@@ -222,7 +222,7 @@ end
 
 # function to solve the Lagrangian relaxation with big M
 function subLag(xs,ts,D,dscen,td,M,b,B,ee,II,I1,I2,JJ,GG,πle,λle)
-  spL = Model(solver = CplexSolver());
+  spL = Model(solver = GurobiSolver());
   @variables(spL, begin
     tN >= 0
     # t and x are the auxiliary variables with the added equality constraints
@@ -259,7 +259,7 @@ end
 
 # function to solve the Lagrangian relaxation with big M
 function subLagI(D,dscen,td,M,b,B,ee,II,I1,I2,JJ,GG)
-  spL = Model(solver = CplexSolver());
+  spL = Model(solver = GurobiSolver());
   @variables(spL, begin
     tN >= 0
     # t and x are the auxiliary variables with the added equality constraints
[…]

### 2017-07-21 PERT_WriteUp.tex
Changed writeup name

--- 2017-07-13 Paper.tex
@@
 		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
-		& \theta^\omega \geq \sum_{i \in I} \pi_i^{\omega,k^\omega} t_i + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,k^\omega} x_{ij} + v^{\omega,k^\omega} x_{ij} & \forall \omega \in \Omega, k^\omega = 1,2, \dots \label{cons:linearCuts}\\
+		& \theta^\omega \geq \sum_{i \in I} \pi_i^{\omega,k^\omega} t_i + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,k^\omega} x_{ij} + v^{\omega,k^\omega} & \forall \omega \in \Omega, k^\omega = 1,2, \dots \label{cons:linearCuts}\\
 		& t_i \geq 0 & \forall i \in I\\
@@
 We will prove this property as follows.
-\\
-	\newline
-	\textcolor{blue}{State the Proofs of the tightness/validity of the Lagrangian cuts}\\
-	\newline
-	The temporal relationship could be determined by a branch-and-bound scheme.
+	\begin{theorem}
+		For a specific scenario \(\omega\), let \(\pi^*\) and \(\lambda^*\) be an optimal solution and \(v^*\) be the optimal objective value to the Lagrangian dual problem (\(R^\omega\)) in (\ref{prob:LagDual}).
+The cut \(\theta^\omega \geq \sum_{i \in I} \pi_i^* (t_i - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^* (x_{ij} - \hat{x}_{ij}) + v^*\) is a valid and tight cut if whether \(t_i \geq H^\omega\) is known for all \(i \in I\).
+According to Definition 2 in \cite{zou2016nested}, the cut is
+		\begin{itemize}
+			\item valid, if \(f^\omega(x,t) \geq \sum_{i \in I} \pi_i^* (t_i - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^* (x_{ij} - \hat{x}_{ij}) + v^*,\ \forall t_i \geq 0, x_{ij} \in \{0,1\}\);
+			\item tight, if \(f^\omega(\hat{x},\hat{t}) = v^*\).
+		\end{itemize} 
+	\end{theorem}
+	\begin{proof}
+		\textcolor{blue}{To be added.}
+	\end{proof}
+	\noi The temporal relationship could be determined by a branch-and-bound scheme.
 Although theoretically for each scenario there are exponential number of possible temporal relationships because each activity can either be before the disruption time or after that, there are only a small number of activities, of which the optimal starting time of the deterministic problem (\ref{prob:static}) is close to the disruption time, that really matter.

### 2017-08-22 Writeup/PERT_WriteUp.tex
Updated tightness proof

--- 2017-07-13 Paper.tex
@@
 			\(I\) & \(\qquad\) & the set of activities;&\\
+			\(I_i\) & \(\qquad\) & the set of activities which directly lead to activity \(i\); &\\
 			\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i\), \(i \in I\);&\\
@@
 		\begin{align}
-		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N - \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) - \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
-		\text{s.t.} \quad & (\ref{cons:tN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange})
+		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N + \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
+		\text{s.t.} \quad & (\ref{cons:tN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange}) \label{cons:X}
 		\end{align}
@@
 	\newline
-	One important observation to help with this issue is that if we can determine the temporal relationship between every activity and the disruption, the restricted version of the function \(f^\omega\) will be convex in \(t\), and we could find a tight and valid Lagrangian cut similar to those in \cite{zou2016nested}.
+	One important observation to help with this issue is that if we can determine the temporal relationship between every activity and the disruption, it is always optimal to start the activity at its earliest possible time.
+For a feasible solution \((\hat{t},\hat{x})\), we define the shifted solution \((\tilde{t},\tilde{x})\) of \((\hat{t},\hat{x})\) as:
+	\begin{definition}
+		Shifted solution of a feasible solution \((\hat{t},\hat{x})\):
+		\begin{itemize}
+			\item \(\tilde{x}_{ij} = \hat{x}_{ij}\)
+			\item For all activities which do not have a predecessor,\\
+				\(\tilde{t}_i = 
+				\begin{cases}
+					H^\omega & \text{if temporal relationship information specifies } t_i \geq H^\omega\\
+					0 & \text{otherwise.}
+				\end{cases}
+				\)
+			\item For all other activities, \\
+				\(\tilde{t}_i = 
+				\begin{cases}
+				\max \{H^\omega, \max_{i' \in I, i' \in I_i} \{\tilde{t}_{i'} + D_{i'}(1 - \sum_{j \in J_{i'}} e_{i'j}\tilde{x}_{i'j})\} \} & \text{if the temporal relationship}\\
+				& \text{information specifies } t_i \geq H^\omega\\
+				\max_{i' \in I, i' \in I_i} \{\tilde{t}_{i'} + D_{i'}(1 - \sum_{j \in J_{i'}} e_{i'j}\tilde{x}_{i'j})\} & \text{otherwise.}
+				\end{cases}
+				\)
+		\end{itemize}
+	\end{definition}
+	\noi We should notice that the temporal relationship should match the feasible solution.
+This is a natural result from solving problem~\ref{prob:subLocal} with temporal relationship information given.
+\\
+	\newline
+	It is obvious to see the following statement is true because delaying an activity as soon as possible when the crashing decision is decided and temporal relationship information is revealed will not bring any benefit.
+	\begin{corollary}
+		For an optimal solution \((t^*,x^*)\) with correct temporal relationship information given for all activities, its shifted solution is also optimal.
+	\end{corollary}
+	\noi Now we will prove that the Lagrangian cuts generated by \cite{zou2016nested} is tight and valid at any shifted solution if temporal relationship information is given for all activities.
+This statement is very important because it provides an accurate evaluation at the optimal solution, which will lead to an algorithm which is able to solve problem~\ref{prob:extensive} to the exactness.
+	\begin{proposition} \label{prop:convex}
+		Suppose the set defined by constraint (\ref{cons:X}) is denoted by \(X\). For any shifted solution \((\tilde{t},\tilde{x})\) with temporal relationship information given for all \( i \in I\), 
+		\[conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  = \]
+		\[conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\]
+	\end{proposition}
+	\begin{proof}
+		Suppose \((t^0, \tau^0, x^0, z^0) \in  conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} \).
+Then there exist a set of points in \(X\) indexed by \(k \in \mathcal{K}\) where \((t^0, \tau^0, x^0, z^0) = \sum_{k \in \mathcal{K}}\rho_{k} (t^k, \tau^k, x^k, z^k) \) and \(\rho_{k} \geq, \sum_{k \in \mathcal{K}} \rho_{k} = 1\).
+Since \(\tilde{x}_{ij} \in \{0,1\}, z_{ij}^k \in [0,1], \forall k \in \mathcal{K}\) and we have \(\sum_{k \in \mathcal{K}} \rho_{k} z^k_{ij} = z^0_{ij} = \tilde{x}_{ij}\), every \(z^k_{ij}\) can only take the same value as \(\tilde{x}_{ij} , \forall k \in \mathcal{K}\), which is an end point of \([0,1]\).\\
+		\newline
+		\(z^k_{ij} = \tilde{x}_{ij}\) and temporal relationship information is given for all \(i \in I\), this means that the shifted solution \(\tilde{t}_i\) is the earliest possible starting time for activity \(i\), so \(\tau_i^k \geq \tilde{t}_i\).
+Similar to the previous statement about the relationship between \(z^k\) and \(\tilde{x}\), as \(\tilde{t}_i\) is taking an end point of the feasible set of \(\tau_i^k\) and \(\sum_{k \in \mathcal{K}} \rho_{k} \tau_i^k = \tilde{t}_i \), we have \(\tau_i^k = \tilde{t}_i,\ \forall k \in \mathcal{K}\).
+Combining the results above,
+		\[conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  \subseteq \]
+		\[conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\]
+		On the other hand, 
+		\[conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  \supseteq \]
+		\[conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\]
+		is also true.
+Suppose a point \((t^0, \tau^0, x^0, z^0) \in conv(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} )\), then we can find a set of points indexed by \(\mathcal{K}\) in \(X \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \} \) such that \((t^0, \tau^0, x^0, z^0) \) is the convex combination of them.
+For each \(k \in \mathcal{K}\), \(\tau_i^k = \tilde{t}_i\) and \(z_{ij}^k = \tilde{x}_{ij}\).
+Therefore, \(\tau^0 = \tilde{t}_i\) and \(z_{ij}^0 = \tilde{x}_{ij}\).
+Plus, each \((t^k, \tau^k, x^k, z^k) \in X \).
+Since \((t^0, \tau^0, x^0, z^0)\) is the convex combination of \((t^k, \tau^k, x^k, z^k)\), \((t^0, \tau^0, x^0, z^0) \in conv(X)\).
+Thus \((t^0, \tau^0, x^0, z^0) \in conv(X) \cap \{(\tau,z) \mid \tau_i = \tilde{t}_i, z_{ij} = \tilde{x}_{ij}, \tau_i, z_{ij} \in \mathbb{R}, \forall i \in I, j \in J_i \}  \).
+	\end{proof}
+	%the restricted version of the function \(f^\omega\) will be convex in \(t\), and we could find a tight and valid Lagrangian cut similar to those in \cite{zou2016nested}.
 This means, for example, if for a specific scenario \(\omega\), \(H^\omega = 5\), and for each activity \(i \in I\) we know whether its starting time \(t_i\) is less than, larger than or equal to \(H^\omega = 5\), then there is a finite set of linear constraints that could be generated to fully characterize \(f^\omega(x,t)\) in formulation~(\ref{prob:master}).
@@
 We will prove this property as follows.
-\\
+	\noi With this property, the Lagrangian cuts derived in \cite{zou2016nested} are valid and tight at shifted solutions when temporal relationship information is given for all activities.
+	\begin{theorem}
+		For a specific scenario \(\omega\), let \(\theta^*\) be the objective value and \(\pi^*\) and \(\lambda^*\) be an optimal solution to the Lagrangian dual problem (\(R^\omega\)) in (\ref{prob:LagDual}), where the first stage solution is a shifted solution \((\tilde{t},\tilde{x})\) with temporal relationship information given for all \(i \in I\).
+The cut \(\theta^\omega \geq \sum_{i \in I} \pi_i^* (t_i - \tilde{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^* (x_{ij} - \tilde{x}_{ij}) + t_N^*\) is a valid and tight cut, where being valid and tight means:
+		\begin{itemize}
+			\item valid, \(f^\omega(x,t) \geq \sum_{i \in I} \pi_i^* (t_i - \tilde{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^* (x_{ij} - \tilde{x}_{ij}) + t_N^*,\ \forall t_i \geq 0, x_{ij} \in \{0,1\}\);
+			\item tight, \(f^\omega(\tilde{x},\tilde{t}) = \theta^*\).
+		\end{itemize} 
+	\end{theorem}
+	\begin{proof}
+		The Lagrangian cut is a lower bound at any solution because of it is a relaxation of problem~(\ref{prob:subLocal}), which means it is always valid.
+See Proposition 6.1 in \cite{nemhauser1988integer} for the detailed proof.\\
 		\newline
-	\textcolor{blue}{State the Proofs of the tightness/validity of the Lagrangian cuts}\\
-	\newline
-	The temporal relationship could be determined by a branch-and-bound scheme.
+		From Proposition~\ref{prop:convex} and Corollary 6.5 from \cite{nemhauser1988integer}, we know the objective value of the Lagrangian dual problem equals to the objective value of the original integer programming problem.
+	\end{proof}
+	\noi The temporal relationship could be determined by a branch-and-bound scheme.
 Although theoretically for each scenario there are exponential number of possible temporal relationships because each activity can either be before the disruption time or after that, there are only a small number of activities, of which the optimal starting time of the deterministic problem (\ref{prob:static}) is close to the disruption time, that really matter.
 If an activity should be starting much earlier than the disruption time in the deterministic problem, it usually will significantly increase the length of the project span by delaying the start of such activity.
-If an activity cannot start until a time much later than the disruption time, it is usually not possible to make it start before the disruption time without committing crashing resources heavily on its precedent activities, which may likely lead to an inferior solution.
-
+If an activity cannot start until a time much later than the disruption time, it is usually not possible to make it start before the disruption time without committing crashing resources heavily on its precedent activities, which may likely lead to an inferior solution.\\
+	\newline
+	\textcolor{blue}{Algorithm of branch and cut.}
 \section{Computational Results} \label{sec:results}

### 2017-09-22 Writeup/Disruption/Disruption Model Reformatted Ver 1.tex
Restructure the whole program and make the recourse continuous

\documentclass[11pt]{article}
\usepackage[small]{titlesec}
\usepackage[top = 0.66in,textwidth = 6.5in, textheight=9.1in]{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{verbatim}
\usepackage{multirow}
\usepackage{framed}
\usepackage{natbib}
\usepackage{float, subfig}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{grffile}
\usepackage{sidecap}
\usepackage{pbox}

\def\qed{\hfill{\(\vcenter{\hrule height1pt \hbox{\vrule width1pt height5pt
     \kern5pt \vrule width1pt} \hrule height1pt}\)} \medskip}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\renewcommand{\textfraction}{0.0}
\newcommand{\dst}{\displaystyle}
\newcommand{\minx}{\mbox{\( \dst \min_{x \in X} \)}}
\newcommand{\Efx}{\mbox{\( \dst E f (x, \xi) \)}}
\newcommand{\Efxhat}{\mbox{\( \dst E f (\hat{x}, \xi) \)}}
\newcommand{\hxx}{\mbox{\( \hat{x} \)}}
\newcommand{\bpi}{\bar{\pi}}
\newcommand{\xx}{\mbox{\( x \)}}
\newcommand{\txxi}{\mbox{\(\xi\)}}
\newcommand{\var}{\mbox{var}}
\newcommand{\cF}{{\cal F}}
\newcommand{\cG}{{\cal G}}
\newcommand{\cN}{{\cal N}}
\newcommand{\cO}{{\cal O}}
\newcommand{\txi}{{\xi}}
\newcommand{\PP}{\mbox{\(SP\)}}
\newcommand{\PPn}{\mbox{\(SP_n\)}}
\newcommand{\PPnx}{\mbox{\(SP_{n_x}\)}}
\newcommand{\noi}{\noindent}
\renewcommand{\ss}{\smallskip}
\newcommand{\ms}{\medskip}
\newcommand{\bs}{\bigskip}
\newcommand{\st}{\mbox{s.t.}}
\newcommand{\wpo}{\mbox{wp1}}
\newcommand{\iid}{\mbox{i.i.d.\ }}
\newcommand{\vsmo}{\vspace*{-0.1in}}
\newcommand{\vsmt}{\vspace*{-0.2in}}
\newcommand{\vso}{\vspace*{0.1in}}
\newcommand{\vst}{\vspace*{0.2in}}
\newcommand{\mc}{\multicolumn}
\newcommand{\cP}{{\cal P}}
\newcommand{\underv}{\mbox{$\underbar{$v$}$}}
%\allowdisplaybreaks

\renewcommand{\P}{{\mathbb P}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\renewcommand{\Re}{{\mathbb R}}

\bibliographystyle{plain}

\begin{document}
%0.27
\baselineskip0.25in

\begin{center}
\begin{large}
\begin{bf}

A Report on Disruption Model \ms

Haoxiang Yang \ms

\today \ms
\end{bf}
\end{large}
\end{center}

\section{Introduction to a Disruption Model}
	In a sequential decision problem, we make decisions in a sequence of time periods, which may be under the influence of uncertainty. The uncertainty usually takes the form of an unknown outcome of parameters, which is not realized before making the decision. In stochastic programming, we model uncertainty by assuming the outcome is governed by a known distribution, or a stochastic process, and in robust optimization we instead assume the outcome belongs to an uncertainty set. Those models mainly focus on the magnitude of the uncertainty and %The distribution or the feasible region of parameters are fixed across the time horizon.}% 
	usually assume that the uncertainty exists in every single time period with the same known distribution or the same uncertainty set. However, it may not be the case in many real-world problems. Here, we model uncertainty in the time periods in which uncertainty occurs, focusing on the notion of disruptions in sequential decision problems. For our purposes, a disruption is a type of event under which uncertain parameters change in a significant way, in value, distribution, etc. We will view disruptions as events that occur infrequently, but that can have a significant impact. So, a disruption could be a one-time event, or an event that happens only a limited number of times over the planning horizon. There have been only limited number of literatures focused on this problem. There are a few papers (\cite{BGZ15},\cite{G78}) addressing the issue of non-stationary objective functions. \cite{RDM13} considers a probabilistic bicriteria model with disruption using stochastic programming. \cite{MSW09} has the closest setting to our problem as it gives a military application of modeling the attack as the disruption. Our work would like to generalize those results and gain some theoretical insights.

\section{A Stochastic Program for Modeling Disruptions}
	\subsection{Single-disruption Formulation}\label{1Dformulation}
	We begin by assuming that at most one disruption can occur over a fixed time horizon. The parameters before and after the disruption are fixed. Here \(\mathscr{T}=\{1,2,\dots,T\}\) represents the time horizon fixed for the sequential decision problem. For an infinite horizon problem, \(T=+\infty\).\\ %As the randomness is not stagewise independent, we can introduce state variable to the model \cite{S11}.
	\newline We assume the possible scenario lies in a finite scenario set \(\Omega\). The probability of each scenario is \(p^\omega\) and \(\sum_{\omega \in \Omega} p^\omega = 1\). The disruption happens at time period \(t_d^\omega\) under scenario \(\omega \in \Omega\), after the decision ot the time period \(t_d^\omega\) is made. We can consider the no-disruption scenario as an element in \(\Omega\) and denote it by \(\omega_0\).\\
	\newline We denote the variables at each epoch before the disruption as \(x_t \text{ and } s_t, t = 1 \dots T\). \(s\) contains the information of the actions/records before observing the uncertainty while \(x\) contains the information of the actions/records after observing the uncertainty in each period. We formulate the model in this structure because it will greatly reduce the complexity of the non-anticipative constraints. \\
	\newline Since there is a positive probability that the disruption may not occur in the timespan, \(x \text{ and } s\) has to be indexed by the whole timespan \(\mathscr{T}\). We denote the decision after the disruption as \(\overline{x_t^\omega} \text{ and } \overline{s_t^\omega}, t \in \{t_d^\omega, \dots, T\}\). There exists a connection between \(s_{t_d^\omega}\) and \(\overline{s_{t_d^\omega}^\omega}\) under scenario \(\omega\) to tie the process before the disruption and the process after the disruption.\\
	\newline Suppose there is no discount factor in this problem, and the problem has a linear objective function and linear constraints. We assume that two sequences of parameters \(CX_t, t\in \mathscr{T}\) and \(CS_t, t\in \mathscr{T}\) are known, which can describe the costs of variables before the disruption under all scenarios. Given a scenario \(\omega\), we assume that parameters \(\overline{CX_t^\omega} \text{ and } \overline{CS_t^\omega}, t \in \{t_d^\omega, \dots, T\}\) are also known to describe the objective function after the disruption. \\
	\newline It is easy to see that without the disruption, it is a deterministic linear programming problem. We can form an optimization model as follows. Notice that it is possible to have same matrix \(A, B, \text{ and } H\) for each period time, when the dynamic of the system does not change over time.
	% We need to write down a multi-stage stochastic optimization model first. Then we show the multi-stage one is equivalent to the one below.
	\begin{align}
		\min \quad & \sum_{\omega \in \Omega} p^\omega [\sum_{t = 1}^{t_d^\omega-1}{(CX_tx_t+CS_ts_t)}+\sum_{t = t_d^\omega}^{T}{(\overline{CX_t^\omega}\ \overline{x_t^\omega} + \overline{CS_t^\omega}\ \overline{s_t^\omega}}) ]\\
		\text{s.t.} \quad & A_{t-1}s_{t-1} + B_tx_{t} + H_ts_{t} = b_t & \quad & \forall t = 1 \dots T\\
		& \overline{A_{t-1}^\omega} \  \overline{s_{t-1}^\omega} + \overline{B_{t}^\omega}\ \overline{x_{t}^\omega} + \overline{H_{t}^\omega}\ \overline{s_{t}^\omega} = \overline{b_t^\omega}  & \quad & \forall t = t_d^\omega \dots T,\ \forall \omega \in \Omega\\
		& \overline{s_{t_d^\omega}^\omega} = s_{t_d^\omega}& \quad & \forall \omega \in \Omega\\
		& x_t, s_t \geq 0 & \quad & \forall t = 1 \dots T\\
		& \overline{x_t^\omega}, \overline{s_t^\omega} \geq 0 & \quad & \forall t = t_d^\omega \dots T,\ \forall \omega \in \Omega
	\end{align}
	Suppose in each epoch the disruption happens according to a Bernoulli distribution with some probability \(p_t\) if there has not been any disruption before. The disruption will lead the system to a deterministic path. The scenario tree is illustrated in Figure~\ref{scenarioTree}.
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.6\textwidth]{single disruption model fig1}
		\caption{Single disruption model with 4 epochs}
		\label{scenarioTree}
	\end{figure}

	\subsection{L-shape Method}
	Given the formulation in Section~\ref{1Dformulation}, we could write down the original problem as a two-stage stochastic linear program. The first stage decision variables are \(x_t, s_t, \ \forall t = 1\dots T\) and the second stage could be viewed as functions of the first stage variables \(G^\omega(s_{t_d^\omega}), \ \forall \omega \in \Omega\).\\
	\newline The master problem can be formulated as follows:
	\begin{align}
		(M) \quad \min \quad & \sum_{\omega \in \Omega}p^\omega\sum_{t = 1}^{t_d^\omega - 1}(CX_t x_t + CS_t s_t) + \sum_{\omega \in \Omega} p^\omega \phi^\omega & \\
		\text{s.t.} \quad & A_{t-1}s_{t-1} + B_tx_{t} + H_ts_{t} = b_t \quad & \forall t = 1 \dots T\\
		& \hat{\pi}_k^\omega s_{t_d^\omega - 1} + \sum_{t = t_d^\omega}^T \gamma_{t,k}^\omega \overline{b_t^\omega} \leq 0 \quad & \forall \omega \in \Omega, \forall k = 1,2 \dots\\
		% Optimality cut generation
		& \phi^\omega \geq G^\omega(s_{t_d^\omega}^l) + \pi^\omega_l(s_{t_d^\omega - 1} - s_{t_d^\omega - 1}^l) \quad & \forall l = 1,2 \dots\\
		& x_t, s_t \geq 0 \quad & \forall t = 1 \dots T
	\end{align}
	\noindent The sub-problem is displayed as follows. For each scenario \(\omega\) we have:
	\begin{align}
		(Sub) \quad G^\omega(s_{t_d^\omega}) = \min \quad & \sum_{t = t_d^\omega}^T \overline{CX_t^\omega} \ \overline{x_t^\omega} + \overline{CS_t^\omega} \ \overline{s_t^\omega}  &\\
		\text{s.t.} \quad & \overline{A_{t-1}^\omega} \  \overline{s_{t-1}^\omega} + \overline{B_{t}^\omega}\ \overline{x_{t}^\omega} + \overline{H_{t}^\omega}\ \overline{s_{t}^\omega} = \overline{b_t^\omega} \quad & \forall t = t_d^\omega \dots T\\
		& \overline{s_{t_d^\omega - 1}^\omega} = s_{t_d^\omega - 1} &\\
		& \overline{x_t^\omega}, \overline{s_t^\omega} \geq 0 \quad & \forall t = t_d^\omega \dots T,\ \forall \omega \in \Omega
	\end{align}
	Let us denote the dual variable for \((14)\) as \(\pi^\omega\) for the scenario \(\omega\). We can see that \(\pi^\omega\) is the slope of the cut generated every iteration \(l\) of the master problem. Without the assumption of relatively complete recourse, we would need to solve the following phase-I problem to obtain the feasibility cuts as \((9)\). Here we denote the dual variables of the set of constraints (17) as \(\hat{\gamma}_{t,\omega}\) and the dual variable of (18) as \(\hat{\pi}^\omega\).
	\begin{align}
		(Sub-PI) \quad F^\omega = \min \quad & \sum_{t = t_d^\omega}^T (\delta_t^+ + \delta_t^-) + (u^+ + u^-) & \\
		\text{s.t.} \quad & \overline{A_{t-1}^\omega} \  \overline{s_{t-1}^\omega} + \overline{B_{t}^\omega}\ \overline{x_{t}^\omega} + \overline{H_{t}^\omega}\ \overline{s_{t}^\omega} + (\delta_t^+ - \delta_t^-) = \overline{b_t^\omega} \quad & \forall t = t_d^\omega \dots T \\
		& \overline{s_{t_d^\omega}^\omega} + (u^+ - u^-) = s_{t_d^\omega} &\\
		& \overline{x_t^\omega}, \overline{s_t^\omega} \geq 0 \quad & \forall t = t_d^\omega \dots T,\ \forall \omega \in \Omega
	\end{align}
	\noi The following L-shape algorithm can solve the single disruption problem. It can be extended to solve multiple-disruption cases.
	% LEFT OUT HERE!!!!

%	The Lagrangian relaxation of the subproblem is shown as follows.
%	\begin{align*}
%		\mathcal{L}(s,x,\pi,\overline{\pi},\gamma) = & \sum_{\omega \in \Omega} p^\omega [\sum_{t = 1}^{t_d^\omega-1}{(CX_tx_t+CS_ts_t)}+\sum_{t = t_d^\omega}^{T}{(\overline{CX_t^\omega}\ \overline{x_t^\omega} + \overline{CS_t^\omega}\ \overline{s_t^\omega}})]\\
%		& + \sum_{t = 1}^T \pi_t(A_{t-1}s_{t-1} + B_tx_{t} + H_ts_{t} - b_t) \\
%		& + \sum_{\omega \in \Omega} \sum_{t = t_d^\omega}^T \overline{\pi_t^\omega}(\overline{A_{t-1}^\omega} \  \overline{S_{t-1}^\omega} + \overline{B_{t}^\omega}\ \overline{x_{t}^\omega} + \overline{H_{t}^\omega}\ \overline{s_{t}^\omega} - \overline{b_t^\omega})\\
%		& + \gamma^\omega (\overline{s_{t_d^\omega}^\omega} - s_{t_d^\omega}) 
%	\end{align*}
%	Therefore, the KKT condition of the original problem is:\\
%	\newline Primal feasibility:
%	\begin{align}
%		& A_{t-1}s_{t-1} + B_tx_{t} + H_ts_{t} = b_t & \quad & \forall t = 1 \dots T\\
%		& \overline{A_{t-1}^\omega} \  \overline{S_{t-1}^\omega} + \overline{B_{t}^\omega}\ \overline{x_{t}^\omega} + \overline{H_{t}^\omega}\ \overline{s_{t}^\omega} = \overline{b_t^\omega}  & \quad & \forall t = t_d^\omega \dots T,\ \forall \omega \in \Omega\\
%		& \overline{s_{t_d^\omega}^\omega} = s_{t_d^\omega}& \quad & \forall \omega \in \Omega\\
%		& x_t, s_t \geq 0 & \quad & \forall t = 1 \dots T\\
%		& \overline{x_t^\omega}, \overline{s_t^\omega} \geq 0 & \quad & \forall t = t_d^\omega \dots T,\ \forall \omega \in \Omega
%	\end{align}
%	\noindent Dual feasibility:
%	\begin{align*}
%	content...
%	\end{align*}
	\subsection{Dantzig-Wolfe Decomposition}
	Remained to be finished.

\section{An MDP for Modeling Disruptions}
		Suppose the process has the Markov property, Markov Decision Process is widely used when modeling the sequential decision making problem with stochastic exogenous information.\\
	\newline To simplify the problem, we start with some basic and fairly restrictive assumptions. Later we will seek to relax them.
	\begin{enumerate}
		\item Finite and modest-sized state space, denoted by \(\mathscr{S}\).
		\item Finite and modest-sized action space, denoted by \(A_s\).
		\item Discrete time: if finite, modest number of decision epoch, \(t \in \mathscr{T}={1,2,\dots}\).
		\item One disruption in the time horizon.
		\item Disruption has only one magnitude, which means the disruption will lead to a deterministic set of parameters. 
		\item The probability of the disruption happening at every single stage is the same, denoted by \(p\).
	\end{enumerate}

	\subsection{Basic Model}
		Before adding the disruption in the model, a non-disruption MDP model should be built in order to explain the whole process.
		\newline \textbf{Decision Epoch}\\
		The decision epoch is a set of integers, \[\mathscr{T}=\{1,2,\dots,T_{max}\},\quad  T_{max} \leq +\infty\]
		If it is an infinite horizon problem, then \(T_{max} = +\infty\)\\
		\newline \textbf{States}\\
		If the state of the non-disruption model consists of only one variable, in the disruption model the state will be a tuple built by augmenting the non-disruption state with a binary variable. \[\mathscr{S}=\{(s_1,0),(s_2,0),\dots,(s_N,0),(s_1,1),(s_2,1),\dots,(s_N,1)\}\] \(s_1,\dots,s_N\) are in the state space of the non-disruption MDP. The binary component represents the status of the disruption, 0 for the scenario the disruption has not happened yet, 1 for the scenario the disruption has already happened.\\
		\newline \textbf{Actions}\\
		The action space in the disruption model is defined the same as in the non-disruption model. Suppose the action space is a bounded discrete set with finitely many elements. The action space can be denoted by \[A_s=\{A_s^1,\dots,A_s^M\} \quad \forall s \in \mathscr{S}\]
		\newline \textbf{Expected Reward}\\
		For different examples the expected reward can vary. For a general purpose we denote the expected reward function as \[r_t(s,a), \quad s \in \mathscr{S}, a \in A_s\]
		\newline \textbf{Transition Probability}\\
		Suppose the decision policy of the disruption MDP is denoted by \(\pi = (\delta^1,\delta^2,\dots)\), where \(\delta^t\), as a vector of length \(|\mathscr{S}|\) with each component \(\delta^t_s\), represent the decision rule at time \(t\). The component \(\delta^t_s\) determines the action that will be taken given the process is at time \(t\) and state \(s\). Suppose the transition probability before the disruption happening is \(Pr_0\{s'|s,\delta_s\}\) and the the transition probability after the disruption happening is \(Pr_1\{s'|s,\delta_s\}\). The transition probability for the whole problem is
		\[ Pr\{s'|s,\delta_s\} = \begin{cases} 
					Pr_0\{s'|s,\delta_s\}(1-p) & \quad \text{if } s \text{ has disruption status 0 and } s' \text{ has disruption status 0}\\ 
					Pr_0\{s'|s,\delta_s\}p & \quad \text{if } s \text{ has disruption status 0 and } s' \text{ has disruption status 1}\\ 
					Pr_1\{s'|s,\delta_s\} & \quad \text{if } s \text{ has disruption status 1 and } s' \text{ has disruption status 1}\\ 
					0 & \quad \text{Otherwise}
					\end{cases} \]
		\newline \textbf{Illustration of the Markov Chain}\\
		\begin{figure}[H]
			\centering
			\includegraphics[width=\textwidth]{Augmented_Network}
			\caption{The original Markov Chain and the partial augmented Markov Chain}
			\label{AugNet}
		\end{figure}
		The core of the transition from state to state is a Markov Chain. Figure~\ref{AugNet} the change from a non-disruption model to a one disruption model. The important idea here is to include the record whether the disruption has happened. This means expanding the previous Markov Chain, which can be considered a network of states, to a set of networks connected by the transitions that describe disruptions. Augmenting the state space, which serves for this purpose, is equivalent to adding the red arcs in the figure. While adding all the connections between two levels, the transition probability will also change into the ones mentioned above. For the simplicity of the illustration, we only added two arcs from one node on the left. The same principle will be applied to other nodes.

	\subsection{Solving the MDP}
	Remained to be finished.

	\subsection{Relaxation of the assumptions}
		\subsubsection{Relaxation of the number of disruptions}
			At first we stated that in the whole timespan there is only one possible disruption. Before and after the disruption the values and the distributions of the parameters are fixed. In order to extend this to a more general level that there may be more than one disruption happening in the timespan, we can enlarge the set of values that \(i_t\) can take in the state space. Before \(i_t\) can only take binary values to indicate whether the disruption has occurred or not. Now we can extend this to a nonnegative integer set \(\{0,1,2,\dots,L\}\), \(L\) is the maximum number of disruptions that possibly happen during the timespan.  This way we expand our network into more than two levels (shown in Figure 2). A level means one disruption and each level of the network is the identical except that the last level will be absorbing level.\\
			\newline The impact of this augmentation is that the state space expands to the size \(L|\mathscr{S}|\).
		\subsubsection{Relaxation of the magnitude of the disruption}
			Suppose at every single epoch it is possible to have a disruption where the values/distributions of the parameters may change into more than one probable result. Here "more than one" is limited to a finite integer value \(N\), and we also suppose that although the results of disruptions may be different, the possible values that a disruption can lead to do not change from time to time. Therefore, we can build parallel networks in the same level. Each parallel network represents one magnitude of the same disruption. The impact of this augmentation is that the state space expands to the size \((N+1)|\mathscr{S}|\).\\
			\newline Combining this with the result of relaxing the number of disruptions, we can build a Markov Chain with multiple levels and disjoint networks within each level. Consider each network as a circle, the structure of the newly built Markov Chain can be displayed as below.
			\begin{figure}[H]
				\centering
				\includegraphics[width=\textwidth*3/4]{Multi_layer}
				\caption{Complete Markov Chain built from relaxations}
			\end{figure}
		\subsubsection{Relaxation of the constant probability of disruption}
			The probability for the disruption to occur may not be a constant over time. Here we would like to discuss two scenarios if the probability \(p\) is a random variable in the timespan between two disruptions. One case is that the probability is a function of time. The other one is that we have another distribution to describe the probability parameter.

	\subsection{Complexity Analysis of the MDP model}
		\cite{LDK95} systematically describes the complexity of the policy iteration algorithm and the value iteration algorithm. Suppose we have a non disruption MDP. \cite{P94} has stated that the policy iteration dominates the value iteration in the convergence rate if the discount rate is fixed. In each iteration the complexity of the policy iteration is polynomial \(O(\max(|\mathscr{S}|^2|\sup_{(s,i)} A_{(s,i)}|,|\mathscr{S}|^3))\) and the complexity of the value iteration is polynomial \(O(|\mathscr{S}|^2|\sup_{(s,i)} A_{(s,i)}|)\). \\
		\newline Therefore, the key to show that both algorithms are polynomial is to show that the value iteration algorithm can stop in polynomial number of iteration. \cite{T90} has shown this result by the following steps. First if we start from an initial value \(v_0\), the distance between \(v_0\) and the optimal value \(v^*\) is proved to be bounded given that the reward function is bounded. By the property of a contraction mapping it requires \(\log(\epsilon/\|v_0-v^*\|)/\log(\gamma)\) iterations to reach the stopping criterion \(\|v_n-v^*\|<\epsilon \quad \forall \epsilon>0\). Besides, we are able to prove that if \(\epsilon \leq \frac{1}{2\delta^{2n+2}|\mathscr{S}|^{|\mathscr{S}|}}\), the value iteration will output an optimal policy. As a result, the value iteration will have a polynomial number of iterations, thus it is a polynomial algorithm.\\
		\newline However, this proof does have the limitation as it assumes the integrality of the reward function and the fixed discount parameter.

\section{Example of the Disruption Model}\label{sec:example}
	The original non-disruption inventory problem can be found from \cite{P94} Section 3.2. With this prototype, we can come up with an example with disruptions. Consider the same company that manages the inventory of a certain product. Each time period (e.g. month) the manager needs to place an order in the beginning and will receive the order instantly (lead time is 0). 
	%The ordering decision is limited to a discrete finite sized set because of the integral unit of the product and the capacity of the facility. 
	The ordering decision is assumed to be continuous within an upper bound. A continuous-valued demand will occur through the period. If the demand exceeds the number of product on hand, each unit of shortage will be charged with a penalty price. \\
	\newline The disruption may be a result of a change in the industry, such as the upgrade of a technology, or the introduction of a new policy. The disruption will happen at the beginning of the period. There are two variations of the time when the disruption occurs. The disruption may occur before the ordering decision is made, or it can occur after the ordering decision. Both variations are realistic and the formulations are slightly different. We will mainly focus on the second variation, in which the disruption happens after the ordering decision is made.\\
	\newline   If a disruption happens, the demand, the purchase and sale prices and the inventory cost of the product are subjected to change from a fixed state to another. The scenario set is denoted by \(\Omega\), and the time of disruption \(t_d^\omega\) and the set of parameters are known for each scenario \(\omega \in \Omega\). The ordering cost contains only a variable cost. 
	%The detailed denotation of parameters of time period $t$ in scenario \(\omega\) are displayed here in Table 1. \\

	The timeline of the events in one epoch is shown in Figure~\ref{timeLine}. \\
	\begin{figure}[H]
		\centering
		\includegraphics[width=\textwidth]{Inventory_Timeline.pdf}
		\caption{Timeline of a month}
		\label{timeLine}
	\end{figure}

	\subsection{Modeling the Inventory Problem with Single-Disruption with a Two-Stage Stochastic Program}
		We will introduce the stochastic programming formulation of the inventory example. Some extensions of the basic model will be included in the end of the section. 
		\begin{table}[H]
			\begin{tabular}{ l l l l }
				\\
				\multicolumn{4}{l}{Indices and index sets} \\
				\\
				\(t \in \mathscr{T}\)  & \qquad & Time periods, \(\mathscr{T} = \{1, 2 \dots T\} \text{; T is the end of the time horizon}\)& \ms \\ 
				\multirow{2}{*}{\(\omega \in \Omega\)} & \qquad & Scenarios. It contains the information of timing and extent. \\ & \qquad &This set includes the ``no-disruption scenario" denoted \(\omega_0\)& \ms\\
				\(t_d^\omega\) & \qquad & Time of disruption under scenario \(\omega\) (\(1\leq t_d^\omega \leq T\)); \(t_d^{\omega_0} = T+1\)&\\
				\\

				\multicolumn{4}{l}{Data} \\
				\\
				%Fixed Ordering Cost		& \(K^0\)		& \(K^1\)	\\ \hline
				\(v_t\) & \qquad & Ordering cost/unit before the disruption & \ms\\
				\(\overline{v_t^\omega}\) & \qquad & Ordering cost/unit after the disruption  & \ms\\ 
%				\(cS_t\) & \qquad & Sales price/unit before the disruption &\\
%				\(\overline{cS_t}^\omega\) & \qquad & Sales price/unit after the disruption &\\
				\(c_t\) & \qquad & Inventory cost/unit	before the disruption & \ms\\
				\(\overline{c_t^\omega}\) & \qquad & Inventory cost/unit after the disruption & \ms\\
				\(q_t\) & \qquad & Outsourcing cost/unit before the disruption & \ms\\
				\(\overline{q_t^\omega}\) & \qquad & Outsourcing cost/unit after the disruption & \ms\\ 
				\(D_t\) & \qquad & Demand set if there is no disruption, \(t \in \mathscr{T}\) & \ms\\
				\(\overline{D_t^\omega}\) & \qquad & Demand set if the disruption happens under the scenarios \(\omega\), \(t \in \{t_d^\omega, \dots, T \}\) & \ms\\ 
				\(M_t\)	& \qquad & Order capacity before the disruption & \ms\\
				\(\overline{M_t^\omega}\) & \qquad & Order capacity after the disruption & \ms\\
				\(p^\omega\) & \qquad & Probability of scenario \(\omega\) &\\
				\\

				\multicolumn{4}{l}{Variables} \\
				\\
				%Fixed Ordering Cost		& \(K^0\)		& \(K^1\)	\\ \hline
				\(X_t\) & \qquad & Number of units ordered in period \(t\) given the disruption has not happened in period \(t\)& \ms\\
				\(Q_t\) & \qquad & Number of units outsourced in period \(t\) given the disruption has not happened in period \(t\)& \ms\\
				\(I_t\) & \qquad & Inventory in period \(t\) given the disruption has not happened in period \(t\)& \ms\\
				\(\overline{X_t^\omega}\) & \qquad & Number of units ordered in period \(t\) given the disruption has happened before the end of period \(t\)& \ms\\
				\multirow{2}{*}{\(\overline{Q_t^\omega}\)} & \qquad & Number of units outsourced in period \(t\) given the disruption has happened before \\ & \qquad & the end of period \(t\)& \ms\\
				\(\overline{I_t^\omega}\) & \qquad & Inventory in period \(t\) given the disruption has happened before the end of period \(t\)& \ms\\
			\end{tabular}
		\end{table}

		\noi The two stage stochastic linear programming can be formulated as follows, \(I_0\) is a constant and we force \(\overline{v^\omega_{t_d^\omega}} = v_{t_d^\omega}, \forall \omega \in \Omega\).
		\begin{align*}
			 \min \quad & \sum_{\omega \in \Omega} p^\omega [\sum_{t = 1}^{t_d^\omega-1}{(c_tI_t + v_tX_t + q_tQ_t)} + \sum_{t = t_d^\omega}^{T}{(\overline{c_t^\omega}\ \overline{I_t^\omega} + \overline{v_t^\omega}\ \overline{X_t^\omega} + \overline{q_t^\omega}\ \overline{Q_t^\omega})}] & \\
			 \text{s.t.} \quad & I_{t-1} + X_{t} - D_{t} + Q_{t} = I_{t} & \forall t = 1, \dots, T\\
			& \overline{I_{t-1}^\omega} + \overline{X_{t}^\omega} - \overline{D_{t}^\omega} + \overline{Q_{t}^\omega} = \overline{I_{t}^\omega} \qquad \forall t = t_d^\omega, \dots, T, & \forall \omega \in \Omega \\
			& I_{t_d^\omega-1} = \overline{I_{t_d^\omega -1}^\omega} & \forall \omega \in \Omega \\
			& X_{t_d^\omega} = \overline{X_{t_d^\omega}^\omega} & \forall \omega \in \Omega \\
			& X_t \leq M_t & \forall t = 1, \dots, T\\
			& \overline{X_{t}^\omega} \leq \overline{M_t^\omega} & \forall t = t_d^\omega, \dots, T, \  \forall \omega \in \Omega\\
			& X, I, Q, \overline{X^\omega}, \overline{I^\omega}, \overline{Q^\omega} \geq 0. &
		\end{align*}
		\noi The master program is displayed as follows. Since the problem has a relatively complete recourse, we do not need to generate feasibility cuts. The optimality cuts use the \(k^{\text{th}}\) optimal dual variables of the constraints in the subproblem.
		\begin{align*}
		\min \quad & \sum_{\omega \in \Omega} p^\omega \sum_{t = 1}^{t_d^\omega - 1} (c_t I_t + v_t X_t + q_t Q_t) + p^\omega \phi_\omega & \\
		\text{s.t.} \quad & I_{t-1} + X_t - D_t + Q_t = I_t \quad & \forall t = 1, \dots, T \\
		& X_t \leq M_t & \forall t = 1, \dots, T \\
		& \phi_\omega \geq \mathcal{G}\omega(I_{t_d^\omega - 1}^k,X_{t_d^\omega}^k) + \pi_{I,\omega}^k (I_{t_d^\omega - 1} - I_{t_d^\omega - 1}^k) + \pi_{X,\omega}^k (X_{t_d^\omega} - I_{t_d^\omega}^k) & \forall k = 1,2, \dots\\
		& X,I,Q \geq 0 & 
		\end{align*}
		\noi The subprogram for a specific scenario \(\omega \in \Omega\) is denoted as \(\mathcal{G}_\omega(I_{t_d^\omega - 1},X_{t_d^\omega})\).
		\begin{align*}
			\mathcal{G}(I_{t_d^\omega - 1},X_{t_d^\omega}) = \min \quad & \sum_{t = t_d^\omega}^{T} (\overline{c_t^\omega} \overline{I_t^\omega} + \overline{v_t^\omega} \overline{X_t^\omega} + \overline{q_t^\omega} \overline{Q_t^\omega}) &\\
			\text{s.t.} \quad & \overline{I_{t-1}^\omega} + \overline{X_t^\omega} - \overline{D_t^\omega} + \overline{Q_t^\omega} = \overline{I_t^\omega}, & \forall t = t_d^\omega, \dots, T \qquad :\gamma_t\\
			& \overline{I_{t_d^\omega -1}^\omega} = I_{t_d^\omega - 1} & \qquad : \pi_I \\
			& \overline{X_{t_d^\omega}^\omega} = I_{t_d^\omega} & \qquad : \pi_X \\
			& \overline{X_t^\omega} \leq \overline{M_t^\omega} & \forall t = t_d^\omega, \dots, T \qquad: u_t
		\end{align*}

	\subsection{Modeling the Inventory Problem with Multiple-Disruptions with a Multi-Stage Stochastic Program}
	Remained to be finished.

	\subsection{Example: Modeling the Inventory Problem with MDP}
		For the example in section~\ref{sec:example}, the unit of the decision epoch is one month. \[\mathscr{T}=\{1,2,\dots,T_{max}\}, \quad T_{max}\leq +\infty\]
		The state of this problem is the tuple that consists of the inventory on hand at the beginning of each decision epoch and the binary variable indicating whether the disruption has happened. It is realistic to suppose the inventory is integer and has an upper bound \(M\). Then the state space of the problem is \[\mathscr{S}=\{(0,0),(1,0),\dots,(M,0),(0,1),(1,1),\dots,(M,1)\}\]
		Suppose at the beginning of the epoch \(t\) the state is \((s_t,i_t),  s_t \in \mathbb{Z}^+, s \leq M, i_t \in \{0,1\}\). The action means the number of the product to be purchased in epoch \(t\). Therefore, the action space is an integer set with an upper bound \(M-s_t\). \[A_{(s_t,i_t)}=\{0, 1, \dots, M-s_t\}\]
		The calculation for the expected reward of each epoch can be divided into three parts: the ordering cost, the holding cost and the revenue. The ordering cost is a function of the action and can be calculated with the following equation. \[O((s_t,i_t),a) = \begin{cases}
		K^i+c_v^{i_t}a & \text{if } a \geq 0 \\
		0 & \text{if } a = 0
		\end{cases}
		\qquad a \in A_{(s_t,i_t)}\]
		The holding cost \(h((s_t,i_t))\) is proportional to the number of products the factory holds for epoch \(t\). According to the timeline in Section 1.2, the number of products held in the inventory is the state at the beginning of epoch \(t\), \(s_t\). Therefore, \[h((s_t,i_t),a)=c_I^{i_t}s_t\]
		It takes more than just the current state to calculate the revenue as the revenue depends on both the current state and the demand information. However, the demand information is stochastic. To express this deterministically, the way in Puternam is to calculate the revenue using both the current state \(s_t\) and the next epoch's state \(s_{t+1}\). \[R((s_t,i_t),(s_{t+1},i_{t+1}),a)=c_s^{i_t}(s_{t+1}-(s_{t}+a))\] 
		This is an exact way to express the revenue, but later we will derive the optimality equation for this MDP and the dependence on the next epoch's state will disappear when we take the expectation value. The expected revenue does not depend on exact demand occurring in this epoch, but depends on the distribution of the demand only. Suppose the probability if a demand \(d\) occurs is denoted by \(p^{*i_t}_d\). The expected revenue is \[R_E((s_t,i_t),a)=c_s^{i_t}(\sum_{d \in D^{i_t}}p^{*i_t}_{d|s_t}d)\]
		The transition probability matrix could be formed if we are given with a specific policy \(\pi=(\delta^1,\delta^2,\dots)\), just as stated in Section 2.1. The transition probability from the state \((s_t,i_t)\) to \((s_{t+1},i_t)\) is \[ Pr\{(s_{t+1}i,_{t+1})|(s_t,i_t),\delta_{(s_t,i_t)}\} = \begin{cases} 
		p^{*i_t}_{s_t+a-s_{t+1}}(1-p) & \quad \text{if } s_{t+1} \neq 0, i_t = 0, i_{t+1} = 0\\ 
		\sum_{d \geq s_t+a} p^{*i_t}_d(1-p) & \quad \text{if } s_{t+1} = 0, i_t=0, i_{t+1} = 0\\ 
		p^{*i_t}_{s_t+a-s_{t+1}}p & \quad \text{if } s_{t+1} \neq 0, i_t = 0, i_{t+1} = 1\\ 
		\sum_{d \geq s_t+a} p^{*i_t}_dp & \quad \text{if } s_{t+1} = 0, i_t=0, i_{t+1} = 1\\ 
		p^{*i_t}_{s_t+a-s_{t+1}} & \quad \text{if } s_{t+1} \neq 0, i_t = 1, i_{t+1} = 1\\ 
		\sum_{d \geq s_t+a} p^{*i_t}_d & \quad \text{if } s_{t+1} = 0, i_t=1, i_{t+1} = 1\\ 
		0 & \quad \text{Otherwise}
		\end{cases} \]

\section{Comments}
Remained to be finished.

\section{Other thoughts}
Remained to be finished.

%----------------------------------------------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{disruption}
%----------------------------------------------------------------------------------------------------------------------

\end{document}

%	With the formulation in the section 1, if we assume each change can only be binary and the possibility of change is known to us as \(p\), then we can rewrite the problem as:
%	\begin{align*}
%	\min \quad & C_Tx+\sum_{i=1}^Tp_ih_i(x_1,\dots,x_i)\\
%	\text{s.t.} \quad & Dx \leq d\\
%	& x \geq 0
%	\end{align*}
%	If we can assume that the problem \(h(x_1,\dots,x_i)\) is a linear programming problem which can be rewritten as:
%	\begin{align*}
%	h(x_1,\dots,x_i)= \min \quad & q_iy_i \\
%	\text{s.t.} \quad & B_ix+D_iy_i=d_i\\
%	\end{align*}
%	Here we let \(h_T(x_1,\dots,x_T)=0\). We may use \(\theta_i\) to create cut for each scenario and each scenario is corresponding to the stage of the disruption happening.

%	After the change, if the part of \(h_i(x_1,\dots,x_i)\) corresponding to each time period has the same form and is independent from each other, we can rewrite the problem in the following form. Here we use an example of resource allocation problem. Suppose we use \(x\) as the capacity we invest in, we would like to minimize the total cost of the entire plan. If we assume each time period the decisions are independent, function \(h_i\) will be equivalent to optimizing over a single time period:
%	\begin{align*}
%	\min \quad & \sum_{j=1}^m C^Y_jy_j\\
%	\text{s.t.} \quad & \sum_{j=1}^m y_j \leq \sum_{\tau=1}^i x_{\tau}
%	\end{align*}
%	The whole formulation will turn to, if we do not consider the discount factor, the following program:
%	\begin{align*}
%	\min \quad & \sum_{i=1}^T (1-p)^{i-1}(C_ix_i+p(T+1-i)\min \sum_{j=1}^m C^Y_jy_{ij})\\
%	\text{s.t.} \quad & \sum_{j=1}^m y_{ij} \leq \sum_{\tau=1}^i x_\tau \quad \forall i=1 \dots T\\
%	& Dx \leq d\\
%	& x \geq 0
%	\end{align*}

% Whatever might be useful...

% \begin{equation}\label{model:true}

% \end{equation}

% \begin{subequations}
% \begin{eqnarray}
% \P \left [ \sqrt{n} \left ( L_n(\theta_n^*) - z^* \right ) \le \eta s_{\max}  \right ]  & \ge &\dst  \P \left [  \sqrt{n} \left ( \bar{F}_{N_k}(\theta^*) - z^* % \right )/\sigma(\theta^*) \le \eta \left ( \frac{s_{\max}}{\sigma(\theta^*)} \right)  \, : \, \forall k \right ] \\
% & = & \dst  \left ( \P \left [  \sqrt{n} \left ( \bar{F}_{N_k}(\theta^*) - z^* \right ) / \sigma(\theta^*) \le \eta  \left ( \frac{s_{\max}}{\sigma(\theta^*)} \right)   \right ] \right )^K,
% \end{eqnarray}
% \end{subequations}

% \begin{theorem}\label{the_lb_theorem}
% Consider model~~\eqref{model:true}, where $\Theta \neq \emptyset$ is convex, $F(\cdot,x,y)$ is convex for all $(x,y)$, $\var [ F(\theta,x,y) ] < \infty$ for all $\theta \in \Theta$, and $z^* > -\infty$. Let $(x^i,y^i)$, $i=1,2,\ldots$ be i.i.d.\ observations partitioned into non-overlapping batches indexed by $N_k$, $k=1,2,\ldots,K$, where $|N_k|=n$ for all $k$. Define $s^2_{\max}$ as in equations~\eqref{sample_variance} and~\eqref{eqn:smax}. Let $0 < \alpha < 1/2$, define $\eta_\ell$ via $\P \left [ \cN(0,1)  \le \eta_\ell \right ] = (1-\alpha)^{1/K}$, and let $L_n(\theta_n^*)$ be the optimal value of~\eqref{eqn:LP}. Assume $\liminf_{n \rightarrow \infty} s^2_{\max} \ge \inf_{\theta \in \Theta^*} \var [ F(\theta,x,y) ]$, w.p.1., where $\Theta^*$ is the set of optimal solutions to~\eqref{model:true}, e.g., a singleton set if~\eqref{model:true} has a unique optimal solution. Then,
% \begin{equation}\label{eqn:lower_bound_result}
% \liminf_{n \rightarrow \infty} \P \left [  L_n(\theta_n^*) - \frac{\eta_\ell s_{\max}}{\sqrt{n}} \le  z^*\right ]  \ge  1-\alpha.
% \end{equation}
% \end{theorem}

### 2017-09-22 Writeup/PERT_WriteUp.tex
Restructure the whole program and make the recourse continuous

@@
 \newcommand{\underv}{\mbox{$\underbar{$v$}$}}
-%\allowdisplaybreaks
+\allowdisplaybreaks
 
@@
 \section{Introduction} \label{sec:intro}
-	\begin{itemize}
-		\item Literature review: PERT set up, applications.
-		\item Literature review: stochastic disruptions.
-		\item Paper structure.
-	\end{itemize}
-	\textcolor{blue}{One sentence background/history on project management.} A project could be viewed as a collection of activities, each of which will consume some time and resources.
+	Project management has been a topic studied by many operations researchers using ``engineering science and optimization theory" \cite{soderlund2004building}.
+In order to derive an abstract model, a project could be viewed as a collection of activities, each of which will consume some time and resources.
 There will be precedence relationships between activities due to logical or technological considerations.
@@
 If we assume a finite set of crashing options, the problem could be modeled as a mixed integer program.
-\textcolor{blue}{list the original crashing problem literature} The static model can be extended to incorporate uncertainty of activity durations.
-Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is really possible to provide an analytical expression of the true expected project span.
-\textcolor{blue}{list the literature of stochastic crashing optimization problems.} Another approach to handle the uncertainty is the robust optimization method.
+The static model can be extended to incorporate uncertainty of activity durations.
+Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is not really possible to provide an analytical expression of the true expected project span \cite{burt1971conditional,van1963letter}.
+Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant,ke2014genetic,kim2007heuristic}.
+Another approach to handle the uncertainty is the robust optimization method.
 In the robust optimization setting, the objective is to minimize the worst case project span within the uncertainty set.
-\textcolor{blue}{list the literature of robust crashing optimization problems}\\
+\textcolor{blue}{select a few papers about robust project crashing and describe what they did.}\\
 	\newline
@@
 A stochastic disruption is an event that may occur any time in the time horizon and change the system parameters significantly.
+There have been a few papers in applying this idea when the disruption could only occur in a set of specified time periods.
 Yu and Qi \cite{yu2004disruptionmgt} introduced scenario-based optimization models and applied it to solve airline scheduling problems.
@@
 This structure ``falls between standard two-stage and multi-stage stochastic programs for a multi-period problem" and reduces the size of the problem to a quadratic growth in the number of time periods.
-Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing continuous disruption time instead of the fixed stages.
-\textcolor{blue}{list the past papers about the (lacked) work in the stochastic disruption}.\\
+Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing continuous disruption time instead of fixed time periods.\\
 	\newline
-	Since it is a new model of uncertainty, we first formally describe the crashing optimization problem with disruptions.
+	We first formally describe the crashing optimization problem under stochastic disruptions.
 Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}.
 The large scale and the discrete non-convex nature of the extended formulation means it may not be solved efficiently to desirable tolerance level.
-In Section~\ref{sec:decomposition}, a branch-and-bound method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
-We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.
-\\
+In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
+We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.\\
 	\newline
-	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the static solution obtained by solving the crashing optimization, and the time improvement by using the decomposition method in Section~\ref{sec:decomposition} compared to solving the extensive formulation.
-The experiment result shows \textcolor{blue}{append summary of the experiment results here.} We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
+	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the solution obtained by solving a  crashing optimization problem with a deterministic disruption, and the computational performance of the decomposition method in Section~\ref{sec:decomposition}, compared to that of solving the extensive formulation.
+The experiment result shows \textcolor{blue}{(append summary of the experiment results here.)} We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
 
 \section{Problem Formulation} \label{sec:formulation}
-	\begin{itemize}
-		\item Static PERT problem formulation/ Stochastic PERT literature review: simulation optimization/ Distributionally robust: Natarajan
-		\item Assumptions: not affected by the disruption once started.
-	\end{itemize}
 	The deterministic project crashing optimization problem is widely researched since 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
 Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\).
-The budget limit \(B\) and the nominal length of each activity \(D_i\) are given.
-For each activity \(i \in I\), there is a finite set of crashing options \(j \in J_i\) and each of them will incur a cost of \(b_{ij}\) while cutting down the nominal activity length to \(1 - e_{ij}\) of the nominal length.
-We assume each activity could be crashed at most once and the problem could be formulated as follows.
+Each element in set \(\mathcal{A}\) is a two dimensional vector \((i,k)\), which indicates that we have to finish activity \(i\) before starting activity \(k\), \(i,k \in I\).
+The nominal length of each activity \(D_i\) is given, which means if there is no disruption, activity \(i\) will require \(D_i\) amount of time to finish.
+For each activity \(i \in I\), there is a finite set of crashing options \(j \in J_i\) and each of them will incur a cost of \(b_{ij}\).
+Applying crashing option \(j\) will decrease the activity length to \(1 - e_{ij}\) of its non-crashed length.
+We assume each activity can be crashed at most once and the total crashing cost could not be over a given budget \(B\).
+The deterministic project crashing problem could be formulated as follows:
 	\begin{subequations} \label{prob:static}
@@
 			\min \quad & t_N &\\
-			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \\
-			& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
-			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \\
+			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:dotN}\\
+			& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A} \label{cons:dott}\\
+			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \label{cons:doBudget}\\
 			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
@@
 In this problem, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
-Variables \(F^\omega_i\) and \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:f}) - (\ref{cons:fg})).
+Variables \(F^\omega_i\) and \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:F}) - (\ref{cons:FG})).
 This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
@@
 			\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega \\
-			& t_N \geq t_i & \\
+			& t_N \geq t_i & \label{cons:tN}\\
 			& t_i^\omega \geq 0 & \forall i \in I, \omega \in \Omega\\
 			& t_i \geq 0 & \forall i \in I\\
-			& H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:f}\\
-			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:g}\\
-			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \label{cons:fg}\\
-			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf1}\\
-			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf2}\\
-			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
-			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
+			& H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:F}\\
+			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:G}\\
+			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \label{cons:FG}\\
+			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:tF1}\\
+			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:tF2}\\
+			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xF1}\\
+			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xF2}\\
 			& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
@@
 		(S^\omega_L) \quad \min \quad & t_N & \\
-		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:tN}\\
+		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:stN}\\
 		& H^\omega - F_i M \leq t_i & \forall i \in I \\
@@
 		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N + \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
-		\text{s.t.} \quad & (\ref{cons:tN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange}) \label{cons:X}
+		\text{s.t.} \quad & (\ref{cons:stN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange}) \label{cons:X}
 		\end{align}
@@
 	\newline
-	\textcolor{blue}{Algorithm of branch and cut.}
+	We now present a branch-and-cut algorithm that generates both Lagrangian cuts and shifted cuts:
+	\begin{algorithm}[H]
+		\caption{Branch-and-cut procedure for the project crashing problem with one stochastic disruption}
+		\label{alg:Cut}
+		\begin{algorithmic}[1]
+			\State Initialize with an empty node list.
+Create a node \(0\) and append it to the node list.
+Let \(LB = -\infty\) and \(UB = +\infty\) denote the lower bound and upper bound of the entire branching tree.
+			\State At node \(0\), initialize with a master problem \((M)\) and a set of sub problems \((S^\omega)\).
+Let \(k = 0\) be the index of nodes.
+Let \(c_m\) denote the number of iterations that the lower bound \(LB\) has not been improved.
+			\While{\(LB < UB\) and \(c_m \leq m\)}
+			\For{\(\omega \in \Omega\)}
+				\State aaa
+			\EndFor{\textbf{end for}}
+
+			\EndWhile{\textbf{end while}}
+
+			\State Plug \(\hat{s}^{p,k}, \hat{s}^{q,k}\) in the sub problem \(SDI\) and solve the sub problem. Record solution \(\lambda^{p,k}, \lambda^{q,k}\) and optimal objective value \(z_{feas}^k\);
+			\While{\(z_{feas}^k > \epsilon\)} 
+			\State Generate the feasibility cut as \(z_{feas}^k -\lambda^{p,k}(s^p - \hat{s}^{p,k}) - \lambda^{q,k} (s^q - \hat{s}^{q,k}) \leq 0\);
+			\State Append the feasibility cut to the master problem and obtain the updated master problem as \((M^{k+1})\);
+			\State \(k := k+1\);
+			\State Solve the master problem \((M^k+1)\); \\
+			\State Record solution \(\hat{s}^{p,k}, \hat{s}^{q,k}\) and optimal objective value \(LB = v^*(M^k)\); 
+			\State Plug \(\hat{s}^{p,k}, \hat{s}^{q,k}\) in the sub problem \(SDI\) and solve the sub problem; \\
+			\State Record solution \(\lambda^{p,k}, \lambda^{q,k}\) and optimal objective value \(z_{feas}^k\);
+			\EndWhile{\textbf{end while}}
+			\State Output \(LB\) as the lower bound of the robust ACOPF problem and \(\hat{s}^{p,k}, \hat{s}^{q,k}\) as the \(\epsilon\)-feasible solution.
+		\end{algorithmic}
+	\end{algorithm}
+	\noi We prove that when this algorithm terminates, the solution obtained will be optimal because of the tightness property described before in this section.
+	\begin{theorem}
+		Algorithm~\ref{alg:Cut} will terminate with an optimal solution to model~\eqref{prob:extensive}.
+	\end{theorem}
+	\begin{proof}
+		aaa
+	\end{proof}
 \section{Computational Results} \label{sec:results}
+	\subsection{Computational Performance}
+		With the implementation of Algorithm~\ref{alg:Cut}, we aim to test the computational performance of the algorithm with a group of test data, where the following performance measures will be specifically checked:
+		\begin{itemize}
+			\item How many nodes does the algorithm explore?
+			\item How many cuts does the algorithm generate before reaching optimality?
+			\item How fast do the upper bound and the lower bound converge?
+		\end{itemize}
+		\textcolor{blue}{Include the test results here.}
+	\subsection{Benchmark Test against Deterministic Project Crashing Problem}
+		We will also compare the result of our model and a deterministic project crashing problem with a known disruption time and a known disruption magnitude as the benchmark, in order to justify the value of our model.
+We suppose the random variable for the timing of the stochastic disruption is denoted by \(H\) and the random variable for the duration of each activity \(i \in I\) after the disruption is denoted by \(\tilde{D}_i\).
+We also suppose that the mean values of those random variables are known as \(\E[H]\) and \(\E[\tilde{D}_i],\ i \in I\).
+A deterministic, moderate-sized mixed integer program can be established as follows:
+		\begin{subequations}
+			\label{prob:dextensive}
+			\begin{align}
+			\min \quad & t_N &\\
+			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:dtN}\\
+			& \E[H] - F_i M \leq t_i & \forall i \in I \label{cons:dFt}\\
+			& \E[H] + G_i M \geq t_i & \forall i \in I \label{cons:dGt}\\
+			& F_i + G_i = 1 & \forall i \in I \label{cons:dFG}\\
+			& t_k - t_i \geq D_i F_i + \E[\tilde{D}_i] G_i - \sum_{j \in J_i} D_i e_{ij} x^F_{ij} - \sum_{j \in J_i} \E[\tilde{D}_i] e_{ij} x^G_{ij} & \forall i \in I, (i,k) \in \mathcal{A} \label{cons:dtt}\\
+			& x_{ij} \geq x_{ij}^F & \forall i \in I,\ j \in J_i \label{cons:dxF1}\\
+			& F_i \geq x_{ij}^F & \forall i \in I,\ j \in J_i \label{cons:dxF2}\\
+			& x_{ij} + F_i - 1 \leq x_{ij}^F & \forall i \in I, \ j \in J_i \label{cons:dxF3}\\
+			& x_{ij} \geq x_{ij}^G & \forall i \in I,\ j \in J_i \label{cons:dxG1}\\
+			& G_i \geq x_{ij}^G & \forall i \in I,\ j \in J_i \label{cons:dxG2}\\
+			& x_{ij} + G_i - 1 \leq x_{ij}^G & \forall i \in I, \ j \in J_i \label{cons:dxG3}\\
+			& \sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B & \label{cons:dBudget}\\
+			& \sum_{j \in J_i} x_{ij}\leq 1 & \forall i \in I \label{cons:dOneCrash}\\ 
+			& t_i \geq 0 & \forall i \in I\\
+			& F_i, G_i \in \{0,1\} & \forall i \in I \\
+			& x_{ij}, x_{ij}^F, x_{ij}^G \in \{0,1\} & \forall i \in I.
+			\end{align}
+		\end{subequations}
+		The objective of this model is to minimize the total project span, assuming that the disruption happens at the expected time \(\E[H]\) and the disruption magnitude will take its mean value.
+Constraints~\eqref{cons:dtN} - \eqref{cons:dFG} replicate constraints~\eqref{cons:tN} - \eqref{cons:FG}.
+Constraint~\eqref{cons:dtt} determines whether the duration of each activity \(i \in I\) takes its nominal value \(D_i\) or its after-disruption value \(\E[\tilde{D}_i]\).
+Constraints~\eqref{cons:dxF1} - \eqref{cons:dxG3} linearize bilinear terms \(x_{ij} F_i\) and \(x_{ij}G_i\).
+The budget constraint~\eqref{cons:dBudget} and the constraint of only one crashing per activity~\eqref{cons:dOneCrash} are inherited as well.
+\\
+		\newline 
+		Apparently this is a simplified version of our disruption model because both the timing and the magnitude of the disruption is assumed deterministic in this case.
+If the gap between the objective value of model~\eqref{prob:dextensive} and that of model~\eqref{prob:extensive} is large, we can conclude that our model adds a significant value by including the stochastic disruption.
+We can also fix only the timing or the magnitude of the disruption and run similar tests.
+This way we will be able to tell which factor, timing or magnitude, is more important to be modeled as a random variable.\\
+		\newline
+		\textcolor{blue}{Include the test results here.}
 

### 2017-09-22 src/branchFunc.jl

@@ -1,0 +1,74 @@
+# this is the branching execution of the procedure
+function branchSimple(pData,disData,Ω,node,that,ωSeq)
+    # simply branch the smallest activity-disruption time pair
+    minDist = Inf;
+    minI = -1;
+    minω = -1;
+    for i in pData.II
+        for ω in Ω
+            # only branch on the non determined activity-disruption pair
+            if node.brInfo[findin(pData.II,i)[1],findin(Ω,ω)[1]] == 0
+                distHt = abs(disData[ω].H - that[i]);
+                if distHt < minDist
+                    minDist = distHt;
+                    minI = i;
+                    minω = ω;
+                end
+            end
+        end
+    end
+    # if we find an activity-disruption pair
+    if (minI != -1)&(minω != -1)
+        brInfo1 = deepcopy(node.brInfo);
+        brInfo1[findin(pData.II,minI)[1],findin(Ω,minω)[1]] = -1;
+        brInfo1 = brInfoExt(pData,disData,Ω,brInfo1,ωSeq);
+        brInfo2 = deepcopy(node.brInfo);
+        brInfo2[findin(pData.II,minI),findin(Ω,minω)] = 1;
+        brInfo2 = brInfoExt(pData,disData,Ω,brInfo2,ωSeq);
+    end
+    # add the constraints of node1 and node2
+    mp1 = copy(node.mp);
+    if brInfo1 != []
+        for i in pData.II
+            for ω in Ω
+                if brInfo1[findin(pData.II,i)[1],findin(Ω,ω)[1]] == -1
+                    @constraint(mp1,mp1[:t][i] <= disData[ω].H - 1e-6);
+                elseif brInfo1[findin(pData.II,i)[1],findin(Ω,ω)[1]] == 1
+                    @constraint(mp1,mp1[:t][i] >= disData[ω].H);
+                end
+            end
+        end
+        # inherit the lbCost of the branched node
+        node1 = nodeType(node.lbCost,mp1,brInfo1);
+    end
+    mp2 = copy(node.mp);
+    if brInfo2 != []
+        for i in pData.II
+            for ω in Ω
+                if brInfo2[findin(pData.II,i)[1],findin(Ω,ω)[1]] == -1
+                    @constraint(mp2,mp2[:t][i] <= disData[ω].H - 1e-6);
+                elseif brInfo2[findin(pData.II,i)[1],findin(Ω,ω)[1]] == 1
+                    @constraint(mp2,mp2[:t][i] >= disData[ω].H);
+                end
[…]

### 2017-09-22 src/cutGen_1l.jl

@@ -1,0 +1,115 @@
+# This is the script with all cut generation
+function createMaster(pData,disData,Ω)
+    mp = Model(solver = GurobiSolver());
+    @variables(mp, begin
+      θ[Ω] >= 0
+      0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
+      t[i in pData.II] >= 0
+    end);
+    @constraint(mp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(mp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(mp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+    @objective(mp,Min,pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
+
+    return mp;
+end
+
+function bGenbuild(pData,dDω,xhat,that,brInfo)
+    M = sum(max(pData.D[i],pData.D[i]+dDω.d[i]) for i in pData.II if i != 0);
+
+    sp = Model(solver = GurobiSolver());
+    @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
+    @variable(sp, t[i in pData.II] >= 0);
+    # relax the logic binary variables
+    @variable(sp, 0 <= F[i in pData.II] <= 1);
+    @variable(sp, 0 <= G[i in pData.II] <= 1);
+    @variable(sp, 0 <= s[i in pData.II,j in pData.Ji[i]] <= 1);
+
+    # add the basic sub problem constraints
+    @constraint(sp, FCons[i in pData.II; brInfo[findin(pData.II,i)[1]] == 0],dDω.H - F[i]*M <= that[i]);
+    @constraint(sp, GCons[i in pData.II; brInfo[findin(pData.II,i)[1]] == 0],dDω.H + G[i]*M >= that[i]);
+    @constraint(sp, FFixed[i in pData.II; brInfo[findin(pData.II,i)[1]] == -1],F[i] == 1);
+    @constraint(sp, GFixed[i in pData.II; brInfo[findin(pData.II,i)[1]] == 1],G[i] == 1);
[…]

### 2017-09-22 src/extForm_1l.jl

@@ -1,0 +1,39 @@
+# This is the extensive formulation of PERT (1st case)
+# the disruption does not affect the activities that have not been started
+
+function extForm(pData,disData,Ω)
+    M = Dict();
+    for ω in Ω
+        M[ω] = sum(max(pData.D[i],pData.D[i]+disData[ω].d[i]) for i in pData.II if i != 0);
+    end
+
+    mp = Model(solver = GurobiSolver());
+    @variable(mp,t0[i in pData.II] >= 0);
+    @variable(mp,0 <= x0[i in pData.II, j in pData.Ji[i]] <= 1);
+    @variable(mp,t[i in pData.II, ω in Ω] >= 0);
+    @variable(mp,0 <= x[i in pData.II, j in pData.Ji[i], ω in Ω] <= 1);
+    @variable(mp,F[i in pData.II, ω in Ω], Bin);
+    @variable(mp,G[i in pData.II, ω in Ω], Bin);
+    @variable(mp,0 <= s[i in pData.II, j in pData.Ji[i], ω in Ω] <= 1);
+
+    @constraint(mp, FConstr[i in pData.II, ω in Ω], disData[ω].H - F[i,ω]*M[ω] <= t0[i]);
+    @constraint(mp, GConstr[i in pData.II, ω in Ω], disData[ω].H + G[i,ω]*M[ω] >= t0[i]);
+    @constraint(mp, FGConstr[i in pData.II, ω in Ω], F[i,ω] + G[i,ω] == 1);
+    @constraint(mp, tConstr1[i in pData.II, ω in Ω], t[i,ω] + (1 - F[i,ω])*M[ω] >= t0[i]);
+    @constraint(mp, tConstr2[i in pData.II, ω in Ω], t[i,ω] - (1 - F[i,ω])*M[ω] <= t0[i]);
+    @constraint(mp, tConstr3[i in pData.II, ω in Ω], t[i,ω] >= disData[ω].H * G[i,ω]);
+    @constraint(mp, xConstr1[i in pData.II, j in pData.Ji[i], ω in Ω], x[i,j,ω] + (1 - F[i,ω]) >= x0[i,j]);
+    @constraint(mp, xConstr2[i in pData.II, j in pData.Ji[i], ω in Ω], x[i,j,ω] - (1 - F[i,ω]) <= x0[i,j]);
[…]

### 2017-09-22 src/readIn.jl

@@ -1,0 +1,157 @@
+using Distributions,HDF5,JLD;
+
+# This is the input function that reads in the project data
+function readInP(pInputAdd,kInputAdd)
+    pRaw = readdlm(pInputAdd,',',header = false);
+    kRaw = readdlm(kInputAdd,',',header = false);
+
+    np,mp = size(pRaw);
+    nk,tempk = size(kRaw);
+    # total budget
+    B = pRaw[1,1];
+    # nominal scenario probability
+    p0 = pRaw[1,2];
+
+    # 0 as the last activity
+    II = [0];
+    Ji = Dict();
+    D = Dict();
+    D[0] = 0;
+    Ji[0] = [];
+    b = Dict();
+    b[0] = Dict();
+    eff = Dict();
+    eff[0] = Dict();
+
+    # read in the activity information
+    for i in 2:np
+        lineID = Int64(pRaw[i,1]);
+        push!(II,lineID);
+        D[lineID] = pRaw[i,2];
+
+        jStart = 3;
+        Ji[lineID] = [];
+        b[lineID] = Dict();
+        eff[lineID] = Dict();
+        jCounter = 0;
+        jStart = 3;
+        while jStart <= mp
+            jCounter += 1;
+            push!(Ji[lineID],jCounter);
+            b[lineID][jCounter] = Float64(pRaw[i,1+2*jCounter]);
+            eff[lineID][jCounter] = Float64(pRaw[i,2+2*jCounter]);
+            jStart += 2;
+        end
+    end
+
+    # read in the activity precedence information
+    K = [];
+    Pre = Dict();
+    Pre[0] = [];
+    Succ = Dict();
+    Succ[0] = [];
+    for i in II
+        if i != 0
+            push!(K,(i,0));
+            push!(Pre[0],i);
+            Pre[i] = [];
+            Succ[i] = [0];
+        end
+    end
+
+    for k in 1:nk
+        fromI = Int64(kRaw[k,1]);
+        toI = Int64(kRaw[k,2]);
+        push!(K,(fromI,toI));
+        push!(Pre[toI],fromI);
+        push!(Succ[fromI],toI);
+    end
+
+    pData = pInfo(II,Ji,D,b,eff,B,p0,K,Pre,Succ);
+    return pData;
+end
+
+# read in the scenario information from file
+function readInDis(ΩInputAdd)
[…]

### 2017-09-22 src/test1_0.jl

@@ -1,0 +1,18 @@
+# This is the script to load the data and solve the problem
+@everywhere using JuMP,Gurobi;
+
+@everywhere include("def.jl");
+@everywhere include("readIn.jl");
+@everywhere include("main_1l.jl");
+@everywhere include("cutGen_1l.jl");
+@everywhere include("tightenGen_1l.jl");
+@everywhere include("branchFunc.jl");
+
+pInputAdd = "test_full_P.csv";
+kInputAdd = "test_full_K.csv";
+ΩInputAdd = "test_full_Omega.csv";
+
+pData = readInP(pInputAdd,kInputAdd);
+disData,Ω = readInDis(ΩInputAdd);
+
+tbest,xbest,fbest = cutProc_Benders(pData,disData,Ω);

### 2017-09-22 src/tightenGen_1l.jl

@@ -1,0 +1,106 @@
+# This is the function to find valid inequalities given temporal relationships
+function getOmegaSeq(disData)
+    sortedDis = sort(collect(disData),by = x->x[2].H);
+    ωSeq = [];
+    for item in sortedDis
+        push!(ωSeq,item[1]);
+    end
+    return ωSeq;
+end
+
+# detect the inconsistency within the same activity
+function findWrongI(i,brInfo,ωSeq)
+    # no -1 should be on the left hand side of 1
+    correctBool = true;
+    oneRight = -1;
+    negoneLeft = length(ωSeq) + 1;
+    for j in 1:length(ωSeq)
+        if brInfo[findin(pData.II,i)[1],ωSeq[j]] == -1
+            negoneLeft = min(j,negoneLeft);
+        end
+        if brInfo[findin(pData.II,i)[1],ωSeq[j]] == 1
+            oneRight = max(j,oneRight);
+        end
+    end
+    if oneRight > negoneLeft
+        correctBool = false;
+    end
+    return correctBool,oneRight,negoneLeft;
+end
+
+# exploint the brInfo
+function brInfoExt(pData,disData,Ω,brInfo,ωSeq)
+    # currently just guarantee the consistency in:
+    #   the same activity: if activity i starts after ω1, then it should also start after any disruption time before disData[ω1].H
+    #   the adjacent activity: if activity i starts before ω1, then all its predecessors should start before ω1
+    oneRight = Dict();
+    negoneLeft = Dict();
+    inconBool = true;
+    for i in pData.II
+        correctBool,oneRight[i],negoneLeft[i] = findWrongI(i,brInfo,ωSeq);
+        if correctBool
+            # if there is no inconsistency, then change the brInfo
+            for j in 1:oneRight[i]
+                brInfo[findin(pData.II,i)[1],findin(Ω,ωSeq[j])[1]] = 1;
+            end
+            for j in negoneLeft[i]:length(Ω)
+                brInfo[findin(pData.II,i)[1],findin(Ω,ωSeq[j])[1]] = -1;
+            end
+        else
+            # if there is an inconsistency, then return [] for brInfo
+            brInfo = [];
+            inconBool = false;
+            break;
+        end
+    end
+    # test the inconsistency among precedence relationships
+    if inconBool
+        brInfoPrev = [];
+        while brInfoPrev != brInfo
+            brInfoPrev = deepcopy(brInfo);
+            for i in pData.II
+                # its predecessors oneRight have to be smaller than its negoneLeft
[…]

### 2018-01-04 Writeup/PERT_New.tex
Updated writeup and the readin functions for stratafication

--- 2017-07-21 PERT_WriteUp.tex
@@
 \usepackage{algorithm}
+\usepackage{longtable}
 \usepackage[noend]{algpseudocode}
@@
 
-\section{Introduction} \label{sec:intro}
-	\begin{itemize}
-		\item Literature review: PERT set up, applications.
-		\item Literature review: stochastic disruptions.
-		\item Paper structure.
-	\end{itemize}
-	\textcolor{blue}{One sentence background/history on project management.} A project could be viewed as a collection of activities, each of which will consume some time and resources.
+\section{Introduction} \label{sec:introduction}
+	Project management has been a topic studied by many operations researchers using ``engineering science and optimization theory" \cite{soderlund2004building}.
+In order to derive an abstract model, a project could be viewed as a collection of activities, each of which will consume some time and resources.
 There will be precedence relationships between activities due to logical or technological considerations.
@@
 If we assume a finite set of crashing options, the problem could be modeled as a mixed integer program.
-\textcolor{blue}{list the original crashing problem literature} The static model can be extended to incorporate uncertainty of activity durations.
-Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is really possible to provide an analytical expression of the true expected project span.
-\textcolor{blue}{list the literature of stochastic crashing optimization problems.} Another approach to handle the uncertainty is the robust optimization method.
+The static model can be extended to incorporate uncertainty of activity durations.
+Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is not really possible to provide an analytical expression of the true expected project span \cite{burt1971conditional,van1963letter}.
+Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant,bowman1994stochastic,ke2014genetic,kim2007heuristic}.
+Another approach to handle the uncertainty is the robust optimization method.
 In the robust optimization setting, the objective is to minimize the worst case project span within the uncertainty set.
-\textcolor{blue}{list the literature of robust crashing optimization problems}\\
+It can be proved that an affinely adaptive recourse decision, although computationally tractable as it can be reformulated as a linear program or a second order conic program (SOCP), may lead to suboptimal solutions \cite{chen2008linear,cohen2007stochastic}.
+However, once the recourse decision rule is extended to a general form, it is only tractable to solve the robust optimization problem with hypercube uncertainty sets, which is a trivial case because the worst-case scenario in the uncertainty set is always the point where every activity takes the upper bound.
+\cite{wiesemann2012robust}.
+In recent years, distributionally robust optimization has been developed quickly in literature \cite{delage2010distributionally}.
+Ahipasaoglu et al.
+\cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.\\
 	\newline
@@
 This structure ``falls between standard two-stage and multi-stage stochastic programs for a multi-period problem" and reduces the size of the problem to a quadratic growth in the number of time periods.
-Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing continuous disruption time instead of the fixed stages.
-\textcolor{blue}{list the past papers about the (lacked) work in the stochastic disruption}.\\
+Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing continuous disruption time instead of fixed time periods.\\
 	\newline
-	Since it is a new model of uncertainty, we first formally describe the crashing optimization problem with disruptions.
+	We first formally describe the crashing optimization problem under stochastic disruptions.
 Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}.
-The large scale and the discrete non-convex nature of the extended formulation means it may not be solved efficiently to desirable tolerance level.
-In Section~\ref{sec:decomposition}, a branch-and-bound method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
-We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.
-\\
+If we assume continuous distributions for the disruption time and magnitude, sample average approximation (SAA) can be used to create a finite set of scenarios and approximate the original problem by a finite-sized optimization problem.
+We prove some important consistency and convergence properties of the SAA problem using independent and identically distributed samples and stratified samples in Section~\ref{sec:consistency}.\\
 	\newline
-	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the static solution obtained by solving the crashing optimization, and the time improvement by using the decomposition method in Section~\ref{sec:decomposition} compared to solving the extensive formulation.
-The experiment result shows \textcolor{blue}{append summary of the experiment results here.} We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
+	The large scale and the discrete non-convex nature of the SAA problem's extended formulation means it may not be solved efficiently to desirable tolerance level.
+In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
+We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.\\
+	\newline
+	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the solution obtained by solving a  crashing optimization problem with a deterministic disruption, and the computational performance of the decomposition method in Section~\ref{sec:decomposition}, compared to that of solving the extensive formulation.
+We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
 
 \section{Problem Formulation} \label{sec:formulation}
-	\begin{itemize}
-		\item Static PERT problem formulation/ Stochastic PERT literature review: simulation optimization/ Distributionally robust: Natarajan
-		\item Assumptions: not affected by the disruption once started.
-	\end{itemize}
 	The deterministic project crashing optimization problem is widely researched since 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
@@
 We assume each activity could be crashed at most once and the problem could be formulated as follows.
-	\begin{subequations} \label{prob:static}
+	\begin{subequations} \label{prob2:static}
 		\begin{align}
 		\min \quad & t_N &\\
-			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \\
-			& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
+		\text{s.t.} \quad & t_N \geq t_i & \forall \,i \in I \\
+		& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall \,i \in I, (i,k) \in \mathcal{A}\\
 		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \\
-			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
-			& t_i \geq 0 & \forall i \in I\\
-			& x_{ij} \in \{0,1\} & \forall i \in I, j \in J_i&
+		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall \,i \in I\\
+		& t_i \geq 0 & \forall \,i \in I\\
+		& 0 \leq x_{ij} \leq 1 & \forall \,i \in I, j \in J_i&
 		\end{align}
 	\end{subequations}
-	Based on this formulation, we can derive the stochastic optimization and the robust optimization models with reference to \textcolor{blue}{list the literature of stochastic/robust crashing optimization problems}.
-We omit these formulations in this paper since our uncertainty model is different from the literature listed above.\\
+	Based on this formulation, we can derive the stochastic optimization and the robust optimization models with reference to the literature listed in Section~\ref{sec:introduction}.
+We omit these formulations in this paper since our uncertainty model is different from previous settings.\\
 	\newline
@@
 	The notation for the model is displayed as follows:
-	\begin{table}[H]
-		\begin{tabular}{ l l l l }
+	\begin{longtable}[H]{ l l l l }
 		\multicolumn{4}{l}{Indices and index sets} \\
@@
 		\(I\) & \(\qquad\) & the set of activities;&\\
+		\(I_i\) & \(\qquad\) & the set of activities which directly lead to activity \(i\); &\\
 		\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i\), \(i \in I\);&\\
@@
 		\(x_{ij}^\omega\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) under scenario \(\omega\), \(i \in I, j \in J_i, \omega \in \Omega \); &\\
-			\(F_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts before disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
 		\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
 		\(S_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\
-		\end{tabular}
-	\end{table}
-	\noi The extensive formulation of the two-stage stochastic program is shown as Formulation~(\ref{prob:extensive}).
+	\end{longtable}
+	\noi The extensive formulation of the two-stage stochastic program is shown as Formulation~(\ref{prob2:extensive}).
 Here \(M\) is a large number to enforce the logic relationships.
 In this problem, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
-Variables \(F^\omega_i\) and \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:f}) - (\ref{cons:fg})).
+Variables \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:F}) - (\ref{cons:G})).
 This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
@@
 These logic constraints ensure the decisions made before the disruption time in each scenario should be the same as the nominal decisions before the same time point, because decisions made with the same amount information should be the same.\\
-	\begin{subequations} \label{prob:extensive}
+	\begin{subequations} \label{prob2:extensive}
 		\begin{align}
 		\min \quad & \sum_{\omega \in \Omega} p^\omega t_N^\omega + p^0 t_N& \\
-			\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall i \in I, \omega \in \Omega \\
-			& t_N \geq t_i & \\
-			& t_i^\omega \geq 0 & \forall i \in I, \omega \in \Omega\\
-			& t_i \geq 0 & \forall i \in I\\
-			& H^\omega - F_i^\omega M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:f}\\
-			& H^\omega + G_i^\omega M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:g}\\
-			& F_i^\omega + G_i^\omega = 1 & \forall i \in I, \omega \in \Omega \label{cons:fg}\\
-			& t_i^\omega + (1 - F_i^\omega)M \geq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf1}\\
-			& t_i^\omega - (1 - F_i^\omega)M \leq t_i & \forall i \in I, \omega \in \Omega \label{cons:tf2}\\
-			& x_{ij}^\omega + (1 - F_i^\omega)M \geq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
-			& x_{ij}^\omega - (1 - F_i^\omega)M \leq x_{ij} & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
-			& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
-			& \sum_{j \in J_i} x_{ij}^\omega \leq 1 & \forall i \in I, \omega \in \Omega \label{cons:crashLim}\\
-			& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B & \forall \omega \in \Omega \label{cons:budget}\\
-			& S_{ij}^\omega \leq G_i^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
-			& S_{ij}^\omega \leq x_{ij}^\omega & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
-			& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 & \forall i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
-			& x_{ij}^\omega \in \{0,1\} & \forall i \in I, j \in J_i, \omega \in \Omega\\
-			& F_i^\omega, G_i^\omega \in \{0,1\}. & \forall i \in I, \omega \in \Omega
+		\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall \,i \in I, \omega \in \Omega \\
+		& t_N \geq t_i & \label{cons:tN}\\
+		& t_i^\omega \geq 0 & \forall \,i \in I, \omega \in \Omega\\
+		& t_i \geq 0 & \forall \,i \in I\\
+		& H^\omega - (1 - G_i^\omega) M \leq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:F}\\
+		& H^\omega + G_i^\omega M \geq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:G}\\
+		& t_i^\omega + G_i^\omega M \geq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:tf1}\\
+		& t_i^\omega - G_i^\omega M \leq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:tf2}\\
+		& x_{ij}^\omega + G_i^\omega \geq x_{ij} & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
+		& x_{ij}^\omega - G_i^\omega \leq x_{ij} & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
+		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
+		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 & \forall \,i \in I, \omega \in \Omega \label{cons:crashLim}\\
+		& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B & \forall \,\omega \in \Omega \label{cons:budget}\\
+		& S_{ij}^\omega \leq G_i^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
+		& S_{ij}^\omega \leq x_{ij}^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
+		& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
+		& t_i \geq 0 & \forall\,i \in I \\
+		& t_i^\omega \geq H^\omega G_i^\omega & \forall\, i \in I, \omega \in \Omega \\
+		& 0 \leq x_{ij} \leq 1 & \forall \,i \in I, j \in J_i\\ 
+		& 0 \leq x_{ij}^\omega \leq 1 & \forall \,i \in I, j \in J_i, \omega \in \Omega\\
+		& G_i^\omega \in \{0,1\}. & \forall \,i \in I, \omega \in \Omega
 		\end{align}
@@
 
+\section{Special Cases} \label{sec:examples}
+	In this section we show a few examples to illustrate the properties of the project crashing problem under stochastic disruption displayed in Section~\ref{sec:formulation}.
+We will focus on simple network structures such as serial and parallel networks.
+We also display some general networks where those properties are (or not) applicable.
+	\subsection{Serial Networks}
+		\begin{itemize}
+			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
+			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
+			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
+			\item Only optimal to delay to a possible disruption time.
+		\end{itemize}
+		The first example we present for a serial network is to show that it might be optimal to delay the start of some activities. The reasons of such delay include:
+		\begin{enumerate}
+			\item Some activities might have a shorter length after disruption. It is beneficial to wait a short period of time to capture this advantage.
+			\item Even if all possible disruption magnitudes are adverse, which means they will lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
+		\end{enumerate}
+		Suppose we have a project with three activities in a serial network form.
+The activity 1 should be finished before the start of activity 2 and the activity 2 should be finished before the start of activity 3.
+The structure of the project is displayed as follows.
+We add two dummy activity ``S" and ``T" to represent the start and the end of the project.
+The total crashing budget is \(1\) and the allowed amount of crashing a single activity is between \(0\) and \(1\).
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.8\textwidth]{serial3}
+			\caption{Example of a 3-activity project}
+			\label{fig:serial3}
+		\end{figure}
+		\noi We can set up a nominal case with the length of activity 1, 2 and 3 as \(9\), \(10\) and \(7\).
+The probability of the disruption not occurring is 0.5.
+If a disruption occurs, it will occur at the time \(H = 9.1\).
+Suppose the disruption will change the length of activity 2 from \(10\) to \(3\) and not affect activity 3.
+We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\), spend the entire budget to crash activity 3 if the disruption occurs, and spend the entire budget to crash activity 2 if the disruption does not occur.
+The expected total project span is 18.35.
+If we force the condition that the starting time of activities could not be delayed, we could not observe whether the disruption happens or not at the starting time of activity 2.
+There will be only one possible situation where three activities will have the duration as 9,10 and 7.
+All resources should be allocated to activity 2 and the total project span is 21, which is larger than the expected total project span if it is allowed to delay the starting time of some activities.
+The reason of such phenomenon is that a disruption may reduce some activities' durations.
+Delaying by a small amount will enable us to collect that reduction in time.\\
+		\newline
+		Even if the disruption can only bring negative effect on the duration of activities, a.k.a.
+lengthening all activities after that, it is still beneficial to delay the start of some activities under some circumstances.
+This means a small delay of some activity may gain the information of disruption which is more valuable and potentially decreases the total project span.
+Such claim can be verified by the serial network described in the last paragraph, only changing some duration parameters in the following way.
+Suppose the nominal duration, the timing of possible disruption and the probability of a disruption occurring remain the same.
+If the disruption occurs, it will change the duration of activity 2 to 9.1 and that of activity 3 to 13.
+For this example, if no delay is allowed, the optimal decision is to allocate the entire budget to activity 2 and the expected total project span is 24.
+If we delay the starting time of the activity 2 to 9.1 so that the disruption can be observed before we commit resources to activity 2, the expected total project span is 23.4.
+	\subsection{Parallel Networks}
+		\begin{itemize}
+			\item Not optimal to delay when \(d_i \geq 0\).
+		\end{itemize}
+	\subsection{Y Networks}
+\section{Properties of the Sample Average Approximation Problem} \label{sec:consistency}
+	\subsection{Cheat?}
+	\subsection{Consistency and Convergence Results}
+	\subsection{IID vs. Stratified Sampling}
 \section{Decomposition Method} \label{sec:decomposition}
-	\begin{itemize}
-		\item Formulation: master, sub
-		\item Cut generation
-		\item Branch and bound method
-	\end{itemize}
-	Problem (\ref{prob:extensive}) is a two-sage stochastic mixed integer program with both binary (\(x\)) and continuous (\(t\)) state variables.
-A state variable here is a variable whose value is passed from the first stage to the second stage.
-Two-stage stochastic linear program could be solved nicely using Benders decomposition (\textcolor{blue}{cite Benders decomposition}).
-\\
-	\newline 
-	For our crashing optimization problem, we could separate the extensive formulation (\ref{prob:extensive}) into a master problem and a series of sub-problems as (\ref{prob:master}) and (\ref{prob:sub}).
-Constraint (\ref{cons:linearCuts}) are generated by solving the sub-problems iteratively for the optimal multipliers \(\pi\) and \(\lambda\).
-In a regular multi-cut Benders decomposition case, the sub problem is a convex optimization problem, usually a linear program.
-This means a finite number of constraints on \(\theta^\omega\) can fully characterize the function \(f^\omega(x,t)\).
-However, in this case \(f^\omega(x,t)\) is a mixed integer linear program.
-It is difficult to solve a stochastic mixed integer program with integer variables in the recourse problem because the linear cuts generated in the regular Benders decomposition could not characterize the recourse function exactly.
-\textcolor{blue}{cite literature about the stochastic integer programs}.
-	\begin{subequations}
-		\label{prob:master}
-		\begin{align}
-		(M) \quad \min \quad & p^0 t_N + \sum_{\omega \in \Omega} p^\omega \theta^\omega & \\
-		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I\\
-		& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall i \in I, (i,k) \in \mathcal{A}\\
-		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \\
-		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
-		& \theta^\omega \geq \sum_{i \in I} \pi_i^{\omega,k^\omega} t_i + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,k^\omega} x_{ij} + v^{\omega,k^\omega} & \forall \omega \in \Omega, k^\omega = 1,2, \dots \label{cons:linearCuts}\\
-		& t_i \geq 0 & \forall i \in I\\
-		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i&
-		\end{align}
-	\end{subequations}
-	\begin{subequations}
-		\label{prob:sub}
-		\begin{align}
-			(S^\omega) \quad f^\omega(\hat{x},\hat{t}) = \min \quad & t_N & \\
-			\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \\
-			& H^\omega - F_i M \leq t_i & \forall i \in I \\
-			& H^\omega + G_i M \geq t_i & \forall i \in I \\
-			& F_i + G_i = 1 & \forall i \in I \\
-			& t_i + (1-F_i) M \geq \hat{t}_i & \forall i \in I\\
-			& t_i - (1-F_i) M \leq \hat{t}_i & \forall i \in I \\
-			& x_{ij} + (1-F_i) \geq \hat{x}_{ij} & \forall i \in I, j \in J_i \\
-			& x_{ij} - (1-F_i) \leq \hat{x}_{ij} & \forall i \in I, j \in J_i \\
-			& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij} & \forall i \in I, (i,k) \in \mathcal{A}\\
-			&\sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B &\\
-			& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
-			& S_{ij} \leq G_i & \forall i \in I, j \in J_i \\
-			& S_{ij} \leq x_{ij} & \forall i \in I, j \in J_i\\
-			& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i\\
-			& t_i \geq 0 & \forall i \in I \\
-			& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i
-		\end{align}
-	\end{subequations}
-	Recently Zou et al.
-\cite{zou2016nested} propose to generate Lagrangian cuts in the place of Benders cuts to solve multi-stage stochastic programs with only binary state variables.
-Their method keeps the structure of Benders decomposition and proves the tightness of Lagrangian cuts.
-To generate the Lagrangian multipliers, a local copy (\(\tau\) and \(z\)) of the state variable (\(\hat{t}\) and \(\hat{x}\)) is first created as in constraint (\ref{cons:local1}) and (\ref{cons:local2}) of formulation (\ref{prob:subLocal}).
-We can then relax the constraint (\ref{cons:local1}) and (\ref{cons:local2}) to create a Lagrangian dual problem (\ref{prob:LagDual}).
-The optimal solution  \(\pi^*\) and \(\lambda^*\) to the Lagrangian dual problem will be used in the Lagrangian cuts as in constraint (\ref{cons:linearCuts}).
-Problem (\ref{prob:LagDual}) can be solved by a subgradient method \textcolor{blue}{cite Fisher's tutorial for solving the Lagrangian Relaxation problem}.\\
-	\begin{subequations}
-		\label{prob:subLocal}
-		\begin{align}
-		(S^\omega_L) \quad \min \quad & t_N & \\
-		\text{s.t.} \quad & t_N \geq t_i & \forall i \in I \label{cons:tN}\\
-		& H^\omega - F_i M \leq t_i & \forall i \in I \\
-		& H^\omega + G_i M \geq t_i & \forall i \in I \\
-		& F_i + G_i = 1 & \forall i \in I \\
-		& t_i + (1-F_i) M \geq \tau_i & \forall i \in I\\
-		& t_i - (1-F_i) M \leq \tau_i & \forall i \in I \\
-		& x_{ij} + (1-F_i) \geq z_{ij} & \forall i \in I, j \in J_i \\
-		& x_{ij} - (1-F_i) \leq z_{ij} & \forall i \in I, j \in J_i \\
-		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij} & \forall i \in I, (i,k) \in \mathcal{A}\\
-		&\sum_{i \in I} \sum_{j \in J_i} b_{ij} x_{ij} \leq B &\\
-		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall i \in I\\
-		& S_{ij} \leq G_i & \forall i \in I, j \in J_i \\
-		& S_{ij} \leq x_{ij} & \forall i \in I, j \in J_i\\
-		& S_{ij} \geq G_i + x_{ij} - 1 & \forall i \in I, j \in J_i \label{cons:s3}\\
-		& z_{ij} = \hat{x}_{ij} & \forall i \in I, j \in J_i \label{cons:local1}\\
-		& \tau_{i} = \hat{t}_{i} & \forall i \in I \label{cons:local2}\\
-		& t_i \geq 0 & \forall i \in I \label{cons:tPos}\\
-		& x_{ij} \in \{0,1\}. & \forall i \in I, j \in J_i\\
-		& \tau_i \geq 0 & \forall i \in I \\
-		& 0 \leq z_{ij} \leq 1 . & \forall i \in I, j \in J_i \label{cons:zRange}
-		\end{align}
-	\end{subequations}
-	\begin{subequations}
-		\label{prob:LagDual}
-		\begin{align}
-		(R^\omega) \quad \max_{\pi,\lambda} \min_{t,\tau,x,z} \quad & t_N - \sum_{i \in I} \pi_i(\tau_{i} - \hat{t}_i) - \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}(z_{ij} - \hat{x}_{ij}) & \\
-		\text{s.t.} \quad & (\ref{cons:tN}) - (\ref{cons:s3})\text{ and } (\ref{cons:tPos}) - (\ref{cons:zRange})
-		\end{align}
-	\end{subequations}
-	The result from \cite{zou2016nested} could not be directly applied in our problem since our state variable contains both continuous variables \(t\) and binary variables \(x\).
-The Lagrangian cuts will only be a lower bound but the tightness could not be guaranteed.
-This means that if we carry out a cutting plane scheme using the Lagrangian cuts, solving the master problem (\ref{prob:master}) will only obtain a lower bound.
-\\
-	\newline
-	One important observation to help with this issue is that if we can determine the temporal relationship between every activity and the disruption, the restricted version of the function \(f^\omega\) will be convex in \(t\), and we could find a tight and valid Lagrangian cut similar to those in \cite{zou2016nested}.
-This means, for example, if for a specific scenario \(\omega\), \(H^\omega = 5\), and for each activity \(i \in I\) we know whether its starting time \(t_i\) is less than, larger than or equal to \(H^\omega = 5\), then there is a finite set of linear constraints that could be generated to fully characterize \(f^\omega(x,t)\) in formulation~(\ref{prob:master}).
-This property is true mainly because once we know the temporal relationship between the starting time of each activity and the disruption time, it is always optimal to start the activity at its earliest possible time.
-We will prove this property as follows.
-	\begin{theorem}
-		For a specific scenario \(\omega\), let \(\pi^*\) and \(\lambda^*\) be an optimal solution and \(v^*\) be the optimal objective value to the Lagrangian dual problem (\(R^\omega\)) in (\ref{prob:LagDual}).
-The cut \(\theta^\omega \geq \sum_{i \in I} \pi_i^* (t_i - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^* (x_{ij} - \hat{x}_{ij}) + v^*\) is a valid and tight cut if whether \(t_i \geq H^\omega\) is known for all \(i \in I\).
-According to Definition 2 in \cite{zou2016nested}, the cut is
-		\begin{itemize}
-			\item valid, if \(f^\omega(x,t) \geq \sum_{i \in I} \pi_i^* (t_i - \hat{t}_i) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^* (x_{ij} - \hat{x}_{ij}) + v^*,\ \forall t_i \geq 0, x_{ij} \in \{0,1\}\);
-			\item tight, if \(f^\omega(\hat{x},\hat{t}) = v^*\).
-		\end{itemize} 
-	\end{theorem}
-	\begin{proof}
-		\textcolor{blue}{To be added.}
-	\end{proof}
-	\noi The temporal relationship could be determined by a branch-and-bound scheme.
-Although theoretically for each scenario there are exponential number of possible temporal relationships because each activity can either be before the disruption time or after that, there are only a small number of activities, of which the optimal starting time of the deterministic problem (\ref{prob:static}) is close to the disruption time, that really matter.
-If an activity should be starting much earlier than the disruption time in the deterministic problem, it usually will significantly increase the length of the project span by delaying the start of such activity.
-If an activity cannot start until a time much later than the disruption time, it is usually not possible to make it start before the disruption time without committing crashing resources heavily on its precedent activities, which may likely lead to an inferior solution.
-
-\section{Computational Results} \label{sec:results}
-
+	Problem~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage. 
+\section{Experiment Results} \label{sec:results}
+	\subsection{Deterministic Counterparts}
+		List the test results of INFORMS presentation. State the fact that the fully stochastic makes great improvement over its deterministic counterparts.
+\section{Stochastic Mixed Integer Program Extension}
 \section{Conclusions} \label{sec:conclusions}
-	\begin{itemize}
-		\item Contributions
-		\item Further directions
-	\end{itemize}
 

### 2018-01-04 src/exploration_strata.jl

@@ -211,3 +211,22 @@ end
 addlazycallback(mp,innerCut);
 addcutcallback(mp,MIPNodeSol);
 mpStatus = solve(mp);
+
+########################################################################
+# compare the stratified sampling results and the MC results
+# sample 50 each, stratified with 10 H * 5 d
+
+vList1 = [];
+vList2 = [];
+for i in 1:1000
+    disData,Ω = autoUGenStrata("LogNormal",[log(35),0.5],nameD,dparams,10,5);
+    ωSeq,ωDict,Hω,Ωt = getOmegaSeq(disData);
+    text,xext,fext,mext = extForm_cheat(pData,disData,Ω);
+    push!(vList1,fext);
+
+    disData,Ω = autoUGenStrata("LogNormal",[log(35),0.5],nameD,dparams,50,1);
+    ωSeq,ωDict,Hω,Ωt = getOmegaSeq(disData);
+    text,xext,fext,mext = extForm_cheat(pData,disData,Ω);
+    push!(vList2,fext);
+    println("------------------ Iteration $(i) Finished ------------------");
+end

### 2018-01-04 src/readIn.jl

@@ -229,3 +229,73 @@ function autoUGenStrata(nameH, Hparams, nameD, dparams, Ωt, Ωd)
     end
     return disData,Ω;
 end
+
+# automatically uncertainty data generation: stratified
+function autoUGenStrata2(nameH, Hparams, nameD, dparams, Ωt, Ωd)
+    disData = Dict();
+
+    if nameH == "Exponential"
+        μ = Hparams[1];
+        distrH = Exponential(μ);
+    elseif nameH == "LogNormal"
+        μ = Hparams[1];
+        σ = Hparams[2];
+        distrH = LogNormal(μ,σ);
+    elseif nameH == "Gamma"
+        α = Hparams[1];
+        θ = Hparams[2];
+        distrH = Gamma(α,θ);
+    elseif nameH == "Uniform"
+        la = Hparams[1];
+        ub = Hparams[2];
+        distrH = Uniform(la,ub+1e-10);
+    elseif nameH == "Normal"
+        μ = Hparams[1];
+        σ = Hparams[2];
+        distrH = Normal(μ,σ);
+    end
+
+    distrD = Dict();
+    for i in keys(dparams)
+        if nameD == "Exponential"
+            μ = dparams[i][1];
+            distrD[i] = Exponential(μ);
+        elseif nameD == "LogNormal"
+            μ = dparams[i][1];
+            σ = dparams[i][2];
+            distrD[i] = LogNormal(μ,σ);
+        elseif nameD == "Gamma"
+            α = dparams[i][1];
+            θ = dparams[i][2];
+            distrD[i] = Gamma(α,θ);
+        elseif nameD == "Uniform"
+            la = dparams[i][1];
+            ub = dparams[i][2];
+            distrD[i] = Uniform(la,ub+1e-10);
+        elseif nameD == "Normal"
+            μ = dparams[i][1];
+            σ = dparams[i][2];
+            distrD[i] = Normal(μ,σ);
+        end
+    end
+
+    ω = 0;
+    Ω = 1:(Ωt*Ωd);
+    dDict = Dict();
+    for ωd in 1:Ωd
+        d = Dict();
+        for i in keys(dparams)
+            d[i] = round(rand(distrD[i]),4);
+        end
+        dDict[ωd] = d;
+    end
+    for ωt in 1:Ωt
+        H = round(rand(distrH),4);
+        for ωd in 1:Ωd
+            ω += 1;
+            pω = 1/(Ωt*Ωd);
[…]

### 2018-01-11 src/extForm_1l.jl
Added a small test example for cut structure and the stratification

@@ -4,7 +4,8 @@
 function extForm(pData,disData,Ω)
     M = Dict();
     for ω in Ω
-        M[ω] = sum(max(pData.D[i],pData.D[i]+disData[ω].d[i]) for i in pData.II if i != 0);
+        #M[ω] = sum(max(pData.D[i],pData.D[i]+disData[ω].d[i]) for i in pData.II if i != 0);
+        M[ω] = 300;
     end
 
     mp = Model(solver = GurobiSolver(Method = 0, OutputFlag = 0, IntFeasTol = 1e-9));
@@ -18,13 +19,13 @@ function extForm(pData,disData,Ω)
     @variable(mp,0 <= s[i in pData.II, j in pData.Ji[i], ω in Ω] <= 1);
 
     @constraint(mp, FConstr[i in pData.II, ω in Ω], disData[ω].H - F[i,ω]*M[ω] <= t0[i]);
-    @constraint(mp, GConstr[i in pData.II, ω in Ω], disData[ω].H - 1e-5 + G[i,ω]*M[ω] >= t0[i]);
+    @constraint(mp, GConstr[i in pData.II, ω in Ω], disData[ω].H - 1e-6 + G[i,ω]*M[ω] >= t0[i]);
     @constraint(mp, FGConstr[i in pData.II, ω in Ω], F[i,ω] + G[i,ω] == 1);
-    @constraint(mp, tConstr1[i in pData.II, ω in Ω], t[i,ω] + (1 - F[i,ω])*M[ω] >= t0[i]);
-    @constraint(mp, tConstr2[i in pData.II, ω in Ω], t[i,ω] - (1 - F[i,ω])*M[ω] <= t0[i]);
+    @constraint(mp, tConstr1[i in pData.II, ω in Ω], t[i,ω] + G[i,ω]*M[ω] >= t0[i]);
+    @constraint(mp, tConstr2[i in pData.II, ω in Ω], t[i,ω] - G[i,ω]*M[ω] <= t0[i]);
     @constraint(mp, tConstr3[i in pData.II, ω in Ω], t[i,ω] >= disData[ω].H * G[i,ω]);
-    @constraint(mp, xConstr1[i in pData.II, j in pData.Ji[i], ω in Ω], x[i,j,ω] + (1 - F[i,ω]) >= x0[i,j]);
[…]

### 2018-01-11 src/small_test.jl

@@ -1,0 +1,22 @@
+# serial example to test out the cut structure
+@everywhere using JuMP,Gurobi,CPLEX,Cbc,Clp;
+
+@everywhere include("def.jl");
+@everywhere include("readIn.jl");
+@everywhere include("main_1l.jl");
+@everywhere include("main_pull.jl");
+@everywhere include("cutGen_1l.jl");
+@everywhere include("tightenGen_1l.jl");
+@everywhere include("branchFunc.jl");
+@everywhere include("detFunc_1l.jl");
+@everywhere include("extForm_1l.jl");
+@everywhere include("main_pull.jl");
+
+pInputAdd = "test_Serial_P.csv";
+kInputAdd = "test_Serial_K.csv";
+ΩInputAdd = "test_Serial_Omega.csv";
+
+pData = readInP(pInputAdd,kInputAdd);
+disData,Ω = readInDis(ΩInputAdd);
+
+text,xext,fext,mext = extForm_cheat(pData,disData,Ω);

### 2018-04-16 Writeup/PERT_New.tex
Added a small test example for cut structure and the stratification
Update the tests

@@
 
-Optimizing Crashing Decisions in Project Management Problem with Disruptions \ms
+Optimal Crashing of a PERT Network with Disruptions \ms
 
@@
 \section{Introduction} \label{sec:introduction}
-	Project management has been a topic studied by many operations researchers using ``engineering science and optimization theory" \cite{soderlund2004building}.
-In order to derive an abstract model, a project could be viewed as a collection of activities, each of which will consume some time and resources.
-There will be precedence relationships between activities due to logical or technological considerations.
-The objective is to find the smallest amount of time needed to finish all activities.
-The project could be represented as an activity network where the length of each link shows the duration of an activity, and the direction of it shows the precedence relationship.
+	The management of complex projects through optimization has a rich history in operations research, beginning with the program evaluation and review technique (PERT) \cite{malcolm1959application} and the critical path method (CPM) of \cite{kelley1961criticalpath}; see S{\"o}derlund \cite{soderlund2004building} for an overview and see \cite{Elmaghraby77}.
+To formulate a mathematical model, a project is viewed as a collection of activities, each of which has some duration and may consume some resources.
+There are precedence relationships between activities due to logical or technological considerations.
+The objective is to complete all activities in minimum time.
+We represent such a project using an acyclic activity network, where the length of each link shows the duration of an activity, and an edge's predecessors capture the precedence relationships.
 An activity cannot start until all its predecessors are completed.
-Two dummy nodes \((S,T)\) are created in the network to represent the start and the end of the project.
-In the network setting with no uncertainty, finding the shortest project span is equivalent to finding the longest path from \(S\) to \(T\).
-Since the activity network is usually acyclic, it is easy to use shortest path algorithms to find a longest path in polynomial time.
-Multiple projects can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
+Multiple activities can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
 More details about the activity network are discussed in \cite{Elmaghraby77}.\\
 	\newline 
-	In the planning stage of a project, decisions can be made to crash a certain set of activities in order to achieve the shortest project span.
-Here crashing an activity means accelerating its progress or compress its duration.
-In this paper, a discrete set of crashing options will be given to the decision makers, each with a fractional number which equals to the crashed duration divided by the original duration.
-One project can only be crashed once with one specific option.
-Each option will incur a certain cost as well and the total cost of crashing could not exceed the budget.
-Static crashing optimization problem is first researched in \cite{fulkerson1961network, kelley1961criticalpath}.
-If we assume a finite set of crashing options, the problem could be modeled as a mixed integer program.
+	In the planning stage of a project, decisions are made to crash a certain set of activities in order to minimize the project's timespan.
+Here crashing an activity means shortening its duration.
+In this paper, a discrete set of crashing options are available, each with fraction specifying the resulting reduction in the activity's duration.
+An activity can be crashed at most once and with a single option.
+Each option incurs a certain cost, and the total cost of crashing cannot exceed the budget.
+Optimization of such static crashing problems is introduced in \cite{fulkerson1961network, kelley1961criticalpath}.
+Under a finite set of crashing options, the problem can be modeled as a mixed integer program.
 The static model can be extended to incorporate uncertainty of activity durations.
-Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is not really possible to provide an analytical expression of the true expected project span \cite{burt1971conditional,van1963letter}.
+Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is is difficult to express analytically the expected project span \cite{burt1971conditional,van1963letter}.
 Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant,bowman1994stochastic,ke2014genetic,kim2007heuristic}.
-Another approach to handle the uncertainty is the robust optimization method.
-In the robust optimization setting, the objective is to minimize the worst case project span within the uncertainty set.
-It can be proved that an affinely adaptive recourse decision, although computationally tractable as it can be reformulated as a linear program or a second order conic program (SOCP), may lead to suboptimal solutions \cite{chen2008linear,cohen2007stochastic}.
-However, once the recourse decision rule is extended to a general form, it is only tractable to solve the robust optimization problem with hypercube uncertainty sets, which is a trivial case because the worst-case scenario in the uncertainty set is always the point where every activity takes the upper bound.
-\cite{wiesemann2012robust}.
-In recent years, distributionally robust optimization has been developed quickly in literature \cite{delage2010distributionally}.
+Another approach to handle the uncertainty is robust optimization, in which the objective is to minimize the worst case project span within a specified uncertainty set.
+While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \cite{chen2008linear,cohen2007stochastic}.
+However, once recourse decisions can take general form, the robust model is only tractable with hypercube uncertainty sets, which is a trivial case because the worst-case scenario in the uncertainty set is always the point where every activity takes its upper bound \cite{wiesemann2012robust}.
 Ahipasaoglu et al.
-\cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.\\
+\cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.\\
 	\newline
-	The uncertainty in our paper lies in the timing and the magnitude of the stochastic disruption, which is modeled in a different way from the random variable distribution in the stochastic programming setting, or from the uncertainty set in the robust optimization setting.
+	The uncertainty in our paper lies in the timing and the magnitude of the stochastic disruption, which is modeled differently from randomness in a two-stage stochastic program or from the uncertainty set in robust optimization.
 A stochastic disruption is an event that may occur any time in the time horizon and change the system parameters significantly.
-There have been a few papers in applying this idea when the disruption could only occur in a set of specified time periods.
-Yu and Qi \cite{yu2004disruptionmgt} introduced scenario-based optimization models and applied it to solve airline scheduling problems.
+A few authors apply this idea when the disruption can only occur in a set of specified time periods.
+Yu and Qi \cite{yu2004disruptionmgt} introduce scenario-based optimization models for airline scheduling.
 Morton et al.
-\cite{morton2009sealift} introduced the modeling of a sealift scheduling problem under finite number of stochastic disruptions within a stochastic programming structure.
+\cite{morton2009sealift} introduce a sealift scheduling problem under a finite number of stochastic disruptions within a stochastic programming structure.
 This structure ``falls between standard two-stage and multi-stage stochastic programs for a multi-period problem" and reduces the size of the problem to a quadratic growth in the number of time periods.
-Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing continuous disruption time instead of fixed time periods.\\
+Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing a continuous disruption time instead of a prespecified set of fixed time periods.
+\\
 	\newline
 	We first formally describe the crashing optimization problem under stochastic disruptions.
-Given the limited number of disruption occurrence, the problem can be formulated as a stochastic mixed integer program and we will present the extensive formulation in Section~\ref{sec:formulation}.
-If we assume continuous distributions for the disruption time and magnitude, sample average approximation (SAA) can be used to create a finite set of scenarios and approximate the original problem by a finite-sized optimization problem.
+Given a limited number of disruption scenarios, the problem can be formulated as a stochastic mixed integer program and we present the extensive formulation in Section~\ref{sec:formulation}.
+If we assume a continuous distribution for the disruption time and magnitude, a sample average approximation (SAA) can be used to create a finite set of scenarios and approximate the original problem by a finite-sized optimization problem.
+We present some important properties of this problem using a serial activity network as a special case in Section~\ref{sec:examples}.
+	\begin{comment}
 	We prove some important consistency and convergence properties of the SAA problem using independent and identically distributed samples and stratified samples in Section~\ref{sec:consistency}.\\
@@
 In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
-We show such a decomposition method will solve the integer program to the exactness within finite number of iterations.\\
+We show such a decomposition method solves the integer program to the exactness within finite number of iterations.\\
 	\newline
 	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the solution obtained by solving a  crashing optimization problem with a deterministic disruption, and the computational performance of the decomposition method in Section~\ref{sec:decomposition}, compared to that of solving the extensive formulation.
-We will conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
+We conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
+	\end{comment}
 
 \section{Problem Formulation} \label{sec:formulation}
-	The deterministic project crashing optimization problem is widely researched since 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
+	The deterministic project crashing optimization problem has been known since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
 Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\).
-The budget limit \(B\) and the nominal length of each activity \(D_i\) are given.
-For each activity \(i \in I\), there is a finite set of crashing options \(j \in J_i\) and each of them will incur a cost of \(b_{ij}\) while cutting down the nominal activity length to \(1 - e_{ij}\) of the nominal length.
-We assume each activity could be crashed at most once and the problem could be formulated as follows.
+The arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\).
+We create a dummy activity \(N\) to represent the end of entire project, which should succeed every activity \(i \in I\).
+\\
+	\newline
+	For each activity \(i \in I\), the nominal length \(D_i\) is given.
+We can apply a finite set of crashing options, \(j \in J_i\), and one unit application of each option incurs a cost of \(b_{ij}\), while it decreases the length of activity \(i\) by \(D_ie_{ij}\).
+The total cost of crashing options cannot exceed a given budget, \(B\).
+We assume each activity can be crashed at most with one unit and the problem can be formulated as follows:
 	\begin{subequations} \label{prob2:static}
@@
 		\min \quad & t_N &\\
-		\text{s.t.} \quad & t_N \geq t_i & \forall \,i \in I \\
-		& t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) & \forall \,i \in I, (i,k) \in \mathcal{A}\\
-		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B & \\
-		& \sum_{j \in J_i} x_{ij} \leq 1 & \forall \,i \in I\\
-		& t_i \geq 0 & \forall \,i \in I\\
-		& 0 \leq x_{ij} \leq 1 & \forall \,i \in I, j \in J_i&
+		\text{s.t.} \quad &  t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:dSep}\\
+		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
+		& t_i \geq 0  \qquad \qquad \forall \,i \in I\\
+		& 0 \leq x_{ij} \leq 1  \qquad \qquad \forall \,i \in I, j \in J_i.
 		\end{align}
 	\end{subequations}
-	Based on this formulation, we can derive the stochastic optimization and the robust optimization models with reference to the literature listed in Section~\ref{sec:introduction}.
-We omit these formulations in this paper since our uncertainty model is different from previous settings.\\
+	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\).
+We aim to minimize the project span, which is the starting time of the dummy activity, \(t_N\).
+Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
+Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
+\\
 	\newline
-	We assume at most one stochastic disruption will occur in the project span.
-The disruption will not affect the activities that have already started but will change the length of activities starting after it according to some given finite discrete distributions.
-The decision of crashing has to be made the same time when the activity starts and cannot be changed after that.
+	In our problem, we assume at most one stochastic disruption can occur in the project span, while the time of such disruption is a random variable.
+We also assume for each activity \(i \in I\), the crashing decision decision for that activity needs to be made prior to the start of that activity, and cannot be changed after that.
+We assume that the disruption does not affect the activities that have already started but changes the length of activities starting after it according to some given distributions.
+We assume there is a discrete finite set of scenarios indexed by \(\Omega\).
+It is usually hard to compute the recourse function directly when some of its parameters are distributed according to continuous distributions, and SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}.
+\\
+	\newline
 	Since there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
 Notice that the definition of the first stage is different from the traditional stochastic program setting.
-Here the first stage contains all the decisions if no disruption occurs and the second stage will characterize the decisions for each realization of the disruption.
-This means that the first stage decision variables are not limited to a certain time period but can be all over the entire time horizon, which allows us to model continuous disruption time.\\
+Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterize the decisions for each realization of the disruption.
+This means that the first stage decision variables are carried out until the disruption, if it ever occurs, and after the disruption, depending on the scenario realized, the scenario-specific recourse decisions are executed.\\
 	\newline
@@
 		\(I\) & \(\qquad\) & the set of activities;&\\
-		\(I_i\) & \(\qquad\) & the set of activities which directly lead to activity \(i\); &\\
 		\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i\), \(i \in I\);&\\
-		\(\Omega\) & \(\qquad\) & the set of possible realizations of disruption;&\\
+		\(\Omega\) & \(\qquad\) & the index set of possible realizations of disruption;&\\
 		\(\mathcal{A}\) &\(\qquad\) & set of arcs which represents the precedence relationship;&\\
@@
 		\(t_{i}\) & \(\qquad\) & nominal starting time of activity \(i\), \(i \in I\);&\\
-		\(x_{ij}\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) in the nominal plan, \(i \in I, j \in J_i\); &\\
+		\(x_{ij}\) & \(\qquad\) & fraction activity \(i\) is crashed by option \(j\) in the nominal plan, \(i \in I, j \in J_i\); &\\
 		\(t_{i}^\omega\) & \(\qquad\) & starting time of activity \(i\) under scenario \(\omega\), \(i \in I, \omega \in \Omega\);&\\
-		\(x_{ij}^\omega\) & \(\qquad\) & indicator whether activity \(i\) is crashed by option \(j\) under scenario \(\omega\), \(i \in I, j \in J_i, \omega \in \Omega \); &\\
+		\(x_{ij}^\omega\) & \(\qquad\) & fraction activity \(i\) is crashed by option \(j\) under scenario \(\omega\), \(i \in I, j \in J_i, \omega \in \Omega \); &\\
 		\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
@@
 	\end{longtable}
-	\noi The extensive formulation of the two-stage stochastic program is shown as Formulation~(\ref{prob2:extensive}).
-Here \(M\) is a large number to enforce the logic relationships.
-In this problem, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
-Variables \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint (\ref{cons:F}) - (\ref{cons:G})).
-This is important in our problem setting because the duration of each activity will depend on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
-For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\).
-This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints (\ref{cons:linearize1}) - (\ref{cons:linearize3}).\\
-	\newline
-	We have to use a set of non-anticipativity constraints (\ref{cons:tf1}) - (\ref{cons:xf2}), different from the one used in a traditional stochastic programming setting, since the first stage decision variables here spans the entire time horizon.
-These logic constraints ensure the decisions made before the disruption time in each scenario should be the same as the nominal decisions before the same time point, because decisions made with the same amount information should be the same.\\
+	\noi The extensive formulation of the two-stage stochastic program is shown as formulation~(\ref{prob2:extensive}):
 	\begin{subequations} \label{prob2:extensive}
 		\begin{align}
-		\min \quad & \sum_{\omega \in \Omega} p^\omega t_N^\omega + p^0 t_N& \\
-		\text{s.t.} \quad & t_N^\omega \geq t_i^\omega & \forall \,i \in I, \omega \in \Omega \\
-		& t_N \geq t_i & \label{cons:tN}\\
-		& t_i^\omega \geq 0 & \forall \,i \in I, \omega \in \Omega\\
-		& t_i \geq 0 & \forall \,i \in I\\
-		& H^\omega - (1 - G_i^\omega) M \leq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:F}\\
-		& H^\omega + G_i^\omega M \geq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:G}\\
-		& t_i^\omega + G_i^\omega M \geq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:tf1}\\
-		& t_i^\omega - G_i^\omega M \leq t_i & \forall \,i \in I, \omega \in \Omega \label{cons:tf2}\\
-		& x_{ij}^\omega + G_i^\omega \geq x_{ij} & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
-		& x_{ij}^\omega - G_i^\omega \leq x_{ij} & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
-		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
-		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 & \forall \,i \in I, \omega \in \Omega \label{cons:crashLim}\\
-		& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B & \forall \,\omega \in \Omega \label{cons:budget}\\
-		& S_{ij}^\omega \leq G_i^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
-		& S_{ij}^\omega \leq x_{ij}^\omega & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
-		& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 & \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
-		& t_i \geq 0 & \forall\,i \in I \\
-		& t_i^\omega \geq H^\omega G_i^\omega & \forall\, i \in I, \omega \in \Omega \\
-		& 0 \leq x_{ij} \leq 1 & \forall \,i \in I, j \in J_i\\ 
-		& 0 \leq x_{ij}^\omega \leq 1 & \forall \,i \in I, j \in J_i, \omega \in \Omega\\
-		& G_i^\omega \in \{0,1\}. & \forall \,i \in I, \omega \in \Omega
+		\min \quad & \sum_{\omega \in \Omega} p^\omega t_N^\omega + p^0 t_N \\
+		\text{s.t.} \quad & t_N^\omega \geq t_i^\omega \qquad \qquad \forall \,i \in I, \omega \in \Omega \\
+		& t_N \geq t_i \qquad \qquad \label{cons:tN}\\
+		& t_i^\omega \geq 0 \qquad \qquad \forall \,i \in I, \omega \in \Omega\\
+		& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
+		& H^\omega - (1 - G_i^\omega) M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:F}\\
+		& H^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G}\\
+		& t_i^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tf1}\\
+		& t_i^\omega - G_i^\omega M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tf2}\\
+		& x_{ij}^\omega + G_i^\omega \geq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
+		& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
+		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
+		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:crashLim}\\
+		& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:budget}\\
+		& S_{ij}^\omega \leq G_i^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
+		& S_{ij}^\omega \leq x_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
+		& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
+		& t_i^\omega \geq H^\omega G_i^\omega \qquad \qquad \forall\, i \in I, \omega \in \Omega \\
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\ 
+		& 0 \leq x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
+		& 0 \leq S_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
+		& G_i^\omega \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega.
 		\end{align}
 	\end{subequations}
+	In model~\eqref{prob2:extensive}, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
+Variables \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint \eqref{cons:F}-\eqref{cons:G}) and \(M\) is a large number to enforce the logic relationships.
+This is important in our problem setting because the duration of each activity depends on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
+For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\).
+This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which is linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.\\
+	\newline
+	We use a set of non-anticipativity constraints \eqref{cons:tf1}-\eqref{cons:xf2}, different from ones used in a traditional stochastic programming because the first stage decision variables here spans the entire time horizon.
+These logic constraints ensure that the decisions made before the disruption time in each scenario are the same as the nominal decisions before the same time point.
 
 \section{Special Cases} \label{sec:examples}
-	In this section we show a few examples to illustrate the properties of the project crashing problem under stochastic disruption displayed in Section~\ref{sec:formulation}.
-We will focus on simple network structures such as serial and parallel networks.
-We also display some general networks where those properties are (or not) applicable.
-	\subsection{Serial Networks}
-		\begin{itemize}
-			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
-			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
-			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
-			\item Only optimal to delay to a possible disruption time.
-		\end{itemize}
-		The first example we present for a serial network is to show that it might be optimal to delay the start of some activities. The reasons of such delay include:
-		\begin{enumerate}
-			\item Some activities might have a shorter length after disruption. It is beneficial to wait a short period of time to capture this advantage.
-			\item Even if all possible disruption magnitudes are adverse, which means they will lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
-		\end{enumerate}
+	In this section we show a serial example to illustrate the nature of the project crashing problem under stochastic disruption.
+From this serial network example we show that it might be optimal to delay the start of some activities, and thus justify the formulation in model~\eqref{prob2:extensive}.
+\\
+	\newline
 	Suppose we have a project with three activities in a serial network form.
-The activity 1 should be finished before the start of activity 2 and the activity 2 should be finished before the start of activity 3.
+Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3.
 The structure of the project is displayed as follows.
-We add two dummy activity ``S" and ``T" to represent the start and the end of the project.
+We add a dummy activity ``N" to represent the end of the project.
 The total crashing budget is \(1\) and the allowed amount of crashing a single activity is between \(0\) and \(1\).
@@
 	\end{figure}
-		\noi We can set up a nominal case with the length of activity 1, 2 and 3 as \(9\), \(10\) and \(7\).
-The probability of the disruption not occurring is 0.5.
-If a disruption occurs, it will occur at the time \(H = 9.1\).
-Suppose the disruption will change the length of activity 2 from \(10\) to \(3\) and not affect activity 3.
+	\noi So, \(I=\{1,2,3,N\}\), and \(D_1=9\), \(D_2=10\), and \(D_3=7\).
+The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\).
+The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario.
+Suppose the disruption changes \(D_2=10\) to \(3\), a.k.a.
+\(d_2^1 = -7\), and not affect activity 3.
 We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\), spend the entire budget to crash activity 3 if the disruption occurs, and spend the entire budget to crash activity 2 if the disruption does not occur.
 The expected total project span is 18.35.
-If we force the condition that the starting time of activities could not be delayed, we could not observe whether the disruption happens or not at the starting time of activity 2.
-There will be only one possible situation where three activities will have the duration as 9,10 and 7.
+If we force the condition that the starting time of activities cannot be delayed, we cannot observe whether the disruption happens or not prior to the start of activity 2.
+There is only one possible situation where three activities have the duration as 9, 10 and 7.
 All resources should be allocated to activity 2 and the total project span is 21, which is larger than the expected total project span if it is allowed to delay the starting time of some activities.
-The reason of such phenomenon is that a disruption may reduce some activities' durations.
-Delaying by a small amount will enable us to collect that reduction in time.\\
+In this example, a disruption may reduce the duration of some activities and delaying by a small amount allows us to realize that reduction in time.\\
 	\newline
-		Even if the disruption can only bring negative effect on the duration of activities, a.k.a.
-lengthening all activities after that, it is still beneficial to delay the start of some activities under some circumstances.
-This means a small delay of some activity may gain the information of disruption which is more valuable and potentially decreases the total project span.
-Such claim can be verified by the serial network described in the last paragraph, only changing some duration parameters in the following way.
-Suppose the nominal duration, the timing of possible disruption and the probability of a disruption occurring remain the same.
-If the disruption occurs, it will change the duration of activity 2 to 9.1 and that of activity 3 to 13.
-For this example, if no delay is allowed, the optimal decision is to allocate the entire budget to activity 2 and the expected total project span is 24.
-If we delay the starting time of the activity 2 to 9.1 so that the disruption can be observed before we commit resources to activity 2, the expected total project span is 23.4.
+	Even if the disruption can only lengthen an activity's duration, it is still beneficial to delay the start of some activities under some circumstances.
+This means a small delay of some activity may gain the information regarding the disruption, which can decrease the project span.
+To see this, we again consider the serial network of Figure~\ref{fig:serial3}.
+We assume the nominal durations, and the stochastic disruption, are identical to those above.
+If the disruption occurs, the durations of activities change by \(d_2^1=0.1\) and \(d_3^1 = 6\).
+For this example, if no delay is allowed, the optimal decision is to have \(x_2 = 1\) and the optimal objective value is 24.
+If we delay the starting time of the activity 2 to \(t_2 = 9.1\) so that the disruption can be observed before we commit resources to activity 2, the optimal expected total project span is 23.4.
+\\
+	\newline
+	Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the starting time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
+We summarize the reasons of such delay include:
+		\begin{enumerate}
+			\item Some activities might have a shorter length after disruption. It is beneficial to wait a short period of time to capture this advantage.
+			\item Even if all possible disruption magnitudes are adverse, which means they lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
+		\end{enumerate}
+	\begin{comment}
+	\textcolor{blue}{ The materials above are the most important idea I want to convey in this section.
+Here are some additional results we have discussed but I haven't compiled to \LaTeX \ yet.
+Time allowing, I can add some stuff in maybe tonight or this coming week.
+		\begin{itemize}
+			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
+			\item The analytical form of the recourse function when all \(d\) are \([0,1]\)-uniformly distributed, all \(D\) are equal, and the crashing option can only be integer.
+			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
+			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
+			\item Only optimal to delay to a possible disruption time.
+		\end{itemize}
+	}
 	\subsection{Parallel Networks}
 		\begin{itemize}
-			\item Not optimal to delay when \(d_i \geq 0\).
+			\item Not optimal to delay when \(d_i \geq 0\) if each branch only contains a single activity.
+			\item If each branch is a serial path, it is possibly beneficial to delay the start of some activities.
 		\end{itemize}
@@
 	Problem~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage.
+
 \section{Experiment Results} \label{sec:results}
@@
 		List the test results of INFORMS presentation. State the fact that the fully stochastic makes great improvement over its deterministic counterparts.
-\section{Stochastic Mixed Integer Program Extension}
+
+%\section{Stochastic Mixed Integer Program Extension}
 \section{Conclusions} \label{sec:conclusions}
+\end{comment}
 

### 2018-04-16 src/cutGen_1l.jl

@@ -77,9 +77,14 @@ function bGenbuild(pData,dDω,xhat,that,brInfo)
     return cutGen;
 end
 
-function bGenbuild_New(pData,dDω,xhat,that,brInfoω)
+function bGenbuild_New(pData,dDω,xhat,that,brInfoω,M = Dict())
     # imbed the logic in the program
-    M = iSolve_NC(pData,dDω,0);
+    if M == Dict()
+        MM = iSolve_NC(pData,dDω,0,brInfoω);
+        for i in pData.II
+            M[i] = MM;
+        end
+    end
 
     # sp = Model(solver = GurobiSolver(OutputFlag = 0));
     sp = Model(solver = GurobiSolver(OutputFlag = 0));
@@ -91,8 +96,8 @@ function bGenbuild_New(pData,dDω,xhat,that,brInfoω)
     @variable(sp, 0 <= s[i in pData.II,j in pData.Ji[i]; brInfoω[findin(pData.II,i)[1]] == 0] <= 1);
 
     # add the basic sub problem constraints
-    @constraint(sp, FCons[i in pData.II; brInfoω[findin(pData.II,i)[1]] == 0],dDω.H - F[i]*M <= that[i]);
-    @constraint(sp, GCons[i in pData.II; brInfoω[findin(pData.II,i)[1]] == 0],dDω.H + G[i]*M >= that[i]);
+    @constraint(sp, FCons[i in pData.II; brInfoω[findin(pData.II,i)[1]] == 0],dDω.H - F[i]*M[i] <= that[i]);
+    @constraint(sp, GCons[i in pData.II; brInfoω[findin(pData.II,i)[1]] == 0],dDω.H + G[i]*M[i] >= that[i]);
     @constraint(sp, FGCons[i in pData.II; brInfoω[findin(pData.II,i)[1]] == 0],F[i] + G[i] == 1);
 
     # add the predecessors and the successors logic constraints
@@ -101,10 +106,10 @@ function bGenbuild_New(pData,dDω,xhat,that,brInfoω)
 
     # add the basic sub problem constraints for the undecided activities
     @constraint(sp, tGbound1[i in pData.II; brInfoω[findin(pData.II,i)[1]] == 0],t[i] >= dDω.H*G[i]);
[…]

### 2018-04-16 src/main_1l.jl

@@ -6,7 +6,7 @@ function cutProc_Benders(pData,disData,Ω,ϵ = 1e-4)
     mp = createMaster(pData,disData,Ω);
     brInfo = precludeRel(pData,disData,Ω);
     nIni = nodeType(0,mp,brInfo);
-    ubCost = Inf;
+    ubCost = 9999999;
     noI = 0;
     noC = 0;
     xbest = Dict();
@@ -27,94 +27,121 @@ function cutProc_Benders(pData,disData,Ω,ϵ = 1e-4)
         # generate Benders cuts until it converges
         mpc = copy(nCurrent.mp);
         mpc = branchAdd(pData,disData,Ω,mpc,nCurrent.brInfo);
-        mpcstatus = solve(mpc);
-        if mpcstatus == :Optimal
-            # if the current lower bound is larger than the upper bound, then prune the node
-            if !(getobjectivevalue(mpc) >= ubCost - ϵ)
-                xhat = getvalue(mpc[:x]);
-                that = getvalue(mpc[:t]);
-                # update the upper bound
-                ubTemp = ubCal(pData,disData,Ω,xhat,that);
-                if ubTemp < ubCost
-                    ubCost = ubTemp;
-                    for i in pData.II
-                        tbest[i] = that[i];
-                        for j in pData.Ji[i]
-                            xbest[i,j] = xhat[i,j];
-                        end
-                    end
-                end
 
-                # update the lower bound
-                if nCurrent.lbCost < getobjectivevalue(mpc)
-                    lbPrev = nCurrent.lbCost;
-                    nCurrent.lbCost = getobjectivevalue(mpc);
-                else
-                    lbPrev = 0;
-                end
+        # calculate the upper bound and the lower bound of each activity's starting time
+        Mlb,Mub = boundCal(pData,disData,Ω,mpc,nCurrent.lbCost,ubCost);
+        # update the brInfo based on the calculated upper bound and the lower bound
+        nCurrent.brInfo = update_brInfo(pData,disData,Ω,Mlb,Mub,nCurrent.brInfo,ωSeq);
+        if nCurrent.brInfo != []
+            mpc = copy(nCurrent.mp);
+            mpc = branchAdd(pData,disData,Ω,mpc,nCurrent.brInfo);
 
-                # stop when not improving
-                contBool = true;
-                while lbPrev < nCurrent.lbCost
-                    # plug in the xhat and that to generate a Benders cut
-                    for ω in Ω
[…]

### 2018-04-16 src/readIn.jl

@@ -1,5 +1,3 @@
-using Distributions,HDF5,JLD;
-
 # This is the input function that reads in the project data
 function readInP(pInputAdd,kInputAdd)
     pRaw = readdlm(pInputAdd,',',header = false);

### 2018-04-16 src/test1_0.jl

@@ -1,5 +1,6 @@
 # This is the script to load the data and solve the problem
 @everywhere using JuMP,Gurobi,CPLEX,Cbc,Clp;
+@everywhere using Distributions,HDF5,JLD;
 
 @everywhere include("def.jl");
 @everywhere include("readIn.jl");

### 2018-04-16 src/test2_0.jl

@@ -1,5 +1,6 @@
 # test the variance of the recourse function with the deterministic solution
 @everywhere using JuMP,Gurobi,CPLEX,Cbc,Clp,HDF5,JLD;
+@everywhere using Distributions,HDF5,JLD;
 
 @everywhere include("def.jl");
 @everywhere include("readIn.jl");

### 2018-06-13 Writeup/PERT_New.tex
Upload all codes for grouping/mixed cuts

@@
 		\end{enumerate}
+
+	\section{Decomposition Method} \label{sec:decomposition}
+	Model~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage.
+It is a type of hard problem that efficient decomposition methods have only been found when additional properties about variables exist \textcolor{blue}{cite past literatures with second stage integers.}
 	\begin{comment}
@@
 	\subsection{IID vs. Stratified Sampling}
-\section{Decomposition Method} \label{sec:decomposition}
-	Problem~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage.
 

### 2018-06-13 src/extForm.jl

@@ -40,8 +40,9 @@ function extForm(pData,disData,Ω)
     solve(mp);
     text = getvalue(mp[:t0]);
     xext = getvalue(mp[:x0]);
+    gext = getvalue(mp[:G]);
     fext = getobjectivevalue(mp);
-    return text,xext,fext,mp;
+    return text,xext,fext,gext,mp;
 end
 
 function extForm_cheat(pData,disData,Ω)
@@ -82,6 +83,7 @@ function extForm_cheat(pData,disData,Ω)
     solve(mp);
     text = getvalue(mp[:t0]);
     xext = getvalue(mp[:x0]);
+    gext = getvalue(mp[:G]);
     fext = getobjectivevalue(mp);
-    return text,xext,fext,mp;
+    return text,xext,fext,gext,mp;
 end

### 2018-06-13 src/mixedFunction.jl

@@ -1,0 +1,35 @@
+# functions of solving mixed first stage problem
+function solveMasterMixed(pData,disData,ωInfo,cutSet,that,xhat,Ghat = Dict())
+    M = 400;
+    mp = Model(solver = GurobiSolver());
+    @variables(mp, begin
+      θ[Ω] >= 0
+      0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
+      t[i in pData.II] >= 0
+      G[i in pData.II,ω in Ω; (i,ω) in ωInfo], Bin
+    end);
+    @constraint(mp, tFixed[i in pData.II], t[i] == that[i]);
+    @constraint(mp, xFixed[i in pData.II, j in pData.Ji[i]], x[i,j] == xhat[i,j]);
+    if Ghat != Dict()
+        @constraint(mp, GFixed[(i,ω) in ωInfo], G[i,ω] == Ghat[i,ω]);
+    end
+    @constraint(mp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(mp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(mp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+
+    # logic constraints between G and t
+    @constraint(mp, tGcons1[i in pData.II, ω in Ω; (i,ω) in ωInfo], t[i] <= disData[ω].H + G[i,ω]*M);
+    @constraint(mp, tGcons2[i in pData.II, ω in Ω; (i,ω) in ωInfo], t[i] >= disData[ω].H - (1 - G[i,ω])*M);
+
+    for ω in Ω
+        if cutSet[ω] != []
+            for nc in 1:length(cutSet[ω])
+                @constraint(mp, θ[ω] >= cutSet[ω][nc][4] + sum(cutSet[ω][nc][1][i]*(mp[:t][i] - cutSet[ω][nc][5][i]) for i in pData.II) +
+                    sum(sum(cutSet[ω][nc][2][i,j]*(mp[:x][i,j] - cutSet[ω][nc][6][i,j]) for j in pData.Ji[i]) for i in pData.II) +
[…]

### 2018-06-13 src/partition.jl

@@ -1,104 +1,0 @@
-function relaxPart(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 9999999)
-    # formulate the linear relaxation of the master problem and solve it to obtain the dual solution
-    partRev = Dict();
-    partNo = Dict();
-    for i in pData.II
-        partRev[i] = Dict();
-        partNo[i] = length(partCurrentTemp[i]);
-        for partIter in 1:partNo[i]
-            for item in partCurrentTemp[i][partIter]
-                partRev[i][item] = partIter;
-            end
-        end
-    end
-
-    lrm = Model(solver = GurobiSolver(OutputFlag = 0));
-
-    @variable(lrm, t[i in pData.II] >= 0);
-    @variable(lrm, 0 <= x[i in pData.II, j in pData.Ji[i]] <= 1);
-    @variable(lrm, G[i in pData.II, ω in Ω]);
-    @variable(lrm, 0 <= F[i in pData.II, m in 1:partNo[i]] <= 1);
-    @variable(lrm, θ[ω in Ω] >= 0);
-
-    @objective(lrm, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
-
-    @constraint(lrm, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
-    @constraint(lrm, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
-    @constraint(lrm, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
-
-    # logic constraints between G and t
-    @constraint(lrm, tGcons1[i in pData.II, ω in Ω], t[i] <= disData[ω].H + G[i,ω]*M);
-    @constraint(lrm, tGcons2[i in pData.II, ω in Ω], t[i] >= disData[ω].H - (1 - G[i,ω])*M);
-
-    # logic constraints of G
-    @constraint(lrm, GijCon[i in pData.II, j in pData.Succ[i],ω in Ω], G[i,ω] <= G[j,ω]);
[…]

### 2018-06-13 src/partition_LP.jl

@@ -1,0 +1,152 @@
+function relaxPart(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 9999999,FPre = [])
+    # formulate the linear relaxation of the master problem and solve it to obtain the dual solution
+    partRev = Dict();
+    partNo = Dict();
+    for i in pData.II
+        partRev[i] = Dict();
+        partNo[i] = length(partCurrentTemp[i]);
+        for partIter in 1:partNo[i]
+            for item in partCurrentTemp[i][partIter]
+                partRev[i][item] = partIter;
+            end
+        end
+    end
+
+    lrm = Model(solver = GurobiSolver(OutputFlag = 0));
+
+    @variable(lrm, t[i in pData.II] >= 0);
+    @variable(lrm, 0 <= x[i in pData.II, j in pData.Ji[i]] <= 1);
+    @variable(lrm, G[i in pData.II, ω in Ω]);
+    @variable(lrm, 0 <= F[i in pData.II, m in 1:partNo[i]] <= 1);
+    @variable(lrm, θ[ω in Ω] >= 0);
+
+    @objective(lrm, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
+
+    @constraint(lrm, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(lrm, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(lrm, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+
+    # logic constraints between G and t
+    @constraint(lrm, tGcons1[i in pData.II, ω in Ω], t[i] <= disData[ω].H + G[i,ω]*M);
+    @constraint(lrm, tGcons2[i in pData.II, ω in Ω], t[i] >= disData[ω].H - (1 - G[i,ω])*M);
+
+    # logic constraints of G
+    @constraint(lrm, GijCon[i in pData.II, j in pData.Succ[i],ω in Ω], G[i,ω] <= G[j,ω]);
[…]

### 2018-06-13 src/partition_LR.jl

@@ -1,0 +1,419 @@
+function lapConstruct(pData,disData,Ω,cutSet,partCurrentTemp,partDet,μ,M = 999999,FPre = [],intInd = 0)
+    partRev = Dict();
+    partNo = Dict();
+    for i in pData.II
+        partRev[i] = Dict();
+        partNo[i] = length(partCurrentTemp[i]);
+        for partIter in 1:partNo[i]
+            for item in partCurrentTemp[i][partIter]
+                partRev[i][item] = partIter;
+            end
+        end
+    end
+
+    lap = Model(solver = GurobiSolver(OutputFlag = 0));
+
+    @variable(lap, t[i in pData.II] >= 0);
+    @variable(lap, 0 <= x[i in pData.II, j in pData.Ji[i]] <= 1);
+    if intInd == 0
+        @variable(lap, 0 <= G[i in pData.II, ω in Ω] <= 1);
+    else
+        @variable(lap, G[i in pData.II, ω in Ω], Bin);
+    end
+    @variable(lap, F[i in pData.II, m in 1:partNo[i]],Bin);
+    if FPre != []
+        @constraint(lap, Fbind[i in pData.II,τ in 1:length(partCurrentTemp[i])], F[i,τ] == FPre[i,τ]);
+    end
+
+    @variable(lap, θ[ω in Ω] >= 0);
+
+    @objective(lap, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] + sum(μ[i,ω]*(G[i,ω] - F[i,partRev[i][ω]]) for i in pData.II) for ω in Ω));
+
+    @constraint(lap, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(lap, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(lap, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+
+    # logic constraints between G and t
[…]

### 2018-06-13 src/sub.jl

@@ -279,3 +279,66 @@ function subPull(pData,dDω,xhat,that,Ghatω,M = 9999999)
     end
     return πdict,γdict,λdict,vk;
 end
+
+function subMixed(pData,dDω,xhat,that,Ghatω,ωCurr,Ω,M = 9999999,returnOpt = 0)
+    sp = Model(solver = GurobiSolver(OutputFlag = 0,Method = 1));
+    @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
+    @variable(sp, t[i in pData.II] >= 0);
+    @variable(sp, s[i in pData.II, j in pData.Ji[i]] >= 0);
+    @variable(sp, 0 <= G[i in pData.II] <= 1);
+
+    # add the basic sub problem constraints
+    @constraint(sp, tGcons1[i in pData.II],dDω.H + G[i]*M >= that[i]);
+    @constraint(sp, tGcons2[i in pData.II],dDω.H - (1 - G[i])*M <= that[i]);
+    @constraint(sp, tGbound[i in pData.II],t[i] >= dDω.H*G[i]);
+    @constraint(sp, tFnAnt1[i in pData.II],t[i] + G[i]*M >= that[i]);
+    @constraint(sp, tFnAnt2[i in pData.II],t[i] - G[i]*M <= that[i]);
+    @constraint(sp, xFnAnt1[i in pData.II, j in pData.Ji[i]],x[i,j] + G[i] >= xhat[i,j]);
+    @constraint(sp, xFnAnt2[i in pData.II, j in pData.Ji[i]],x[i,j] - G[i] <= xhat[i,j]);
+
+    # linearize the bilinear term of x[i,j]*G[i]
+    @constraint(sp, xGlin1[i in pData.II, j in pData.Ji[i]], s[i,j] <= G[i]);
+    @constraint(sp, xGlin2[i in pData.II, j in pData.Ji[i]], s[i,j] <= x[i,j] + 1 - G[i]);
+    @constraint(sp, xGlin3[i in pData.II, j in pData.Ji[i]], s[i,j] >= x[i,j] - 1 + G[i]);
+
+    @constraint(sp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(sp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
[…]

### 2018-06-13 src/test_mixedProcess.jl

@@ -1,0 +1,155 @@
+# process of mixed first stage
+@everywhere using JuMP,Gurobi,CPLEX;
+@everywhere using Distributions,HDF5,JLD;
+
+@everywhere include("def.jl");
+@everywhere include("readIn.jl");
+@everywhere include("master.jl");
+@everywhere include("sub.jl");
+@everywhere include("cuts.jl");
+@everywhere include("detForm.jl");
+@everywhere include("extForm.jl");
+@everywhere include("ubCalFunc.jl");
+
+pInputAdd = "test_14_P.csv";
+kInputAdd = "test_14_K.csv";
+ΩInputAdd = "test_14_Omega_full.csv";
+ϕInputAdd = "test_14_Phi_full.csv";
+
+pData = readInP(pInputAdd,kInputAdd);
+nameD,dparams = readInUnc(ϕInputAdd);
+data = load("testData_500.jld");
+disData = data["disData"];
+Ω = 1:500;
+text = data["text"];
+xext = data["xext"];
+Gext = data["gext"];
+fext = data["fext"];
+GextDict = Dict();
+for ω in Ω
+    GextDict[ω] = Dict();
+    for i in pData.II
+        GextDict[ω][i] = Gext[i,ω];
+    end
+end
+
+ωInfo = [];
+cutSet = Dict();
+for ω in Ω
+    cutSet[ω] = [];
+end
+ubCost = Inf;
+lbCost = -Inf;
+
+keepIter = true;
+tlb = Dict();
+xlb = Dict();
+Glb = Dict();
+θlb = Dict();
+lbPrev = -Inf;
+ωWrong = [];
+while keepIter
+    mp = createMaster_Mixed(pData,disData,Ω,ωInfo,cutSet,400);
+    solve(mp);
+    # obtain the solution
+    that = Dict();
+    xhat = Dict();
+    Ghat = Dict();
+    θhat = Dict();
+    for i in pData.II
+        that[i] = getvalue(mp[:t][i]);
+        for j in pData.Ji[i]
+            xhat[i,j] = getvalue(mp[:x][i,j]);
+        end
+        for ω in Ω
+            if (i,ω) in ωInfo
+                Ghat[i,ω] = getvalue(mp[:G][i,ω]);
+            end
+        end
+    end
+    for ω in Ω
+        θhat[ω] = getvalue(mp[:θ][ω]);
+    end
+    lbCost = getobjectivevalue(mp);
[…]

### 2018-06-13 src/test_partition.jl

@@ -12,7 +12,10 @@
 @everywhere include("branchFunc.jl");
 @everywhere include("detForm.jl");
 @everywhere include("extForm.jl");
-@everywhere include("main_pull.jl");
+@everywhere include("ubCalFunc.jl");
+@everywhere include("tighten.jl");
+@everywhere include("partition_LP.jl");
+@everywhere include("partition_LR.jl");
 
 pInputAdd = "test_14_P.csv";
 kInputAdd = "test_14_K.csv";
@@ -26,8 +29,8 @@ disData = orderdisData(disData,Ω);
 
 # create the initial partition
 tdet,xdet,fdet = detBuild(pData);
-ub = ubCal(pData,disData,Ω,xdet,tdet);
-brInfo = precludeRel(pData,disData,Ω,ub);
+ubdet = ubCal(pData,disData,Ω,xdet,tdet);
+brInfo = precludeRel(pData,disData,Ω,ubdet);
 partCurrent = Dict();
 partDet = Dict();
 for i in pData.II
@@ -123,11 +126,15 @@ for i in pData.II
         xbest[i,j] = getvalue(mp[:x][i,j]);
     end
 end
+FBest = getvalue(mp[:G]);
 μp = relaxPart(pData,disData,Ω,cutSet,partCurrent,partDet,400);
-partNew = createPar(pData,disData,Ω,partCurrent,partDet,μp);
+μd = lapConstruct2(pData,disData,Ω,cutSet,partCurrent,partDet,400);
+μcut = lapConstructCut(pData,disData,Ω,cutSet,partCurrent,partDet,ub,400);
+partNew = createPar(pData,disData,Ω,partCurrent,partDet,μd);
 
 # Repeat the process of partition --- generate cuts
 partCurrent = partNew;
+partDet = partDetNew;
 partRev = Dict();
 for i in pData.II
     partRev[i] = Dict();
@@ -195,5 +202,6 @@ for i in pData.II
         xbest[i,j] = getvalue(mp[:x][i,j]);
     end
 end
+FBest = getvalue(mp[:G]);
 μp = relaxPart(pData,disData,Ω,cutSet,partCurrent,partDet,400);
 partNew = createPar(pData,disData,Ω,partCurrent,partDet,μp);

### 2018-06-13 src/ubCalFunc.jl

@@ -47,6 +47,50 @@ function subIntG(pData,dDω,xhat,that,Ghatω)
     return getobjectivevalue(sp);
 end
 
+function subIntGMixed(pData,dDω,xhat,that,ωCurr,Ghatω,M = 400,returnOpt = 0)
+    # solve the MIP recourse problem
+    sp = Model(solver = GurobiSolver(OutputFlag = 0,Method = 1));
+    @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
+    @variable(sp, t[i in pData.II] >= 0);
+    @variable(sp, s[i in pData.II, j in pData.Ji[i]] >= 0);
+    @variable(sp, G[i in pData.II], Bin);
+
+    # add the basic sub problem constraints
+    @constraint(sp, tGcons1[i in pData.II],dDω.H + G[i]*M >= that[i]);
+    @constraint(sp, tGcons2[i in pData.II],dDω.H - (1 - G[i])*M <= that[i]);
+    @constraint(sp, tGbound[i in pData.II],t[i] >= dDω.H*G[i]);
+    @constraint(sp, tFnAnt1[i in pData.II],t[i] + G[i]*M >= that[i]);
+    @constraint(sp, tFnAnt2[i in pData.II],t[i] - G[i]*M <= that[i]);
+    @constraint(sp, xFnAnt1[i in pData.II, j in pData.Ji[i]],x[i,j] + G[i] >= xhat[i,j]);
+    @constraint(sp, xFnAnt2[i in pData.II, j in pData.Ji[i]],x[i,j] - G[i] <= xhat[i,j]);
+
+    # linearize the bilinear term of x[i,j]*G[i]
+    @constraint(sp, xGlin1[i in pData.II, j in pData.Ji[i]], s[i,j] <= G[i]);
+    @constraint(sp, xGlin2[i in pData.II, j in pData.Ji[i]], s[i,j] <= x[i,j] + 1 - G[i]);
+    @constraint(sp, xGlin3[i in pData.II, j in pData.Ji[i]], s[i,j] >= x[i,j] - 1 + G[i]);
+
+    @constraint(sp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(sp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
[…]

### 2018-06-21 Writeup/PERT_New.tex
Add the mixed process and colGen process

--- 2018-04-16 Writeup/PERT_New.tex
@@
 		\end{enumerate}
+	\textcolor{blue}{Add the two activity closed form solution test. Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
+	\section{Decomposition Method} \label{sec:decomposition}
+	Model~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage.
+It is a type of hard problem that efficient decomposition methods have only been found when additional properties about variables exist \textcolor{blue}{cite past literatures with second stage integers.}
 	\begin{comment}

### 2018-06-21 src/colGenFunc.jl

@@ -1,0 +1,6 @@
+function masterF(pData,disData,Ω,cutSet,colGen)
+    # the master with generated columns
+end
+
+function subF(pData,dDω,that,xhat,Fhat)
+end

### 2018-06-21 src/master.jl

@@ -96,3 +96,55 @@ function createMaster_Mixed(pData,disData,Ω,ωInfo,cutSet,M = 9999999)
 
     return mp;
 end
+
+# create a master problem with a selection of binary variables
+function createMaster_MixedL(pData,disData,Ω,ωInfo,cutSet,partCurrentTemp,partDetTemp,M = 9999999)
+    # find the matching between scenario and partition
+    partRev = Dict();
+    partNo = Dict();
+    for i in pData.II
+        partRev[i] = Dict();
+        partNo[i] = length(partCurrent[i]);
+        for partIter in 1:partNo[i]
+            for item in partCurrent[i][partIter]
+                partRev[i][item] = partIter;
+            end
+        end
+    end
+    # cutSet includes the cuts generated
+    mp = Model(solver = GurobiSolver(IntFeasTol = 1e-9,FeasibilityTol = 1e-9));
+    @variables(mp, begin
+      θ[Ω] >= 0
+      0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
+      t[i in pData.II] >= 0
+      0 <= G[i in pData.II,ω in Ω] <= 1
+    end);
+    for (i,ω) in ωInfo
+        setcategory(G[i,ω], :Bin);
+    end
+    @constraint(mp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(mp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(mp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+
+    # logic constraints between G and t
+    @constraint(mp, tGcons1I[i in pData.II, ω in Ω], t[i] <= disData[ω].H + G[i,ω]*M);
+    @constraint(mp, tGcons2I[i in pData.II, ω in Ω], t[i] >= disData[ω].H - (1 - G[i,ω])*M);
+    # logic constraints of G
+    @constraint(mp, GijCon[i in pData.II, j in pData.Succ[i],ω in Ω], G[i,ω] <= G[j,ω]);
[…]

### 2018-06-21 src/misc_scripts.jl

@@ -10,6 +10,10 @@ if length(keys(cutSet[ω][nc][7])) != 0
     cutValue += sum(cutSet[ω][nc][3][i,ω1]*(Gext[i,ω1] - cutSet[ω][nc][7][i,ω1]) for (i,ω1) in keys(cutSet[ω][nc][7]));
 end
 
+cutSet[ω][nc][4] + sum(cutSet[ω][nc][1][i]*(that[i] - cutSet[ω][nc][5][i]) for i in pData.II) +
+            sum(sum(cutSet[ω][nc][2][i,j]*(xhat[i,j] - cutSet[ω][nc][6][i,j]) for j in pData.Ji[i]) for i in pData.II if i != 0) +
+            sum(cutSet[ω][nc][3][i]*(Ghat[i,ω] - cutSet[ω][nc][7][i]) for i in pData.II);
+
 ##########################################################################################
 # obtain the 50/500 test data
 pInputAdd = "test_14_P.csv";

### 2018-06-21 src/partition_LP.jl

@@ -1,4 +1,4 @@
-function relaxPart(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 9999999,FPre = [])
+function relaxPart(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 9999999,FPre = [],returnOpt = 0)
     # formulate the linear relaxation of the master problem and solve it to obtain the dual solution
     partRev = Dict();
     partNo = Dict();
@@ -58,7 +58,11 @@ function relaxPart(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 9999999,F
             μp[i,ω] = -getdual(lrm[:GFCon][i,ω]);
         end
     end
-    return μp;
+    if returnOpt == 0
+        return μp;
+    else
+        return μp,lrm;
+    end
 end
 
 function createPar(pData,disData,Ω,partCurrentTemp,partDetTemp,μp)
@@ -144,6 +148,101 @@ function createParCut(pData,disData,Ω,partCurrentTemp,partDetTemp,μp)
         end
     end
 
+    return partNew,partDetNew;
+end
+
+function createParOpt(pData,disData,Ω,partCurrentTemp,partDetTemp,cutSet,Tmax = 200)
+    # formulate the linear relaxation of the master problem and solve it to obtain the dual solution
+    partRev = Dict();
+    partNo = Dict();
+    for i in pData.II
+        partRev[i] = Dict();
+        partNo[i] = length(partCurrentTemp[i]);
+        for partIter in 1:partNo[i]
+            for item in partCurrentTemp[i][partIter]
+                partRev[i][item] = partIter;
+            end
+        end
+    end
+    # obtain the range where the F is undecided
+    partZero = Dict();
+    for i in pData.II
+        zeroMin = minimum([ω for ω in Ω if partDetTemp[i][partRev[i][ω]] == 0]) - 1;
+        zeroMax = maximum([ω for ω in Ω if partDetTemp[i][partRev[i][ω]] == 0]);
+        partZero[i] = zeroMin:zeroMax;
+    end
+    H = Dict();
+    H[0] = 0;
+    H[length(Ω)+1] = Tmax;
+    for ω in Ω
+        H[ω] = disData[ω].H;
+    end
+
[…]

### 2018-06-21 src/partition_LR.jl

@@ -53,7 +53,7 @@ function lapConstruct(pData,disData,Ω,cutSet,partCurrentTemp,partDet,μ,M = 999
     return lap;
 end
 
-function lapConstruct2(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 999999,FPre = [])
+function lapConstruct2(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 999999,FPre = [],returnOpt = 0)
     # dual model to solve the Lagrangian problem analytically
     partRev = Dict();
     partNo = Dict();
@@ -130,7 +130,11 @@ function lapConstruct2(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 99999
             μp[i,ω] = getvalue(lap[:μ][i,ω]);
         end
     end
-    return μp;
+    if returnOpt == 0
+        return μp;
+    else
+        return μp,lap;
+    end
 end
 
 function lapConstructFix(pData,disData,Ω,cutSet,partCurrentTemp,partDet,M = 999999,FPre = [])

### 2018-06-21 src/sub.jl

@@ -277,7 +277,7 @@ function subPull(pData,dDω,xhat,that,Ghatω,M = 9999999)
             λdict[i,j] = (getdual(sp[:xFnAnt1])[i,j] + getdual(sp[:xFnAnt2])[i,j]);
         end
     end
-    return πdict,γdict,λdict,vk;
+    return πdict,λdict,γdict,vk;
 end
 
 function subMixed(pData,dDω,xhat,that,Ghatω,ωCurr,Ω,M = 9999999,returnOpt = 0)

### 2018-06-21 src/test_mixedNew.jl

@@ -33,6 +33,43 @@ for ω in Ω
     end
 end
 
+tdet,xdet,fdet = detBuild(pData);
+ubdet = ubCal(pData,disData,Ω,xdet,tdet);
+brInfo = precludeRel(pData,disData,Ω,ubdet);
+partCurrent = Dict();
+partDet = Dict();
+for i in pData.II
+    # for each activity, break it into two partition, brInfo == 0 and brInfo == 1
+    partCurrent[i] = [];
+    partDet[i] = [];
+    part1 = [ω for ω in Ω if brInfo[findin(pData.II,i)[1],ω] == 1];
+    if part1 != []
+        push!(partCurrent[i],part1);
+        push!(partDet[i],1);
+    end
+    part0 = [ω for ω in Ω if brInfo[findin(pData.II,i)[1],ω] == 0];
+    if part0 != []
+        push!(partCurrent[i],part0);
+        push!(partDet[i],0);
+    end
+    partn1 = [ω for ω in Ω if brInfo[findin(pData.II,i)[1],ω] == -1];
+    if partn1 != []
+        push!(partCurrent[i],partn1);
+        push!(partDet[i],-1);
+    end
+end
+
+partRev = Dict();
+for i in pData.II
+    partRev[i] = Dict();
+    partNo = length(partCurrent[i]);
+    for partIter in 1:partNo
+        for item in partCurrent[i][partIter]
+            partRev[i][item] = partIter;
+        end
+    end
+end
+
 ωInfo = [];
 cutSet = Dict();
 for ω in Ω
@@ -46,32 +83,30 @@ tlb = Dict();
 xlb = Dict();
 Glb = Dict();
 θlb = Dict();
-lbPrev = -Inf;
 ωWrong = [];
 while keepIter
-    mp = createMaster_Mixed(pData,disData,Ω,ωInfo,cutSet,400);
+    mp = createMaster_MixedL(pData,disData,Ω,ωInfo,cutSet,partCurrent,partDet,400);
     solve(mp);
     # obtain the solution
     that = Dict();
     xhat = Dict();
     Ghat = Dict();
     θhat = Dict();
+    Ghatω = Dict();
     for i in pData.II
         that[i] = getvalue(mp[:t][i]);
         for j in pData.Ji[i]
             xhat[i,j] = getvalue(mp[:x][i,j]);
         end
         for ω in Ω
-            if (i,ω) in ωInfo
[…]

### 2018-06-21 src/ubCalFunc.jl

@@ -21,6 +21,43 @@ function subInt(pData,dDω,xhat,that)
     return getobjectivevalue(sp);
 end
 
+function subIntC(pData,dDω,xhat,that,M = 999999,returnOpt = 0)
+    # solve the MIP recourse problem
+    sp = Model(solver = GurobiSolver(OutputFlag = 0));
+    @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
+    @variable(sp, 0 <= s[i in pData.II,j in pData.Ji[i]] <= 1);
+    @variable(sp, t[i in pData.II] >= 0);
+    @variable(sp, G[i in pData.II], Bin);
+
+    # add the basic sub problem constraints
+    @constraint(sp, FCons[i in pData.II],dDω.H - (1 - G[i])*M <= that[i]);
+    @constraint(sp, GCons[i in pData.II],dDω.H + G[i]*M >= that[i]);
+
+    @constraint(sp, tGcons1[i in pData.II], t[i] <= that[i] + M*G[i]);
+    @constraint(sp, tGcons2[i in pData.II], t[i] >= that[i] - M*G[i]);
+    @constraint(sp, boundT[i in pData.II], t[i] >= dDω.H*G[i]);
+    @constraint(sp, xGcons1[i in pData.II,j in pData.Ji[i]], x[i,j] <= xhat[i,j] + G[i]);
+    @constraint(sp, xGcons2[i in pData.II,j in pData.Ji[i]], x[i,j] >= xhat[i,j] - G[i]);
+
+    @constraint(sp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(sp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+    # linearize the bilinear term of x[i,j]*G[i]
+    @constraint(sp, xGlin1[i in pData.II, j in pData.Ji[i]], s[i,j] <= G[i]);
+    @constraint(sp, xGlin2[i in pData.II, j in pData.Ji[i]], s[i,j] <= x[i,j]);
+    @constraint(sp, xGlin3[i in pData.II, j in pData.Ji[i]], s[i,j] >= x[i,j] - 1 + G[i]);
+
+    @constraint(sp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]] + dDω.d[k[1]]*G[k[1]]
[…]

### 2018-06-25 src/colGenFunc.jl
Update the tests

@@ -1,6 +1,308 @@
-function masterF(pData,disData,Ω,cutSet,colGen)
-    # the master with generated columns
+# create a master problem with a selection of binary variables
+function masterMax(pData,disData,Ω,ωInfoOld,Ghat,ωInfoNew,cutSet,partCurrentTemp,partDetTemp,M = 9999999, solveOpt = 0)
+    partRev = Dict();
+    partNo = Dict();
+    for i in pData.II
+        partRev[i] = Dict();
+        partNo[i] = length(partCurrent[i]);
+        for partIter in 1:partNo[i]
+            for item in partCurrent[i][partIter]
+                partRev[i][item] = partIter;
+            end
+        end
+    end
+    # cutSet includes the cuts generated
+    mp = Model(solver = GurobiSolver(IntFeasTol = 1e-9,FeasibilityTol = 1e-9,OutputFlag = 0));
+    @variables(mp, begin
+      θ[Ω] >= 0
+      0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
+      t[i in pData.II] >= 0
+      0 <= G[i in pData.II,ω in Ω] <= 1
+    end);
+    for (i,ω) in ωInfoNew
+        setcategory(G[i,ω], :Bin);
+    end
+    @constraint(mp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(mp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(mp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
+
+    # logic constraints between G and t
+    @constraint(mp, tGcons1I[i in pData.II, ω in Ω], t[i] <= disData[ω].H + G[i,ω]*M);
+    @constraint(mp, tGcons2I[i in pData.II, ω in Ω], t[i] >= disData[ω].H - (1 - G[i,ω])*M);
+    # logic constraints of G
+    @constraint(mp, GijCon[i in pData.II, j in pData.Succ[i],ω in Ω], G[i,ω] <= G[j,ω]);
[…]

### 2018-06-25 src/master.jl

@@ -133,6 +133,7 @@ function createMaster_MixedL(pData,disData,Ω,ωInfo,cutSet,partCurrentTemp,part
     @constraint(mp, GijCon[i in pData.II, j in pData.Succ[i],ω in Ω], G[i,ω] <= G[j,ω]);
     @constraint(mp, Gω12Con[i in pData.II, ω in 1:(length(Ω)-1)], G[i,ω] >= G[i,ω + 1]);
     @constraint(mp, Gdet1[i in pData.II, ω in Ω; partDet[i][partRev[i][ω]] == 1], G[i,ω] == 1);
+    @constraint(mp, Gdet0[i in pData.II, ω in Ω; partDet[i][partRev[i][ω]] == -1], G[i,ω] == 0);
 
     for ω in Ω
         if cutSet[ω] != []
@@ -146,5 +147,49 @@ function createMaster_MixedL(pData,disData,Ω,ωInfo,cutSet,partCurrentTemp,part
 
     @objective(mp, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
 
+    return mp;
+end
+
+function masterF(pData,disData,Ω,ωInfo,cutSet,Tmax = 999999)
+    H = Dict();
+    H[0] = 0;
+    H[length(Ω)+1] = Tmax;
+    for ω in Ω
+        H[ω] = disData[ω].H;
+    end
+
+    # the master with generated columns
+    mp = Model(solver = GurobiSolver(IntFeasTol = 1e-9,FeasibilityTol = 1e-9));
+    @variables(mp, begin
+      θ[Ω] >= 0
+      0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
+      t[i in pData.II] >= 0
+      0 <= F[i in pData.II,ω in 0:length(Ω)] <= 1
+    end);
+    for (i,ω) in ωInfo
+        setcategory(F[i,ω], :Bin);
+    end
+
+    @constraint(mp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(mp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
[…]

### 2018-06-25 src/sub.jl

@@ -342,3 +342,92 @@ function subMixed(pData,dDω,xhat,that,Ghatω,ωCurr,Ω,M = 9999999,returnOpt = 
         return πdict,λdict,γdict,vk,sp;
     end
 end
+
+function subF(pData,dDω,that,xhat,Fhat,M = 999999)
+    sp = Model(solver = GurobiSolver(OutputFlag = 0,Method = 1));
+    @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
+    @variable(sp, t[i in pData.II] >= 0);
+    @variable(sp, s[i in pData.II, j in pData.Ji[i]] >= 0);
+    @variable(sp, 0 <= G[i in pData.II] <= 1);
+
+    # add the basic sub problem constraints
+    @constraint(sp, GFcons[i in pData.II, ω in Ω], G[i,ω] == sum(Fhat[i,ω1] for ω1 in 0:length(Ω) if ω1 >= ω));
+    @constraint(sp, tGbound[i in pData.II],t[i] >= dDω.H*G[i]);
+    @constraint(sp, tFnAnt1[i in pData.II],t[i] + G[i]*M >= that[i]);
+    @constraint(sp, tFnAnt2[i in pData.II],t[i] - G[i]*M <= that[i]);
+    @constraint(sp, xFnAnt1[i in pData.II, j in pData.Ji[i]],x[i,j] + G[i] >= xhat[i,j]);
+    @constraint(sp, xFnAnt2[i in pData.II, j in pData.Ji[i]],x[i,j] - G[i] <= xhat[i,j]);
+
+    # linearize the bilinear term of x[i,j]*G[i]
+    @constraint(sp, xGlin1[i in pData.II, j in pData.Ji[i]], s[i,j] <= G[i]);
+    @constraint(sp, xGlin2[i in pData.II, j in pData.Ji[i]], s[i,j] <= x[i,j] + 1 - G[i]);
+    @constraint(sp, xGlin3[i in pData.II, j in pData.Ji[i]], s[i,j] >= x[i,j] - 1 + G[i]);
+
+    @constraint(sp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
+    @constraint(sp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
[…]

### 2018-06-25 src/test_mixedNew.jl

@@ -7,9 +7,15 @@
 @everywhere include("master.jl");
 @everywhere include("sub.jl");
 @everywhere include("cuts.jl");
+@everywhere include("iSolve.jl");
+@everywhere include("tighten.jl");
+@everywhere include("branchFunc.jl");
 @everywhere include("detForm.jl");
 @everywhere include("extForm.jl");
 @everywhere include("ubCalFunc.jl");
+@everywhere include("tighten.jl");
+@everywhere include("partition_LP.jl");
+@everywhere include("partition_LR.jl");
 
 pInputAdd = "test_14_P.csv";
 kInputAdd = "test_14_K.csv";
@@ -83,6 +89,8 @@ tlb = Dict();
 xlb = Dict();
 Glb = Dict();
 θlb = Dict();
+xbest = Dict();
+tbest = Dict();
 ωWrong = [];
 while keepIter
     mp = createMaster_MixedL(pData,disData,Ω,ωInfo,cutSet,partCurrent,partDet,400);
@@ -110,8 +118,11 @@ while keepIter
     lbPrev = lbCost;
     πdict = Dict();
     λdict = Dict();
+    πdict1 = Dict();
+    λdict1 = Dict();
     γdict = Dict();
     vk = Dict();
+    vk1 = Dict();
     θInt = Dict();
     ubTemp = pData.p0*that[0];
     for ω in Ω
@@ -120,6 +131,7 @@ while keepIter
             Ghatω[ω][i] = Ghat[i,ω];
         end
         πdict[ω],λdict[ω],γdict[ω],vk[ω] = subPull(pData,disData[ω],xhat,that,Ghatω[ω],400);
+        #πdict1[ω],λdict1[ω],vk1[ω] = subLag(pData,disData[ω],xhat,that,Ghatω[ω],γdict[ω],400);
         ubTemp += disData[ω].prDis*subIntC(pData,disData[ω],xhat,that,400);
     end
     if ubCost > ubTemp
@@ -185,7 +197,7 @@ for i in pData.II
     disMin = Inf;
     bestω = -1;
     for ω in Ω
-        if !((i,ω) in ωInfo)
+        if !((i,ω) in ωInfo)&(Glb[i,ω] < 1)&(Glb[i,ω] > 0)
             if abs(disData[ω].H - tlb[i]) < disMin
                 bestω = ω;
                 disMin = abs(disData[ω].H - tlb[i]);
@@ -193,6 +205,7 @@ for i in pData.II
         end
[…]

### 2018-06-25 src/ubCalFunc.jl

@@ -132,7 +132,7 @@ function ubCal(pData,disData,Ω,xhat,that)
     # calculate the upper bound of the problem given the master solution
     ubCost = that[0]*pData.p0;
     for ω in Ω
-        cω = subInt(pData,disData[ω],xhat,that);
+        cω = subIntC(pData,disData[ω],xhat,that);
         ubCost += disData[ω].prDis*cω;
     end
     return ubCost;
@@ -141,7 +141,7 @@ end
 function ubCalP(pData,disData,Ω,xhat,that)
     # parallel version of calculating the upper bound
     ubCost = that[0]*pData.p0;
-    cωList = pmap(ω -> subInt(pData,disData[ω],xhat,that), Ω);
+    cωList = pmap(ω -> subIntC(pData,disData[ω],xhat,that), Ω);
     ubCost += sum(cωList[i]*disData[Ω[i]].prDis for i in 1:length(ω));
     return ubCost;
 end

### 2018-07-17 Writeup/PERT_New.tex
Update the tests
Update the writeup

--- 2018-04-16 Writeup/PERT_New.tex
@@
 \usepackage{amssymb}
+\usepackage{accents}
 \usepackage{tabularx}
@@
 \newcommand{\mbf}{\mathbf}
+\renewcommand{\underbar}{\underaccent{\bar}}
 
@@
 The arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\).
-We create a dummy activity \(N\) to represent the end of entire project, which should succeed every activity \(i \in I\).
+We create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project.
+\(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \).
 \\
@@
 We assume each activity can be crashed at most with one unit and the problem can be formulated as follows:
-	\begin{subequations} \label{prob2:static}
+	\begin{subequations} \label{prob:static}
 		\begin{align}
-		\min \quad & t_N &\\
+		\min \quad & t_T &\\
 		\text{s.t.} \quad &  t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:dSep}\\
@@
 	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\).
-We aim to minimize the project span, which is the starting time of the dummy activity, \(t_N\).
+We aim to minimize the project span, which is the starting time of the terminal activity, \(t_T\).
 Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
@@
 	\newline
-	In our problem, we assume at most one stochastic disruption can occur in the project span, while the time of such disruption is a random variable.
-We also assume for each activity \(i \in I\), the crashing decision decision for that activity needs to be made prior to the start of that activity, and cannot be changed after that.
-We assume that the disruption does not affect the activities that have already started but changes the length of activities starting after it according to some given distributions.
-We assume there is a discrete finite set of scenarios indexed by \(\Omega\).
-It is usually hard to compute the recourse function directly when some of its parameters are distributed according to continuous distributions, and SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}.
+	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span.
+We also assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards.
+The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
+It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}.
+In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\).
+For each scenario \(\\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\).
 \\
 	\newline
-	Since there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
-Notice that the definition of the first stage is different from the traditional stochastic program setting.
-Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterize the decisions for each realization of the disruption.
-This means that the first stage decision variables are carried out until the disruption, if it ever occurs, and after the disruption, depending on the scenario realized, the scenario-specific recourse decisions are executed.\\
+	If there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
+The definition of our first stage is different from the traditional stochastic program setting.
+Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterizes the decisions for each realization of the disruption.
+This means that the first stage decision variables are carried out until the disruption, if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
 	\newline
@@
 		\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
-		\(S_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\
+		\(z_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\
 	\end{longtable}
-	\noi The extensive formulation of the two-stage stochastic program is shown as formulation~(\ref{prob2:extensive}):
-	\begin{subequations} \label{prob2:extensive}
+	\noi The extensive formulation of the two-stage stochastic program is shown as formulation~\eqref{prob:extensive}:
+	\begin{subequations} \label{prob:extensive}
 		\begin{align}
-		\min \quad & \sum_{\omega \in \Omega} p^\omega t_N^\omega + p^0 t_N \\
-		\text{s.t.} \quad & t_N^\omega \geq t_i^\omega \qquad \qquad \forall \,i \in I, \omega \in \Omega \\
-		& t_N \geq t_i \qquad \qquad \label{cons:tN}\\
-		& t_i^\omega \geq 0 \qquad \qquad \forall \,i \in I, \omega \in \Omega\\
-		& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
-		& H^\omega - (1 - G_i^\omega) M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:F}\\
-		& H^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G}\\
-		& t_i^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tf1}\\
-		& t_i^\omega - G_i^\omega M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tf2}\\
-		& x_{ij}^\omega + G_i^\omega \geq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf1}\\
-		& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xf2}\\
-		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} S_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:duration}\\
-		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:crashLim}\\
-		& \sum_{i \in I}\sum_{j \in J_i} b_jx_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:budget}\\
-		& S_{ij}^\omega \leq G_i^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
-		& S_{ij}^\omega \leq x_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
-		& S_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
+		\min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\
+		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:Sep}\\
+		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:Budget}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:SingleBudget}\\
+		& H^\omega + G_i^\omega M \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G1}\\
+		& H^\omega - (1 - G_i^\omega) M \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:G2}\\
+		& t_i^\omega + G_i^\omega M_t \geq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tG1}\\
+		& t_i^\omega - G_i^\omega M_t \leq t_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:tG2}\\
+		& x_{ij}^\omega + G_i^\omega \geq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xG1}\\
+		& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xG2}\\
+		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:scenSep}\\
+		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:scenBudget1}\\
+		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:scenBudget}\\
+		& z_{ij}^\omega \leq G_i^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
+		& z_{ij}^\omega \leq x_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize2}\\
+		& z_{ij}^\omega \geq G_i^\omega + x_{ij}^\omega - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize3}\\
+		& t_i \geq 0 \qquad \qquad \forall \,i \in I \label{cons:nonnegt}\\
 		& t_i^\omega \geq H^\omega G_i^\omega \qquad \qquad \forall\, i \in I, \omega \in \Omega \\
@@
 		& 0 \leq x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
-		& 0 \leq S_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
+		& 0 \leq z_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
 		& G_i^\omega \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega.
@@
 	\end{subequations}
-	In model~\eqref{prob2:extensive}, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
-Variables \(G^\omega_i\) are used to identify whether activity \(i\) starts before or after the disruption time (in constraint \eqref{cons:F}-\eqref{cons:G}) and \(M\) is a large number to enforce the logic relationships.
-This is important in our problem setting because the duration of each activity depends on its temporal relationship to the disruption time, which is reflected in constraint (\ref{cons:duration}).
-For this duration constraint, the original expression of the duration of activity \(i\) is \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\).
-This contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which is linearized by introducing a binary variable \(S_{ij}^\omega\) and bounding it by constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.\\
-	\newline
-	We use a set of non-anticipativity constraints \eqref{cons:tf1}-\eqref{cons:xf2}, different from ones used in a traditional stochastic programming because the first stage decision variables here spans the entire time horizon.
-These logic constraints ensure that the decisions made before the disruption time in each scenario are the same as the nominal decisions before the same time point.
+	In model~\eqref{prob:extensive}, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
+We keep the constraints~\eqref{cons:dSep}-\eqref{cons:dSingleBudget} for the nominal scenario as~\eqref{cons:Sep}-\eqref{cons:SingleBudget}.
+In constraints~\eqref{cons:G1}-\eqref{cons:G2}, variables \(G^\omega_i\) takes value \(1\) if activity \(i\) starts after the disruption time; otherwise it takes value 0, and \(M\) is a large number to enforce this logic relationships.
+This is important in our problem setting because the duration of each activity depends on its temporal relationship to the disruption time, which is reflected in constraint~\eqref{cons:scenSep}.
+Also we have to ensure that the decisions made before the disruption time in each scenario are the same as the nominal decisions.
+Therefore, we set up non-anticipativity constraints~\eqref{cons:tG1}-\eqref{cons:xG2}.
+For each scenario, the duration of activity \(i\) becomes \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\), which expands to the form of constraint~\eqref{cons:scenSep}.
+If \(G_i^\omega = 0\), which means activity \(i\) starts before the disruption time of scenario \(\omega\), this expression is the same as \(D_i (1 - \sum_{j \in J_i} e_{ij}x_{ij})\) since \(x_{ij} = x_{ij}^\omega\) is enforced by constraints~\eqref{cons:xG1} and~\eqref{cons:xG2}.
+If \(G_i^\omega = 1\), then the duration of activity \(i\) is changed to \(D_i + d_i^\omega\).
+The expression \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\) contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(z_{ij}^\omega\) and constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.
 
-\section{Special Cases} \label{sec:examples}
-	In this section we show a serial example to illustrate the nature of the project crashing problem under stochastic disruption.
-From this serial network example we show that it might be optimal to delay the start of some activities, and thus justify the formulation in model~\eqref{prob2:extensive}.
+\section{Illustration of Problem Properties via Examples} \label{sec:examples}
+	In this section we show a serial example to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem.
+In the deterministic project crashing problem, all activities on the critical path should start as soon as possible.
+However, with a stochastic disruption, it might be optimal to delay the start of some activities.
+Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\).
 \\
 	\newline
+	It is obvious that the delay can possibly be beneficial if \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\).
+We use a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption, a.k.a., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
 Suppose we have a project with three activities in a serial network form.
@@
 The structure of the project is displayed as follows.
-We add a dummy activity ``N" to represent the end of the project.
-The total crashing budget is \(1\) and the allowed amount of crashing a single activity is between \(0\) and \(1\).
+We add a dummy activity ``T" to represent the end of the project.
+The total crashing budget is \(1\).
 	\begin{figure}[H]
@@
 	\end{figure}
-	\noi So, \(I=\{1,2,3,N\}\), and \(D_1=9\), \(D_2=10\), and \(D_3=7\).
+	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\).
+There is only one crashing option for each activity, so we omit the subscript to index the crashing options.
+We use \(e_i = 0.5\) for all \(i \in I\).
 The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\).
 The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario.
-Suppose the disruption changes \(D_2=10\) to \(3\), a.k.a.
-\(d_2^1 = -7\), and not affect activity 3.
-We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\), spend the entire budget to crash activity 3 if the disruption occurs, and spend the entire budget to crash activity 2 if the disruption does not occur.
-The expected total project span is 18.35.
-If we force the condition that the starting time of activities cannot be delayed, we cannot observe whether the disruption happens or not prior to the start of activity 2.
-There is only one possible situation where three activities have the duration as 9, 10 and 7.
-All resources should be allocated to activity 2 and the total project span is 21, which is larger than the expected total project span if it is allowed to delay the starting time of some activities.
-In this example, a disruption may reduce the duration of some activities and delaying by a small amount allows us to realize that reduction in time.\\
-	\newline
-	Even if the disruption can only lengthen an activity's duration, it is still beneficial to delay the start of some activities under some circumstances.
-This means a small delay of some activity may gain the information regarding the disruption, which can decrease the project span.
-To see this, we again consider the serial network of Figure~\ref{fig:serial3}.
-We assume the nominal durations, and the stochastic disruption, are identical to those above.
-If the disruption occurs, the durations of activities change by \(d_2^1=0.1\) and \(d_3^1 = 6\).
-For this example, if no delay is allowed, the optimal decision is to have \(x_2 = 1\) and the optimal objective value is 24.
-If we delay the starting time of the activity 2 to \(t_2 = 9.1\) so that the disruption can be observed before we commit resources to activity 2, the optimal expected total project span is 23.4.
+Suppose the disruption does not affect activity 1, \(d_1^1 = 0\), increases the duration of activity 2 by \(0.1\), \(d_2^1 = 0.1\), and increases the duration of activity 3 by \(6\), \(d_3^1 = 6\).
+We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\).
+There we are able to observe whether the disruption happens.
+If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise it is optimal to crash activity 2 with \(1\) amount of resource.
+The expected total project span is \(23.4\), as the optimal project span given no disruption is \(21.1\) and that under disruption is \(25.7\).
+If every activity starts as soon as possible, like in the deterministic problem, we cannot observe whether the disruption happens or not prior to the start of activity 2.
+Under this condition, the best solution is to crash activity 2 with \(1\) amount of crashing resource, and the optimal expected project span is \(24\), larger than \(23.4\).
 \\
@@
 		\end{enumerate}
+	In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
+We present a following example to showcase this property.
+Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}.
+The nominal durations of two activities are \(D_1 = 3, D_2 = 4\).
+The disruption does not affect the duration of activity 1, as \(d_1 = 0\), and lengthens the activity 2 by a random variable distributed in a uniform distribution with upper bound \(10\) and lower bound \(0\), as \(d_2 \sim \mathcal{U}(0,10)\).
+The crashing option setting is the same as the previous example, as there is only one crashing option for each activity and \(e_i = 0.5, \forall i \in I\).
+The total budget \(B = 1\).
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.8\textwidth]{2act}
+			\caption{Left: an illustration of a 2-activity project; right: probability distribution function of disruption time.}
+			\label{fig:2act}
+		\end{figure}
+	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\).
+Activity 1 starts at time \(t_1 = 0\) and activity 2 starts at time \(t_2 = 1.5\).
+The optimal expected project span is \(\mathbb{E}[t_T] = 6.5\).
+We can compare an alternative solution which crash activity 2 with one unit of resource, which has a longer expected duration.
+Crashing activity 2 matches the intuition from the deterministic case where on the critical path the activities with longer expected duration are prioritized.
+However, in this case with a stochastic disruption, the latter solution (\(t_1 = 0, t_2 = 3, x_1 = 0, x_2 = 1\)) yields a longer expected project span as \(\mathbb{E}[t_T] = 7.5\).
+The reason behind this gap is that by crashing activity 1 with one unit amount of resource, the probability of activity 2 starting before the disruption increases to \(0.8\), which prevents activity 2 from seeing the increased duration.
+\\
+	\newline
+	These examples above indicate that the crashing optimization problem with stochastic disruption has complicated nature.
+The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
+	\textcolor{blue}{Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
+
+	\section{Decomposition Method} \label{sec:decomposition}
+	Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program (2SMIP).
+If we attempt to decompose it into a master problem~\eqref{prob:masterOri} and scenario-specific subproblems~\eqref{prob:subOri}, the state variables \(t\) and \(x\) are all continuous and binary variables exist in the recourse problems.
+The recourse problems become nonconvex.
+Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
+For example, Sherali/Fracticelli, Sen/Higle, Ntaimo/Sen, Sherali/Zhu, Sen/Sherali, Gade/Kucukyavuz/Sen solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where disjunctive cuts or Gomory cuts are added.
+Ahmed/Sun/Zou assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
+Caroe/Tind solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not optimistic.
+	\begin{subequations}
+		\label{prob:masterOri}
+		\begin{align}
+		(M) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\
+		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MSep}\\
+		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:MBudget}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MSingleBudget}\\
+		& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i.
+		\end{align}
+	\end{subequations}
+	\begin{subequations}
+		\label{prob:subOri}
+		\begin{align}
+		(S^\omega) \qquad f^\omega(\hat{t},\hat{x}) = \min \quad & t_T \\
+		& H^\omega + G_i M \geq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:sG1}\\
+		& H^\omega - (1 - G_i) M \leq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:sG2}\\
+		& t_i + G_i M_t \geq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:stG1}\\
+		& t_i - G_i M_t \leq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:stG2}\\
+		& x_{ij} + G_i \geq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sxG1}\\
+		& x_{ij} - G_i \leq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sxG2}\\
+		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij} \nonumber \\ 
+		& \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:subSep}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:subBudget1}\\
+		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij} \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:subBudget}\\
+		& z_{ij} \leq G_i \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize1}\\
+		& z_{ij} \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize2}\\
+		& z_{ij} \geq G_i + x_{ij} - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize3}\\
+		& t_i \geq H^\omega G_i \qquad \qquad \forall\, i \in I, \omega \in \Omega \\
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
+		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
+		& G_i \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega. \label{cons:subInt}
+		\end{align}
+	\end{subequations}
+	We can relax the integrality constraints~\eqref{cons:subInt} and solve the subproblem to obtain Benders' cuts.
+Although those Benders' cuts are no longer a tight approximation of the recourse function \(f^\omega(x,t), \forall \omega \in \Omega\), they still provide a valid lower bound.
+On the other hand, in each iteration of the Benders' decomposition, the upper bound can be obtained by solving the subproblems~\eqref{prob:subOri}, given a first stage solution.
+We observe that a smaller \(M\) yields a tighter gap between the upper bound and the lower bound, because we can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
+	\begin{equation}
+		(\hat{t}_i - H^\omega)/M \leq G_i \leq (\hat{t}_i - H^\omega)/M + 1
+	\end{equation}
+	and \(G_i\) can take a wider range of value when \(M\) is larger.
+Therefore, sequentially tightening \(M\) is helpful to generate a tighter lower bound as the algorithm progresses.
+Eventually, if for a scenario we can fix the \(G_i\) for all \(i \in I\) to either 0 or 1, the Benders' cuts will be tight.\\
+	\newline
+	From now on we assume the scenarios \(\omega \in \Omega\) are ordered according to their time \(H^\omega\) in an ascending order.
+We can also observe that if we know \(\hat{t}_i \geq H^{\omega'_i}\) for some \(\omega'_i\), \(G_i\) has to take value 1 in all subproblem \(S^\omega\) where \(\omega < \omega'_i\).
+On the other hand if we know \(\hat{t}_i \leq H^{\omega'_i}\) for some \(\omega'_i\), \(G_i\) has to take value 0 in all subproblem \(S^\omega\) where \(\omega > \omega'_i\).
+These observations inform us that by bounding the value of first stage variable \(t_i,\ \forall i \in I\), we can determine the value of \(G_i\) in many subproblems, which strengthens the Benders' cuts.\\
+	\newline
+	We propose a decomposition algorithm to solve model~\eqref{prob:extensive}.
+Our method partitions the continuous feasible region of the master problem by introducing of a set of binary variables.
+As we refine the partition of \(t\)-space, we can generate tightened Benders' cuts to approximate the recourse function.
+For any crashing optimization problem, we can bound the first stage \(t_i\) variables by lower bound \(0\) and upper bound \(T_{\max} = H^{|\Omega|} + t_T^0\), where \(t_T^0\) is the longest \(S\)-\(T\) path of activity network \(\mathcal{G} = (I,\mathcal{A})\) and the arc length of \((i,j) \in \mathcal{A}\) equals to \(D_i\).
+This means that suppose the optimal solution of model~\eqref{prob:extensive} is denoted as \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\), the latter two representing the scenario specific starting time and crashing decisions, we have:
+	\begin{proposition} \label{prop:bounds}
+		 \(t^*_i \in [0,T_{\max}],\ \forall i \in I\).
+	\end{proposition}
+	\begin{proof}
+		Constraint~\eqref{cons:nonnegt} enforces the lower bound of this proposition. \\
+		\newline 
+		To derive the upper bound, 
+		we first establish a feasible solution \(\tilde{t}_i = H^{|\Omega|} + t^0_i,\ \forall i \in I\), \(\tilde{x}_{ij} = 0,\ \forall i \in I, j \in J_i\) and \(\tilde{G}_i^\omega = 1,\ \forall i \in I, \omega \in \Omega\), where \(t^0_i\) represents the length of the longest \(S\)-\(i\) path of \(\mathcal{G}\).
+		If we assume that there exists some \(i \in \tilde{I}\) such that \(t_i^* > T_{\max}\), we know \(T \in \tilde{I}\).
+There, we can keep \(x^*\), \(G^{*,\omega}\), \(t^{*,\omega}\) and \(x^{*,\omega}\) for all \(\omega \in \Omega\) the same, and replace the \(t_i^*\) by \(\tilde{t}_i\) for all \(i \in \tilde{I}\) without violating any constraints.
+This yields another feasible solution which has a smaller value of \(t_T^*\) since \(T \in \tilde{I}, \tilde{t}_T = T_{\max} < t_T^*\).
+Therefore the new objective value obtained by this feasible solution is smaller, which contradicts the assumption that \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\) is an optimal solution.
+	\end{proof}
+	\noi Proposition~\ref{prop:bounds} indicates that all \(t_i,\ \forall i \in I\) are bounded on an interval \([0,T_{\max}]\).
+Since there are precedence relationships between activities, the possible range of different activities' starting time can be further limited.
+We first set up two parameters \(H^0 = 0\) and \(H^{|\Omega| + 1} = T_{\max}\) and then define a partition of this interval for each \(i \in I\) to exploit this limitation as follows:
+	\begin{definition}
+		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}\), which is an ordered set of two-element tuples \((\bar{\omega}^q,\underbar{\omega}^q)\), which is indexed by \(q \in \mathcal{Q}\) and corresponds to the upper bound scenario index and the lower bound scenario index.
+The partition has the following properties:
+		\begin{itemize}
+			\item \(\underbar{\omega}^1 = 0\)
+			\item \(\bar{\omega}^{|\mathcal{Q}|} = T_{\max}\)
+			\item \(\bar{\omega}^q = \underbar{\omega}^{q + 1}\).
+		\end{itemize}
+	\end{definition}
+	\noi A simple example of such partition can be illustrated in Figure~\ref{fig:simplePart}.
+In this example we have five scenarios \(\Omega = \{1,2,3,4,5\}\), ordered by the disruption time.
+The partition has three elements, each illustrated by a box with dashed lines and represent a part of the interval.
+For partition element \(1\), the lower bound scenario index is \(0\) and the upper bound scenario index is \(2\), which means the range corresponding to it is lower bounded by \(H^0 = 0\) and upper bounded by \(H^2\).
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\textwidth]{simplePart}
+		\caption{An illustration of partition on interval \([0,T_{\max}]\).}
+		\label{fig:simplePart}
+	\end{figure}
+	Here we present the modified master problem and subproblems with the addition of partition:
+	\begin{subequations}
+		\begin{align}
+			(M_P) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
+			\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MpSep}\\
+			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:MpBudget}\\
+			& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MpSingleBudget}\\
+			& \sum_{q \in \mathcal{Q}_i} y^q_i = 1 \qquad \qquad \forall i \in I \\
+			& \sum_{q \in \mathcal{Q}_i} \underbar{H}_i^{q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} \bar{H}_i^{q} y_i^{q} \qquad \qquad \forall i \in I\\
+			& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
+			&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber \\
+			& \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots\\
+			& y_i^q \in \{0,1\} \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i\\
+			& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
+			& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i.
+		\end{align}
+	\end{subequations}
+	\textcolor{blue}{
+		Proof of NP-hard.\\
+		Proof of validity of tighter cuts: strengthened Benders cuts.\\
+		Proof of increasing-decreasing behavior.
+	}
 	\begin{comment}
@@
 	\subsection{IID vs. Stratified Sampling}
-\section{Decomposition Method} \label{sec:decomposition}
-	Problem~\eqref{prob2:extensive} is a two-stage stochastic mixed integer program with binary variables in the second stage.
 
-\section{Experiment Results} \label{sec:results}
 	\subsection{Deterministic Counterparts}
@@
 
+\section{Experimental Results} \label{sec:results}
+
 \bibliographystyle{plain}

### 2018-08-03 Writeup/PERT_New.tex
Updated the test_Ext_time

@@
 \newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{assumption}{Assumption}
 \newtheorem{conjecture}[theorem]{Conjecture}
@@
 The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
-	\textcolor{blue}{Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
+	\textcolor{blue}{NP-hardness proof. Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
 
@@
 		(S^\omega) \qquad f^\omega(\hat{t},\hat{x}) = \min \quad & t_T \\
-		& H^\omega + G_i M \geq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:sG1}\\
-		& H^\omega - (1 - G_i) M \leq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:sG2}\\
-		& t_i + G_i M_t \geq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:stG1}\\
-		& t_i - G_i M_t \leq \hat{t}_i \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:stG2}\\
-		& x_{ij} + G_i \geq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sxG1}\\
-		& x_{ij} - G_i \leq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sxG2}\\
+		& H^\omega + G_i M \geq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:sG1}\\
+		& H^\omega - (1 - G_i) M \leq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:sG2}\\
+		& t_i + G_i M_t \geq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:stG1}\\
+		& t_i - G_i M_t \leq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:stG2}\\
+		& x_{ij} + G_i \geq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sxG1}\\
+		& x_{ij} - G_i \leq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sxG2}\\
 		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij} \nonumber \\ 
-		& \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:subSep}\\
-		& \sum_{j \in J_i} x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:subBudget1}\\
+		& \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:subSep}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1 \qquad \qquad \forall \,i \in I \label{cons:subBudget1}\\
 		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij} \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:subBudget}\\
-		& z_{ij} \leq G_i \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize1}\\
-		& z_{ij} \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize2}\\
-		& z_{ij} \geq G_i + x_{ij} - 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:sublinearize3}\\
-		& t_i \geq H^\omega G_i \qquad \qquad \forall\, i \in I, \omega \in \Omega \\
-		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
-		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
-		& G_i \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega. \label{cons:subInt}
+		& z_{ij} \leq G_i \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sublinearize1}\\
+		& z_{ij} \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sublinearize2}\\
+		& z_{ij} \geq G_i + x_{ij} - 1 \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sublinearize3}\\
+		& t_i \geq H^\omega G_i \qquad \qquad \forall\, i \in I \label{cons:subH}\\
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
+		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
+		& G_i \in \{0,1\}. \qquad \qquad \forall \,i \in I. \label{cons:subInt}
 		\end{align}
@@
 We observe that a smaller \(M\) yields a tighter gap between the upper bound and the lower bound, because we can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
-	\begin{equation}
+	\begin{equation} \label{cons:Grange}
 		(\hat{t}_i - H^\omega)/M \leq G_i \leq (\hat{t}_i - H^\omega)/M + 1
@@
 	\begin{definition}
-		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}\), which is an ordered set of two-element tuples \((\bar{\omega}^q,\underbar{\omega}^q)\), which is indexed by \(q \in \mathcal{Q}\) and corresponds to the upper bound scenario index and the lower bound scenario index.
+		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}_i\), which is an ordered set of two-element tuples \((\underbar{\omega}^q,\bar{\omega}^q)\), indexed by \(q \in \mathcal{Q}_i\) and corresponds to the upper bound scenario index and the lower bound scenario index.
 The partition has the following properties:
@@
 			\item \(\underbar{\omega}^1 = 0\)
-			\item \(\bar{\omega}^{|\mathcal{Q}|} = T_{\max}\)
+			\item \(\bar{\omega}^{|\mathcal{Q}_i|} = T_{\max}\)
 			\item \(\bar{\omega}^q = \underbar{\omega}^{q + 1}\).
@@
 	\end{figure}
-	Here we present the modified master problem and subproblems with the addition of partition:
+	\noi For each activity \(i \in I\), with the partition \(\mathcal{P}_i\) defined, we can see the starting time \(t_i\) of the master problem lies in the range specified by one element of \(\mathcal{P}_i\).
+We introduce an indicator \(y_i^q\), \(\forall i \in I, q \in \mathcal{Q}_i\) in the first stage:
+	\begin{equation}
+		y_i^q = \begin{cases}
+			1 & \text{if \(t_i \in [H^{\underbar{\omega}^q},H^{\bar{\omega}^q}]\)}\\
+			0 & \text{otherwise}
+		\end{cases}
+		\qquad \forall i \in I, q \in \mathcal{Q}_i,
+	\end{equation}
+	and we use the following constraints to represent this relationship:
+	\begin{subequations} \label{cons:yCons}
+		\begin{align}
+			& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
+			& \sum_{q \in \mathcal{Q}_i} y_i^q = 1 \qquad \qquad \forall i \in I. \label{cons:sumy1}
+		\end{align}
+	\end{subequations}
+	In constraint~\eqref{cons:sumy1}, we enforce that \(t_i\) can only lie in one of the ranges specified by the partition, as only one of \(y_i^q\) can take value \(1\) for each \(i \in I\).
+Depending on the value of \(y_i^q\), we can write the bounds of the such range as in~\eqref{cons:tyBounds}.
+\\
+	\newline
+	The benefit of setting up the \(y\) variables is to obtain tighter bounds for \(t_i\) than the generic bounds \([0,T_{\max}]\) in Proposition~\ref{prop:bounds}.
+Suppose solving the master problem provides a solution \(\hat{y}_i^{\tilde{q}}, \forall i \in I, q \in \mathcal{Q}_i \).
+Then we can replace the big-\(M\) in constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} of the scenario with moderate \(M_i^{\omega,+}\) and \(M_i^{\omega,-}\) because introducing variables \(y\) gives us better bounds on \(t_i\):
+	\begin{subequations}
+		\begin{align}
+			& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega\\
+			& M_i^{\omega,-} = H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q，
+		\end{align}
+	\end{subequations}
+	and the constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} become:
+	\begin{subequations} \label{cons:newBoundsm}
+		\begin{align}
+			H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
+			H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
+		\end{align}
+	\end{subequations}
+	The multiplication of \(G_i \hat{y}_i^q\) makes the dual of subproblem no longer linear of \(y\).
+To fix this, since \(\hat{y}_i^q\) is binary and \(G_i\) for all \(i \in I, q \in \mathcal{Q}_i\), we can introduce variables \(F_i^q\) to linearize the bilinear term and rewrite constraints~\eqref{cons:newBoundsm} as follows:
+	\begin{subequations} \label{cons:newBoundsmlin}
+		\begin{align}
+			H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
+			G_i H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
+			F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin1}\\
+			F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin2}\\
+			F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:FGlin3}
+		\end{align}
+	\end{subequations}
+	In the subproblem, for each activity \(i \in I\), there is only one \(\hat{q} \in \mathcal{Q}_i\) such that \(\hat{y}_i^{\hat{q}} = 1\), which means \(\hat{t}_i \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\).
+We examine the validity and effectiveness result of these tightened constraints.
+For validity, we check if constraints~\eqref{cons:newBoundsm} matches the logic when \(G_i\) is binary, while for effectiveness, we need to compare the feasible range of \(G\) in constraints~\eqref{cons:Grange} and that specified by constraints~\eqref{cons:newBoundsm}.
+\\
+	\newline
+	For a specific \(i \in I\), constraints~\eqref{cons:newBoundsm} can be rewritten using \(\hat{q}\):
+	\begin{subequations} \label{cons:sGnew}
+		\begin{align}
+		H^\omega + G_i \left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right) \geq \hat{t}_i \label{cons:sGnew1}\\
+		H^\omega - (1 - G_i) \left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) \leq \hat{t}_i. \label{cons:sGnew2}
+		\end{align}
+	\end{subequations}
+	For a scenario \(\omega \in \Omega\), there are three possible positions of \(H^\omega\) relative to this range with \(\hat{y}_i^{\hat{q}} = 1\): \(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\), \(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\), or \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\).
+When \(G_i = 1\), the left-hand side of constraint~\eqref{cons:sGnew1} is \(H^{\bar{\omega}^{\hat{q}}}\) and the left-hand side of constraint~\eqref{cons:sGnew2} is \(H^\omega\).
+When \(G_i = 0\), the left-hand side of constraint~\eqref{cons:sGnew1} is \(H^\omega\), and the left-hand side of constraint~\eqref{cons:sGnew2} is \(H^{\underbar{\omega}^{\hat{q}}}\).
+	\begin{enumerate}
+		\item 
+			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}})\): we can see that if \(\hat{t}_i \geq H^\omega\), by logic \(G_i\) should take value \(1\).
+Constraints~\eqref{cons:sGnew} match \(\hat{t}_i \geq H^\omega\) for \(G_i = 1\) and is violated for \(G_i = 0\).
+Similar validity results hold if \(\hat{t}_i < H^\omega\).
+In addition, the possible value \(G_i\) can take changes from the one shown in~\eqref{cons:Grange} to:
+			\begin{equation*}
+			\left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right) \leq G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1
+			\end{equation*}
+			Since the value of \(M\) decreases compared to constraints~\eqref{cons:Grange}, when \(\hat{t}_i \geq H^\omega\), the lower bound increases and upper bound is \(1\).
+When \(\hat{t}_i < H^\omega\), the upper bound decreases and the lower bound is \(0\).
+Therefore, the feasible range of \(G_i\) for each \(i \in I\) shrinks, which achieves the goal to tighten the subproblem relaxation.
+		\item 
+			\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): we can see \(G_i = 1\) is feasible and \(G_i = 0\) violates constraint~\eqref{cons:sGnew1}. The possible value \(G_i\) can take becomes:
+			\begin{align*}
+			G_i \geq \left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right)\\
+			G_i \geq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1.
+			\end{align*}
+			Similar to Case 1, the lower bound increases compared to using a large \(M\) and the upper bound is \(1\), and we achieve a tightened relaxation.
+		\item 
+			\(H^\omega \geq H^{\bar{\omega}^{\hat{q}}}\): we can see \(G_i = 0\) is feasible and \(G_i = 1\) violates constraint~\eqref{cons:sGnew2}. The possible value \(G_i\) can take becomes:
+			\begin{align*}
+			G_i \leq \left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right)\\
+			G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1.
+			\end{align*}
+			Similar to Case 1, the upper bound decreases compared to using a large \(M\) and the lower bound is \(0\), and we achieve a tightened relaxation.
+	\end{enumerate}
+	The tightened constraints~\eqref{cons:newBoundsm} is shown to have validity and effectiveness properties.
+However, for the latter two situations, \(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\) and \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\), \(G_i\) can still take fractional value.
+We further tighten the formulation by adding two constraints involving \(y\), such that if the subproblems belonging to those two situations, \(G_i\) can be fixed as either \(0\) or \(1\).
+For scenario \(\omega \in \Omega\), suppose solving the master problem provides the solution \(\hat{y}_i^q, \forall i \in I, q \in \mathcal{Q}_i\), we have:
+		\begin{equation}\label{cons:subyG}
+			\sum_{q \in \mathcal{Q}_i, H^\omega < H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
+		\end{equation}
+	Again we check the validity and the effectiveness result of constraints~\eqref{cons:subyG} for the three situations listed above:
+	\begin{enumerate}
+		\item 
+			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}})\): the lower bound is \(0\) since \(y_i^q = 0\) for all elements of partition left of \(\hat{q}\), and the upper bound is \(1\) because \(y_i^q = 0\) for all elements of partition right of \(\hat{q}\).
+Therefore, \(0 \leq G_i \leq 1\) is valid.
+		\item 
+			\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): the lower bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega < H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 1\).
+This matches the logic since \(\hat{t}_i \geq H^\omega\).
+		\item 
+			\(H^\omega \geq H^{\bar{\omega}^{\hat{q}}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
+This matches the logic since \(\hat{t}_i \leq H^\omega\).
+	\end{enumerate}
+	With the addition of constraints~\eqref{cons:newBoundsmlin} and~\eqref{cons:subyG} in the subproblems, we present the tightened version of subproblems as follows: 
+	\begin{subequations}
+		\label{prob:subTightened}
+		\begin{align}
+		(S_P^\omega) \qquad \min \quad & t_T \\
+		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
+		& G_i H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
+		& F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin1t}\\
+		& F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin2t}\\
+		& F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:sFGlin3t}\\
+		& G_i \geq \sum_{q \in \mathcal{Q}_i, H^\omega < H^{\underbar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
+		& G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG2t}\\
+		& \text{Constraints~\eqref{cons:stG1}-\eqref{cons:subH}}\\
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
+		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
+		& 0 \leq G_i \leq 1. \qquad \qquad \forall \,i \in I. \label{cons:G01t}
+		\end{align}
+	\end{subequations}
+	Suppose we solve the subproblems \((S_P^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\):
+	\begin{equation} \label{cons:cut}
+		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
+	\end{equation}
+	Since the subproblem is a linear relaxation, \(\theta^\omega\) is a lower approximation of \(f^\omega\) for the current partition.
+However, since the validity result depends on the current partition, the cut needs to be modified once the partition is updated to retain the validity result.
+We assume that the update only refines the partition for each \(i \in I\):
+	\begin{assumption}
+		For two partitions \(\mathcal{P}^1_i\) and \(\mathcal{P}^2_i\), indexed by \(\mathcal{Q}^1_i\) and \(\mathcal{Q}^2_i\) respectively, where \(\mathcal{P}^2_i\) is used in a later iteration than \(\mathcal{P}^1_i\), we have:
+		\begin{equation*}
+		\forall q^2 \in \mathcal{Q}^2_i, \exists q^1 \in \mathcal{Q}^1_i \text{ s.t. } \bar{\omega}^{q^1} \geq \bar{\omega}^{q^2} \text{ and } \underbar{\omega}^{q^1} \leq \underbar{\omega}^{q^1}.
+		\end{equation*}
+	\end{assumption}
+	\noi Suppose at the current iteration for each \(i \in I\), the partition is \(\mathcal{P}_i\) indexed by \(\mathcal{Q}_i\), cut~\eqref{cons:cut} can be updated to:
+	\begin{align} \label{cons:updatedcut}
+		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
+		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber\\
+		& \qquad \forall \ell = 1,2, \dots,
+	\end{align}
+	and we prove the validity of this updated cut:
+	\begin{proposition}
+		With constraint~\eqref{cons:updatedcut}, \(\theta^\omega\) is a valid lower approximation of \(f^\omega\) for all \(\omega \in \Omega\).
+	\end{proposition}
+	\begin{proof}
+		content...
+	\end{proof}
+	\noi Here we present the modified master problem with valid cuts~\eqref{cons:updatedcut}:
 	\begin{subequations}
@@
 		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MpSingleBudget}\\
+		& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I\\
 		& \sum_{q \in \mathcal{Q}_i} y^q_i = 1 \qquad \qquad \forall i \in I \\
-			& \sum_{q \in \mathcal{Q}_i} \underbar{H}_i^{q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} \bar{H}_i^{q} y_i^{q} \qquad \qquad \forall i \in I\\
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
@@
 	\textcolor{blue}{
-		Proof of NP-hard.\\
-		Proof of validity of tighter cuts: strengthened Benders cuts.\\
-		Proof of increasing-decreasing behavior.
-	}
+	\begin{itemize}
+		\item algorithm
+		\item end points of each partition
+		\item proof of convergence if we have \(y_i^q\) for every \(\omega\)
+	\end{itemize}}
 	\begin{comment}

### 2018-08-03 src/master.jl

@@ -223,56 +223,12 @@ function createMaster_Div(pData,disData,Ω,divSet,divDet,cutSet,Tmax)
         H[ω] = disData[ω].H;
     end
 
-    mp = Model(solver = GurobiSolver(IntFeasTol = 1e-9,FeasibilityTol = 1e-9));
+    mp = Model(solver = GurobiSolver(IntFeasTol = 1e-9,FeasibilityTol = 1e-9,OutputFlag = 0));
     @variables(mp, begin
       θ[Ω] >= 0
       0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
       t[i in pData.II] >= 0
       y[i in pData.II, par in 1:length(divSet[i])], Bin
-    end);
-    @constraint(mp, budgetConstr, sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B);
-    @constraint(mp, durationConstr[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]]*(1-sum(pData.eff[k[1]][j]*x[k[1],j] for j in pData.Ji[k[1]])));
-    @constraint(mp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
-    @constraint(mp, tub[i in pData.II], t[i] <= sum(H[divSet[i][par].endH]*y[i,par] for par in 1:length(divSet[i])));
-    @constraint(mp, tlb[i in pData.II], t[i] >= sum(H[divSet[i][par].startH]*y[i,par] for par in 1:length(divSet[i])));
-    @constraint(mp, yConstr[i in pData.II], sum(y[i,par] for par in 1:length(divSet[i])) == 1);
-    @constraint(mp, yLimit[i in pData.II, par in 1:length(divSet[i]); divDet[i][par] != 0], y[i,par] == 0);
-    @objective(mp, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
-
-    # add the cut
-    # cutInfo = 2 dimensional vector, first dimention record the primal solution,
-    # second dimension record the dual solution for every scenario
-    for nc in 1:length(cutSet)
-        for ω in Ω
-            if cutSet[nc][2][ω] != []
-                # if there is a cut for scenario ω in iteration nc
[…]

### 2018-08-03 src/runExpr.jl

@@ -1,1 +1,0 @@
-function runExp(pInputAdd,kInputAdd,ϕInputAdd,dHName,dHParam,dPName,dPParam,)

### 2018-08-03 src/test_Ext_time.jl

@@ -26,7 +26,7 @@ kInputAdd = "/home/haoxiang/PERT_tests/14_ExponentialD_LogNormalH/test_14_K.csv"
 pData = readInP(pInputAdd,kInputAdd);
 nameD,dparams = readInUnc(ϕInputAdd);
 disData,Ω = autoUGen("LogNormal",[log(35),0.5],nameD,dparams,500,1 - pData.p0);
-disData = orderdisData(disData,Ω
+disData = orderdisData(disData,Ω);
 
 text,xext,fext,gext,mp = extForm_cheat(pData,disData,Ω,999999);
 ubmp = mp.objVal;

### 2018-08-06 Writeup/PERT_New.tex
Update the extensive formulation

@@
 		\begin{align}
-		(M) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\
+		(M) \quad z^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\
 		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MSep}\\
@@
 		\begin{align}
-		(S_P^\omega) \qquad \min \quad & t_T \\
+		(S_P^\omega) \qquad v^\omega = \min \quad & t_T \\
 		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
@@
 	\end{subequations}
-	Suppose we solve the subproblems \((S_P^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\):
+	Suppose we solve the subproblems \((S_P^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\), where coefficients \(\pi,\lambda\) and \(\gamma\) can be calculated based on the dual variables obtained:
 	\begin{equation} \label{cons:cut}
-		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
+		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
 	\end{equation}
@@
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
-		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber\\
+		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, H^{\bar{\omega}^{\tilde{q}}} \leq H^{\bar{\omega}^{q,\ell}},H^{\underbar{\omega}^{\tilde{q}}} \geq H^{\bar{\omega}^{q,\ell}} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber\\
 		& \qquad \forall \ell = 1,2, \dots,
@@
 	\noi Here we present the modified master problem with valid cuts~\eqref{cons:updatedcut}:
-	\begin{subequations}
+	\begin{subequations} \label{prob:masterTightened}
 		\begin{align}
-		(M_P) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
+		(M_P) \quad z_P^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
 		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MpSep}\\
@@
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
-		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber \\
+		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber \\
 		& \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots\\
@@
 	\end{subequations}
+	The decomposition algorithm is presented as follows:
+	\begin{algorithm}
+		\caption{Decomposition algorithm for model~\eqref{prob:extensive}}
+		\label{alg:Cut}
+		\begin{algorithmic}[1]
+			\State Initialize with cut iteration number \(\ell := 0\), lower bound \(LB := 0\), upper bound \(UB := +\infty\), initial partition \(\mathcal{P}^\ell\) with its indexed set \(\mathcal{Q}^\ell\), and specified tolerance \(\epsilon > 0\) and \(\delta > 0\);
+			\While{\(\frac{UB - LB}{UB} > \epsilon\)} 
+			\State Solve master problem \((M_P)\) and obtain solution \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and optimal value \(z_{P}^*\);
+			\State Update \(LB = z_{P}^*\) if \(z_{P}^* > LB\);
+			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t},\hat{x})\). 
+			\State Calculate \(z^* = p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t},\hat{x})\) and update \(UB := z^*\) if \(z^* < UB\);
+			\State For each \(\omega \in \Omega\), solve problem \((S_P^\omega)\) given \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and obtain optimal value \(v^{\omega,\ell}\) and coefficients \(\pi^{\omega,\ell}, \lambda^{\omega,\ell}, \gamma^{\omega,\ell}\);
+			\If{\(z^*_P \geq p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
+			\State Obtain optimal value \(V^*\); 
+			\Else
+			\State Stop and return the status of infeasibility;
+			\EndIf
+			\vspace{0.1cm}
+			\EndWhile{\textbf{end while}}
+			\State Output \(V^*\) as a lower bound on the optimal value of model~\eqref{prob:extensive}, and output \(\hat{s}^{p,k}, \hat{s}^{q,k}\) as an \(\epsilon\)-feasible solution.
+		\end{algorithmic}
+	\end{algorithm}
+
 	\textcolor{blue}{

### 2018-08-22 Writeup/PERT_New.tex
Upload the expected model

--- 2018-08-03 Writeup/PERT_New.tex
@@
 Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
-For example, Sherali/Fracticelli, Sen/Higle, Ntaimo/Sen, Sherali/Zhu, Sen/Sherali, Gade/Kucukyavuz/Sen solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where disjunctive cuts or Gomory cuts are added.
+\textcolor{blue}{For example, Sherali/Fracticelli, Sen/Higle, Ntaimo/Sen, Sherali/Zhu, Sen/Sherali, Gade/Kucukyavuz/Sen solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where disjunctive cuts or Gomory cuts are added.
 Ahmed/Sun/Zou assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
 Caroe/Tind solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not optimistic.
+}
 	\begin{subequations}
@@
 		\item 
-			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}})\): we can see that if \(\hat{t}_i \geq H^\omega\), by logic \(G_i\) should take value \(1\).
+			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\): we can see that if \(\hat{t}_i \geq H^\omega\), by logic \(G_i\) should take value \(1\).
 Constraints~\eqref{cons:sGnew} match \(\hat{t}_i \geq H^\omega\) for \(G_i = 1\) and is violated for \(G_i = 0\).
@@
 		\item 
-			\(H^\omega \geq H^{\bar{\omega}^{\hat{q}}}\): we can see \(G_i = 0\) is feasible and \(G_i = 1\) violates constraint~\eqref{cons:sGnew2}. The possible value \(G_i\) can take becomes:
+			\(H^\omega > H^{\bar{\omega}^{\hat{q}}}\): we can see \(G_i = 0\) is feasible and \(G_i = 1\) violates constraint~\eqref{cons:sGnew2}. The possible value \(G_i\) can take becomes:
 			\begin{align*}
@@
 		\begin{equation}\label{cons:subyG}
-			\sum_{q \in \mathcal{Q}_i, H^\omega < H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
+			\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
 		\end{equation}
@@
 		\item 
-			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}})\): the lower bound is \(0\) since \(y_i^q = 0\) for all elements of partition left of \(\hat{q}\), and the upper bound is \(1\) because \(y_i^q = 0\) for all elements of partition right of \(\hat{q}\).
+			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\): the lower bound is \(0\) since \(y_i^q = 0\) for all elements of partition left of \(\hat{q}\), and the upper bound is \(1\) because \(y_i^q = 0\) for all elements of partition right of \(\hat{q}\).
 Therefore, \(0 \leq G_i \leq 1\) is valid.
 		\item 
-			\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): the lower bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega < H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 1\).
+			\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): the lower bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 1\).
 This matches the logic since \(\hat{t}_i \geq H^\omega\).
 		\item 
-			\(H^\omega \geq H^{\bar{\omega}^{\hat{q}}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
+			\(H^\omega > H^{\bar{\omega}^{\hat{q}}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
 This matches the logic since \(\hat{t}_i \leq H^\omega\).
@@
 		\begin{align}
-		(S_P^\omega) \qquad \min \quad & t_T \\
+		(S_{\mathcal{P}}^\omega) \qquad g^\omega_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
 		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
@@
 		& F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:sFGlin3t}\\
-		& G_i \geq \sum_{q \in \mathcal{Q}_i, H^\omega < H^{\underbar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
+		& G_i \geq \sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
 		& G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG2t}\\
@@
 	\end{subequations}
-	Suppose we solve the subproblems \((S_P^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\):
+	Suppose we solve the subproblems \((S_{\mathcal{P}}^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\), where coefficients \(\pi,\lambda\) and \(\gamma\) can be calculated based on the dual variables obtained:
 	\begin{equation} \label{cons:cut}
-		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
+		\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
 	\end{equation}
@@
 We assume that the update only refines the partition for each \(i \in I\):
-	\begin{assumption}
-		For two partitions \(\mathcal{P}^1_i\) and \(\mathcal{P}^2_i\), indexed by \(\mathcal{Q}^1_i\) and \(\mathcal{Q}^2_i\) respectively, where \(\mathcal{P}^2_i\) is used in a later iteration than \(\mathcal{P}^1_i\), we have:
+	\begin{definition} \label{definition:refinement}
+		For two partitions \(\mathcal{P}^1_i\) and \(\mathcal{P}^2_i\), indexed by \(\mathcal{Q}^1_i\) and \(\mathcal{Q}^2_i\) respectively, where \(\mathcal{P}^2_i\) is a refinement of \(\mathcal{P}^1_i\), we have:
 		\begin{equation*}
@@
 		\end{equation*}
-	\end{assumption}
-	\noi Suppose at the current iteration for each \(i \in I\), the partition is \(\mathcal{P}_i\) indexed by \(\mathcal{Q}_i\), cut~\eqref{cons:cut} can be updated to:
+	\end{definition}
+	\noi Suppose at the current iteration for each \(i \in I\), the partition is \(\mathcal{P}_i\) indexed by \(\mathcal{Q}_i\), and this partition is updated from past partitions by only a sequence of refinement defined in Definition~\ref{definition:refinement}, cut~\eqref{cons:cut} can be updated to the following form so that the \(y\) variable has a proper dimension matching the current partition:
 	\begin{align} \label{cons:updatedcut}
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
-		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber\\
-		& \qquad \forall \ell = 1,2, \dots,
+		& \qquad \sum_{i \in I} \sum_{\tilde{q} \in \mathcal{Q}^{\ell}_i} \gamma_{i,\tilde{q}}^{\omega,\ell} \left( \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }y_i^{q} - \hat{y}_i^{\tilde{q},\ell} \right) \qquad \forall \ell = 1,2, \dots.
 	\end{align}
-	and we prove the validity of this updated cut:
-	\begin{proposition}
-		With constraint~\eqref{cons:updatedcut}, \(\theta^\omega\) is a valid lower approximation of \(f^\omega\) for all \(\omega \in \Omega\).
+	We show that, given a partition, \(\mathcal{P}\), which is updated from sequential refinement, \(\mathcal{P}^\ell, \ell = 1,2,\dots\), the cut~\eqref{cons:updatedcut} is a valid lower approximation for function \(g\):
+	\begin{proposition} \label{prop:validity}
+		Suppose we have a partition, \(\mathcal{P}\), which is indexed by sets \(\mathcal{Q}\), and the sequence of partitions, \(\{\mathcal{P}^\ell\}_{\ell = 1}\), each of which is indexed by sets \(\mathcal{Q}^\ell\).
+Assuming \(\mathcal{P}\) is a refinement of \(\mathcal{P}^\ell\) for every \(\ell = 1,2, \dots\), for any \(\omega \in \Omega\), we have
+		\begin{align} \label{cons:validlb}
+			&g^\omega_{\mathcal{P}}(t,x,y) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
+			& \qquad \qquad \sum_{i \in I} \sum_{\tilde{q} \in \mathcal{Q}^{\ell}_i} \gamma_{i,\tilde{q}}^{\omega,\ell} \left( \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }y_i^{q} - \hat{y}_i^{\tilde{q},\ell} \right) \qquad \forall \ell = 1,2, \dots.
+		\end{align}
+		at any given feasible \((t,x,y)\).
 	\end{proposition}
 	\begin{proof}
-		content...
+		We denote the recourse function corresponding to the partition \(\mathcal{P}^{\ell}\) as \(g^\omega_{\mathcal{P}^\ell}(t,x,y)\), where \(y\) has the correct dimension according to \(\mathcal{P}^\ell\).
+We first prove that
+		\begin{equation} \label{cons:gglb}
+			g^\omega_{\mathcal{P}}(t,x,y) \geq g^{\omega}_{\mathcal{P}^\ell}(t,x,\tilde{y}) \qquad \forall \ell = 1,2,\dots
+		\end{equation}
+		where \[\tilde{y}_i^{\tilde{q}} = \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }y_i^{q} \qquad  \forall i \in I, \tilde{q} \in \mathcal{Q}^\ell_i\]
+		Suppose for an \(\omega \in \Omega\) and a \((t,x,y)\), we solve the problem \(S_{\mathcal{P}}^\omega\) and obtain the optimal solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},F^{\omega,*})\).
+It is easy to see that by transforming \(F^{\omega,*}\) to \(\tilde{F}^{\omega,*}\) with \[\tilde{F}^{\omega,*,\tilde{q}}_i = \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }F_i^{\omega,*,q} \qquad  \forall i \in I, \tilde{q} \in \mathcal{Q}^\ell_i,\]
+		we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\).
+Therefore, inequality~\eqref{cons:gglb}.
+Furthermore, the cut generated at partition \(\mathcal{P}^\ell\) is
+		\[\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right),\]
+		 which means that for any feasible \((t,x,\tilde{y})\), we have 
+		 \begin{equation} \label{cons:validglb}
+		 	g^\omega_{\mathcal{P}^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
+		 \end{equation}
+		 By substituting \(\tilde{y}\) by \(y\) and combining inequalities~\eqref{cons:gglb} and~\eqref{cons:validglb}, we obtain the result of~\eqref{cons:validlb}.
 	\end{proof}
-	\noi Here we present the modified master problem with valid cuts~\eqref{cons:updatedcut}:
-	\begin{subequations}
+	\noi Proposition~\ref{prop:validity} states that if we perform a proper modification on the \(y\) variables to all cuts generated in the past, the modified cuts~\eqref{cons:updatedcut} will be a valid lower approximation for the current recourse function.
+Therefore, we incorporate the modified cuts~\eqref{cons:updatedcut} in our master problem, given a partition \(\mathcal{P}\) indexed by \(\mathcal{Q}\), which is shown as follows:
+	\begin{subequations} \label{prob:masterTightened}
 		\begin{align}
-		(M_P) \quad \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
+		(M_{\mathcal{P}}) \quad z_{\mathcal{P}}^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
 		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MpSep}\\
@@
 		& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I\\
-		& \sum_{q \in \mathcal{Q}_i} y^q_i = 1 \qquad \qquad \forall i \in I \\
+		& \sum_{q \in \mathcal{Q}_i} y^q_i = 1 \qquad \qquad \forall i \in I \label{cons:MpY1}\\
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
-		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_i^{\omega,q,\ell} \left( \sum_{\tilde{q} \in \mathcal{Q}_i, \bar{H}_i^{\tilde{q}} \leq \bar{H}_i^{\ell,q},\underbar{H}_i^{\tilde{q}} \geq \underbar{H}_i^{\ell,q} }y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \nonumber \\
+		&\qquad + \sum_{i \in I} \sum_{\tilde{q} \in \mathcal{Q}^{\ell}_i} \gamma_{i,\tilde{q}}^{\omega,\ell} \left( \sum_{q \in \mathcal{Q}_i, \bar{H}_i^{q} \leq \bar{H}_i^{\ell,\tilde{q}},\underbar{H}_i^{q} \geq \underbar{H}_i^{\ell,\tilde{q}} }y_i^{q} - \hat{y}_i^{\tilde{q},\ell} \right) \nonumber \\
 		& \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots\\
@@
 	\end{subequations}
-	\textcolor{blue}{
-	\begin{itemize}
-		\item algorithm
-		\item end points of each partition
-		\item proof of convergence if we have \(y_i^q\) for every \(\omega\)
-	\end{itemize}}
+	We can see that if we keep refining the partition, the generated cuts will become tighter and we will be able to provide an improving lower bound as it progresses.
+The decomposition algorithm is presented as follows:
+	\begin{algorithm}
+		\caption{Decomposition algorithm to solve problem~\eqref{prob:extensive}}
+		\label{alg:Cut}
+		\begin{algorithmic}[1]
+			\State Initialize with cut iteration number \(\ell = 0\), lower bound \(LB = 0\), upper bound \(UB = +\infty\), initial partition \(\mathcal{P}^\ell\) with its indexed set \(\mathcal{Q}^\ell\), and specified tolerance \(\epsilon > 0\) and \(\delta > 0\);
+			\While{\(\frac{UB - LB}{UB} > \epsilon\)} 
+			\State Solve master problem \((M_{\mathcal{P}})\) and obtain solution \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and optimal value \(z_{P}^*\);
+			\If{\(z_{P}^* > LB\)}
+			\State Update \(LB = z_{P}^*\);
+			\EndIf
+			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t},\hat{x})\). 
+			\State Calculate \(z^* = p^0 \hat{t}^\ell_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^\ell,\hat{x}^\ell)\)
+			\If{\(z^* < UB\)} 
+			\State Update \(UB := z^*\) and record the best incumbent solution as \(t^* = \hat{t}^\ell, x^* = \hat{x}^\ell\) and \(y^* = \hat{y}^\ell\);
+			\EndIf
+			\State For each \(\omega \in \Omega\), solve problem \((S_{\mathcal{P}}^\omega)\) given \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and obtain optimal value \(v^{\omega,\ell}\) and coefficients \(\pi^{\omega,\ell}, \lambda^{\omega,\ell}, \gamma^{\omega,\ell}\);
+			\If{\(z^*_P < p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
+			\State Add the cuts of form~\eqref{cons:cut} to the master problem;
+			\State Keep \(\mathcal{P}^{\ell + 1} = \mathcal{P}^\ell\) and \(\mathcal{Q}^{\ell + 1} = \mathcal{Q}^\ell\); 
+			\State Update \(\ell = \ell + 1\);
+			\Else
+			\State Refine the partition and obtain the new partition \(\mathcal{P}^{\ell + 1}\) and its indexed sets \(\mathcal{Q}^{\ell + 1}\);
+			\State Update \(\ell = \ell + 1\);
+			\State Update the previously generated cuts in the master problem to the form of~\eqref{cons:updatedcut};
+			\EndIf
+			\vspace{0.1cm}
+			\EndWhile{\textbf{end while}}
+			\State Output \(UB\) as the optimal value of model~\eqref{prob:extensive}, and \(t^*, x^*,y^*\) as the optimal solution.
+		\end{algorithmic}
+	\end{algorithm}
+	Finally we prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
+Since every partition update is a refinement and we have a finite set of scenario \(\Omega\), we can prove the finite convergence of Algorithm~\ref{alg:Cut} as long as with the finest partition we reach the optimum of problem~\eqref{prob:extensive}.
+	\begin{proposition} \label{prop:finestPar}
+		If a partition \(\hat{\mathcal{P}}\) has indexed sets \(\hat{\mathcal{Q}}\) and for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), we have \[z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y),\]
+		where 
+		\begin{equation*}
+			\mathbb{X} = \left\{(t,x,y) \left| 
+			\begin{aligned}
+			& \eqref{cons:MpSep}-\eqref{cons:MpY1}\\ 
+			&y_i^q \in \{0,1\} \qquad \forall i \in I, q \in \hat{\mathcal{Q}}_i\\
+			& t_i \geq 0 \qquad \forall i \in I\\
+			& 0 \leq x_{ij} \leq 1 \qquad \forall i \in I, j \in J_i
+			\end{aligned}
+			\right. \right\}.
+		\end{equation*}
+	\end{proposition}
+	\begin{proof}
+		First we can consider the subproblem \((S_\mathcal{P}^\omega)\) as a partial linear relaxation of the original extensive formulation. So \(z^* \leq z^*_\mathcal{P}\) is automatically true.\\
+		\newline
+		Next we prove that, given the partition in Proposition~\ref{prop:finestPar}, we can construct a feasible solution, \((t^*,x^*,G^*)\), to the extensive formulation~\eqref{prob:extensive} with the same objective value from the optimal solution, \((\hat{t},\hat{x},\hat{y})\), to the problem
+		\[\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y).\]
+		Suppose for \(i \in I\), we denote the index of partition where \(y\) variable takes value \(1\) as \(q_i\).
+Since \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), either \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \leq H^{\underbar{\omega}^q}\}\) or \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \geq H^{\bar{\omega}^q}\}\) is true.
+Thus, constraints~\eqref{cons:syG1t} and~\eqref{cons:syG2t} enforce that \(G_i\) in the problem \((S_{\hat{\mathcal{P}}}^\omega)\) takes binary value because the right-hand side expressions of those two constraints must be \(0\) or \(1\) simultaneously.
+This means that although subproblems are linear programs, the integrality is implied.
+Therefore, when we obtain the optimal solution \(\hat{G}^\omega\) from solving problems \((S_{\hat{\mathcal{P}}}^\omega)\) for each \(\omega \in \Omega\), solution \((\hat{t},\hat{x},\hat{G})\) will be feasible for the extensive formulation because \((\hat{t},\hat{x},\hat{y}) \in \mathbb{X}\) and \(G\) variables satisfy the constraints~\eqref{cons:stG1}-\eqref{cons:subH} and binary constraints.
+This result is equivalent to \(z_{\hat{\mathcal{P}}}^* \geq z^*\).
+Combining the results above we conclude that \(z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y).\)
+	\end{proof}
+	\begin{theorem} \label{thm:converge}
+		Algorithm~\ref{alg:Cut} terminates in finite number of iteration for any \(\epsilon \geq 0\). 
+	\end{theorem}
+	\begin{proof}
+		From Proposition~\ref{prop:finestPar} we know that with the finest partition \(\hat{\mathcal{P}}\) where for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y)\) is equivalent to solving the extensive formulation.
+Since there are only finite number of scenarios, it takes finite number of steps of refinement to reach the finest partition.
+\\
+		\newline
+		For each subproblem, there is only a finite number of possible values of dual variables because each corresponds to one of the finitely many different bases.
+This means that, for any partition \(\mathcal{P}\), the recourse function \(g^\omega_{\mathcal{P}}\) can be represented by finitely many linear cuts.
+Therefore, in algorithm~\ref{alg:Cut}, only a finite number of cuts are added for a finite number of partitions before \(UB = z^*\) and \(LB = z^*_{\hat{\mathcal{P}}}\) is achieved, a.k.a.
+\(\frac{UB - LB}{UB} = 0\).
+	\end{proof}
 	\begin{comment}

### 2018-08-22 src/expModel.jl

@@ -1,0 +1,32 @@
+# script for two-stage expected time expected magnitude disruption program
+function expModel(pData,eH,ed,M = 9999999)
+    mp = Model(solver = GurobiSolver(IntFeasTol = 1e-9, TimeLimit = TL));
+
+    @variable(mp,t0[i in pData.II] >= 0);
+    @variable(mp,0 <= x0[i in pData.II, j in pData.Ji[i]] <= 1);
+    @variable(mp,t[i in pData.II] >= 0);
+    @variable(mp,0 <= x[i in pData.II, j in pData.Ji[i]] <= 1);
+    @variable(mp,G[i in pData.II], Bin);
+    @variable(mp,0 <= s[i in pData.II, j in pData.Ji[i]] <= 1);
+
+    @constraint(mp, FConstr[i in pData.II], eH - (1 - G[i])*M <= t0[i]);
+    @constraint(mp, GConstr[i in pData.II], eH + G[i]*M >= t0[i]);
+    @constraint(mp, tConstr1[i in pData.II], t[i] + G[i]*M >= t0[i]);
+    @constraint(mp, tConstr2[i in pData.II], t[i] - G[i]*M <= t0[i]);
+    @constraint(mp, tConstr3[i in pData.II], t[i] >= eH * G[i]);
+    @constraint(mp, xConstr1[i in pData.II, j in pData.Ji[i]], x[i,j] + G[i] >= x0[i,j]);
+    @constraint(mp, xConstr2[i in pData.II, j in pData.Ji[i]], x[i,j] - G[i] <= x0[i,j]);
+    @constraint(mp, durationConstr1[k in pData.K], t[k[2]] - t[k[1]] >= pData.D[k[1]] + ed[i][k[1]]*G[k[1]]
+                      - sum(pData.D[k[1]]*pData.eff[k[1]][j]*x[k[1],j] + ed[i][k[1]]*pData.eff[k[1]][j]*s[k[1],j] for j in pData.Ji[k[1]]));
+    @constraint(mp, durationConstr2[k in pData.K], t0[k[2]] - t0[k[1]] >= pData.D[k[1]]*(1 - sum(pData.eff[k[1]][j]*x0[k[1],j] for j in pData.Ji[k[1]])));
+    @constraint(mp, xConstr[i in pData.II], sum(x[i,j] for j in pData.Ji[i]) <= 1);
[…]

### 2018-09-10 src/convexify.jl
Fixed convexify typos and big-M

@@ -9,16 +9,16 @@ function solveLR(pData,dDω,cutSetω,tm,xm,M,returnDual = 0)
     @variable(sp, 0 <= s[i in pData.II,j in pData.Ji[i]] <= 1);
 
     # add the basic sub problem constraints
-    @constraint(sp, FCons[i in pData.II],dDω.H - (1 - G[i])*M[i] <= that[i]);
-    @constraint(sp, GCons[i in pData.II],dDω.H + G[i]*M[i] >= that[i]);
+    @constraint(sp, FCons[i in pData.II],dDω.H - (1 - G[i])*M <= that[i]);
+    @constraint(sp, GCons[i in pData.II],dDω.H + G[i]*M >= that[i]);
 
     # add the predecessors and the successors logic constraints
     @constraint(sp, GSuccessors[i in pData.II, k in pData.Succ[i]], G[i] <= G[k]);
 
     # add the basic sub problem constraints
     @constraint(sp, tGbound[i in pData.II],t[i] >= dDω.H*G[i]);
-    @constraint(sp, tFnAnt1[i in pData.II],t[i] + G[i]*M[i] >= that[i]);
-    @constraint(sp, tFnAnt2[i in pData.II],t[i] - G[i]*M[i] <= that[i]);
+    @constraint(sp, tFnAnt1[i in pData.II],t[i] + G[i]*M >= that[i]);
+    @constraint(sp, tFnAnt2[i in pData.II],t[i] - G[i]*M <= that[i]);
     @constraint(sp, xFnAnt1[i in pData.II, j in pData.Ji[i]],x[i,j] + G[i] >= xhat[i,j]);
     @constraint(sp, xFnAnt2[i in pData.II, j in pData.Ji[i]],x[i,j] - G[i] <= xhat[i,j]);
 
@@ -72,10 +72,10 @@ function solveLR(pData,dDω,cutSetω,tm,xm,M,returnDual = 0)
         λDict = Dict();
         for i in pData.II
             πDict[i] = getdual(FCons[i]) + getdual(GCons[i]) + getdual(tFnAnt1[i]) + getdual(tFnAnt2[i]) +
-                sum(getdual(cuts[nc])*cutSetω[nc][1][i] for nc in 1:length(cutSetω)));
[…]

### 2018-09-10 src/test_Ext_time.jl

@@ -27,12 +27,12 @@ kInputAdd = "/home/haoxiang/PERT_tests/14_ExponentialD_LogNormalH/test_14_K.csv"
 
 pData = readInP(pInputAdd,kInputAdd);
 nameD,dparams = readInUnc(ϕInputAdd);
-disData,Ω = autoUGen("LogNormal",[log(35),0.5],nameD,dparams,50,1 - pData.p0);
+disData,Ω = autoUGen("LogNormal",[log(35),0.5],nameD,dparams,5,1 - pData.p0);
 disData = orderdisData(disData,Ω);
 
 # deterministic solution
 tdet,xdet,fdet = detBuild(pData);
-ubdet = ubCal(pData,disData,Ω,xdet,tdet,999999);
+ubdet = ubCalP(pData,disData,Ω,xdet,tdet,999999);
 
 # expected solution
 eH = exp(log(35)+1/2*0.5^2);
@@ -45,7 +45,7 @@ for i in pData.II
     end
 end
 texp,xexp,fexp,Gexp,mexp = expModel(pData,eH,ed);
-ubexp = ubCal(pData,disData,Ω,xexp,texp,999999);
+ubexp = ubCalP(pData,disData,Ω,xexp,texp,999999);
 
 # our decomposition method
 tic();

### 2018-09-18 Writeup/PERT_New.tex
Fixed convexify typos and big-M
Added the header

@@
 The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
-	\textcolor{blue}{NP-hardness proof. Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }
+	\textcolor{blue}{NP-hardness proof.}
+	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.
 
@@
 \section{Experimental Results} \label{sec:results}
+%	\textcolor{blue}{Test results:
+%	\begin{itemize}
+%		\item Describe the test examples: where do they come from, number of nodes, how are they generated.
+%		\item Cite Sen's paper and describe the implementation.
+%		\item Results.
+%	\end{itemize}}
+	In this section, we address the following questions with our computational results:
+	\begin{enumerate}
+		\item What is the value of model~\eqref{prob:extensive} that takes account of randomness in both timing and magnitude of a disruption?
+In other words, what are other alternative solutions that are easier to obtain but possibly inferior?
+How does quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
+		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
+		\item What is the time improvement of Algorithm~\ref{alg:Cut} compared to solving extensive formulation~\eqref{prob:extensive} using state-of-the-art MIP solvers?
+Other algorithms solving 2SMIP with mixed binary recourse?
+	\end{enumerate}
+	We first introduce the PERT network used for test and distribution information used to characterize uncertainty in Section~\ref{subsec:example}.
+In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of solution to model~\eqref{prob:extensive} compared to the alternative ones.
+We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
+Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
+	\newline
+	All tests are run on a server with 20 Intel Xeon cores at 3.1 GHz and 256 GB of RAM.
+All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform.
+All linear programs and mixed integer programs are solved by Gurobi 8.01 \cite{gurobi2016} with default parameters.
 
+	\subsection{Test Cases Construction} \label{subsec:example}
+	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
+	In this section, we first construct a deterministic problem assuming no disruption occurs and three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
+	\subsection{Simulation Budget} \label{subsec:budget}
+	\subsection{Computational Performance} \label{subsec:time}
 \bibliographystyle{plain}

### 2018-09-18 src/header.jl

@@ -1,0 +1,23 @@
+# test sbb
+@everywhere using JuMP,Gurobi,CPLEX,Ipopt;
+@everywhere using Distributions,HDF5,JLD;
+
+@everywhere include("piecewiseU.jl");
+@everywhere include("def.jl");
+@everywhere include("readIn.jl");
+@everywhere include("master.jl");
+@everywhere include("sub.jl");
+@everywhere include("cuts.jl");
+@everywhere include("iSolve.jl");
+@everywhere include("tighten.jl");
+@everywhere include("branchFunc.jl");
+@everywhere include("detForm.jl");
+@everywhere include("extForm.jl");
+@everywhere include("expModel.jl");
+@everywhere include("ubCalFunc.jl");
+@everywhere include("tighten.jl");
+@everywhere include("partition_LP.jl");
+@everywhere include("partition_LR.jl");
+@everywhere include("part_tight.jl");
+@everywhere include("partitionSolve.jl");
+@everywhere include("convexify.jl");

### 2018-09-18 src/readIn.jl

@@ -1,4 +1,36 @@
-@everywhere include("piecewiseU.jl");
+function buildDistrn(nameDistr,paramDistr)
+    if nameDistr == "Exponential"
+        μ = paramDistr[1];
+        distrObj = Exponential(μ);
+    elseif nameDistr == "LogNormal"
+        μ = paramDistr[1];
+        σ = paramDistr[2];
+        distrObj = LogNormal(μ,σ);
+    elseif nameDistr == "Gamma"
+        α = paramDistr[1];
+        θ = paramDistr[2];
+        distrObj = Gamma(α,θ);
+    elseif nameDistr == "Uniform"
+        la = paramDistr[1];
+        ub = paramDistr[2];
+        distrObj = Uniform(la,ub+1e-10);
+    elseif nameDistr == "Normal"
+        μ = paramDistr[1];
+        σ = paramDistr[2];
+        distrObj = Normal(μ,σ);
+    elseif nameDistr == "PiecewiseU"
+        endPts = paramDistr[1];
+        mass = paramDistr[2];
+        distrObj = piecewiseUniformSampler(endPts,mass);
+    elseif nameDistr == "Singleton"
+        endPts = [paramDistr[1]];
+        mass = [1];
+        distrObj = piecewiseUniformSampler(endPts,mass);
+    end
+
+    return distrObj;
+end
+
 # This is the input function that reads in the project data
 function readInP(pInputAdd,kInputAdd)
     pRaw = readdlm(pInputAdd,',',header = false);
@@ -106,54 +138,11 @@ end
 function autoUGen(nameH, Hparams, nameD, dparams, Ωn, totalProb)
     disData = Dict();
     Ω = 1:Ωn;
-
-    if nameH == "Exponential"
-        μ = Hparams[1];
-        distrH = Exponential(μ);
-    elseif nameH == "LogNormal"
-        μ = Hparams[1];
-        σ = Hparams[2];
-        distrH = LogNormal(μ,σ);
-    elseif nameH == "Gamma"
-        α = Hparams[1];
-        θ = Hparams[2];
-        distrH = Gamma(α,θ);
-    elseif nameH == "Uniform"
-        la = Hparams[1];
-        ub = Hparams[2];
-        distrH = Uniform(la,ub+1e-10);
-    elseif nameH == "Normal"
-        μ = Hparams[1];
-        σ = Hparams[2];
-        distrH = Normal(μ,σ);
-    elseif nameH == "PiecewiseU"
[…]

### 2018-09-23 Writeup/PERT_New.tex
Added the master pruning cuts

@@
 Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
-\textcolor{blue}{For example, Sherali/Fracticelli, Sen/Higle, Ntaimo/Sen, Sherali/Zhu, Sen/Sherali, Gade/Kucukyavuz/Sen solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where disjunctive cuts or Gomory cuts are added.
-Ahmed/Sun/Zou assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
-Caroe/Tind solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not optimistic.
-}
+For example, Gade et al.
+\cite{gade2014decomposition} solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where Gomory cuts are added.
+Ahmed et al.
+\cite{zou2016nested} assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
+Car{\o}e and Tind \cite{caroe1998shaped} solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not verified.
+Qi and Sen \cite{qi2017ancestral} have mixed integer variables in both the master and the recourse problems.
+Parametric disjunctive cuts, derived in Chen et al.
+\cite{chen2012computational}, are generated to convexify recourse problems while Benders' cuts approximate recourse value functions.
+\textcolor{blue}{Although this method suits our problem settings, we implement it only to find that it does not converge in a reasonable time frame.} Therefore, we propose a new decomposition method that utilizes the special structure of our problem.
+\\
+	\newline
+	We first rewrite the extensive formulation into a master problem \((M)\) and a set of recourse problems \((S^\omega)\), \(\omega \in \Omega\):
+	%The recourse problem becomes a linear program as long as we can determine the temporal relationship between each activity and the disruption, and an early determination of the value of \(G\) help accelerate the decomposition process.
 	\begin{subequations}

### 2018-09-23 src/convexify.jl

@@ -397,7 +397,7 @@ function convexify(pData,disData,Ω,Tmax,Tmax1,nTree,ϵ = 1e-2,cutLim = 100)
     end
 
     LBList = [];
-    while !(stopBool)
+    while (!(stopBool))&(length(LBList) <= 20)
         # solve the master problem and obtain the master solution
         solve(mp);
         tm = Dict();

### 2018-09-23 src/partitionSolve.jl

@@ -80,6 +80,10 @@ function partitionSolve(pData,disData,ϵ = 0.01,tightenBool = 0)
             mp = updateMaster(mp,ubInfo,lbInfo);
             divSet,divDet = revisePar(pData,disData,divSet,divDet,ubInfo,lbInfo);
             mp = createMaster_Div(pData,disData,Ω,divSet,divDet,cutSet,Tmax);
+        elseif tightenBool == 2
+            mpTemp = copy(mp);
+            divDet = obtainDet(pData,disData,Ω,mpTemp,ub,divSet,divDet);
+            mp = createMaster_Div(pData,disData,Ω,divSet,divDet,cutSet,Tmax);
         end
         while keepIter
             solve(mp);

### 2018-09-23 src/test_Ext_time.jl

@@ -1,9 +1,14 @@
 addprocs(20);
+@everywhere using JuMP,Gurobi,CPLEX,Ipopt;
+@everywhere using Distributions,HDF5,JLD;
 # test sbb
 @everywhere include("header.jl");
 
-filePath = "/Users/haoxiangyang/Desktop/PERT_tests/14_ExponentialD_LogNormalH/"
-pData,disDataSet = genData(filePath,5);
+#filePath = "/Users/haoxiangyang/Desktop/PERT_tests/14_ExponentialD_LogNormalH/"
+filePath = "/home/haoxiang/PERT_tests/14";
+Ωsize = 5;
+Ω = 1:Ωsize;
+pData,disDataSet = genData(filePath,Ωsize);
 disData = disDataSet[1];
 
 # deterministic solution

### 2018-09-23 src/tighten.jl

@@ -320,3 +320,20 @@ function longestPath(pData)
     end
     return lDict;
 end
+
+function obtainDet(pData,disData,Ω,mpTemp,ub,divSet,divDet)
+    # predetermine some y's data
+    @constraint(mpTemp,pData.p0*mpTemp[:t][0] + sum(disData[ω].prDis*mpTemp[:θ][ω] for ω in Ω) <= ub);
+    for i in pData.II
+        # fix the y[i,par] to be 1 and solve the problem, if infeasible, then y[i,par] has to be 0
+        for par in 1:length(divSet[i])
+            mpTTemp = copy(mpTemp);
+            @constraint(mpTTemp,y[i,par] == 1);
+            mpStatus = solve(mpTTemp);
+            if mpStatus == :Infeasible
+                divDet[i,par] = -1;
+            end
+        end
+    end
+    return divDet;
+end

### 2018-09-29 src/readIn.jl
Change the data generation output

@@ -270,7 +270,7 @@ function genData(filePath,Ωsize,dataSize = 1,pName = "test_P.csv",kName = "test
         push!(disDataSet,disData);
     end
     if saveOpt == 0
-        return pData,disDataSet,dparams,Hparams;
+        return pData,disDataSet,nameD,nameH,dparams,Hparams;
     else
         save("test.jld","pData",pData,"disDataSet",disDataSet);
     end

### 2018-09-29 src/test_Ext_time.jl

@@ -8,7 +8,7 @@ addprocs(20);
 filePath = "/home/haoxiang/PERT_tests/14";
 Ωsize = 500;
 Ω = 1:Ωsize;
-pData,disDataSet,dparams,Hparams = genData(filePath,Ωsize);
+pData,disDataSet,nameD,nameH,dparams,Hparams = genData(filePath,Ωsize);
 disData = disDataSet[1];
 
 # deterministic solution
@@ -30,13 +30,13 @@ ubexp = ubCalP(pData,disData,Ω,xexp,texp,999999);
 
 # our decomposition method
 tic();
-tbest,xbest,lbCost,ubCost = partitionSolve(pData,disData,0.001);
+tbest,xbest,lbCost,ubCost = partitionSolve(pData,disData,0.01);
 timedecomp = toc();
 gapdecomp = (ubCost - lbCost)/ubCost;
 
 # extensive formulation
 tic();
-text,xext,fext,gext,mext = extForm_cheat(pData,disData,Ω,1e-2,999999);
+text,xext,fext,gext,mext = extForm_cheat(pData,disData,Ω,1e-4,999999);
 timeext = toc();
 θext = Dict();
 for ω in Ω
@@ -54,10 +54,10 @@ save("test_Ext_time.jld","dDict",dDict);
 ############################################
 ubList = [];
 for n in 1:30
-    disData,Ω = autoUGen("LogNormal",[log(35),0.5],nameD,dparams,500,1 - pData.p0);
-    disData = orderdisData(disData,Ω);
-    ubdet = ubCal(pData,disData,Ω,xdet,tdet,999999);
-    ubexp = ubCal(pData,disData,Ω,xexp,texp,999999);
-    ubext = ubCal(pData,disData,Ω,xext,text,999999);
-    push!(ubList,[ubdet,ubexp,ubext]);
+    disData1,Ω = autoUGen("LogNormal",Hparams,"Exponential",dparams,500,1 - pData.p0);
+    disData1 = orderdisData(disData1,Ω);
+    ubdet1 = ubCalP(pData,disData1,Ω,xdet,tdet,999999);
+    ubexp1 = ubCalP(pData,disData1,Ω,xexp,texp,999999);
+    ubext1 = ubCalP(pData,disData1,Ω,xext,text,999999);
+    push!(ubList,[ubdet1,ubexp1,ubext1]);
 end

### 2018-10-26 Writeup/PERT_New_Oct_14.tex
Add the Wong Magnanti Dual cut

--- 2018-09-23 Writeup/PERT_New.tex
@@
 \renewcommand{\underbar}{\underaccent{\bar}}
-
-\bibliographystyle{plain}
 
@@
 The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
-	\textcolor{blue}{NP-hardness proof.}
 	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.
@@
 \cite{chen2012computational}, are generated to convexify recourse problems while Benders' cuts approximate recourse value functions.
-\textcolor{blue}{Although this method suits our problem settings, we implement it only to find that it does not converge in a reasonable time frame.} Therefore, we propose a new decomposition method that utilizes the special structure of our problem.
+Although this method suits our problem settings, we implement it only to find that it does not converge in a reasonable time frame.
+Therefore, we propose a new decomposition method that utilizes the special structure of our problem.
 \\
@@
 We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
-Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
+Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation.\\
 	\newline
@@
 	\subsection{Test Cases Construction} \label{subsec:example}
+	\textcolor{blue}{Where we find our tests:
+	\begin{itemize}
+		\item Plambeck paper: Case 11
+		\item V42: Case 14
+		\item Case 19 from Elmgrabhy
+		\item Case 55 from Elmgrabhy
+		\item Randomized network 100 nodes
+		\item Plambeck paper: Case 110
+	\end{itemize}}
+	\noi We construct our test cases based on the activity networks used in the previous literature.
 	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
@@
 	\subsection{Simulation Budget} \label{subsec:budget}
+	In this section, we show that a large sample size can lead to a significantly better solution compared to the one yielded by a small sample size.
+We also compare, with a finite budget on the number of samples, what budget allocation plan works the best in terms of the computational time and solution bias.
 	\subsection{Computational Performance} \label{subsec:time}
+	In this section, we show the computational advantage our method has compared to directly solving the extensive formulation.
 \bibliographystyle{plain}

### 2018-10-26 src/partSolve_Callback.jl

@@ -140,7 +140,8 @@ function partBenders(cb)
         end
     end
     push!(ubCostList,ubTemp);
-    dataList = pmap(ω -> sub_divT(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
+    #dataList = pmap(ω -> sub_divT(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
+    dataList = pmap(ω -> sub_divTDual(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
     for ω in Ω
         πdict[ω] = dataList[ω][1];
         λdict[ω] = dataList[ω][2];

### 2018-10-26 src/part_tight.jl

@@ -250,3 +250,111 @@ function findSuccAll(pData)
     end
     return allSucc;
 end
+
+function iniPart(pData,disData,Ω,sN,MM)
+    Tmax = disData[length(Ω)].H + longestPath(pData)[0];
+    H = Dict();
+    H[0] = 0;
+    H[length(Ω)+1] = Tmax;
+    for ω in Ω
+        H[ω] = disData[ω].H;
+    end
+
+    # sample sN scenarios and solve the small extensive formulation
+    tList = Dict();
+    for i in pData.II
+        tList[i] = [];
+    end
+    ubList = [];
+    for m in 1:MM
+        #randList = rand(Ω,sN);
+        disData1 = Dict();
+        Ω1 = 1:sN;
+        randList = [(ω - 1)*MM + m for ω in Ω1];
+        for i in Ω1
+            disData1[i] = deepcopy(disData[randList[i]]);
+            disData1[i].prDis = (1 - pData.p0)/length(Ω1);
+        end
+        text,xext,fext,gext,mext = extForm_cheat(pData,disData1,Ω1,1e-4,999999);
+        ubext = ubCalP(pData,disData,Ω,xext,text,999999);
+        push!(ubList,ubext);
+        for i in pData.II
+            push!(tList[i],text[i]);
+        end
+    end
+
+    # ubList = [];
+    # tList = Dict();
+    # for i in pData.II
+    #     tList[i] = [];
+    # end
+    # for m in 1:MM
+    #     disData1 = Dict();
+    #     Ω1 = (sN*(m - 1)+1):sN*m;
+    #     for i in 1:length(Ω1)
+    #         disData1[i] = disData[Ω1[i]];
+    #     end
+    #     text,xext,fext,gext,mext = extForm_cheat(pData,disData1,1:length(Ω1),1e-4,999999);
+    #     ubext = ubCalP(pData,disData,Ω,xext,text,999999);
+    #     push!(ubList,ubext);
+    #     for i in pData.II
+    #         push!(tList[i],text[i]);
+    #     end
+    # end
+
+    # return the min-max decomposition
+    tHList = [];
+    for i in pData.II
+        tHstart = maximum([ω for ω in keys(H) if H[ω] <= minimum(tList[i])]);
+        tHend = minimum([ω for ω in keys(H) if H[ω] >= maximum(tList[i])]);
+        push!(tHList,[i,tHstart,tHend]);
+    end
+    return ubList,HList;
[…]

### 2018-10-26 src/sub.jl

@@ -650,3 +650,164 @@ function sub_divT(pData,dDω,ωCurr,that,xhat,yhat,divSet,H,M,returnOpt = 0)
         return πdict,λdict,γdict,vk,sp;
     end
 end
+
+function sub_divTDual(pData,dDω,ωCurr,that,xhat,yhat,divSet,H,M,returnOpt = 0)
+    # solve the subproblem by dual formulation
+    sp = Model(solver = GurobiSolver(OutputFlag = 0));
+    @variable(sp, λFG1[i in pData.II, par in 1:length(divSet[i])] <= 0);
+    @variable(sp, λFG2[i in pData.II, par in 1:length(divSet[i])] <= 0);
+    @variable(sp, λFG3[i in pData.II, par in 1:length(divSet[i])] >= 0);
+    @variable(sp, λHG1[i in pData.II] <= 0);
+    @variable(sp, λHG2[i in pData.II] >= 0);
+    @variable(sp, λGy1[i in pData.II] >= 0);
+    @variable(sp, λGy2[i in pData.II] <= 0);
+    @variable(sp, λGG[k in pData.K] <= 0);
+    @variable(sp, λtG1[i in pData.II] >= 0);
+    @variable(sp, λtG2[i in pData.II] >= 0);
+    @variable(sp, λtG3[i in pData.II] <= 0);
+    @variable(sp, λxG1[i in pData.II, j in pData.Ji[i]] >= 0);
+    @variable(sp, λxG2[i in pData.II, j in pData.Ji[i]] <= 0);
+    @variable(sp, λsG1[i in pData.II, j in pData.Ji[i]] <= 0);
+    @variable(sp, λsG2[i in pData.II, j in pData.Ji[i]] <= 0);
+    @variable(sp, λsG3[i in pData.II, j in pData.Ji[i]] >= 0);
+    @variable(sp, λbudget <= 0);
+    @variable(sp, λxub[i in pData.II] <= 0);
+    @variable(sp, λdur[k in pData.K] >= 0);
+
+    tBool = Dict();
+    for i in pData.II
+        if i != 0
+            tBool[i] = 0;
+        else
+            tBool[i] = 1;
+        end
+    end
+
+    # t constraint
+    @constraint(sp, tConstr[i in pData.II], tBool[i] - λtG1[i] - λtG2[i] - λtG3[i] +
[…]

### 2018-10-26 src/test_time.jl

@@ -5,14 +5,13 @@ addprocs(20);
 @everywhere include("header.jl");
 
 #filePath = "/Users/haoxiangyang/Desktop/PERT_tests/75_Lognormal_Exponential/"
-filePath = "/home/haoxiang/PERT_tests/14_Lognormal_Exponential";
+filePath = "/home/haoxiang/PERT_tests/55_Lognormal_Exponential/";
 Ωsize = 500;
 Ω = 1:Ωsize;
 ϵ = 1e-2;
 pData,disDataSet,nameD,nameH,dparams,Hparams = genData(filePath,Ωsize);
-data = load("test_cuts.jld");
-disData = data["disData"];
-dataDet = load("test_Ext_time_exponential.jld");
+disData = disDataSet[1];
+
 allSucc = findSuccAll(pData);
 distanceDict = Dict();
 for i in pData.II

### 2018-11-02 Writeup/PERT_New.tex
Change the data generation output
Finish the test_value

@@
 	\subsection{Test Cases Construction} \label{subsec:example}
+	\textcolor{blue}{Where we find our tests:
+		\begin{itemize}
+			\item Plambeck paper: Case 11
+			\item V42: Case 14
+			\item Case 19 from Elmgrabhy
+			\item Case 55 from Elmgrabhy
+			\item Randomized network 75, 100 nodes
+			\item Plambeck paper: Case 110
+	\end{itemize}}
+	\noi Although it is easy to construct an activity network with randomly distributed disruption time and magnitude, not all instances constructed can well illustrate properties of our problem.
+Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value.
+We create one activity network with 14 activities and
 	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
-	In this section, we first construct a deterministic problem assuming no disruption occurs and three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
+	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling random timing and magnitude of the disruption.
+First, we can solve a deterministic problem assuming no disruption occurs.
+Next, we can  three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
 	\subsection{Simulation Budget} \label{subsec:budget}

### 2018-11-09 Writeup/PERT_New.tex
Change the solver to Cplex

--- 2018-09-23 Writeup/PERT_New.tex
@@
 In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\).
-For each scenario \(\\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\).
+For each scenario \(\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\).
 \\
@@
 We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
-Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
+Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation.\\
+	%  and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)
 	\newline
@@
 All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform.
-All linear programs and mixed integer programs are solved by Gurobi 8.01 \cite{gurobi2016} with default parameters.
+All linear programs and mixed integer programs are solved by \textcolor{blue}{CPLEX} with both the feasibility tolerance and the integrality tolerance as \(10^{-7}\).
+We refer interested readers to \textcolor{blue}{GitHub repository} for the input data and the code used in this paper.
+%Gurobi 8.01 \cite{gurobi2016}
 
 	\subsection{Test Cases Construction} \label{subsec:example}
+%	\textcolor{blue}{Where we find our tests:
+%		\begin{itemize}
+%			\item Plambeck paper: Case 11
+%			\item V42: Case 14
+%			\item Case 19 from Elmgrabhy
+%			\item Case 55 from Elmgrabhy
+%			\item Randomized network 75, 100 nodes
+%			\item Plambeck paper: Case 110
+%	\end{itemize}}
+	\noi Although it is easy to construct an activity network with randomly distributed disruption time and magnitude, not all instances constructed can well illustrate properties of our problem.
+Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value.
+We use two activity networks from \textcolor{blue}{Plambeck et al.}, one with 11 activities and the other with 110 activities.
+We also take two examples from Elmgrabhy \cite{Elmaghraby77}, one with 19 activities and the other with 55 activities.
+We manually create one activity network with 14 activities and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}.
+In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities.\\
+	\newline
+	For every test case, the timing of disruption follows a lognormal distribution since its value has to be nonnegative.
+The disruption magnitude of activities follows an exponential distribution of which the parameter differs among activities.
+The exponential distribution can best model the drastic change caused by a disruption.
+	\subsection{Simulation Budget} \label{subsec:budget}
+	We first examine the quality of solutions generated from different sizes of samples.
+It is well known that the objective value obtained by SAA approaches the objective function of the original problem as the sample size grows to infinity, and the expected value of the SAA objective value improves as the sample size increases~\cite{shapiro2009lectures}.
+However, when the sample size increases, the computational cost increases as well.
+Understanding how the solution quality changes according to different sample sizes is important to help us decide a proper sample size while achieving a decent solution.
+For each test case in Section~\ref{subsec:example}, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(n = 10, 50, 100, 200, 500\) and \(1000\).
+For each of those solutions, we test against a set of \(5000\) samples and obtain the object value.
+We compare the
 	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
-	In this section, we first construct a deterministic problem assuming no disruption occurs and three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
-	\subsection{Simulation Budget} \label{subsec:budget}
+	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling both the random timing and magnitude of the disruption.
+First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET").
+Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), the timing is random but the magnitude is at its expected value (denoted as ``\(H\)Only"), and the magnitude is random but the timing is at its expected value (denoted as ``\(d\)Only").
+Finally, we construct the full stochastic model where both the timing and the magnitude are random (denoted as ``FULL").
 	\subsection{Computational Performance} \label{subsec:time}

### 2018-11-09 src/detForm.jl

@@ -2,7 +2,8 @@
 
 function detBuild(pData)
     # build the deterministic crashing optimization problem
-    mp = Model(solver = GurobiSolver(OutputFlag = 0));
+    # mp = Model(solver = GurobiSolver(OutputFlag = 0));
+    mp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
     # mp = Model(solver = ClpSolver());
 
     @variable(mp, t[i in pData.II] >= 0);

### 2018-11-09 src/facilityTest.jl

@@ -1,0 +1,101 @@
+function masterFacility(f,c,d,M,I,J)
+    mp = Model(solver = GurobiSolver());
+    @variable(mp, x[i in I], Bin);
+    @variable(mp, θ >= 0);
+    @objective(mp, Min, sum(f[i]*x[i] for i in I) + θ);
+    return mp;
+end
+
+function subFacility(f,c,cz,d,M,I,J,xhat)
+    sp = Model(solver = GurobiSolver());
+    @variable(sp, 0 <= xs[i in I] <= 1);
+    @variable(sp, y[i in I,j in J] >= 0);
+    @variable(sp, z[j in J] >= 0);
+    @constraint(sp, supply[i in I], sum(y[i,j] for j in J) <= M[i]*xs[i]);
+    @constraint(sp, demand[j in J], sum(y[i,j] for i in I) + z[j] >= d[j]);
+    @constraint(sp, xeqn[i in I], xs[i] == xhat[i]);
+    @objective(sp, Min, sum(sum(c[i,j]*y[i,j] for j in J) for i in I) + sum(cz[j]*z[j] for j in J));
+
+    solve(sp);
+    πDict = Dict();
+    for i in I
+        πDict[i] = getdual(sp[:xeqn][i]);
+    end
+    v = getobjectivevalue(sp);
+    return πDict,v;
+end
+
+function addFacCuts(mp,πDict,v,xhat,I)
+    @constraint(mp, mp[:θ] >= v + sum(πDict[i]*(mp[:x][i] - xhat[i]) for i in I));
+    return mp;
+end
+
+function subFacility_Lag(f,c,cz,d,M,I,J,xhat,πCurr)
+    sp = Model(solver = GurobiSolver());
+    @variable(sp, 0 <= xs[i in I] <= 1);
+    @variable(sp, y[i in I,j in J] >= 0);
+    @variable(sp, z[j in J] >= 0);
+    @constraint(sp, supply[i in I], sum(y[i,j] for j in J) <= M[i]*xs[i]);
+    @constraint(sp, demand[j in J], sum(y[i,j] for i in I) + z[j] >= d[j]);
+    @objective(sp, Min, sum(sum(c[i,j]*y[i,j] for j in J) for i in I) + sum(cz[j]*z[j] for j in J) + sum(πCurr[i]*(xs[i] - xhat[i]) for i in I));
+
+    solve(sp);
+    v = getobjectivevalue(sp);
[…]

### 2018-11-09 src/master.jl

@@ -1,6 +1,6 @@
 function createMaster(pData,disData,Ω,Tmax = 999999)
-    mp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
-    #mp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
+    # mp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
+    mp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
     @variables(mp, begin
       θ[Ω] >= 0
       0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
@@ -31,8 +31,8 @@ function createMaster_Par(pData,disData,Ω,partCurrent,partDet,cutSet,M = 999999
 
     # partCurrent is a list of scenario arrays, each element is a partition of scenarios
     # cutSet includes the cuts generated
-    #mp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
-    mp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
+    mp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
+    # mp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
     @variables(mp, begin
       θ[Ω] >= 0
       0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
@@ -76,8 +76,8 @@ function createMaster_Mixed(pData,disData,Ω,ωInfo,cutSet,M = 9999999)
         H[ω] = disData[ω].H;
     end
     # cutSet includes the cuts generated
[…]

### 2018-11-09 src/partSolve_Callback_tightened_sol.jl

@@ -173,8 +173,8 @@ yhistList = [];
 ubList,tHList,ubInc,tInc,xInc,θInc = iniPart(pData,disData,Ω,sN,MM);
 
 # move the createMaster_Callback here
-mp = Model(solver = GurobiSolver(IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
-# mp = Model(solver = CplexSolver(CPX_PARAM_EPRHS = 1e-7,CPX_PARAM_EPINT = 1e-7));
+# mp = Model(solver = GurobiSolver(IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
+mp = Model(solver = CplexSolver(CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_EPINT = 1e-8));
 @variables(mp, begin
   θ[ω in Ω] >= 0
   0 <= x[i in pData.II,j in pData.Ji[i]] <= 1

### 2018-11-09 src/python/defType.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Oct 28 22:56:46 2018
+
+@author: haoxiangyang
+"""
+
+# define the variable type
+class pInfo:
+    def __init__(self, II, Ji, D, b, eff, B, p0, K, Pre, Succ):
+        self.II = II
+        self.Ji = Ji
+        self.D = D
+        self.b = b
+        self.eff = eff
+        self.B = B
+        self.p0 = p0
+        self.K = K
+        self.Pre = Pre
+        self.Succ = Succ
+        
+class disInfo:
+    def __init__(self, H, d, prDis):
+        self.H = H
+        self.d = d
+        self.prDis = prDis
+        
+class partType:
+    def __init__(self, startH, endH):
+        self.startH = startH
+        self.endH = endH

### 2018-11-09 src/python/detForm.py

@@ -1,0 +1,39 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Oct 28 22:55:59 2018
+
+@author: haoxiangyang
+"""
+
+# deterministic formulation
+from gurobipy import *
+
+def detBuild(pData):
+    # build the deterministic crashing optimization problem
+    mp = Model('deterministic')
+    mp.Params.OutputFlag = 0
+
+    t = mp.addVars(pData.II)
+    xInd = []
+    for i in pData.II:
+        for j in pData.Ji[i]:
+            xInd.append((i,j))
+    x = mp.addVars(xInd, ub = 1)
+
+    durationConstr = mp.addConstrs(t[k[1]] - t[k[0]] >= pData.D[k[0]]*(1 - sum(pData.eff[k[0]][j]*x[k[0],j] 
+        for j in pData.Ji[k[0]])) for k in pData.K)
+    budgetConstr = mp.addConstr(sum(sum(x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B)
+    xConstr = mp.addConstrs(sum(x[i,j] for j in pData.Ji[i]) <= 1 for i in pData.II)
+
+    mp.setObjective(t[0], GRB.MINIMIZE)
+    mp.optimize()
+
+    tdet = {}
+    xdet = {}
+    for i in pData.II:
+        tdet[i] = t[i].X
+        for j in pData.Ji[i]:
+            xdet[i,j] = x[i,j].X
+    fdet = mp.objVal
+    return tdet,xdet,fdet

### 2018-11-09 src/python/master.py

@@ -1,0 +1,14 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Oct 28 22:55:31 2018
+
+@author: haoxiangyang
+"""
+
+# master problems
+def createMaster(pData,disData,Omega,Tmax):
+    pass
+
+def createMaster_div(pData,disData,Omega,divSet,divDet,cutSet,Tmax,distanceDict,allSucc,yOption,yLim,yCuts = 1,cutyn = []):
+    pass

### 2018-11-09 src/python/readIn.py

@@ -1,0 +1,251 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Oct 28 22:54:08 2018
+
+@author: haoxiangyang
+"""
+
+# read in the data
+from defType import *
+import numpy as np
+import scipy.stats
+import csv
+import pickle
+import os
+
+def buildDistrn(nameDistr,paramDistr):
+    if nameDistr == "Exponential":
+        μ = paramDistr[0]
+        distrObj = scipy.stats.expon(0,μ)
+    elif nameDistr == "LogNormal":
+        μ = paramDistr[0]
+        σ = paramDistr[1]
+        distrObj = scipy.stats.lognorm([σ],scale = np.exp(μ))
+    elif nameDistr == "Gamma":
+        α = paramDistr[0]
+        θ = paramDistr[1]
+        distrObj = scipy.stats.gamma(scale = α,loc = θ)
+    elif nameDistr == "Uniform":
+        la = paramDistr[0]
+        ub = paramDistr[1]
+        distrObj = scipy.stats.uniform(loc = la,scale = ub+1e-10 - la)
+    elif nameDistr == "Normal":
+        μ = paramDistr[0]
+        σ = paramDistr[1]
+        distrObj = scipy.stats.norm(loc = μ,scale = σ)
+    elif nameDistr == "Singleton":
+        la = paramDistr[0]
+        distrObj = scipy.stats.uniform(loc = la,scale = 0)
+        
+    return distrObj
+
+# input function that reads in the project data
+def readInP(pInputAdd,kInputAdd):
+    fi = open(pInputAdd,"r")
+    csvReader = csv.reader(fi)
+    pRaw = []
+    for item in csvReader:
+        pRaw.append(item)
+    fi.close()
+    
+    fi = open(kInputAdd,"r")
+    csvReader = csv.reader(fi)
+    kRaw = []
+    for item in csvReader:
+        kRaw.append(item)
+    fi.close()
+    
+    npp = len(pRaw)
+    nk = len(kRaw)
+    
+    # total budget
+    B = float(pRaw[0][0])
+    # nominal scenario probability
+    p0 = float(pRaw[0][1])
+    
+    # 0 as the last activity
+    II = [0]
+    Ji = {}
+    D = {}
+    D[0] = 0
+    Ji[0] = []
+    
+    b = {}
+    b[0] = {}
+    eff = {}
+    eff[0] = {}
+    
+    # read in the activity information
+    for i in range(1,npp):
[…]

### 2018-11-09 src/python/sub.py

@@ -1,0 +1,20 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sun Oct 28 22:55:19 2018
+
+@author: haoxiangyang
+"""
+
+import numpy as np
+
+
+# sub problems
+def sub_divT(pData,dDomega,omegaCurr,that,xhat,yhat,divSet,H,M,returnOpt = 0):
+    pass
+    
+def sub_divTDual(pData,dDomega,omegaCurr,that,xhat,yhat,divSet,H,M,returnOpt = 0):
+    pass
+
+def sub_divTDualT(pData,dDomega,omegaCurr,that,xhat,yhat,divSet,H,M,tcoreList,xcoreList,ycoreList,returnOpt = 0):
+    pass

### 2018-11-09 src/python/ubCalFunc.py

@@ -1,0 +1,62 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Oct 29 01:32:05 2018
+
+@author: haoxiangyang
+"""
+
+from gurobipy import *
+
+# functions to calculate the upper bound
+
+def subIntC(pData,dDomega,xhat,that,M,returnOpt = 0):
+    # solve the MIP recourse problem
+    sp = Model()
+    sp.Params.OutputFlag = 0
+    t = sp.addVars(pData.II)
+    xInd = []
+    for i in pData.II:
+        for j in pData.Ji[i]:
+            xInd.append((i,j))
+    x = sp.addVars(xInd, ub = 1)
+    s = sp.addVars(xInd, ub = 1)
+    G = sp.addVars(pData.II, vtype = GRB.BINARY)
+
+    # add the basic sub problem constraints
+    FCons = sp.addConstrs(dDomega.H - (1 - G[i])*M <= that[i] for i in pData.II)
+    GCons = sp.addConstrs(dDomega.H + G[i]*M >= that[i] for i in pData.II)
+
+    tGcons1 = sp.addConstrs(t[i] <= that[i] + M*G[i] for i in pData.II)
+    tGcons2 = sp.addConstrs(t[i] >= that[i] - M*G[i] for i in pData.II)
+    boundT = sp.addConstrs(t[i] >= dDomega.H*G[i] for i in pData.II)
+    xGcons1 = sp.addConstrs(x[i,j] <= xhat[i,j] + G[i] for i in pData.II for j in pData.Ji[i])
+    xGcons2 = sp.addConstrs(x[i,j] >= xhat[i,j] - G[i] for i in pData.II for j in pData.Ji[i])
+
+    budgetConstr = sp.addConstr(sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B)
+    xConstr = sp.addConstrs(sum(x[i,j] for j in pData.Ji[i]) <= 1 for i in pData.II)
+    # linearize the bilinear term of x[i,j]*G[i]
+    xGlin1 = sp.addConstrs(s[i,j] <= G[i] for i in pData.II for j in pData.Ji[i])
+    xGlin2 = sp.addConstrs(s[i,j] <= x[i,j] for i in pData.II for j in pData.Ji[i])
[…]

### 2018-11-09 src/sub.jl

@@ -237,8 +237,8 @@ end
 function subPull(pData,dDω,xhat,that,Ghatω,M = 9999999)
 
     # sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
-    #sp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
-    sp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
+    sp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
+    #sp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
     @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
     @variable(sp, t[i in pData.II] >= 0);
     @variable(sp, s[i in pData.II, j in pData.Ji[i]] >= 0);
@@ -393,8 +393,8 @@ end
 function subLag(pData,dDω,xhat,that,Ghatω,γhat,M = 9999999)
 
     # sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
-    #sp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
-    sp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
+    sp = Model(solver = CplexSolver(CPX_PARAM_EPINT = 1e-8,CPX_PARAM_EPRHS = 1e-8,CPX_PARAM_SCRIND = 0));
+    # sp = Model(solver = GurobiSolver(OutputFlag = 0, IntFeasTol = 1e-8, FeasibilityTol = 1e-8));
     @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
     @variable(sp, t[i in pData.II] >= 0);
     @variable(sp, s[i in pData.II, j in pData.Ji[i]] >= 0);
@@ -437,8 +437,8 @@ end
[…]

### 2018-11-09 src/test_time.jl

@@ -1,4 +1,4 @@
-addprocs(20);
+addprocs(30);
 @everywhere using JuMP,Gurobi,CPLEX,Ipopt;
 @everywhere using Distributions,HDF5,JLD;
 # test sbb
@@ -11,16 +11,18 @@ pathList = ["/home/haoxiang/PERT_tests/11_Lognormal_Exponential/",
 
 for fileInd in 1:length(pathList)
     filePath = pathList[fileInd];
-    Ωsize = [100,200,500,1000];
+    Ωsize = [100,200,300,400,500,750,1000];
     dDict = Dict();
     for Ωl in 1:length(Ωsize)
-        Ω = 1:Ωsize[Ωl];
-        ϵ = 1e-2;
+        global Ω = 1:Ωsize[Ωl];
+        global ϵ = 1e-2;
+        global pData;
         pData,disDataSet,nameD,nameH,dparams,Hparams = genData(filePath,Ωsize[Ωl]);
-        disData = disDataSet[1];
+        global pData = pData;
+        global disData = disDataSet[1];
 
-        allSucc = findSuccAll(pData);
-        distanceDict = Dict();
+        global allSucc = findSuccAll(pData);
+        global distanceDict = Dict();
         for i in pData.II
             for j in allSucc[i]
                 distanceDict[i,j] = detCal(pData,i,j);
@@ -30,7 +32,7 @@ for fileInd in 1:length(pathList)
         global sN = 20;
         global MM = 25;
         tic();
-        include("partSolve_Callback_tightened_sol.jl");
+        include("partSolve_Callback_tightened.jl");
         timedecomp = toc();
         gapdecomp = (ubCost - lbCost)/ubCost;
 

### 2018-11-09 src/test_value.jl

@@ -1,4 +1,4 @@
-addprocs(20);
+addprocs(30);
 @everywhere using JuMP,Gurobi,CPLEX,Ipopt;
 @everywhere using Distributions,HDF5,JLD;
 # test sbb
@@ -10,6 +10,7 @@ pathList = ["/home/haoxiang/PERT_tests/11_Lognormal_Exponential/",
 
 # filePath = "/Users/haoxiangyang/Desktop/PERT_tests/14_Lognormal_Exponential/"
 dDict = Dict();
+ubList = Dict();
 global sN = 20;
 global MM = 25;
 for fileInd in 1:length(pathList)
@@ -73,7 +74,7 @@ for fileInd in 1:length(pathList)
         end
     end
     tic();
-    include("partSolve_Callback_tightened_sol.jl");
+    include("partSolve_Callback_tightened.jl");
     timeHOnly = toc();
     gapHOnly = (ubCost - lbCost)/ubCost;
     xHOnly = deepcopy(xbest);
@@ -83,7 +84,7 @@ for fileInd in 1:length(pathList)
 
     # full solution
     tic();
-    include("partSolve_Callback_tightened_sol.jl");
+    include("partSolve_Callback_tightened.jl");
     timeFull = toc();
     gapFull = (ubCost - lbCost)/ubCost;
     ubFull = ubCost;
@@ -97,7 +98,7 @@ for fileInd in 1:length(pathList)
                 tdOnly,xdOnly,gdOnly,ubdOnly,
                 tHOnly,xHOnly,ubHOnly,gapHOnly];
 
-    ubList = [];
+    ubList[fileInd] = [];
     for n in 1:20
         println("----------------Iteration $(n)----------------");
         disData1,Ω = autoUGen("LogNormal",Hparams,"Exponential",dparams,5000,1 - pData.p0);
@@ -107,7 +108,7 @@ for fileInd in 1:length(pathList)
         ubFull1 = ubCalP(pData,disData1,Ω,xFull,tFull,999999);
         ubdOnly1 = ubCalP(pData,disData1,Ω,xdOnly,tdOnly,999999);
         ubHOnly1 = ubCalP(pData,disData1,Ω,xHOnly,tHOnly,999999);
-        push!(ubList,[ubdet1,ubexp1,ubFull1,ubdOnly1,ubHOnly1]);
[…]

### 2018-11-09 src/tighten.jl

@@ -371,7 +371,8 @@ function obtainDet(pData,disData,Ω,mpTemp,ub,divSet,divDet)
 end
 
 function detCal(pData,i,j)
-    mp = Model(solver = GurobiSolver(OutputFlag = 0));
+    mp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
+    #mp = Model(solver = GurobiSolver(OutputFlag = 0));
     @variables(mp, begin
       0 <= x[i in pData.II,j in pData.Ji[i]] <= 1
       t[i in pData.II] >= 0

### 2018-11-09 src/ubCalFunc.jl

@@ -1,7 +1,7 @@
 function subInt(pData,dDω,xhat,that)
     # solve the MIP recourse problem
-    # sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
-    sp = Model(solver = GurobiSolver(OutputFlag = 0));
+    sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
+    # sp = Model(solver = GurobiSolver(OutputFlag = 0));
     @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
     @variable(sp, t[i in pData.II] >= 0);
 
@@ -24,8 +24,8 @@ end
 
 function subIntC(pData,dDω,xhat,that,M = 999999,returnOpt = 0)
     # solve the MIP recourse problem
-    # sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
-    sp = Model(solver = GurobiSolver(OutputFlag = 0));
+    sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
+    # sp = Model(solver = GurobiSolver(OutputFlag = 0));
     @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
     @variable(sp, 0 <= s[i in pData.II,j in pData.Ji[i]] <= 1);
     @variable(sp, t[i in pData.II] >= 0);
@@ -64,8 +64,8 @@ function subIntG(pData,dDω,xhat,that,Ghatω)
     # solve the MIP recourse problem
     M = sum(max(pData.D[i],pData.D[i]+dDω.d[i]) for i in pData.II if i != 0);
 
-    sp = Model(solver = GurobiSolver(OutputFlag = 0));
-    # sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
+    # sp = Model(solver = GurobiSolver(OutputFlag = 0));
+    sp = Model(solver = CplexSolver(CPX_PARAM_SCRIND = 0));
     @variable(sp, 0 <= x[i in pData.II,j in pData.Ji[i]] <= 1);
     @variable(sp, t[i in pData.II] >= 0);
 
@@ -88,8 +88,8 @@ end
 
 function subIntGMixed(pData,dDω,xhat,that,ωCurr,Ghatω,M = 400,returnOpt = 0)
     # solve the MIP recourse problem
[…]

### 2018-11-26 Writeup/PERT_Paper.tex
Updated the writeups

--- 2018-11-02 Writeup/PERT_New.tex
@@
 
-Optimal Crashing of a PERT Network with Disruptions \ms
+Optimizing Crashing Decisions in a Project Management Problem with Disruptions \ms
 
@@
 \section{Introduction} \label{sec:introduction}
-	The management of complex projects through optimization has a rich history in operations research, beginning with the program evaluation and review technique (PERT) \cite{malcolm1959application} and the critical path method (CPM) of \cite{kelley1961criticalpath}; see S{\"o}derlund \cite{soderlund2004building} for an overview and see \cite{Elmaghraby77}.
-To formulate a mathematical model, a project is viewed as a collection of activities, each of which has some duration and may consume some resources.
-There are precedence relationships between activities due to logical or technological considerations.
-The objective is to complete all activities in minimum time.
-We represent such a project using an acyclic activity network, where the length of each link shows the duration of an activity, and an edge's predecessors capture the precedence relationships.
-An activity cannot start until all its predecessors are completed.
-Multiple activities can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
-More details about the activity network are discussed in \cite{Elmaghraby77}.\\
+	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method (CPM) of \cite{kelley1961criticalpath} for the deterministic project management problems; see S{\"o}derlund \cite{soderlund2004building} for an overview.
+A project is a collection of activities \(I\) of some duration \(D_i, i \in I\), and there are precedence relationships, \(\mathcal{A} \subseteq I \times I\), between activities due to logical or technological considerations.
+A project can be characterized as an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\).
+An arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\), and its length shows the duration of an activity \(D_i\).
+An activity cannot start until all its predecessors are completed, while multiple activities can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
+More details about the activity network are discussed in Elmaghraby~\cite{Elmaghraby77}.
+In this setting, ``crashing" is an action that consumes certain amount of resource and shorten the duration of activities accordingly~\cite{kuhl2008dynamic}.
+We can apply a finite set of crashing options, \(j \in J_i\), to activity \(i \in I\).
+One unit application of each option incurs a cost of \(b_{ij}\), while it decreases the length of activity \(i\) by \(D_ie_{ij}\); i.e., the crashed duration is proportional to both the nominal activity duration and the crashing decision.
+The total cost of crashing options cannot exceed a given budget, \(B\).
+The deterministic project crashing optimization problem has been known since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
+The objective is to complete all activities in minimum time by allocating resources with budget constraints.
+\\
 	\newline
-	In the planning stage of a project, decisions are made to crash a certain set of activities in order to minimize the project's timespan.
-Here crashing an activity means shortening its duration.
-In this paper, a discrete set of crashing options are available, each with fraction specifying the resulting reduction in the activity's duration.
+	We can create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project.
+\(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \).
+Then the objective can be interpreted as to minimize the starting time of activity \(T\).
+	 We decide the amount of resource and the starting time of each activity.
+We assume a discrete set of crashing options are available, each with fraction specifying the resulting reduction in the activity's duration.
 An activity can be crashed at most once and with a single option.
 Each option incurs a certain cost, and the total cost of crashing cannot exceed the budget.
-Optimization of such static crashing problems is introduced in \cite{fulkerson1961network, kelley1961criticalpath}.
 Under a finite set of crashing options, the problem can be modeled as a mixed integer program.
-The static model can be extended to incorporate uncertainty of activity durations.
+
+	The static model can be extended to incorporate uncertainty of activity durations, starting with the program evaluation and review technique (PERT) \cite{malcolm1959application}.
 Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is is difficult to express analytically the expected project span \cite{burt1971conditional,van1963letter}.
@@
 \cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.\\
+	\newline 
+	The crashing optimization problem finds wide applications in project management~\cite{demeulemeester2006project, jaselskis1991allocation}, machine scheduling~\cite{blazewicz1983scheduling,hall1996machine}, health services scheduling~\cite{cardoen2010operating}, chemical processes~\cite{li2008process}, and digital circuit sizing~\cite{kim2007heuristic}.\\
 	\newline
@@
 \section{Problem Formulation} \label{sec:formulation}
-	The deterministic project crashing optimization problem has been known since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
-Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\).
+	 Suppose the activity network is represented by a directed graph , where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\).
 The arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\).
-We create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project.
-\(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \).
 \\
 	\newline
-	For each activity \(i \in I\), the nominal length \(D_i\) is given.
-We can apply a finite set of crashing options, \(j \in J_i\), and one unit application of each option incurs a cost of \(b_{ij}\), while it decreases the length of activity \(i\) by \(D_ie_{ij}\).
-The total cost of crashing options cannot exceed a given budget, \(B\).
-We assume each activity can be crashed at most with one unit and the problem can be formulated as follows:
+	For each activity \(i \in I\), the nominal length \(D_i\) is given.  and the problem can be formulated as follows:
 	\begin{subequations} \label{prob:static}

### 2018-11-27 Writeup/PERT_Paper.tex
Reverse the change of Section 5

--- 2018-11-09 Writeup/PERT_New.tex
@@
 \usepackage{framed}
-\usepackage{natbib}
+\usepackage[square,sort,comma,numbers]{natbib}
+\usepackage{url}
 \usepackage{float, subfig}
@@
 \section{Introduction} \label{sec:introduction}
-	The management of complex projects through optimization has a rich history in operations research, beginning with the program evaluation and review technique (PERT) \cite{malcolm1959application} and the critical path method (CPM) of \cite{kelley1961criticalpath}; see S{\"o}derlund \cite{soderlund2004building} for an overview and see \cite{Elmaghraby77}.
-To formulate a mathematical model, a project is viewed as a collection of activities, each of which has some duration and may consume some resources.
-There are precedence relationships between activities due to logical or technological considerations.
-The objective is to complete all activities in minimum time.
-We represent such a project using an acyclic activity network, where the length of each link shows the duration of an activity, and an edge's predecessors capture the precedence relationships.
-An activity cannot start until all its predecessors are completed.
-Multiple activities can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
-More details about the activity network are discussed in \cite{Elmaghraby77}.\\
+	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath} for the deterministic project management problems; see S{\"o}derlund \cite{soderlund2004building} for an overview.
+A project is a collection of activities \(I\) of some duration \(D_i, i \in I\), and there are precedence relationships, \(\mathcal{A} \subseteq I \times I\), between activities due to logical or technological considerations.
+A project can be characterized as an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\).
+An arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\), and its length shows the duration of an activity \(D_i\).
+An activity cannot start until all its predecessors are completed, while multiple activities can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
+More details about the activity network are discussed in Elmaghraby~\cite{Elmaghraby77}.
+In this setting, ``crashing" is an action that consumes certain amount of resource and shorten the duration of activities accordingly~\cite{kuhl2008dynamic}.
+We can apply a finite set of crashing options, \(j \in J_i\), to activity \(i \in I\).
+One unit application of each option incurs a cost of \(b_{ij}\), while it decreases the length of activity \(i\) by \(D_ie_{ij}\); i.e., the crashed duration is proportional to both the nominal activity duration and the crashing decision.
+The total cost of crashing options cannot exceed a given budget, \(B\).
+The deterministic optimization problem for crashing decisions has been proposed since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
+The goal is to complete all activities in minimum time by allocating resources under budget constraints.
+We can create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project.
+\(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \).
+Then the objective is then equivalent to minimize the starting time of activity \(T\).
+Thus, we formulate the deterministic project crashing optimization problem as:
+	\begin{subequations} \label{prob:static}
+		\begin{align}
+		\min \quad & t_T &\\
+		\text{s.t.} \quad &  t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:dSep}\\
+		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
+		& t_i \geq 0  \qquad \qquad \forall \,i \in I \label{cons:dNonnegt}\\
+		& 0 \leq x_{ij} \leq 1  \qquad \qquad \forall \,i \in I, j \in J_i. \label{cons:dxub}
+		\end{align}
+	\end{subequations}
+	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\).
+We aim to minimize the project span, which is the starting time of the terminal activity, \(t_T\).
+Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
+Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
+In constraint~\eqref{cons:dxub}, we can put an artificial upper bound \(1\) on all crashing decisions \(x_{ij}\) by taking proper values of \(e_{ij}\).
+\\
 	\newline
-	In the planning stage of a project, decisions are made to crash a certain set of activities in order to minimize the project's timespan.
-Here crashing an activity means shortening its duration.
-In this paper, a discrete set of crashing options are available, each with fraction specifying the resulting reduction in the activity's duration.
-An activity can be crashed at most once and with a single option.
-Each option incurs a certain cost, and the total cost of crashing cannot exceed the budget.
-Optimization of such static crashing problems is introduced in \cite{fulkerson1961network, kelley1961criticalpath}.
-Under a finite set of crashing options, the problem can be modeled as a mixed integer program.
-The static model can be extended to incorporate uncertainty of activity durations.
-Monte Carlo simulation methods are used to estimate the expected project span given distributions of activity lengths, since it is is difficult to express analytically the expected project span \cite{burt1971conditional,van1963letter}.
-Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant,bowman1994stochastic,ke2014genetic,kim2007heuristic}.
+	The deterministic model can be extended to incorporate uncertainty of activity durations, starting with the program evaluation and review technique (PERT) \cite{malcolm1959application}.
+The PERT model assumes that activities are independently distributed with beta distributions, and the expected project span can be approximated by a normal distribution.
+However, this assumption may not be accurate for a general case~\cite{Elmaghraby77}.
+Therefore, assuming the activity durations follow a given probability distribution, Monte Carlo simulation methods can be used to estimate the expected project span, since it is is difficult to express analytically the expected project span \cite{burt1971conditional,van1963letter}.
+Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}.
 Another approach to handle the uncertainty is robust optimization, in which the objective is to minimize the worst case project span within a specified uncertainty set.
-While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \cite{chen2008linear,cohen2007stochastic}.
+While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \cite{chen2008linear, cohen2007stochastic}.
 However, once recourse decisions can take general form, the robust model is only tractable with hypercube uncertainty sets, which is a trivial case because the worst-case scenario in the uncertainty set is always the point where every activity takes its upper bound \cite{wiesemann2012robust}.
 Ahipasaoglu et al.
-\cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.\\
+\cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.
+The project crashing optimization problem finds wide applications in project management~\cite{demeulemeester2006project, jaselskis1991allocation,tonchia2018industrial}, machine scheduling~\cite{blazewicz1983scheduling,hall1996machine}, health services scheduling~\cite{cardoen2010operating}, chemical processes~\cite{li2008process}, and digital circuit sizing~\cite{kim2007heuristic}.\\
 	\newline
@@
 \section{Problem Formulation} \label{sec:formulation}
-	The deterministic project crashing optimization problem has been known since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
-Suppose the activity network is represented by a directed graph \(\mathcal{G} = (I,\mathcal{A})\), where the set of activities is denoted by \(I\) and their precedence relationship is characterized by \(\mathcal{A}\).
-The arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\).
-We create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project.
-\(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \).
-\\
-	\newline
-	For each activity \(i \in I\), the nominal length \(D_i\) is given.
-We can apply a finite set of crashing options, \(j \in J_i\), and one unit application of each option incurs a cost of \(b_{ij}\), while it decreases the length of activity \(i\) by \(D_ie_{ij}\).
-The total cost of crashing options cannot exceed a given budget, \(B\).
-We assume each activity can be crashed at most with one unit and the problem can be formulated as follows:
-	\begin{subequations} \label{prob:static}
-		\begin{align}
-		\min \quad & t_T &\\
-		\text{s.t.} \quad &  t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:dSep}\\
-		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
-		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
-		& t_i \geq 0  \qquad \qquad \forall \,i \in I\\
-		& 0 \leq x_{ij} \leq 1  \qquad \qquad \forall \,i \in I, j \in J_i.
-		\end{align}
-	\end{subequations}
-	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\).
-We aim to minimize the project span, which is the starting time of the terminal activity, \(t_T\).
-Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
-Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
-\\
-	\newline
-	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span.
-We also assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards.
+	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span, since for the applications we are interested in (natural disasters, terrorist attacks, major market crashes, etc.), it is unlikely for two disruptions to occur in entire the time horizon.
+For example, it is unlikely for two major earthquakes to hit the same area twice within a month.
+It is reasonable to assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
 The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
@@
 We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
-Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation.\\
-	%  and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)
+Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
 	\newline
@@
 All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform.
-All linear programs and mixed integer programs are solved by \textcolor{blue}{CPLEX} with both the feasibility tolerance and the integrality tolerance as \(10^{-7}\).
-We refer interested readers to \textcolor{blue}{GitHub repository} for the input data and the code used in this paper.
-%Gurobi 8.01 \cite{gurobi2016}
+All linear programs and mixed integer programs are solved by Gurobi 8.01 \cite{gurobi2016} with default parameters.
 
@@
 	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
-	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling both the random timing and magnitude of the disruption.
+	I	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling random timing and magnitude of the disruption.
 First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET").
@@
 	\subsection{Computational Performance} \label{subsec:time}
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{PERT_Bib}

### 2018-11-27 Writeup/PERT_Paper.tex
Add stratified sampling generation

@@
 	\newline
-	The uncertainty in our paper lies in the timing and the magnitude of the stochastic disruption, which is modeled differently from randomness in a two-stage stochastic program or from the uncertainty set in robust optimization.
+	In this paper, we propose using the concept of stochastic disruptions to model the uncertainty, which is different from the setting of a stochastic program or a robust optimization problem.
 A stochastic disruption is an event that may occur any time in the time horizon and change the system parameters significantly.
@@
 We present some important properties of this problem using a serial activity network as a special case in Section~\ref{sec:examples}.
-	\begin{comment}
-	We prove some important consistency and convergence properties of the SAA problem using independent and identically distributed samples and stratified samples in Section~\ref{sec:consistency}.\\
-	\newline
 The large scale and the discrete non-convex nature of the SAA problem's extended formulation means it may not be solved efficiently to desirable tolerance level.
 In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
-We show such a decomposition method solves the integer program to the exactness within finite number of iterations.\\
-	\newline
-	The experiment results are presented in Section~\ref{sec:results}, including the comparison between the quality of our solution and the solution obtained by solving a  crashing optimization problem with a deterministic disruption, and the computational performance of the decomposition method in Section~\ref{sec:decomposition}, compared to that of solving the extensive formulation.
+We show such a decomposition method solves the integer program to the exactness within finite number of iterations.
+The experiment results are presented in Section~\ref{sec:results}, including the relationship between the solution quality and the sample size, the comparison between the quality of our solution and the deterministic/semi-stochastic alternative solutions, and the computational performance of the decomposition method presented in Section~\ref{sec:decomposition}.
 We conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
-	\end{comment}
 
 \section{Problem Formulation} \label{sec:formulation}
-	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span, since for the applications we are interested in (natural disasters, terrorist attacks, major market crashes, etc.), it is unlikely for two disruptions to occur in entire the time horizon.
-For example, it is unlikely for two major earthquakes to hit the same area twice within a month.
-It is reasonable to assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
+	For a project crashing problem under stochastic disruptions, we assume at most one stochastic disruption can occur at a random time in the project span, since for the applications we are interested in (natural disasters, terrorist attacks, major market crashes, etc.), it is unlikely for two disruptions to occur in entire the time horizon.
+For example, suppose we manage a construction project, and we aim to plan against the potential hazard caused by earthquakes.
+It is unlikely for two major earthquakes to hit the same area twice within a year (aftershocks can be considered part of a major earthquake.) It is also reasonable to assume for each activity \(i \in I\), the crashing decision needs to be made at the start of that activity, and cannot be changed afterwards, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
 The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
@@
 	Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program (2SMIP).
-If we attempt to decompose it into a master problem~\eqref{prob:masterOri} and scenario-specific subproblems~\eqref{prob:subOri}, the state variables \(t\) and \(x\) are all continuous and binary variables exist in the recourse problems.
-The recourse problems become nonconvex.
-Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
-For example, Gade et al.
-\cite{gade2014decomposition} solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where Gomory cuts are added.
-Ahmed et al.
-\cite{zou2016nested} assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
-Car{\o}e and Tind \cite{caroe1998shaped} solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not verified.
-Qi and Sen \cite{qi2017ancestral} have mixed integer variables in both the master and the recourse problems.
-Parametric disjunctive cuts, derived in Chen et al.
-\cite{chen2012computational}, are generated to convexify recourse problems while Benders' cuts approximate recourse value functions.
-\textcolor{blue}{Although this method suits our problem settings, we implement it only to find that it does not converge in a reasonable time frame.} Therefore, we propose a new decomposition method that utilizes the special structure of our problem.
-\\
-	\newline
-	We first rewrite the extensive formulation into a master problem \((M)\) and a set of recourse problems \((S^\omega)\), \(\omega \in \Omega\):
-	%The recourse problem becomes a linear program as long as we can determine the temporal relationship between each activity and the disruption, and an early determination of the value of \(G\) help accelerate the decomposition process.
+First we can decompose it into a master problem \((M)\) and a set of subproblems \((S^\omega)\), \(\omega \in \Omega\) as follows.
+The state variables \(t\) and \(x\) are all continuous and binary variables exist in the recourse problems, which makes recourse problems nonconvex.
 	\begin{subequations}
@@
 	\end{subequations}
+	Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
+For example, Gade et al.
+\cite{gade2014decomposition} solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where Gomory cuts are added.
+Ahmed et al.
+\cite{zou2016nested} assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
+Car{\o}e and Tind \cite{caroe1998shaped} solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not verified.
+Qi and Sen \cite{qi2017ancestral} have mixed integer variables in both the master and the recourse problems.
+Parametric disjunctive cuts, derived in Chen et al.
+\cite{chen2012computational}, are generated to convexify recourse problems while Benders' cuts approximate recourse value functions.
+Although this method suits our problem settings, we implement it only to find that it does not converge in a reasonable time frame.
+Therefore, we need a new decomposition method that utilizes the special structure of our problem.
+\\
+	\newline
 	We can relax the integrality constraints~\eqref{cons:subInt} and solve the subproblem to obtain Benders' cuts.

### 2018-11-27 src/test_Extensive.jl

@@ -1,0 +1,34 @@
+addprocs(30);
+global noThreads = 30;
+@everywhere using JuMP,Gurobi,CPLEX,Ipopt;
+@everywhere using Distributions,HDF5,JLD;
+# test sbb
+@everywhere include("header.jl");
+
+#filePath = "/Users/haoxiangyang/Desktop/PERT_tests/75_Lognormal_Exponential/"
+pathList = ["/home/haoxiang/PERT_tests/11_Lognormal_Exponential/",
+            "/home/haoxiang/PERT_tests/14_Lognormal_Exponential/",
+            "/home/haoxiang/PERT_tests/19_Lognormal_Exponential/"];
+Ωsize = [100,200,300,400,500,750,1000];
+dDict = Dict();
+for fileInd in 1:length(pathList)
+    filePath = pathList[fileInd];
+    dDict[fileInd] = Dict();
+    for Ωl in 1:length(Ωsize)
+        global Ω = 1:Ωsize[Ωl];
+        global ϵ = 1e-2;
+        global pData;
+        pData,disDataSet,nameD,nameH,dparams,Hparams = genData(filePath,Ωsize[Ωl]);
+        global disData = disDataSet[1];
+        # extensive formulation
+        tic();
+        text,xext,fext,gext,mext = extForm_cheat(pData,disData,Ω,ϵ,999999);
+        timeext = toc();
+        ubmp = mext.objVal;
+        lbmp = mext.objBound;
+        gapext = (mext.objVal - mext.objBound)/mext.objVal;
+        ubext = ubCal(pData,disData,Ω,xext,text,999999);
+        dDict[fileInd][Ωsize[Ωl]] = [text,xext,lbmp,ubmp,ubext,gapext,timeext];
+        save("test_Ext_extensive.jld","dDict",dDict);
+    end
+end

### 2019-02-25 Writeup/PERT_Paper_Draft1.tex
Updated writeup + upload python deterministic tests

--- 2018-11-27 Writeup/PERT_Paper.tex
@@
 
-Optimizing Crashing Decisions in a Project Management Problem with Disruptions \ms
+Optimal Crashing of an Activity Network with Disruptions \ms
 
@@
 \section{Introduction} \label{sec:introduction}
-	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath} for the deterministic project management problems; see S{\"o}derlund \cite{soderlund2004building} for an overview.
-A project is a collection of activities \(I\) of some duration \(D_i, i \in I\), and there are precedence relationships, \(\mathcal{A} \subseteq I \times I\), between activities due to logical or technological considerations.
-A project can be characterized as an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\).
-An arc \((i,j) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(j\), and its length shows the duration of an activity \(D_i\).
-An activity cannot start until all its predecessors are completed, while multiple activities can be processed at the same time without a upper limit, as long as the precedence requirement is satisfied.
-More details about the activity network are discussed in Elmaghraby~\cite{Elmaghraby77}.
-In this setting, ``crashing" is an action that consumes certain amount of resource and shorten the duration of activities accordingly~\cite{kuhl2008dynamic}.
+	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath} (see S{\"o}derlund \cite{soderlund2004building} for an overview).
+A project is a collection of activities \(I\)
+	 %of some duration \(D_i, i \in I\)
+	 , and there are precedence relationships, \(\mathcal{A} \subseteq I \times I\), between activities due to logical or technological considerations.
+A project can be characterized by an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\).
+An arc \((i,k) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(k\), and its length shows the required separation between their start time,
+	 %duration of an activity 
+	 \(D_{ik}\).
+An activity cannot start until all its predecessors are completed, while multiple activities can be processed at the same time without an upper limit, as long as the precedence requirements are satisfied.
+See Elmaghraby~\cite{Elmaghraby77} for a detailed treatment of activity networks.
+In this setting, ``crashing" is an action that consumes a certain amount of resource and shortens the duration of activities accordingly~\cite{kuhl2008dynamic}.
 We can apply a finite set of crashing options, \(j \in J_i\), to activity \(i \in I\).
-One unit application of each option incurs a cost of \(b_{ij}\), while it decreases the length of activity \(i\) by \(D_ie_{ij}\); i.e., the crashed duration is proportional to both the nominal activity duration and the crashing decision.
-The total cost of crashing options cannot exceed a given budget, \(B\).
-The deterministic optimization problem for crashing decisions has been proposed since the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
-The goal is to complete all activities in minimum time by allocating resources under budget constraints.
-We can create two dummy activities \(S\) and \(T\) to represent the start and the end of entire project.
-\(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \).
-Then the objective is then equivalent to minimize the starting time of activity \(T\).
-Thus, we formulate the deterministic project crashing optimization problem as:
+One unit application of each option incurs a cost of \(b_{ij}\), \textcolor{blue}{while it decreases all required separation lengths starting from activity \(i\) by \(D_{ik}e_{ij},\ \forall (i,k) \in \mathcal{A}\); i.e., the crashed duration is proportional to both the nominal separation length and the crashing decision.} The total cost of crashing cannot exceed a given budget, \(B\).
+The deterministic optimization problem for crashing an activity network was proposed in the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
+The goal is to complete all activities in minimum time by allocating resources under one or more budget constraints.
+We create two dummy activities \(S\) and \(T\) to represent the start and the end of the entire project.
+Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \), and they both have zero duration, \(D_{Si} = D_{iT} = 0,\ \forall i \in I\).
+Given $t_S \equiv 0$, the objective is then to minimize the start time of activity \(T\).
+Thus, we formulate the deterministic project crashing problem as:
 	\begin{subequations} \label{prob:static}
@@
 		\min \quad & t_T &\\
-		\text{s.t.} \quad &  t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:dSep}\\
+		\text{s.t.} \quad &  t_k - t_i \geq D_{ik}\left(1 - \sum_{j \in J_i} x_{ij} e_{ij}\right) \qquad \qquad \forall \,(i,k) \in \mathcal{A} \label{cons:dSep}\\
 		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
 		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
-		& t_i \geq 0  \qquad \qquad \forall \,i \in I \label{cons:dNonnegt}\\
-		& 0 \leq x_{ij} \leq 1  \qquad \qquad \forall \,i \in I, j \in J_i. \label{cons:dxub}
+		& x_{ij} \geq 0  \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:dxub}\\
+		& t_S = 0. \label{cons:dNonnegt}
 		\end{align}
 	\end{subequations}
-	In this formulation, \(t_i\) represents the starting time of activity \(i \in I\).
-We aim to minimize the project span, which is the starting time of the terminal activity, \(t_T\).
-Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finishing time of activity \(i\) is \(t_i + D_i (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
+	In this formulation, \(t_i\) represents the start time of activity \(i \in I\).
+We aim to minimize the project span, which is the start time of the terminal activity, \(t_T\).
+Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finish time of activity \(i\) is \(t_i + D_{ik} (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
 Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
-In constraint~\eqref{cons:dxub}, we can put an artificial upper bound \(1\) on all crashing decisions \(x_{ij}\) by taking proper values of \(e_{ij}\).
-\\
+Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities since activity \(S\) precedes every other activity.\\
+	% In constraint~\eqref{cons:dxub}, we can put an artificial upper bound \(1\) on all crashing decisions \(x_{ij}\) by taking proper values of \(e_{ij}\). \\
 	\newline
-	The deterministic model can be extended to incorporate uncertainty of activity durations, starting with the program evaluation and review technique (PERT) \cite{malcolm1959application}.
+	When the program evaluation and review technique (PERT) \cite{malcolm1959application} was introduced, activity durations were modeled as independent beta random variables, and the project duration approximated by a normal distribution.
+Extensions that allow for more general assumptions followed \cite{Elmaghraby77}, and Monte Carlo simulation plays a role in estimating the expected project span, which is difficult to express analytically \cite{burt1971conditional,van1963letter}.
+	%The deterministic model can be extended to incorporate uncertainty of activity duration, starting with the program evaluation and review technique (PERT) \cite{malcolm1959application}.
 The PERT model assumes that activities are independently distributed with beta distributions, and the expected project span can be approximated by a normal distribution.
 However, this assumption may not be accurate for a general case~\cite{Elmaghraby77}.
-Therefore, assuming the activity durations follow a given probability distribution, Monte Carlo simulation methods can be used to estimate the expected project span, since it is is difficult to express analytically the expected project span \cite{burt1971conditional,van1963letter}.
-Heuristics and simulation-based algorithms have been developed to solve the stochastic project crashing problem \cite{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}.
+Therefore, assuming the activity duration follow a given probability distribution, Monte Carlo simulation methods can be used to estimate the expected project span, since it is is difficult to express the expected project span analytically \cite{burt1971conditional,van1963letter}.
+	Heuristics and simulation-based algorithms have been developed to approximately solve the stochastic project crashing problem \cite{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}.
 Another approach to handle the uncertainty is robust optimization, in which the objective is to minimize the worst case project span within a specified uncertainty set.
@@
 	In this paper, we propose using the concept of stochastic disruptions to model the uncertainty, which is different from the setting of a stochastic program or a robust optimization problem.
-A stochastic disruption is an event that may occur any time in the time horizon and change the system parameters significantly.
+A stochastic disruption is an event that may occur at any time in the time horizon and change the system parameters significantly.
 A few authors apply this idea when the disruption can only occur in a set of specified time periods.
@@
 We present some important properties of this problem using a serial activity network as a special case in Section~\ref{sec:examples}.
-The large scale and the discrete non-convex nature of the SAA problem's extended formulation means it may not be solved efficiently to desirable tolerance level.
+The large scale and the discrete non-convex nature of the SAA problem's extended formulation indicate that it may not be solved efficiently to desirable tolerance level.
 In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
-We show such a decomposition method solves the integer program to the exactness within finite number of iterations.
+We show such a decomposition method solves the integer program to the exactness within a finite number of iterations.
 The experiment results are presented in Section~\ref{sec:results}, including the relationship between the solution quality and the sample size, the comparison between the quality of our solution and the deterministic/semi-stochastic alternative solutions, and the computational performance of the decomposition method presented in Section~\ref{sec:decomposition}.
@@
 For example, suppose we manage a construction project, and we aim to plan against the potential hazard caused by earthquakes.
-It is unlikely for two major earthquakes to hit the same area twice within a year (aftershocks can be considered part of a major earthquake.) It is also reasonable to assume for each activity \(i \in I\), the crashing decision needs to be made at the start of that activity, and cannot be changed afterwards, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
+It is unlikely for two major earthquakes to hit the same area twice within a year (aftershocks can be considered part of a major earthquake.) It is also reasonable to assume for each activity \(i \in I\), the crashing decision needs to be made at the start of that activity, and cannot be changed afterward, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
 The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
@@
 Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterizes the decisions for each realization of the disruption.
-This means that the first stage decision variables are carried out until the disruption, if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
+The first stage decision variables are carried out until the disruption if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
 	\newline
@@
 		\\
-		\(t_{i}\) & \(\qquad\) & nominal starting time of activity \(i\), \(i \in I\);&\\
+		\(t_{i}\) & \(\qquad\) & nominal start time of activity \(i\), \(i \in I\);&\\
 		\(x_{ij}\) & \(\qquad\) & fraction activity \(i\) is crashed by option \(j\) in the nominal plan, \(i \in I, j \in J_i\); &\\
-		\(t_{i}^\omega\) & \(\qquad\) & starting time of activity \(i\) under scenario \(\omega\), \(i \in I, \omega \in \Omega\);&\\
+		\(t_{i}^\omega\) & \(\qquad\) & start time of activity \(i\) under scenario \(\omega\), \(i \in I, \omega \in \Omega\);&\\
 		\(x_{ij}^\omega\) & \(\qquad\) & fraction activity \(i\) is crashed by option \(j\) under scenario \(\omega\), \(i \in I, j \in J_i, \omega \in \Omega \); &\\
@@
 
+\section{NP-Hardness} \label{sec:nphard}
+	In this section, we prove that the project crashing optimization problem under a stochastic disruption is NP-hard.
+The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (DTCT) problem.
+In De et al.~\cite{de1997complexity}, the authors show that an exactly-one-in-three 3SAT (EOIT\_3SAT) problem can be transformed to an instance of the DTCT decision problem in polynomial time.
+Since EOIT\_3SAT is NP-complete (see \cite{Garey1979ComputersAI} for the detailed proof), the authors prove that the DTCT decision problem is also NP-complete, and the DTCT optimization problem is NP-hard.\\
+	\newline
+	Similar to De et al.~\cite{de1997complexity}, we also first introduce the EOIT\_3SAT problem: let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables.
+A literal can be either \(u\) or \(\bar{u} = \neg u\) for a \(u \in U\).
+Let \(C = \{c_1, c_2, \dots, c_m\}\) be a set of clauses, each of which is formed by a disjunction of three literals.
+The EOIT\_3SAT problem asks for whether there is a truth assignment for \(U\) such that each clause in \(C\) has exactly one true literal.
+\\
+	\newline
+	Based on the above instance of EOIT\_3SAT, we formulate an instance of the activity network for the project crashing problem.
+The activity network consists of three layers of nodes: the first layer contains \(4n\) nodes and represents the truth assignment of each variable; the second layer contains \(3m\) nodes and represents the value of clauses; the third layer contains node \(T\) which represents the end of the project.
+The first layer has \(n\) components in parallel, each of which corresponds to a variable and contains 4 nodes connected, as shown in Figure~\ref{fig:layer1}.
+Figure~\ref{fig:layer1} also displays the connection between the first layer and the third layer.
+We set the scenario set as a singleton \(\Omega = \{1\}\) and set the disruption time as \(H^1 = 0\) with probability \(p^1 = 1\).
+We set parameter values associated with the arcs in Figure~\ref{fig:layer1} as:
+	\begin{align*}
+	& D_{u_{j1},u_{j2}} = 0 \qquad \quad d^1_{u_{j1},u_{j2}} = 0  \\
+	& D_{u_{j1},u_{j4}} = 2 \qquad \quad d^1_{u_{j1},u_{j4}} = -1  \\
+	& D_{u_{j2},u_{j3}} = 1 \qquad \quad d^1_{u_{j2},u_{j3}} = 1\\
+	& D_{u_{j4},T} = 0 \qquad \quad \;\; d^1_{u_{j4},T} = 0.
+	\end{align*}
+	We do not allow any activities within the first layer to be crashed, i.e., \(J_{u_{jk}} = \emptyset\), for all \(j = 1,2,\dots, n,\ k = 1,2,3,4\).
+With this setup, the length of the critical path for the \(j\)-th component is always \(2\) for all \(j = 1,2,\dots,n\), as it is optimal to have activity \(u_{j1}\) start at time \(0\).
+However, whether the critical path traverses activities \(u_{j2}\) and \(u_{j3}\) (top path) or the activity \(u_{j4}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\).
+If \(G^1_{u_{j1}} = 1\), the \(G\) variables will take value \(1\) for all subsequent nodes.
+The top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} + D_{u_{j2},u_{j3}} +d^1_{u_{j2},u_{j3}} = 0 + 0 + 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j4}} + d^1_{u_{j1},u_{j4}} = 2 - 1 = 1\), which makes the top path critical.
+If \(G^1_{u_{j1}} = 0\), it is optimal to have activity \(u_{j2}\) start before the disruption as well, i.e., \(G^1_{u_{j2}} = 0\).
+The top path yields a length of \(D_{u_{j1},u_{j4} - 2} + D_{u_{j2},u_{j3}} = 0 + 1 = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j4}} = 2\), which makes the bottom path critical.
+We can consider the value of \(G_{u_{j1}}\) as the truth assignment of variable \(u_j\).
+If the variable \(u_j\) is TRUE, the critical path is the top path; if it is FALSE, the critical path is the bottom path.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\textwidth]{layer1}
+		\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\) in the first layer of the constructed activity network for EOIT\_3SAT.}
+		\label{fig:layer1}
+	\end{figure}
+	\noi The arcs from activities \(u_{j3}\) and \(u_{j4}\) in Figure~\ref{fig:layer1} point to activities in the second layer.
+Next, we construct the second layer of activities and the arcs connecting the first layer and the second layer, in a similar manner as Figure 2(b) in~\cite{de1997complexity}.
+To best illustrate the arc construction, we show an example of a clause, \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\), with two original variables, \(u_j\) and \(u_k\), and one negative complement, \(\bar{u}_{\ell}\).
+We can consider the activity \(c_{ip}\) corresponding to the truth assignment of the variable \(u_p\), for \(p \in \{j,k,\ell\}\).
+For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p4}\) with activity \(c_{ip}\), and activity \(u_{p3}\) with activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\).
+For the negative complement variable \(u_\ell\), we connect activity \(u_{\ell 3}\) with activity \(c_{i \ell}\), and activity \(u_\ell 4\) with activities \(c_{iq},\ q \in \{j,k\}\).
+This example by no means limits the clauses to two variables and one negative complement but aims to showcase the procedure of constructing the network components corresponding to a variable and the negative complement of a variable.
+From now on we refer to the activities representing variables as \(u\)-activities and those representing clauses as \(c\)-activities.\\
+	\newline
+	We let both the nominal duration \(D\) and the disrupted effect \(d\) for the arcs between \(u\)-activities and \(c\)-activities be \(0\). For the arcs between \(c\)-activities and \(T\), we set:
+	%The parameters of arcs in Figure~\ref{fig:layer2} are set as:
+	\begin{align*}
+	%	& D_{u_{p3},c_{iq}} = 0 \qquad \quad d^1_{u_{p3},c_{iq}} = 0 \quad \forall p \in \{j,k\}, q \in \{j,k,\ell\}, p \neq q\\
+	%	& D_{u_{p4},c_{ip}} = 0 \qquad \quad d^1_{u_{p4},c_{ip}} = 0 \quad \forall p \in \{j,k\}\\
+	%	& D_{u_{\ell 3},c_{i\ell}} = 0 \qquad \quad d^1_{u_{\ell 3},c_{i \ell}} = 0\\
+	%	& D_{u_{\ell 4},c_{iq}} = 0 \qquad \quad d^1_{u_{\ell 4},c_{iq}} = 0 \quad \forall q \in \{j,k\}\\
+		& D_{c_{iq},T} = 1 \qquad \quad \;\; d^1_{c_{iq},T} = 0 \;\;\;\quad \forall q \in \{j,k,\ell\}.
+	\end{align*}
+	Unlike the \(u\)-activities, each \(c\)-activity can be crashed with a single option with effectiveness \(e_{c_{ip}1} = 1\), \(\forall p \in \{j,k,\ell\}\).
+The total budget, \(B\), is then set to \(B = 2m\), where \(m\) is the total number of clauses.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.5\textwidth]{layer2}
+		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for EOIT\_3SAT with the arcs connecting it with the first and the third layer.}
+		\label{fig:layer2}
+	\end{figure}
+	\noi For simplicity, the reasoning behind this construction is stated using the example in Figure~\ref{fig:layer2}: for variable \(u_j\), if \(G^1_{u_{j1}} = 1\), the activity \(u_{j4}\) can start at time \(1\), while the earliest time the activity \(u_{j3}\) can start is \(2\).
+If \(G^1_{u_{j1}} = 0\), the activity \(u_{j3}\) can start at time \(1\), while the earliest time the activity \(u_{j4}\) can start is \(2\).
+This is the same for variable \(u_k\) but directly opposite for variable \(u_\ell\).
+The truth assignments indicate which path is critical, which is similar in De et al.~\cite{de1997complexity}, where the truth assignments indicate which crashing option to select for variables nodes.
+\\
+	\newline
+	%Without loss of generality, suppose \(u_j\) is the only TRUE assignment, then activity \(c_{ij}\) can start as early as time \(1\), while the other two \(c\)-activities can only start after time \(2\).
+	We can prove the following lemmas.
+Without loss of generality, a clause can be made of without negative complement of variables.
+For clarity, Figure~\ref{fig:layer2} equivalent for a clause without negative complement is displayed as Figure~\ref{fig:layer2nonneg}, which is used to illustrate the proofs for Lemma~\ref{lemma:onlyOne} and Lemma~\ref{lemma:iff}.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.5\textwidth]{layer2nonneg}
+		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee u_{\ell}\), in the second layer of the constructed activity network for EOIT\_3SAT with the arcs connecting it with the first and the third layer.}
+		\label{fig:layer2nonneg}
+	\end{figure}
+	\begin{lemma} \label{lemma:onlyOne}
+		For any clause \(c_i = u_j \vee u_k \vee u_\ell,\ i = 1,2,\dots,m\), there is at most one activity \(c_{iq^*},\ q^* \in \{j,k,\ell\}\) that has the earliest start time as \(1\), and the start time for \(c_{iq}\) is \(2\), for \(q \in \{j,k,\ell\}, q \neq q^*\).
+	\end{lemma}
+	\begin{proof}[Proof of Lemma \ref{lemma:onlyOne}]
+		Without loss of generality, suppose both \(c_{ij}\) and \(c_{ik}\) can start at time \(1\).
+This means that both \(u_{j3}\) and \(u_{j4}\) needs to start at time \(1\), which is impossible because no matter what value \(G^1_{u_{j1}}\) takes, at least one activity in \(\{u_{j3},u_{j4}\}\) has to start after time \(2\).
+	\end{proof}
+	\begin{lemma} \label{lemma:iff}
+		For any clause \(c_i = u_j \vee u_k \vee u_\ell,\ i = 1,2,\dots,m\), one activity \(c_{iq^*},\ q^* \in \{j,k,\ell\}\) has the earliest start time as \(1\) if and only if variable \(\{u_{q^*}\}\) is the only variable in the clause to which the truth assignment is TRUE.
+	\end{lemma}
+	\begin{proof}[Proof of Lemma \ref{lemma:iff}]
+		Without loss of generality, we assume \(q^* = j\).\\
+		\(\implies\):  Suppose \(u_j\) is FALSE, then activity \(u_{j4}\) can only start after time \(2\), which will lead to the contradiction that \(c_{ij}\) can start as early as time \(1\).
+Suppose either \(u_k\) or \(u_\ell\) is TRUE in addition to \(u_j\).
+Since there is going to be an arc from either activity \(u_{k3}\) or \(u_{\ell 3}\) to activity \(c_{ij}\), and either \(u_{k3}\) or \(u_{\ell_3}\) cannot start before time \(2\), it leads to a contradiction that \(c_{ij}\) can start as early as time \(1\).
+Therefore, if activity \(c_{ij}\) can start at time \(1\), then \(u_j\) is the only variable which is TRUE.\\
+		\(\impliedby\): if only \(u_j\) is TRUE, then \(u_{j4}, u_{k3}\) and \(u_{\ell 3}\) can all start as early as time \(1\), which means that the earliest start time of \(c_{ij}\) is \(1\).
+	\end{proof}
+	%For a clause \(i\) that contains variable \(j\), activity \(u_{j4}\) connects to \(c_{ij}\) and activity \(u_{j3}\) connects to the \(c\)-activities which do not correspond to variable \(u_j\).
+This means that if variable \(u_j\) is assigned a TRUE value, activity \(c_{ij}\) can start as soon as time \(1\) and the other two \(c\)-activities can start no earlier than time \(2\).
+	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of EOIT\_3SAT, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\).
+Since we have a total of \(B = 2m\) units of resource, we can crash all of those \(c\)-activities to achieve a project length of \(2\).
+This means that we can transform an EOIT\_3SAT problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above.
+If we can find a feasible EOIT\_3SAT assignment, it is possible to obtain a project length less than or equal to 2.
+Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption.
+We first formally define the project crashing decision problem under a stochastic disruption:
+	\begin{definition}
+		A project crashing decision problem under a stochastic disruption is: if we solve is model~\ref{prob:extensive}, there a feasible \(\{t,x,G\}\) such that the optimal expected project length is smaller than or equal to \(\mathcal{T}\).
+	\end{definition}
+	\begin{theorem}\label{thm:npcomplete}
+		For an instance of the EOIT\_3SAT problem, we construct the corresponding project crashing decision problem under a stochastic disruption: let \(\Omega = \{1\}\), \(H^1 = 0\), \(\mathcal{T} = 2\), and the precedence relationships, the crashing options and budget are constructed by the process shown in the Section~\ref{sec:nphard}.
+This decision problem has a solution if and only if the given instance of EOIT\_3SAT problem has a solution.
+	\end{theorem}
+	\begin{proof}[Proof of Theorem~\ref{thm:npcomplete}]
+		(polynomial transformation) 
+		%We first show that any instance of the project crashing decision problem is constructed in time that is polynomial in the length of the given instance of EOIT\_3SAT, and has a length that is polynomially related to the length of that instance.
+		Suppose the EOIT\_SAT problem has \(n\) variables and \(m\) clauses, the constructed activity network for the project crashing problem has \(4n + 3m + 1\) activities and \(5n + 12m\) arcs, which are both polynomial in the size of the original EOIT\_SAT problem.
+And all numbers in the project crashing decision problem are smaller than a constant, \(2\).\\
+		(\(\implies\)) Suppose the EOIT\_SAT instance has a solution.
+We have shown that we can start every activity as early as possible, and spend the budget to crash all \(c\)-activities which correspond to the literals with FALSE assignment and have the start time at \(2\).
+\\
+		(\(\impliedby\)) Suppose the project crashing decision problem has a solution \((\hat{t},\hat{x},\hat{G})\) where \(t_T = 2\).
+By Lemma~\ref{lemma:onlyOne} we know that for each clause there are at most one \(c\)-activity that can start at time \(1\), which means in total there must be at least \(2m\) number of \(c\)-activities with a start time later than \(2\).
+Since the crashing budget is exactly \(2m\), if there are more than \(2m\) \(c\)-activities that starts after time \(2\), the project length will be larger than 2, which means that there are exactly \(2m\) number of \(c\)-activities starting at time \(2\).
+This is equivalent to that exactly one \(c\)-activity in each of the \(m\) clauses starts at time \(1\).
+From Lemma~\ref{lemma:iff} we can directly obtain the result that for each clause there is exactly one variable to which the truth assignment is TRUE, which is essentially a solution to the EOIT\_3SAT instance.\\
+		\newline
+		EOIT\_3SAT is a NP-complete problem~\cite{Garey1979ComputersAI}.
+The project crashing decision problem under a stochastic disruption in NP, since we can check in \(O(n^2)\) to check whether a given input is feasible and has \(t_T \leq \mathcal{T}\).
+This complete the proof that the project crashing decision problem under a stochastic disruption is NP-complete.
+	\end{proof}
+	\begin{theorem} \label{thm:nphard}
+		The project crashing optimization problem under a stochastic disruption is NP-hard.
+	\end{theorem}
+	\begin{proof}[Proof of Theorem~\ref{thm:nphard}]
+		From Theorem~\ref{thm:npcomplete} states that the project crashing decision problem under a stochastic disruption is NP-complete.
+This implies the project crashing optimization problem under a stochastic disruption, formulated as model~\ref{prob:extensive}, is NP-hard.
+	\end{proof}
+%	\noi For the network \(G(I,\mathcal{A})\) constructed by the process above, we introduce the decision problem: suppose the disruption time takes a constant value \(0\), is there a set of start time \(t_i,\ i \in I\), a set of crashing plan \(x_{ij},\ i \in I, j \in J_i\) and a set of indicators \(G_i\) showing whether activity \(i\) starts before the disruption or after.
+
 \section{Illustration of Problem Properties via Examples} \label{sec:examples}
-	In this section we show a serial example to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem.
+	In this section, we show examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem.
 In the deterministic project crashing problem, all activities on the critical path should start as soon as possible.
@@
 We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\).
-There we are able to observe whether the disruption happens.
-If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise it is optimal to crash activity 2 with \(1\) amount of resource.
+There we can observe whether the disruption happens.
+If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise, it is optimal to crash activity 2 with \(1\) amount of resource.
 The expected total project span is \(23.4\), as the optimal project span given no disruption is \(21.1\) and that under disruption is \(25.7\).
@@
 	\newline
-	Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the starting time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
-We summarize the reasons of such delay include:
+	Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
+We summarize the reasons for such delay include:
 		\begin{enumerate}
-			\item Some activities might have a shorter length after disruption. It is beneficial to wait a short period of time to capture this advantage.
+			\item Some activities might have a shorter length after the disruption. It is beneficial to wait a short period of time to capture this advantage.
 			\item Even if all possible disruption magnitudes are adverse, which means they lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
@@
 	In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
-We present a following example to showcase this property.
+We present the following example to showcase this property.
 Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}.
-The nominal durations of two activities are \(D_1 = 3, D_2 = 4\).
+The nominal duration of two activities is \(D_1 = 3, D_2 = 4\).
 The disruption does not affect the duration of activity 1, as \(d_1 = 0\), and lengthens the activity 2 by a random variable distributed in a uniform distribution with upper bound \(10\) and lower bound \(0\), as \(d_2 \sim \mathcal{U}(0,10)\).
@@
 The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
-	\textcolor{blue}{NP-hardness proof.}
+	%\textcolor{blue}{NP-hardness proof.}
 	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.
@@
 	\end{subequations}
-	Most of previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
+	Most of the previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
 For example, Gade et al.
-\cite{gade2014decomposition} solve 2SMIPs with pure binary first stage variables using sequential convex approximation of recourse by a branch-and-cut process framework where Gomory cuts are added.
+\cite{gade2014decomposition} solve 2SMIPs with pure binary first stage variables using a sequential convex approximation of recourse by a branch-and-cut process framework where Gomory cuts are added.
 Ahmed et al.
-\cite{zou2016nested} assumes state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
+\cite{zou2016nested} assume state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
 Car{\o}e and Tind \cite{caroe1998shaped} solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not verified.
@@
 For any crashing optimization problem, we can bound the first stage \(t_i\) variables by lower bound \(0\) and upper bound \(T_{\max} = H^{|\Omega|} + t_T^0\), where \(t_T^0\) is the longest \(S\)-\(T\) path of activity network \(\mathcal{G} = (I,\mathcal{A})\) and the arc length of \((i,j) \in \mathcal{A}\) equals to \(D_i\).
-This means that suppose the optimal solution of model~\eqref{prob:extensive} is denoted as \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\), the latter two representing the scenario specific starting time and crashing decisions, we have:
+This means that suppose the optimal solution of model~\eqref{prob:extensive} is denoted as \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\), the latter two representing the scenario specific start time and crashing decisions, we have:
 	\begin{proposition} \label{prop:bounds}
@@
 	\noi Proposition~\ref{prop:bounds} indicates that all \(t_i,\ \forall i \in I\) are bounded on an interval \([0,T_{\max}]\).
-Since there are precedence relationships between activities, the possible range of different activities' starting time can be further limited.
+Since there are precedence relationships between activities, the possible range of different activities' start time can be further limited.
 We first set up two parameters \(H^0 = 0\) and \(H^{|\Omega| + 1} = T_{\max}\) and then define a partition of this interval for each \(i \in I\) to exploit this limitation as follows:
 	\begin{definition}
-		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}_i\), which is an ordered set of two-element tuples \((\underbar{\omega}^q,\bar{\omega}^q)\), indexed by \(q \in \mathcal{Q}_i\) and corresponds to the upper bound scenario index and the lower bound scenario index.
+		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}_i\), which is an ordered set of two-element tuples %\((\underbar{\omega}^q,\bar{\omega}^q)\), 
+		\((\underbar{H}^q,\bar{H}^q)\), 
+		indexed by \(q \in \mathcal{Q}_i\).
+We use \(\underbar{H}^q\) to specify the lower bound of \(q\)-th element of the partition and \(\bar{H}^q\) to specify its upper bound.
+Each of them corresponds to a disruption time of some scenario.
+		%and corresponds to the lower bound scenario index and the upper bound scenario index. the disruption time of 
 		The partition has the following properties:
 		\begin{itemize}
-			\item \(\underbar{\omega}^1 = 0\)
-			\item \(\bar{\omega}^{|\mathcal{Q}_i|} = T_{\max}\)
-			\item \(\bar{\omega}^q = \underbar{\omega}^{q + 1}\).
+			%\item \(\underbar{\omega}^1 = 0\)
+			\item \(\underbar{H}^1 = H^0 = 0\)
+			%\item \(\bar{\omega}^{|\mathcal{Q}_i|} = T_{\max}\)
+			\item \(\bar{H}^{|\mathcal{Q}_i|} = H^{|\Omega| + 1} = T_{\max}\)
+			%\item \(\bar{\omega}^q = \underbar{\omega}^{q + 1}\).
+			\item \(\bar{H}^q = \underbar{H}^{q + 1}\).
 		\end{itemize}
@@
 	\end{figure}
-	\noi For each activity \(i \in I\), with the partition \(\mathcal{P}_i\) defined, we can see the starting time \(t_i\) of the master problem lies in the range specified by one element of \(\mathcal{P}_i\).
+	\noi For each activity \(i \in I\), with the partition \(\mathcal{P}_i\) defined, we can see the start time \(t_i\) of the master problem lies in the range specified by one element of \(\mathcal{P}_i\).
 We introduce an indicator \(y_i^q\), \(\forall i \in I, q \in \mathcal{Q}_i\) in the first stage:
@@
 		y_i^q = \begin{cases}
-			1 & \text{if \(t_i \in [H^{\underbar{\omega}^q},H^{\bar{\omega}^q}]\)}\\
+			%1 & \text{if \(t_i \in [H^{\underbar{\omega}^q},H^{\bar{\omega}^q}]\)}\\
+			1 & \text{if \(t_i \in [\underbar{H}^q,\bar{H}^q]\)}\\
 			0 & \text{otherwise}
@@
 		\begin{align}
-			& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
+			%& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
+			& \sum_{q \in \mathcal{Q}_i} \underbar{H}^q y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} \bar{H}^q y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
 			& \sum_{q \in \mathcal{Q}_i} y_i^q = 1 \qquad \qquad \forall i \in I. \label{cons:sumy1}
@@
 		\begin{align}
-			& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega\\
-			& M_i^{\omega,-} = H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q，
+			%& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega\\
+			%& M_i^{\omega,-} = H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q，
+			& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} \bar{H}^q \hat{y}_i^q - H^\omega\\
+			& M_i^{\omega,-} = H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q，
 		\end{align}
@@
 		\begin{align}
-			H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
-			H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
+			%H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
+			%H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
+			H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} \bar{H}^q \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
+			H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
 		\end{align}
@@
 		\begin{align}
-			H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
-			G_i H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
+			%H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
+			%G_i H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
+			%F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin1}\\
+			%F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin2}\\
+			%F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:FGlin3}
+			H^\omega + \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
+			G_i H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
 			F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin1}\\
@@
 	\end{subequations}
-	In the subproblem, for each activity \(i \in I\), there is only one \(\hat{q} \in \mathcal{Q}_i\) such that \(\hat{y}_i^{\hat{q}} = 1\), which means \(\hat{t}_i \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\).
+	In the subproblem, for each activity \(i \in I\), there is only one \(\hat{q} \in \mathcal{Q}_i\) such that \(\hat{y}_i^{\hat{q}} = 1\), which means \(\hat{t}_i \in 
+	%[H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\). 
+	[\underbar{H}^{\hat{q}},\bar{H}^{\hat{q}}]\). 
 	We examine the validity and effectiveness result of these tightened constraints.
@@
 		\begin{align}
-		H^\omega + G_i \left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right) \geq \hat{t}_i \label{cons:sGnew1}\\
-		H^\omega - (1 - G_i) \left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) \leq \hat{t}_i. \label{cons:sGnew2}
+		%H^\omega + G_i \left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right) \geq \hat{t}_i \label{cons:sGnew1}\\
+		%H^\omega - (1 - G_i) \left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) \leq \hat{t}_i. \label{cons:sGnew2}
+		H^\omega + G_i \left( \bar{H}^{\hat{q}} - H^\omega \right) \geq \hat{t}_i \label{cons:sGnew1}\\
+		H^\omega - (1 - G_i) \left(H^\omega - \underbar{H}^{\hat{q}} \right) \leq \hat{t}_i. \label{cons:sGnew2}
 		\end{align}
 	\end{subequations}
-	For a scenario \(\omega \in \Omega\), there are three possible positions of \(H^\omega\) relative to this range with \(\hat{y}_i^{\hat{q}} = 1\): \(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\), \(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\), or \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\).
-When \(G_i = 1\), the left-hand side of constraint~\eqref{cons:sGnew1} is \(H^{\bar{\omega}^{\hat{q}}}\) and the left-hand side of constraint~\eqref{cons:sGnew2} is \(H^\omega\).
-When \(G_i = 0\), the left-hand side of constraint~\eqref{cons:sGnew1} is \(H^\omega\), and the left-hand side of constraint~\eqref{cons:sGnew2} is \(H^{\underbar{\omega}^{\hat{q}}}\).
+	For a scenario \(\omega \in \Omega\), there are three possible positions of \(H^\omega\) relative to this range with \(\hat{y}_i^{\hat{q}} = 1\): 
+	%\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\), \(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\), or \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\). 
+	\(H^\omega \in [\underbar{H}^{\hat{q}},\bar{H}^{\hat{q}}]\), \(H^\omega < \underbar{H}^{\hat{q}}\), or \(H^\omega > \bar{H}^{\hat{q}}\). 
+	When \(G_i = 1\), the left-hand side of constraint~\eqref{cons:sGnew1} is \(\bar{H}^{\hat{q}}\) and the left-hand side of constraint~\eqref{cons:sGnew2} is \(H^\omega\).
+When \(G_i = 0\), the left-hand side of constraint~\eqref{cons:sGnew1} is \(H^\omega\), and the left-hand side of constraint~\eqref{cons:sGnew2} is
+	%\(H^{\underbar{\omega}^{\hat{q}}}\).
+	\(\underbar{H}^{\hat{q}}\).
 	\begin{enumerate}
 		\item 
-			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\): we can see that if \(\hat{t}_i \geq H^\omega\), by logic \(G_i\) should take value \(1\).
+			\(H^\omega \in
+			 %[H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\): 
+			 [\underbar{H}^{\hat{q}},\bar{H}^{\hat{q}}]\): 
+			 we can see that if \(\hat{t}_i \geq H^\omega\), by logic \(G_i\) should take value \(1\).
 Constraints~\eqref{cons:sGnew} match \(\hat{t}_i \geq H^\omega\) for \(G_i = 1\) and is violated for \(G_i = 0\).
@@
 In addition, the possible value \(G_i\) can take changes from the one shown in~\eqref{cons:Grange} to:
-			\begin{equation*}
-			\left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right) \leq G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1
-			\end{equation*}
+			\begin{equation}
+			%\left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right) \leq G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1
+			\left(\hat{t}_i - H^\omega \right)/\left( \bar{H}^{\hat{q}} - H^\omega \right) \leq G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - \underbar{H}^{\hat{q}} \right) + 1 \label{cons:case1}
+			\end{equation}
 			Since the value of \(M\) decreases compared to constraints~\eqref{cons:Grange}, when \(\hat{t}_i \geq H^\omega\), the lower bound increases and upper bound is \(1\).
@@
 		\item 
-			\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): we can see \(G_i = 1\) is feasible and \(G_i = 0\) violates constraint~\eqref{cons:sGnew1}. The possible value \(G_i\) can take becomes:
-			\begin{align*}
-			G_i \geq \left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right)\\
-			G_i \geq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1.
-			\end{align*}
+			%\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): 
+			\(H^\omega < \underbar{H}^{\hat{q}}\): 
+			we can see \(G_i = 1\) is feasible and \(G_i = 0\) violates constraint~\eqref{cons:sGnew1}. The possible value \(G_i\) can take becomes:
+			\begin{subequations}
+				\begin{align}
+				%G_i \geq \left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right)\\
+				%G_i \geq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1.
+				G_i \geq \left(\hat{t}_i - H^\omega \right)/\left( \bar{H}^{\hat{q}} - H^\omega \right) \label{cons:case2eqn1}\\
+				G_i \geq (\hat{t}_i - H^\omega)/\left(H^\omega - \underbar{H}^{\hat{q}} \right) + 1. \label{cons:case2eqn2}
+				\end{align}
+			\end{subequations}
+			Notice that the inequality~\eqref{cons:case2eqn2} is always weaker than~\eqref{cons:case2eqn1} because the right-hand side of~\eqref{cons:case2eqn2} is smaller than 0 while the right-hand side of~\eqref{cons:case2eqn1} is positive.
 Similar to Case 1, the lower bound increases compared to using a large \(M\) and the upper bound is \(1\), and we achieve a tightened relaxation.
 		\item 
-			\(H^\omega > H^{\bar{\omega}^{\hat{q}}}\): we can see \(G_i = 0\) is feasible and \(G_i = 1\) violates constraint~\eqref{cons:sGnew2}. The possible value \(G_i\) can take becomes:
-			\begin{align*}
-			G_i \leq \left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right)\\
-			G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1.
-			\end{align*}
+			%\(H^\omega > H^{\bar{\omega}^{\hat{q}}}\): 
+			\(H^\omega > \bar{H}^{\hat{q}}\): 
+			we can see \(G_i = 0\) is feasible and \(G_i = 1\) violates constraint~\eqref{cons:sGnew2}. The possible value \(G_i\) can take becomes:
+			\begin{subequations}
+				\begin{align}
+				%G_i \leq \left(\hat{t}_i - H^\omega \right)/\left( H^{\bar{\omega}^{\hat{q}}} - H^\omega \right)\\
+				%G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - H^{\underbar{\omega}^{\hat{q}}} \right) + 1.
+				G_i \leq \left(\hat{t}_i - H^\omega \right)/\left( \bar{H}^{\hat{q}} - H^\omega \right) \label{cons:case3eqn1}\\
+				G_i \leq (\hat{t}_i - H^\omega)/\left(H^\omega - \underbar{H}^{\hat{q}} \right) + 1. \label{cons:case3eqn2}
+				\end{align}
+			\end{subequations}
+			Notice that the inequality~\eqref{cons:case3eqn1} is always weaker than~\eqref{cons:case3eqn2} because the right-hand side of~\eqref{cons:case3eqn1} is greater than 1 while the right-hand side of~\eqref{cons:case3eqn2} is between 0 and 1.
 Similar to Case 1, the upper bound decreases compared to using a large \(M\) and the lower bound is \(0\), and we achieve a tightened relaxation.
 	\end{enumerate}
-	The tightened constraints~\eqref{cons:newBoundsm} is shown to have validity and effectiveness properties.
-However, for the latter two situations, \(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\) and \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\), \(G_i\) can still take fractional value.
+	The tightened constraints~\eqref{cons:newBoundsm} is shown to have validity and effectiveness properties. However, for the latter two situations, 
+	%\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\) and \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\), 
+	\(H^\omega < \underbar{H}^{\hat{q}}\) and \(H^\omega > \bar{H}^{\hat{q}}\), 
+	\(G_i\) can still take fractional value.
 We further tighten the formulation by adding two constraints involving \(y\), such that if the subproblems belonging to those two situations, \(G_i\) can be fixed as either \(0\) or \(1\).
@@
 		\begin{equation}\label{cons:subyG}
-			\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
+			%\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
+			\sum_{q \in \mathcal{Q}_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q \qquad \forall i \in I 
 		\end{equation}
@@
 		\item 
-			\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\): the lower bound is \(0\) since \(y_i^q = 0\) for all elements of partition left of \(\hat{q}\), and the upper bound is \(1\) because \(y_i^q = 0\) for all elements of partition right of \(\hat{q}\).
+			%\(H^\omega \in [H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\): 
+			\(H^\omega \in [\underbar{H}^{\hat{q}},\bar{H}^{\hat{q}}]\): 
+			the lower bound is \(0\) since \(y_i^q = 0\) for all elements of partition left of \(\hat{q}\), and the upper bound is \(1\) because \(y_i^q = 0\) for all elements of partition right of \(\hat{q}\).
 Therefore, \(0 \leq G_i \leq 1\) is valid.
 		\item 
-			\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): the lower bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 1\).
-This matches the logic since \(\hat{t}_i \geq H^\omega\).
+			%\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\): 
+			\(H^\omega < \underbar{H}^{\hat{q}}\): 
+			the lower bound is \(1\) since the summation term, 
+			%\(\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), 
+			\(\sum_{q \in \mathcal{Q}_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), 
+			which forces \(G_i = 1\). This matches the logic since \(\hat{t}_i \geq H^\omega\).
 		\item 
-			\(H^\omega > H^{\bar{\omega}^{\hat{q}}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
+			\(H^\omega > \bar{H}^{\hat{q}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
 This matches the logic since \(\hat{t}_i \leq H^\omega\).
@@
 		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
-		& G_i H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
+		& G_i H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
 		& F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin1t}\\
@@
 		& F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:sFGlin3t}\\
-		& G_i \geq \sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
-		& G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG2t}\\
+		& G_i \geq \sum_{q \in \mathcal{Q}_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
+		& G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG2t}\\
 		& \text{Constraints~\eqref{cons:stG1}-\eqref{cons:subH}}\\
@@
 		\begin{equation*}
-		\forall q^2 \in \mathcal{Q}^2_i, \exists q^1 \in \mathcal{Q}^1_i \text{ s.t. } \bar{\omega}^{q^1} \geq \bar{\omega}^{q^2} \text{ and } \underbar{\omega}^{q^1} \leq \underbar{\omega}^{q^1}.
+		\forall q^2 \in \mathcal{Q}^2_i, \exists q^1 \in \mathcal{Q}^1_i \text{ s.t. } \bar{H}^{q^1} \geq \bar{H}^{q^2} \text{ and } \underbar{H}^{q^1} \leq \underbar{H}^{q^1}.
 		\end{equation*}
 	\end{definition}
-	\noi Suppose at the current iteration for each \(i \in I\), the partition is \(\mathcal{P}_i\) indexed by \(\mathcal{Q}_i\), and this partition is updated from past partitions by only a sequence of refinement defined in Definition~\ref{definition:refinement}, cut~\eqref{cons:cut} can be updated to the following form so that the \(y\) variable has a proper dimension matching the current partition:
+	\noi Suppose at the current iteration for each \(i \in I\), the partition is \(\mathcal{P}_i\) indexed by \(\mathcal{Q}_i\), and this partition is updated from past partitions by only a sequence of refinement defined in Definition~\ref{definition:refinement}.
+Therefore, we can find a set of elements of the current partition,  \(\mathcal{P}_i\) refined from the \(q\)-th element in the partition \(\mathcal{P}^\ell_i\) in the previous iteration \(\ell\).
+We name such set as a ``descendant set", denoted by \(\Delta_i(\ell,q)\).
+Cut~\eqref{cons:cut} can then be updated to the following form so that the \(y\) variable has a proper dimension matching the current partition:
 	\begin{align} \label{cons:updatedcut}
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
-		& \qquad \sum_{i \in I} \sum_{\tilde{q} \in \mathcal{Q}^{\ell}_i} \gamma_{i,\tilde{q}}^{\omega,\ell} \left( \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }y_i^{q} - \hat{y}_i^{\tilde{q},\ell} \right) \qquad \forall \ell = 1,2, \dots.
+		& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad \forall \ell = 1,2, \dots.
 	\end{align}
@@
 			&g^\omega_{\mathcal{P}}(t,x,y) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
-			& \qquad \qquad \sum_{i \in I} \sum_{\tilde{q} \in \mathcal{Q}^{\ell}_i} \gamma_{i,\tilde{q}}^{\omega,\ell} \left( \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }y_i^{q} - \hat{y}_i^{\tilde{q},\ell} \right) \qquad \forall \ell = 1,2, \dots.
+			& \qquad \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad \forall \ell = 1,2, \dots.
 		\end{align}
@@
 		\end{equation}
-		where \[\tilde{y}_i^{\tilde{q}} = \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }y_i^{q} \qquad  \forall i \in I, \tilde{q} \in \mathcal{Q}^\ell_i\]
+		where \[\tilde{y}_i^{q} =  \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} \qquad  \forall i \in I, q \in \mathcal{Q}^\ell_i. \]
 		Suppose for an \(\omega \in \Omega\) and a \((t,x,y)\), we solve the problem \(S_{\mathcal{P}}^\omega\) and obtain the optimal solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},F^{\omega,*})\).
-It is easy to see that by transforming \(F^{\omega,*}\) to \(\tilde{F}^{\omega,*}\) with \[\tilde{F}^{\omega,*,\tilde{q}}_i = \sum_{q \in \mathcal{Q}_i, H^{\bar{\omega}^{q}} \leq H^{\bar{\omega}^{\tilde{q},\ell}},H^{\underbar{\omega}^{q}} \geq H^{\bar{\omega}^{\tilde{q},\ell}} }F_i^{\omega,*,q} \qquad  \forall i \in I, \tilde{q} \in \mathcal{Q}^\ell_i,\]
-		we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\).
-Therefore, inequality~\eqref{cons:gglb}.
+It is easy to see that by transforming \(F^{\omega,*}\) to \(\tilde{F}^{\omega,*}\) with \[\tilde{F}^{\omega,*,q}_i = \sum_{\tilde{q} \in \Delta_i(\ell,q) }F_i^{\omega,*,\tilde{q}} \qquad  \forall i \in I, q \in \mathcal{Q}^\ell_i;\]
+		thus, we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\).
+Therefore, inequality~\eqref{cons:gglb} holds.
 Furthermore, the cut generated at partition \(\mathcal{P}^\ell\) is
-		\[\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right),\]
+		\[\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right),\]
 		 which means that for any feasible \((t,x,\tilde{y})\), we have 
 		 \begin{equation} \label{cons:validglb}
-		 	g^\omega_{\mathcal{P}^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
+		 	g^\omega_{\mathcal{P}^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
 		 \end{equation}
@@
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
-		&\qquad + \sum_{i \in I} \sum_{\tilde{q} \in \mathcal{Q}^{\ell}_i} \gamma_{i,\tilde{q}}^{\omega,\ell} \left( \sum_{q \in \mathcal{Q}_i, \bar{H}_i^{q} \leq \bar{H}_i^{\ell,\tilde{q}},\underbar{H}_i^{q} \geq \underbar{H}_i^{\ell,\tilde{q}} }y_i^{q} - \hat{y}_i^{\tilde{q},\ell} \right) \nonumber \\
-		& \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots\\
+		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)}y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots\\
 		& y_i^q \in \{0,1\} \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i\\
@@
 	We can see that if we keep refining the partition, the generated cuts will become tighter and we will be able to provide an improving lower bound as it progresses.
-The decomposition algorithm is presented as follows:
-	\begin{algorithm}
+We refine the partition by selecting the element of \(\mathcal{P}^\ell\) indexed by \(q\), \(q \in \mathcal{Q}^\ell_i\), for each activity \(i \in I\), where for some scenarios \(\omega \in \Omega\) with \(H^\omega \in [\underbar{H}^q,\bar{H}^q]\), \(G_i^\omega\) has a fractional value, and divide the interval into three subintervals, each covering approximately the same number of scenarios.
+The decomposition algorithm is presented as follows:\\
+	\begin{algorithm}[H]
 		\caption{Decomposition algorithm to solve problem~\eqref{prob:extensive}}
@@
 	\end{algorithm}
-	Finally we prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
+	\noi Finally we prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
 Since every partition update is a refinement and we have a finite set of scenario \(\Omega\), we can prove the finite convergence of Algorithm~\ref{alg:Cut} as long as with the finest partition we reach the optimum of problem~\eqref{prob:extensive}.
@@
 			\begin{aligned}
-			& \eqref{cons:MpSep}-\eqref{cons:MpY1}\\ 
+			& \text{Constraints } \eqref{cons:MpSep}-\eqref{cons:MpY1}\\ 
 			&y_i^q \in \{0,1\} \qquad \forall i \in I, q \in \hat{\mathcal{Q}}_i\\
@@
 		Suppose for \(i \in I\), we denote the index of partition where \(y\) variable takes value \(1\) as \(q_i\).
-Since \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), either \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \leq H^{\underbar{\omega}^q}\}\) or \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \geq H^{\bar{\omega}^q}\}\) is true.
+Since \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\mathcal{Q}}_i\), either \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \leq \underbar{H}^q\}\) or \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \geq \bar{H}^q\}\) is true.
 Thus, constraints~\eqref{cons:syG1t} and~\eqref{cons:syG2t} enforce that \(G_i\) in the problem \((S_{\hat{\mathcal{P}}}^\omega)\) takes binary value because the right-hand side expressions of those two constraints must be \(0\) or \(1\) simultaneously.
@@
 	\begin{proof}
-		From Proposition~\ref{prop:finestPar} we know that with the finest partition \(\hat{\mathcal{P}}\) where for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y)\) is equivalent to solving the extensive formulation.
+		From Proposition~\ref{prop:finestPar} we know that with the finest partition \(\hat{\mathcal{P}}\) where for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\mathcal{Q}}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y)\) is equivalent to solving the extensive formulation.
 Since there are only finite number of scenarios, it takes finite number of steps of refinement to reach the finest partition.
@@
 %\section{Stochastic Mixed Integer Program Extension}
-\section{Conclusions} \label{sec:conclusions}
 \end{comment}
@@
 In other words, what are other alternative solutions that are easier to obtain but possibly inferior?
-How does quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
+How does the quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
 		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
@@
 	We first introduce the PERT network used for test and distribution information used to characterize uncertainty in Section~\ref{subsec:example}.
-In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of solution to model~\eqref{prob:extensive} compared to the alternative ones.
+In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of the solution to model~\eqref{prob:extensive} compared to the alternative ones.
 We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
-Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
+Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation.\\
 	\newline
@@
 Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value.
-We use two activity networks from \textcolor{blue}{Plambeck et al.}, one with 11 activities and the other with 110 activities.
-We also take two examples from Elmgrabhy \cite{Elmaghraby77}, one with 19 activities and the other with 55 activities.
-We manually create one activity network with 14 activities and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}.
+We use an activity network from Plambeck et al.~\cite{plambeck1996sample} with 11 activities, % and the other with 110 activities.
+	one from Elmgrabhy \cite{Elmaghraby77} with 19 activities, and 
+	 %and the other with 55 activities. 
+	 we also manually create one activity network with 14 activities. 
+	 %and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}. 
 	 In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities.\\
@@
 The exponential distribution can best model the drastic change caused by a disruption.
+	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
+	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling random timing and magnitude of the disruption.
+First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET").
+Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), the timing is random but the magnitude is at its expected value (denoted as ``\(H\)Only"), and the magnitude is random but the timing is at its expected value (denoted as ``\(d\)Only").
+Finally, we construct the full stochastic model where both the timing and the magnitude are random (denoted as ``FULL").
+To generate those five solutions, we use a sample of size \(500\).
+We can obtain a point estimation for the upper bound by plugging each of these solutions in the SAA problem with the original \(500\) samples, and we call this estimation as ``in-sample" since these samples are also used to obtain solutions.
+We also sample 20 batches of samples of \(|\Omega| = 5000\), and obtain another upper bound estimation, and its confidence interval, by plugging each of those solutions in every batch of the sample.
+We present the comparison of different solutions of Case 11 in Figure~\ref{fig:value}.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\textwidth]{case11_altValues}
+		\caption{Comparison of quality of alternative solutions to the problem~\eqref{prob:extensive}}
+		\label{fig:value}
+	\end{figure}
+	Figure~\ref{fig:value} shows that the solution quality is poor without considering the uncertainty of disruption timing.
+When we assume the disruption timing is uncertain, the computational effort required to obtain ``\(H\)Only" solution and the fully stochastic solution is on the same level, since we need to include the same number of binary variables.
+To further test whether having a fully stochastic model is the best, we run a pair-wise \(t\)-test.
+The null hypothesis is that whether the difference between the upper bound generated by one alternative solution and that generated by the fully stochastic solution is less than 0.
+The result of the \(t\)-test is displayed in Table~\ref{table:value}.
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{c c c c c c}
+			\hline
+			& Det & Exp & dOnly & HOnly & Full\\
+			In-sample obj & 118.35 & 112.33 & 114.91 & 98.82 & 98.82 \\
+			Out-of-sample obj mean & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 \\
+			t-test result (p-value) & \(< 10^{-5}\) & \(< 10^{-5}\)& \(< 10^{-5}\)&  \(0.001945\)& -\\
+			\hline
+		\end{tabular}
+		\caption{Compare optimal values from alternatives of the disruption model}
+		\label{table:value}
+	\end{table}
+	The pair-wise \(t\)-test rejects all null hypotheses, which shows that the difference between an alternative solution is significantly larger than the fully stochastic solution.
+We can conclude the fully stochastic solution is the best solution, and this justifies the value of having a fully stochastic model, albeit its complexity.
 	\subsection{Simulation Budget} \label{subsec:budget}
@@
 Understanding how the solution quality changes according to different sample sizes is important to help us decide a proper sample size while achieving a decent solution.
-For each test case in Section~\ref{subsec:example}, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(n = 10, 50, 100, 200, 500\) and \(1000\).
-For each of those solutions, we test against a set of \(5000\) samples and obtain the object value.
-We compare the
-	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
-	I	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling random timing and magnitude of the disruption.
-First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET").
-Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), the timing is random but the magnitude is at its expected value (denoted as ``\(H\)Only"), and the magnitude is random but the timing is at its expected value (denoted as ``\(d\)Only").
-Finally, we construct the full stochastic model where both the timing and the magnitude are random (denoted as ``FULL").
+For each test case in Section~\ref{subsec:example}, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(|\Omega| \in \{10, 50, 75, 100, 200, 300, 400, 500\}\).
+For each of those solutions, we test against a set of \(5000\) samples and obtain the object value as a point estimation of the upper bound for each batch.
+We can also obtain the \(95\%\) confidence interval of the lower bound and the upper bound estimation for each sample size.
+We present the result for Case 19 in Figure~\ref{fig:budget}.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\textwidth]{case19_budget_ublb}
+		\caption{Confidence intervals of the lower/upper bound estimation for sample size \(|\Omega| \in \{10, 50, 75, 100, 200, 300, 400, 500\}\)}
+		\label{fig:budget}
+	\end{figure}
+	We can see the gap between the upper bound and the lower bound estimation is decreasing as the sample size increases.
+A decent solution can be obtained by sampling a moderate number of samples, since the upper bound estimation stabilizes when the sample size is greater than \(100\).
+However, to achieve a good lower bound estimation requires a large number of samples.
+This comes from the nature of our uncertainty model, as we need to consider both timing and magnitude of the disruption.
 	\subsection{Computational Performance} \label{subsec:time}
+	In this section we present the computational result of our decomposition method. 
+	%We solve each of the test cases with different sizes of samples \(|\Omega| \in \{100,200,300,400,500,1000\}\) (\(20\) times for each sample size) and show the mean computational time. 
+	We can see the benefit of our decomposition method in Figure~\ref{fig:time}, with the example of Case 11.
+In each master iteration, we solve a master problem with a small number of binary variables.
+Although we need to solve multiple rounds of the master problem and the number of binary variables is increasing since the partition is refined in every iteration, we still can observe a significant improvement by using our proposed decomposition method, especially when the sample size is large.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\textwidth]{case11_time}
+		\caption{Computational performance for sample size \(|\Omega| \in \{100, 200, 300, 400, 500,1000\}\)}
+		\label{fig:time}
+	\end{figure}
+\section{Conclusions} \label{sec:conclusions}
+	In this paper, we establish the concept of stochastic disruption and formulate a two-stage stochastic mixed integer program to model a project crashing optimization problem under the influence of single disruption.
+We use examples to illustrate the counterintuitive properties of our problem that it is possible to delay the start or crash a shorter activity to accelerate the whole project.
+Moreover, the computational results justify the need to use a two-stage stochastic mixed integer program to model this problem.
+It is computationally challenging to solve a two-stage stochastic mixed integer program with binary variables in the second stage.
+Therefore, we propose a decomposition method which uses the logic relationship to generate strong linear programming relaxation of recourse problems and sequentially partitions the master feasible regions to generate Benders' cuts.
+The proposed method can significantly improve the computational performance, especially for the large sample sizes, which we show is often required to obtain a good solution/estimation of bounds.\\
+	\newline
+	There are multiple possible extensions of the results in this paper.
+First, there is still room to improve the computational performance of the decomposition method.
+Currently, the refining process is to divide the partition element with fractional \(G\) values into three partitions evenly.
+This can be enhanced by learning the right partition points so that the lower bound can be tightened faster.
+In addition, we are working on exploiting the network structures to improve the quality of cuts or prune partitions.
 \bibliographystyle{plainnat}

### 2019-02-25 src/python/defClass.py

@@ -1,0 +1,30 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 21 15:16:10 2019
+
+@author: haoxiangyang
+"""
+
+# definition of variables/structures
+# activity network information
+class pInfo:
+    def __init__(self,II,Ji,D,b,eff,B,p0,K,Pre,Succ):
+        self.II = II
+        self.Ji = Ji
+        self.D = D
+        self.b = b
+        self.eff = eff
+        self.B = B
+        self.p0 = p0
+        self.K = K
+        self.Pre = Pre
+        self.Succ = Succ
+        
+# disruption information
+class disInfo:
+    def __init__(self,H,d,prDis):
+        self.H = H
+        self.d = d
+        self.prDis = prDis
+        

### 2019-02-25 src/python/extForm.py

@@ -1,0 +1,169 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 21 17:52:06 2019
+
+@author: haoxiangyang
+"""
+from gurobipy import *
+
+# deterministic formulations
+
+def detBuild(pData):
+    # construct the deterministic crashing problem
+    mp = Model('deterministic_model')
+    mp.setParam('OutputFlag',0)
+    
+    # set up variables
+    t = mp.addVars(pData.II, lb = 0, name = "t")
+    JJ = [(i,j) for i in pData.II for j in pData.Ji[i]]
+    x = mp.addVars(JJ, lb = 0, ub = 1, name = "x")
+    
+    # set up constraints
+    durationConstr = mp.addConstrs((t[k[1]] - t[k[0]] >= pData.D[k[0]]*(1 - sum(pData.eff[k[0]][j]*x[k[0],j] for j in pData.Ji[k[0]])) for k in pData.K), name = "durationConstr")
+    budgetConstr = mp.addConstr((sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B), name = "budgetConstr")
+    xConstr = mp.addConstrs((sum(x[i,j] for j in pData.Ji[i]) <= 1 for i in pData.II), name = "xConstr")
+    mp.setObjective(t[0],GRB.MINIMIZE)
+    mp.update()
+    mp.optimize()
+    
+    tdet = {}
+    xdet = {}
+    fdet = mp.objVal
+    for i in pData.II:
+        tdet[i] = t[i].X
+    for j in JJ:
+        xdet[j] = x[j].X
+    return tdet,xdet,fdet
+
+def expModel(pData,eH,ed,M = 9999999):
+    # script for two-stage expected time expected magnitude disruption program
+    mp = Model('expected_model')
+    
+    # set up variables
+    t0 = mp.addVars(pData.II, lb = 0, name = "t0")
+    JJ = [(i,j) for i in pData.II for j in pData.Ji[i]]
+    x0 = mp.addVars(JJ, lb = 0, ub = 1, name = "x0")
+    t = mp.addVars(pData.II, lb = 0, name = "t")
+    x = mp.addVars(JJ, lb = 0, ub = 1, name = "x")
+    G = mp.addVars(pData.II, vtype=GRB.BINARY, name = "G")
[…]

### 2019-02-25 src/python/readIn.py

@@ -1,0 +1,197 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 21 15:20:53 2019
+
+@author: haoxiangyang
+"""
+import os
+import pickle
+import csv
+import numpy as np
+from defClass import *
+
+distrList = ['normal','exponential','lognormal','uniform']
+
+# read in the project activity information and link information
+def readInP(pInputAdd,kInputAdd):
+    fi = open(pInputAdd,"r")
+    csvReader = csv.reader(fi,dialect = 'excel')
+    pRaw = []
+    for item in csvReader:
+        pRaw.append(item)
+    fi.close()
+    
+    fi = open(kInputAdd,"r")
+    csvReader = csv.reader(fi,dialect = 'excel')
+    kRaw = []
+    for item in csvReader:
+        kRaw.append(item)
+    fi.close()
+    
+    np = len(pRaw)
+    mp = len(pRaw[0])
+    nk = len(kRaw)
+    
+    # total budget and nominal scenario probability
+    B = float(pRaw[0][0])
+    p0 = float(pRaw[0][1])
+    
+    II = [0]
+    Ji = {}
+    D = {}
+    D[0] = 0
+    Ji[0] = []
+    
+    b = {}
+    b[0] = {}
+    eff = {}
+    eff[0] = {}
+    
+    # read in the activity information
+    for i in range(1,np):
+        lineID = int(pRaw[i][0])
+        II.append(lineID)
+        D[lineID] = float(pRaw[i][1])
+        
+        jStart = 2
+        Ji[lineID] = []
+        b[lineID] = {}
+        eff[lineID] = {}
+        jCounter = 0
+        while jStart <= mp-1:
+            jCounter += 1
+            Ji[lineID].append(jCounter)
+            b[lineID][jCounter] = float(pRaw[i][2*jCounter])
+            eff[lineID][jCounter] = float(pRaw[i][1+2*jCounter])
+            jStart += 2
+    
+    # read in the activity precedence information
+    K = []
+    Pre = {}
+    Pre[0] = []
+    Succ = {}
+    Succ[0] = []
+    for i in II:
+        if i != 0:
+            K.append((i,0))
+            Pre[0].append(i)
+            Pre[i] = []
+            Succ[i] = [0]
+    
+    for k in range(nk):
+        fromI = int(kRaw[k][0])
+        toI = int(kRaw[k][1])
[…]

### 2019-02-25 src/python/tighten.py

@@ -1,0 +1,45 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Feb 25 16:10:33 2019
+
+@author: haoxiangyang
+"""
+
+# auxiliary functions to tighten the branch-and-cut process
+
+import numpy as np
+
+def longestPath(pData):
+    # obtain the longest path using negative Dijkstra
+    lDict = {}
+    finishedList = []
+    activeList = []
+    for i in pData.II:
+        if pData.Pre[i] == []:
+            lDict[i] = 0
+        else:
+            lDict[i] = -np.inf
+    while len(finishedList) < len(pData.II):
+        for i in pData.II:
+            if not((i in activeList) or (i in finishedList)):
+                enterBool = True
+                for j in pData.Pre[i]:
+                    if not(j in finishedList):
+                        enterBool = False
+                if enterBool:
+                    activeList.append(i)
+        # find the largest activity in activeList
+        maxVal = -np.inf
+        maxInd = -1
+        for iInd in activeList:
+            if maxVal < lDict[iInd]:
+                maxVal = lDict[iInd]
+                maxInd = iInd
+        # update the activities connected to maxInd
+        for j in pData.Succ[maxInd]:
+            if lDict[j] < lDict[maxInd] + pData.D[maxInd]:
+                lDict[j] = lDict[maxInd] + pData.D[maxInd]
+        finishedList.append(maxInd)
+        activeList.remove(maxInd)
+    return lDict

### 2019-02-25 src/python/ubCalFunc.py

@@ -1,0 +1,67 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Feb  4 11:52:38 2019
+
+@author: haoxiangyang
+"""
+
+from multiprocessing import Pool
+from gurobipy import *
+
+def subInt(pData,dDomega,xh,th,M = 999999,returnOpt = 0):
+    # solve the mixed integer subproblem to compute the scenario ub
+    sp = Model('subInt')
+    sp.Params.OutputFlag = 0
+    t = sp.addVars(pData.II, lb = 0)
+    JJ = [(i,j) for i in pData.II for j in pData.Ji[i]]
+    x = sp.addVars(JJ, lb = 0, ub = 1)
+    s = sp.addVars(JJ, lb = 0, ub = 1)
+    G = sp.addVars(pData.II, vtype = GRB.BINARY)
+
+    # add the basic sub problem constraints
+    FCons = sp.addConstrs(dDomega.H - (1 - G[i])*M <= th[i] for i in pData.II)
+    GCons = sp.addConstrs(dDomega.H + G[i]*M >= th[i] for i in pData.II)
+
+    tGcons1 = sp.addConstrs(t[i] <= th[i] + M*G[i] for i in pData.II)
+    tGcons2 = sp.addConstrs(t[i] >= th[i] - M*G[i] for i in pData.II)
+    boundT = sp.addConstrs(t[i] >= dDomega.H*G[i] for i in pData.II)
+    xGcons1 = sp.addConstrs(x[i,j] <= xh[i,j] + G[i] for i in pData.II for j in pData.Ji[i])
+    xGcons2 = sp.addConstrs(x[i,j] >= xh[i,j] - G[i] for i in pData.II for j in pData.Ji[i])
+
+    budgetConstr = sp.addConstr(sum(sum(pData.b[i][j]*x[i,j] for j in pData.Ji[i]) for i in pData.II) <= pData.B)
+    xConstr = sp.addConstrs(sum(x[i,j] for j in pData.Ji[i]) <= 1 for i in pData.II for j in pData.Ji[i])
+    # linearize the bilinear term of x[i,j]*G[i]
+    xGlin1 = sp.addConstrs(s[i,j] <= G[i] for i in pData.II for j in pData.Ji[i])
+    xGlin2 = sp.addConstrs(s[i,j] <= x[i,j] for i in pData.II for j in pData.Ji[i])
[…]

### 2019-05-09 Writeup/PERT_Paper_Draft2.tex
Fixed bugs in sub.jl

--- 2019-02-25 Writeup/PERT_Paper_Draft1.tex
@@
 \newcommand{\cF}{{\cal F}}
+\newcommand{\cA}{{\cal A}}
 \newcommand{\cG}{{\cal G}}
@@
 \newcommand{\cP}{{\cal P}}
+\newcommand{\tcb}{\textcolor{blue}}
 \newcommand{\underv}{\mbox{$\underbar{$v$}$}}
@@
 	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath} (see S{\"o}derlund \cite{soderlund2004building} for an overview).
-A project is a collection of activities \(I\)
-	 %of some duration \(D_i, i \in I\)
-	 , and there are precedence relationships, \(\mathcal{A} \subseteq I \times I\), between activities due to logical or technological considerations.
-A project can be characterized by an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\).
-An arc \((i,k) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(k\), and its length shows the required separation between their start time,
-	 %duration of an activity 
-	 \(D_{ik}\).
-An activity cannot start until all its predecessors are completed, while multiple activities can be processed at the same time without an upper limit, as long as the precedence requirements are satisfied.
+A project is a collection of activities, between which there are precedence relationships due to logical or technological considerations.
+The precedence relationship is usually reflected as a required separation time between the start time of two activities.
+Multiple activities can be processed at the same time and there is no limit on how many activities can be processed simultaneously, as long as the precedence requirements are satisfied.
 See Elmaghraby~\cite{Elmaghraby77} for a detailed treatment of activity networks.
 In this setting, ``crashing" is an action that consumes a certain amount of resource and shortens the duration of activities accordingly~\cite{kuhl2008dynamic}.
-We can apply a finite set of crashing options, \(j \in J_i\), to activity \(i \in I\).
-One unit application of each option incurs a cost of \(b_{ij}\), \textcolor{blue}{while it decreases all required separation lengths starting from activity \(i\) by \(D_{ik}e_{ij},\ \forall (i,k) \in \mathcal{A}\); i.e., the crashed duration is proportional to both the nominal separation length and the crashing decision.} The total cost of crashing cannot exceed a given budget, \(B\).
 The deterministic optimization problem for crashing an activity network was proposed in the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
-The goal is to complete all activities in minimum time by allocating resources under one or more budget constraints.
-We create two dummy activities \(S\) and \(T\) to represent the start and the end of the entire project.
-Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \), and they both have zero duration, \(D_{Si} = D_{iT} = 0,\ \forall i \in I\).
-Given $t_S \equiv 0$, the objective is then to minimize the start time of activity \(T\).
-Thus, we formulate the deterministic project crashing problem as:
-	\begin{subequations} \label{prob:static}
-		\begin{align}
-		\min \quad & t_T &\\
-		\text{s.t.} \quad &  t_k - t_i \geq D_{ik}\left(1 - \sum_{j \in J_i} x_{ij} e_{ij}\right) \qquad \qquad \forall \,(i,k) \in \mathcal{A} \label{cons:dSep}\\
-		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
-		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
-		& x_{ij} \geq 0  \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:dxub}\\
-		& t_S = 0. \label{cons:dNonnegt}
-		\end{align}
-	\end{subequations}
-	In this formulation, \(t_i\) represents the start time of activity \(i \in I\).
-We aim to minimize the project span, which is the start time of the terminal activity, \(t_T\).
-Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finish time of activity \(i\) is \(t_i + D_{ik} (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
-Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
-Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities since activity \(S\) precedes every other activity.\\
-	% In constraint~\eqref{cons:dxub}, we can put an artificial upper bound \(1\) on all crashing decisions \(x_{ij}\) by taking proper values of \(e_{ij}\). \\
+The goal is to complete all activities in minimum time by allocating resources under one or more budget constraints.\\
 	\newline
@@
 Extensions that allow for more general assumptions followed \cite{Elmaghraby77}, and Monte Carlo simulation plays a role in estimating the expected project span, which is difficult to express analytically \cite{burt1971conditional,van1963letter}.
-	%The deterministic model can be extended to incorporate uncertainty of activity duration, starting with the program evaluation and review technique (PERT) \cite{malcolm1959application}.
-The PERT model assumes that activities are independently distributed with beta distributions, and the expected project span can be approximated by a normal distribution.
-However, this assumption may not be accurate for a general case~\cite{Elmaghraby77}.
-Therefore, assuming the activity duration follow a given probability distribution, Monte Carlo simulation methods can be used to estimate the expected project span, since it is is difficult to express the expected project span analytically \cite{burt1971conditional,van1963letter}.
 	Heuristics and simulation-based algorithms have been developed to approximately solve the stochastic project crashing problem \cite{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}.
@@
 \section{Problem Formulation} \label{sec:formulation}
-	For a project crashing problem under stochastic disruptions, we assume at most one stochastic disruption can occur at a random time in the project span, since for the applications we are interested in (natural disasters, terrorist attacks, major market crashes, etc.), it is unlikely for two disruptions to occur in entire the time horizon.
-For example, suppose we manage a construction project, and we aim to plan against the potential hazard caused by earthquakes.
-It is unlikely for two major earthquakes to hit the same area twice within a year (aftershocks can be considered part of a major earthquake.) It is also reasonable to assume for each activity \(i \in I\), the crashing decision needs to be made at the start of that activity, and cannot be changed afterward, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
-The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
-It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}.
-In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\).
-For each scenario \(\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\).
-\\
-	\newline
-	If there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
-The definition of our first stage is different from the traditional stochastic program setting.
-Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterizes the decisions for each realization of the disruption.
-The first stage decision variables are carried out until the disruption if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
-	\newline
-	The notation for the model is displayed as follows:
+	Nomenclature:
+	%The notation for the model is displayed as follows:
 	\begin{longtable}[H]{ l l l l }
@@
 		\\
-		\(D_{i}\)& \(\qquad\) & original duration of activity \(i\), \(i \in I\);&\\
+		\(D_{ik}\)& \(\qquad\) & nominal separation time between activity \(i\) and \(k\), \((i,k) \in \cA\);&\\
 		\(e_{ij}\) & \(\qquad\) & effectiveness of crashing option \(j\), \(i \in I, j \in J_i\);&\\
-		\(B\) & \(\qquad\) & total budget;&\\
-		\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j\), \(i \in I, j \in J_i\);&\\
+		\(B\) & \(\qquad\) & total budget of crashing options;&\\
+		\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j\) for activity \(i\), \(i \in I, j \in J_i\);&\\
 		\(H^\omega\) &\(\qquad\) & disruption time in scenario \(\omega\), \(\omega \in \Omega\);&\\
@@
 	\end{longtable}
-	\noi The extensive formulation of the two-stage stochastic program is shown as formulation~\eqref{prob:extensive}:
+	\noi We first review the formulation of the deterministic crashing optimization problem in~\cite{fulkerson1961network, kelley1961criticalpath}.
+A set of activities, \(I\), together with the precedence relationships, \(\mathcal{A} \subseteq I \times I\) form an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\) which represent the project.
+An arc \((i,k) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(k\), and its length, \(D_{ik}\), shows that the start time of activity \(i\) has to be at least \(D_{ik}\) before the start time of activity \(k\).
+We create two dummy activities \(S, T \in I\) to represent the start and the end of the entire project.
+Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \), and they both have zero duration, \(D_{Si} = D_{iT} = 0,\ \forall i \in I\).
+We can apply a finite set of crashing options, \(j \in J_i\), to activity \(i \in I\).
+One unit application of each option incurs a cost of \(b_{ij}\), while it decreases all required separation lengths starting from activity \(i\) by \(D_{ik}e_{ij},\ \forall (i,k) \in \mathcal{A}\), where \(e_{ij} \in [0,1]\) denotes the unit effectiveness of the crashing option \(j\).
+For example, suppose the required separation between the start time of activity \(1\) and \(2\) is \(D_{12} = 10\), and applying one unit of crashing option \(1\) on activity \(1\) decreases that to its half; i.e., \(e_{11} = 0.5\).
+If we apply \(0.4\) unit of crashing option \(1\) on activity \(1\), \(x_{11} = 0.4\), the required separation between activity \(1\) and \(2\) becomes \(10(1 - 0.4 \times 0.5) = 8\).
+The total cost of crashing cannot exceed a given budget, \(B\).
+Given $t_S \equiv 0$, the objective is then to minimize the start time of activity \(T\).
+Thus, we formulate the deterministic project crashing problem as:
+	\begin{subequations} \label{prob:static}
+		\begin{align}
+		\min \quad & t_T &\\
+		\text{s.t.} \quad &  t_k - t_i \geq D_{ik}\left(1 - \sum_{j \in J_i} x_{ij} e_{ij}\right) \qquad \qquad \forall \,(i,k) \in \mathcal{A} \label{cons:dSep}\\
+		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
+		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
+		& x_{ij} \geq 0  \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:dxub}\\
+		& t_S = 0. \label{cons:dNonnegt}
+		\end{align}
+	\end{subequations}
+	In this formulation, \(t_i\) represents the start time of activity \(i \in I\).
+We aim to minimize the project span, which is the start time of the terminal activity, \(t_T\).
+Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finish time of activity \(i\) is \(t_i + D_{ik} (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
+Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
+Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities since activity \(S\) precedes every other activity.\\
+	\newline
+	For a project crashing problem under stochastic disruptions, we assume at most one stochastic disruption can occur at a random time in the project span, since for the applications we are interested in (natural disasters, terrorist attacks, major market crashes, etc.), it is unlikely for two disruptions to occur in entire the time horizon.
+For example, suppose we manage a construction project, and we aim to plan against the potential hazard caused by earthquakes.
+It is unlikely for two major earthquakes to hit the same area twice within a year (aftershocks can be considered part of a major earthquake.) It is also reasonable to assume for each activity \(i \in I\), the crashing decision needs to be made at the start of that activity, and cannot be changed afterward, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
+The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
+It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}.
+In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\).
+For each scenario \(\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration between activity \(i\) and \(k\), \(d_{ik}, \forall (i,k) \in \cA\).
+\\
+	\newline
+	If there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
+The definition of our first stage is different from the traditional stochastic program setting.
+Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterizes the decisions for each realization of the disruption.
+The first stage decision variables are carried out until the disruption if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
+	\newline
+	The extensive formulation of the two-stage stochastic program is shown as formulation~\eqref{prob:extensive}:
 	\begin{subequations} \label{prob:extensive}
@@
 		\min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\
-		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:Sep}\\
+		\text{s.t.} \quad & t_k - t_i \geq D_{ik}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \, (i,k) \in \mathcal{A} \label{cons:Sep}\\
 		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:Budget}\\
@@
 		& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xG2}\\
-		& t_k^\omega - t_i^\omega \geq D_i + d_i^\omega G_i^\omega -\sum_{j \in J_i} D_i e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij}^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:scenSep}\\
+		& t_k^\omega - t_i^\omega \geq D_{ik} + d_{ik}^\omega G_i^\omega -\sum_{j \in J_i} D_{ik} e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_{ik}^\omega e_{ij} z_{ij}^\omega \qquad \qquad \forall \,(i,k) \in \cA, \omega \in \Omega \label{cons:scenSep}\\
 		& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:scenBudget1}\\
@@
 Therefore, we set up non-anticipativity constraints~\eqref{cons:tG1}-\eqref{cons:xG2}.
-For each scenario, the duration of activity \(i\) becomes \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\), which expands to the form of constraint~\eqref{cons:scenSep}.
-If \(G_i^\omega = 0\), which means activity \(i\) starts before the disruption time of scenario \(\omega\), this expression is the same as \(D_i (1 - \sum_{j \in J_i} e_{ij}x_{ij})\) since \(x_{ij} = x_{ij}^\omega\) is enforced by constraints~\eqref{cons:xG1} and~\eqref{cons:xG2}.
-If \(G_i^\omega = 1\), then the duration of activity \(i\) is changed to \(D_i + d_i^\omega\).
-The expression \((D_i + d_i^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\) contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(z_{ij}^\omega\) and constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.
+For each scenario, the duration between activity \(i\) and \(k\) becomes \((D_{ik} + d_{ik}^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\), which expands to the form of constraint~\eqref{cons:scenSep}.
+If \(G_i^\omega = 0\), which means activity \(i\) starts before the disruption time of scenario \(\omega\), this expression is the same as \(D_{ik} (1 - \sum_{j \in J_i} e_{ij}x_{ij})\) since \(x_{ij} = x_{ij}^\omega\) is enforced by constraints~\eqref{cons:xG1} and~\eqref{cons:xG2}.
+If \(G_i^\omega = 1\), then the duration between activity \(i\) and \(k\) is changed to \(D_{ik} + d_{ik}^\omega\).
+The expression \((D_{ik} + d_{ik}^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\) contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(z_{ij}^\omega\) and constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.
 
@@
 	In this section, we prove that the project crashing optimization problem under a stochastic disruption is NP-hard.
-The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (DTCT) problem.
-In De et al.~\cite{de1997complexity}, the authors show that an exactly-one-in-three 3SAT (EOIT\_3SAT) problem can be transformed to an instance of the DTCT decision problem in polynomial time.
-Since EOIT\_3SAT is NP-complete (see \cite{Garey1979ComputersAI} for the detailed proof), the authors prove that the DTCT decision problem is also NP-complete, and the DTCT optimization problem is NP-hard.\\
-	\newline
-	Similar to De et al.~\cite{de1997complexity}, we also first introduce the EOIT\_3SAT problem: let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables.
+The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (\verb|DTCT|) problem.
+In De et al.~\cite{de1997complexity}, the authors show that an exactly-one-in-three \verb|3SAT| (\verb|EOIT_3SAT|) problem can be transformed to an instance of the \verb|DTCT| decision problem in polynomial time.
+Since \verb|EOIT_3SAT| is NP-complete (see \cite{Garey1979ComputersAI} for the detailed proof), the authors prove that the \verb|DTCT| decision problem is also NP-complete, and the \verb|DTCT| optimization problem is NP-hard.\\
+	\newline
+	Similar to De et al.~\cite{de1997complexity}, we also first introduce the \verb|EOIT_3SAT| problem: let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables.
 A literal can be either \(u\) or \(\bar{u} = \neg u\) for a \(u \in U\).
 Let \(C = \{c_1, c_2, \dots, c_m\}\) be a set of clauses, each of which is formed by a disjunction of three literals.
-The EOIT\_3SAT problem asks for whether there is a truth assignment for \(U\) such that each clause in \(C\) has exactly one true literal.
-\\
-	\newline
-	Based on the above instance of EOIT\_3SAT, we formulate an instance of the activity network for the project crashing problem.
-The activity network consists of three layers of nodes: the first layer contains \(4n\) nodes and represents the truth assignment of each variable; the second layer contains \(3m\) nodes and represents the value of clauses; the third layer contains node \(T\) which represents the end of the project.
-The first layer has \(n\) components in parallel, each of which corresponds to a variable and contains 4 nodes connected, as shown in Figure~\ref{fig:layer1}.
-Figure~\ref{fig:layer1} also displays the connection between the first layer and the third layer.
+The \verb|EOIT_3SAT| problem asks for whether there is a truth assignment for \(U\) such that each clause in \(C\) has exactly one true literal.
+\\
+	\newline
+	Based on the above instance of \verb|EOIT_3SAT|, we formulate an instance of the activity network for the project crashing problem.
+The activity network consists of three layers of nodes: the first layer contains \(3n\) nodes and represents the truth assignment of each variable; the second layer contains \(3m\) nodes and represents the value of clauses; the third layer contains node \(T\) which represents the end of the project.
+The first layer has \(n\) components in parallel, each of which corresponds to a variable and contains 3 nodes connected, denoted as \(u_{j1},\ u_{j2}\) and \(u_{j3}\) for the component \(j\), as shown in Figure~\ref{fig:layer1}.
+Figure~\ref{fig:layer1} also displays how the first layer connects to the third layer.
 We set the scenario set as a singleton \(\Omega = \{1\}\) and set the disruption time as \(H^1 = 0\) with probability \(p^1 = 1\).
@@
 	\begin{align*}
-	& D_{u_{j1},u_{j2}} = 0 \qquad \quad d^1_{u_{j1},u_{j2}} = 0  \\
-	& D_{u_{j1},u_{j4}} = 2 \qquad \quad d^1_{u_{j1},u_{j4}} = -1  \\
-	& D_{u_{j2},u_{j3}} = 1 \qquad \quad d^1_{u_{j2},u_{j3}} = 1\\
-	& D_{u_{j4},T} = 0 \qquad \quad \;\; d^1_{u_{j4},T} = 0.
+	& D_{u_{j1},u_{j2}} = 1 \qquad \quad d^1_{u_{j1},u_{j2}} = 1\\
+	& D_{u_{j1},u_{j3}} = 2 \qquad \quad d^1_{u_{j1},u_{j3}} = -1  \\
+	& D_{u_{j3},T} = 0 \qquad \quad \;\; d^1_{u_{j3},T} = 0.
 	\end{align*}
-	We do not allow any activities within the first layer to be crashed, i.e., \(J_{u_{jk}} = \emptyset\), for all \(j = 1,2,\dots, n,\ k = 1,2,3,4\).
+	We do not allow any activities within the first layer to be crashed, i.e., \(J_{u_{jk}} = \emptyset\), for all \(j = 1,2,\dots, n,\ k = 1,2,3\).
 With this setup, the length of the critical path for the \(j\)-th component is always \(2\) for all \(j = 1,2,\dots,n\), as it is optimal to have activity \(u_{j1}\) start at time \(0\).
-However, whether the critical path traverses activities \(u_{j2}\) and \(u_{j3}\) (top path) or the activity \(u_{j4}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\).
+However, whether the critical path traverses activities \(u_{j2}\) (top path) or the activity \(u_{j3}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\).
 If \(G^1_{u_{j1}} = 1\), the \(G\) variables will take value \(1\) for all subsequent nodes.
-The top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} + D_{u_{j2},u_{j3}} +d^1_{u_{j2},u_{j3}} = 0 + 0 + 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j4}} + d^1_{u_{j1},u_{j4}} = 2 - 1 = 1\), which makes the top path critical.
+The top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} = 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} + d^1_{u_{j1},u_{j3}} = 2 - 1 = 1\), which makes the top path critical.
 If \(G^1_{u_{j1}} = 0\), it is optimal to have activity \(u_{j2}\) start before the disruption as well, i.e., \(G^1_{u_{j2}} = 0\).
-The top path yields a length of \(D_{u_{j1},u_{j4} - 2} + D_{u_{j2},u_{j3}} = 0 + 1 = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j4}} = 2\), which makes the bottom path critical.
-We can consider the value of \(G_{u_{j1}}\) as the truth assignment of variable \(u_j\).
+The top path yields a length of \(D_{u_{j1},u_{j2}} = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} = 2\), which makes the bottom path critical.
+We can consider the value of \(G^1_{u_{j1}}\) as the truth assignment of variable \(u_j\).
 If the variable \(u_j\) is TRUE, the critical path is the top path; if it is FALSE, the critical path is the bottom path.
@@
 		\includegraphics[width=0.8\textwidth]{layer1}
-		\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\) in the first layer of the constructed activity network for EOIT\_3SAT.}
+		\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\) in the first layer of the constructed activity network for \texttt{EOIT\char`_3SAT}.}
 		\label{fig:layer1}
 	\end{figure}
-	\noi The arcs from activities \(u_{j3}\) and \(u_{j4}\) in Figure~\ref{fig:layer1} point to activities in the second layer.
+	\noi The arcs from activities \(u_{j2}\) and \(u_{j3}\) in Figure~\ref{fig:layer1} point to activities in the second layer.
 Next, we construct the second layer of activities and the arcs connecting the first layer and the second layer, in a similar manner as Figure 2(b) in~\cite{de1997complexity}.
@@
 We can consider the activity \(c_{ip}\) corresponding to the truth assignment of the variable \(u_p\), for \(p \in \{j,k,\ell\}\).
-For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p4}\) with activity \(c_{ip}\), and activity \(u_{p3}\) with activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\).
-For the negative complement variable \(u_\ell\), we connect activity \(u_{\ell 3}\) with activity \(c_{i \ell}\), and activity \(u_\ell 4\) with activities \(c_{iq},\ q \in \{j,k\}\).
+For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p3}\) with activity \(c_{ip}\), and activity \(u_{p2}\) with activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\).
+For the negative complement variable \(u_\ell\), we connect activity \(u_{\ell 2}\) with activity \(c_{i \ell}\), and activity \(u_{\ell 3}\) with activities \(c_{iq},\ q \in \{j,k\}\).
 This example by no means limits the clauses to two variables and one negative complement but aims to showcase the procedure of constructing the network components corresponding to a variable and the negative complement of a variable.
@@
 	\begin{align*}
-	%	& D_{u_{p3},c_{iq}} = 0 \qquad \quad d^1_{u_{p3},c_{iq}} = 0 \quad \forall p \in \{j,k\}, q \in \{j,k,\ell\}, p \neq q\\
-	%	& D_{u_{p4},c_{ip}} = 0 \qquad \quad d^1_{u_{p4},c_{ip}} = 0 \quad \forall p \in \{j,k\}\\
-	%	& D_{u_{\ell 3},c_{i\ell}} = 0 \qquad \quad d^1_{u_{\ell 3},c_{i \ell}} = 0\\
-	%	& D_{u_{\ell 4},c_{iq}} = 0 \qquad \quad d^1_{u_{\ell 4},c_{iq}} = 0 \quad \forall q \in \{j,k\}\\
 		& D_{c_{iq},T} = 1 \qquad \quad \;\; d^1_{c_{iq},T} = 0 \;\;\;\quad \forall q \in \{j,k,\ell\}.
@@
 		\includegraphics[width=0.5\textwidth]{layer2}
-		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for EOIT\_3SAT with the arcs connecting it with the first and the third layer.}
+		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer.}
 		\label{fig:layer2}
@@
 	\newline
-	%Without loss of generality, suppose \(u_j\) is the only TRUE assignment, then activity \(c_{ij}\) can start as early as time \(1\), while the other two \(c\)-activities can only start after time \(2\).
 	We can prove the following lemmas.
@@
 		\includegraphics[width=0.5\textwidth]{layer2nonneg}
-		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee u_{\ell}\), in the second layer of the constructed activity network for EOIT\_3SAT with the arcs connecting it with the first and the third layer.}
+		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee u_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer.}
 		\label{fig:layer2nonneg}
@@
 		Without loss of generality, suppose both \(c_{ij}\) and \(c_{ik}\) can start at time \(1\).
-This means that both \(u_{j3}\) and \(u_{j4}\) needs to start at time \(1\), which is impossible because no matter what value \(G^1_{u_{j1}}\) takes, at least one activity in \(\{u_{j3},u_{j4}\}\) has to start after time \(2\).
+This means that both \(u_{j2}\) and \(u_{j3}\) needs to start at time \(1\), which is impossible because no matter what value \(G^1_{u_{j1}}\) takes, at least one activity in \(\{u_{j2},u_{j3}\}\) has to start after time \(2\).
 	\end{proof}
@@
 		Without loss of generality, we assume \(q^* = j\).\\
-		\(\implies\):  Suppose \(u_j\) is FALSE, then activity \(u_{j4}\) can only start after time \(2\), which will lead to the contradiction that \(c_{ij}\) can start as early as time \(1\).
+		\(\implies\):  Suppose \(u_j\) is FALSE, then activity \(u_{j3}\) can only start after time \(2\), which will lead to the contradiction that \(c_{ij}\) can start as early as time \(1\).
 Suppose either \(u_k\) or \(u_\ell\) is TRUE in addition to \(u_j\).
-Since there is going to be an arc from either activity \(u_{k3}\) or \(u_{\ell 3}\) to activity \(c_{ij}\), and either \(u_{k3}\) or \(u_{\ell_3}\) cannot start before time \(2\), it leads to a contradiction that \(c_{ij}\) can start as early as time \(1\).
+Since there is going to be an arc from either activity \(u_{k2}\) or \(u_{\ell 2}\) to activity \(c_{ij}\), and either \(u_{k2}\) or \(u_{\ell 2}\) cannot start before time \(2\), it leads to a contradiction that \(c_{ij}\) can start as early as time \(1\).
 Therefore, if activity \(c_{ij}\) can start at time \(1\), then \(u_j\) is the only variable which is TRUE.\\
-		\(\impliedby\): if only \(u_j\) is TRUE, then \(u_{j4}, u_{k3}\) and \(u_{\ell 3}\) can all start as early as time \(1\), which means that the earliest start time of \(c_{ij}\) is \(1\).
+		\(\impliedby\): if only \(u_j\) is TRUE, then \(u_{j3}, u_{k2}\) and \(u_{\ell 2}\) can all start as early as time \(1\), which means that the earliest start time of \(c_{ij}\) is \(1\).
 	\end{proof}
-	%For a clause \(i\) that contains variable \(j\), activity \(u_{j4}\) connects to \(c_{ij}\) and activity \(u_{j3}\) connects to the \(c\)-activities which do not correspond to variable \(u_j\).
-This means that if variable \(u_j\) is assigned a TRUE value, activity \(c_{ij}\) can start as soon as time \(1\) and the other two \(c\)-activities can start no earlier than time \(2\).
-	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of EOIT\_3SAT, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\).
+	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of \verb|EOIT_3SAT|, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\).
 Since we have a total of \(B = 2m\) units of resource, we can crash all of those \(c\)-activities to achieve a project length of \(2\).
-This means that we can transform an EOIT\_3SAT problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above.
-If we can find a feasible EOIT\_3SAT assignment, it is possible to obtain a project length less than or equal to 2.
+This means that we can transform an \verb|EOIT_3SAT| problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above.
+If we can find a feasible \verb|EOIT_3SAT| assignment, it is possible to obtain a project length less than or equal to 2.
 Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption.
@@
 	\begin{theorem}\label{thm:npcomplete}
-		For an instance of the EOIT\_3SAT problem, we construct the corresponding project crashing decision problem under a stochastic disruption: let \(\Omega = \{1\}\), \(H^1 = 0\), \(\mathcal{T} = 2\), and the precedence relationships, the crashing options and budget are constructed by the process shown in the Section~\ref{sec:nphard}.
-This decision problem has a solution if and only if the given instance of EOIT\_3SAT problem has a solution.
+		For an instance of the \verb|EOIT_3SAT| problem, we construct the corresponding project crashing decision problem under a stochastic disruption: let \(\Omega = \{1\}\), \(H^1 = 0\), \(\mathcal{T} = 2\), and the precedence relationships, the crashing options and budget are constructed by the process shown in the Section~\ref{sec:nphard}.
+This decision problem has a solution if and only if the given instance of \verb|EOIT_3SAT| problem has a solution.
 	\end{theorem}
@@
 		(polynomial transformation) 
-		%We first show that any instance of the project crashing decision problem is constructed in time that is polynomial in the length of the given instance of EOIT\_3SAT, and has a length that is polynomially related to the length of that instance.
-		Suppose the EOIT\_SAT problem has \(n\) variables and \(m\) clauses, the constructed activity network for the project crashing problem has \(4n + 3m + 1\) activities and \(5n + 12m\) arcs, which are both polynomial in the size of the original EOIT\_SAT problem.
+		%We first show that any instance of the project crashing decision problem is constructed in time that is polynomial in the length of the given instance of \verb|EOIT_3SAT|, and has a length that is polynomially related to the length of that instance.
+		Suppose the \verb|EOIT_3SAT| problem has \(n\) variables and \(m\) clauses, the constructed activity network for the project crashing problem has \(4n + 3m + 1\) activities and \(5n + 12m\) arcs, which are both polynomial in the size of the original \verb|EOIT_3SAT| problem.
 And all numbers in the project crashing decision problem are smaller than a constant, \(2\).\\
-		(\(\implies\)) Suppose the EOIT\_SAT instance has a solution.
+		(\(\implies\)) Suppose the \verb|EOIT_3SAT| instance has a solution.
 We have shown that we can start every activity as early as possible, and spend the budget to crash all \(c\)-activities which correspond to the literals with FALSE assignment and have the start time at \(2\).
@@
 This is equivalent to that exactly one \(c\)-activity in each of the \(m\) clauses starts at time \(1\).
-From Lemma~\ref{lemma:iff} we can directly obtain the result that for each clause there is exactly one variable to which the truth assignment is TRUE, which is essentially a solution to the EOIT\_3SAT instance.\\
-		\newline
-		EOIT\_3SAT is a NP-complete problem~\cite{Garey1979ComputersAI}.
+From Lemma~\ref{lemma:iff} we can directly obtain the result that for each clause there is exactly one variable to which the truth assignment is TRUE, which is essentially a solution to the \verb|EOIT_3SAT| instance.\\
+		\newline
+		\verb|EOIT_3SAT| is a NP-complete problem~\cite{Garey1979ComputersAI}.
 The project crashing decision problem under a stochastic disruption in NP, since we can check in \(O(n^2)\) to check whether a given input is feasible and has \(t_T \leq \mathcal{T}\).
@@
 	\end{proof}
-%	\noi For the network \(G(I,\mathcal{A})\) constructed by the process above, we introduce the decision problem: suppose the disruption time takes a constant value \(0\), is there a set of start time \(t_i,\ i \in I\), a set of crashing plan \(x_{ij},\ i \in I, j \in J_i\) and a set of indicators \(G_i\) showing whether activity \(i\) starts before the disruption or after.
 
 \section{Illustration of Problem Properties via Examples} \label{sec:examples}
-	In this section, we show examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem.
+	In this section, we show two examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, and its distinctions from the deterministic problem.
 In the deterministic project crashing problem, all activities on the critical path should start as soon as possible.
 However, with a stochastic disruption, it might be optimal to delay the start of some activities.
-Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\).
-\\
-	\newline
-	It is obvious that the delay can possibly be beneficial if \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\).
-We use a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption, a.k.a., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
-Suppose we have a project with three activities in a serial network form.
-Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3.
-The structure of the project is displayed as follows.
-We add a dummy activity ``T" to represent the end of the project.
-The total crashing budget is \(1\).
+In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
+We use the following two examples to show that the deterministic optimal solution could be significantly inferior in the stochastic setting because of those two properties.
+\tcb{Starting from this section, we assume that required separations between an activity \(i\) and all its successors \(k\) are the same for simplicity; i.e., for every activity \(i\) we use \(D_i\) to represent the duration of activity \(i\) and \(d_i^\omega\) to denote the change of duration due to the disruption scenario \(\omega\):
+	\begin{align*}
+		& D_{ik} = D_i \qquad \qquad \forall (i,k) \in \cA\\
+		& d^{\omega}_{ik} = d^{\omega}_i \qquad \qquad \forall (i,k) \in \cA, \omega \in \Omega.
+	\end{align*}}
 	\begin{figure}[H]
 		\centering
-		\includegraphics[width=0.8\textwidth]{serial3}
-		\caption{Example of a 3-activity project}
-		\label{fig:serial3}
+		\includegraphics[width=0.6\textwidth]{serial2}
+		\caption{Example of a 2-activity serial network project}
+		\label{fig:serial2}
 	\end{figure}
-	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\).
-There is only one crashing option for each activity, so we omit the subscript to index the crashing options.
-We use \(e_i = 0.5\) for all \(i \in I\).
-The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\).
-The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario.
-Suppose the disruption does not affect activity 1, \(d_1^1 = 0\), increases the duration of activity 2 by \(0.1\), \(d_2^1 = 0.1\), and increases the duration of activity 3 by \(6\), \(d_3^1 = 6\).
-We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\).
-There we can observe whether the disruption happens.
-If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise, it is optimal to crash activity 2 with \(1\) amount of resource.
-The expected total project span is \(23.4\), as the optimal project span given no disruption is \(21.1\) and that under disruption is \(25.7\).
-If every activity starts as soon as possible, like in the deterministic problem, we cannot observe whether the disruption happens or not prior to the start of activity 2.
-Under this condition, the best solution is to crash activity 2 with \(1\) amount of crashing resource, and the optimal expected project span is \(24\), larger than \(23.4\).
-\\
-	\newline
-	Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
-We summarize the reasons for such delay include:
+	\begin{example} \label{eg:delay}
+		It is obvious that the delay can possibly be beneficial when \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\) because the decrease in duration may outweigh the length of delay to move the start of activity \(i\) after the disruption.
+Therefore, we set up a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption; i.e., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
+Consider a network with two activities in series, as shown in Figure~\ref{fig:serial2}.
+Suppose we have a parameter \(k > 4\).
+In this example, $I=\{S,1,2,T\}$ with nominal durations $D_1 = k$ and $D_2 = 1$.
+We assume only one crashing option for each activity, and so we omit index $j$.
+We let $e_1=e_2=1 - \frac{1}{2k}$, assume $b_i=1$ for all $i \in I$, and we let $B=1$.
+Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=1 - \frac{1}{k}$, or we have a disruption that occurs at time $\varepsilon \leq \frac{1}{2}$ with probability $p^1=\frac{1}{k}$.
+If a disruption occurs, the nominal activity durations are lengthened by $d_1 = k$ and $d_2 = (k - 1)^2$.
+\\
+		\newline
+		If we start each activity without delay, then \(t_1 = 0,\ x_1=x_1^1\), and for any \(x_1 \leq 1\), \(t_2 \geq \frac{1}{2} \geq D_1(1 - e_1 x_1) \), which means activity \(2\) will start after the disruption.
+Since \(k > 1\), the expected duration of activity \(1\), $D_1 = k$ is greater than the expected duration of activity 2, $ D_2 + p^1 d_2 = 1 + \frac{1}{k} (k-1)^2 = k - 1 + \frac{1}{k}$.
+As a result, it is optimal to spend the entire budget on activity \(1\): $x_1=x_1^1=1$ and $x_2=x_2^1=0$, and the expected project duration is:
+		\begin{subequations}
+			\label{nodelay}
+			\begin{align}
+			&D_1 (1 - e_1 x_1) + p^0 D_2 + p^1 (D_2 + d_2) \\
+			= & k \left(1 - (1 - \frac{1}{2k})\cdot 1 \right) + (1 - \frac{1}{k}) \cdot 1 + \frac{1}{k} \left(1 + (k -1)^2\right) \\
+			= & k - \frac{1}{2} + \frac{1}{k}.
+			\end{align} 
+		\end{subequations}
+		On the other hand, if we delay the start of activity 1 until $t_2= \varepsilon$ then $x_1$ and $x_1^1$ need not be equal.
+Since for \(k > 2 + \sqrt{2}\), $k = D_1 > D_2 = 1$ and $(k - 1)^2 + 1 = D_2+d_2 > D_1 + d_1 = k + k$, we have $x_2=1$ and $x_3^1=1$ in an optimal solution, and the expected duration is:
+		\begin{subequations}
+			\begin{align}\label{delay}
+				&\varepsilon + p^0 \left[D_1 \cdot \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) + D_2 \right]  + p^1 \left[(D_1 + d_1) + \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) (D_2 + d_2) \right]\\
+				= & \varepsilon + \frac{k - 1}{k} \left(k \cdot \frac{1}{2k} + 1\right) + \frac{1}{k} \left[ (k + k) + \frac{1}{2k} \left((k-1)^2 + 1\right) \right] \\
+				= & \varepsilon + 4 - \frac{5}{2k} + \frac{1}{k^2}.
+			\end{align}
+		\end{subequations}
+		In the example above, as \(k \to +\infty\), the project span without delay approaches \(+\infty\), but the project span with delay has a constant limit \(\varepsilon + 4\).
+This example shows that with the possibility that a rare but pathological disruption may occur, it is infinitely better to delay the start of some activities.
+In summary, the reasons for such delay include:
 		\begin{enumerate}
@@
 		\end{enumerate}
-	In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
-We present the following example to showcase this property.
-Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}.
-The nominal duration of two activities is \(D_1 = 3, D_2 = 4\).
-The disruption does not affect the duration of activity 1, as \(d_1 = 0\), and lengthens the activity 2 by a random variable distributed in a uniform distribution with upper bound \(10\) and lower bound \(0\), as \(d_2 \sim \mathcal{U}(0,10)\).
-The crashing option setting is the same as the previous example, as there is only one crashing option for each activity and \(e_i = 0.5, \forall i \in I\).
-The total budget \(B = 1\).
-		\begin{figure}[H]
-			\centering
-			\includegraphics[width=0.8\textwidth]{2act}
-			\caption{Left: an illustration of a 2-activity project; right: probability distribution function of disruption time.}
-			\label{fig:2act}
-		\end{figure}
-	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\).
-Activity 1 starts at time \(t_1 = 0\) and activity 2 starts at time \(t_2 = 1.5\).
-The optimal expected project span is \(\mathbb{E}[t_T] = 6.5\).
-We can compare an alternative solution which crash activity 2 with one unit of resource, which has a longer expected duration.
-Crashing activity 2 matches the intuition from the deterministic case where on the critical path the activities with longer expected duration are prioritized.
-However, in this case with a stochastic disruption, the latter solution (\(t_1 = 0, t_2 = 3, x_1 = 0, x_2 = 1\)) yields a longer expected project span as \(\mathbb{E}[t_T] = 7.5\).
-The reason behind this gap is that by crashing activity 1 with one unit amount of resource, the probability of activity 2 starting before the disruption increases to \(0.8\), which prevents activity 2 from seeing the increased duration.
-\\
-	\newline
-	These examples above indicate that the crashing optimization problem with stochastic disruption has complicated nature.
+		Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
+	\end{example}
+	\begin{example} \label{eg:short}
+		Consider the same network with two activities in series as shown in Figure~\ref{fig:serial2}.
+Let $D_1$ and $D_2$ denote the two durations with $D_2 > D_1$.
+Assume $d_1=0$, $d_2 > 0$, $e_1=e_2=\frac{1}{2}$, and $B=1$.
+Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=\frac{1}{2}$, or we have a disruption that occurs at time $\frac{1}{2}D_1$ with probability $p^1=\frac{1}{2}$.
+Here, the optimal solution is to crash the shorter activity, i.e., $x_1=1$, which yields an expected project span of $\frac{1}{2}D_1 + D_2$ with start times $t_1=0$ and $t_2=\frac{1}{2}D_1$.
+In contrast, if $0 \le x_1 < 1$ then the expected duration is $D_1 (1-\frac{1}{2} x_1) + (D_2 + d_2)(1-\frac{1}{2} x_2)$, so that the ratio of the objective functions grows arbitrarily large as $d_2$ grows.
+The intuition behind crashing the shorter activity is that it allows us to initiate activity 2 in time to avoid having to incur delay $d_2$.
+	\end{example}
+
+	\noi Example~\ref{eg:delay} and~\ref{eg:short} indicate that the crashing optimization problem with stochastic disruption has complicated nature.
 The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
-	%\textcolor{blue}{NP-hardness proof.}
-	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.
 
@@
 Each of them corresponds to a disruption time of some scenario.
-		%and corresponds to the lower bound scenario index and the upper bound scenario index. the disruption time of 
 		The partition has the following properties:
@@
 		\begin{align}
-			%& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
 			& \sum_{q \in \mathcal{Q}_i} \underbar{H}^q y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} \bar{H}^q y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
@@
 		\begin{align}
-			%& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega\\
-			%& M_i^{\omega,-} = H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q，
 			& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} \bar{H}^q \hat{y}_i^q - H^\omega\\
@@
 		\begin{align}
-			%H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
-			%H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
 			H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} \bar{H}^q \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
@@
 		\begin{align}
-			%H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
-			%G_i H^\omega - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
-			%F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin1}\\
-			%F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin2}\\
-			%F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:FGlin3}
 			H^\omega + \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
@@
 		(S_{\mathcal{P}}^\omega) \qquad g^\omega_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
-		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
-		& G_i H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
+		\text{s.t.} \quad & \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i - H^\omega \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
+		& H^\omega G_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
 		& F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin1t}\\
@@
 		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
+		& 0 \leq F_i^q \leq 1 \qquad \qquad \forall \,i \in I, q \in \mathcal{Q}_i\\
 		& 0 \leq G_i \leq 1. \qquad \qquad \forall \,i \in I. \label{cons:G01t}

### 2019-05-09 src/partSolve_Callback_tightened_sol.jl

@@ -44,13 +44,13 @@ ubextList,tHList,ubInc,tbest,xbest,θbest,textList,xextList = iniPart(pData,disD
 lbCost = -Inf;
 lbCostList = [];
 global ubCost = ubInc;
-ubCostList = [ubCost];
 
 tcoreList = deepcopy(textList);
 xcoreList = deepcopy(xextList);
 ubcoreList = deepcopy(ubextList);
 ycoreList = [];
 errorList = [];
+GList = [];
 
 brInfo = precludeRelNew(pData,H,ubCost);
 
@@ -91,8 +91,6 @@ end
 # pre-separate the partition
 #divSet,divDet = splitPar_CI(divSet,divDet,tHList);
 for l in 1:length(textList)
-    push!(tcoreList,textList[l]);
-    push!(xcoreList,xextList[l]);
     ycoreItem = Dict();
     for i in pData.II
         for par in 1:length(divSet[i])
@@ -110,8 +108,9 @@ end
 
 function partBenders(cb)
     currentLB = MathProgBase.cbgetbestbound(cb);
-    println("lazy,$(currentLB)");
-    if currentLB <= minimum(ubCostList)
+    currentUB = minimum(ubcoreList);
+    println("lazy, $(currentLB), $(currentUB)");
+    if currentLB <= currentUB
         # the callback function
         that = Dict();
         xhat = Dict();
@@ -140,7 +139,7 @@ function partBenders(cb)
         γdict = Dict();
         vk = Dict();
         θInt = Dict();
-        ubCost = minimum(ubCostList);
+        ubCost = minimum(ubcoreList);
         ubTemp,θInt = ubCalP(pData,disData,Ω,xhat,that,Tmax1,1);
         if ubCost > ubTemp
             for i in pData.II
@@ -150,29 +149,35 @@ function partBenders(cb)
                 end
             end
         end
-        push!(ubCostList,ubTemp);
+        push!(ubcoreList,ubTemp);
 
         #dataList = pmap(ω -> sub_divT(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
         # obtain the cores
         tcore,xcore,ycore = avgCore(pData,divSet,tcoreList,xcoreList,ycoreList);
-        dataList = pmap(ω -> sub_divTDualT2(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict,tcore,xcore,ycore), Ω);
[…]

### 2019-05-09 src/sub.jl

@@ -1431,42 +1431,49 @@ function sub_divTT(pData,dDω,ωCurr,that,xhat,yhat,divSet,H,M,returnOpt = 0)
 
     @objective(smp, Min, t[0]);
     smpStatus = solve(smp);
-    vk = getobjectivevalue(smp);
-    if returnOpt == 0
-        return vk;
-    else
-        # the cut generated is θ >= v - λ(x - xhat) - π(t - that)
-        λdict = Dict();             # dual for x
-        πdict = Dict();             # dual for t
-        γdict = Dict();             # dual for y
-        for i in pData.II
-            πdict[i] = -getdual(smp[:GCons1][i]) - getdual(smp[:GCons2][i]) +
-                (getdual(smp[:tFnAnt1][i]) + getdual(smp[:tFnAnt2][i]) +
-                sum(getdual(smp[:xGlin4][i,j])*(getvalue(smp[:x][i,j]) - 1) +
-                getdual(smp[:xGlin5][i,j])*getvalue(smp[:x][i,j]) +
-                getdual(smp[:xGlin6][i,j])*getvalue(smp[:x][i,j]) +
-                getdual(smp[:xGlin7][i,j])*getvalue(smp[:x][i,j]) for j in pData.Ji[i]));
-            for j in pData.Ji[i]
-                λdict[i,j] = (getdual(smp[:xFnAnt1][i,j]) + getdual(smp[:xFnAnt2][i,j]));
-            end
-            for par in 1:length(divSet[i])
-                γdict[i,par] = H[divSet[i][par].startH]*getdual(smp[:GCons2][i]) +
-                    getdual(smp[:GyRelax2][i,par]) + getdual(smp[:GyRelax3][i,par]) -
-                    sum(getdual(smp[:xGlin4][i,j])*H[divSet[i][par].endH]*getvalue(smp[:s][i,j]) +
-                    getdual(smp[:xGlin5][i,j])*H[divSet[i][par].startH]*(getvalue(smp[:x][i,j]) - getvalue(smp[:s][i,j]))
-                    getdual(smp[:xGlin6][i,j])*H[divSet[i][par].startH]*(getvalue(smp[:s][i,j]) - getvalue(smp[:x][i,j]) + 1) -
-                    getdual(smp[:xGlin7][i,j])*H[divSet[i][par].endH]*getvalue(smp[:s][i,j]) for j in pData.Ji[i]);
-                if dDω.H <= H[divSet[i][par].startH]
[…]

### 2019-05-09 src/test1.jl

@@ -7,10 +7,10 @@ global noThreads = 30;
 
 pathList = ["/home/haoxiang/PERT_tests/current/11/",
             "/home/haoxiang/PERT_tests/current/14/",
-            "/home/haoxiang/PERT_tests/current/19/"];
-#            ,"/home/haoxiang/PERT_tests/current/35/",
-#            "/home/haoxiang/PERT_tests/current/55/",
-#            "/home/haoxiang/PERT_tests/current/75/"];
+            "/home/haoxiang/PERT_tests/current/19/",
+            "/home/haoxiang/PERT_tests/current/35/",
+            "/home/haoxiang/PERT_tests/current/55/",
+            "/home/haoxiang/PERT_tests/current/75/"];
 HsList = 0.1:0.1:0.9;
 for fileInd in 1:length(pathList)
     filePath = pathList[fileInd];

### 2019-05-09 src/test_time.jl

@@ -6,9 +6,13 @@ global noThreads = 30;
 @everywhere include("header.jl");
 
 #filePath = "/Users/haoxiangyang/Desktop/PERT_tests/75_Lognormal_Exponential/"
-pathList = ["/home/haoxiang/PERT_tests/11_Lognormal_Exponential/",
-            "/home/haoxiang/PERT_tests/14_Lognormal_Exponential/",
-            "/home/haoxiang/PERT_tests/19_Lognormal_Exponential/"];
+pathList = ["/home/haoxiang/PERT_tests/current/11/",
+            "/home/haoxiang/PERT_tests/current/14/",
+            "/home/haoxiang/PERT_tests/current/19/",
+            "/home/haoxiang/PERT_tests/current/35/",
+            "/home/haoxiang/PERT_tests/current/55/",
+            "/home/haoxiang/PERT_tests/current/75/"];
+            
 Ωsize = [100,200,300,400,500,750,1000];
 sNList = [20,20,20,20,20,30,40];
 MMList = [5,10,15,20,25,25,25];
@@ -53,7 +57,7 @@ for fileInd in 1:length(pathList)
 
         # extensive formulation
         tic();
-        text,xext,fext,gext,mext = extForm_cheat(pData,disData,Ω,1e-2,999999);
+        text,xext,fext,gext,mext = extForm_cheat(pData,disData,Ω,1e-4,999999);
         timeext = toc();
         ubmp = mext.objVal;
         lbmp = mext.objBound;

### 2019-05-13 Writeup/PERT_Paper_Draft1.tex
Add branch and bound rules

@@
 		Without loss of generality, we assume \(q^* = j\).\\
-		\(\implies\):  Suppose \(u_j\) is FALSE, then activity \(u_{j4}\) can only start after time \(2\), which will lead to the contradiction that \(c_{ij}\) can start as early as time \(1\).
+		\(\implies\):  Suppose \(u_j\) is FALSE, then activity \(u_{j3}\) can only start after time \(2\), which will lead to the contradiction that \(c_{ij}\) can start as early as time \(1\).
 Suppose either \(u_k\) or \(u_\ell\) is TRUE in addition to \(u_j\).
-Since there is going to be an arc from either activity \(u_{k3}\) or \(u_{\ell 3}\) to activity \(c_{ij}\), and either \(u_{k3}\) or \(u_{\ell_3}\) cannot start before time \(2\), it leads to a contradiction that \(c_{ij}\) can start as early as time \(1\).
+Since there is going to be an arc from either activity \(u_{k2}\) or \(u_{\ell 2}\) to activity \(c_{ij}\), and either \(u_{k2}\) or \(u_{\ell 2}\) cannot start before time \(2\), it leads to a contradiction that \(c_{ij}\) can start as early as time \(1\).
 Therefore, if activity \(c_{ij}\) can start at time \(1\), then \(u_j\) is the only variable which is TRUE.\\
-		\(\impliedby\): if only \(u_j\) is TRUE, then \(u_{j4}, u_{k3}\) and \(u_{\ell 3}\) can all start as early as time \(1\), which means that the earliest start time of \(c_{ij}\) is \(1\).
+		\(\impliedby\): if only \(u_j\) is TRUE, then \(u_{j3}, u_{k2}\) and \(u_{\ell 2}\) can all start as early as time \(1\), which means that the earliest start time of \(c_{ij}\) is \(1\).
 	\end{proof}
@@
 This means that if variable \(u_j\) is assigned a TRUE value, activity \(c_{ij}\) can start as soon as time \(1\) and the other two \(c\)-activities can start no earlier than time \(2\).
-	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of EOIT\_3SAT, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\).
+	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of \verb|EOIT_3SAT|, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\).
 Since we have a total of \(B = 2m\) units of resource, we can crash all of those \(c\)-activities to achieve a project length of \(2\).
-This means that we can transform an EOIT\_3SAT problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above.
-If we can find a feasible EOIT\_3SAT assignment, it is possible to obtain a project length less than or equal to 2.
+This means that we can transform an \verb|EOIT_3SAT| problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above.
+If we can find a feasible \verb|EOIT_3SAT| assignment, it is possible to obtain a project length less than or equal to 2.
 Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption.
@@
 \section{Illustration of Problem Properties via Examples} \label{sec:examples}
-	In this section, we show examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem.
+	In this section, we show two examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, and its distinctions from the deterministic problem.
 In the deterministic project crashing problem, all activities on the critical path should start as soon as possible.
 However, with a stochastic disruption, it might be optimal to delay the start of some activities.
-Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\).
-\\
-	\newline
-	It is obvious that the delay can possibly be beneficial if \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\).
-We use a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption, a.k.a., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
-Suppose we have a project with three activities in a serial network form.
+In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
+We use the following two examples to show that the deterministic optimal solution could be significantly inferior in the stochastic setting because of those two properties.
+\tcb{Starting from this section, we assume that required separations between an activity \(i\) and all its successors \(k\) are the same for simplicity; i.e., for every activity \(i\) we use \(D_i\) to represent the duration of activity \(i\) and \(d_i^\omega\) to denote the change of duration due to the disruption scenario \(\omega\):
+	\begin{align*}
+		& D_{ik} = D_i \qquad \qquad \forall (i,k) \in \cA\\
+		& d^{\omega}_{ik} = d^{\omega}_i \qquad \qquad \forall (i,k) \in \cA, \omega \in \Omega.
+	\end{align*}}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.6\textwidth]{serial2}
+		\caption{Example of a 2-activity serial network project}
+		\label{fig:serial2}
+	\end{figure}
+	\begin{example} \label{eg:delay}
+		It is obvious that the delay can possibly be beneficial when \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\) because the decrease in duration may outweigh the length of delay to move the start of activity \(i\) after the disruption.
+Therefore, we set up a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption; i.e., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
+Consider a network with two activities in series, as shown in Figure~\ref{fig:serial2}.
+Suppose we have a parameter \(k > 4\).
+In this example, $I=\{S,1,2,T\}$ with nominal durations $D_1 = k$ and $D_2 = 1$.
+We assume only one crashing option for each activity, and so we omit index $j$.
+We let $e_1=e_2=1 - \frac{1}{2k}$, assume $b_i=1$ for all $i \in I$, and we let $B=1$.
+Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=1 - \frac{1}{k}$, or we have a disruption that occurs at time $\varepsilon \leq \frac{1}{2}$ with probability $p^1=\frac{1}{k}$.
+If a disruption occurs, the nominal activity durations are lengthened by $d_1 = k$ and $d_2 = (k - 1)^2$.
+\\
+		\newline
+		If we start each activity without delay, then \(t_1 = 0,\ x_1=x_1^1\), and for any \(x_1 \leq 1\), \(t_2 \geq \frac{1}{2} \geq D_1(1 - e_1 x_1) \), which means activity \(2\) will start after the disruption.
+Since \(k > 1\), the expected duration of activity \(1\), $D_1 = k$ is greater than the expected duration of activity 2, $ D_2 + p^1 d_2 = 1 + \frac{1}{k} (k-1)^2 = k - 1 + \frac{1}{k}$.
+As a result, it is optimal to spend the entire budget on activity \(1\): $x_1=x_1^1=1$ and $x_2=x_2^1=0$, and the expected project duration is:
+		\begin{subequations}
+			\label{nodelay}
+			\begin{align}
+			&D_1 (1 - e_1 x_1) + p^0 D_2 + p^1 (D_2 + d_2) \\
+			= & k \left(1 - (1 - \frac{1}{2k})\cdot 1 \right) + (1 - \frac{1}{k}) \cdot 1 + \frac{1}{k} \left(1 + (k -1)^2\right) \\
+			= & k - \frac{1}{2} + \frac{1}{k}.
+			\end{align} 
+		\end{subequations}
+		On the other hand, if we delay the start of activity 1 until $t_2= \varepsilon$ then $x_1$ and $x_1^1$ need not be equal.
+Since for \(k > 2 + \sqrt{2}\), $k = D_1 > D_2 = 1$ and $(k - 1)^2 + 1 = D_2+d_2 > D_1 + d_1 = k + k$, we have $x_2=1$ and $x_3^1=1$ in an optimal solution, and the expected duration is:
+		\begin{subequations}
+			\begin{align}\label{delay}
+				&\varepsilon + p^0 \left[D_1 \cdot \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) + D_2 \right]  + p^1 \left[(D_1 + d_1) + \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) (D_2 + d_2) \right]\\
+				= & \varepsilon + \frac{k - 1}{k} \left(k \cdot \frac{1}{2k} + 1\right) + \frac{1}{k} \left[ (k + k) + \frac{1}{2k} \left((k-1)^2 + 1\right) \right] \\
+				= & \varepsilon + 4 - \frac{5}{2k} + \frac{1}{k^2}.
+			\end{align}
+		\end{subequations}
+		In the example above, as \(k \to +\infty\), the project span without delay approaches \(+\infty\), but the project span with delay has a constant limit \(\varepsilon + 4\).
+This example shows that with the possibility that a rare but pathological disruption may occur, it is infinitely better to delay the start of some activities.
+In summary, the reasons for such delay include:
+		\begin{enumerate}
+			\item Some activities might have a shorter length after the disruption. It is beneficial to wait a short period of time to capture this advantage.
+			\item Even if all possible disruption magnitudes are adverse, which means they lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
+		\end{enumerate}
+		Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
+	\end{example}
+	\begin{example} \label{eg:short}
+		Consider the same network with two activities in series as shown in Figure~\ref{fig:serial2}.
+Let $D_1$ and $D_2$ denote the two durations with $D_2 > D_1$.
+Assume $d_1=0$, $d_2 > 0$, $e_1=e_2=\frac{1}{2}$, and $B=1$.
+Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=\frac{1}{2}$, or we have a disruption that occurs at time $\frac{1}{2}D_1$ with probability $p^1=\frac{1}{2}$.
+Here, the optimal solution is to crash the shorter activity, i.e., $x_1=1$, which yields an expected project span of $\frac{1}{2}D_1 + D_2$ with start times $t_1=0$ and $t_2=\frac{1}{2}D_1$.
+In contrast, if $0 \le x_1 < 1$ then the expected duration is $D_1 (1-\frac{1}{2} x_1) + (D_2 + d_2)(1-\frac{1}{2} x_2)$, so that the ratio of the objective functions grows arbitrarily large as $d_2$ grows.
+The intuition behind crashing the shorter activity is that it allows us to initiate activity 2 in time to avoid having to incur delay $d_2$.
+		%\\
+		%\newline
+		%This example shows that because the disruption may significantly change the duration of an activity, crashing shorter activities at the beginning of the project to prevent disruption may yield a significantly better result than crashing longer activities closer to the end of the project.
+	\end{example}
+
+	\noi Example~\ref{eg:delay} and~\ref{eg:short} indicate that the crashing optimization problem with stochastic disruption has complicated nature.
+The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
+
+%	Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\). \\
+%	\newline
+%	  Suppose we have a project with three activities in a serial network form.
 Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3.
@@
 The total crashing budget is \(1\).
-	\begin{figure}[H]
-		\centering
-		\includegraphics[width=0.8\textwidth]{serial3}
-		\caption{Example of a 3-activity project}
-		\label{fig:serial3}
-	\end{figure}
-	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\).
+%	
+%	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\).
 There is only one crashing option for each activity, so we omit the subscript to index the crashing options.
@@
 \\
-	\newline
-	Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
-We summarize the reasons for such delay include:
-		\begin{enumerate}
-			\item Some activities might have a shorter length after the disruption. It is beneficial to wait a short period of time to capture this advantage.
-			\item Even if all possible disruption magnitudes are adverse, which means they lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
-		\end{enumerate}
-	In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
-We present the following example to showcase this property.
+%	\newline
+%	 We present the following example to showcase this property.
 Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}.
@@
 The total budget \(B = 1\).
-		\begin{figure}[H]
-			\centering
-			\includegraphics[width=0.8\textwidth]{2act}
-			\caption{Left: an illustration of a 2-activity project; right: probability distribution function of disruption time.}
-			\label{fig:2act}
-		\end{figure}
-	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\).
+%	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\).
 Activity 1 starts at time \(t_1 = 0\) and activity 2 starts at time \(t_2 = 1.5\).
@@
 \\
-	\newline
-	These examples above indicate that the crashing optimization problem with stochastic disruption has complicated nature.
-The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
+%	\newline
+
 	%\textcolor{blue}{NP-hardness proof.}
@@
 		(S_{\mathcal{P}}^\omega) \qquad g^\omega_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
-		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
-		& G_i H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
+		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
+		& H^\omega G_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
 		& F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin1t}\\

### 2019-05-13 Writeup/PERT_Paper_Draft2.tex
Add branch and bound rules

@@
 			\end{subequations}
-			Notice that the inequality~\eqref{cons:case2eqn2} is always weaker than~\eqref{cons:case2eqn1} because the right-hand side of~\eqref{cons:case2eqn2} is smaller than 0 while the right-hand side of~\eqref{cons:case2eqn1} is positive.
+			Notice that the inequality~\eqref{cons:case2eqn2} is strictly weaker than~\eqref{cons:case2eqn1} because the right-hand side of~\eqref{cons:case2eqn2} is smaller than 0 while the right-hand side of~\eqref{cons:case2eqn1} is positive.
 Similar to Case 1, the lower bound increases compared to using a large \(M\) and the upper bound is \(1\), and we achieve a tightened relaxation.
@@
 It is easy to see that by transforming \(F^{\omega,*}\) to \(\tilde{F}^{\omega,*}\) with \[\tilde{F}^{\omega,*,q}_i = \sum_{\tilde{q} \in \Delta_i(\ell,q) }F_i^{\omega,*,\tilde{q}} \qquad  \forall i \in I, q \in \mathcal{Q}^\ell_i;\]
-		thus, we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\).
+		we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\).
 Therefore, inequality~\eqref{cons:gglb} holds.

### 2019-05-13 Writeup/pert_example.tex
Add branch and bound rules

\documentclass[11pt]{article}
%\usepackage[small,compact]{titlesec}
\usepackage[small]{titlesec}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{subfig,enumerate,url,color}
\setlength{\textheight}{9.1in}
\setlength{\topmargin}{-0.66in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\def\qed{\hfill{\(\vcenter{\hrule height1pt \hbox{\vrule width1pt height5pt
     \kern5pt \vrule width1pt} \hrule height1pt}\)} \medskip}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\renewcommand{\textfraction}{0.0}
\newcommand{\dst}{\displaystyle}
\newcommand{\minx}{\mbox{\( \dst \min_{x \in X} \)}}
\newcommand{\Efx}{\mbox{\( \dst E f (x, \xi) \)}}
\newcommand{\Efxhat}{\mbox{\( \dst E f (\hat{x}, \xi) \)}}
\newcommand{\hxx}{\mbox{\( \hat{x} \)}}
\newcommand{\bpi}{\bar{\pi}}
\newcommand{\xx}{\mbox{\( x \)}}
\newcommand{\txxi}{\mbox{\(\xi\)}}
\newcommand{\var}{\mbox{var}}
\newcommand{\cF}{{\cal F}}
\newcommand{\cG}{{\cal G}}
\newcommand{\txi}{{\xi}}
\newcommand{\PP}{\mbox{\(SP\)}}
\newcommand{\PPn}{\mbox{\(SP_n\)}}
\newcommand{\PPnx}{\mbox{\(SP_{n_x}\)}}
\newcommand{\noi}{\noindent}
\renewcommand{\ss}{\smallskip}
\newcommand{\ms}{\medskip}
\newcommand{\bs}{\bigskip}
\newcommand{\st}{\mbox{s.t.}}
\newcommand{\wpo}{\mbox{wp1}}
\newcommand{\iid}{\mbox{i.i.d.\ }}
\newcommand{\vsmo}{\vspace*{-0.1in}}
\newcommand{\vsmt}{\vspace*{-0.2in}}
\newcommand{\vso}{\vspace*{0.1in}}
\newcommand{\vst}{\vspace*{0.2in}}
\newcommand{\mc}{\multicolumn}
\newcommand{\cP}{{\cal P}}
\newcommand{\cU}{{\cal U}}
\renewcommand{\P}{{\mathbb P}}
\newcommand{\underv}{\mbox{$\underbar{$v$}$}}
\allowdisplaybreaks

\bibliographystyle{plain}

\begin{document}
%0.27
\baselineskip0.20in

\begin{center}
\begin{large}

{\bf PERT Example} \bs

Haoxiang Yang and David Morton \ms

January 2019 \bs

\end{large}
\end{center}

\section*{Examples}

\noindent Haoxiang: I started generalizing (slightly) your example to understand what is possible\ldots

\begin{example}
Consider a network with three activities in series, as shown in Figure~\ref{fig:pert_example}. In this example, $I=\{S,1,2,3,T\}$ with nominal durations $D_1, D_2$, and $D_3$. We assume only one crashing option for each activity, and so we omit  index $j$. We let $e_1=0$, $e_2=e_3=\frac{1}{2}$, assume $b_i=1$ for all $i \in I$, and we let $B=1$. Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=\frac{1}{2}$, or we have a disruption that occurs at time $H^1=D_1+\varepsilon$ with probability $p^1=\frac{1}{2}$. If a disruption occurs, the nominal activity durations are lengthened by $d_1=0$, $d_2$, and $d_3$. 
%We assume $D_2 > D_3$ so that if we knew there would be no disruption, it would be best to crash activity~2, and we assume $D_3+d_3 > D_2+d_3$ so that if we knew there would be a disruption, it would be best to crash activity~3. 
Clearly, we can take $x_1=x_1^1=0$. If we start each activity without delay, then $x_2=x_2^1$ and thus $x_3=x_3^1$ in an optimal solution. As a result, if $D_2 + \frac{1}{2} d_2 > D_3 + \frac{1}{2} d_3$ then $x_2=x_2^1=1$ and $x_3=x_3^1=0$, and the expected project duration is:
\begin{equation}\label{nodelay}
D_1 + \frac{1}{2} D_2 + D_3 + \frac{1}{4}d_2 + \frac{1}{2} d_3.
\end{equation} 
On the other hand, if we delay the start of activity 2 until $t_2=D_1+\varepsilon$ then $x_2$ and $x_2^1$ need not be equal. If $D_2 > D_3$ and $D_3+d_3 > D_2 + d_2$ then in an optimal solution $x_2=1$ and $x_3^1=1$, and the expected duration is:
\begin{equation}\label{delay}
\varepsilon + D_1 + \frac{3}{4} D_2 + \frac{3}{4} D_3 + \frac{1}{2} d_2 + \frac{1}{4} d_3.
\end{equation}
The three requisite inequalities on $D_2, D_3, d_2, d_3$ are equivalent to:
\[ D_2 - D_3 > (D_3+d_3) - (D_2+d_2) > 0.\]
For $k > 1$ let $D_2=k D$ (with $D_3=D$) and let $d_3=k d_2$ (with $d_2=d$). Then the above conditions amount to:
\[ 2 D > d > D . \]
\end{example}
Notes to Haoxiang:
\begin{enumerate}
\item We are interested in the ratio of equation~\eqref{delay} to~\eqref{nodelay}, and bounds on this ratio. Can delaying improve the objective function by an arbitrarily large constant? I just did this quickly, but I think in the limit with $\varepsilon$ and $D_1$ small and $k$ large we obtain a ratio of $\frac{5}{6}$. I'm not confident that this is correct, but the main question is: Is this the best ratio possible? 
\item Can you modify the example so that the above ratio is arbitrarily small or is $\frac{5}{6}$ the best possible? You could change the $e_i$ values from $\frac{1}{2}$ and that would improve the $\frac{5}{6}$ value, but I don't know that it would make the ratio shrink to zero in the limit. Maybe to $\frac{3}{4}$ or $\frac{1}{2}$? 
\item The main issue is: Can you modify the example to include more activities, or in some other way, so that in the limit as $k$ (or however it's parameterized) grows large the ratio shrinks to zero? 
\end{enumerate}

\newpage

\begin{example}\label{example2} 
Consider a network with two activities in series [we don't need a figure]. Let $D_1$ and $D_2$ denote the two durations with $D_2 > D_1$. Assume $d_1=0$, $d_2 > 0$, $e_1=e_2=\frac{1}{2}$, and $B=1$. Let $\P(H=\frac{1}{2}D_1)=\frac{1}{2}$. Here, the optimal solution is to crash the shorter activity, i.e., $x_1=1$, which yields an expected project span of $\frac{1}{2}D_1 + D_2$ with start times $t_1=0$ and $t_2=\frac{1}{2}D_1$. In contrast, if $0 \le x_1 < 1$ then the expected duration is $D_1 (1-\frac{1}{2} x_1) + (D_2 + d_2)(1-\frac{1}{2} x_2)$, so that the ratio of the objective functions grows arbitrarily large as $d_2$ grows. The intuition behind crashing the shorter activity is that it allows us to initiate activity 2 in time to avoid having to incur delay $d_2$.
\end{example}
Haoxiang: I think the message with these examples is: (i) make the example as simple as possible to illustrate the effect you're trying to show, e.g., don't make $d_2$ random unless it's necessary and (ii) create the example to show how large the effect might be. \medskip

\section*{Complexity}

In terms of a complexity result, Example~\ref{example2} suggests that you can take two activities in series, and you can construct the disruption time distribution so that it makes sense to have $x_i \in \{0,1\}$. If $x_i=1$ you can avoid the discrete delay on the second activity in series $i$. Now consider the set-covering construct that is used in this paper:

\textcolor{blue}{\url{https://faculty.nps.edu/joroyset/docs/BrownCarlyleRoysetWood2005.pdf}}

We use $i \in N_1$ to index $|N_1|$ parallel pairs, each with crashing decision $x_i, i \in N_1$. The sets $N_i \subset N_2$ are defined by the set covering problem. We're interested in the longest path from $S$ to $T$ ($a$ to $b$ in their paper). It's true that they have interdiction and crashing and we just have crashing, and they're trying to choose $i$'s in $N_1$ to make the longest path long, but let's see if you can use this idea to prove a complexity result. If you need to, let's start by assuming completely separate budgets for crashing activities in $N_1$ and $N_2$.

\end{document}

### 2019-05-13 src/cutValue.jl

@@ -62,3 +62,47 @@ function cutValue(pData,disData,text,xext,gext,θext,cutSet)
     end
     return θs;
 end
+
+function cutValueY(pData,disData,text,xext,yext,θext,cutSet,divSet)
+    H = Dict();
+    H[0] = 0;
+    H[length(Ω)+1] = Tmax;
+    for ω in Ω
+        H[ω] = disData[ω].H;
+    end
+
+    θs = Dict();
+    # for each batch of cut
+    for nc in 1:length(cutSet)
+        # for each scenario
+        for l in 1:length(cutSet[nc][2])
+            ω = cutSet[nc][2][l][1];
+            vk = cutSet[nc][2][l][2];
+            πk = cutSet[nc][2][l][3];
+            λk = cutSet[nc][2][l][4];
+            γk = cutSet[nc][2][l][5];
+            θs[ω,nc] = vk + sum(πk[i]*(text[i] - cutSet[nc][1][1][i]) for i in pData.II);
+            for i in pData.II
+                for j in pData.Ji[i]
+                    θs[ω,nc] += λk[i,j]*(xext[i,j] - cutSet[nc][1][2][i,j]);
+                end
+                for par in 1:length(cutSet[nc][1][4][i])
+                    ysum = 0;
+                    for parNew in 1:length(divSet[i])
+                        if revPar(cutSet[nc][1][4][i],divSet[i][parNew]) == par
+                            ysum += yext[i,parNew];
+                        end
+                    end
+                    θs[ω,nc] += γk[i,par]*(ysum - cutSet[nc][1][3][i,par]);
+                end
+            end
+        end
+    end
+
+    for (ω,nc) in keys(θs)
+        if θs[ω,nc] > θext[ω]
+            println((ω,nc)," ",θs[ω,nc]," ",θext[ω]);
+        end
+    end
+    return θs;
+end

### 2019-05-13 src/liftTest.jl

@@ -1,0 +1,48 @@
+m = Model(solver = GurobiSolver());
+that = 0.8;
+#@variable(m, 0 <= that <= 1);
+@variable(m,x);
+@variable(m,0 <= G <= 1);
+@variable(m,0 <= F <= 1.1);
+@constraint(m, cons1, 0.5 - 0.5G <= that);
+@constraint(m, cons2, 1.1 - 0.6G >= that);
+@constraint(m, cons3, x + 4*F -2.2*G + 1.2 == 2*that);
+@constraint(m, cons4, F <= that);
+@constraint(m, cons5, F <= 1.1*G);
+@constraint(m, cons6, F >= that - 1.1*(1 - G));
+
+@objective(m,Min,x);
+solve(m);
+
+λ1 = getdual(cons1);
+λ2 = getdual(cons2);
+λ3 = getdual(cons3);
+λ4 = getdual(cons4);
+λ5 = getdual(cons5);
+λ6 = getdual(cons6);
+println(λ1 + λ2 + 2*λ3 + λ4 + λ6);
+
+
+m = Model(solver = GurobiSolver());
+that = 0.4;
+#@variable(m, 0 <= that <= 1);
+@variable(m,x);
+@variable(m,0 <= G <= 1);
+@variable(m,0 <= F <= 1.1);
+#@constraint(m, cons1, 0.5 - 0.5G <= that);
+#@constraint(m, cons2, 1.1 - 0.6G >= that);
+@constraint(m, cons3, 4*F -2.2*G + 1 - x == 2*that);
+@constraint(m, cons4, F <= that);
+@constraint(m, cons5, F <= 1.1*G);
+@constraint(m, cons6, F >= that - 0.5*(1 - G));
+@constraint(m, cons7, F >= 0.5*G);
+
+@objective(m,Min,x);
+solve(m);
+λ1 = getdual(cons1);
+λ2 = getdual(cons2);
+λ3 = getdual(cons3);
+λ4 = getdual(cons4);
+λ5 = getdual(cons5);
+λ6 = getdual(cons6);
+println(λ1 + λ2 + 2*λ3 + λ4 + λ6);

### 2019-05-13 src/partSolve_Callback_tightened_sol.jl

@@ -1,4 +1,5 @@
 # calculate the largest possible starting time for each activity in any disrupted scenario
+global nSplit = 5;
 Tmax = disData[length(Ω)].H + longestPath(pData)[0];
 pdData = deepcopy(pData);
 for i in pData.II
@@ -154,8 +155,8 @@ function partBenders(cb)
         #dataList = pmap(ω -> sub_divT(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
         # obtain the cores
         tcore,xcore,ycore = avgCore(pData,divSet,tcoreList,xcoreList,ycoreList);
-        dataList = pmap(ω -> sub_divTT(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
-        #dataList = pmap(ω -> sub_divTDualT2(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict,tcore,xcore,ycore), Ω);
+        #dataList = pmap(ω -> sub_divTT(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict), Ω);
+        dataList = pmap(ω -> sub_divTDualT2(pData,disData[ω],ω,that,xhat,yhat,divSet,H,lDict,tcore,xcore,ycore), Ω);
         errorInd = [];
         cutDual = [];
         for ω in Ω
@@ -231,9 +232,7 @@ while keepIter
     @constraint(mp, yConstr[i in pData.II], sum(y[i,par] for par in 1:length(divSet[i])) == 1);
     @constraint(mp, yLimit[i in pData.II, par in 1:length(divSet[i]); divDet[i][par] != 0], y[i,par] == 0);
 
-    #@objective(mp, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
-    @objective(mp, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω) + r*sum(t[i] for i in pData.II));
-
+    @objective(mp, Min, pData.p0*t[0] + sum(disData[ω].prDis*θ[ω] for ω in Ω));
     tCurrent = Dict();
     xCurrent = Dict();
     θCurrent = Dict();
@@ -273,20 +272,6 @@ while keepIter
     end
 
     # find the current best upper bound from coreList
-    # lbmin = ubInc;
-    # coreMinind = -1;
-    # θbestR = Dict();
-    # for l in 1:length(tcoreList)
[…]

### 2019-05-13 src/part_tight.jl

@@ -340,49 +340,133 @@ function iniPart(pData,disData,Ω,sN,MM,returnOpt = 0,noThreads = 30)
     end
 end
 
-function splitAny(PartSet,PartDet,splitInfo)
-    newPartSet = copy(PartSet);
-    newPartDet = copy(PartDet);
-    for (i,splitStart,splitEnd) in splitInfo
+function splitAny(PartSet,PartDet,Ω,breakPoints)
+    # breakPoints is a dictionary with keys from pData.II
+    newPartSet = deepcopy(PartSet);
+    newPartDet = deepcopy(PartDet);
+    for i in keys(breakPoints)
         partSetiTemp = [];
         partDetiTemp = [];
         for par in 1:length(PartSet[i])
             # split the current partition, essentially split twice using the start and the end
-            if (splitStart < PartSet[i][par].endH)&(splitStart > PartSet[i][par].startH)&(PartDet[i][par] == 0)
-                if (splitEnd < PartSet[i][par].endH)&(splitEnd > PartSet[i][par].startH)
-                    part1 = partType(PartSet[i][par].startH,splitStart);
-                    part2 = partType(splitStart,splitEnd);
-                    part3 = partType(splitEnd,PartSet[i][par].endH);
-                    push!(partSetiTemp,part1);
-                    push!(partSetiTemp,part2);
-                    push!(partSetiTemp,part3);
+            bps = sort([j for j in breakPoints[i] if (j < PartSet[i][par].endH)&(j > PartSet[i][par].startH)]);
+            if bps != []
+                currentStart = PartSet[i][par].startH;
+                for j in bps
+                    partCurrent = partType(currentStart,j);
+                    push!(partSetiTemp,partCurrent);
                     push!(partDetiTemp,0);
-                    push!(partDetiTemp,0);
-                    push!(partDetiTemp,0);
-                else
-                    part1 = partType(PartSet[i][par].startH,splitStart);
-                    part2 = partType(splitStart,PartSet[i][par].endH);
-                    push!(partSetiTemp,part1);
-                    push!(partSetiTemp,part2);
-                    push!(partDetiTemp,0);
-                    push!(partDetiTemp,0);
+                    currentStart = j;
                 end
[…]

### 2019-05-13 src/test2.jl

@@ -7,10 +7,10 @@ global noThreads = 30;
 
 pathList = ["/home/haoxiang/PERT_tests/current/11/",
             "/home/haoxiang/PERT_tests/current/14/",
-            "/home/haoxiang/PERT_tests/current/19/"];
-#            ,"/home/haoxiang/PERT_tests/current/35/",
-#            "/home/haoxiang/PERT_tests/current/55/",
-#            "/home/haoxiang/PERT_tests/current/75/"];
+            "/home/haoxiang/PERT_tests/current/19/",
+            "/home/haoxiang/PERT_tests/current/35/",
+            "/home/haoxiang/PERT_tests/current/55/",
+            "/home/haoxiang/PERT_tests/current/75/"];
 dOptList = ["a","d","r"];
 for fileInd in 1:length(pathList)
     filePath = pathList[fileInd];

### 2019-05-30 Writeup/PERT_Paper_Draft3.tex
Update the non-BB method

--- 2019-05-13 Writeup/PERT_Paper_Draft2.tex
@@
 \newcommand{\underv}{\mbox{$\underbar{$v$}$}}
+\newcommand*{\thead}[1]{\multicolumn{1}{c}}
 \allowdisplaybreaks
@@
 	\section{Introduction} \label{sec:introduction}
-	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath} (see S{\"o}derlund \cite{soderlund2004building} for an overview).
+		The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \citep{kelley1961criticalpath}; see \citet{soderlund2004building} for an overview.
 A project is a collection of activities, between which there are precedence relationships due to logical or technological considerations.
-The precedence relationship is usually reflected as a required separation time between the start time of two activities.
-Multiple activities can be processed at the same time and there is no limit on how many activities can be processed simultaneously, as long as the precedence requirements are satisfied.
-See Elmaghraby~\cite{Elmaghraby77} for a detailed treatment of activity networks.
-In this setting, ``crashing" is an action that consumes a certain amount of resource and shortens the duration of activities accordingly~\cite{kuhl2008dynamic}.
-The deterministic optimization problem for crashing an activity network was proposed in the 1960s \cite{fulkerson1961network, kelley1961criticalpath}.
-The goal is to complete all activities in minimum time by allocating resources under one or more budget constraints.\\
-	\newline
-	When the program evaluation and review technique (PERT) \cite{malcolm1959application} was introduced, activity durations were modeled as independent beta random variables, and the project duration approximated by a normal distribution.
-Extensions that allow for more general assumptions followed \cite{Elmaghraby77}, and Monte Carlo simulation plays a role in estimating the expected project span, which is difficult to express analytically \cite{burt1971conditional,van1963letter}.
-	Heuristics and simulation-based algorithms have been developed to approximately solve the stochastic project crashing problem \cite{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}.
-Another approach to handle the uncertainty is robust optimization, in which the objective is to minimize the worst case project span within a specified uncertainty set.
-While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \cite{chen2008linear, cohen2007stochastic}.
-However, once recourse decisions can take general form, the robust model is only tractable with hypercube uncertainty sets, which is a trivial case because the worst-case scenario in the uncertainty set is always the point where every activity takes its upper bound \cite{wiesemann2012robust}.
-Ahipasaoglu et al.
-\cite{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.
-The project crashing optimization problem finds wide applications in project management~\cite{demeulemeester2006project, jaselskis1991allocation,tonchia2018industrial}, machine scheduling~\cite{blazewicz1983scheduling,hall1996machine}, health services scheduling~\cite{cardoen2010operating}, chemical processes~\cite{li2008process}, and digital circuit sizing~\cite{kim2007heuristic}.\\
-	\newline
-	In this paper, we propose using the concept of stochastic disruptions to model the uncertainty, which is different from the setting of a stochastic program or a robust optimization problem.
-A stochastic disruption is an event that may occur at any time in the time horizon and change the system parameters significantly.
-A few authors apply this idea when the disruption can only occur in a set of specified time periods.
-Yu and Qi \cite{yu2004disruptionmgt} introduce scenario-based optimization models for airline scheduling.
-Morton et al.
-\cite{morton2009sealift} introduce a sealift scheduling problem under a finite number of stochastic disruptions within a stochastic programming structure.
-This structure ``falls between standard two-stage and multi-stage stochastic programs for a multi-period problem" and reduces the size of the problem to a quadratic growth in the number of time periods.
-Our setting inherits the philosophy of \cite{morton2009sealift} but enhances the model by allowing a continuous disruption time instead of a prespecified set of fixed time periods.
-\\
-	\newline
-	We first formally describe the crashing optimization problem under stochastic disruptions.
-Given a limited number of disruption scenarios, the problem can be formulated as a stochastic mixed integer program and we present the extensive formulation in Section~\ref{sec:formulation}.
+A precedence relationship is usually reflected as the start time of one activity following the completion of another.
+Typically, multiple activities can be processed at the same time, and there is no limit on how many activities can be processed simultaneously, as long as the precedence requirements are satisfied.
+See~\citet{Elmaghraby77} for a detailed treatment of activity networks.
+In this setting, ``crashing" is an action that consumes a certain amount of one or more resources and shortens the duration of an activity accordingly~\citep{kuhl2008dynamic}.
+A deterministic optimization model for crashing an activity network was proposed in the 1960s \citep{fulkerson1961network, kelley1961criticalpath}, in which the goal is to complete the project in minimum time by allocating resources under one or more budget constraints.\\
+		\newline
+		When the program evaluation and review technique (PERT) was introduced~\citep{malcolm1959application}, activity durations were modeled as independent beta random variables, and the project duration approximated by a normal distribution.
+Extensions that allow for more general assumptions followed \citep{Elmaghraby77}, and Monte Carlo simulation plays a role in estimating the expected project span, which is difficult to express analytically \citep{burt1971conditional,van1963letter}.
+Heuristics and simulation-based algorithms have been developed to approximately solve the stochastic project crashing problem \citep{aghaie2009ant, bowman1994stochastic, ke2014genetic, kim2007heuristic}.
+Another approach to handle uncertainty in activity duration is robust optimization, in which the objective is to minimize the worst case project span over a specified uncertainty set.
+While affinely adaptive recourse decisions are computationally tractable as linear, or second-order cone, programs, this restriction may lead to suboptimal solutions \citep{chen2008linear, cohen2007stochastic}.
+However, once recourse decisions can take general form, the robust model is only tractable with rectangular uncertainty sets
+		\citep{wiesemann2012robust}.
+\citet{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.
+The project crashing optimization problem finds application in project management~\citep{demeulemeester2006project, jaselskis1991allocation,tonchia2018industrial}, machine scheduling~\citep{blazewicz1983scheduling,hall1996machine}, health services scheduling~\citep{cardoen2010operating}, chemical processes~\citep{li2008process}, and digital circuit sizing~\citep{kim2007heuristic}.\\
+		\newline
+		In this paper, we propose using the concept of stochastic disruptions to model uncertainty in the duration of activities, which differs from existing approaches in both stochastic programming and robust optimization.
+A stochastic disruption is an event that may occur at any point in the problem's time horizon and results in a change---typically a significant change---in the system's parameters.
+A few authors apply this idea in models with discrete time periods, in which the disruption can only occur in a set of specified time periods.
+\citet{yu2004disruptionmgt} introduce scenario-based optimization models for airline scheduling.
+\citet{morton2009sealift} introduce a sealift scheduling problem under a finite number of stochastic disruptions within a stochastic programming structure; this model structure ``falls between standard two-stage and multi-stage stochastic programs for a multi-period problem" and reduces the size of the problem (scenario tree) to quadratic, rather than exponential, growth in the number of time periods.
+Our setting inherits the philosophy of \citet{morton2009sealift}, but enhances the model by allowing the random disruption time to be continuous in the context of an activity network, instead of a prespecified set of fixed time periods.
+\\
+		\newline
+		Given a limited number of disruption scenarios, the problem of optimizing crashing decisions to minimize expected completion time can be formulated as a stochastic mixed-integer program, and we present the model in Section~\ref{sec:formulation}.
 If we assume a continuous distribution for the disruption time and magnitude, a sample average approximation (SAA) can be used to create a finite set of scenarios and approximate the original problem by a finite-sized optimization problem.
-We present some important properties of this problem using a serial activity network as a special case in Section~\ref{sec:examples}.
-The large scale and the discrete non-convex nature of the SAA problem's extended formulation indicate that it may not be solved efficiently to desirable tolerance level.
-In Section~\ref{sec:decomposition}, a branch-and-cut method based on Benders decomposition is developed to solve the crashing optimization problem with a disruption.
-We show such a decomposition method solves the integer program to the exactness within a finite number of iterations.
-The experiment results are presented in Section~\ref{sec:results}, including the relationship between the solution quality and the sample size, the comparison between the quality of our solution and the deterministic/semi-stochastic alternative solutions, and the computational performance of the decomposition method presented in Section~\ref{sec:decomposition}.
-We conclude our paper with remarks on potential extensions of this model in Section~\ref{sec:conclusions}.
+In Section~\ref{sec:nphard} we show that the problem is NP-hard even with continuous allocation of crashing effort and just two scenarios.
+Section~\ref{sec:examples} presents properties of the problem using a serial activity network as a special case.
+The potentially large scale and the discrete, non-convex nature of the SAA problem's formulation suggest that it may be computationally challenging to solve.
+In Section~\ref{sec:decomposition}, a method based on Benders' decomposition is developed to solve our problem of optimizing crashing decisions under stochastic disruptions.
+We show such a decomposition method can solve the integer program in a finite number of iterations.
+Experiment results are presented in Section~\ref{sec:results}, including the empirical relationship between solution quality and sample size, the comparison between the quality of our solution and solutions of alternative models, and the computational performance of the decomposition method of Section~\ref{sec:decomposition}.
+We conclude with remarks on potential extensions of our model in Section~\ref{sec:conclusions}.
 
 	\section{Problem Formulation} \label{sec:formulation}
-	Nomenclature:
-	%The notation for the model is displayed as follows:
+		{Nomenclature:}
 		\begin{longtable}[H]{ l l l l }
-		\multicolumn{4}{l}{Indices and index sets} \\
-		\\
+			\multicolumn{4}{l}{\em Indices and index sets} \\
 			\(I\) & \(\qquad\) & the set of activities;&\\
-		\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i\), \(i \in I\);&\\
-		\(\Omega\) & \(\qquad\) & the index set of possible realizations of disruption;&\\
-		\(\mathcal{A}\) &\(\qquad\) & set of arcs which represents the precedence relationship;&\\
-		\\
-		\multicolumn{4}{l}{Parameters} \\
-		\\
-		\(D_{ik}\)& \(\qquad\) & nominal separation time between activity \(i\) and \(k\), \((i,k) \in \cA\);&\\
-		\(e_{ij}\) & \(\qquad\) & effectiveness of crashing option \(j\), \(i \in I, j \in J_i\);&\\
-		\(B\) & \(\qquad\) & total budget of crashing options;&\\
-		\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j\) for activity \(i\), \(i \in I, j \in J_i\);&\\
-		\(H^\omega\) &\(\qquad\) & disruption time in scenario \(\omega\), \(\omega \in \Omega\);&\\
-		\(d_{i}^\omega\) & \(\qquad\)&the change of duration of activity \(i\) in realization \(\omega\), &\\
-		& \(\qquad\) & if the activity is started after the disruption, \(i \in I, \omega \in \Omega\);& \\
-		\(p^\omega\) & \(\qquad\) & the probability of scenario \(\omega\), \(\omega \in \Omega\);& \\
+			\(J_i\) & \(\qquad\) & the set of crashing options for activity \(i \in I\);&\\
+			\(\Omega\) & \(\qquad\) & the index set for disruption scenarios (sample space);&\\
+			\(\cA\) &\(\qquad\) & set of arcs, which represents precedence relationships;&\\
+			\\
+			\multicolumn{4}{l}{\em Parameters} \\
+			\(D_{ik}\)& \(\qquad\) & nominal duration between possible start times of activities \(i\) and \(k\), \((i,k) \in \cA\);&\\
+			\(e_{ij}\) & \(\qquad\) & effectiveness of crashing option $j \in J_i$ for activity \(i \in I\);&\\
+			\(B\) & \(\qquad\) & total budget for crashing options;&\\
+			\(b_{ij}\) & \(\qquad\) & cost of crashing option \(j \in J_i\) for activity \(i \in I\);&\\
+			\(H^\omega\) &\(\qquad\) & disruption time under scenario \(\omega \in \Omega\);&\\
+			\(d_{ik}^\omega\) & \(\qquad\)& increase in duration of \((i,k) \in \cA\) under \(\omega \in \Omega\), if started after the disruption; &\\
+			\(p^\omega\) & \(\qquad\) & the probability of scenario \(\omega \in \Omega\);& \\
 			\(p^0\) & \(\qquad\) & the probability of no disruption;& \\
 			\\
-		\multicolumn{4}{l}{Decision Variables}\\
-		\\
-		\(t_{i}\) & \(\qquad\) & nominal start time of activity \(i\), \(i \in I\);&\\
-		\(x_{ij}\) & \(\qquad\) & fraction activity \(i\) is crashed by option \(j\) in the nominal plan, \(i \in I, j \in J_i\); &\\
-		\(t_{i}^\omega\) & \(\qquad\) & start time of activity \(i\) under scenario \(\omega\), \(i \in I, \omega \in \Omega\);&\\
-		\(x_{ij}^\omega\) & \(\qquad\) & fraction activity \(i\) is crashed by option \(j\) under scenario \(\omega\), \(i \in I, j \in J_i, \omega \in \Omega \); &\\
-		\(G_i^\omega\) & \(\qquad\) & indicator whether activity \(i\) starts after disruption in realization \(\omega\), \(i \in I, \omega \in \Omega\);&\\
-		\(z_{ij}^\omega\) & \(\qquad\) & binary term to linearize the bilinear term \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&\\
+			\multicolumn{4}{l}{\em Decision variables}\\
+			\(t_{i}\) & \(\qquad\) & nominal start time of activity \(i \in I\);&\\
+			\(x_{ij}\) & \(\qquad\) & crashing of activity \(i \in I\) by option \(j \in J_i\) in the nominal plan; &\\
+			\(t_{i}^\omega\) & \(\qquad\) & start time of activity \(i \in I\) under scenario \(\omega \in \Omega\);&\\
+			\(x_{ij}^\omega\) & \(\qquad\) & crashing of activity \(i \in I\) by option \(j \in J_i\) under scenario \(\omega \in \Omega\); &\\
+			\(G_i^\omega\) & \(\qquad\) & binary indicator whether activity \(i \in I\) starts after disruption under \(\omega \in \Omega\);&\\
+			\(z_{ij}^\omega\) & \(\qquad\) & binary term to linearize bilinear term, \(G_i^\omega x_{ij}^\omega\), \(i \in I, j \in J_{i}, \omega \in \Omega\).&
 		\end{longtable}
-	\noi We first review the formulation of the deterministic crashing optimization problem in~\cite{fulkerson1961network, kelley1961criticalpath}.
-A set of activities, \(I\), together with the precedence relationships, \(\mathcal{A} \subseteq I \times I\) form an acyclic activity network \(\mathcal{G} = (I,\mathcal{A})\) which represent the project.
-An arc \((i,k) \in \mathcal{A}\) indicates that activity \(i\) has to be finished before the start of activity \(k\), and its length, \(D_{ik}\), shows that the start time of activity \(i\) has to be at least \(D_{ik}\) before the start time of activity \(k\).
-We create two dummy activities \(S, T \in I\) to represent the start and the end of the entire project.
-Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\} \), and they both have zero duration, \(D_{Si} = D_{iT} = 0,\ \forall i \in I\).
+		\noi We first review an optimization model for a deterministic crashing problem; see~\citet{fulkerson1961network, kelley1961criticalpath}.
+A set of activities, \(I\), together with precedence relationships, \(\cA \subseteq I \times I\), form an acyclic activity network \(\mathcal{G} = (I,\cA)\), which represents the project.
+An arc \((i,k) \in \cA\) indicates that activity \(i\) has to finish before activity \(k\) starts, and its length, \(D_{ik}\), shows that the start time of activity \(i\) has to be at least \(D_{ik} \ge 0\) before the start time of activity \(k\).
+We create two dummy activities \(S, T \in I\) to represent the start and the termination of the entire project.
+Activity \(S\) should precede every activity \(i \in I \backslash \{S\}\) and \(T\) should succeed every activity \(i \in I \backslash \{T\}\), either directly or by implication, and they both have zero duration.
+
 		We can apply a finite set of crashing options, \(j \in J_i\), to activity \(i \in I\).
-One unit application of each option incurs a cost of \(b_{ij}\), while it decreases all required separation lengths starting from activity \(i\) by \(D_{ik}e_{ij},\ \forall (i,k) \in \mathcal{A}\), where \(e_{ij} \in [0,1]\) denotes the unit effectiveness of the crashing option \(j\).
-For example, suppose the required separation between the start time of activity \(1\) and \(2\) is \(D_{12} = 10\), and applying one unit of crashing option \(1\) on activity \(1\) decreases that to its half; i.e., \(e_{11} = 0.5\).
-If we apply \(0.4\) unit of crashing option \(1\) on activity \(1\), \(x_{11} = 0.4\), the required separation between activity \(1\) and \(2\) becomes \(10(1 - 0.4 \times 0.5) = 8\).
+One unit application of each option incurs a cost of \(b_{ij}\), and it decreases the corresponding durations by \(D_{ik}e_{ij},\ \forall (i,k) \in \cA\), where \(e_{ij} \in [0,1]\) denotes the unit effectiveness of crashing option \(j\).
+For example, suppose the duration between the start time of activity \(1\) and \(2\) is \(D_{12} = 10\), and applying one unit of crashing option \(1\) to activity \(1\) decreases the duration by half; i.e., \(e_{11} = 0.5\).
+If we apply \(0.4\) unit of crashing option \(1\) to activity \(1\), \(x_{11} = 0.4\), the required separation between activity \(1\) and \(2\) becomes \(10(1 - 0.4 \cdot 0.5) = 8\).
 The total cost of crashing cannot exceed a given budget, \(B\).
-Given $t_S \equiv 0$, the objective is then to minimize the start time of activity \(T\).
-Thus, we formulate the deterministic project crashing problem as:
+The objective is then to minimize the start time of activity \(T\), and thus, we formulate the deterministic project crashing problem as:
 		\begin{subequations} \label{prob:static}
@@
 			\min \quad & t_T &\\
-		\text{s.t.} \quad &  t_k - t_i \geq D_{ik}\left(1 - \sum_{j \in J_i} x_{ij} e_{ij}\right) \qquad \qquad \forall \,(i,k) \in \mathcal{A} \label{cons:dSep}\\
+			\text{s.t.} \quad &  t_k - t_i \geq D_{ik}\left(1 - \sum_{j \in J_i} e_{ij} x_{ij} \right) \qquad \qquad \forall \,(i,k) \in \cA \label{cons:dSep}\\
 			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:dBudget}\\
 			& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:dSingleBudget}\\
-		& x_{ij} \geq 0  \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:dxub}\\
-		& t_S = 0. \label{cons:dNonnegt}
+			& 0 \le x_{ij} \leq 1  \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:dxub}\\
+			& t_i \geq 0 \qquad \qquad \qquad \;\, \forall\, i \in I. \label{cons:dNonnegt}
 			\end{align}
@@
 We aim to minimize the project span, which is the start time of the terminal activity, \(t_T\).
-Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until activity \(i\) is finished, since the finish time of activity \(i\) is \(t_i + D_{ik} (1- \sum_{j \in J_i} x_{ij}e_{ij})\).
+Constraint~\eqref{cons:dSep} guarantees the precedence relationship: if activity \(i\) precedes activity \(k\), activity \(k\) cannot start until time \(t_i + D_{ik} (1- \sum_{j \in J_i} e_{ij} x_{ij})\).
 Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
-Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities since activity \(S\) precedes every other activity.\\
-	\newline
-	For a project crashing problem under stochastic disruptions, we assume at most one stochastic disruption can occur at a random time in the project span, since for the applications we are interested in (natural disasters, terrorist attacks, major market crashes, etc.), it is unlikely for two disruptions to occur in entire the time horizon.
-For example, suppose we manage a construction project, and we aim to plan against the potential hazard caused by earthquakes.
-It is unlikely for two major earthquakes to hit the same area twice within a year (aftershocks can be considered part of a major earthquake.) It is also reasonable to assume for each activity \(i \in I\), the crashing decision needs to be made at the start of that activity, and cannot be changed afterward, especially when contracts are involved in commitment of resources~\cite{oberlender1993project}.
-The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution.
-It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}.
-In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\).
-For each scenario \(\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration between activity \(i\) and \(k\), \(d_{ik}, \forall (i,k) \in \cA\).
-\\
-	\newline
-	If there is at most one disruption, we can model the problem as a two-stage stochastic mixed integer program.
-The definition of our first stage is different from the traditional stochastic program setting.
-Here the first stage contains decisions through completion of the project if no disruption occurs and the second stage characterizes the decisions for each realization of the disruption.
+Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities.\\
+		\newline
+		For a project crashing problem under stochastic disruptions, we assume at most one stochastic disruption can occur at a random time in the project span.
+While this assumption may be limiting in some settings, it is appropriate when it is unlikely for two or more disruptions to occur during the time horizon, and can apply, e.g., for natural disasters, major market crashes, cyber attacks, and work stoppages.
+For example, suppose we manage a construction project, and we aim to plan against the potential hazard caused by an earthquake or an employee strike.
+It may be unlikely for two major earthquakes or strikes to affect the same project within the relevant time period.
+We further assume that for each activity \(i \in I\), the crashing decision needs to be made prior to the start of that activity, which is reasonable, e.g., when contracts are involved in commitment of resources~\citep{oberlender1993project}.
+We assume a disruption does not affect activities that have already started (including those already finished) at the time of the disruption, but the disruption changes the length of activities that have not yet started according to a known probability distribution.
+It is usually hard to compute the recourse function directly when random parameters have a continuous distribution, and therefore we use sample average approximation (SAA)~\citep{kim2015guide,shapiro2009lectures}.
+In this paper, we assume there is a finite set of scenarios indexed by \(\omega \in \Omega\).
+For each scenario \(\omega\), the random realization of parameters, which we denote \(\xi^\omega\), consists of the timing of the disruption, \(H^\omega\), and the magnitude of the disruption via increases in the duration parameters, \(d^\omega_{ik}, \forall (i,k) \in \cA\).
+\\
+		\newline
+		Because we assume at most one disruption, we can model the problem as a two-stage stochastic mixed integer program, in which the timing of the second stage is random.
+That is, the definition of our stages differs from the usual stochastic programming setting.
+Here the first stage contains decisions through completion of the project, and we follow this policy if no disruption occurs.
+And, the second stage characterizes the decisions for each realization of the disruption, which commence at the random time, $H^\omega$.
 The first stage decision variables are carried out until the disruption if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
@@
 			\min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\
-		\text{s.t.} \quad & t_k - t_i \geq D_{ik}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \, (i,k) \in \mathcal{A} \label{cons:Sep}\\
+			\text{s.t.} \quad & t_k - t_i \geq D_{ik} \left ( 1 - \sum_{j \in J_i} e_{ij} x_{ij} \right ) \qquad \qquad \forall \, (i,k) \in \cA \label{cons:Sep}\\
 			& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:Budget}\\
@@
 			& x_{ij}^\omega - G_i^\omega \leq x_{ij} \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:xG2}\\
-		& t_k^\omega - t_i^\omega \geq D_{ik} + d_{ik}^\omega G_i^\omega -\sum_{j \in J_i} D_{ik} e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_{ik}^\omega e_{ij} z_{ij}^\omega \qquad \qquad \forall \,(i,k) \in \cA, \omega \in \Omega \label{cons:scenSep}\\
+			& t_k^\omega - t_i^\omega \geq D_{ik} + d_{ik}^\omega G_i^\omega -\sum_{j \in J_i} D_{ik} e_{ij} x_{ij}^\omega - \sum_{j \in J_i} d_{ik}^\omega e_{ij} z_{ij}^\omega \qquad  \forall \,(i,k) \in \cA, \omega \in \Omega \label{cons:scenSep}\\
+			& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:scenBudget}\\
 			& \sum_{j \in J_i} x_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, \omega \in \Omega \label{cons:scenBudget1}\\
-		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij}^\omega \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:scenBudget}\\
 			& z_{ij}^\omega \leq G_i^\omega \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega \label{cons:linearize1}\\
@@
 			& t_i \geq 0 \qquad \qquad \forall \,i \in I \label{cons:nonnegt}\\
-		& t_i^\omega \geq H^\omega G_i^\omega \qquad \qquad \forall\, i \in I, \omega \in \Omega \\
+			& t_i^\omega \geq H^\omega G_i^\omega \qquad \qquad \forall\, i \in I, \omega \in \Omega \label{cons:extra} \\
 			& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\ 
@@
 		\end{subequations}
-	In model~\eqref{prob:extensive}, we are minimizing the expected project span by taking the sum of each scenario's project span weighted by the scenario probability.
-We keep the constraints~\eqref{cons:dSep}-\eqref{cons:dSingleBudget} for the nominal scenario as~\eqref{cons:Sep}-\eqref{cons:SingleBudget}.
-In constraints~\eqref{cons:G1}-\eqref{cons:G2}, variables \(G^\omega_i\) takes value \(1\) if activity \(i\) starts after the disruption time; otherwise it takes value 0, and \(M\) is a large number to enforce this logic relationships.
+		In model~\eqref{prob:extensive}, we minimize the expected project span, weighing the span under each scenario by its probability.
+We replicate constraints~\eqref{cons:dSep}-\eqref{cons:dSingleBudget} for the nominal scenario as~\eqref{cons:Sep}-\eqref{cons:SingleBudget}.
+In constraints~\eqref{cons:G1}-\eqref{cons:G2}, variable \(G^\omega_i\) takes value \(1\) if activity \(i\) starts after the disruption time; otherwise it takes value 0, and \(M\) is a large number to enforce the logic of this relationship.
 This is important in our problem setting because the duration of each activity depends on its temporal relationship to the disruption time, which is reflected in constraint~\eqref{cons:scenSep}.
-Also we have to ensure that the decisions made before the disruption time in each scenario are the same as the nominal decisions.
-Therefore, we set up non-anticipativity constraints~\eqref{cons:tG1}-\eqref{cons:xG2}.
+Also, we must ensure that decisions made before the disruption time in each scenario match the nominal decisions, and constraints~\eqref{cons:tG1}-\eqref{cons:xG2} capture these non-anticipativity conditions.
 For each scenario, the duration between activity \(i\) and \(k\) becomes \((D_{ik} + d_{ik}^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\), which expands to the form of constraint~\eqref{cons:scenSep}.
-If \(G_i^\omega = 0\), which means activity \(i\) starts before the disruption time of scenario \(\omega\), this expression is the same as \(D_{ik} (1 - \sum_{j \in J_i} e_{ij}x_{ij})\) since \(x_{ij} = x_{ij}^\omega\) is enforced by constraints~\eqref{cons:xG1} and~\eqref{cons:xG2}.
-If \(G_i^\omega = 1\), then the duration between activity \(i\) and \(k\) is changed to \(D_{ik} + d_{ik}^\omega\).
-The expression \((D_{ik} + d_{ik}^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\) contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which can be linearized by introducing a binary variable \(z_{ij}^\omega\) and constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.
+If \(G_i^\omega = 0\), which means activity \(i\) starts before the disruption time of scenario \(\omega\), this expression is the same as \(D_{ik} (1 - \sum_{j \in J_i} e_{ij}x_{ij})\) because \(x_{ij} = x_{ij}^\omega\) is enforced by constraints~\eqref{cons:xG1} and~\eqref{cons:xG2}.
+If \(G_i^\omega = 1\), then the duration between activity \(i\) and \(k\) is changed to \(D_{ik} + d_{ik}^\omega \ge 0\).
+We allow a negative ``increase'' in duration $d_{ik}^\omega$, but require the overall duration to be nonnegative.
+The expression \((D_{ik} + d_{ik}^\omega G_i^\omega)(1 - \sum_{j \in J_i} e_{ij}x_{ij}^\omega)\) contains a bilinear term \(G_i^\omega x_{ij}^\omega\), which we linearize using binary variable \(z_{ij}^\omega\) and constraints \eqref{cons:linearize1}-\eqref{cons:linearize3}.
 
@@
 			\centering
-		\includegraphics[width=0.8\textwidth]{layer1}
+			\includegraphics[width=0.6\textwidth]{layer1}
 			\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\) in the first layer of the constructed activity network for \texttt{EOIT\char`_3SAT}.}
@@
 \section{Illustration of Problem Properties via Examples} \label{sec:examples}
-	In this section, we show two examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, and its distinctions from the deterministic problem.
+	We show two examples of serial activity networks to give insight regarding the nature of the project crashing problem under a stochastic disruption, and to draw distinctions relative to its deterministic counterpart.
 In the deterministic project crashing problem, all activities on the critical path should start as soon as possible.
-However, with a stochastic disruption, it might be optimal to delay the start of some activities.
-In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path.
-We use the following two examples to show that the deterministic optimal solution could be significantly inferior in the stochastic setting because of those two properties.
-\tcb{Starting from this section, we assume that required separations between an activity \(i\) and all its successors \(k\) are the same for simplicity; i.e., for every activity \(i\) we use \(D_i\) to represent the duration of activity \(i\) and \(d_i^\omega\) to denote the change of duration due to the disruption scenario \(\omega\):
+However, with a stochastic disruption, it is sometimes optimal to delay the start of one or more activities.
+In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a shorter expected duration is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to crash the activity with the longest duration on the critical path, under equal $b_{ij}$ and $e_{ij}$ values.
+We use two examples to show that the deterministic optimal solution can be significantly inferior in the stochastic setting because of these two properties.
+Here, we assume that required duration that separates the start of activity \(i\) and the start of a successor, \(k\), only depends on $i$; i.e., for each activity \(i\) we use \(D_i\) to denote the duration of activity \(i\) and \(d_i^\omega\) to denote the change in duration under scenario \(\omega\):
 	\begin{align*}
@@
 	& d^{\omega}_{ik} = d^{\omega}_i \qquad \qquad \forall (i,k) \in \cA, \omega \in \Omega.
-	\end{align*}}
+	\end{align*}
+	Clearly delaying the start of an activity may be beneficial when \(d_i^\omega < 0\) for some \(i \in I, \omega \in \Omega\) because the expected decrease in duration may exceed the delay required to move the start of activity \(i\) after a potential disruption.
+In the following example, we show value of delay, even if all activities are lengthened by the disruption; i.e., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
 	\begin{figure}[H]
 		\centering
-		\includegraphics[width=0.6\textwidth]{serial2}
+		\includegraphics[width=0.4\textwidth]{serial2}
 		\caption{Example of a 2-activity serial network project}
@@
 	\begin{example} \label{eg:delay}
-		It is obvious that the delay can possibly be beneficial when \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\) because the decrease in duration may outweigh the length of delay to move the start of activity \(i\) after the disruption.
-Therefore, we set up a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption; i.e., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\).
-Consider a network with two activities in series, as shown in Figure~\ref{fig:serial2}.
-Suppose we have a parameter \(k > 4\).
-In this example, $I=\{S,1,2,T\}$ with nominal durations $D_1 = k$ and $D_2 = 1$.
+		Consider a network with two activities in series, as shown in Figure~\ref{fig:serial2} with $I=\{S,1,2,T\}$, and let parameter \(k > 4\).
+Let the nominal durations be $D_1 = k$ and $D_2 = 1$.
 We assume only one crashing option for each activity, and so we omit index $j$.
 We let $e_1=e_2=1 - \frac{1}{2k}$, assume $b_i=1$ for all $i \in I$, and we let $B=1$.
-Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=1 - \frac{1}{k}$, or we have a disruption that occurs at time $\varepsilon \leq \frac{1}{2}$ with probability $p^1=\frac{1}{k}$.
+Let $\Omega=\{1\}$ so that either we have no disruption with probability $p^0=1 - \frac{1}{k}$, or we have a disruption that occurs at time $\varepsilon < \frac{1}{2}$ with probability $p^1=\frac{1}{k}$.
 If a disruption occurs, the nominal activity durations are lengthened by $d_1 = k$ and $d_2 = (k - 1)^2$.
@@
 		If we start each activity without delay, then \(t_1 = 0,\ x_1=x_1^1\), and for any \(x_1 \leq 1\), \(t_2 \geq \frac{1}{2} \geq D_1(1 - e_1 x_1) \), which means activity \(2\) will start after the disruption.
-Since \(k > 1\), the expected duration of activity \(1\), $D_1 = k$ is greater than the expected duration of activity 2, $ D_2 + p^1 d_2 = 1 + \frac{1}{k} (k-1)^2 = k - 1 + \frac{1}{k}$.
+Since \(k > 1\), the duration of activity~\(1\), $D_1 = k$, exceeds the expected duration of activity 2, $ D_2 + p^1 d_2 = 1 + \frac{1}{k} (k-1)^2 = k - 1 + \frac{1}{k}$.
 As a result, it is optimal to spend the entire budget on activity \(1\): $x_1=x_1^1=1$ and $x_2=x_2^1=0$, and the expected project duration is:
-		\begin{subequations}
-			\label{nodelay}
-			\begin{align}
+		\begin{align*}
 		&D_1 (1 - e_1 x_1) + p^0 D_2 + p^1 (D_2 + d_2) \\
-			= & k \left(1 - (1 - \frac{1}{2k})\cdot 1 \right) + (1 - \frac{1}{k}) \cdot 1 + \frac{1}{k} \left(1 + (k -1)^2\right) \\
+		= & k \left(1 - \left (1 - \frac{1}{2k} \right )\cdot 1 \right) + (1 - \frac{1}{k}) \cdot 1 + \frac{1}{k} \left(1 + (k -1)^2\right) \\
 		= & k - \frac{1}{2} + \frac{1}{k}.
-			\end{align} 
-		\end{subequations}
-		On the other hand, if we delay the start of activity 1 until $t_2= \varepsilon$ then $x_1$ and $x_1^1$ need not be equal.
-Since for \(k > 2 + \sqrt{2}\), $k = D_1 > D_2 = 1$ and $(k - 1)^2 + 1 = D_2+d_2 > D_1 + d_1 = k + k$, we have $x_2=1$ and $x_3^1=1$ in an optimal solution, and the expected duration is:
-		\begin{subequations}
-			\begin{align}\label{delay}
+		\end{align*}
+		On the other hand, if we delay the start of activity 1 until $t_1= \varepsilon$ then $x_1$ and $x_1^1$ need not be equal.
+Since for \(k > 2 + \sqrt{2}\), $k = D_1 > D_2 = 1$ and $(k - 1)^2 + 1 = D_2+d_2 > D_1 + d_1 = k + k$, we have $x_1=1$, $x_1^1=0$, $x_2^1=1$ in an optimal solution, and the expected duration is:
+		\begin{align*}
 		&\varepsilon + p^0 \left[D_1 \cdot \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) + D_2 \right]  + p^1 \left[(D_1 + d_1) + \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) (D_2 + d_2) \right]\\
@@
 		= & \varepsilon + 4 - \frac{5}{2k} + \frac{1}{k^2}.
-			\end{align}
-		\end{subequations}
-		In the example above, as \(k \to +\infty\), the project span without delay approaches \(+\infty\), but the project span with delay has a constant limit \(\varepsilon + 4\).
-This example shows that with the possibility that a rare but pathological disruption may occur, it is infinitely better to delay the start of some activities.
-In summary, the reasons for such delay include:
-		\begin{enumerate}
-			\item Some activities might have a shorter length after the disruption. It is beneficial to wait a short period of time to capture this advantage.
-			\item Even if all possible disruption magnitudes are adverse, which means they lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
-		\end{enumerate}
-		Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.
+		\end{align*}
 	\end{example}
+	In Example~\ref{eg:delay} if require that activity~1 be started without delay then the objective function grows to infinity with $k$, but the optimal project span by delaying the start of activity~1 by $\varepsilon$ has a constant limit of \(\varepsilon + 4\).
+This example shows that the gap between the optimal solution under a no-delay policy and an optimal solution that allows for delay---as we do in model~\eqref{prob:extensive}---can be arbitrarily large.
+Because it is possible for an optimal crashing plan to contain a delay for some activities, model~\eqref{prob:extensive} uses decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assuming that each activity starts as soon as all of its predecessors are finished.
+	%In summary, the reasons for such delay include:
+	%		\begin{enumerate}
+	%			\item Some activities might have a shorter length after the disruption. It is beneficial to wait a short period of time to capture this advantage.
+	%			\item Even if all possible disruption magnitudes are adverse, which means they lengthen all activities, it is beneficial to delay an activity so that the crashing resource could be optimally applied according to the realization of disruption.
+	%		\end{enumerate}
 	\begin{example} \label{eg:short}
-		Consider the same network with two activities in series as shown in Figure~\ref{fig:serial2}.
-Let $D_1$ and $D_2$ denote the two durations with $D_2 > D_1$.
-Assume $d_1=0$, $d_2 > 0$, $e_1=e_2=\frac{1}{2}$, and $B=1$.
-Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=\frac{1}{2}$, or we have a disruption that occurs at time $\frac{1}{2}D_1$ with probability $p^1=\frac{1}{2}$.
+		We again consider the network with two activities from Figure~\ref{fig:serial2}.
+Let $D_2 > D_1$, $d_1=0$, $d_2 > 0$, $e_1=e_2=\frac{1}{2}$, and $B=1$.
+We again consider a single disruption scenario, $\Omega=\{1\}$, so that either we have no disruption, $p^0=\frac{1}{2}$, or we have a disruption that occurs at time $H^1=\frac{1}{2}D_1$ with probability $p^1=\frac{1}{2}$.
 Here, the optimal solution is to crash the shorter activity, i.e., $x_1=1$, which yields an expected project span of $\frac{1}{2}D_1 + D_2$ with start times $t_1=0$ and $t_2=\frac{1}{2}D_1$.
-In contrast, if $0 \le x_1 < 1$ then the expected duration is $D_1 (1-\frac{1}{2} x_1) + (D_2 + d_2)(1-\frac{1}{2} x_2)$, so that the ratio of the objective functions grows arbitrarily large as $d_2$ grows.
-The intuition behind crashing the shorter activity is that it allows us to initiate activity 2 in time to avoid having to incur delay $d_2$.
+In contrast, if $0 \le x_1 < 1$ then the expected duration is $D_1 (1-\frac{1}{2} x_1) + (D_2 + \frac{1}{2} d_2)(1-\frac{1}{2} x_2)$, so that the ratio of the objective functions grows arbitrarily large as $d_2$ grows.
 	\end{example}
 
-	\noi Example~\ref{eg:delay} and~\ref{eg:short} indicate that the crashing optimization problem with stochastic disruption has complicated nature.
-The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
+	\noi In Example~\ref{eg:short} the intuition behind crashing the shorter activity is that it allows us to initiate activity~2 in time to avoid incurring delay~$d_2$.
+Both examples in this section suggest that the intuition associated with the deterministic version of the optimal crashing problem does not always apply in the stochastic setting, and provides further motivation for employing a model like that in formulation~\eqref{prob:extensive}.
 
 	\section{Decomposition Method} \label{sec:decomposition}
-	Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program (2SMIP).
-First we can decompose it into a master problem \((M)\) and a set of subproblems \((S^\omega)\), \(\omega \in \Omega\) as follows.
+	Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program (2SMIP), which is large-scale and computationally expensive in general~\cite{ahmed2011smip}.
+We first follow the Benders' decomposition method to separate the model into a master problem \((M)\) and a set of subproblems \((S^\omega)\), \(\omega \in \Omega\).
 The state variables \(t\) and \(x\) are all continuous and binary variables exist in the recourse problems, which makes recourse problems nonconvex.
@@
 		& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
-		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i.
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i. \label{cons:Mxbounds}
 		\end{align}
@@
 	\newline
-	We can relax the integrality constraints~\eqref{cons:subInt} and solve the subproblem to obtain Benders' cuts.
-Although those Benders' cuts are no longer a tight approximation of the recourse function \(f^\omega(x,t), \forall \omega \in \Omega\), they still provide a valid lower bound.
-On the other hand, in each iteration of the Benders' decomposition, the upper bound can be obtained by solving the subproblems~\eqref{prob:subOri}, given a first stage solution.
-We observe that a smaller \(M\) yields a tighter gap between the upper bound and the lower bound, because we can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
+	We can relax the integrality constraints~\eqref{cons:subInt} and perform Benders' decomposition on the relaxed problem.
+Benders' cuts provide a valid lower approximation of the recourse function \(f^\omega(t,x), \forall \omega \in \Omega\) but may not be tight.
+In each iteration of the Benders' decomposition, an upper bound can be obtained by evaluating the subproblems~\eqref{prob:subOri} with the first stage solution.
+The main challenge is how to gradually tighten the lower approximation while quickly locate a good upper bound, and all topics in this section aim to tackle either aspect of this challenge.
+	\subsection{Partitioning-based Decomposition Method} \label{subsec:partition}
+	The relaxation quality is poor since a big-\(M\) needs to be incorporated in our recourse problems to represent the logical condition whether the starting time of activity \(i\) is before or after the disruption time.
+A smaller big-\(M\) yields a tighter relaxation and helps prevent numerical issues~\cite{camm1990cutting,klotz2013practical}.
+We can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
 	\begin{equation} \label{cons:Grange}
@@
 		\begin{align}
-		(S_{\mathcal{P}}^\omega) \qquad g^\omega_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
+		(S_{\mathcal{P}}^\omega) \qquad f^\omega_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
 		\text{s.t.} \quad & \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i - H^\omega \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
@@
 		\begin{align} \label{cons:validlb}
-			&g^\omega_{\mathcal{P}}(t,x,y) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
+		&f^\omega_{\mathcal{P}}(t,x,y) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
 		& \qquad \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad \forall \ell = 1,2, \dots.
@@
 	\begin{proof}
-		We denote the recourse function corresponding to the partition \(\mathcal{P}^{\ell}\) as \(g^\omega_{\mathcal{P}^\ell}(t,x,y)\), where \(y\) has the correct dimension according to \(\mathcal{P}^\ell\).
+		We denote the recourse function corresponding to the partition \(\mathcal{P}^{\ell}\) as \(f^\omega_{\mathcal{P}^\ell}(t,x,y)\), where \(y\) has the correct dimension according to \(\mathcal{P}^\ell\).
 We first prove that
 		\begin{equation} \label{cons:gglb}
-			g^\omega_{\mathcal{P}}(t,x,y) \geq g^{\omega}_{\mathcal{P}^\ell}(t,x,\tilde{y}) \qquad \forall \ell = 1,2,\dots
+		f^\omega_{\mathcal{P}}(t,x,y) \geq f^{\omega}_{\mathcal{P}^\ell}(t,x,\tilde{y}) \qquad \forall \ell = 1,2,\dots
 		\end{equation}
@@
 		\begin{equation} \label{cons:validglb}
-		 	g^\omega_{\mathcal{P}^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
+		f^\omega_{\mathcal{P}^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
 		\end{equation}
@@
 The decomposition algorithm is presented as follows:\\
-	\begin{algorithm}[H]
-		\caption{Decomposition algorithm to solve problem~\eqref{prob:extensive}}
+	\begin{algorithm}
+		\caption{Partition Based Decomposition algorithm to solve problem~\eqref{prob:extensive}}
 		\label{alg:Cut}
 		\begin{algorithmic}[1]
-			\State Initialize with cut iteration number \(\ell = 0\), lower bound \(LB = 0\), upper bound \(UB = +\infty\), initial partition \(\mathcal{P}^\ell\) with its indexed set \(\mathcal{Q}^\ell\), and specified tolerance \(\epsilon > 0\) and \(\delta > 0\);
+			\State Initialize with cut iteration number \(\ell = 0\), lower bound \(LB = 0\), upper bound \(UB = +\infty\), initial partition \(\mathcal{P}^\ell\) with its indexed set \(\mathcal{Q}^\ell\), and specified tolerance parameters \(\epsilon > 0\) and \(\delta > 0\);
 			\While{\(\frac{UB - LB}{UB} > \epsilon\)} 
@@
 			\EndIf
-			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t},\hat{x})\). 
+			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t}^{\ell},\hat{x}^{\ell})\). 
 			\State Calculate \(z^* = p^0 \hat{t}^\ell_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^\ell,\hat{x}^\ell)\)
@@
 			\State For each \(\omega \in \Omega\), solve problem \((S_{\mathcal{P}}^\omega)\) given \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and obtain optimal value \(v^{\omega,\ell}\) and coefficients \(\pi^{\omega,\ell}, \lambda^{\omega,\ell}, \gamma^{\omega,\ell}\);
-			\If{\(z^*_P < p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
+			\If{\(z^*_{\mathcal{P}} < p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
 			\State Add the cuts of form~\eqref{cons:cut} to the master problem;
@@
 			\EndWhile{\textbf{end while}}
-			\State Output \(UB\) as the optimal value of model~\eqref{prob:extensive}, and \(t^*, x^*,y^*\) as the optimal solution.
+			\State Output \(UB\) as the optimal value of model~\eqref{prob:extensive}, and \(t^*, x^*\) as the optimal solution.
 		\end{algorithmic}
 	\end{algorithm}
-	\noi Finally we prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
+	\noi We prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
 Since every partition update is a refinement and we have a finite set of scenario \(\Omega\), we can prove the finite convergence of Algorithm~\ref{alg:Cut} as long as with the finest partition we reach the optimum of problem~\eqref{prob:extensive}.
 	\begin{proposition} \label{prop:finestPar}
-		If a partition \(\hat{\mathcal{P}}\) has indexed sets \(\hat{\mathcal{Q}}\) and for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), we have \[z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y),\]
+		If a partition \(\hat{\mathcal{P}}\) has indexed sets \(\hat{\mathcal{Q}}\) and for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), we have \[z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y),\]
 		where 
@@
 		Next we prove that, given the partition in Proposition~\ref{prop:finestPar}, we can construct a feasible solution, \((t^*,x^*,G^*)\), to the extensive formulation~\eqref{prob:extensive} with the same objective value from the optimal solution, \((\hat{t},\hat{x},\hat{y})\), to the problem
-		\[\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y).\]
+		\[\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y).\]
 		Suppose for \(i \in I\), we denote the index of partition where \(y\) variable takes value \(1\) as \(q_i\).
@@
 This result is equivalent to \(z_{\hat{\mathcal{P}}}^* \geq z^*\).
-Combining the results above we conclude that \(z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y).\)
+Combining the results above we conclude that \(z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y).\)
 	\end{proof}
@@
 	\begin{proof}
-		From Proposition~\ref{prop:finestPar} we know that with the finest partition \(\hat{\mathcal{P}}\) where for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\mathcal{Q}}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} g^\omega_{\hat{\mathcal{P}}}(t,x,y)\) is equivalent to solving the extensive formulation.
+		From Proposition~\ref{prop:finestPar} we know that with the finest partition \(\hat{\mathcal{P}}\) where for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\mathcal{Q}}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y)\) is equivalent to solving the extensive formulation.
 Since there are only finite number of scenarios, it takes finite number of steps of refinement to reach the finest partition.
@@
 		For each subproblem, there is only a finite number of possible values of dual variables because each corresponds to one of the finitely many different bases.
-This means that, for any partition \(\mathcal{P}\), the recourse function \(g^\omega_{\mathcal{P}}\) can be represented by finitely many linear cuts.
+This means that, for any partition \(\mathcal{P}\), the recourse function \(f^\omega_{\mathcal{P}}\) can be represented by finitely many linear cuts.
 Therefore, in algorithm~\ref{alg:Cut}, only a finite number of cuts are added for a finite number of partitions before \(UB = z^*\) and \(LB = z^*_{\hat{\mathcal{P}}}\) is achieved, a.k.a.
@@
 	\end{proof}
-	\begin{comment}
-	\textcolor{blue}{ The materials above are the most important idea I want to convey in this section.
-Here are some additional results we have discussed but I haven't compiled to \LaTeX \ yet.
-Time allowing, I can add some stuff in maybe tonight or this coming week.
-		\begin{itemize}
-			\item Concavity of \(\mathbb{E}_d \left[ f(x,H,d) | H \right]\) in \(d\).
-			\item The analytical form of the recourse function when all \(d\) are \([0,1]\)-uniformly distributed, all \(D\) are equal, and the crashing option can only be integer.
-			\item The recourse function is a decreasing function in terms of remaining budget, given the same remaining task set.
-			\item Not optimal to delay the start of activity \(i\) unless there is no investment before \(i\), given a fixed \(H\).
-			\item Only optimal to delay to a possible disruption time.
-		\end{itemize}
-	}
-	\subsection{Parallel Networks}
-		\begin{itemize}
-			\item Not optimal to delay when \(d_i \geq 0\) if each branch only contains a single activity.
-			\item If each branch is a serial path, it is possibly beneficial to delay the start of some activities.
-		\end{itemize}
-	\subsection{Y Networks}
-\section{Properties of the Sample Average Approximation Problem} \label{sec:consistency}
-	\subsection{Cheat?}
-	\subsection{Consistency and Convergence Results}
-	\subsection{IID vs. Stratified Sampling}
-
-	\subsection{Deterministic Counterparts}
-		List the test results of INFORMS presentation. State the fact that the fully stochastic makes great improvement over its deterministic counterparts.
-
-%\section{Stochastic Mixed Integer Program Extension}
-\end{comment}
+
+	\subsection{Pruning Partitions Using Bound Tightening} \label{subsec:FBBT}
+	Feasibility-based and optimization-based bound tightening has been proved powerful in mixed integer nonlinear programming to improve computational performance~\cite{belotti2012fbbt,coffrin2015strengthening,sundar2018OBBT}.
+Feasibility-based bound tightening (FBBT) process is suitable to our problem because the precedence relationships put limits on some activities that they cannot start before a certain time.
+For each activity \(i \in I\), we solve the following linear programs to identify the lower bound and the upper bound of the starting time of each activity.
+	\begin{subequations} \label{prob:btminmax}
+		\begin{align}
+		\min/\max \quad & t_i \\
+		\text{s.t.} \quad & \eqref{cons:MSep} - \eqref{cons:Mxbounds}\\
+		& \underbar{t}_i \leq t_i \leq \bar{t}_i \qquad \forall i \in I.
+		\end{align}
+	\end{subequations}
+	The bound tightening process starts with a set of initial bounds \(\underbar{t}_i = 0\) and \(\bar{t}_i = T_{\max}\) for each \(i \in I\).
+We solve model~\eqref{prob:btminmax} iteratively and update \(\bar{t}_i\) and \(\underbar{t}_i\) until the bounds converge respectively.\\
+	\newline
+	We run FBBT at the beginning of our decomposition method to provide the initial partition \(\mathcal{P}^0\) to start Algorithm~\ref{alg:Cut}.
+If we can tighten the bounds of some activities, for example, by branch-and-bound or heuristics, we can run FBBT to tighten the bounds for all activities, which leads to a tighter formulation of the subproblems, \(S^{\omega}_{\mathcal{P}}\).
+\\
+
+	\subsection{Obtaining Heuristic Upper Bound} \label{subsec:HUB}
+	We observe that it takes many iterations in Algorithm~\ref{alg:Cut} to find a good feasible solution.
+When there is not a tight upper bound as cutoff value, it takes longer to solve model \(\mathcal{M}_{\mathcal{P}}\).
+On the other hand, it is fast to solve model~\eqref{prob:extensive} with a small number of scenarios (e.g., 20 scenarios).
+Solving this small model provides a feasible solution \(\hat{t},\hat{x}\), which can be used to generate an upper bound for the problem with large number of scenarios.
+Therefore, we bootstrap small subsets of scenarios from the original scenario set, i.e., \(\Omega'_n \subset \Omega,\ n = 1,2,\dots\), and solve model~\eqref{prob:extensive} with each of those subsets to generate upper bound evaluations.
+Then we select the smallest to serve as the upper bound for model \(\mathcal{M}_{\mathcal{P}}\).
+\\
+	\newline
+	There are many ways to generate the subsets \(\Omega'_n\).
+We observe that it is beneficial to spread the scenarios within each subset in a similar distribution as the original scenario set.
+We first sort the scenarios so that the scenario with a larger disruption time has a larger index.
+Suppose we want to generate \(N\) subsets with an equal size \(|\Omega'|\) such that \(N \cdot |\Omega'| = |\Omega|\).
+The \(n\)-th subset is indexed by:
+	\[\Omega'_n = \{n + (j - 1) \cdot |\Omega'|,\ j = 1,2,\dots, N\}.\]
+	The upper bound generated using this heuristic is within \(5\%\) of the optimal objective value for every test case.
+\tcb{In Section~\ref{sec:results} we compare the computational time of the decomposition method with and without the initial upper bound and show the significant performance improvement by adding such a heuristic upper bound.}
+
+	\subsection{Magnanti-Wong Type Heuristics on Benders Cuts Generation} \label{subsec:MW}
+	For Benders decomposition with a mixed integer master program, it is observed that the subproblems have multiple optimal dual, which means that at a specific incumbent solution, there are multiple valid cuts to generate.
+Magnanti and Wong~\cite{magnanti1981accelerating} provide a method to select Pareto-optimal cuts.
+Such Pareto-optimal cuts are stronger than ordinary Benders cuts at the relative interior of the feasible region of the master problem.
+It means that the generated Pareto-optimal cuts have a higher value when the integrality is relaxed, which helps tighten the linear programming relaxation of the master program.\\
+	\newline
+	We applies a heuristics that pursues the same goal as Magnanti and Wong~\cite{magnanti1981accelerating} to tighten the cuts at interior points of the feasible region of the master program \((M_\mathcal{P})\).
+We keep a record of all feasible solutions obtained in the past, \(\hat{t}\) and \(\hat{x}\), find the right \(\hat{y}\) for each of them with the current version of partition, and calculate the average of those points to obtain an average point, (\(t^0,x^0,y^0\)).
+We then solve the subproblems following the same procedure as in Magnanti and Wong~\cite{magnanti1981accelerating}, using this average point in the place of the core point.
+For each scenario \(\omega \in \Omega\), first we solve model~\eqref{prob:subTightened} with the current master solution \((\hat{t},\hat{x},\hat{y})\)to obtain the optimal value \(f^*_{\mathcal{P}}(\hat{t},\hat{x},\hat{y})\).
+Suppose the dual problem of \((S^\omega_\mathcal{P})\) can be represented in a simplified form~\eqref{prob:subdual}; \tcb{see Appendix for the expanded version of model~\eqref{prob:subdual}.}
+	\begin{subequations} \label{prob:subdual}
+		\begin{align}
+		\max_{\pi,\lambda,\gamma,\eta} \quad & \pi^\top (\hat{t} + b_t) + \lambda^\top (\hat{x} + b_x) + \gamma^\top (\hat{y} + b_y) + \eta^\top b \\
+		\text{s.t.} \quad & A^\top_{\pi} \pi + A^\top_{\lambda} \lambda + A^\top_{\gamma} \gamma + A^\top_{\eta} \eta \leq c.
+		\end{align}
+	\end{subequations}
+	Given a small error tolerance, \(\epsilon = 10^{-5}\), we solve the maximization problem to obtain enhanced Benders cuts parameters \(\tilde{v}\), \(\pi\), \(\lambda\) and \(\gamma\):
+	\begin{subequations} \label{prob:subMW}
+		\begin{align}
+		\tilde{v} = \max_{\pi,\lambda,\gamma,\eta} \quad & \pi^\top (t^0 + b_t) + \lambda^\top (x^0 + b_x) + \gamma^\top (y^0 + b_y) + \eta^\top b  \\
+		\text{s.t.} \quad & \pi^\top (\hat{t} + b_t) + \lambda^\top (\hat{x} + b_x) + \gamma^\top (\hat{y} + b_y) + \eta^\top b \geq (1 - \epsilon) f^*_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) \\
+		& A^\top_{\pi} \pi + A^\top_{\lambda} \lambda + A^\top_{\gamma} \gamma + A^\top_{\eta} \eta \leq c.
+		\end{align}
+	\end{subequations}
+	\noi Our average point (\(t^0,x^0,y^0\)) may not always be in the relative interior of the master problem feasible region: if for all past solutions there exists an \(i \in I\) and \(q \in \mathcal{Q}_i\) such that \(\hat{y}_i^q = 1\), then \(y_i^{0,q}\) takes a binary value for all \(q \in \mathcal{Q}_i\), and does not lie in the relative interior of the master problem feasible region.
+Although it means our generated cuts may not be Pareto-optimal, they help improve the computational performance, as shown in Table~\ref{table:heuristics} in Section~\ref{sec:results}.
+
+	\subsection{Combining Partitioning with Branch-and-Bound} \label{subsec:bbpartition}
+	The decomposition method using partitions (Algorithm 1) can be further enhanced by a branch-and-bound process, which helps reduce the number of binary variables added to the master and enables solving simpler MIPs in parallel.
+The branch-and-bound tree consists of nodes, each corresponding to model~\eqref{prob:masterTightened} with different partitions.
+The root node starts with the initial partition.
+For each node, we perform the Benders' decomposition process with the master problem \((\mathcal{M}_{\mathcal{P}})\) subproblems, \((S_{\mathcal{P}}^\omega),\ \forall \omega \in \Omega\), to generate cuts for the node until it converges.
+The optimal solution of the node provides a lower bound to the original problem~\ref{prob:extensive} since for every \(\omega \in \Omega\), \((S_{\mathcal{P}}^\omega)\) is a relaxation for \((S^\omega)\).
+We solve \((S^\omega)\) for \(\omega \in \Omega\) to obtain an evaluation of the upper bound.
+If the gap between this upper bound and the lower bound smaller than the tolerance, we can mark the current node complete and start processing the next available node in the tree.
+If not, we branch on a scenario \(\hat{\omega}\) with the largest relaxation gap at the optimal solution of the node, \(f^{\hat{\omega}}(\hat{t},\hat{x}) - f^{\hat{\omega}}_{\mathcal{P}}(\hat{t},\hat{x},\hat{y})\), with a specified activity \(\hat{i} \in I\) where subproblem of scenario \(\hat{\omega}\) has a fractional \(G_i\).
+The current node branches out to two children nodes: one with the constraint \(t_{\hat{i}} \leq H^{\hat{\omega}}\) and the other with the constraint \(t_{\hat{i}} \geq H^{\hat{\omega}}\).
+Correspondingly, the partition \(\mathcal{Q}_{\hat{i}}\) will be refined because branching creates a natural partition at \(H^{\hat{\omega}}\), and some \(y_{\hat{i}}^{q}\) for the new partition will be forced to take value 0.\\
+	\newline
+	After this branching process, for each children node, we can still refine the partition on all activities \(i \in I\) similar to the description in Section~\ref{subsec:partition}.
+The children will inherit the parent node's cuts and they will be updated in a similar fashion of inequality~\eqref{cons:updatedcut}.
+Suppose for activity \(i \in I\), the current node \(n\) has a partition \(\mathcal{P}_i^n\) indexed by set \(\mathcal{Q}_i^n\); its parent node \(m\) has a partition \(\mathcal{P}_i^m\) indexed by set \(\mathcal{Q}_i^m\), the cuts inherited from node \(m\) will be updated for node \(n\) as:
+	\begin{align}\label{cons:updatedcutBB}
+	& \theta^\omega \geq v^{\omega,m,\ell} + \sum_{i \in I} \pi_i^{\omega,m,\ell} (t_i - \hat{t}_i^{m,\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,m,\ell} (x_{ij} - \hat{x}_{ij}^{m,\ell}) + \nonumber \\
+	& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{m}_i} \gamma_{i}^{\omega,m,q} \left( \sum_{\tilde{q} \in \Delta^n_i(m,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,m,\ell} \right) \qquad \forall \ell = 1,2, \dots.
+	\end{align}
+	Here \(\Delta^n_i(m,q)\) represents the descendant set of the partition \(\mathcal{P}_i^n\) refined from the \(q\)-th element in the partition \(\mathcal{P}_i^m\).
+The cuts remain valid since the new partitions of the children node are refinements of the parent node partition, even with the branching action.
+The parent node is marked complete once the refining process is done, and we search for the next available node with the smallest lower bound to perform the Benders decomposition on.
+\\
+	\newline
+	There are many rules to select the activity \(\hat{i}\) to branch on.
+In our observation, the biggest contributor to the relaxation gap, \(f^{\hat{\omega}}(\hat{t},\hat{x}) - f^{\hat{\omega}}_{\mathcal{P}}(\hat{t},\hat{x},\hat{y})\), is that variable \(G\) can take fractional value in relaxation problem \(S_{\mathcal{P}}^\omega\).
+Since the magnitude of the disruption, \(d_i^\omega\), is usually large in value to model significant effect of the stochastic disruption, a fractional \(G\) can have a large impact on the separation constraint~\eqref{cons:subSep}.
+When \(d_i^\omega\) has a very large positive value and \(G_i\) is supposed to take value \(1\), the possibility of \(G_i\) being a fractional value close to zero will decrease the separation between activity \(i\) and \(k\) by a large amount, and thus create a large gap between the relaxation problem and the original mixed-integer subproblem.
+Therefore, when we branch on the scenario \(\hat{\omega}\), suppose the subproblem has a solution \(\hat{G}_i\), we select the activity with the maximum violation measure of \(d_i^{\hat{\omega}} \hat{G}_i\), \(\rho_i^{\hat{\omega}}\):
+	\begin{align}
+	\rho_i^{\hat{\omega}} = \begin{cases}
+	d_i^{\hat{\omega}} \hat{G}_i & \text{if } t_i < H^{\hat{\omega}}\\
+	d_i^{\hat{\omega}} (1 - \hat{G}_i) & \text{if } t_i > H^{\hat{\omega}}\\
+	\min\{d_i^{\hat{\omega}} \hat{G}_i, d_i^{\hat{\omega}} (1 - \hat{G}_i)\} & \text{otherwise.}
+	\end{cases}
+	\end{align}
+	With all pieces together, we summarize the new algorithm of the partitioning based branch-and-bound decomposition method in Algorithm~\ref{alg:CutBB}.
+We can perform the algorithm steps on each available node in parallel to improve the time performance.
+	\begin{algorithm}
+		\caption{Partitioning Based Branch-and-Bound Decomposition algorithm to solve problem~\eqref{prob:extensive}}
+		\label{alg:CutBB}
+		\begin{algorithmic}[1]
+			\State Initialize with specified tolerance parameters \(\epsilon > 0\) and \(\delta > 0\), a global upper bound \(UB\), and the tree of node \(1\) marked available with the following properties: cut iteration number \(\ell_1 = 1\), lower bound \(LB^1\), initial partition \(\mathcal{P}^1\) with its indexed set \(\mathcal{Q}^1\);
+			\While{there exists an available node such that \(\frac{UB - LB^n}{UB} > \epsilon\)}
+			\State Select the available node \(n\) with smallest \(LB^n\);
+			\State Append the inherited cuts from all ancestors of node \(n\) in the form of inequality~\eqref{cons:updatedcutBB};
+			\Repeat
+			\State Solve master problem \((M_{\mathcal{P}})\) of node \(n\), obtain solution \(\hat{t}^{\ell^n}, \hat{x}^{\ell^n}, \hat{y}^{\ell^n}, \hat{\theta}^{\ell^n}\)
+
+			\hspace{1cm} and optimal value \(z_{\mathcal{P}}^*\);
+			\If{\(z_{\mathcal{P}}^* > LB^n\)}
+			\State Update \(LB^n = z_{\mathcal{P}}^*\);
+			\EndIf
+			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t}^{\ell^n},\hat{x}^{\ell^n})\). 
+			\State Calculate \(z^* = p^0 \hat{t}^{\ell^n}_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^{\ell^n},\hat{x}^{\ell^n})\)
+			\If{\(z^* < UB\)} 
+			\State Update \(UB := z^*\) and record the best incumbent solution as \(t^* = \hat{t}^{\ell^n}, x^* = \hat{x}^{\ell^n}\)
+
+			\hspace{1.7cm} and \(y^* = \hat{y}^{\ell^n}\);
+			\EndIf
+			\State For each \(\omega \in \Omega\), solve problem \((S_{\mathcal{P}}^\omega)\) given \(\hat{t}^{\ell^n}, \hat{x}^{\ell^n}, \hat{y}^{\ell^n}, \hat{\theta}^{\ell^n}\)
+
+			\hspace{1cm} obtain optimal value \(v^{\omega,\ell^n}\) and coefficients \(\pi^{\omega,\ell^n}, \lambda^{\omega,\ell^n}, \gamma^{\omega,\ell^n}\);
+			\State Add the cuts of form~\eqref{cons:cut} to the master problem;
+			\State Update \(\ell^n = \ell^n + 1\);
+			\Until{\(z^*_{\mathcal{P}} \geq z^* - \delta\)}
+			\If{\(\frac{UB - LB^n}{UB} > \epsilon\)}
+			\State Branch the node to generate two children nodes \(n_1\) and \(n_2\);
+			\State Refine the partition for nodes \(n_1\) and \(n_2\) to obtain \(\mathcal{P}^{n_1}\) and \(\mathcal{P}^{n_2}\), respectively;
+			\State Let \(LB^{n_1} = LB^{n_2} = LB^n\);
+			\Else
+			\State Mark node \(n\) complete;
+			\EndIf
+			\vspace{0.1cm}
+			\EndWhile{\textbf{end while}}
+			\State Output \(UB\) as the optimal value of model~\eqref{prob:extensive}, and \(t^*, x^*\) as the optimal solution.
+		\end{algorithmic}
+	\end{algorithm}
+
+	\subsection{Numerical Example of the Partitioning Based Branch-and-Bound Decomposition Method}
+	In this section, we use an example to illustrate the process of the partitioning based branch-and-bound decomposition method.
+Since the size of this example is small, we choose to solve the problem to optimality, i.e., \(\epsilon = 0\).
+Suppose we have a serial network with five activities, \(i \in I = \{1,2,3,4,5\}\) in Figure~\ref{fig:fiveAct}.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.8\textwidth]{fiveAct}
+		\caption{A five-activity serial network to illustrate Algorithm~\ref{alg:CutBB}}
+		\label{fig:fiveAct}
+	\end{figure}
+	\noi Each activity has a duration \(D_i = 1,\ \forall i \in I\), and each activity can be crashed with an option that will decrease the duration by 90\% with one unit of resource consumption, i.e., \(e_{i1} = 0.9,\ \forall i \in I\).
+The total resource budget \(B = 2\).
+The probability of no disruption is \(p_0 = 0.2\), and the disruption can occur at four discrete time points: \(H^1 = 1,\ H^2 = 2,\ H^3 = 3,\ H^4 = 4\) with equal probability \(p^\omega = 0.2,\ \forall \omega \in \Omega = \{1,2,3,4\}\).
+The duration increase by \(d_i^\omega = 10,\ \forall i \in I, \omega \in \Omega\).
+From this setup, we can bound the starting time of activity from above by \(T_{\max} = 9\).
+\\
+	\newline
+	We first tighten the bound of starting time for each activity. Then we can start Algorithm~\ref{alg:CutBB} with the initial node \(1\). The partition of the initial node is:
+	\begin{align*}
+	&\mathcal{P}_1^1 = \{(0,9)\} \qquad \qquad \;\; \mathcal{Q}_1^1 = \{1\}\\
+	&\mathcal{P}_2^1 = \{(0,9)\} \qquad \qquad \;\; \mathcal{Q}_2^1 = \{1\}\\
+	&\mathcal{P}_3^1 = \{(0,9)\} \qquad \qquad \;\; \mathcal{Q}_3^1 = \{1\}\\
+	&\mathcal{P}_4^1 = \{(0,1),(1,9)\} \qquad  \mathcal{Q}_4^1 = \{1,2\} \qquad y_4^1 = 0\\
+	&\mathcal{P}_5^1 = \{(0,2),(2,9)\} \qquad  \mathcal{Q}_5^1 = \{1,2\} \qquad y_5^1 = 0\\
+	&\mathcal{P}_T^1 = \{(0,3),(3,9)\} \qquad  \mathcal{Q}_T^1 = \{1,2\} \qquad y_T^1 = 0.
+	\end{align*}
+	We can perform the Benders decomposition on node \(1\).
+The process converges to an optimal value \(z^*_{\mathcal{P}} = 4.072\).
+In the process, we update the upper bound with the best \(z^*\) found in the process, as \(UB = 6.607\).
+The optimal solution is:
+	\begin{align*}
+	& \hat{t}_1 = 0 \qquad \qquad \hat{x}_{11} = 0\\
+	& \hat{t}_2 = 1 \qquad \qquad \hat{x}_{21} = 0.1124\\
+	& \hat{t}_3 = 1.899 \qquad \; \hat{x}_{31} = 0.1124\\
+	& \hat{t}_4 = 2.798 \qquad \; \hat{x}_{41} = 0.8860\\
+	& \hat{t}_5 = 2.997 \qquad \; \hat{x}_{51} = 0.8892\\
+	& \hat{t}_T = 3.2.
+	\end{align*}
+	At this solution, the largest relaxation gap is incurred at \(\hat{\omega} = 1\) with the value \(f^{\hat{\omega}}(\hat{t},\hat{x}) - f^{\hat{\omega}}_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = 8.75\).
+The optimal solution to the subproblem \(S^1_\mathcal{P}\) has a fractional solution \(G_3 = 0.125\).
+Since the optimality gap at node 1 is larger than 0, we branch on scenario \(1\) and activity \(3\), creating two children nodes, node \(2\) and node \(3\).
+Node 2 has an additional constraint, \(t_3 \geq H^1 = 1\) and node 3 has an additional constraint \(t_3 \leq H^1 = 1\).
+For each activity \(i \in I\), we refine the partition by selecting the scenario with the largest nonzero \(\rho_i^\omega\) for \(\omega \in \Omega\).
+If for an activity \(i \in I\), there is no scenario with positive \(\rho_i^\omega\), we do not refine the partition for such activity.
+As stated in Section~\ref{subsec:FBBT}, we can solve a series of linear programs~\eqref{prob:btminmax} to tighten the bounds of starting times for node 2 and node 3, respectively with their additional constraint \(t_3 \geq 1\) and \(t_3 \leq 1\).
+After refinement and bound tightening, we obtain the partition for node 2 and node 3 as follows:
+	\begin{align*}
+	& \text{Node 2:}\\
+	&\mathcal{P}_1^2 = \{(0,9)\} \qquad \qquad \qquad \quad \mathcal{Q}_1^2 = \{1\}\\
+	&\mathcal{P}_2^2 = \{(0,9)\} \qquad \qquad \qquad \quad \mathcal{Q}_2^2 = \{1\}\\
+	&\mathcal{P}_3^2 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_3^2 = \{1,2\} \qquad \quad  y_3^1 = 0\\
+	&\mathcal{P}_4^2 = \{(0,1),(1,2),(2,9)\} \qquad  \mathcal{Q}_4^2 = \{1,2,3\} \qquad y_4^1 = 0\\
+	&\mathcal{P}_5^2 = \{(0,2),(2,3),(3,9)\} \qquad  \mathcal{Q}_5^2 = \{1,2,3\} \qquad y_5^1 = 0\\
+	&\mathcal{P}_T^2 = \{(0,3),(3,4),(4,9)\} \qquad  \mathcal{Q}_T^2 = \{1,2,3\} \qquad y_T^1 = 0.
+	\end{align*}
+	\begin{align*}
+	& \text{Node 3:}\\
+	&\mathcal{P}_1^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_1^3 = \{1,2\} \qquad \quad y_1^2 = 0\\
+	&\mathcal{P}_2^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_2^3 = \{1,2\} \qquad \quad y_2^2 = 0\\
+	&\mathcal{P}_3^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_3^3 = \{1,2\} \qquad \quad y_3^2 = 0\\
+	&\mathcal{P}_4^3 = \{(0,1),(1,2),(2,9)\} \qquad  \mathcal{Q}_4^3 = \{1,2,3\} \qquad y_4^1 = 0\\
+	&\mathcal{P}_5^3 = \{(0,2),(2,3),(3,9)\} \qquad  \mathcal{Q}_5^3 = \{1,2,3\} \qquad y_5^1 = 0\\
+	&\mathcal{P}_T^3 = \{(0,3),(3,4),(4,9)\} \qquad  \mathcal{Q}_T^3 = \{1,2,3\} \qquad y_T^1 = 0.
+	\end{align*}
+	We mark node 1 as complete and move on to node 2, which is the available node with the smallest lower bound.
+Processing node 2 with Benders decomposition yields an optimal solution of 6.1111.
+The node 2 branches to node 4 and 5, which inherit the cuts and the lower bound from node 2.
+\\
+	\newline
+	The next available node with the smallest lower bound is node 3. Node 3 yields an optimal value of 6 and an optimal solution as: 
+	\begin{align*}
+	& \hat{t}_1 = 0 \qquad \qquad \hat{x}_{11} = 1\\
+	& \hat{t}_2 = 0.1 \qquad \quad\; \hat{x}_{21} = \frac{1}{9}\\
+	& \hat{t}_3 = 1 \qquad \qquad \hat{x}_{31} = 0\\
+	& \hat{t}_4 = 2 \qquad \qquad \hat{x}_{41} = 0\\
+	& \hat{t}_5 = 3 \qquad \qquad \hat{x}_{51} = \frac{8}{9}\\
+	& \hat{t}_T = 3.2.
+	\end{align*}
+	The relaxation gap is zero, which means that the upper bound is updated to \(UB = 6\) as well.
+This leads to a zero optimality gap at node 3.
+For node 4 and node 5, since their lower bounds are larger than the current upper bound, they will not be processed by the algorithm.
+The algorithm terminates with the best solution as \(\hat{t}\) and \(\hat{x}\), and the optimal objective value is 6.
 
@@
 	%			\item Case 55 from Elmgrabhy
-	%			\item Randomized network 75, 100 nodes
+	%			\item Randomized network 35, 75 nodes
 	%			\item Plambeck paper: Case 110
@@
 Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value.
-We use an activity network from Plambeck et al.~\cite{plambeck1996sample} with 11 activities, % and the other with 110 activities.
-	one from Elmgrabhy \cite{Elmaghraby77} with 19 activities, and 
-	 %and the other with 55 activities. 
-	 we also manually create one activity network with 14 activities. 
-	 %and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}. 
+We use an activity network from Plambeck et al.~\cite{plambeck1996sample} with 11 activities, one from Elmgrabhy~\cite{Elmaghraby77} with 19 activities, and we manually create one activity network with 14 activities and randomly generate one network with 35 activities using the tool \emph{RanGen}~\citep{demeulemeester2003rangen}.
 In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities.\\
@@
 To generate those five solutions, we use a sample of size \(500\).
-We can obtain a point estimation for the upper bound by plugging each of these solutions in the SAA problem with the original \(500\) samples, and we call this estimation as ``in-sample" since these samples are also used to obtain solutions.
-We also sample 20 batches of samples of \(|\Omega| = 5000\), and obtain another upper bound estimation, and its confidence interval, by plugging each of those solutions in every batch of the sample.
+We can obtain a point estimation for the upper bound by plugging each of these solutions in the SAA problem with the original \(500\) samples, and we call this estimation, \(z^*\), as ``in-sample" since these samples are also used to obtain solutions.
+We also sample 20 batches of samples of \(|\Omega| = 5000\), and obtain the confidence interval of the upper bound estimation, \(\bar{z}\), by testing the solution on these batches.
 We present the comparison of different solutions of Case 11 in Figure~\ref{fig:value}.
@@
 		\centering
-		\includegraphics[width=0.8\textwidth]{case11_altValues}
+		\includegraphics[width=0.8\textwidth]{graphValues}
 		\caption{Comparison of quality of alternative solutions to the problem~\eqref{prob:extensive}}
@@
 	\end{figure}
-	Figure~\ref{fig:value} shows that the solution quality is poor without considering the uncertainty of disruption timing.
+	\noi Figure~\ref{fig:value} shows that the solution quality is poor without considering the uncertainty of disruption timing.
 When we assume the disruption timing is uncertain, the computational effort required to obtain ``\(H\)Only" solution and the fully stochastic solution is on the same level, since we need to include the same number of binary variables.
-To further test whether having a fully stochastic model is the best, we run a pair-wise \(t\)-test.
-The null hypothesis is that whether the difference between the upper bound generated by one alternative solution and that generated by the fully stochastic solution is less than 0.
-The result of the \(t\)-test is displayed in Table~\ref{table:value}.
 	\begin{table}[H]
 		\centering
-		\begin{tabular}{c c c c c c}
+		\begin{tabular}{ c | l l | l l | l l | l l | l l}
 			\hline
-			& Det & Exp & dOnly & HOnly & Full\\
-			In-sample obj & 118.35 & 112.33 & 114.91 & 98.82 & 98.82 \\
-			Out-of-sample obj mean & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 \\
-			t-test result (p-value) & \(< 10^{-5}\) & \(< 10^{-5}\)& \(< 10^{-5}\)&  \(0.001945\)& -\\
+			& \multicolumn{2}{c |}{Deterministic} & \multicolumn{2}{c |}{Expected} & \multicolumn{2}{c |}{dOnly} & \multicolumn{2}{c |}{HOnly} & \multicolumn{2}{c}{Full}\\
+			& \(z^*\) & CI of \(\bar{z}\) & \(z^*\) & CI of  \(\bar{z}\) & \(z^*\) & CI of \(\bar{z}\) & \(z^*\) & CI of \(\bar{z}\) & \(z^*\) & CI of \(\bar{z}\) \\ \hline
+			Case 11 & 118.35 & 112.33 & 114.91 & 98.82 & 98.82 \\
+			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 \\
+			Case 19 & & & &  & -\\
+			Case 35 & & & &  & -\\
 			\hline
@@
 	\end{table}
+	To further test whether having a fully stochastic model is the best, we run a pair-wise \(t\)-test.
+The null hypothesis is that whether the difference between the upper bound generated by one alternative solution and that generated by the fully stochastic solution is less than 0.
 The pair-wise \(t\)-test rejects all null hypotheses, which shows that the difference between an alternative solution is significantly larger than the fully stochastic solution.
@@
 We can also obtain the \(95\%\) confidence interval of the lower bound and the upper bound estimation for each sample size.
-We present the result for Case 19 in Figure~\ref{fig:budget}.
-	\begin{figure}[H]
+We present the upper bound results in Table~\ref{table:budgetU}, the lower bound results in Table~\ref{table:budgetL} and present visualization of the results with Figure~\ref{fig:budget}.
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{ c | l l l l l l l l}
+			\hline
+			& 10 & 20 & 50 & 100 & 200 & 500 & 1000 & 2000 \\ \hline
+			Case 11& 118.35 & 112.33 & 114.91 & 98.82 & 98.82 & & \\
+			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 & &  \\
+			Case 19 & & & &  & - & & \\
+			\hline
+		\end{tabular}
+		\caption{Upper bound confidence interval for solutions generated by different budgets.}
+		\label{table:budgetU}
+	\end{table}
+
+	\begin{table}[H]
+		\centering
+		\begin{tabular}{ c | l l l l l l l l}
+			\hline
+			& 10 & 20 & 50 & 100 & 200 & 500 & 1000 & 2000 \\ \hline
+			Case 11& 118.35 & 112.33 & 114.91 & 98.82 & 98.82 & &  \\
+			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 & &  \\
+			Case 19 & & & &  & - & & \\
+			\hline
+		\end{tabular}
+		\caption{Lower bound estimation for solutions generated by different sample sizes.}
+		\label{table:budgetL}
+	\end{table}
+
+	\begin{figure}
 		\centering
 		\includegraphics[width=0.8\textwidth]{case19_budget_ublb}
-		\caption{Confidence intervals of the lower/upper bound estimation for sample size \(|\Omega| \in \{10, 50, 75, 100, 200, 300, 400, 500\}\)}
+		\caption{Confidence intervals of the lower/upper bound estimation for different sample sizes.}
 		\label{fig:budget}
@@
 	In this section we present the computational result of our decomposition method.
-	%We solve each of the test cases with different sizes of samples \(|\Omega| \in \{100,200,300,400,500,1000\}\) (\(20\) times for each sample size) and show the mean computational time. 
-	We can see the benefit of our decomposition method in Figure~\ref{fig:time}, with the example of Case 11.
+\tcb{We first show the effectiveness of finding a heuristic upper bound and generating Magnanti-Wong heuristic cuts.
+For all test cases, we use a sample size \(|\Omega| = 500\).
+In Table~\ref{table:heuristics}, ``UB" means that we only use heuristic upper bound in Section~\ref{subsec:HUB} and generate regular Benders cuts, and ``MW" means that we generate Magnanti-Wong heuristic cuts in Section~\ref{subsec:MW} without a prespecified initial upper bound.
+We also test the time performance of using neither and using both heuristics.}
+	\begin{table}[H]
+		\centering		
+		\begin{tabular}{ c | l l l l }
+			\hline
+			& Case 11 & Case 14 & Case 19 & Case 35 \\ \hline
+			Neither & & & &  \\
+			UB & & & & \\
+			MW & & & & \\
+			Both & & & & \\
+			\hline
+		\end{tabular}
+		\caption{Computational improvement by utilizing heuristic upper bound generation and Magnanti-Wong heuristic cuts.}
+		\label{table:heuristics}
+	\end{table}
+	\noi Next we show the comparison of time running Algorithm~\ref{alg:Cut}, Algorithm~\ref{alg:CutBB}, and directly solving the extensive formulation~\eqref{prob:extensive} using Gurobi.
 In each master iteration, we solve a master problem with a small number of binary variables.
 Although we need to solve multiple rounds of the master problem and the number of binary variables is increasing since the partition is refined in every iteration, we still can observe a significant improvement by using our proposed decomposition method, especially when the sample size is large.
+	\begin{table}[H]
+		\centering		
+		\begin{tabular}{ c | l l l l l l l l l l l l }
+			\hline
+			&10 & 20 & 50 & 100 & 200 & 300 & 400 & 500 & 750 & 1000 & 1500 & 2000 \\ \hline
+			Case 11& 118.35 & 112.33 & 114.91 & 98.82 & 98.82 \\
+			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 \\
+			Case 19 & & & &  & -\\
+			\hline
+		\end{tabular}
+		\caption{Computational performance for different sample sizes.}
+		\label{table:time}
+	\end{table}
 	\begin{figure}[H]
@@
 		\includegraphics[width=0.8\textwidth]{case11_time}
-		\caption{Computational performance for sample size \(|\Omega| \in \{100, 200, 300, 400, 500,1000\}\)}
+		\caption{Computational performance for different sample sizes.}
+		% \(|\Omega| \in \{100, 200, 300, 400, 500,1000\}\
 		\label{fig:time}

### 2019-05-30 src/partSolve_BB_shared_noMW.jl

@@ -1,0 +1,765 @@
+function recoverpInfo(II,D,eff,b,K,p0,B)
+    IIList = [i for i in II];
+    Ddict = Dict();
+    for i in 1:length(IIList)
+        Ddict[IIList[i]] = D[i];
+    end
+    KList = [(K[k,1],K[k,2]) for k in 1:size(K)[1]];
+    Succ = Dict();
+    Pre = Dict();
+    for i in IIList
+        Succ[i] = [];
+        Pre[i] = [];
+    end
+    for k in 1:size(K)[1]
+        push!(Succ[K[k,1]],K[k,2]);
+        push!(Pre[K[k,2]],K[k,1]);
+    end
+    bdict = Dict();
+    effdict = Dict();
+    Ji = Dict();
+    Jmax = size(eff)[2];
+    for i in 1:length(IIList)
+        Ji[IIList[i]] = [j for j in 1:Jmax if eff[i,j] != 0];
+        bdict[IIList[i]] = [b[i,j] for j in 1:Jmax if b[i,j] != 0];
+        effdict[IIList[i]] = [eff[i,j] for j in 1:Jmax if eff[i,j] != 0];
+    end
+    pd = pInfo(IIList, Ji, Ddict, bdict, effdict, B, p0, KList, Pre, Succ)
+    return pd;
+end
+
+function recoverdInfo(II,HOriShare,disdShare,disPrShare,Tmax)
+    Ω = [];
+    disData = Dict();
+    for ω in 1:length(HOriShare)
+        push!(Ω,ω);
+        d = Dict();
+        for i in 1:length(II)
+            d[II[i]] = disdShare[i,ω];
+        end
+        disData[ω] = disInfo(HOriShare[ω],d,disPrShare[ω]);
+    end
+    H = Dict();
+    H[0] = 0;
+    # remove the duplicate ones
+    counter = 1;
+    for ω in Ω
+        if !(disData[ω].H in values(H))
+            H[counter] = disData[ω].H;
+            counter += 1;
+        end
+    end
+    H[counter] = Tmax;
+    HRev = Dict();
+    for hIter in keys(H)
+        HRev[H[hIter]] = hIter;
+    end
+    return disData,H,Ω,HRev;
+end
+
+function recoverdis(IIShare,distanceShare)
+    allSucc = Dict();
+    distanceDict = Dict();
+    for i in IIShare
+        allSucc[i] = [];
+    end
+    for i in 1:size(distanceShare)[1]
[…]

### 2019-05-30 src/partSolve_Callback_tightened_sol.jl

@@ -1,384 +1,419 @@
 # calculate the largest possible starting time for each activity in any disrupted scenario
-Tmax = disData[length(Ω)].H + longestPath(pData)[0];
-pdData = deepcopy(pData);
-for i in pData.II
-    if i != 0
-        pdData.D[i] = pData.D[i] + maximum([disData[ω].d[i] for ω in Ω])
-    else
-        pdData.D[i] = pData.D[i];
-    end
-end
-lDict = longestPath(pdData);
-for i in pData.II
-    lDict[i] += disData[length(Ω)].H;
-end
-Tmax1 = lDict[0];
-
-allSucc = findSuccAll(pData);
-distanceDict = Dict();
-for i in pData.II
-    for j in allSucc[i]
-        distanceDict[i,j] = detCal(pData,i,j);
-    end
-end
-
-H = Dict();
-H[0] = 0;
-# remove the duplicate ones
-counter = 1;
-for ω in Ω
-    if !(disData[ω].H in values(H))
-        H[counter] = disData[ω].H;
-        counter += 1;
-    end
-end
-H[counter] = Tmax;
-HΩ = 1:(counter - 1);
-HRev = Dict();
-for hIter in keys(H)
-    HRev[H[hIter]] = hIter;
-end
-
-# start with an upper bound based on the smaller stochastic solution
-ubextList,tHList,ubInc,tbest,xbest,θbest,textList,xextList = iniPart(pData,disData,Ω,sN,MM,1,noThreads);
-lbCost = -Inf;
-lbCostList = [];
-global ubCost = ubInc;
-
-tcoreList = deepcopy(textList);
-xcoreList = deepcopy(xextList);
-ubcoreList = deepcopy(ubextList);
-ycoreList = [];
-errorList = [];
-GList = [];
-
-brInfo = precludeRelNew(pData,H,ubCost);
-
-# initialize cutSet and divSet
-cutSet = [];
-divSet = Dict();
-divDet = Dict();
-for i in pData.II
-    set1 = [h for h in HΩ if brInfo[findfirst(pData.II,i),h] == 1];
-    setn1 = [h for h in HΩ if brInfo[findfirst(pData.II,i),h] == -1];
-
-    if set1 != []
-        set1t = partType(0,maximum(set1));
-        if setn1 != []
-            setn1t = partType(minimum(setn1),length(HΩ) + 1);
-            set0t = partType(maximum(set1),minimum(setn1));
[…]

### 2019-05-30 src/test_value.jl

@@ -97,7 +97,7 @@ for fileInd in 1:length(pathList)
         end
     end
     #tHOnly,xHOnly,fHOnly,gHOnly,mHOnly = extForm_cheat(pData,disData,Ω,1e-2,999999,noThreads);
-    tHOnly,xHOnly,ubHOnly,lbHOnly,timeIter,treeList,timeHOnly = partSolve_BB_para_share(pData,disData,Ω,sN,MM,noThreads,5,1,1e-2,5,1000);
+    tHOnly,xHOnly,ubHOnly,lbHOnly,timeIter,treeList,timeHOnly = partSolve_BB_para_share(pData,disData,Ω,sN,MM,noThreads,5,1,1e-2,5,2000);
     gapHOnly = (ubHOnly - lbHOnly)/ubHOnly;
     fHOnly = ubHOnly;
     disData = deepcopy(disData1);
@@ -107,7 +107,7 @@ for fileInd in 1:length(pathList)
 
     # full solution
     #tFull,xFull,fFull,gFull,mFull = extForm_cheat(pData,disData,Ω,1e-2,999999,noThreads);
-    tFull,xFull,ubFull,lbFull,timeIter,treeList,timeFull = partSolve_BB_para_share(pData,disData,Ω,sN,MM,noThreads,5,1,1e-2,5,1000);
+    tFull,xFull,ubFull,lbFull,timeIter,treeList,timeFull = partSolve_BB_para_share(pData,disData,Ω,sN,MM,noThreads,5,1,1e-2,5,2000);
     gapFull = (ubFull - lbFull)/ubFull;
     fFull = lbFull;
     push!(dDict[fileInd],[tFull,xFull,fFull,ubFull,gapFull,timeFull]);
@@ -128,3 +128,17 @@ for fileInd in 1:length(pathList)
         save("test_Ext_value.jld","dDict",dDict,"ubDict",ubDict);
     end
 end
+
+################################################################################################
+# plot the result
+
+graphOutput = zeros(4,5);
+stdOutput = zeros(4,5);
+for i in 1:4
+    # cases
+    for j in 1:5
+        graphOutput[i,j] = mean([ubDict[i][k][j] for k in 1:20]);
+        stdOutput[i,j] = std([ubDict[i][k][j] for k in 1:20])*1.96;
+    end
+end
+writedlm("value_figure.csv",graphOutput,',');

### 2019-07-10 Writeup/PERT_Paper_Draft3.tex
Save current state

@@
 \usepackage{color}
+\usepackage{scalefnt}
 \usepackage{amssymb}
@@
 \usepackage[square,sort,comma,numbers]{natbib}
+\bibpunct[, ]{(}{)}{,}{a}{}{,}%
+\def\bibhang{24pt}%
+\def\newblock{\ }%
+\def\BIBand{and}
 \usepackage{url}
@@
 \newcommand{\cN}{{\cal N}}
-\newcommand{\cO}{{\cal O}}
+\newcommand{\cQ}{{\cal Q}}
 \newcommand{\txi}{{\xi}}
@@
 \newcommand{\cP}{{\cal P}}
-\newcommand{\tcb}{\textcolor{blue}}
+\newcommand{\cH}{{\cal H}}
+\newcommand{\thead}{\multicolumn{1}{c |}}
 \newcommand{\underv}{\mbox{$\underbar{$v$}$}}
-\newcommand*{\thead}[1]{\multicolumn{1}{c}}
 \allowdisplaybreaks
@@
 \renewcommand{\underbar}{\underaccent{\bar}}
+\newcommand{\tcr}{\textcolor{red}}
+\newcommand{\tcb}{\textcolor{blue}}
 
@@
 	\section{Introduction} \label{sec:introduction}
-		The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \citep{kelley1961criticalpath}; see \citet{soderlund2004building} for an overview.
+	The management of complex projects through optimization has a rich history in operations research, beginning with the critical path method of \cite{kelley1961criticalpath}; see \citet{soderlund2004building} for an overview.
 A project is a collection of activities, between which there are precedence relationships due to logical or technological considerations.
 A precedence relationship is usually reflected as the start time of one activity following the completion of another.
+	%a required separation time between the start time of two activities. 
 	Typically, multiple activities can be processed at the same time, and there is no limit on how many activities can be processed simultaneously, as long as the precedence requirements are satisfied.
@@
 	{Nomenclature:}
+	%The notation for the model is displayed as follows:
 	\begin{longtable}[H]{ l l l l }
@@
 		\begin{align}
-			\min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\
+		z^* = \min \quad & p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega \\
 		\text{s.t.} \quad & t_k - t_i \geq D_{ik} \left ( 1 - \sum_{j \in J_i} e_{ij} x_{ij} \right ) \qquad \qquad \forall \, (i,k) \in \cA \label{cons:Sep}\\
@@
 		& 0 \leq z_{ij}^\omega \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \omega \in \Omega\\
-			& G_i^\omega \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega.
+		& G_i^\omega \in \{0,1\}. \qquad \qquad \forall \,i \in I, \omega \in \Omega. \label{cons:Gbounds}
 		\end{align}
@@
 	\section{NP-Hardness} \label{sec:nphard}
-		In this section, we prove that the project crashing optimization problem under a stochastic disruption is NP-hard.
-The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (\verb|DTCT|) problem.
+	We show that the optimal project crashing problem under a stochastic disruption is NP-hard even with a single disruption scenario, which occurs with probability one at time zero.
+	%The proof process is largely based on the proof of De et al.~1997 for the discrete time-cost tradeoff (\verb|DTCT|) problem.
 In De et al.~\cite{de1997complexity}, the authors show that an exactly-one-in-three \verb|3SAT| (\verb|EOIT_3SAT|) problem can be transformed to an instance of the \verb|DTCT| decision problem in polynomial time.
 Since \verb|EOIT_3SAT| is NP-complete (see \cite{Garey1979ComputersAI} for the detailed proof), the authors prove that the \verb|DTCT| decision problem is also NP-complete, and the \verb|DTCT| optimization problem is NP-hard.\\
-		\newline
-		Similar to De et al.~\cite{de1997complexity}, we also first introduce the \verb|EOIT_3SAT| problem: let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables.
-A literal can be either \(u\) or \(\bar{u} = \neg u\) for a \(u \in U\).
-Let \(C = \{c_1, c_2, \dots, c_m\}\) be a set of clauses, each of which is formed by a disjunction of three literals.
-The \verb|EOIT_3SAT| problem asks for whether there is a truth assignment for \(U\) such that each clause in \(C\) has exactly one true literal.
-\\
-		\newline
-		Based on the above instance of \verb|EOIT_3SAT|, we formulate an instance of the activity network for the project crashing problem.
-The activity network consists of three layers of nodes: the first layer contains \(3n\) nodes and represents the truth assignment of each variable; the second layer contains \(3m\) nodes and represents the value of clauses; the third layer contains node \(T\) which represents the end of the project.
-The first layer has \(n\) components in parallel, each of which corresponds to a variable and contains 3 nodes connected, denoted as \(u_{j1},\ u_{j2}\) and \(u_{j3}\) for the component \(j\), as shown in Figure~\ref{fig:layer1}.
-Figure~\ref{fig:layer1} also displays how the first layer connects to the third layer.
-We set the scenario set as a singleton \(\Omega = \{1\}\) and set the disruption time as \(H^1 = 0\) with probability \(p^1 = 1\).
-We set parameter values associated with the arcs in Figure~\ref{fig:layer1} as:
-		\begin{align*}
+	%	\newline
+	%Similar to De et al.~\cite{de1997complexity}, 
+	Our proof relies on a transformation from the exactly-one-in-three \verb|3SAT| (\verb|EOIT_3SAT|) problem: Let \(U = \{u_1,u_2, \dots, u_n\}\) be a set of variables.
+A literal can be either \(u\) or \(\bar{u} = \neg u\) for \(u \in U\).
+Let \(C = \{c_1, c_2, \dots, c_m\}\) be a set of clauses, each of which is formed by a disjunction of three literals, e.g., \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\).
+The \verb|EOIT_3SAT| problem asks whether there is a truth assignment for each \(u \in U\) such that each clause in \(C\) has exactly one true literal.
+\citet{de1997complexity} use \verb|EOIT_3SAT| to prove that an activity network problem, in which there are a finite set of alternatives for each activity with different duration and cost, is NP-hard, and we use similar proof constructs.
+\\
+	\newline
+	Starting with an instance of \verb|EOIT_3SAT|, we formulate an activity network using three layers of nodes.
+The first layer contains \(3n\) nodes and represents the truth assignment of each variable in \verb|EOIT_3SAT|.
+The second layer contains \(3m\) nodes and represents the value of \verb|EOIT_3SAT|'s clauses.
+And, the third layer consists of terminal node \(T\), the end of the project.
+Each of the first layer's \(n\) components corresponds to a variable and contains three nodes, denoted \(u_{j1},\ u_{j2}\), and \(u_{j3}\), which are connected as shown in Figure~\ref{fig:layer1}.
+The figure also shows how the first layer connects to the third layer.
+We let \(\Omega = \{1\}\), and \(H^1 = 0\) with probability \(p^1 = 1\).
+We define the parameter values associated with the arcs in Figure~\ref{fig:layer1} as:
+	\begin{subequations}\label{eqn:first_layer}
+		\begin{align}
 		& D_{u_{j1},u_{j2}} = 1 \qquad \quad d^1_{u_{j1},u_{j2}} = 1\\
@@
 		& D_{u_{j3},T} = 0 \qquad \quad \;\; d^1_{u_{j3},T} = 0.
-		\end{align*}
-		We do not allow any activities within the first layer to be crashed, i.e., \(J_{u_{jk}} = \emptyset\), for all \(j = 1,2,\dots, n,\ k = 1,2,3\).
-With this setup, the length of the critical path for the \(j\)-th component is always \(2\) for all \(j = 1,2,\dots,n\), as it is optimal to have activity \(u_{j1}\) start at time \(0\).
-However, whether the critical path traverses activities \(u_{j2}\) (top path) or the activity \(u_{j3}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\).
-If \(G^1_{u_{j1}} = 1\), the \(G\) variables will take value \(1\) for all subsequent nodes.
-The top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} = 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} + d^1_{u_{j1},u_{j3}} = 2 - 1 = 1\), which makes the top path critical.
-If \(G^1_{u_{j1}} = 0\), it is optimal to have activity \(u_{j2}\) start before the disruption as well, i.e., \(G^1_{u_{j2}} = 0\).
-The top path yields a length of \(D_{u_{j1},u_{j2}} = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} = 2\), which makes the bottom path critical.
+		\end{align}
+	\end{subequations}
+	No activities in the first layer can be crashed, i.e., 
+	\begin{equation}\label{eqn:first_layer_crash}	
+	J_{u_{jk}} = \emptyset, \ \mbox{for all} \  j = 1,2,\dots, n,\ k = 1,2,3.
+	\end{equation}	
+	The start node, $S$, connects to each~$u_{j1}$ with zero duration.
+It is optimal to start each activity \(u_{j1}\) at time \(0\) because the inclusive inequalities in constraints~\eqref{cons:G1}-\eqref{cons:G2} still allow us to choose \(G^1_{u_{j1}}  \in \{0,1\}\) for each variable in $U$.
+With this setup, the length of the longer path through the \(j\)-th component is always~\(2\), \(j = 1,2,\dots,n\).
+Whether the longer path traverses activity~\(u_{j2}\) (top path in Figure~\ref{fig:layer1}) or activity~\(u_{j3}\) (bottom path) depends on the value of \(G^1_{u_{j1}}\).
+	%\tcr{If \(G^1_{u_{j1}} = 1\), the \(G\) variables will take value \(1\) for all subsequent nodes on the path from $u_{j1}$ to $T$.} 
+	If \(G^1_{u_{j1}} = 1\) then the top path yields a length of \(D_{u_{j1},u_{j2}} + d^1_{u_{j1},u_{j2}} = 1 + 1 = 2\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} + d^1_{u_{j1},u_{j3}} = 2 - 1 = 1\).
+If \(G^1_{u_{j1}} = 0\)
+	%\tcr{it is optimal to have activity \(u_{j2}\) start before the disruption as well, i.e., \(G^1_{u_{j2}} = 0\)} 
+	then the top path yields a length of \(D_{u_{j1},u_{j2}} = 1\), while the bottom path yields a length of \(D_{u_{j1},u_{j3}} = 2\).
 We can consider the value of \(G^1_{u_{j1}}\) as the truth assignment of variable \(u_j\).
-If the variable \(u_j\) is TRUE, the critical path is the top path; if it is FALSE, the critical path is the bottom path.
+If variable \(u_j\) is TRUE, the top path is longer; if it is FALSE the bottom path is longer.
 	\begin{figure}[H]
 		\centering
-			\includegraphics[width=0.6\textwidth]{layer1}
-			\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\) in the first layer of the constructed activity network for \texttt{EOIT\char`_3SAT}.}
+		\includegraphics[width=0.55\textwidth]{layer1}
+		\caption{A component corresponding to variable \(u_j,\ j = 1,2,\dots, n\), in the first layer of the activity network for \texttt{EOIT\char`_3SAT}}
 		\label{fig:layer1}
 	\end{figure}
-		\noi The arcs from activities \(u_{j2}\) and \(u_{j3}\) in Figure~\ref{fig:layer1} point to activities in the second layer.
-Next, we construct the second layer of activities and the arcs connecting the first layer and the second layer, in a similar manner as Figure 2(b) in~\cite{de1997complexity}.
-To best illustrate the arc construction, we show an example of a clause, \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\), with two original variables, \(u_j\) and \(u_k\), and one negative complement, \(\bar{u}_{\ell}\).
-We can consider the activity \(c_{ip}\) corresponding to the truth assignment of the variable \(u_p\), for \(p \in \{j,k,\ell\}\).
-For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p3}\) with activity \(c_{ip}\), and activity \(u_{p2}\) with activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\).
-For the negative complement variable \(u_\ell\), we connect activity \(u_{\ell 2}\) with activity \(c_{i \ell}\), and activity \(u_{\ell 3}\) with activities \(c_{iq},\ q \in \{j,k\}\).
-This example by no means limits the clauses to two variables and one negative complement but aims to showcase the procedure of constructing the network components corresponding to a variable and the negative complement of a variable.
+	\noi The arcs from activities \(u_{j2}\) and \(u_{j3}\) in Figure~\ref{fig:layer1} point to activities in the second layer, which we now construct, 
+	%in a similar manner as Figure 2(b) in~
+	again following ideas in~\citet{de1997complexity}.
+Consider the clause \(c_i = u_j \vee u_k \vee \bar{u}_{\ell}\), with literals consisting of two original variables, \(u_j\) and \(u_k\), and one complement, \(\bar{u}_{\ell}\).
+We consider an activity, \(c_{ip}\), corresponding to the truth assignment of the variable \(u_p\), for \(p \in \{j,k,\ell\}\).
+For the original variables \(u_p\), \(p \in \{j,k\}\), we connect activity \(u_{p3}\) to activity \(c_{ip}\), and we connect activity \(u_{p2}\) to the other two activities \(c_{iq}\), where \(q \in \{j,k,\ell\}, q \neq p\).
+For the complemented variable~\(\bar{u}_\ell\), we do the opposite, connecting activity \(u_{\ell 2}\) to activity \(c_{i \ell}\), and activity \(u_{\ell 3}\) to activities \(c_{iq},\ q \in \{j,k\}\).
+This
+	%example by no means limits the clauses to two variables and one negative complement but aims to showcase 
+	illustrates the general rule by which a clause with three literals (typically a mix of original and complemented variables) yields the network topology: 
+	\begin{subequations}\label{eqn:layer2}
+		\begin{eqnarray}	
+		&\bullet& \mbox{{\em original variables} result in a connection from $u_{j3}$ to $c_{ij}$ via a single arc and} \nonumber \\
+		&& \mbox{a connection from~$u_{j2}$ to the other two $c_j$-activity nodes; and,}  \\
+		&\bullet& \mbox{{\em complemented variables} result in the opposite.}
+		\end{eqnarray}
+	\end{subequations}
+	%the procedure of constructing the network components corresponding to a variable and the negative complement of a variable. 
 	From now on we refer to the activities representing variables as \(u\)-activities and those representing clauses as \(c\)-activities.\\
 	\newline
-		We let both the nominal duration \(D\) and the disrupted effect \(d\) for the arcs between \(u\)-activities and \(c\)-activities be \(0\). For the arcs between \(c\)-activities and \(T\), we set:
-		%The parameters of arcs in Figure~\ref{fig:layer2} are set as:
-		\begin{align*}
-		& D_{c_{iq},T} = 1 \qquad \quad \;\; d^1_{c_{iq},T} = 0 \;\;\;\quad \forall q \in \{j,k,\ell\}.
-		\end{align*}
-		Unlike the \(u\)-activities, each \(c\)-activity can be crashed with a single option with effectiveness \(e_{c_{ip}1} = 1\), \(\forall p \in \{j,k,\ell\}\).
-The total budget, \(B\), is then set to \(B = 2m\), where \(m\) is the total number of clauses.
-		\begin{figure}[H]
+	We make the following assignments:
+	\begin{subequations}\label{eqn:EOIT_assignments}
+		\begin{eqnarray}
+		&& D_{u_{jp},c_{ij}}=d^1_{u_{jp},c_{ij}}=0 \qquad \forall i=1,\ldots,m, j=1,\ldots,n, p=2,3: u_j \ \mbox{is in clause} \ c_i \label{eqn:u_c_distance} \\
+		&& D_{c_{ij},T}=1 \ \mbox{and} \ d^1_{c_{ij},T}=0 \qquad \forall i=1,\ldots,m, j=1,\ldots,n:  u_j \ \mbox{is in clause} \ c_i  \label{eqn:c_T_distance} \\
+		&&e_{c_{ij},1} = 1 \qquad \forall i=1,\ldots,m, j=1,\ldots,n:  u_j \ \mbox{is in clause} \ c_i \label{eqn:e_unit_effectiveness} \\
+		&& b_{ij}=1 \qquad \forall i=1,\ldots,m, j=1,\ldots,n:  u_j \ \mbox{is in clause} \ c_i \label{eqn:b_unit_cost} \\
+		&& B=2m \label{eqn:budget_is_2m}
+		\end{eqnarray}
+	\end{subequations}
+	The nominal duration and the disrupted duration for the arcs between \(u\)-activities and \(c\)-activities are \(0\) per equation~\eqref{eqn:u_c_distance}.
+The nominal and disrupted durations for the arcs between the \(c\)-activities and \(T\) are specified in equation~\eqref{eqn:c_T_distance}.
+Unlike the \(u\)-activities, each \(c\)-activity can be crashed with a single option with unit effectiveness as given in equation~\eqref{eqn:e_unit_effectiveness}.
+We assign the budget in equation~\eqref{eqn:budget_is_2m}, where \(m\) is the total number of clauses, and assign unit $b_{ij}$ values in equation~\eqref{eqn:b_unit_cost}.
+	\begin{figure}
 		\centering
-			\includegraphics[width=0.5\textwidth]{layer2}
-			\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer.}
+		\includegraphics[width=0.42\textwidth]{layer2}
+		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee \bar{u}_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer}
 		\label{fig:layer2}
 	\end{figure}
-		\noi For simplicity, the reasoning behind this construction is stated using the example in Figure~\ref{fig:layer2}: for variable \(u_j\), if \(G^1_{u_{j1}} = 1\), the activity \(u_{j4}\) can start at time \(1\), while the earliest time the activity \(u_{j3}\) can start is \(2\).
-If \(G^1_{u_{j1}} = 0\), the activity \(u_{j3}\) can start at time \(1\), while the earliest time the activity \(u_{j4}\) can start is \(2\).
-This is the same for variable \(u_k\) but directly opposite for variable \(u_\ell\).
-The truth assignments indicate which path is critical, which is similar in De et al.~\cite{de1997complexity}, where the truth assignments indicate which crashing option to select for variables nodes.
-\\
-		\newline
-		We can prove the following lemmas.
+	\noi We illustrate the logic behind this construction using Figure~\ref{fig:layer2}.
+For variable \(u_j\), if \(G^1_{u_{j1}} = 1\) then the earliest time activity \(u_{j2}\) can start is \(2\), and activity \(u_{j3}\) can start at time \(1\).
+If \(G^1_{u_{j1}} = 0\) then the earliest time activity \(u_{j3}\) can start is \(2\), and activity \(u_{j2}\) can start at time \(1\).
+The same holds for variable \(u_k\), and the opposite for variable \(u_\ell\).
+The truth assignments indicate which path is longer.
+	%\tcr{and which crashing option to select for the \tcr{$c$-activity} nodes}. 
+	\\
+	\newline
+	%	\tcb{We can prove the following lemmas.
 Without loss of generality, a clause can be made of without negative complement of variables.
-For clarity, Figure~\ref{fig:layer2} equivalent for a clause without negative complement is displayed as Figure~\ref{fig:layer2nonneg}, which is used to illustrate the proofs for Lemma~\ref{lemma:onlyOne} and Lemma~\ref{lemma:iff}.
-		\begin{figure}[H]
+For clarity, Figure~\ref{fig:layer2} equivalent for a clause without negative complement is displayed as Figure~\ref{fig:layer2nonneg}, which is used to illustrate the proofs for Lemma~\ref{lemma:onlyOne} and Lemma~\ref{lemma:iff}.}
+	Next, we establish two lemmas, which relate start times at certain nodes in the activity network corresponding to an instance of \verb|EOIT_3SAT|.
+	\begin{figure}
 		\centering
-			\includegraphics[width=0.5\textwidth]{layer2nonneg}
+		\includegraphics[width=0.45\textwidth]{layer2nonneg}
 		\caption{The \(i\)-th clause, \(u_{j} \vee u_{k} \vee u_{\ell}\), in the second layer of the constructed activity network for \texttt{EOIT\char`_3SAT} with the arcs connecting it with the first and the third layer.}
@@
 	\begin{lemma} \label{lemma:onlyOne}
-			For any clause \(c_i = u_j \vee u_k \vee u_\ell,\ i = 1,2,\dots,m\), there is at most one activity \(c_{iq^*},\ q^* \in \{j,k,\ell\}\) that has the earliest start time as \(1\), and the start time for \(c_{iq}\) is \(2\), for \(q \in \{j,k,\ell\}, q \neq q^*\).
+		Consider an instance of \verb|EOIT_3SAT|, and the corresponding activity network for this instance.
+		For each clause, \(c_i\), 
+		%= u_j \vee u_k \vee u_\ell,\ 
+		\(i = 1,2,\dots,m\), there is at most one activity \(c_{iq^*},\ q^* \in \{j,k,\ell\}\), that has $1$ as its earliest start time, and the start time for \(c_{iq}\) is \(2\), for \(q \in \{j,k,\ell\}, q \neq q^*\).
 	\end{lemma}
 	\begin{proof}[Proof of Lemma \ref{lemma:onlyOne}]
+		The proof enumerates eight cases, and we begin with $c_i=u_j \vee u_k \vee u_\ell$, which has a component of the activity network illustrated in Figure~\ref{fig:layer2nonneg}.
 Without loss of generality, suppose both \(c_{ij}\) and \(c_{ik}\) can start at time \(1\).
-This means that both \(u_{j2}\) and \(u_{j3}\) needs to start at time \(1\), which is impossible because no matter what value \(G^1_{u_{j1}}\) takes, at least one activity in \(\{u_{j2},u_{j3}\}\) has to start after time \(2\).
+This means that both \(u_{j2}\) and \(u_{j3}\) need to start at time \(1\), which is impossible because regardless of \(G^1_{u_{j1}}\)'s value, at least one activity in \(\{u_{j2},u_{j3}\}\) can start no earlier than time \(2\).
+The proof is completed by enumerating the remaining seven cases---with variables $u_j, u_k, u_\ell$ in all combinations of original or complemented form---in analogous fashion.
 	\end{proof}
 	\begin{lemma} \label{lemma:iff}
-			For any clause \(c_i = u_j \vee u_k \vee u_\ell,\ i = 1,2,\dots,m\), one activity \(c_{iq^*},\ q^* \in \{j,k,\ell\}\) has the earliest start time as \(1\) if and only if variable \(\{u_{q^*}\}\) is the only variable in the clause to which the truth assignment is TRUE.
+		Consider an instance of \verb|EOIT_3SAT|, and the corresponding activity network for this instance.
+		For any clause, \(c_i\), 
+		%= u_j \vee u_k \vee u_\ell,\ i = 1,2,\dots,m\), 
+		activity \(c_{iq^*},\ q^* \in \{j,k,\ell\}\), has an earliest start time of \(1\) if and only if the corresponding {literal}, \(u_{q^*} \ \mbox{or} \ \bar{u}_{q^*} \), is the only {literal} in the clause to which the truth assignment is TRUE.
 	\end{lemma}
 	\begin{proof}[Proof of Lemma \ref{lemma:iff}]
-			Without loss of generality, we assume \(q^* = j\).\\
-			\(\implies\):  Suppose \(u_j\) is FALSE, then activity \(u_{j3}\) can only start after time \(2\), which will lead to the contradiction that \(c_{ij}\) can start as early as time \(1\).
-Suppose either \(u_k\) or \(u_\ell\) is TRUE in addition to \(u_j\).
-Since there is going to be an arc from either activity \(u_{k2}\) or \(u_{\ell 2}\) to activity \(c_{ij}\), and either \(u_{k2}\) or \(u_{\ell 2}\) cannot start before time \(2\), it leads to a contradiction that \(c_{ij}\) can start as early as time \(1\).
-Therefore, if activity \(c_{ij}\) can start at time \(1\), then \(u_j\) is the only variable which is TRUE.\\
-			\(\impliedby\): if only \(u_j\) is TRUE, then \(u_{j3}, u_{k2}\) and \(u_{\ell 2}\) can all start as early as time \(1\), which means that the earliest start time of \(c_{ij}\) is \(1\).
+		The proof again enumerates eight cases, and we begin with $c_i=u_j \vee u_k \vee u_\ell$; see Figure~\ref{fig:layer2nonneg}. Without loss of generality, we assume \(q^* = j\).\\
+		\((\implies)\): In turn we suppose $u_j$ is FALSE or $u_k$ is TRUE or $u_\ell$ is TRUE. 
+		First, suppose \(u_j\) is FALSE, i.e., $G_{u_{j1}}^1=0$.
+Then activity \(u_{j3}\) can start no earlier than time \(2\), which leads to the contradiction that \(c_{ij}\) can start as early as time \(1\); see Figure~\ref{fig:layer2nonneg}.
+Suppose \(u_k\) is TRUE.
+		%in addition to \(u_j\). This "in addition" shouldn't be there. It's u_j=TRUE AND u_k=FALSE AND u_\ell=FALSE. So, assuming the negation is u_j=FALSE OR u_k=TRUE OR u_\ell=TRUE.
+		Since there is an arc from \(u_{k2}\) to activity \(c_{ij}\), and since \(u_{k2}\) cannot start before time \(2\) this again contradicts that \(c_{ij}\) can start as early as time \(1\).
+The argument for $u_\ell$ being TRUE is identical.
+Therefore, if activity \(c_{ij}\) can start at time \(1\) then \(u_j\) is the only literal which is TRUE.\\
+		\((\impliedby)\): if only \(u_j\) is TRUE, then \(u_{j3}, u_{k2}\) and \(u_{\ell 2}\) can all start as early as time \(1\); again, see Figure~\ref{fig:layer2nonneg}.
+This means that the earliest start time for \(c_{ij}\) is \(1\).
+\\
+		We again complete the proof by enumerating the remaining seven cases. 
 	\end{proof}
-		\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of \verb|EOIT_3SAT|, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\).
-Since we have a total of \(B = 2m\) units of resource, we can crash all of those \(c\)-activities to achieve a project length of \(2\).
-This means that we can transform an \verb|EOIT_3SAT| problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above.
-If we can find a feasible \verb|EOIT_3SAT| assignment, it is possible to obtain a project length less than or equal to 2.
-Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption.
-We first formally define the project crashing decision problem under a stochastic disruption:
+	\noi As a result of Lemmas~\ref{lemma:onlyOne} and~\ref{lemma:iff},  we can transform an \verb|EOIT_3SAT| instance to an instance of model~\eqref{prob:extensive} using the activity network construction process just described.
+In particular, we know that if there exists a truth assignment to the variables of $U$ that meets the requirement of \verb|EOIT_3SAT|, there are exactly $2m$  \(c\)-activities (two per clause) that can start no earlier than time \(2\).
+Since we have budget \(B = 2m\), we can crash all of those \(c\)-activities to achieve a project length of \(2\).
+If there is no truth assignment that meets the requirement of \verb|EOIT_3SAT| then model~\eqref{prob:extensive}'s optimal value is $3$.
+	%If we can find a feasible assignment, in the sense of \verb|EOIT_3SAT|, to the variables of $U$ then it is possible to obtain a project length \tcb{less than or equal} \tcr{equal} to 2.
+Otherwise, the minimum length is $3$.
+	%Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption. We first formally define the project crashing decision problem under a stochastic disruption:
+	We formalize this in what follows.
 	\begin{definition}
-			A project crashing decision problem under a stochastic disruption is: if we solve is model~\ref{prob:extensive}, there a feasible \(\{t,x,G\}\) such that the optimal expected project length is smaller than or equal to \(\mathcal{T}\).
+		{\sc Stochastic Crashing Decision Problem:} Is there a feasible solution, $(t,x,G)$, to model~\eqref{prob:extensive} with objective function value of at most $\tau$?
+		%A project crashing decision problem under a stochastic disruption is: if we solve is model~\ref{prob:extensive}, there a feasible \(\{t,x,G\}\) such that the optimal expected project length is smaller than or equal to \(\mathcal{T}\).
 	\end{definition}
 	\begin{theorem}\label{thm:npcomplete}
-			For an instance of the \verb|EOIT_3SAT| problem, we construct the corresponding project crashing decision problem under a stochastic disruption: let \(\Omega = \{1\}\), \(H^1 = 0\), \(\mathcal{T} = 2\), and the precedence relationships, the crashing options and budget are constructed by the process shown in the Section~\ref{sec:nphard}.
-This decision problem has a solution if and only if the given instance of \verb|EOIT_3SAT| problem has a solution.
+		Consider an instance of \verb|EOIT_3SAT|, and the corresponding activity network for this instance.
+In particular, let \(\Omega = \{1\}\), \(H^1 = 0\), $p^1=1$, and let the network topology and model parameters be given by Figure~\ref{fig:layer1}, rule~\eqref{eqn:layer2} and equations~\eqref{eqn:first_layer}, \eqref{eqn:first_layer_crash}, and \eqref{eqn:EOIT_assignments}.
+Let \(\tau = 2\).
+The answer to the {\sc Stochastic Crashing Decision Problem} is yes if and only if the given instance of \verb|EOIT_3SAT| problem has a solution, i.e., a truth assignment to the variables so that each clause has exactly one true literal.
 	\end{theorem}
 	\begin{proof}[Proof of Theorem~\ref{thm:npcomplete}]
-			(polynomial transformation) 
+		%		(polynomial transformation) 
 		%We first show that any instance of the project crashing decision problem is constructed in time that is polynomial in the length of the given instance of \verb|EOIT_3SAT|, and has a length that is polynomially related to the length of that instance.
-			Suppose the \verb|EOIT_3SAT| problem has \(n\) variables and \(m\) clauses, the constructed activity network for the project crashing problem has \(4n + 3m + 1\) activities and \(5n + 12m\) arcs, which are both polynomial in the size of the original \verb|EOIT_3SAT| problem.
-And all numbers in the project crashing decision problem are smaller than a constant, \(2\).\\
-			(\(\implies\)) Suppose the \verb|EOIT_3SAT| instance has a solution.
-We have shown that we can start every activity as early as possible, and spend the budget to crash all \(c\)-activities which correspond to the literals with FALSE assignment and have the start time at \(2\).
-\\
-			(\(\impliedby\)) Suppose the project crashing decision problem has a solution \((\hat{t},\hat{x},\hat{G})\) where \(t_T = 2\).
-By Lemma~\ref{lemma:onlyOne} we know that for each clause there are at most one \(c\)-activity that can start at time \(1\), which means in total there must be at least \(2m\) number of \(c\)-activities with a start time later than \(2\).
-Since the crashing budget is exactly \(2m\), if there are more than \(2m\) \(c\)-activities that starts after time \(2\), the project length will be larger than 2, which means that there are exactly \(2m\) number of \(c\)-activities starting at time \(2\).
-This is equivalent to that exactly one \(c\)-activity in each of the \(m\) clauses starts at time \(1\).
-From Lemma~\ref{lemma:iff} we can directly obtain the result that for each clause there is exactly one variable to which the truth assignment is TRUE, which is essentially a solution to the \verb|EOIT_3SAT| instance.\\
-			\newline
-			\verb|EOIT_3SAT| is a NP-complete problem~\cite{Garey1979ComputersAI}.
-The project crashing decision problem under a stochastic disruption in NP, since we can check in \(O(n^2)\) to check whether a given input is feasible and has \(t_T \leq \mathcal{T}\).
-This complete the proof that the project crashing decision problem under a stochastic disruption is NP-complete.
+		The \verb|EOIT_3SAT| problem has \(n\) variables and \(m\) clauses, and the constructed activity network for the project crashing problem has $3n + 3m + 2$ activities and \(4n + 12m\)
+		%\tcb{I'm with you on $12m$ but why $5n$. $n$ come to the first layer from $S$, $n$ go to $T$ from the first layer and there are $2n$ more within the first layer. what am i missing?}
+		arcs. Thus the size of the activity network and the time required to construct the network are both polynomial in the size of the original \verb|EOIT_3SAT| instance. \\
+		%And all numbers in the project crashing decision problem are smaller than a constant, \(2\).\\
+		{(\(\impliedby\))} Suppose the \verb|EOIT_3SAT| instance has a solution.
+A feasible solution to the instance of model~\eqref{prob:extensive} starts every activity as early as possible.
+Under the \verb|EOIT_3SAT| hypothesis, by Lemmas~\ref{lemma:onlyOne} and~\ref{lemma:iff} exactly $2m$ $c$-activities have earliest start times of $2$ and the remaining $m$ have an earliest start time of $1$.
+Spending the budget, $B=2m$, to crash all $2m$ \(c\)-activities that correspond to the literals with FALSE assignment, yields an objective function value of \(2\).
+\\
+		{(\(\implies\))} Suppose the instance of model~\eqref{prob:extensive} has a solution, \((\hat{t},\hat{x},\hat{G})\), with an objective function value of $2$.
+By Lemma~\ref{lemma:onlyOne} we know that for each clause there is at most one \(c\)-activity that can start at time~\(1\), which means there must be at least \(2m\) \(c\)-activities with a start time of at least $2$.
+Since $B=2m$, if there are more than \(2m\) \(c\)-activities that start at time \(2\) or after, the objective function value of model~\eqref{prob:extensive} must exceed 2.
+Hence, there are exactly \(2m\) \(c\)-activities starting at time \(2\).
+Lemmas~\ref{lemma:onlyOne} and~\ref{lemma:iff} then imply that exactly one \(c\)-activity in each of the \(m\) clauses starts at time \(1\); i.e,.
+for each clause there is exactly one variable to which the truth assignment is TRUE.\\
+		\newline
+		\verb|EOIT_3SAT| is NP-complete~\citep{Garey1979ComputersAI}.
+The {\sc Stochastic Crashing Decision Problem} is in NP because we can check in {\(O(n+m)\)} time whether a given solution is feasible and has an objective function value of at most $\tau$.
+%This complete the proof that the project crashing decision problem under a stochastic disruption is NP-complete.
 	\end{proof}
-		\begin{theorem} \label{thm:nphard}
-			The project crashing optimization problem under a stochastic disruption is NP-hard.
-		\end{theorem}
-		\begin{proof}[Proof of Theorem~\ref{thm:nphard}]
-			From Theorem~\ref{thm:npcomplete} states that the project crashing decision problem under a stochastic disruption is NP-complete.
+	\noi
+	As a result of Theorem~\ref{thm:npcomplete} we immediately obtain the following result.
+	\begin{corollary} \label{thm:nphard}
+		Model~\eqref{prob:extensive} is NP-hard, even under a single disruption scenario, which occurs with probability one at time zero.
+		%		The project crashing optimization problem under a stochastic disruption is NP-hard.
+	\end{corollary}
+	%	\begin{proof}[Proof of Corollary~\ref{thm:nphard}]
+	%		From Theorem~\ref{thm:npcomplete} states that the project crashing decision problem under a stochastic disruption is NP-complete.
 This implies the project crashing optimization problem under a stochastic disruption, formulated as model~\ref{prob:extensive}, is NP-hard.
-		\end{proof}
+	%	\end{proof}
 
@@
 	%		\end{enumerate}
+
 	\begin{example} \label{eg:short}
@@
 
-	\section{Decomposition Method} \label{sec:decomposition}
-	Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program (2SMIP), which is large-scale and computationally expensive in general~\cite{ahmed2011smip}.
-We first follow the Benders' decomposition method to separate the model into a master problem \((M)\) and a set of subproblems \((S^\omega)\), \(\omega \in \Omega\).
-The state variables \(t\) and \(x\) are all continuous and binary variables exist in the recourse problems, which makes recourse problems nonconvex.
+	\section{A Decomposition Algorithm} \label{sec:decomposition}
+	%Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program XXX, which is can be large in scale and computationally expensive to solve.
+	%in general~\cite{ahmed2011smip}. 
+	%We rewrite model~\eqref{prob:extensive} in a recursive form, which will help suggest a decomposition algorithm. 
+	%can rewrite it into a master problem \((M)\) and a set of subproblems \((S^\omega)\) for \(\omega \in \Omega\) as follows. The 
+	%state variables \(t\) and \(x\) are both continuous and binary variables exist in the recourse problems, which makes recourse problems nonconvex.
+	Model~\eqref{prob:extensive} is a two-stage stochastic mixed-integer program, which we can rewrite as follows:
+	%	decompose into a master problem \((M)\) and a set of subproblems \((S^\omega)\), \(\omega \in \Omega\), as follows.
+The state variables~\(t\) and~\(x\) are continuous, and binary variables in the recourse problems, which makes recourse problems nonconvex.
 	\begin{subequations}
@@
 		\begin{align}
-		(M) \quad z^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\
-		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MSep}\\
+		z^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega(t,x)\\
+		\text{s.t.} \quad & t_k - t_i \geq D_{ik} \left (1 - \sum_{j \in J_i} e_{ij} x_{ij} \right ) \qquad \qquad \forall (i,k) \in \cA \label{cons:MSep}\\
 		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:MBudget}\\
 		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MSingleBudget}\\
-		& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
-		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i. \label{cons:Mxbounds}
-		\end{align}
-	\end{subequations}
+		& {t_i \geq 0} \qquad \qquad \qquad \; \forall \,i \in I\\
+		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i, \label{cons:Mxbounds}
+		\end{align}
+	\end{subequations}
+	\noi where
 	\begin{subequations}
@@
 		\begin{align}
-		(S^\omega) \qquad f^\omega(\hat{t},\hat{x}) = \min \quad & t_T \\
-		& H^\omega + G_i M \geq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:sG1}\\
+		(S^\omega) \qquad 
+		f^\omega(\hat{t},\hat{x}) = \min \quad & t_T \\
+		\text{s.t.} \quad & H^\omega + G_i M \geq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:sG1}\\
 		& H^\omega - (1 - G_i) M \leq \hat{t}_i \qquad \qquad \forall \,i \in I \label{cons:sG2}\\
@@
 		& x_{ij} - G_i \leq \hat{x}_{ij} \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sxG2}\\
-		& t_k - t_i \geq D_i + d_i^\omega G_i -\sum_{j \in J_i} D_i e_{ij} x_{ij} - \sum_{j \in J_i} d_i^\omega e_{ij} z_{ij} \nonumber \\ 
-		& \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:subSep}\\
+		& t_k - t_i \geq D_{ik} + d_{ik}^\omega G_i -\sum_{j \in J_i} D_{ik} e_{ij} x_{ij} - \sum_{j \in J_i} d_{ik}^\omega e_{ij} z_{ij} %\nonumber \\ 
+		%& \qquad 
+		\ \ 
+		\forall \, (i,k) \in \cA \label{cons:subSep}\\
+		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:subBudget}\\
 		& \sum_{j \in J_i} x_{ij} \leq 1 \qquad \qquad \forall \,i \in I \label{cons:subBudget1}\\
-		& \sum_{i \in I}\sum_{j \in J_i} b_{ij}x_{ij} \leq B \qquad \qquad \forall \,\omega \in \Omega \label{cons:subBudget}\\
 		& z_{ij} \leq G_i \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sublinearize1}\\
@@
 		& z_{ij} \geq G_i + x_{ij} - 1 \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:sublinearize3}\\
+		& {t_i \ge 0} \quad \quad \forall i \in I \\
 		& t_i \geq H^\omega G_i \qquad \qquad \forall\, i \in I \label{cons:subH}\\
 		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
-		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
-		& G_i \in \{0,1\}. \qquad \qquad \forall \,i \in I. \label{cons:subInt}
-		\end{align}
-	\end{subequations}
-	Most of the previous literature of stochastic mixed integer programming assumes a special structure or property which cannot be applied to our problem setting.
-For example, Gade et al.
-\cite{gade2014decomposition} solve 2SMIPs with pure binary first stage variables using a sequential convex approximation of recourse by a branch-and-cut process framework where Gomory cuts are added.
-Ahmed et al.
-\cite{zou2016nested} assume state variables to be binary so that the Lagrangian cuts are a tight approximation of the recourse function.
-Car{\o}e and Tind \cite{caroe1998shaped} solves a more general case of 2SMIP by using the MIP duality theory but the practical tractability is not verified.
-Qi and Sen \cite{qi2017ancestral} have mixed integer variables in both the master and the recourse problems.
-Parametric disjunctive cuts, derived in Chen et al.
-\cite{chen2012computational}, are generated to convexify recourse problems while Benders' cuts approximate recourse value functions.
-Although this method suits our problem settings, we implement it only to find that it does not converge in a reasonable time frame.
-Therefore, we need a new decomposition method that utilizes the special structure of our problem.
-\\
-	\newline
-	We can relax the integrality constraints~\eqref{cons:subInt} and perform Benders' decomposition on the relaxed problem.
-Benders' cuts provide a valid lower approximation of the recourse function \(f^\omega(t,x), \forall \omega \in \Omega\) but may not be tight.
-In each iteration of the Benders' decomposition, an upper bound can be obtained by evaluating the subproblems~\eqref{prob:subOri} with the first stage solution.
-The main challenge is how to gradually tighten the lower approximation while quickly locate a good upper bound, and all topics in this section aim to tackle either aspect of this challenge.
-	\subsection{Partitioning-based Decomposition Method} \label{subsec:partition}
-	The relaxation quality is poor since a big-\(M\) needs to be incorporated in our recourse problems to represent the logical condition whether the starting time of activity \(i\) is before or after the disruption time.
-A smaller big-\(M\) yields a tighter relaxation and helps prevent numerical issues~\cite{camm1990cutting,klotz2013practical}.
-We can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
-	\begin{equation} \label{cons:Grange}
-	(\hat{t}_i - H^\omega)/M \leq G_i \leq (\hat{t}_i - H^\omega)/M + 1
-	\end{equation}
-	and \(G_i\) can take a wider range of value when \(M\) is larger.
-Therefore, sequentially tightening \(M\) is helpful to generate a tighter lower bound as the algorithm progresses.
-Eventually, if for a scenario we can fix the \(G_i\) for all \(i \in I\) to either 0 or 1, the Benders' cuts will be tight.\\
-	\newline
-	From now on we assume the scenarios \(\omega \in \Omega\) are ordered according to their time \(H^\omega\) in an ascending order.
-We can also observe that if we know \(\hat{t}_i \geq H^{\omega'_i}\) for some \(\omega'_i\), \(G_i\) has to take value 1 in all subproblem \(S^\omega\) where \(\omega < \omega'_i\).
-On the other hand if we know \(\hat{t}_i \leq H^{\omega'_i}\) for some \(\omega'_i\), \(G_i\) has to take value 0 in all subproblem \(S^\omega\) where \(\omega > \omega'_i\).
-These observations inform us that by bounding the value of first stage variable \(t_i,\ \forall i \in I\), we can determine the value of \(G_i\) in many subproblems, which strengthens the Benders' cuts.\\
-	\newline
-	We propose a decomposition algorithm to solve model~\eqref{prob:extensive}.
-Our method partitions the continuous feasible region of the master problem by introducing of a set of binary variables.
-As we refine the partition of \(t\)-space, we can generate tightened Benders' cuts to approximate the recourse function.
-For any crashing optimization problem, we can bound the first stage \(t_i\) variables by lower bound \(0\) and upper bound \(T_{\max} = H^{|\Omega|} + t_T^0\), where \(t_T^0\) is the longest \(S\)-\(T\) path of activity network \(\mathcal{G} = (I,\mathcal{A})\) and the arc length of \((i,j) \in \mathcal{A}\) equals to \(D_i\).
-This means that suppose the optimal solution of model~\eqref{prob:extensive} is denoted as \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\), the latter two representing the scenario specific start time and crashing decisions, we have:
-	\begin{proposition} \label{prop:bounds}
-		\(t^*_i \in [0,T_{\max}],\ \forall i \in I\).
-	\end{proposition}
-	\begin{proof}
-		Constraint~\eqref{cons:nonnegt} enforces the lower bound of this proposition. \\
-		\newline 
-		To derive the upper bound, 
-		we first establish a feasible solution \(\tilde{t}_i = H^{|\Omega|} + t^0_i,\ \forall i \in I\), \(\tilde{x}_{ij} = 0,\ \forall i \in I, j \in J_i\) and \(\tilde{G}_i^\omega = 1,\ \forall i \in I, \omega \in \Omega\), where \(t^0_i\) represents the length of the longest \(S\)-\(i\) path of \(\mathcal{G}\).
-		If we assume that there exists some \(i \in \tilde{I}\) such that \(t_i^* > T_{\max}\), we know \(T \in \tilde{I}\).
-There, we can keep \(x^*\), \(G^{*,\omega}\), \(t^{*,\omega}\) and \(x^{*,\omega}\) for all \(\omega \in \Omega\) the same, and replace the \(t_i^*\) by \(\tilde{t}_i\) for all \(i \in \tilde{I}\) without violating any constraints.
-This yields another feasible solution which has a smaller value of \(t_T^*\) since \(T \in \tilde{I}, \tilde{t}_T = T_{\max} < t_T^*\).
-Therefore the new objective value obtained by this feasible solution is smaller, which contradicts the assumption that \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\) is an optimal solution.
-	\end{proof}
-	\noi Proposition~\ref{prop:bounds} indicates that all \(t_i,\ \forall i \in I\) are bounded on an interval \([0,T_{\max}]\).
-Since there are precedence relationships between activities, the possible range of different activities' start time can be further limited.
-We first set up two parameters \(H^0 = 0\) and \(H^{|\Omega| + 1} = T_{\max}\) and then define a partition of this interval for each \(i \in I\) to exploit this limitation as follows:
-	\begin{definition}
-		For an activity \(i \in I\), the partition of interval \([0,T_{\max}]\) is denoted by \(\mathcal{P}_i\), which is an ordered set of two-element tuples %\((\underbar{\omega}^q,\bar{\omega}^q)\), 
-		\((\underbar{H}^q,\bar{H}^q)\), 
-		indexed by \(q \in \mathcal{Q}_i\).
-We use \(\underbar{H}^q\) to specify the lower bound of \(q\)-th element of the partition and \(\bar{H}^q\) to specify its upper bound.
-Each of them corresponds to a disruption time of some scenario.
-		The partition has the following properties:
+		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i \label{cons:subzbounds}\\
+		& G_i \in \{0,1\} \qquad \qquad \forall \,i \in I. \label{cons:subInt}
+		\end{align}
+	\end{subequations}
+	A number of existing approches for stochastic mixed-integer programming assume a special structure not satisfied by our model.
+For example, \citet{gade2014decomposition} solve two-stage stochastic programs with pure binary first stage variables, and general integer second stage variables; they derive a finitely convergent sequential convex approximation and a branch-and-cut framework involving Gomory cuts that are parameterized by the first-stage decision variables.
+\citet{zou2016nested} assume state variables are binary (or general integer via binary expansion) in a multi-stage setting so that the Lagrangian cuts are a tight approximation of the recourse function; see also~\citet{philpott2016midas}.
+\citet{caroe1998shaped} solve a more general case of two-stage models by using integer programming duality, but there is limited computational work investigating their approach.
+\citet{qi2017ancestral} allow mixed-integer variables in both the first stage and the recourse problem, and parametric disjunctive cuts convexify recourse problems while Benders' cuts approximate recourse functions~\citep{chen2012computational}.
+Although this method suits our problem setting, preliminary computational results found that it was not competitive with the scheme we describe here, which makes use of the special structure of our problem.
+\\
+	\newline
+	A simple approach is to relax the integrality constraints~\eqref{cons:subInt} of {\em subproblem} ($S^\omega$), and execute a multi-cut L-shaped decomposition algorithm on this linear programming (LP) relaxation.
+The resulting optimality cuts provide a valid lower approximation of the recourse functions, \(f^\omega(t,x), \forall \omega \in \Omega\), but may not be tight.
+In each iteration of the decomposition, an upper bound can be obtained by solving subproblems~\eqref{prob:subOri} with the first stage solution.
+The main challenge is how to iteratively tighten the lower bound while quickly locating a good upper bound.
+The topics in this section aim to tackle these two issues.
+\\
+	\newline
+	The combinatorial decision, $G_i \in \{0,1\}$,  $i \in I$, for each ($S^\omega$) is (almost fully) decided by the first-stage continuous variables, $t_i$.
+If $\hat{t}_i > H^\omega$ then $G_i=1$, if $\hat{t}_i < H^\omega$ then $G_i=0$, and only if they are equal is there a combinatorial choice.
+This observation motivates the decomposition algorithm that we develop.
+We could pull these binary variables to the first stage, but doing so involves $|I| | \Omega |$ variables and does not scale well.
+Instead, we partition an interval, which we denote $[0,T_{\max}]$, containing each $t_i$, and we adaptively refine that partition.
+This helps control the number of binary first-stage variables, and has further benefits in terms of tightening lower bounds, as we describe in what follows.
+We will be specific later regarding the value of $T_{\max}$, but for now we simply assume we have a value such that $t_i \in [0,T_{\max}]$ is a redundant constraint in model~\eqref{prob:extensive}.
+\\
+	\newline
+	We assume that $\Omega = \{1,2,\ldots,|\Omega|\}$ is such that $\omega < \omega^\prime$ implies $H^\omega \le H^{\omega^\prime}$ with strict inequality if the realizations of $H$ are distinct, and we let $H^0 \equiv 0 \le H^1$ and $H^{|\Omega|+1} \equiv T_{\max} \ge H^{|\Omega|}$.
+We define a partition of $[0,T_{\max}]$ for each \(i \in I\) as follows.
+	\begin{definition}\label{definition:partition}
+		For each activity \(i \in I\), we define a partition of interval \([0,T_{\max}]\)  as an ordered set of two-element tuples  \(\cP_i = \{[\underbar{H}^q,\bar{H}^q],\ q \in \cQ_i\}\) with an index set \(\cQ_i=\{1,2,\ldots,|\cQ_i|\} \) and the following properties:
 		\begin{itemize}
-			%\item \(\underbar{\omega}^1 = 0\)
-			\item \(\underbar{H}^1 = H^0 = 0\)
-			%\item \(\bar{\omega}^{|\mathcal{Q}_i|} = T_{\max}\)
-			\item \(\bar{H}^{|\mathcal{Q}_i|} = H^{|\Omega| + 1} = T_{\max}\)
-			%\item \(\bar{\omega}^q = \underbar{\omega}^{q + 1}\).
-			\item \(\bar{H}^q = \underbar{H}^{q + 1}\).
+			\item \(\underbar{H}^1 = H^0 \equiv 0\)
+			\item \(\bar{H}^{|\cQ_i|} = H^{|\Omega| + 1} \equiv T_{\max}\)
+			\item $\underbar{H}^q < \bar{H}^q  \ \ \forall q \in \cQ_i$
+			\item \(\bar{H}^q = \underbar{H}^{q + 1} \  \ \forall q \in \cQ_i \).
 		\end{itemize}
 	\end{definition}
-	\noi A simple example of such partition can be illustrated in Figure~\ref{fig:simplePart}.
-In this example we have five scenarios \(\Omega = \{1,2,3,4,5\}\), ordered by the disruption time.
-The partition has three elements, each illustrated by a box with dashed lines and represent a part of the interval.
-For partition element \(1\), the lower bound scenario index is \(0\) and the upper bound scenario index is \(2\), which means the range corresponding to it is lower bounded by \(H^0 = 0\) and upper bounded by \(H^2\).
+	\noi With the possible exceptions of $\underbar{H}^1$ and $\bar{H}^{|\cQ_i|}$, each \(\underbar{H}^q\) and \(\bar{H}^q\) corresponds to a disruption time of some scenario, and a simple example is illustrated in Figure~\ref{fig:simplePart} in which we have five scenarios, \(\Omega = \{1,2,3,4,5\}\).
+The partition has three intervals as illustrated.
+The second interval has lower bound \(H^2\) and upper bound \(H^5\).
 	\begin{figure}[H]
@@
 		\includegraphics[width=0.8\textwidth]{simplePart}
-		\caption{An illustration of partition on interval \([0,T_{\max}]\).}
+		\caption{An illustration of a partition of interval \([0,T_{\max}]\)}
 		\label{fig:simplePart}
 	\end{figure}
-	\noi For each activity \(i \in I\), with the partition \(\mathcal{P}_i\) defined, we can see the start time \(t_i\) of the master problem lies in the range specified by one element of \(\mathcal{P}_i\).
-We introduce an indicator \(y_i^q\), \(\forall i \in I, q \in \mathcal{Q}_i\) in the first stage:
-	\begin{equation}
-	y_i^q = \begin{cases}
-	%1 & \text{if \(t_i \in [H^{\underbar{\omega}^q},H^{\bar{\omega}^q}]\)}\\
-	1 & \text{if \(t_i \in [\underbar{H}^q,\bar{H}^q]\)}\\
-	0 & \text{otherwise}
-	\end{cases}
-	\qquad \forall i \in I, q \in \mathcal{Q}_i,
-	\end{equation}
-	and we use the following constraints to represent this relationship:
+	\noi For each activity \(i \in I\) the first-stage start time \(t_i\) lies an interval of \(\cP_i\), and we introduce a first-stage indicator variable:
+	%	\begin{equation}
+	%		y_i^q = \begin{cases}
+	%			%1 & \text{if \(t_i \in [H^{\underbar{\omega}^q},H^{\bar{\omega}^q}]\)}\\
+	%			1 & \text{if \(t_i \in [\underbar{H}^q,\bar{H}^q]\)}\\
+	%			0 & \text{otherwise}
+	%		\end{cases}
+	%		\qquad \forall i \in I, q \in \cQ_i,
+	%	\end{equation}
+	%	and we use the following constraints to represent this relationship:
 	\begin{subequations} \label{cons:yCons}
 		\begin{align}
-		& \sum_{q \in \mathcal{Q}_i} \underbar{H}^q y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} \bar{H}^q y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
-		& \sum_{q \in \mathcal{Q}_i} y_i^q = 1 \qquad \qquad \forall i \in I. \label{cons:sumy1}
-		\end{align}
-	\end{subequations}
-	In constraint~\eqref{cons:sumy1}, we enforce that \(t_i\) can only lie in one of the ranges specified by the partition, as only one of \(y_i^q\) can take value \(1\) for each \(i \in I\).
-Depending on the value of \(y_i^q\), we can write the bounds of the such range as in~\eqref{cons:tyBounds}.
-\\
-	\newline
-	The benefit of setting up the \(y\) variables is to obtain tighter bounds for \(t_i\) than the generic bounds \([0,T_{\max}]\) in Proposition~\ref{prop:bounds}.
-Suppose solving the master problem provides a solution \(\hat{y}_i^{\tilde{q}}, \forall i \in I, q \in \mathcal{Q}_i \).
-Then we can replace the big-\(M\) in constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} of the scenario with moderate \(M_i^{\omega,+}\) and \(M_i^{\omega,-}\) because introducing variables \(y\) gives us better bounds on \(t_i\):
-	\begin{subequations}
+		& \sum_{q \in \cQ_i} \underbar{H}^q y_i^{q} \leq t_i \leq \sum_{q \in \cQ_i} \bar{H}^q y_i^{q} \qquad \qquad \forall i \in I \label{cons:tyBounds}\\
+		& \sum_{q \in \cQ_i} y_i^q = 1 \qquad \qquad \forall i \in I \label{cons:sumy1} \\
+		& y_i^q \in \{0,1\}, \quad \quad \forall i \in I, q \in \cQ_i.
+		\end{align}
+	\end{subequations}
+	{Constraints~\eqref{cons:yCons} require that \(t_i\) be associated with one of the intervals of the partition.
+In model~\eqref{prob:extensive} if $t_i=H^\omega$ then $G_i^\omega$ can either be 0 (activity $i$ is said to start before $\omega$'s disruption) or 1 ($i$ starts after the disruption).
+If $t_i=\bar{H}^q = \underbar{H}^{q + 1}=H^\omega$ for some $\omega$ then the $y$-variables have a similar choice, and our convention is that if the $y$-variables choose $t_i \in [\underbar{H}^q,\bar{H}^q]$ then activity $i$ is said to start before the disruption and if $t_i \in [\underbar{H}^{q+1},\bar{H}^{q+1}]$ then $i$ starts after the disruption.}
+	%	\newline
+	\subsection{Tightening Big-\(M\) with Partitions} \label{subsec:tightenM}
+	The tightness of ($S^\omega$)'s LP relaxation relies, in part, on the big-$M$ value used in constraints to represent the logical condition of whether activity \(i\) starts before or after a disruption.
+A smaller, but still valid, big-\(M\) value yields a tighter relaxation, and can further help prevent numerical issues~\citep[e.g.,][]{camm1990cutting,klotz2013practical}.
+We can rewrite constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} as:
+	\begin{equation} \label{cons:Grange}
+	(\hat{t}_i - H^\omega)/M \leq G_i \leq (\hat{t}_i - H^\omega)/M + 1.
+	\end{equation}
+	Variable \(G_i\) can take a wider range of values when \(M\) is large.
+Tightening \(M\) hinges on specifying valid ranges for \(\hat{t}_i\).
+Furthermore, we know that if \(\hat{t}_i > H^{\omega'}\) for some \(\omega'\) then \(G_i\) has to take value 1 in all subproblems ($S^\omega$) with \(\omega < \omega'\).
+On the other hand, if \(\hat{t}_i < H^{\omega'}\) for some \(\omega'\) then \(G_i\) must be 0  for all subproblems ($S^\omega$) in which \(\omega > \omega'\).
+If we can fix the \(G_i\) for all \(i \in I\) to either 0 or 1 the resulting optimality cuts will be tight.
+\\
+	%	\newline
+	%    These observations inform us that a tighter \(M\) and more binary valued \(G\) can result from bounding the value of first stage variable \(t_i,\ \forall i \in I\).
+We start with a set of initial bounds specified by Proposition~\ref{prop:bounds}.
+From now on we assume the scenarios \(\omega \in \Omega\) are sorted according to their time \(H^\omega\) in an ascending order.
+	%This means that suppose the optimal solution of model~\eqref{prob:extensive} is denoted as \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\), the latter two representing the scenario specific start time and crashing decisions, we have:
+	{
+		\begin{proposition} \label{prop:bounds}
+			Let \(t_i^0\) be the longest \(S\)-\(i\) path in the activity network \(\mathcal{G} = (I,\cA)\) in which the arc length of \((i,k) \in \cA\) is \(D_{ik}\) and in which no crashing is allowed.
+Let \(t^*\) denote (part of) an optimal solution to model~\eqref{prob:extensive}.
+Then there exists a \(t^*\) such that \(t^*_i \in [0,H^{|\Omega|} + t_i^0],\ \forall i \in I\) provided $M$ and $M_t$ are sufficiently large.
+			%\(T_{\max} = H^{|\Omega|} + t_T^0\), where 
+		\end{proposition}
+		\begin{proof}
+			Constraint~\eqref{cons:nonnegt} enforces the lower bound of $0$. \\
+			%under our assumption that $D_{ik} + d_{ik}^\omega \ge 0$ for all $(i,k) \in \cA$, $\omega \in \Omega$. \\
+			\newline 
+			By hypothesis \(t_k^0 - t_i^0 \geq D_{ik}, \forall (i,k) \in \cA\) since \(t_i^0\) is the longest \(S\)-\(i\) path of \(\mathcal{G}\) in which the arc length of \((i,k) \in \cA\) is \(D_{ik}\) and in which no crashing is allowed.
+We prove the upper bound on \(t_i^*\) by contradiction.
+\\
+			\newline
+			Suppose there does not exist a \(t^*\) such that \(t^*_i \in [0,H^{|\Omega|} + t_i^0],\ \forall i \in I\).
+Then for every \(t^*\), there must be a set \(I^* \subseteq I\) such that \(t_i^* > H^{|\Omega|} + t^0_i\) for $i \in I^*$.
+Let the corresponding optimal values of variables \(x_{ij}, G_i^\omega, t_i^\omega, x_{ij}^\omega, z_{ij}^\omega\) be denoted \(x_{ij}^*, G_i^{\omega,*}, t_i^{\omega,*}, x_{ij}^{\omega,*}, z_{ij}^{\omega,*}\), respectively.
+We can establish a feasible solution to model~\eqref{prob:extensive} as follows:
+			\begin{subequations} \label{eqn:feasSol}
 				\begin{align}
-		& M_i^{\omega,+} = \sum_{q \in \mathcal{Q}_i} \bar{H}^q \hat{y}_i^q - H^\omega\\
-		& M_i^{\omega,-} = H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q，
-		\end{align}
-	\end{subequations}
-	and the constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} become:
+				& \tilde{t}_i = H^{|\Omega|} + t^0_i \qquad \forall i \in I^* \label{eqn:tequal1} \\
+				& \tilde{t}_i = t_i^* \qquad \forall i \in I \backslash I^* \label{eqn:tequal2}\\
+				& \tilde{x}_{ij} = x_{ij}^* \qquad \forall i \in I, j \in J_i \\
+				& \tilde{G}_i^\omega = G_i^{\omega,*} \qquad \forall i \in I, \omega \in \Omega \\
+				& \tilde{t}_i^\omega = t^{\omega,*}_i \qquad \forall i \in I, \omega \in \Omega \\
+				& \tilde{x}_{ij}^\omega = x_{ij}^{\omega,*} \qquad \forall i \in I, j \in J_i, \omega \in \Omega \\
+				& \tilde{z}_{ij}^\omega = z_{ij}^{\omega,*} \qquad \forall i \in I, j \in J_i, \omega \in \Omega.
+				\end{align}
+			\end{subequations}
+			We see this solution is feasible by examining the constraints of model~\eqref{prob:extensive}:
+			\begin{itemize}
+				% the separation constraints?
+				\item For constraint~\eqref{cons:Sep}, we examine the following four possible cases:
+				\begin{itemize}
+					\item \(i \in I^*, k \in I^*\): since \(\tilde{x}_{ij} \geq 0\) and \(t_k^0 - t_i^0 \geq D_{ik}\), we have \[\tilde{t}_k - \tilde{t}_i  = t_k^0 - t_i^0 \geq D_{ik} \geq D_{ik} \left(1 - \sum_{j \in J_i} e_{ij} \tilde{x}_{ij} \right);\]
+					\item \(i \in I^*, k \notin I^*\): we have \(\tilde{t}_i < t_i^*\) since \(i \in I^*\), and then \[\tilde{t}_k - \tilde{t}_i > t_k^* - t_i^* \geq D_{ik} \left( 1 - \sum_{j \in J_i} e_{ij} x^*_{ij} \right) = D_{ik} \left(1 - \sum_{j \in J_i} e_{ij} \tilde{x}_{ij} \right);\]
+					\item \(i \notin I^*, k \in I^*\): since \(t_i^* \leq H^{|\Omega|} + t_i^0\), \(\tilde{x}_{ij} \geq 0\) and \(t_k^0 - t_i^0 \geq D_{ik}\), we have
+					\[\tilde{t}_k - \tilde{t}_i = H^{|\Omega|} + t_k^0 - t_i^* \geq H^{|\Omega|} + t_k^0 - \left(H^{|\Omega|} + t_i^0 \right) = t_k^0 - t_i^0 \geq D_{ik} \geq D_{ik} \left (1 - \sum_{j \in J_i} e_{ij} \tilde{x}_{ij} \right ); \]
+					\item \(i,k \notin I^*\): the constraint is unchanged and feasible;
+				\end{itemize}
+				% can G_i^\omega remains the same?
+				\item For variable \(G_i^\omega\):
+				\begin{itemize}
+					\item if \(i \notin I^*\): we have \(\tilde{t}_i = t_i^*\). Therefore, constraints~\eqref{cons:G1}-\eqref{cons:tG2} is unchanged and feasible;
+					\item if \(i \in I^*\): variable \(G_i^{*,\omega}\) is forced to take value \(1\) for all \(\omega \in \Omega\).
+Since \(\tilde{t}_i = H^{|\Omega|} + t_i^0 \geq H^{|\Omega|}\), for any \(\omega \in \Omega\), \(\tilde{G}_i^\omega = G_i^{*,\omega} = 1\) remains feasible.
+Therefore, constraints~\eqref{cons:G1}-\eqref{cons:tG2} hold for $M$ and $M_t$ sufficiently large.
+				\end{itemize}
+				\item Since the values for \(\tilde{t}_i^\omega, \tilde{x}_{ij}, \tilde{x}_{ij}^\omega, G_i^\omega, z_{ij}^\omega\) all remain the same, constraints~\eqref{cons:Budget},~\eqref{cons:SingleBudget},~\eqref{cons:xG1}-\eqref{cons:Gbounds} are all satisfied by the solution in~\eqref{eqn:feasSol}.
+			\end{itemize}
+			We can also see that \(\tilde{t}_i \leq t_i^* ,\ \forall i \in I\) because of equations~\eqref{eqn:tequal1} and~\eqref{eqn:tequal2}.
+Thus, the feasible solution in~\eqref{eqn:feasSol} yields an objective function value \(p^0 \tilde{t}_T + \sum_{\omega \in \Omega} p^\omega \tilde{t}_T^{\omega} \le p^0 t_T^* + \sum_{\omega \in \Omega} p^\omega t_T^{*,\omega}\).
+This means that the feasible solution in~\eqref{eqn:feasSol} is optimal.
+As \(\tilde{t}_i \leq H^{|\Omega|} + t_i^0,\ \forall i \in I\), it contradicts the assumption that there does not exist an optimal solution with \(t^*_i \in [0,H^{|\Omega|} + t_i^0],\ \forall i \in I\).
+			%Suppose there exists some \(i\) such that \(t_i^* > T_{\max}\). Since activity \(T\) succeeds every activity in \(I\backslash\{T\}\), we have \(t_T^* > T_{\max}\). 
+			%With $\tilde{G}_i^\omega=1$ for all $i \in I, \omega \in \Omega$ there is no coupling between variables $\tilde{t}_i^\omega$ and $\tilde{t}_i$. 
+			%However, \(T_{\max}\) is also the objective function value obtained by the feasible solution in~\eqref{eqn:feasSol}, which contradicts that \(t^*\) is optimal.
+Therefore, for all activity \(i \in I\), \(t_i^*\) must be smaller or equal to \(T_{\max}\).
+			%		There, we can keep \(x^*\), \(G^{*,\omega}\), \(t^{*,\omega}\) and \(x^{*,\omega}\) for all \(\omega \in \Omega\) the same, and replace the \(t_i^*\) by \(\tilde{t}_i\) for all \(i \in \tilde{I}\) without violating any constraints.
+This yields another feasible solution which has a smaller value of \(t_T^*\) since \(T \in \tilde{I}, \tilde{t}_T = T_{\max} < t_T^*\).
+Therefore the new objective value obtained by this feasible solution is smaller, which contradicts the assumption that \((t^*,x^*,G^{*,\cdot},t^{*,\cdot},x^{*,\cdot})\) is an optimal solution.
+			%\tcb{I think the statement of the proposition is correct, but I don't think the proof is valid.
+The objective function of model~\eqref{prob:extensive} is $p^0 t_T + \sum_{\omega \in \Omega} p^\omega t_T^\omega$.
+Your proof is making an argument based on $t_T^*$ being the objective function value rather than the {\em expected} duration.
+The $d_{ik}^\omega$ values can be negative and so the expected duration isn't $T_{\max}$.}
+	\end{proof}}
+	\noi For simplicity of exposition, we use a uniform upper bound on every \(t_i\) for \(i \in I\) as \(T_{\max} = H^{|\Omega|} + t_T^0\).
+While Proposition~\ref{prop:bounds} bounds the start-time variables, \(t_i,\ \forall i \in I\), to the interval \([0,T_{\max}]\),
+	%, precedence relationships between activities allow for further tightening of the bounds, and 
+	the $y$-variables of~\eqref{cons:yCons} allow for tighter bounds.   
+	%The benefit of setting up the \(y\) variables is to obtain tighter bounds for \(t_i\) than the generic bounds \([0,T_{\max}]\) in Proposition~\ref{prop:bounds}. 
+	Given a partition for each activity and given a first-stage solution with \(\hat{y}_i^{q}, \forall i \in I, q \in \cQ_i \), we can replace 
+	%the big-\(M\) in 
+	constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} with:
+	%of the scenario with moderate \(M_i^{\omega,+}\) and \(M_i^{\omega,-}\) because introducing variables \(y\) gives us better bounds on \(t_i\):
+	%	\begin{subequations}
+	%		\begin{align}
+	%			& M_i^{\omega,+} = \sum_{q \in \cQ_i} \bar{H}^q \hat{y}_i^q - H^\omega\\
+	%			& M_i^{\omega,-} = H^\omega - \sum_{q \in \cQ_i} \underbar{H}^q \hat{y}_i^q，
+	%		\end{align}
+	%	\end{subequations}
+	%	and the constraints~\eqref{cons:sG1} and~\eqref{cons:sG2} become:
 	\begin{subequations} \label{cons:newBoundsm}
 		\begin{align}
-		H^\omega + G_i \left(\sum_{q \in \mathcal{Q}_i} \bar{H}^q \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
-		H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
-		\end{align}
-	\end{subequations}
-	The multiplication of \(G_i \hat{y}_i^q\) makes the dual of subproblem no longer linear of \(y\).
-To fix this, since \(\hat{y}_i^q\) is binary and \(G_i\) for all \(i \in I, q \in \mathcal{Q}_i\), we can introduce variables \(F_i^q\) to linearize the bilinear term and rewrite constraints~\eqref{cons:newBoundsm} as follows:
+		H^\omega + G_i \left(\sum_{q \in \cQ_i} \bar{H}^q \hat{y}_i^q - H^\omega \right) \geq \hat{t}_i \qquad \qquad \forall i \in I\\
+		H^\omega - (1 - G_i) \left(H^\omega - \sum_{q \in \cQ_i} \underbar{H}^q \hat{y}_i^q \right) \leq \hat{t}_i \qquad \qquad \forall i \in I.
+		\end{align}
+	\end{subequations}
+	%	The multiplication of \(G_i \hat{y}_i^q\) makes the dual of subproblem no longer linear of \(y\). To fix this, since \(\hat{y}_i^q\) is binary and \(G_i\) for all \(i \in I, q \in \cQ_i\), we can 
+	In a first-stage solution, $\hat{y}_i^q=1$ for a specific $q$ satisfying $\underbar{H}^{q} \le \hat{t}_i \le \bar{H}^{q}$, and verifying the validity of constraints~\eqref{cons:newBoundsm} in replacing~\eqref{cons:sG1}-\eqref{cons:sG2} is straightforward by enumerating the cases \(H^\omega \in [\underbar{H}^{{q}},\bar{H}^{{q}}]\), \(H^\omega < \underbar{H}^{{q}}\), and \(H^\omega > \bar{H}^{{q}}\).
+In the degenerate case in which $H^\omega$ coincides with $\bar{H}^q$ or $\underbar{H}^q$, the corresponding constraint from~\eqref{cons:newBoundsm} is as tight as possible, i.e., a simple bound on $\hat{t}_i$ involving $H^\omega$.
+Otherwise constraints~\eqref{cons:newBoundsm} reduce to the following analog of~\eqref{cons:Grange}:
+	\begin{equation}
+	(\hat{t}_i - H^\omega) / (\bar{H}^q-H^\omega) \leq G_i \leq  (\hat{t}_i - H^\omega)/(H^\omega-\underbar{H}^q) + 1,
+	\end{equation}
+	and we see that smaller values of $\bar{H}^q$ and larger values of $\underbar{H}^q$ have the effect of tightening the big-$M$ value in constraints~\eqref{cons:Grange}.
+
+	We introduce variables \(F_i^q\) to linearize the bilinear terms, and rewrite constraints~\eqref{cons:newBoundsm} as follows:
 	\begin{subequations} \label{cons:newBoundsmlin}
-		\begin{align}
-		H^\omega + \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:FG1}\\
-		G_i H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
-		F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin1}\\
-		F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:FGlin2}\\
-		F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:FGlin3}
-		\end{align}
-	\end{subequations}
-	In the subproblem, for each activity \(i \in I\), there is only one \(\hat{q} \in \mathcal{Q}_i\) such that \(\hat{y}_i^{\hat{q}} = 1\), which means \(\hat{t}_i \in 
+		\begin{eqnarray}
+		&&\sum_{q \in \cQ_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i- H^\omega \qquad \qquad \forall i \in I \label{cons:FG1}\\
+		&&H^\omega G_i  - \sum_{q \in \cQ_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \cQ_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:FG2}\\
+		&&F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \cQ_i \label{cons:FGlin1}\\
+		&&F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \cQ_i \label{cons:FGlin2}\\
+		&&F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \cQ_i. \label{cons:FGlin3}
+		\end{eqnarray}
+	\end{subequations}
+
+	\begin{comment}
+	In the subproblem, for each activity \(i \in I\), there is only one \(\hat{q} \in \cQ_i\) such that \(\hat{y}_i^{\hat{q}} = 1\), which means \(\hat{t}_i \in 
 	%[H^{\underbar{\omega}^{\hat{q}}},H^{\bar{\omega}^{\hat{q}}}]\). 
@@
 When \(\hat{t}_i < H^\omega\), the upper bound decreases and the lower bound is \(0\).
-Therefore, the feasible range of \(G_i\) for each \(i \in I\) shrinks, which achieves the goal to tighten the subproblem relaxation.
+Therefore, the feasible range of \(G_i\) for each \(i \in I\) shrinks, the subproblem relaxation is tightened.
 	\item 
@@
 	\end{enumerate}
-	The tightened constraints~\eqref{cons:newBoundsm} is shown to have validity and effectiveness properties. However, for the latter two situations, 
+	The tightened constraints~\eqref{cons:newBoundsm} is shown to have validity and effectiveness properties. 
+	\end{comment}
+
+	%	However, for the latter two situations, 
 	%\(H^\omega < H^{\underbar{\omega}^{\hat{q}}}\) and \(H^\omega > H^{\bar{\omega}^{\hat{q}}}\), 
-	\(H^\omega < \underbar{H}^{\hat{q}}\) and \(H^\omega > \bar{H}^{\hat{q}}\), 
-	\(G_i\) can still take fractional value.
-We further tighten the formulation by adding two constraints involving \(y\), such that if the subproblems belonging to those two situations, \(G_i\) can be fixed as either \(0\) or \(1\).
-For scenario \(\omega \in \Omega\), suppose solving the master problem provides the solution \(\hat{y}_i^q, \forall i \in I, q \in \mathcal{Q}_i\), we have:
+	%	\(H^\omega < \underbar{H}^{\hat{q}}\) and \(H^\omega > \bar{H}^{\hat{q}}\), 
+	%	\(G_i\) can still take fractional value. 
+	We can further tighten the formulation by adding two constraints involving \(y\) that cover cases when \(G_i\) can be fixed to \(0\) or \(1\).
+Again given a partition of each activity and a first-stage solution \(\hat{y}_i^q, \forall i \in I, q \in \cQ_i\), we have:
 	\begin{equation}\label{cons:subyG}
-	%\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
-	\sum_{q \in \mathcal{Q}_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q \qquad \forall i \in I 
+	%\sum_{q \in \cQ_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \cQ_i, H^\omega \geq H^{\bar{\omega}^q}} \hat{y}_i^q \qquad \forall i \in I 
+	\sum_{q \in \cQ_i, H^\omega {\leq} \underbar{H}^q} \hat{y}_i^q \leq G_i \leq 1 - \sum_{q \in \cQ_i, H^\omega {\geq} \bar{H}^q} \hat{y}_i^q \qquad \forall i \in I.
 	\end{equation}
+	\tcr{
+		%Do one or the other or both of $H^\omega \leq \underbar{H}^q$ and $H^\omega \geq \bar{H}^q$ need to be {\em strict} inequalities?
+		%Imagine the case in which the interval is $\underbar{H}^q=\bar{H}^q=H^\omega$ then we're infeasible for $\omega$.
+		%If $t_i=H^\omega$ for some $i$ and $\omega$ then $G_i^\omega$ has a choice; i.e., it can choose to either declare activity $i$'s start time to be before or after the disruption.
+Suppose we have the finest necessary partition in place.
+The way that constraints~\eqref{cons:yCons} are written, the $y$-variables have the same choice.
+If $t_i=H^2$ then the $y$-variables can either choose to associate $t_i$ with interval $[H^1,H^2]$ or with interval $[H^2,H^3]$.
+	}
+	{For the case in which \(H^\omega \in (\underbar{H}^q,\bar{H}^q)\) for the $q$ with $\hat{y}_i^q=1$, constraint~\eqref{cons:subyG} adds no restriction, but for the cases in which \(H^\omega \le \underbar{H}^q\) and \(H^\omega \ge \bar{H}^q\), $G_i$ is forced to $1$ and $0$, respectively.}
+	\begin{comment}
 	Again we check the validity and the effectiveness result of constraints~\eqref{cons:subyG} for the three situations listed above:
@@
 	the lower bound is \(1\) since the summation term, 
-		%\(\sum_{q \in \mathcal{Q}_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), 
-		\(\sum_{q \in \mathcal{Q}_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), 
+	%\(\sum_{q \in \cQ_i, H^\omega \leq H^{\underbar{\omega}^q}} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), 
+	\(\sum_{q \in \cQ_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), 
 	which forces \(G_i = 1\). This matches the logic since \(\hat{t}_i \geq H^\omega\).
 	\item 
-		\(H^\omega > \bar{H}^{\hat{q}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \mathcal{Q}_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
+	\(H^\omega > \bar{H}^{\hat{q}}\): the upper bound is \(1\) since the summation term, \(\sum_{q \in \cQ_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q\), includes \(y_i^{\hat{q}}\), which forces \(G_i = 0\).
 This matches the logic since \(\hat{t}_i \leq H^\omega\).
 	\end{enumerate}
-	With the addition of constraints~\eqref{cons:newBoundsmlin} and~\eqref{cons:subyG} in the subproblems, we present the tightened version of subproblems as follows: 
+	\end{comment}	
+	\subsection{Partition-based Decomposition Method} \label{subsec:partition}
+	% 
+	% As we refine the partition of \(t\)-space, we can generate tightened Benders' cuts to approximate the recourse function. 
+	% %, we can determine the value of \(G_i\) in many subproblems, which strengthens the Benders' cuts.\\
+
+	Our decomposition algorithm to solve model~\eqref{prob:extensive} iteratively partitions the continuous feasible region of the first-stage $t$-variables by introducing binary variables that facilitate tighter optimality cuts.
+With the addition of constraints~\eqref{cons:newBoundsmlin} and~\eqref{cons:subyG}, the tightened subproblem is:
 	\begin{subequations}
@@
 		\begin{align}
-		(S_{\mathcal{P}}^\omega) \qquad f^\omega_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
-		\text{s.t.} \quad & \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i - H^\omega \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
-		& H^\omega G_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
-		& F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin1t}\\
-		& F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i \label{cons:sFGlin2t}\\
-		& F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i. \label{cons:sFGlin3t}\\
-		& G_i \geq \sum_{q \in \mathcal{Q}_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
-		& G_i \leq 1 - \sum_{q \in \mathcal{Q}_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG2t}\\
-		& \text{Constraints~\eqref{cons:stG1}-\eqref{cons:subH}}\\
-		& 0 \leq x_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
-		& 0 \leq z_{ij} \leq 1 \qquad \qquad \forall \,i \in I, j \in J_i\\
-		& 0 \leq F_i^q \leq 1 \qquad \qquad \forall \,i \in I, q \in \mathcal{Q}_i\\
+		(S_{\cP}^\omega) \qquad f^\omega_{\cP}(\hat{t},\hat{x},\hat{y}) = \min \quad & t_T \\
+		\text{s.t.} \quad & \sum_{q \in \cQ_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i - H^\omega \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
+		& H^\omega G_i - \sum_{q \in \cQ_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \cQ_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\
+		& F_i^q \leq G_i \qquad \qquad \forall i \in I, q \in \cQ_i \label{cons:sFGlin1t}\\
+		& F_i^q \leq \hat{y}_i^q \qquad \qquad \forall i \in I, q \in \cQ_i \label{cons:sFGlin2t}\\
+		& F_i^q \geq G_i + \hat{y}_i^q - 1 \qquad \qquad \forall i \in I, q \in \cQ_i. \label{cons:sFGlin3t}\\
+		& G_i \geq \sum_{q \in \cQ_i, H^\omega \leq \underbar{H}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG1t}\\
+		& G_i \leq 1 - \sum_{q \in \cQ_i, H^\omega \geq \bar{H}^q} \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:syG2t}\\
+		& \text{constraints~\eqref{cons:stG1}-\eqref{cons:subzbounds}} \\
+		& 0 \leq F_i^q \leq 1 \qquad \qquad \forall \,i \in I, q \in \cQ_i\\
 		& 0 \leq G_i \leq 1. \qquad \qquad \forall \,i \in I. \label{cons:G01t}
@@
 	\end{subequations}
-	Suppose we solve the subproblems \((S_{\mathcal{P}}^\omega)\) for every \(\omega \in \Omega\) and generate a linear cut indexed by \(\ell\), where coefficients \(\pi,\lambda\) and \(\gamma\) can be calculated based on the dual variables obtained:
+	We express $(S_{\cP}^\omega)$ in LP relaxation form, excluding constraints~\eqref{cons:subInt}.
+Let $\ell$ denote the iteration of the decomposition algorithm, and $(\hat{t}^\ell,\hat{x}^\ell,\hat{y}^\ell)$ denote a given first-stage decision.
+We solve \((S_{\cP}^\omega)\) for each \(\omega \in \Omega\) and construct an optimality cut of the form:
 	\begin{equation} \label{cons:cut}
-	\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i,q}^{\omega,\ell} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
+	\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \cQ^{\ell}_i} {\gamma_{i}^{\omega,\ell,q}} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right).
 	\end{equation}
-	Since the subproblem is a linear relaxation, \(\theta^\omega\) is a lower approximation of \(f^\omega\) for the current partition.
-However, since the validity result depends on the current partition, the cut needs to be modified once the partition is updated to retain the validity result.
-We assume that the update only refines the partition for each \(i \in I\):
+	Here, $\theta^\omega$ is a continuous decision variable that forms an outer-linearization of $f^\omega_{\cP}(t,x,y)$; parameter~$v^{\omega,\ell}$ is the optimal value of \((S_{\cP}^\omega)\) at $(\hat{t}^\ell,\hat{x}^\ell,\hat{y}^\ell)$; and, coefficients \(\pi,\lambda\) and \(\gamma\) are appropriate sums of dual variables from the LP relaxation---e.g., $\pi_i^{\omega,\ell}$ involves dual variables from constraints~\eqref{cons:stG1}-\eqref{cons:stG2} and~\eqref{cons:sFG1t}-\eqref{cons:sFG2t}.
+	Since we solve a linear relaxation, \(\theta^\omega\) is a lower bound on \(f^\omega(\hat{t}^\ell,\hat{x}^\ell,\hat{y}^\ell)\).
+However, the cut needs to be modified once the partition is updated to maintain validity, and we assume that the update only refines the partition for each \(i \in I\):
 	\begin{definition} \label{definition:refinement}
-		For two partitions \(\mathcal{P}^1_i\) and \(\mathcal{P}^2_i\), indexed by \(\mathcal{Q}^1_i\) and \(\mathcal{Q}^2_i\) respectively, where \(\mathcal{P}^2_i\) is a refinement of \(\mathcal{P}^1_i\), we have:
+		For two partitions \(\cP^1_i\) and \(\cP^2_i\), indexed by \(\cQ^1_i\) and \(\cQ^2_i\), respectively, we say \(\cP^2_i\) is a {\em refinement} of \(\cP^1_i\) provided:
 		\begin{equation*}
-		\forall q^2 \in \mathcal{Q}^2_i, \exists q^1 \in \mathcal{Q}^1_i \text{ s.t. } \bar{H}^{q^1} \geq \bar{H}^{q^2} \text{ and } \underbar{H}^{q^1} \leq \underbar{H}^{q^1}.
+		\forall q^2 \in \cQ^2_i, \exists q^1 \in \cQ^1_i \text{ s.t. } \bar{H}^{q^1} \geq \bar{H}^{q^2} \text{ and } {\underbar{H}^{q^1} \leq \underbar{H}^{q^2}}.
 		\end{equation*}
 	\end{definition}
-	\noi Suppose at the current iteration for each \(i \in I\), the partition is \(\mathcal{P}_i\) indexed by \(\mathcal{Q}_i\), and this partition is updated from past partitions by only a sequence of refinement defined in Definition~\ref{definition:refinement}.
-Therefore, we can find a set of elements of the current partition,  \(\mathcal{P}_i\) refined from the \(q\)-th element in the partition \(\mathcal{P}^\ell_i\) in the previous iteration \(\ell\).
-We name such set as a ``descendant set", denoted by \(\Delta_i(\ell,q)\).
-Cut~\eqref{cons:cut} can then be updated to the following form so that the \(y\) variable has a proper dimension matching the current partition:
+	\noi At the current iteration for each \(i \in I\), let the partition \(\cP_i\) be indexed by \(\cQ_i\), and assume this partition is formed from earlier partitions by a sequence of refinements satisfying Definition~\ref{definition:refinement}.
+We can then find a set of intervals in the current partition,  \(\cP_i\), whose union is the \(q\)-th interval in partition \(\cP^\ell_i\) from previous iteration \(\ell\).
+We index such a {\em descendant set} by \(\Delta_i(\ell,q)\).
+Cut~\eqref{cons:cut} can then be updated to the following form:
 	\begin{align} \label{cons:updatedcut}
-	& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
-	& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad \forall \ell = 1,2, \dots.
-	\end{align}
-	We show that, given a partition, \(\mathcal{P}\), which is updated from sequential refinement, \(\mathcal{P}^\ell, \ell = 1,2,\dots\), the cut~\eqref{cons:updatedcut} is a valid lower approximation for function \(g\):
+	& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + %\nonumber \\
+	%& \qquad 
+	\sum_{i \in I} \sum_{q \in \cQ^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{q^\prime \in \Delta_i(\ell,q)} y_i^{q^\prime} - \hat{y}_i^{q,\ell} \right). %\qquad \forall \ell = 1,2, \dots.
+	\end{align}
+	We show that given a partition, \(\cP=\bigtimes_{i \in I} \cP_i\), which is updated by sequential refinement from a previous partition, \(\cP^\ell = \bigtimes_{i \in I} \cP_i^\ell\), the optimality cut~\eqref{cons:updatedcut} is a valid lower approximation for~$f^\omega_{\cP}(t,x,y)$.
 	\begin{proposition} \label{prop:validity}
-		Suppose we have a partition, \(\mathcal{P}\), which is indexed by sets \(\mathcal{Q}\), and the sequence of partitions, \(\{\mathcal{P}^\ell\}_{\ell = 1}\), each of which is indexed by sets \(\mathcal{Q}^\ell\).
-Assuming \(\mathcal{P}\) is a refinement of \(\mathcal{P}^\ell\) for every \(\ell = 1,2, \dots\), for any \(\omega \in \Omega\), we have
+		For each $i \in I$, suppose we have a partition, \(\cP_i\), indexed by \(\cQ_i\), which is a refinement of \(\cP_i^\ell\), indexed by \(\cQ_i^\ell\). Then at any given feasible \((t,x,y)\) we have
+		{
+			\scalefont{0.950}		
 			\begin{align} \label{cons:validlb}
-		&f^\omega_{\mathcal{P}}(t,x,y) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \nonumber \\
-		& \qquad \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad \forall \ell = 1,2, \dots.
-		\end{align}
-		at any given feasible \((t,x,y)\).
+			&f^\omega_{\cP}(t,x,y) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + %\nonumber \\
+			%& \qquad \qquad 
+			\sum_{i \in I} \sum_{q \in \cQ^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{q^\prime \in \Delta_i(\ell,q)} y_i^{q^\prime} - \hat{y}_i^{q,\ell} \right). % \qquad \forall \ell = 1,2, \dots. 
+			\end{align}
+		}
 	\end{proposition}
 	\begin{proof}
-		We denote the recourse function corresponding to the partition \(\mathcal{P}^{\ell}\) as \(f^\omega_{\mathcal{P}^\ell}(t,x,y)\), where \(y\) has the correct dimension according to \(\mathcal{P}^\ell\).
-We first prove that
+		We denote the recourse function corresponding to partition \(\cP^{\ell}\) by \(f^\omega_{\cP^\ell}(t,x,y)\), where \(y\) has the correct dimension according to \(\cP^\ell\). We first show that 
 		\begin{equation} \label{cons:gglb}
-		f^\omega_{\mathcal{P}}(t,x,y) \geq f^{\omega}_{\mathcal{P}^\ell}(t,x,\tilde{y}) \qquad \forall \ell = 1,2,\dots
+		f^\omega_{\cP}(t,x,y) \geq f^{\omega}_{\cP^\ell}(t,x,\tilde{y}),
 		\end{equation}
-		where \[\tilde{y}_i^{q} =  \sum_{\tilde{q} \in \Delta_i(\ell,q)} y_i^{\tilde{q}} \qquad  \forall i \in I, q \in \mathcal{Q}^\ell_i. \]
-		Suppose for an \(\omega \in \Omega\) and a \((t,x,y)\), we solve the problem \(S_{\mathcal{P}}^\omega\) and obtain the optimal solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},F^{\omega,*})\).
-It is easy to see that by transforming \(F^{\omega,*}\) to \(\tilde{F}^{\omega,*}\) with \[\tilde{F}^{\omega,*,q}_i = \sum_{\tilde{q} \in \Delta_i(\ell,q) }F_i^{\omega,*,\tilde{q}} \qquad  \forall i \in I, q \in \mathcal{Q}^\ell_i;\]
-		we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\).
+		where 
+		\begin{equation}\label{eqn:y_ytilde_sub}
+		\tilde{y}_i^{q} =  \sum_{q^\prime \in \Delta_i(\ell,q)} y_i^{q^\prime} \qquad  \forall i \in I, q \in \cQ^\ell_i.
+		\end{equation}
+		Suppose for given \((t,x,y)\), we solve (\(S_{\cP}^\omega\)) and obtain an optimal solution \((t^{\omega},x^{\omega},G^{\omega},F^{\omega})\).
+We then form \[\tilde{F}^{\omega,q}_i = \sum_{q^\prime \in \Delta_i(\ell,q) }F_i^{\omega,q^\prime} \qquad  \forall i \in I, q \in \cQ^\ell_i, \]
+		and we obtain a feasible solution \((t^{\omega},x^{\omega},G^{\omega},\tilde{F}^{\omega})\) to subproblem (\(S_{\cP^\ell}^\omega\)).
 Therefore, inequality~\eqref{cons:gglb} holds.
-Furthermore, the cut generated at partition \(\mathcal{P}^\ell\) is
-		\[\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right),\]
+Furthermore, the cut generated under partition \(\cP^\ell\) is
+		\[\theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \cQ^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( y_i^{q} - \hat{y}_i^{q,\ell} \right),\]
 		which means that for any feasible \((t,x,\tilde{y})\), we have 
 		\begin{equation} \label{cons:validglb}
-		f^\omega_{\mathcal{P}^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
+		f^\omega_{\cP^\ell}(t,x,\tilde{y}) \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) + \sum_{i \in I} \sum_{q \in \cQ^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \tilde{y}_i^{q} - \hat{y}_i^{q,\ell} \right).
 		\end{equation}
-		By substituting \(\tilde{y}\) by \(y\) and combining inequalities~\eqref{cons:gglb} and~\eqref{cons:validglb}, we obtain the result of~\eqref{cons:validlb}.
+		Using equation~\eqref{eqn:y_ytilde_sub}, we replace \(\tilde{y}\) by \(y\), and combine inequalities~\eqref{cons:gglb} and~\eqref{cons:validglb} to obtain~\eqref{cons:validlb}.
 	\end{proof}
-	\noi Proposition~\ref{prop:validity} states that if we perform a proper modification on the \(y\) variables to all cuts generated in the past, the modified cuts~\eqref{cons:updatedcut} will be a valid lower approximation for the current recourse function.
-Therefore, we incorporate the modified cuts~\eqref{cons:updatedcut} in our master problem, given a partition \(\mathcal{P}\) indexed by \(\mathcal{Q}\), which is shown as follows:
+	\noi Proposition~\ref{prop:validity} states that by properly modifying the \(y\)-variables in cuts generated under earlier partitions, the resulting cuts~\eqref{cons:updatedcut} are valid in the sense of providing a lower approximation on the LP relaxation of the recourse function.
+Therefore, we incorporate the modified cuts~\eqref{cons:updatedcut} in the following master problem, given a partition \(\cP\), which is indexed by \(\cQ\):
 	\begin{subequations} \label{prob:masterTightened}
 		\begin{align}
-		(M_{\mathcal{P}}) \quad z_{\mathcal{P}}^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
-		\text{s.t.} \quad & t_k - t_i \geq D_{i}(1 - \sum_{j \in J_i} x_{ij} e_{ij}) \qquad \qquad \forall \,i \in I, (i,k) \in \mathcal{A} \label{cons:MpSep}\\
+		(M_{\cP}) \quad z_{\cP}^* = \min \quad &p^0 t_T + \sum_{\omega \in \Omega} p^\omega \theta^{\omega}\\
+		\text{s.t.} \quad & t_k - t_i \geq D_{ik} \left ( 1 - \sum_{j \in J_i} e_{ij} x_{ij} \right ) \qquad \qquad \forall (i,k) \in \cA \label{cons:MpSep}\\
 		& \sum_{i \in I} \sum_{j \in J_i} b_{ij}x_{ij} \leq B  \label{cons:MpBudget}\\
 		& \sum_{j \in J_i} x_{ij} \leq 1  \qquad \qquad \forall \,i \in I \label{cons:MpSingleBudget}\\
-		& \sum_{q \in \mathcal{Q}_i} H^{\underbar{\omega}^q} y_i^{q} \leq t_i \leq \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} y_i^{q} \qquad \qquad \forall i \in I\\
-		& \sum_{q \in \mathcal{Q}_i} y^q_i = 1 \qquad \qquad \forall i \in I \label{cons:MpY1}\\
+		& \sum_{q \in \cQ_i} \underbar{H}^{q} y_i^{q} \leq t_i \leq \sum_{q \in \cQ_i} \bar{H}^{q} y_i^{q} \qquad \qquad \forall i \in I \label{cons:which_interval_for_t} \\
+		& \sum_{q \in \cQ_i} y^q_i = 1 \qquad \qquad \forall i \in I \label{cons:MpY1}\\
 		& \theta^\omega \geq v^{\omega,\ell} + \sum_{i \in I} \pi_i^{\omega,\ell} (t_i - \hat{t}_i^{\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,\ell} (x_{ij} - \hat{x}_{ij}^{\ell}) \nonumber \\
-		&\qquad + \sum_{i \in I} \sum_{q \in \mathcal{Q}^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{\tilde{q} \in \Delta_i(\ell,q)}y_i^{\tilde{q}} - \hat{y}_i^{q,\ell} \right) \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots\\
-		& y_i^q \in \{0,1\} \qquad \qquad \forall i \in I, q \in \mathcal{Q}_i\\
+		&\qquad + \sum_{i \in I} \sum_{q \in \cQ^{\ell}_i} \gamma_{i}^{\omega,\ell,q} \left( \sum_{q' \in \Delta_i(\ell,q)}y_i^{q'} - \hat{y}_i^{q,\ell} \right) \qquad  \forall \omega \in \Omega, \ell = 1, 2, \dots, L \label{cons:master_the_cuts} \\
+		& y_i^q \in \{0,1\} \qquad \qquad \forall i \in I, q \in \cQ_i \label{cons:binary_y_variables} \\
 		& t_i \geq 0 \qquad \qquad \forall \,i \in I\\
@@
 	\end{subequations}
-	We can see that if we keep refining the partition, the generated cuts will become tighter and we will be able to provide an improving lower bound as it progresses.
-We refine the partition by selecting the element of \(\mathcal{P}^\ell\) indexed by \(q\), \(q \in \mathcal{Q}^\ell_i\), for each activity \(i \in I\), where for some scenarios \(\omega \in \Omega\) with \(H^\omega \in [\underbar{H}^q,\bar{H}^q]\), \(G_i^\omega\) has a fractional value, and divide the interval into three subintervals, each covering approximately the same number of scenarios.
-The decomposition algorithm is presented as follows:\\
-	\begin{algorithm}
-		\caption{Partition Based Decomposition algorithm to solve problem~\eqref{prob:extensive}}
+	As we refine the partitions, the generated cuts become tighter and we provide tighter lower bounds on model~\eqref{prob:extensive}'s optimal value.
+We refine the partition by selecting the interval of \(\cP_i\) for each activity \(i \in I\), where for some scenarios \(\omega \in \Omega\) with \(H^\omega \in [\underbar{H}^q,\bar{H}^q]\), \(G_i^\omega\) has a fractional value, and partition the interval {as we describe in further detail in Section~\ref{subsec:refine}}.
+The decomposition procedure is given in Algorithm~\ref{alg:Cut}.
+\\
+	\begin{algorithm}[ht]
+		\caption{Partition-based decomposition algorithm to solve model~\eqref{prob:extensive}}
 		\label{alg:Cut}
 		\begin{algorithmic}[1]
-			\State Initialize with cut iteration number \(\ell = 0\), lower bound \(LB = 0\), upper bound \(UB = +\infty\), initial partition \(\mathcal{P}^\ell\) with its indexed set \(\mathcal{Q}^\ell\), and specified tolerance parameters \(\epsilon > 0\) and \(\delta > 0\);
-			\While{\(\frac{UB - LB}{UB} > \epsilon\)} 
-			\State Solve master problem \((M_{\mathcal{P}})\) and obtain solution \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and optimal value \(z_{P}^*\);
-			\If{\(z_{P}^* > LB\)}
-			\State Update \(LB = z_{P}^*\);
+			\State Initialize cut iteration number \(\ell = 0\), lower bound \(LB = 0\), upper bound \(UB = +\infty\), initial partition \(\cP^\ell\) with its indexed set \(\cQ^\ell\), and tolerance parameters \( \epsilon \ge \delta \ge 0\);
+			\While{\(\frac{UB - LB}{UB} > \epsilon\)} \label{alg:while_step}
+			\State Solve \((M_{\cP})\) and obtain solution \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and optimal value \(z_{\cP}^*\);
+			\If{\(z_{\cP}^* > LB\)}
+			\State Update \(LB = z_{\cP}^*\);
 			\EndIf
-			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t}^{\ell},\hat{x}^{\ell})\). 
-			\State Calculate \(z^* = p^0 \hat{t}^\ell_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^\ell,\hat{x}^\ell)\)
-			\If{\(z^* < UB\)} 
-			\State Update \(UB := z^*\) and record the best incumbent solution as \(t^* = \hat{t}^\ell, x^* = \hat{x}^\ell\) and \(y^* = \hat{y}^\ell\);
+			\State For each \(\omega \in \Omega\), solve \((S^\omega)\) and obtain \(f^{\omega}(\hat{t}^{\ell},\hat{x}^{\ell})\) and \(\hat{G}^\ell\); 
+			\State Calculate \(\bar{z} = p^0 \hat{t}^\ell_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^\ell,\hat{x}^\ell)\); \label{alg:upper_bound_calculation} 
+			\If{\(\bar{z} < UB\)} 
+			\State Update \(UB =\bar{z}\) and incumbent solution as \(t^* = \hat{t}^\ell, x^* = \hat{x}^\ell\) and \(G^* = \hat{G}^\ell\);
 			\EndIf
-			\State For each \(\omega \in \Omega\), solve problem \((S_{\mathcal{P}}^\omega)\) given \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}, \hat{\theta}^{\ell}\) and obtain optimal value \(v^{\omega,\ell}\) and coefficients \(\pi^{\omega,\ell}, \lambda^{\omega,\ell}, \gamma^{\omega,\ell}\);
-			\If{\(z^*_{\mathcal{P}} < p^0 \hat{t}_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
-			\State Add the cuts of form~\eqref{cons:cut} to the master problem;
-			\State Keep \(\mathcal{P}^{\ell + 1} = \mathcal{P}^\ell\) and \(\mathcal{Q}^{\ell + 1} = \mathcal{Q}^\ell\); 
-			\State Update \(\ell = \ell + 1\);
+			\For{each \(\omega \in \Omega\)}
+			\State solve \((S_{\cP}^\omega)\) given \(\hat{t}^{\ell}, \hat{x}^{\ell}, \hat{y}^{\ell}\) and obtain optimal value \(v^{\omega,\ell}\) and \(\pi^{\omega,\ell}, \lambda^{\omega,\ell}, \gamma^{\omega,\ell}\); \label{alg:step_to_solve_LP_sub}
+			\If{\(\hat{\theta}^{\omega,\ell} < v^{\omega,\ell} - \delta\)}
+			add cut of form~\eqref{cons:cut} to \((M_{\cP})\);
+			\EndIf
+			\EndFor
+			\State Let \(\ell = \ell + 1\);
+			%\State For each \(\omega \in \Omega\), 
+			%\If{\(\bar{z}_{\cP} < p^0 \hat{t}^\ell_T + \sum_{\omega \in \Omega} p^\omega v^{\omega,\ell} - \delta\)}
+			\If{there are cuts added}
+			%\State Add \tcr{nonredundant} cuts of form~\eqref{cons:cut} to \((M_{\cP})\);
+			\State Let \(\cP^{\ell + 1} = \cP^\ell\) and \(\cQ^{\ell + 1} = \cQ^\ell\); 
 			\Else
-			\State Refine the partition and obtain the new partition \(\mathcal{P}^{\ell + 1}\) and its indexed sets \(\mathcal{Q}^{\ell + 1}\);
-			\State Update \(\ell = \ell + 1\);
-			\State Update the previously generated cuts in the master problem to the form of~\eqref{cons:updatedcut};
+			\State Refine the partition and obtain the new partition \(\cP^{\ell + 1}\) and its indexed sets \(\cQ^{\ell + 1}\); \label{alg:refine_partition}
+			%			\State Let \(\ell = \ell + 1\);
+			\State Update previously generated cuts in \(\cP^\ell\) to the form of~\eqref{cons:updatedcut};
 			\EndIf
@@
 			\EndWhile{\textbf{end while}}
-			\State Output \(UB\) as the optimal value of model~\eqref{prob:extensive}, and \(t^*, x^*\) as the optimal solution.
+			\State Output \(UB\) as the $\epsilon$-optimal value of model~\eqref{prob:extensive}, and \((t^*, x^*, G^*)\) as the $\epsilon$-optimal solution.
 		\end{algorithmic}
 	\end{algorithm}
+	%	\tcr{Do we need to make some assumption on $\delta$ relative to $\epsilon$? Suppose $\delta$ is huge; we'll never add a cut.}
 	\noi We prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
 Since every partition update is a refinement and we have a finite set of scenario \(\Omega\), we can prove the finite convergence of Algorithm~\ref{alg:Cut} as long as with the finest partition we reach the optimum of problem~\eqref{prob:extensive}.
+	%	We let $\cH=\{H^\omega \, | \, \omega \in \Omega \}$ denote the set of (distinct) disruption times.
+When a specific disruption time has scenarios with multiple magnitudes we have $|\cH| < |\Omega|$.
+
+	\newpage
+
 	\begin{proposition} \label{prop:finestPar}
-		If a partition \(\hat{\mathcal{P}}\) has indexed sets \(\hat{\mathcal{Q}}\) and for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{\omega}^q = \underbar{\omega}^q + 1,\ \forall q \in \hat{\mathcal{Q}}_i\), we have \[z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y),\]
+		Assume that the realizations of $H^\omega$, $\omega \in \Omega$, are distinct.
+Assume that for each partition, \({\cP}_i\) indexed by $\cQ_i$, and for each $H^\omega$ we have $H^\omega=\bar{H}^q$ for some $q \in \cQ_i$, i.e., $|\cQ_i|=|\Omega|+1$ so that each partition is as fine as possible.
+Then
+		\begin{equation}\label{eqn:proposition_equivalent}
+		z^* = \min_{(t,x,y) \in \mathbb{X}}\ p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega_{{\cP}}(t,x,y),
+		\end{equation}
 		where 
@@
 		\begin{aligned}
-		& \text{Constraints } \eqref{cons:MpSep}-\eqref{cons:MpY1}\\ 
-		&y_i^q \in \{0,1\} \qquad \forall i \in I, q \in \hat{\mathcal{Q}}_i\\
+		& \text{constraints } \eqref{cons:MpSep}\mbox{-}\eqref{cons:MpY1}\\ 
+		&y_i^q \in \{0,1\} \qquad \forall i \in I, q \in {\cQ}_i\\
 		& t_i \geq 0 \qquad \forall i \in I\\
@@
 		\end{aligned}
-		\right. \right\}.
+		\right. \right\}
 		\end{equation*}
+		and where $z^*$ is the optimal value of model~\eqref{prob:extensive}.
 	\end{proposition}
 	\begin{proof}
-		First we can consider the subproblem \((S_\mathcal{P}^\omega)\) as a partial linear relaxation of the original extensive formulation. So \(z^* \leq z^*_\mathcal{P}\) is automatically true.\\
-		\newline
-		Next we prove that, given the partition in Proposition~\ref{prop:finestPar}, we can construct a feasible solution, \((t^*,x^*,G^*)\), to the extensive formulation~\eqref{prob:extensive} with the same objective value from the optimal solution, \((\hat{t},\hat{x},\hat{y})\), to the problem
-		\[\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y).\]
+		We can formulate an extensive form for model~\eqref{eqn:proposition_equivalent}, i.e., an analog of model~\eqref{prob:extensive}, using $\mathbb{X}$ and model~\eqref{prob:subTightened}, where the decision variables of model~\eqref{prob:subTightened} are now also indexed by $\omega$.
+Let $\Omega=\{1,2,\ldots,|\Omega|\}$ so that the realizations of the disruption times are given by $H^1 < H^2 < \cdots < H^{|\Omega|}$.
+By Definition~\ref{definition:partition}, under the hypothesis of the proposition, the intervals of each partition are given by the finest partition, $[H^0,H^1], [H^1,H^2], \ldots, [H^{|\Omega|-1},H^{|\Omega|}], [H^{|\Omega|},H^{|\Omega|+1}]$, which we can index by $q=1,2,\ldots,|\Omega|,|\Omega|+1$, where $H^0=0$ and $H^{|\Omega|+1}=T_{\max}$.
+Under the assumed partition, constraints~\eqref{cons:syG1t}-\eqref{cons:syG2t} in the extensive form of~\eqref{eqn:proposition_equivalent} reduce to
+		\begin{equation}\label{eqn:one_to_one_formula}
+		\sum_{q=\omega+1}^{|\Omega|+1} y_i^{q} \le G_i^\omega \le 1 - \left ( \sum_{q=1}^\omega y_i^{q} \right ), \forall i \in I, \omega \in \Omega.
+		\end{equation}
+		Under this finest partition, there is a one-to-one mapping between the $G$- and $y$-variables under the binary restrictions imposed by models~\eqref{prob:extensive} and~\eqref{eqn:proposition_equivalent}.
+In particular,
+		\begin{equation}\label{eqn:one_to_one}
+		y_i^q=1 \ \mbox{if and only if} \  G_i^\omega=1 \  \forall \omega \ge q+1 \ \mbox{and} \ G_i^\omega=0 \ \forall \omega \le q. 
+		\end{equation}
+		Any feasible solution to model~\eqref{prob:extensive} necessarily satisfies the condition $G_i^{\omega} \le G_i^{\omega+1}$ required by~\eqref{eqn:one_to_one} via constraint~\eqref{cons:G2}.
+And, constraints~\eqref{cons:MpY1} and~\eqref{cons:binary_y_variables} ensures the $0$-$0$ or $1$-$1$ nature of the left- and right-hand side of~\eqref{eqn:one_to_one_formula}.
+By Proposition~\ref{prop:bounds} we know $t_i \in [0,T_{\max}]$, and hence this restriction imposed by model~\eqref{eqn:proposition_equivalent} is nonbinding.
+As a result, model~\eqref{prob:extensive} and the extensive form of model~\eqref{eqn:proposition_equivalent} are equivalent and yield the same optimal value.
+	\end{proof}
+	%under $F_i^{q,\omega}=G_i^\omega y_i^q$. 
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\begin{comment}
+	For a feasible solution $(t,x)$ to model~\eqref{eqn:proposition_equivalent} the additional $y$-variables associate each first-stage $t_i$ with an interval on $[0,T_{\max}]$, which is not restrictive by Proposition~\ref{prop:bounds}.
+Given $(t,x)$
+
+	Models~\eqref{prob:extensive} and~\eqref{prob:masterOri} have the same optimal value.
+For a feasible solution $(t,x)$ to model~\eqref{prob:masterOri} the additional $y$-variables associate each first-stage $t_i$ with an interval on $[0,T_{\max}]$, which is not restrictive by Proposition~\ref{prop:bounds}.
+\tcr{Subproblem~\((S_\cP^\omega)\), which defines $f^\omega_{{\cP}}(t,x,y)$, is a partial linear relaxation of the constraints of model~\eqref{prob:extensive}.} \tcb{I'm not sure this is true.
+The model defining $f^\omega_{{\cP}}(t,x,y)$ takes $y$ as input, which could be the {\em wrong} choice given $(t,x)$.} So \(z^*_\cP \leq z^*\) is automatically true.\\
+	\newline
+	Next we prove that, given the partition in~\eqref{eqn:partition}, we can construct a feasible solution, \((t^*,x^*,G^*)\), to the extensive formulation~\eqref{prob:extensive} with the same objective value from the optimal solution, \((\hat{t},\hat{x},\hat{y})\), to the problem
+	\[\min_{(t,x,y) \in \mathbb{X}}\ p^0 t_T + \sum_{\omega \in \Omega} p^\omega f^\omega_{\hat{\cP}}(t,x,y).\]
 	Suppose for \(i \in I\), we denote the index of partition where \(y\) variable takes value \(1\) as \(q_i\).
-Since \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\mathcal{Q}}_i\), either \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \leq \underbar{H}^q\}\) or \(q_i \in \{q \in \hat{\mathcal{Q}}_i \mid H^\omega \geq \bar{H}^q\}\) is true.
-Thus, constraints~\eqref{cons:syG1t} and~\eqref{cons:syG2t} enforce that \(G_i\) in the problem \((S_{\hat{\mathcal{P}}}^\omega)\) takes binary value because the right-hand side expressions of those two constraints must be \(0\) or \(1\) simultaneously.
+Since \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\cQ}_i\), either \(q_i \in \{q \in \hat{\cQ}_i \mid H^\omega \leq \underbar{H}^q\}\) or \(q_i \in \{q \in \hat{\cQ}_i \mid H^\omega \geq \bar{H}^q\}\) is true.
+Thus, constraints~\eqref{cons:syG1t} and~\eqref{cons:syG2t} enforce that \(G_i\) in the problem \((S_{\hat{\cP}}^\omega)\) takes binary value because the right-hand side expressions of those two constraints must be \(0\) or \(1\) simultaneously.
 This means that although subproblems are linear programs, the integrality is implied.
-Therefore, when we obtain the optimal solution \(\hat{G}^\omega\) from solving problems \((S_{\hat{\mathcal{P}}}^\omega)\) for each \(\omega \in \Omega\), solution \((\hat{t},\hat{x},\hat{G})\) will be feasible for the extensive formulation because \((\hat{t},\hat{x},\hat{y}) \in \mathbb{X}\) and \(G\) variables satisfy the constraints~\eqref{cons:stG1}-\eqref{cons:subH} and binary constraints.
-This result is equivalent to \(z_{\hat{\mathcal{P}}}^* \geq z^*\).
-Combining the results above we conclude that \(z^* = \min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y).\)
-	\end{proof}
+Therefore, when we obtain the optimal solution \(\hat{G}^\omega\) from solving problems \((S_{\hat{\cP}}^\omega)\) for each \(\omega \in \Omega\), solution \((\hat{t},\hat{x},\hat{G})\) will be feasible for the extensive formulation because \((\hat{t},\hat{x},\hat{y}) \in \mathbb{X}\) and \(G\) variables satisfy the constraints~\eqref{cons:stG1}-\eqref{cons:subH} and binary constraints.
+This result is equivalent to \(z_{\hat{\cP}}^* \geq z^*\).
+Combining the results above we conclude that \(z^* = \min_{(t,x,y) \in \mathbb{X}}\ p^0 t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\cP}}(t,x,y).\)
+	\end{comment}	
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	\begin{theorem} \label{thm:converge}
-		Algorithm~\ref{alg:Cut} terminates in finite number of iteration for any \(\epsilon \geq 0\). 
+		Assume that the realizations of $H^\omega$, $\omega \in \Omega$, are distinct, and assume that we obtain a dual extreme-point solution to subproblem~\((S_{\cP}^\omega)\) in step~\ref{alg:step_to_solve_LP_sub} of Algorithm~\ref{alg:Cut}.
+Then, the algorithm terminates in finite number of iterations to an $\epsilon$-optimal solution to model~\eqref{prob:extensive} for any \(\epsilon \ge 0\).
 	\end{theorem}
 	\begin{proof}
-		From Proposition~\ref{prop:finestPar} we know that with the finest partition \(\hat{\mathcal{P}}\) where for each \(i \in I\), \(|\hat{\mathcal{Q}}_i| = |\Omega|\) and \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\mathcal{Q}}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\mathcal{P}}}(t,x,y)\) is equivalent to solving the extensive formulation.
+		Let $z^*$ denote the optimal value of model~\eqref{prob:extensive} or equivalently model~\eqref{prob:masterOri}.
+The value of $UB$ in the algorithm is an upper bound on $z^*$ because $(\hat{t}^\ell,\hat{x}^\ell)$ is a feasible solution, and its objective function value in model~\eqref{prob:masterOri} is evaluated in step~\ref{alg:upper_bound_calculation} of the algorithm.
+The value of $LB$ in the algorithm is a lower bound on $z^*$ because: (i)~Proposition~\ref{prop:validity} ensures that the cuts~\eqref{cons:master_the_cuts} are an outer linearizations of $f_{\cP}(t,x,y)$; inequality~\eqref{cons:gglb} in the proof of Proposition~\ref{prop:validity} shows that $f_{\cP}$ becomes tighter as the partition is refined; and, Proposition~\ref{prop:finestPar} shows that the finest partition yields a model equivalent to  model~\eqref{prob:extensive}.
+Thus, if Algorithm~\ref{alg:Cut} terminates according to step~\ref{alg:while_step} then the current incumbent is an $\epsilon$-optimal solution.
+
+		For a fixed partition, $\cP$, Algorithm~\ref{alg:Cut} can only add a finite number of new cuts because each linear program~\((S_{\cP}^\omega)\) has a finite number of dual extreme points.
+After the final iteration in which new cuts are added, partition $\cP$ is refined in step~\ref{alg:refine_partition} of the algorithm.
+Because there are a finite number of scenarios the finest possible partition, if necessary, will be obtained in a finite number of iterations.
+From Proposition~\ref{prop:finestPar} we know that with the finest partition the solution to model~\eqref{eqn:proposition_equivalent} yields an optimal solution, and we will obtain the requisite cuts~\eqref{cons:master_the_cuts} so that models~\eqref{prob:masterTightened} and~\eqref{eqn:proposition_equivalent} are equivalent in a finite number of iterations.
+		%	\(\hat{\cP}\) where for each \(i \in I\), \(|\hat{\cQ}_i| = |\Omega|\) and \(\bar{H}^q = \underbar{H}^{q + 1},\ \forall q \in \hat{\cQ}_i\), solving the problem \(\min_{(t,x,y) \in \mathbb{X}}\ t_T + \sum_{\omega \in \Omega} f^\omega_{\hat{\cP}}(t,x,y)\) is equivalent to solving the extensive formulation.
 Since there are only finite number of scenarios, it takes finite number of steps of refinement to reach the finest partition.
 \\
-		\newline
-		For each subproblem, there is only a finite number of possible values of dual variables because each corresponds to one of the finitely many different bases.
-This means that, for any partition \(\mathcal{P}\), the recourse function \(f^\omega_{\mathcal{P}}\) can be represented by finitely many linear cuts.
-Therefore, in algorithm~\ref{alg:Cut}, only a finite number of cuts are added for a finite number of partitions before \(UB = z^*\) and \(LB = z^*_{\hat{\mathcal{P}}}\) is achieved, a.k.a.
+		%		\newline
+		%		For each subproblem, there is only a finite number of possible values of dual variables because each corresponds to one of the finitely many different bases.
+This means that, for any partition \(\cP\), the recourse function \(f^\omega_{\cP}\) can be represented by finitely many linear cuts.
+Therefore, in algorithm~\ref{alg:Cut}, only a finite number of cuts are added for a finite number of partitions before \(UB = z^*\) and \(LB = z^*_{\hat{\cP}}\) is achieved, a.k.a.
 \(\frac{UB - LB}{UB} = 0\).
@@
 	\subsection{Pruning Partitions Using Bound Tightening} \label{subsec:FBBT}
-	Feasibility-based and optimization-based bound tightening has been proved powerful in mixed integer nonlinear programming to improve computational performance~\cite{belotti2012fbbt,coffrin2015strengthening,sundar2018OBBT}.
-Feasibility-based bound tightening (FBBT) process is suitable to our problem because the precedence relationships put limits on some activities that they cannot start before a certain time.
-For each activity \(i \in I\), we solve the following linear programs to identify the lower bound and the upper bound of the starting time of each activity.
+	Feasibility-based and optimization-based bound tightening schemes have been proved powerful in mixed integer nonlinear programming to improve computational performance~\citep[e.g.,][]{belotti2012fbbt,coffrin2015strengthening,sundar2018OBBT}.
+A feasibility-based bound tightening (FBBT) process is suitable for our problem because the precedence relationships limit the start times of  activities.
+We solve the following linear programs to identify the lower and upper bounds on the first-stage start time of each activity:
 	\begin{subequations} \label{prob:btminmax}
@@
 		\min/\max \quad & t_i \\
-		\text{s.t.} \quad & \eqref{cons:MSep} - \eqref{cons:Mxbounds}\\
+		\text{s.t.} \quad & \text{constraints \eqref{cons:MSep}-\eqref{cons:Mxbounds}}\\
 		& \underbar{t}_i \leq t_i \leq \bar{t}_i \qquad \forall i \in I.
@@
 	The bound tightening process starts with a set of initial bounds \(\underbar{t}_i = 0\) and \(\bar{t}_i = T_{\max}\) for each \(i \in I\).
-We solve model~\eqref{prob:btminmax} iteratively and update \(\bar{t}_i\) and \(\underbar{t}_i\) until the bounds converge respectively.\\
-	\newline
-	We run FBBT at the beginning of our decomposition method to provide the initial partition \(\mathcal{P}^0\) to start Algorithm~\ref{alg:Cut}.
-If we can tighten the bounds of some activities, for example, by branch-and-bound or heuristics, we can run FBBT to tighten the bounds for all activities, which leads to a tighter formulation of the subproblems, \(S^{\omega}_{\mathcal{P}}\).
-\\
-
-	\subsection{Obtaining Heuristic Upper Bound} \label{subsec:HUB}
-	We observe that it takes many iterations in Algorithm~\ref{alg:Cut} to find a good feasible solution.
-When there is not a tight upper bound as cutoff value, it takes longer to solve model \(\mathcal{M}_{\mathcal{P}}\).
-On the other hand, it is fast to solve model~\eqref{prob:extensive} with a small number of scenarios (e.g., 20 scenarios).
-Solving this small model provides a feasible solution \(\hat{t},\hat{x}\), which can be used to generate an upper bound for the problem with large number of scenarios.
-Therefore, we bootstrap small subsets of scenarios from the original scenario set, i.e., \(\Omega'_n \subset \Omega,\ n = 1,2,\dots\), and solve model~\eqref{prob:extensive} with each of those subsets to generate upper bound evaluations.
-Then we select the smallest to serve as the upper bound for model \(\mathcal{M}_{\mathcal{P}}\).
-\\
-	\newline
-	There are many ways to generate the subsets \(\Omega'_n\).
-We observe that it is beneficial to spread the scenarios within each subset in a similar distribution as the original scenario set.
-We first sort the scenarios so that the scenario with a larger disruption time has a larger index.
-Suppose we want to generate \(N\) subsets with an equal size \(|\Omega'|\) such that \(N \cdot |\Omega'| = |\Omega|\).
-The \(n\)-th subset is indexed by:
-	\[\Omega'_n = \{n + (j - 1) \cdot |\Omega'|,\ j = 1,2,\dots, N\}.\]
-	The upper bound generated using this heuristic is within \(5\%\) of the optimal objective value for every test case.
-\tcb{In Section~\ref{sec:results} we compare the computational time of the decomposition method with and without the initial upper bound and show the significant performance improvement by adding such a heuristic upper bound.}
-
-	\subsection{Magnanti-Wong Type Heuristics on Benders Cuts Generation} \label{subsec:MW}
-	For Benders decomposition with a mixed integer master program, it is observed that the subproblems have multiple optimal dual, which means that at a specific incumbent solution, there are multiple valid cuts to generate.
-Magnanti and Wong~\cite{magnanti1981accelerating} provide a method to select Pareto-optimal cuts.
-Such Pareto-optimal cuts are stronger than ordinary Benders cuts at the relative interior of the feasible region of the master problem.
-It means that the generated Pareto-optimal cuts have a higher value when the integrality is relaxed, which helps tighten the linear programming relaxation of the master program.\\
-	\newline
-	We applies a heuristics that pursues the same goal as Magnanti and Wong~\cite{magnanti1981accelerating} to tighten the cuts at interior points of the feasible region of the master program \((M_\mathcal{P})\).
-We keep a record of all feasible solutions obtained in the past, \(\hat{t}\) and \(\hat{x}\), find the right \(\hat{y}\) for each of them with the current version of partition, and calculate the average of those points to obtain an average point, (\(t^0,x^0,y^0\)).
-We then solve the subproblems following the same procedure as in Magnanti and Wong~\cite{magnanti1981accelerating}, using this average point in the place of the core point.
-For each scenario \(\omega \in \Omega\), first we solve model~\eqref{prob:subTightened} with the current master solution \((\hat{t},\hat{x},\hat{y})\)to obtain the optimal value \(f^*_{\mathcal{P}}(\hat{t},\hat{x},\hat{y})\).
-Suppose the dual problem of \((S^\omega_\mathcal{P})\) can be represented in a simplified form~\eqref{prob:subdual}; \tcb{see Appendix for the expanded version of model~\eqref{prob:subdual}.}
+We solve model~\eqref{prob:btminmax} iteratively and update \(\bar{t}_i\) and \(\underbar{t}_i\) until the bounds converge for every \(i \in I\).\\
+	\newline
+	We run FBBT at the beginning of our decomposition method to provide the initial partition \(\cP^0\) to start Algorithm~\ref{alg:Cut}.
+If we can tighten the bounds of some activities, for example, by branch-and-bound or heuristics, we can run FBBT to tighten the bounds for all activities, which leads to a tighter formulation of the subproblems, \((S^{\omega}_{\cP})\), as further detailed in Section~\ref{subsec:bbpartition}.
+
+	\subsection{Obtaining a Heuristic Upper Bound} \label{subsec:HUB}
+	In our computation, we observe that it can take many iterations of Algorithm~\ref{alg:Cut} before we find a good feasible solution.
+When there is not a tight upper bound to use as a ``cutoff value,'' it takes an integer programming solver longer to solve model \((M_{\cP})\).
+On the other hand, we can quickly solve the extensive formulation~\eqref{prob:extensive} when the number of scenarios is small; e.g., \(|\Omega| = 20\).
+Solving such a model provides a feasible first-stage solution \((\hat{t},\hat{x})\), which can be used to generate an upper bound for the problem with the larger, original set of scenarios.
+Therefore, we can generate \(N\) small subsets of scenarios from the original scenario set, i.e., \(\Omega_n \subset \Omega,\ n = 1,2,\dots N\), and solve model~\eqref{prob:extensive} with each of those subsets to generate candidate upper bounds, and select the one with the smallest expected project span under $\Omega$.
+\\
+	\newline
+	In generating \(\Omega_n\), we observe that it is beneficial to have diverse scenarios within each subset.
+	%in a similar distribution as the original scenario set. 
+	As above, We sort the scenarios by disruption time so $H^\omega < H^{\omega+1}$.
+For simplicity, suppose each subset has equal size so that \(N \cdot |\Omega_n| = |\Omega|, \ \forall n\).
+The \(n\)-th subset is then:
+	\[\Omega_n = \{ \omega \, | \, \omega=n + (j - 1) \cdot |\Omega_n|,\ j = 1,2,\dots, N\}.\]
+	In Section~\ref{sec:results} we compare the computational time of the decomposition method with and without initial upper bounds, and show the significant performance improvement by including the heuristic upper bound.
+
+	\subsection{Magnanti-Wong Cut Generation} \label{subsec:MW}
+	In a Benders' decomposition algorithm, linear programming subproblems can have multiple optimal dual solutions, which means that at a specific incumbent solution, there are multiple valid cuts that could be generated.
+\citet{magnanti1981accelerating} provide a method to select Pareto-optimal cuts, which cannot be dominated by ordinary cuts,
+	%in the relative interior of the feasible region of the master problem. It means that the generated Pareto-optimal cuts have a higher value when the integrality is relaxed, 
+	and help tighten the linear programming relaxation of the master program.\\
+	\newline
+	We apply a technique that pursues the same goal as~\citeauthor{magnanti1981accelerating} in order to tighten cuts at interior points of \((M_\cP)\).
+We record \((\hat{t},\hat{x})\) solutions from previous iterations, compute the corresponding \(\hat{y}\) for the current partition, and obtain the average, which we denote (\(t^0,x^0,y^0\)).
+We then solve the subproblems following the procedure of~\citet{magnanti1981accelerating}, using this average point as a proxy for the core point, i.e., a point on the relative interior of the LP relaxation of \((M_{\cP})\)'s feasible region.
+For each scenario \(\omega \in \Omega\), first we solve model~\eqref{prob:subTightened} with the current master solution  \((\hat{t},\hat{x},\hat{y})\) to obtain the optimal value, \(f^{\omega}_{\cP}(\hat{t},\hat{x},\hat{y})\).
+Next we need to find dual variables that ensure the dual objective value at \((\hat{t},\hat{x},\hat{y})\) is within a small tolerance of \(f^{\omega}_{\cP}(\hat{t},\hat{x},\hat{y})\) (e.g., \(\epsilon_{MW} = 10^{-5}\)), while maximizing the dual objective value at \((t^0,x^0,y^0)\).
+Let the following denote the dual of \((S^\omega_\cP)\) in compact form:
 	\begin{subequations} \label{prob:subdual}
 		\begin{align}
+		f^{\omega}_{\cP}(\hat{t},\hat{x},\hat{y})=
 		\max_{\pi,\lambda,\gamma,\eta} \quad & \pi^\top (\hat{t} + b_t) + \lambda^\top (\hat{x} + b_x) + \gamma^\top (\hat{y} + b_y) + \eta^\top b \\
@@
 	\end{subequations}
-	Given a small error tolerance, \(\epsilon = 10^{-5}\), we solve the maximization problem to obtain enhanced Benders cuts parameters \(\tilde{v}\), \(\pi\), \(\lambda\) and \(\gamma\):
+	We have suppressed the subproblem dependence on $\omega$; Appendix~\ref{appen:probdual} details the full version of model~\eqref{prob:subdual}.
+	We solve the following to obtain Magnanti-Wong cut parameters, \({v}\), \(\pi\), \(\lambda\), and~\(\gamma\):
 	\begin{subequations} \label{prob:subMW}
 		\begin{align}
-		\tilde{v} = \max_{\pi,\lambda,\gamma,\eta} \quad & \pi^\top (t^0 + b_t) + \lambda^\top (x^0 + b_x) + \gamma^\top (y^0 + b_y) + \eta^\top b  \\
-		\text{s.t.} \quad & \pi^\top (\hat{t} + b_t) + \lambda^\top (\hat{x} + b_x) + \gamma^\top (\hat{y} + b_y) + \eta^\top b \geq (1 - \epsilon) f^*_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) \\
+		{v} = \max_{\pi,\lambda,\gamma,\eta} \quad & \pi^\top (t^0 + b_t) + \lambda^\top (x^0 + b_x) + \gamma^\top (y^0 + b_y) + \eta^\top b  \\
+		\text{s.t.} \quad & \pi^\top (\hat{t} + b_t) + \lambda^\top (\hat{x} + b_x) + \gamma^\top (\hat{y} + b_y) + \eta^\top b \geq (1 - \epsilon_{MW}) f^{\omega}_{\cP}(\hat{t},\hat{x},\hat{y}) \\
 		& A^\top_{\pi} \pi + A^\top_{\lambda} \lambda + A^\top_{\gamma} \gamma + A^\top_{\eta} \eta \leq c.
@@
 	\end{subequations}
-	\noi Our average point (\(t^0,x^0,y^0\)) may not always be in the relative interior of the master problem feasible region: if for all past solutions there exists an \(i \in I\) and \(q \in \mathcal{Q}_i\) such that \(\hat{y}_i^q = 1\), then \(y_i^{0,q}\) takes a binary value for all \(q \in \mathcal{Q}_i\), and does not lie in the relative interior of the master problem feasible region.
-Although it means our generated cuts may not be Pareto-optimal, they help improve the computational performance, as shown in Table~\ref{table:heuristics} in Section~\ref{sec:results}.
-
-	\subsection{Combining Partitioning with Branch-and-Bound} \label{subsec:bbpartition}
-	The decomposition method using partitions (Algorithm 1) can be further enhanced by a branch-and-bound process, which helps reduce the number of binary variables added to the master and enables solving simpler MIPs in parallel.
-The branch-and-bound tree consists of nodes, each corresponding to model~\eqref{prob:masterTightened} with different partitions.
-The root node starts with the initial partition.
-For each node, we perform the Benders' decomposition process with the master problem \((\mathcal{M}_{\mathcal{P}})\) subproblems, \((S_{\mathcal{P}}^\omega),\ \forall \omega \in \Omega\), to generate cuts for the node until it converges.
-The optimal solution of the node provides a lower bound to the original problem~\ref{prob:extensive} since for every \(\omega \in \Omega\), \((S_{\mathcal{P}}^\omega)\) is a relaxation for \((S^\omega)\).
-We solve \((S^\omega)\) for \(\omega \in \Omega\) to obtain an evaluation of the upper bound.
-If the gap between this upper bound and the lower bound smaller than the tolerance, we can mark the current node complete and start processing the next available node in the tree.
-If not, we branch on a scenario \(\hat{\omega}\) with the largest relaxation gap at the optimal solution of the node, \(f^{\hat{\omega}}(\hat{t},\hat{x}) - f^{\hat{\omega}}_{\mathcal{P}}(\hat{t},\hat{x},\hat{y})\), with a specified activity \(\hat{i} \in I\) where subproblem of scenario \(\hat{\omega}\) has a fractional \(G_i\).
-The current node branches out to two children nodes: one with the constraint \(t_{\hat{i}} \leq H^{\hat{\omega}}\) and the other with the constraint \(t_{\hat{i}} \geq H^{\hat{\omega}}\).
-Correspondingly, the partition \(\mathcal{Q}_{\hat{i}}\) will be refined because branching creates a natural partition at \(H^{\hat{\omega}}\), and some \(y_{\hat{i}}^{q}\) for the new partition will be forced to take value 0.\\
-	\newline
-	After this branching process, for each children node, we can still refine the partition on all activities \(i \in I\) similar to the description in Section~\ref{subsec:partition}.
-The children will inherit the parent node's cuts and they will be updated in a similar fashion of inequality~\eqref{cons:updatedcut}.
-Suppose for activity \(i \in I\), the current node \(n\) has a partition \(\mathcal{P}_i^n\) indexed by set \(\mathcal{Q}_i^n\); its parent node \(m\) has a partition \(\mathcal{P}_i^m\) indexed by set \(\mathcal{Q}_i^m\), the cuts inherited from node \(m\) will be updated for node \(n\) as:
+	\noi Our average point, (\(t^0,x^0,y^0\)), may not be in the relative interior of the master problem's feasible region, e.g.,  if all solutions contributing to the average have a component of $y$ taking value zero or one.
+Although this means the resulting  cuts may not be Pareto-optimal, they may still  improve computational performance,
+	%as shown in Table~\ref{table:heuristics} 
+	and we investigate this in Section~\ref{sec:results}.
+
+	\subsection{Cut Selection}
+	The Benders decomposition process within Algorithm~\ref{alg:Cut} takes a multicut approach.
+Many previous works have discussed the benefits and drawbacks of the multicut approach~\citep{birge2011introduction,trukhanov2010adaptive}.
+Although a multicut approach is able to obtain a good outer approximation of the recourse functions quickly, it is harder to solve the mixed integer master problem in later iterations since a large number of cuts are appended to the master problem.
+\\
+	\newline
+	We observe the similar phenomenon that keeping all cuts generated slows down solving the master problem.
+Therefore, we apply a simple cut selection process to only keep the tight cuts at the end of each Benders iteration.
+Refining partitions renders many cuts loose, and the cuts far from the optimal solution in the optimal solution may have a poor quality.
+Therefore, keeping only a limited number of cuts eliminates many redundant constraints, while it still provides a decent lower bound for the master problem.
+With this cut selection process, the number of cuts remaining in the master problem is moderate and a significant computational improvement is achieved.
+Detailed computational results showing this effectiveness of cut selection is presented in Table~\ref{table:time}.
+
+	\subsection{Refining Partitions}\label{subsec:refine} 
+	In this section we first discuss how a partition is refined in step~\ref{alg:refine_partition} of Algorithm~\ref{alg:Cut}. 
+	%There could be many rules to refine the partition. 
+	The most significant contributor to the optimality gap is that variable \(G\) can take fractional values in the relaxed problem~\((S_{\cP}^\omega)\).
+For example, if \(d_{ik}^\omega \gg D_{ik}\) then \(G_i\) can take a fractional value far from an optimal value.
+	%For example, \(G_i\) should take value \(1\) when activity \(i\) starts after the disruption, but solving LP relaxation may output an optimal \(G_i\) as close to 0. 
+	This can significantly alter the duration between activity \(i\) and \(k\) (see constraint~\eqref{cons:subSep}) in the LP relaxation, and thus create a large gap between the relaxation and the original mixed-integer subproblem.
+Let \(N_p\) be a parameter that denotes the number of new partitions for each activity \(i \in I\); we use $N_p=5$ in our computation.
+Suppose subproblem \((S_\cP^\omega)\) has as part of its solution \({G}_i^\omega, i \in I \).
+	%when we branch on the scenario \(\hat{\omega}\), suppose  
+	Then separately for each $i \in I$ our rule selects for partitioning up to \(N_p\) scenarios with the largest values of:
+	\begin{align}\label{eqn:define_rho}
+	\rho_{i}^{{\omega}} = \begin{cases}
+	\max_{(i,k) \in \cA} d_{ik}^{{\omega}} {G}_i^\omega & \text{if } t_i < H^{{\omega}}\\
+	\max_{(i,k) \in \cA} d_{ik}^{{\omega}} (1 - {G}_i^\omega) & \text{if } t_i > H^{{\omega}}\\
+	\min\{\max_{(i,k) \in \cA} d_{ik}^{{\omega}} {G}_i^\omega, \max_{(i,k) \in \cA} d_{ik}^{{\omega}} (1 - {G}_i^\omega)\} & \text{if $t_i=H^{\omega}$.}
+	\end{cases}
+	\end{align}
+
+	\subsection{Branch-and-Cut Algorithm}\label{subsec:bbpartition}
+	In Algorithm~\ref{alg:Cut} we iteratively refine the partition defining the $y$-variables, and each time we solve master~\eqref{prob:masterTightened} we must solve a mixed integer linear program, which we do with a commercial integer programming solver.
+	Algorithm~\ref{alg:Cut} is not a branch-and-cut~(B\&C) algorithm in that it does not adaptively generate different cuts at different parts of a branch-and-bound tree.
+As an improvement of Algorithm~\ref{alg:Cut}, here a B\&C algorithm is proposed, which involves a branch-and-bound (B\&B) tree with nodes that we manage.
+The root node in our B\&B tree involves the original partition, and we solve that node using the Benders' decomposition, which iteratively adds cuts to master~\eqref{prob:masterTightened} until the problem is solved for the fixed partition, as in Algorithm~\ref{alg:Cut}.
+In the B\&C algorithm we recursively branch on a continuous variable $t_i$ via $t_i \le H^\omega$ and $t_i \ge H^\omega$ for some $i$-$\omega$ pair.
+Rather than actually branching on the continuous $t$-variables, this branching is carried out using the partition $(\cP_i,\cQ_i)$ by fixing the corresponding subset of $y_i^q$-variables to zero.
+This helps manage both the number of binary variables and the number of optimality cuts in a master problem.
+Moreover, in our implementation we solve the nodes in our B\&B tree in parallel.
+\\
+	\newline
+	%Algorithm~\ref{alg:Cut} can be further enhanced by a branch-and-cut process, which helps reduce the number of binary variables added to the master and enables solving simpler integer programs in parallel.
+	%The branch-and-bound (B\&B) tree consists of nodes corresponding to master problem~\eqref{prob:masterTightened} with additional branching constraints. 
+	%The root node starts with the initial partition. 
+	%For each B\&B node, we perform the Benders' decomposition process until it converges. 
+	The optimal value of a B\&B node provides a lower bound on the optimal value of~\eqref{prob:extensive}.
+We also continually update a global upper bound each time we obtain a feasible solution in a Benders' decomposition iteration.
+If the gap between a node's lower bound and the global upper bound is smaller than the tolerance, we mark the node as fathomed.
+If not, we branch as follows:
+	\begin{subequations}\label{eqn:branch_rule}
+		\begin{eqnarray}
+		&& \mbox{select} \ \omega \in \mbox{argmax}_{\omega \in \Omega}  \left [ f^{{\omega}}(\hat{t},\hat{x}) - f^{{\omega}}_{\cP}(\hat{t},\hat{x},\hat{y}) \right ] \label{branch:select_omega} \\
+		&& \mbox{select} \ i \in \mbox{argmax}_{i \in I} \left [ \rho_i^\omega \right ]. \label{branch:select_i}
+		\end{eqnarray}
+	\end{subequations}	
+	In~\eqref{branch:select_omega} we select the scenario~\({\omega}\) with the largest relaxation gap.
+Then in~\eqref{branch:select_i} we select the activity with the largest \(\rho_{i}^{{\omega}}\) from equation~\eqref{eqn:define_rho}.
+This defines the $i$-$\omega$ pair for branching on $t_i \le H^\omega$ versus $t_i \ge H^\omega$ using the $y$-variables in a form of SOS branching.
+\\
+	%subproblem of scenario \(\hat{\omega}\) has a fractional \(G_i\).
+	%	The current node branches out to two children nodes: one with the constraint \(t_{\hat{i}} \leq H^{\hat{\omega}}\) and the other with the constraint \(t_{\hat{i}} \geq H^{\hat{\omega}}\).
+Correspondingly, the partition \(\cQ_{\hat{i}}\) will be refined because branching creates a natural partition at \(H^{\hat{\omega}}\), and some \(y_{\hat{i}}^{q}\) for the new partition will be forced to take value 0.\\
+	\newline
+	After a branch, for each child node we refine the partition on all activities \(i \in I\) according to Section~\ref{subsec:refine}.
+	%similar to the description in Section~\ref{subsec:partition}. 
+	The children inherit the parent node's cuts, updated in a similar fashion as inequality~\eqref{cons:updatedcut}.
+To set up notation for Algorithm~\ref{alg:CutBB},  suppose for activity \(i \in I\), the current B\&B node, say node \(n\), has a partition \(\cP_i^n\) indexed by set \(\cQ_i^n\), and its parent node \(m\) has a partition \(\cP_i^m\) indexed by set \(\cQ_i^m\).
+Then, the cuts inherited from node \(m\) are updated for node \(n\) as:
 	\begin{align}\label{cons:updatedcutBB}
-	& \theta^\omega \geq v^{\omega,m,\ell} + \sum_{i \in I} \pi_i^{\omega,m,\ell} (t_i - \hat{t}_i^{m,\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,m,\ell} (x_{ij} - \hat{x}_{ij}^{m,\ell}) + \nonumber \\
-	& \qquad \sum_{i \in I} \sum_{q \in \mathcal{Q}^{m}_i} \gamma_{i}^{\omega,m,q} \left( \sum_{\tilde{q} \in \Delta^n_i(m,q)} y_i^{\tilde{q}} - \hat{y}_i^{q,m,\ell} \right) \qquad \forall \ell = 1,2, \dots.
-	\end{align}
-	Here \(\Delta^n_i(m,q)\) represents the descendant set of the partition \(\mathcal{P}_i^n\) refined from the \(q\)-th element in the partition \(\mathcal{P}_i^m\).
-The cuts remain valid since the new partitions of the children node are refinements of the parent node partition, even with the branching action.
-The parent node is marked complete once the refining process is done, and we search for the next available node with the smallest lower bound to perform the Benders decomposition on.
-\\
-	\newline
-	There are many rules to select the activity \(\hat{i}\) to branch on.
-In our observation, the biggest contributor to the relaxation gap, \(f^{\hat{\omega}}(\hat{t},\hat{x}) - f^{\hat{\omega}}_{\mathcal{P}}(\hat{t},\hat{x},\hat{y})\), is that variable \(G\) can take fractional value in relaxation problem \(S_{\mathcal{P}}^\omega\).
-Since the magnitude of the disruption, \(d_i^\omega\), is usually large in value to model significant effect of the stochastic disruption, a fractional \(G\) can have a large impact on the separation constraint~\eqref{cons:subSep}.
-When \(d_i^\omega\) has a very large positive value and \(G_i\) is supposed to take value \(1\), the possibility of \(G_i\) being a fractional value close to zero will decrease the separation between activity \(i\) and \(k\) by a large amount, and thus create a large gap between the relaxation problem and the original mixed-integer subproblem.
-Therefore, when we branch on the scenario \(\hat{\omega}\), suppose the subproblem has a solution \(\hat{G}_i\), we select the activity with the maximum violation measure of \(d_i^{\hat{\omega}} \hat{G}_i\), \(\rho_i^{\hat{\omega}}\):
-	\begin{align}
-	\rho_i^{\hat{\omega}} = \begin{cases}
-	d_i^{\hat{\omega}} \hat{G}_i & \text{if } t_i < H^{\hat{\omega}}\\
-	d_i^{\hat{\omega}} (1 - \hat{G}_i) & \text{if } t_i > H^{\hat{\omega}}\\
-	\min\{d_i^{\hat{\omega}} \hat{G}_i, d_i^{\hat{\omega}} (1 - \hat{G}_i)\} & \text{otherwise.}
-	\end{cases}
-	\end{align}
-	With all pieces together, we summarize the new algorithm of the partitioning based branch-and-bound decomposition method in Algorithm~\ref{alg:CutBB}.
-We can perform the algorithm steps on each available node in parallel to improve the time performance.
-	\begin{algorithm}
-		\caption{Partitioning Based Branch-and-Bound Decomposition algorithm to solve problem~\eqref{prob:extensive}}
+	& \theta^\omega \geq v^{\omega,m,\ell} + \sum_{i \in I} \pi_i^{\omega,m,\ell} (t_i - \hat{t}_i^{\, m,\ell}) + \sum_{i \in I} \sum_{j \in J_i} \lambda_{ij}^{\omega,m,\ell} (x_{ij} - \hat{x}_{ij}^{m,\ell}) + \nonumber \\
+	& \qquad \sum_{i \in I} \sum_{q \in \cQ^{m}_i} \gamma_{i}^{\omega,m,q} \left( \sum_{q^\prime \in \Delta^n_i(m,q)} y_i^{q^\prime} - \hat{y}_i^{q,m,\ell} \right) \qquad \forall \ell = 1,2, \dots, L.
+	\end{align}
+	Here, \(\Delta^n_i(m,q)\) represents the descendant set of the partition \(\cP_i^n\) refined from the \(q\)-th element in the partition \(\cP_i^m\).
+The cuts remain valid by Proposition~\ref{prop:validity} because the partitions in the child node refine those of the parent node.
+The parent node is marked as fathomed after a refinement, and we select the next available node with the smallest lower bound.
+\\
+	\newline
+	Putting all these pieces together, we summarize our partition-based branch-and-cut decomposition method in Algorithm~\ref{alg:CutBB}.
+As indicated above, in implementation we execute the algorithm's steps on each available node in parallel.
+	\begin{algorithm}[ht]
+		\caption{Partition-based branch-and-cut algorithm to solve model~\eqref{prob:extensive}}
 		\label{alg:CutBB}
 		\begin{algorithmic}[1]
-			\State Initialize with specified tolerance parameters \(\epsilon > 0\) and \(\delta > 0\), a global upper bound \(UB\), and the tree of node \(1\) marked available with the following properties: cut iteration number \(\ell_1 = 1\), lower bound \(LB^1\), initial partition \(\mathcal{P}^1\) with its indexed set \(\mathcal{Q}^1\);
+			\State Initialize tolerance parameters \(\epsilon \geq \delta \geq 0\), and a global upper bound \(UB\). 
+			\State Initialize the B\&B tree with node \(1\), with the following properties: cut iteration number \(\ell_1 = 1\), lower bound \(LB^1\), initial partition \(\cP^1\) with its indexed set \(\cQ^1\);
 			\While{there exists an available node such that \(\frac{UB - LB^n}{UB} > \epsilon\)}
-			\State Select the available node \(n\) with smallest \(LB^n\);
-			\State Append the inherited cuts from all ancestors of node \(n\) in the form of inequality~\eqref{cons:updatedcutBB};
+			\State Select available node \(n\) with smallest \(LB^n\);
+			\State Append inherited cuts from parent of node \(n\) to master~\((M^n_{\cP})\) using~\eqref{cons:updatedcutBB};
 			\Repeat
-			\State Solve master problem \((M_{\mathcal{P}})\) of node \(n\), obtain solution \(\hat{t}^{\ell^n}, \hat{x}^{\ell^n}, \hat{y}^{\ell^n}, \hat{\theta}^{\ell^n}\)
-
-			\hspace{1cm} and optimal value \(z_{\mathcal{P}}^*\);
-			\If{\(z_{\mathcal{P}}^* > LB^n\)}
-			\State Update \(LB^n = z_{\mathcal{P}}^*\);
+			\State Solve \((M^n_{\cP})\) and obtain solution \(\hat{t}^{\, \ell^n}, \hat{x}^{\ell^n}, \hat{y}^{\ell^n}, \hat{\theta}^{\ell^n}\) and optimal value \(z_{\cP}^*\);
+			\If{\(z_{\cP}^* > LB^n\)}
+			\State Update \(LB^n = z_{\cP}^*\);
 			\EndIf
-			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t}^{\ell^n},\hat{x}^{\ell^n})\). 
-			\State Calculate \(z^* = p^0 \hat{t}^{\ell^n}_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^{\ell^n},\hat{x}^{\ell^n})\)
-			\If{\(z^* < UB\)} 
-			\State Update \(UB := z^*\) and record the best incumbent solution as \(t^* = \hat{t}^{\ell^n}, x^* = \hat{x}^{\ell^n}\)
-
-			\hspace{1.7cm} and \(y^* = \hat{y}^{\ell^n}\);
+			\State For each \(\omega \in \Omega\), solve problem \((S^\omega)\) and obtain \(f^{\omega}(\hat{t}^{\ell^n},\hat{x}^{\ell^n})\) and \(\hat{G}^{\ell^n}\);
+			\State Calculate \(\bar{z} = p^0 \hat{t}^{\, \ell^n}_T + \sum_{\omega \in \Omega} p^\omega f^{\omega}(\hat{t}^{\ell^n},\hat{x}^{\ell^n})\);
+			\If{\(\bar{z} < UB\)} 
+			\State Update \(UB = \bar{z}\) and incumbent solution as \(t^* = \hat{t}^{\, \ell^n}, x^* = \hat{x}^{\ell^n}\) and \(G^* = \hat{G}^{\ell^n}\);
 			\EndIf
-			\State For each \(\omega \in \Omega\), solve problem \((S_{\mathcal{P}}^\omega)\) given \(\hat{t}^{\ell^n}, \hat{x}^{\ell^n}, \hat{y}^{\ell^n}, \hat{\theta}^{\ell^n}\)
-
-			\hspace{1cm} obtain optimal value \(v^{\omega,\ell^n}\) and coefficients \(\pi^{\omega,\ell^n}, \lambda^{\omega,\ell^n}, \gamma^{\omega,\ell^n}\);
-			\State Add the cuts of form~\eqref{cons:cut} to the master problem;
-			\State Update \(\ell^n = \ell^n + 1\);
-			\Until{\(z^*_{\mathcal{P}} \geq z^* - \delta\)}
+			\For{each \(\omega \in \Omega\)}
+			\State solve \((S_{\cP}^\omega)\) given \(\hat{t}^{\, \ell^n}, \hat{x}^{\ell^n}, \hat{y}^{\ell^n}\) and obtain optimal value \(v^{\omega,\ell^n}\) and \(\pi^{\omega,\ell^n}, \lambda^{\omega,\ell^n}, \gamma^{\omega,\ell^n}\); \label{alg:bbCutLBSub}
+			\If{\(\hat{\theta}^{\omega,\ell} < v^{\omega,\ell} - \delta\)}
+			add cut of form~\eqref{cons:cut} to \((M^n_{\cP})\);
+			\EndIf
+			\EndFor
+			\State Let \(\ell^n = \ell^n + 1\);
+			\Until{no cut is added;}
 			\If{\(\frac{UB - LB^n}{UB} > \epsilon\)}
-			\State Branch the node to generate two children nodes \(n_1\) and \(n_2\);
-			\State Refine the partition for nodes \(n_1\) and \(n_2\) to obtain \(\mathcal{P}^{n_1}\) and \(\mathcal{P}^{n_2}\), respectively;
+			\State Branch via~\eqref{eqn:branch_rule}, creating two available children nodes, \(n_1\) and \(n_2\), from node \(n\);
+			%   			    \hspace{1cm} and mark them available;
+			\State Refine the partition for nodes \(n_1\) and \(n_2\) to obtain \(\cP^{n_1}\) and \(\cP^{n_2}\), respectively;
 			\State Let \(LB^{n_1} = LB^{n_2} = LB^n\);
-			\Else
-			\State Mark node \(n\) complete;
 			\EndIf
+			\State Mark node \(n\) as fathomed;
 			\vspace{0.1cm}
 			\EndWhile{\textbf{end while}}
-			\State Output \(UB\) as the optimal value of model~\eqref{prob:extensive}, and \(t^*, x^*\) as the optimal solution.
+			\State Output \(UB\) as the $\epsilon$-optimal value of model~\eqref{prob:extensive}, and \((t^*, x^*, G^*)\) as the \(\epsilon\)-optimal solution.
 		\end{algorithmic}
@@
 
-	\subsection{Numerical Example of the Partitioning Based Branch-and-Bound Decomposition Method}
-	In this section, we use an example to illustrate the process of the partitioning based branch-and-bound decomposition method.
-Since the size of this example is small, we choose to solve the problem to optimality, i.e., \(\epsilon = 0\).
-Suppose we have a serial network with five activities, \(i \in I = \{1,2,3,4,5\}\) in Figure~\ref{fig:fiveAct}.
+	\subsection{Numerical Example of the Partitioning Based Branch-and-Bound Decomposition Method} \label{subsec:numeg}
+	In this section, we use an example to illustrate Algorithm~\ref{alg:CutBB} with $\epsilon=0$.
+We consider the network with five activities, \(i \in I = \{1,2,3,4,5\}\), shown in Figure~\ref{fig:fiveAct}.
 	\begin{figure}[H]
 		\centering
-		\includegraphics[width=0.8\textwidth]{fiveAct}
+		\includegraphics[width=0.6\textwidth]{fiveAct}
 		\caption{A five-activity serial network to illustrate Algorithm~\ref{alg:CutBB}}
@@
 	\end{figure}
-	\noi Each activity has a duration \(D_i = 1,\ \forall i \in I\), and each activity can be crashed with an option that will decrease the duration by 90\% with one unit of resource consumption, i.e., \(e_{i1} = 0.9,\ \forall i \in I\).
-The total resource budget \(B = 2\).
-The probability of no disruption is \(p_0 = 0.2\), and the disruption can occur at four discrete time points: \(H^1 = 1,\ H^2 = 2,\ H^3 = 3,\ H^4 = 4\) with equal probability \(p^\omega = 0.2,\ \forall \omega \in \Omega = \{1,2,3,4\}\).
-The duration increase by \(d_i^\omega = 10,\ \forall i \in I, \omega \in \Omega\).
+	\noi Each activity has a duration \(D_i = 1,\ \forall i \in I\), and can be crashed with a single option that decreases the duration by 90\% with one unit of resource consumption, i.e., \(e_{i1} = 0.9,\ \forall i \in I\), and we let \(B = 2\).
+The probability of no disruption is \(p^0 = 0.2\), and the disruption can occur at four discrete time points, \(H^1 = 1,\ H^2 = 2,\ H^3 = 3,\ H^4 = 4\), with equal probability \(p^\omega = 0.2,\ \forall \omega \in \Omega = \{1,2,3,4\}\).
+The increase in duration is \(d_i^\omega = 10,\ \forall i \in I, \omega \in \Omega\).
 From this setup, we can bound the starting time of activity from above by \(T_{\max} = 9\).
@@
 	\newline
-	We first tighten the bound of starting time for each activity. Then we can start Algorithm~\ref{alg:CutBB} with the initial node \(1\). The partition of the initial node is:
+	\tcr{We first tighten the bound of starting time for each activity.
+Necessary?
+Seems like a stand-alone sentence.} We start Algorithm~\ref{alg:CutBB} with the initial node \(1\), and initial partition:
 	\begin{align*}
-	&\mathcal{P}_1^1 = \{(0,9)\} \qquad \qquad \;\; \mathcal{Q}_1^1 = \{1\}\\
-	&\mathcal{P}_2^1 = \{(0,9)\} \qquad \qquad \;\; \mathcal{Q}_2^1 = \{1\}\\
-	&\mathcal{P}_3^1 = \{(0,9)\} \qquad \qquad \;\; \mathcal{Q}_3^1 = \{1\}\\
-	&\mathcal{P}_4^1 = \{(0,1),(1,9)\} \qquad  \mathcal{Q}_4^1 = \{1,2\} \qquad y_4^1 = 0\\
-	&\mathcal{P}_5^1 = \{(0,2),(2,9)\} \qquad  \mathcal{Q}_5^1 = \{1,2\} \qquad y_5^1 = 0\\
-	&\mathcal{P}_T^1 = \{(0,3),(3,9)\} \qquad  \mathcal{Q}_T^1 = \{1,2\} \qquad y_T^1 = 0.
+	&\cP_1^1 = \{(0,9)\} \qquad \qquad \;\; \cQ_1^1 = \{1\}\\
+	&\cP_2^1 = \{(0,9)\} \qquad \qquad \;\; \cQ_2^1 = \{1\}\\
+	&\cP_3^1 = \{(0,9)\} \qquad \qquad \;\; \cQ_3^1 = \{1\}\\
+	&\cP_4^1 = \{(0,1),(1,9)\} \qquad  \cQ_4^1 = \{1,2\} \qquad y_4^1 = 0\\
+	&\cP_5^1 = \{(0,2),(2,9)\} \qquad  \cQ_5^1 = \{1,2\} \qquad y_5^1 = 0\\
+	&\cP_T^1 = \{(0,3),(3,9)\} \qquad  \cQ_T^1 = \{1,2\} \qquad y_T^1 = 0.
 	\end{align*}
-	We can perform the Benders decomposition on node \(1\).
-The process converges to an optimal value \(z^*_{\mathcal{P}} = 4.072\).
+	We can perform the Benders' decomposition on node \(1\).
+The process converges to an optimal value \(z^*_{\cP} = 4.072\).
 In the process, we update the upper bound with the best \(z^*\) found in the process, as \(UB = 6.607\).
@@
 	\end{align*}
-	At this solution, the largest relaxation gap is incurred at \(\hat{\omega} = 1\) with the value \(f^{\hat{\omega}}(\hat{t},\hat{x}) - f^{\hat{\omega}}_{\mathcal{P}}(\hat{t},\hat{x},\hat{y}) = 8.75\).
-The optimal solution to the subproblem \(S^1_\mathcal{P}\) has a fractional solution \(G_3 = 0.125\).
+	At this solution, the largest relaxation gap is incurred at \(\hat{\omega} = 1\) with a value \(8.75\).
+The optimal solution to the subproblem \((S^1_\cP)\) has a fractional solution \(G_3 = 0.125\).
 Since the optimality gap at node 1 is larger than 0, we branch on scenario \(1\) and activity \(3\), creating two children nodes, node \(2\) and node \(3\).
@@
 	& \text{Node 2:}\\
-	&\mathcal{P}_1^2 = \{(0,9)\} \qquad \qquad \qquad \quad \mathcal{Q}_1^2 = \{1\}\\
-	&\mathcal{P}_2^2 = \{(0,9)\} \qquad \qquad \qquad \quad \mathcal{Q}_2^2 = \{1\}\\
-	&\mathcal{P}_3^2 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_3^2 = \{1,2\} \qquad \quad  y_3^1 = 0\\
-	&\mathcal{P}_4^2 = \{(0,1),(1,2),(2,9)\} \qquad  \mathcal{Q}_4^2 = \{1,2,3\} \qquad y_4^1 = 0\\
-	&\mathcal{P}_5^2 = \{(0,2),(2,3),(3,9)\} \qquad  \mathcal{Q}_5^2 = \{1,2,3\} \qquad y_5^1 = 0\\
-	&\mathcal{P}_T^2 = \{(0,3),(3,4),(4,9)\} \qquad  \mathcal{Q}_T^2 = \{1,2,3\} \qquad y_T^1 = 0.
+	&\cP_1^2 = \{(0,9)\} \qquad \qquad \qquad \quad \cQ_1^2 = \{1\}\\
+	&\cP_2^2 = \{(0,9)\} \qquad \qquad \qquad \quad \cQ_2^2 = \{1\}\\
+	&\cP_3^2 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_3^2 = \{1,2\} \qquad \quad  y_3^1 = 0\\
+	&\cP_4^2 = \{(0,1),(1,2),(2,9)\} \qquad  \cQ_4^2 = \{1,2,3\} \qquad y_4^1 = 0\\
+	&\cP_5^2 = \{(0,2),(2,3),(3,9)\} \qquad  \cQ_5^2 = \{1,2,3\} \qquad y_5^1 = 0\\
+	&\cP_T^2 = \{(0,3),(3,4),(4,9)\} \qquad  \cQ_T^2 = \{1,2,3\} \qquad y_T^1 = 0.
 	\end{align*}
@@
 	& \text{Node 3:}\\
-	&\mathcal{P}_1^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_1^3 = \{1,2\} \qquad \quad y_1^2 = 0\\
-	&\mathcal{P}_2^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_2^3 = \{1,2\} \qquad \quad y_2^2 = 0\\
-	&\mathcal{P}_3^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \mathcal{Q}_3^3 = \{1,2\} \qquad \quad y_3^2 = 0\\
-	&\mathcal{P}_4^3 = \{(0,1),(1,2),(2,9)\} \qquad  \mathcal{Q}_4^3 = \{1,2,3\} \qquad y_4^1 = 0\\
-	&\mathcal{P}_5^3 = \{(0,2),(2,3),(3,9)\} \qquad  \mathcal{Q}_5^3 = \{1,2,3\} \qquad y_5^1 = 0\\
-	&\mathcal{P}_T^3 = \{(0,3),(3,4),(4,9)\} \qquad  \mathcal{Q}_T^3 = \{1,2,3\} \qquad y_T^1 = 0.
+	&\cP_1^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_1^3 = \{1,2\} \qquad \quad y_1^2 = 0\\
+	&\cP_2^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_2^3 = \{1,2\} \qquad \quad y_2^2 = 0\\
+	&\cP_3^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_3^3 = \{1,2\} \qquad \quad y_3^2 = 0\\
+	&\cP_4^3 = \{(0,1),(1,2),(2,9)\} \qquad  \cQ_4^3 = \{1,2,3\} \qquad y_4^1 = 0\\
+	&\cP_5^3 = \{(0,2),(2,3),(3,9)\} \qquad  \cQ_5^3 = \{1,2,3\} \qquad y_5^1 = 0\\
+	&\cP_T^3 = \{(0,3),(3,4),(4,9)\} \qquad  \cQ_T^3 = \{1,2,3\} \qquad y_T^1 = 0.
 	\end{align*}
 	We mark node 1 as complete and move on to node 2, which is the available node with the smallest lower bound.
-Processing node 2 with Benders decomposition yields an optimal solution of 6.1111.
+Processing node 2 with Benders' decomposition yields an optimal solution of 6.1111.
 The node 2 branches to node 4 and 5, which inherit the cuts and the lower bound from node 2.
@@
 	The next available node with the smallest lower bound is node 3. Node 3 yields an optimal value of 6 and an optimal solution as: 
-	\begin{align*}
+	\begin{subequations} \label{eqn:optSol}
+		\begin{align}
 		& \hat{t}_1 = 0 \qquad \qquad \hat{x}_{11} = 1\\
@@
 		& \hat{t}_T = 3.2.
-	\end{align*}
+		\end{align}
+	\end{subequations}
 	The relaxation gap is zero, which means that the upper bound is updated to \(UB = 6\) as well.
 This leads to a zero optimality gap at node 3.
-For node 4 and node 5, since their lower bounds are larger than the current upper bound, they will not be processed by the algorithm.
-The algorithm terminates with the best solution as \(\hat{t}\) and \(\hat{x}\), and the optimal objective value is 6.
+Node 4 and node 5 will not be processed since their lower bounds are larger than the current upper bound.
+The algorithm terminates with the best solution in~\eqref{eqn:optSol}.
+The recorded best \(G\) variables indicate that activity 1,2 and 3 start before disruption scenario \(1\), activity 4 starts before disruption scenario \(2\), and activity 5 starts before disruption scenario \(3\).
+The optimal objective value is 6.
 
@@
 		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
-		\item What is the time improvement of Algorithm~\ref{alg:Cut} compared to solving extensive formulation~\eqref{prob:extensive} using state-of-the-art MIP solvers?
-Other algorithms solving 2SMIP with mixed binary recourse?
+		\item What is the time improvement of Algorithm~\ref{alg:CutBB} compared to solving extensive formulation~\eqref{prob:extensive} using a state-of-the-art MIP solver?
+How effective are the upper bound generation and Magnanti-Wong cuts?
 	\end{enumerate}
-	We first introduce the PERT network used for test and distribution information used to characterize uncertainty in Section~\ref{subsec:example}.
+	We first introduce the test case PERT networks and distribution information used to characterize uncertainty in Section~\ref{subsec:testcases}.
 In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of the solution to model~\eqref{prob:extensive} compared to the alternative ones.
 We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
-Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation.\\
-	\newline
-	All tests are run on a server with 20 Intel Xeon cores at 3.1 GHz and 256 GB of RAM.
-All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform.
-All linear programs and mixed integer programs are solved by Gurobi 8.01 \cite{gurobi2016} with default parameters.
-
-	\subsection{Test Cases Construction} \label{subsec:example}
+Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:CutBB} compared to solving extensive formulation.
+\\
+	\newline
+	All tests are run on a server with 30 Intel Xeon cores at 3.1 GHz and 256 GB of RAM.
+For Algorithm~\ref{alg:CutBB}, each node is solved by 6 cores and we allow at most 5 nodes to be solved simultaneously so that the maximum number of cores used at any time is still 30.
+All models are constructed using version 0.18.0 of the JuMP package~\citep{DunningHuchetteLubin2017} on the Julia platform.
+All linear programs and mixed integer programs are solved by Gurobi 8.01~\citep{gurobi2016} with default parameters.
+
+	\subsection{Test Cases Construction} \label{subsec:testcases}
 	%	\textcolor{blue}{Where we find our tests:
@@
 	%			\item Case 55 from Elmgrabhy
-	%			\item Randomized network 35, 75 nodes
+	%			\item Randomized network 35, 75, 100 nodes
 	%			\item Plambeck paper: Case 110
@@
 Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value.
-We use an activity network from Plambeck et al.~\cite{plambeck1996sample} with 11 activities, one from Elmgrabhy~\cite{Elmaghraby77} with 19 activities, and we manually create one activity network with 14 activities and randomly generate one network with 35 activities using the tool \emph{RanGen}~\citep{demeulemeester2003rangen}.
-In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities.\\
-	\newline
-	For every test case, the timing of disruption follows a lognormal distribution since its value has to be nonnegative.
-The disruption magnitude of activities follows an exponential distribution of which the parameter differs among activities.
-The exponential distribution can best model the drastic change caused by a disruption.
+We use an activity network from~\citet{plambeck1996sample} with 11 activities, and % and the other with 110 activities.
+	one from~\citet{Elmaghraby77} with 19 activities. 
+	%and the other with 55 activities. 
+	We also manually create one activity network with 14 activities and randomly generate one network with 35 activities using the tool \emph{RanGen}~\citep{demeulemeester2003rangen}.
+	%and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}. 
+	In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities. Data of all test cases are detailed in Appendix~\ref{appen:data}.\\
+	\newline
+	For every test case, the timing of the disruption is randomly generated from a lognormal distribution since its value has to be nonnegative.
+The disruption magnitude of activities follows an exponential distribution of which the parameter differs among activities since the exponential distribution is widely used to model the service time~\citep{ross1996stochastic}.
+	%. The exponential distribution can best model the drastic change caused by a disruption.
 	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
-	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling random timing and magnitude of the disruption.
+	In this section, we compare the quality of five solutions obtained under alternative problem settings to show the value of modeling random timing and magnitude of the disruption.
 First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET").
-Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), the timing is random but the magnitude is at its expected value (denoted as ``\(H\)Only"), and the magnitude is random but the timing is at its expected value (denoted as ``\(d\)Only").
-Finally, we construct the full stochastic model where both the timing and the magnitude are random (denoted as ``FULL").
-To generate those five solutions, we use a sample of size \(500\).
-We can obtain a point estimation for the upper bound by plugging each of these solutions in the SAA problem with the original \(500\) samples, and we call this estimation, \(z^*\), as ``in-sample" since these samples are also used to obtain solutions.
+Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), timing is random but magnitude is at its expected value (denoted as ``\(H\)Only"), and magnitude is random but timing is at its expected value (denoted as ``\(d\)Only").
+Finally, we construct the fully stochastic model where both timing and magnitude are random (denoted as ``FULL").
+We sample \(500\) scenarios to solve for solutions of \(H\)Only, \(d\)Only and Full settings, and we generate 20 batches of samples of size \(5000\) to estimate an upper bound for each candidate solution.
+We present the upper bound estimation for those five candidate solutions in Figure~\ref{fig:value} and the \(95\%\) confidence interval in Table~\ref{table:value}.\\
+	%by plugging each of these solutions in the SAA problem with the original \(500\) samples, and we call this estimation, \(z^*\), as ``in-sample" since these samples are also used to obtain solutions.
 We also sample 20 batches of samples of \(|\Omega| = 5000\), and obtain the confidence interval of the upper bound estimation, \(\bar{z}\), by testing the solution on these batches.
 We present the comparison of different solutions of Case 11 in Figure~\ref{fig:value}.
-	\begin{figure}[H]
+	\begin{figure}
 		\centering
@@
 	\end{figure}
-	\noi Figure~\ref{fig:value} shows that the solution quality is poor without considering the uncertainty of disruption timing.
-When we assume the disruption timing is uncertain, the computational effort required to obtain ``\(H\)Only" solution and the fully stochastic solution is on the same level, since we need to include the same number of binary variables.
+
+	\noi We align all test cases in the same scale and set the upper bound of FULL as 1 in Figure~\ref{fig:value}.
+It shows that the solution quality is poor without considering the uncertainty of disruption timing.
+The upper bound estimation of DET is at least \(30\%\) larger than that of FULL.
+The upper bound estimations of \(d\)Only and EXP are similar and at least \(10\%\) larger than that of FULL.
+For Case 14, the upper bound estimation of \(H\)Only is \(20\%\) larger than that of FULL.
+Although for other three cases, the upper bound estimation of \(H\)Only is close to that of FULL, the computational effort required to obtain \(H\)Only solution and the fully stochastic solution is on the same level, often much more.
+The test result justifies the value of having a fully stochastic model.
+	%, since we need to include the same number of binary variables and same disruption magnitude brings symmetry issues. 
 	\begin{table}[H]
-		\centering
-		\begin{tabular}{ c | l l | l l | l l | l l | l l}
+		%\centering
+		\resizebox{\linewidth}{!}{%
+			\begin{tabular}{ c | l | l | l | l | l }
 				\hline
-			& \multicolumn{2}{c |}{Deterministic} & \multicolumn{2}{c |}{Expected} & \multicolumn{2}{c |}{dOnly} & \multicolumn{2}{c |}{HOnly} & \multicolumn{2}{c}{Full}\\
-			& \(z^*\) & CI of \(\bar{z}\) & \(z^*\) & CI of  \(\bar{z}\) & \(z^*\) & CI of \(\bar{z}\) & \(z^*\) & CI of \(\bar{z}\) & \(z^*\) & CI of \(\bar{z}\) \\ \hline
-			Case 11 & 118.35 & 112.33 & 114.91 & 98.82 & 98.82 \\
-			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 \\
-			Case 19 & & & &  & -\\
-			Case 35 & & & &  & -\\
+				& \thead{DET} & \thead{EXP} & \thead{\(d\)Only} & \thead{\(H\)Only} & \multicolumn{1}{c}{FULL}\\ \hline
+				Case 11	&	575.80 \(\pm\) 16.88	&	454.33\(\pm\) 18.34		&	454.33\(\pm\) 18.34	&	287.05\(\pm\) 14.91  &	287.29\(\pm\) 14.92	\\
+				Case 14	&	3309.27\(\pm\) 177.18	&	2878.65\(\pm\) 176.70 &	2876.42\(\pm\) 176.55	&	3098.05\(\pm\) 133.06	&	2602.97\(\pm\) 110.12	\\
+				Case 19	&	426.09\(\pm\) 10.09	&	389.61\(\pm\) 7.88	&	388.77\(\pm\) 8.43	&	355.29\(\pm\) 7.14	&	356.42\(\pm\) 5.86	\\
+				Case 35	&	1353.80\(\pm\) 21.11	&	1183.74\(\pm\) 18.52	&	1188.93\(\pm\) 19.53	&	1078.57\(\pm\) 17.31	&	1068.29\(\pm\) 17.47	\\
 				\hline
-		\end{tabular}
+		\end{tabular}}
 		\caption{Compare optimal values from alternatives of the disruption model}
@@
 	\end{table}
-	To further test whether having a fully stochastic model is the best, we run a pair-wise \(t\)-test.
+	%\noi To further test whether having a fully stochastic model is the best, we run a pair-wise \(t\)-test.
 The null hypothesis is that whether the difference between the upper bound generated by one alternative solution and that generated by the fully stochastic solution is less than 0.
 The pair-wise \(t\)-test rejects all null hypotheses, which shows that the difference between an alternative solution is significantly larger than the fully stochastic solution.
-We can conclude the fully stochastic solution is the best solution, and this justifies the value of having a fully stochastic model, albeit its complexity.
+
 	\subsection{Simulation Budget} \label{subsec:budget}
-	We first examine the quality of solutions generated from different sizes of samples.
-It is well known that the objective value obtained by SAA approaches the objective function of the original problem as the sample size grows to infinity, and the expected value of the SAA objective value improves as the sample size increases~\cite{shapiro2009lectures}.
+	We examine the quality of solutions generated from different sizes of samples.
+It is well known that the objective value obtained by SAA approaches the objective function of the original problem as the sample size grows to infinity, and the expected value of the SAA objective value improves as the sample size increases~\citep{shapiro2009lectures}.
 However, when the sample size increases, the computational cost increases as well.
 Understanding how the solution quality changes according to different sample sizes is important to help us decide a proper sample size while achieving a decent solution.
-For each test case in Section~\ref{subsec:example}, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(|\Omega| \in \{10, 50, 75, 100, 200, 300, 400, 500\}\).
-For each of those solutions, we test against a set of \(5000\) samples and obtain the object value as a point estimation of the upper bound for each batch.
+For each test case, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(|\Omega| \in \{10, 20, 50, 100, 200, 500\}\).
+For each solution, we test against a set of \(5000\) samples and obtain the object value as a point estimation of the upper bound.
 We can also obtain the \(95\%\) confidence interval of the lower bound and the upper bound estimation for each sample size.
-We present the upper bound results in Table~\ref{table:budgetU}, the lower bound results in Table~\ref{table:budgetL} and present visualization of the results with Figure~\ref{fig:budget}.
+We present the upper bound results in Table~\ref{table:budgetU}, the lower bound results in Table~\ref{table:budgetL} and visualization of the results with Figure~\ref{fig:budget}.
+
 	\begin{table}[H]
-		\centering
-		\begin{tabular}{ c | l l l l l l l l}
+		%\centering
+		\resizebox{\linewidth}{!}{%
+			\begin{tabular}{ c | l l l l l l }
 				\hline
-			& 10 & 20 & 50 & 100 & 200 & 500 & 1000 & 2000 \\ \hline
-			Case 11& 118.35 & 112.33 & 114.91 & 98.82 & 98.82 & & \\
-			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 & &  \\
-			Case 19 & & & &  & - & & \\
+				& \multicolumn{1}{c}{10} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{50} & \multicolumn{1}{c}{100} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{500}  \\ \hline
+				Case 11	&	326.05	\(\pm\)	80.59	&	293.43	\(\pm\)	24.20	&	290.95	\(\pm\)	28.51	&	283.06	\(\pm\)	12.24	&	280.10	\(\pm\)	6.59	&	278.33	\(\pm\)	2.30	\\
+				Case 14	&	3002.42	\(\pm\)	537.69	&	2942.09	\(\pm\)	778.43	&	2714.87	\(\pm\)	330.61	&	2645.71	\(\pm\)	100.15	&	2627.94	\(\pm\)	40.46	&	2626.90	\(\pm\)	39.51	\\
+				Case 19	&	385.41	\(\pm\)	42.29	&	383.67	\(\pm\)	45.78	&	358.99	\(\pm\)	16.76	&	355.28	\(\pm\)	10.21	&	352.57	\(\pm\)	7.65	&	350.91	\(\pm\)	1.83	\\
+				Case 35	&	1130.18	\(\pm\)	117.51	&	1102.57	\(\pm\)	45.66	&	1091.34	\(\pm\)	33.00	&	1080.23	\(\pm\)	21.86	&	1073.05	\(\pm\)	10.53	&	1070.08	\(\pm\)	5.20	\\
 				\hline
-		\end{tabular}
-		\caption{Upper bound confidence interval for solutions generated by different budgets.}
+		\end{tabular}}
+		\caption{Upper bound confidence interval for solutions generated by different budgets}
 		\label{table:budgetU}
@@
 	\begin{table}[H]
-		\centering
-		\begin{tabular}{ c | l l l l l l l l}
+		%\centering
+		\resizebox{\linewidth}{!}{%
+			\begin{tabular}{ c | l l l l l l }
 				\hline
-			& 10 & 20 & 50 & 100 & 200 & 500 & 1000 & 2000 \\ \hline
-			Case 11& 118.35 & 112.33 & 114.91 & 98.82 & 98.82 & &  \\
-			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 & &  \\
-			Case 19 & & & &  & - & & \\
+				& \multicolumn{1}{c}{10} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{50} & \multicolumn{1}{c}{100} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{500}  \\ \hline
+				Case 11	&	296.44	\(\pm\)	255.34	&	247.24	\(\pm\)	134.57	&	266.30	\(\pm\)	140.43	&	275.33	\(\pm\)	73.14	&	289.32	\(\pm\)	66.97	&	274.79	\(\pm\)	36.59	\\
+				Case 14	&	1868.25	\(\pm\)	2152.85	&	1991.32	\(\pm\)	1273.90	&	2244.39	\(\pm\)	992.31	&	2310.86	\(\pm\)	688.76	&	2508.60	\(\pm\)	456.24	&	2477.13	\(\pm\)	275.11	\\
+				Case 19	&	310.07	\(\pm\)	123.11	&	324.00	\(\pm\)	85.84	&	331.84	\(\pm\)	53.49	&	339.69	\(\pm\)	36.10	&	344.84	\(\pm\)	21.78	&	345.10	\(\pm\)	14.26	\\
+				Case 35	&	1166.85	\(\pm\)	586.64	&	1107.83	\(\pm\)	282.44	&	1055.84	\(\pm\)	202.07	&	1036.82	\(\pm\)	120.40	&	1060.78	\(\pm\)	82.29	&	1065.76	\(\pm\)	54.10	\\
 				\hline
-		\end{tabular}
-		\caption{Lower bound estimation for solutions generated by different sample sizes.}
+		\end{tabular}}
+		\caption{Lower bound confidence interval for solutions generated by different budgets}
 		\label{table:budgetL}
@@
 
-	\begin{figure}
+	\begin{figure}[H]
 		\centering
-		\includegraphics[width=0.8\textwidth]{case19_budget_ublb}
-		\caption{Confidence intervals of the lower/upper bound estimation for different sample sizes.}
+		\includegraphics[width=\textwidth]{graphBudgets}
+		\caption{Confidence intervals of the lower/upper bound estimation for different sample sizes}
 		\label{fig:budget}
 	\end{figure}
-	We can see the gap between the upper bound and the lower bound estimation is decreasing as the sample size increases.
+	We can see the gap between the upper bound and the lower bound estimation decreases and both estimations become less variant as the sample size increases.
 A decent solution can be obtained by sampling a moderate number of samples, since the upper bound estimation stabilizes when the sample size is greater than \(100\).
@@
 This comes from the nature of our uncertainty model, as we need to consider both timing and magnitude of the disruption.
+
 	\subsection{Computational Performance} \label{subsec:time}
 	In this section we present the computational result of our decomposition method.
-\tcb{We first show the effectiveness of finding a heuristic upper bound and generating Magnanti-Wong heuristic cuts.
+The results in this section reflect the effectiveness of the techniques introduced in Section~\ref{sec:decomposition}.
+We start with the comparison of the initial lower bound with and without the bounds on variable \(t\) tightened.
+	\newline
+	We show the quality of the heuristic upper bound obtained in Section~\ref{subsec:HUB}.
+We use the same 20 batches of samples as in Section~\eqref{subsec:budget}.
+For each batch we compare the true optimal value with the heuristic upper bounds.
+Table~\ref{table:hub} shows the smallest gap, the average gap and the largest gap, all in percentage, between the heuristic upper bound and the true optimal value.
+We split each sample into equal-sized subsamples to generate the heuristic upper bound.
+We use \(N = 10\) for \(|\Omega| = 100\), \(N = 10\) for \(|\Omega| = 200\), and \(N = 20\) for \(|\Omega| = 500\).
+We also report the average running time of obtaining the heuristic upper bound.
+	\begin{table}[H]
+		\centering		
+		\begin{tabular}{ c | c | l l l | r}
+			\hline
+			\multirow{2}{*}{\(\quad\)} & \multirow{2}{*}{Sample size} & \multicolumn{3}{c |}{Gap (\%)} & \multirow{2}{*}{Average Time (Sec).} \\
+			& & Smallest & Average & Largest &\\
+			\hline
+			\multirow{3}{*}{Case 11} & 100 & 0.01	& 0.5	& 2.3	& 5.6\\
+			& 200 & 0	& 0.15	& 0.83	& 17.8\\
+			& 500 & 0	& 0.07	& 0.37	& 67.5\\
+			\hline
+			\multirow{3}{*}{Case 14} & 100 & 1.34	& 6.02	& 16.14	& 7.7\\
+			& 200 & 1.58	& 3.9	& 8.91	& 30.4\\
+			& 500 & 0.75	& 2.35	& 3.96	& 104.4\\
+			\hline
+			\multirow{3}{*}{Case 19} & 100 & 0.56	& 2.67	& 5.28	& 9.9\\
+			& 200 & 0.05	& 0.99	& 2.03	& 37.2\\
+			& 500 & 0	& 0.72	& 1.59	& 127.6\\
+			\hline
+			\multirow{3}{*}{Case 35} & 100 & 0	& 0.64	& 2.65	& 5.8\\
+			& 200 & 0.08	& 0.46	& 1.3	& 25.7\\
+			& 500 & 0	& 0.32	& 1.25	& 59.0\\
+			\hline
+		\end{tabular}
+		\caption{Gap information between the heuristic upper bound and optimal value for twenty random samples}
+		\label{table:hub}
+	\end{table}
+	\noi We can see that the average upper bound gap is larger than 5\% only for Case 14 when the sample size equals to 100.
+Among all 240 samples, there are only 15 of which the heuristic upper bound is more than 5\% larger than the optimal value.
+We also observe that as the sample size grows, the heuristic upper bound's quality improves.
+\\
+	\newline
+	Next we show the effectiveness of finding a heuristic upper bound and generating Magnanti-Wong cuts.
 For all test cases, we use a sample size \(|\Omega| = 500\).
-In Table~\ref{table:heuristics}, ``UB" means that we only use heuristic upper bound in Section~\ref{subsec:HUB} and generate regular Benders cuts, and ``MW" means that we generate Magnanti-Wong heuristic cuts in Section~\ref{subsec:MW} without a prespecified initial upper bound.
-We also test the time performance of using neither and using both heuristics.}
+In Table~\ref{table:heuristics}, ``UB" means that we only use heuristic upper bound in Section~\ref{subsec:HUB} and generate regular Benders' cuts, and ``MW" means that we generate Magnanti-Wong cuts in Section~\ref{subsec:MW} without a prespecified initial upper bound.
+We also test the time performance of using neither and using both techniques.
 	\begin{table}[H]
@@
 			\hline
-			& Case 11 & Case 14 & Case 19 & Case 35 \\ \hline
-			Neither & & & &  \\
-			UB & & & & \\
-			MW & & & & \\
-			Both & & & & \\
+			Running Time (sec.) & Case 11 & Case 14 & Case 19 & Case 35 \\ \hline
+			Neither & 226.2 & 3573.8 & 4499.5 & 458.6 \\
+			UB & 153.8 & 3003.7 & 2899.9 & 110.7\\
+			MW & 290.4 & 2386.4 & 2002.1 & 451.0\\
+			Both & 222.3 & 2342.4 & 1411.5 & 170.2\\
 			\hline
 		\end{tabular}
-		\caption{Computational improvement by utilizing heuristic upper bound generation and Magnanti-Wong heuristic cuts.}
+		\caption{Computational improvement by utilizing heuristic upper bound generation and Magnanti-Wong heuristic cuts}
 		\label{table:heuristics}
 	\end{table}
-	\noi Next we show the comparison of time running Algorithm~\ref{alg:Cut}, Algorithm~\ref{alg:CutBB}, and directly solving the extensive formulation~\eqref{prob:extensive} using Gurobi.
-In each master iteration, we solve a master problem with a small number of binary variables.
-Although we need to solve multiple rounds of the master problem and the number of binary variables is increasing since the partition is refined in every iteration, we still can observe a significant improvement by using our proposed decomposition method, especially when the sample size is large.
+	Table~\ref{table:heuristics} shows that obtaining a heuristic upper bound can significantly improve the computational time since many branches will be cut off by the heuristic upper bound when solving the master MIP.
+Magnanti-Wong cuts are effective for Case 14 and Case 19 but not for the other two cases.
+The effectiveness of such cuts may depend on the geometric nature of test cases, and it is valuable to investigate this phenomenon with more test cases in the future.\\
+	\newline
+	\noi Next we compare the running time of Algorithm~\ref{alg:Cut} (denoted as A\ref{alg:Cut}), Algorithm~\ref{alg:CutBB} (denoted as A\ref{alg:CutBB}), with and without the cut selection process (CS), and solving the extensive formulation~\eqref{prob:extensive} using Gurobi.
+The computational time is presented in Table~\ref{table:time}.
+	\begin{table}[ht]
+		\centering		
+		\begin{tabular}{ c | c | l l l l l}
+			\hline
+			\multirow{2}{*}{Running Time (sec.)} & \multirow{2}{*}{Sample Size (\(|\Omega|\))} & \multicolumn{5}{c}{Methods} \\ \cline{3-7}
+			& & A\ref{alg:Cut} & A\ref{alg:Cut}+CS & A\ref{alg:CutBB} & A\ref{alg:CutBB}+CS & Extensive  \\ \hline
+			\multirow{4}{*}{Case 11} & 100 & 14.6 & 12.1 & 20.0 & 10.0 & 7.1 \\
+			& 200 & 27.8 & 60.8 & 20.0 & 30.0 & 49.9\\
+			& 500 & 445.8 & 407.4 & 145.1 & 163.2 & 1634.3\\
+			& 1000 & 411.2 & 500.0 & 80.1 & 88.1 & 5622.7\\
+			\hline
+			\multirow{4}{*}{Case 14} & 100 & 83.5 & 57.4 & 70.1 & 60.1 & 17.2 \\
+			& 200 & 246.9 & 233.2 & 212.9 & 136.4 & 212.7 \\
+			& 500 & 2882.6 & 2635.8 & 1651.5 & 1122.1 & 1677.0 \\
+			& 1000 & 10388.4 & 12692.3 & 4777.6 & 2673.7 & 12027.1 \\
+			\hline
+			\multirow{4}{*}{Case 19} & 100 & 335.6 & 190.4 & 112.6 & 80.1 & 82.4 \\
+			& 200 & 412.2 & 337.0 & 552.6 & 270.4 & 383.8 \\
+			& 500 & 2732.1 & 2434.2 & 1008.4 & 830.8 & 3960.4 \\
+			& 1000 & 18251.8 & 14811.1 & 13995.4 & 3623.8 & 44537.3 \\
+			\hline
+			\multirow{4}{*}{Case 35} & 100 & 60.5 & 57.5 & 50.0 & 40.0 & 9.6 \\
+			& 200 & 18.9 & 17.5 & 20.0 & 20.0 & 40.3 \\
+			& 500 & 81.9 & 80.5 & 30.0 & 30.0 & 346.9 \\
+			& 1000 & 313.0 & 303.9 & 50.1 & 50.1 & 690.5 \\
+			\hline
+		\end{tabular}
+		\caption{Comparison of computational performance with different sample sizes for Algorithm~\ref{alg:CutBB} and solving extensive formulation using Gurobi}
+		\label{table:time}
+	\end{table}
+	% decomposition works
+	Table~\ref{table:time} shows that although solving the extensive formulation may be faster when the sample size is small, the decomposition algorithms generally perform much better when the sample size is large.
+The only exception is in Case 14 where Algorithm~\ref{alg:Cut} has a longer running time than solving the extensive formulation, no matter whether we select cuts or not.
+In our decomposition methods, although we need to solve the master problem multiple times, the number of binary variables is significantly smaller than that in the extensive formulation.
+Therefore, when the sample size is large, our decomposition methods can still a better computational results than solving the extensive formulation.\\
+	\newline
+	% algorithm 2 is better, why
+	Algorithm~\ref{alg:CutBB} is faster than Algorithm~\ref{alg:Cut} when \(|\Omega| \geq 500\).
+When the sample size is large, Algorithm~\ref{alg:Cut} requires many master iterations to converge.
+In later iterations of Algorithm~\ref{alg:Cut}, solving the mixed integer master program becomes significantly harder.
+For Algorithm~\ref{alg:CutBB}, the time saved by processing nodes in parallel outweighs the slightly longer solving time at each node due to using fewer cores.
+Moreover, because of branching, the master problems in the B\&B tree with a small number of binary variables in Algorithm~\ref{alg:CutBB}, which further accelerates solving the master problem.
+	% cut selection is useful, especially in algorithm 2
+	The results also show that selecting cuts can be helpful for the decomposition methods.
+Applying the cut selection process gains a larger improvement for Algorithm~\ref{alg:CutBB} than for Algorithm~\ref{alg:Cut}.
+	%\begin{figure}
+	%	\centering
+	%	\includegraphics[width=0.8\textwidth]{case11_time}
+	%	\caption{Computational performance for different sample sizes.}
+	% \(|\Omega| \in \{100, 200, 300, 400, 500,1000\}\
+	%	\label{fig:time}
+	%\end{figure}
+
+	\section{Conclusions} \label{sec:conclusions}
+	In this paper, we establish the concept of the stochastic disruption and formulate a two-stage stochastic mixed integer program to model a project crashing optimization problem under the influence of a single disruption.
+We use examples to illustrate the properties of our problem that it is possible to delay the start or crash a shorter activity to accelerate the whole project.
+Moreover, the computational results justify the need to use a two-stage stochastic mixed integer program to model this problem.
+It is computationally challenging to solve a two-stage stochastic mixed integer program with binary variables in the second stage, and we prove that it is NP-hard.
+Therefore, we propose a decomposition method which uses the logic relationship to sequentially partitions the continuous feasible regions of the master problem to generate tighter Benders' cuts.
+The proposed method can significantly improve the computational performance, especially for the large sample sizes, which we show is often required to obtain a good solution/estimation of bounds.\\
+	\newline
+	There are multiple possible extensions of the results in this paper.
+First, there is still room to improve the computational performance of the decomposition method.
+More branching and refining rules can be tested for the best computational performance.
+In addition, it is worthwhile to inspect the network structures so that we can improve the quality of cuts or prune partitions.
+
+	\bibliographystyle{plainnat}
+	\bibliography{PERT_Bib}
+
+	\pagebreak
+
+	\appendix
+	\section{Detailed Formulation of Model~\eqref{prob:subdual}} \label{appen:probdual}
+	The detailed version of model~\eqref{prob:subdual} is presented as follows:
+	\begin{subequations}
+		\begin{align}
+		\max \quad & \sum_{i \in I} \sum_{q \in \cQ_i} \left[
+		\hat{y}_i^q \lambda_{F2,i}^q + (\hat{y}_i^q - 1) \lambda_{F3,i}^q + \hat{y}_i^q \underbar{H}_i^q \lambda_{H2,i} + \lambda_{\bar{F},i}^q \right] + &\nonumber \\
+		& \sum_{i \in I} \left[(H^\omega - \hat{t}_i) \lambda_{H1,i} - \hat{t}_i \left(\lambda_{H2,i} + \lambda_{t1,i} + \lambda_{t2,i} \right) + \lambda_{xs,i} + \lambda_{\bar{G},i} \right] + &\nonumber \\
+		& \sum_{i \in I} \sum_{j \in J_i} \left[\hat{x}_{ij} \left(\lambda_{x1,ij} + \lambda_{x2,ij} \right) + \lambda_{\bar{z},ij} + \lambda_{\bar{x},ij} + \lambda_{z3,ij}\right] + &\nonumber \\
+		& \sum_{i \in I} \left[ \left(\sum_{q \in \cQ_i: H^\omega \leq \underbar{H}_i^q} \hat{y}_i^q \right) \lambda_{y1,i} + \left(\sum_{q \in \cQ_i: H^\omega \geq \bar{H}_i^q} \hat{y}_i^q \right) \lambda_{y2,i} \right] + &\nonumber \\
+		& B \lambda_{B} + \sum_{(i,k) \in \cA} D_{ik} \lambda_{d,ik} &\\
+		\st \quad & -\lambda_{t1,i} - \lambda_{t2,i} -\lambda_{t3,i} + \sum_{(i,k) \in \cA} \lambda_{d,ik} - \sum_{(k,i) \in \cA} \lambda_{d,ki} \geq 0 & \forall\, i \in I\backslash\{T\} \label{cons:dualt1}\\
+		& 1 - \lambda_{t1,i} - \lambda_{t2,i} -\lambda_{t3,i} + \sum_{(i,k) \in \cA} \lambda_{d,ik} - \sum_{(k,i) \in \cA} \lambda_{d,ki} \geq 0 & i = T \label{cons:dualt2}\\
+		& -\lambda_{x1,ij} -\lambda_{x2,ij} +\lambda_{z2,ij} + \lambda_{z3,ij} - b_{ij} \lambda_B - & \nonumber \\
+		& \qquad \qquad \lambda_{xs,i} - \lambda_{\bar{x},ij} - \sum_{(i,k) \in \cA} D_{ik} e_{ij} \lambda_{d,ik} \geq 0 & \forall\, i \in I, j \in J_i \label{cons:dualx}\\
+		& \sum_{q \in \cQ_i} \left(\lambda_{F1,i}^q + \lambda_{F3,i}^q \right) - H^\omega \left(\lambda_{H1,i} - \lambda_{H2,i} \right) - \lambda_{y1,i} - \lambda_{y2,i} - \lambda_{\bar{G},i} + & \nonumber \\
+		& \qquad \qquad \sum_{(k,i) \in \cA} \lambda_{G,ki} - \sum_{(i,k) \in \cA} \lambda_{G,ik} - M_t \lambda_{t1,i} + M_t \lambda_{t2,i} + H^\omega \lambda_{t3,i} + & \nonumber \\
+		& \qquad \qquad \sum_{j \in J_i} \left(-\lambda_{x1,ij} + \lambda_{x2,ij} + \lambda_{z1,ij} + \lambda_{z3,ij} \right) + \sum_{(i,k) \in \cA} d_{ik}^\omega \lambda_{d,ik} \geq 0 & \forall\, i \in I \label{cons:dualG}\\
+		&-\lambda_{F1,i}^q - \lambda_{F2,i}^q - \lambda_{F3,i}^q + \bar{H}_i^q \lambda_{H1,i} - \underbar{H}_i^q \lambda_{H2,i} - \lambda_{\bar{F},i}^q \geq 0 & \forall \, i \in I, q \in \cQ_i \label{cons:dualF}\\
+		&-\lambda_{z1,ij} - \lambda_{z2,ij} - \lambda_{z3,ij} - \sum_{(i,k) \in \cA} d_{ik}^\omega e_{ij} \lambda_{d,ik} - \lambda_{\bar{z},ij} \geq 0 & \forall \, i \in I, j \in J_i \label{cons:dualz}\\
+		& \lambda_{H1,i},\lambda_{y2,i},\lambda_{t2,i}, \lambda_{xs,i},\lambda_{\bar{G},i} \leq 0 & \forall\, i\in I \\
+		& \lambda_{x2,ij}, \lambda_{z1,ij}, \lambda_{z2,ij}, \lambda_{\bar{x},ij}, \lambda_{\bar{z},ij} \leq 0 & \forall\, i \in I, j \in J_i \\
+		& \lambda_{F1,i}^q,\lambda_{F2,i}^q,\lambda_{\bar{F},i}^q \leq 0 & \forall\, i \in I, q \in \cQ_i\\
+		& \lambda_{G,ik} \leq 0 & \forall\, (i,k) \in \cA \\
+		& \lambda_B \leq 0 &\\
+		& \lambda_{H2,i},\lambda_{y1,i},\lambda_{t1,i},\lambda_{t3,i} \geq 0 & \forall\, i\in I \\
+		& \lambda_{x1,ij}, \lambda_{z3,ij} \geq 0 & \forall\, i \in I, j \in J_i \\
+		& \lambda_{F1,i}^q \geq 0 & \forall\, i \in I, q \in \cQ_i\\
+		& \lambda_{d,ik} \geq 0 & \forall\, (i,k) \in \cA .
+		\end{align}
+	\end{subequations}
+
+	\noi The formulation above is an exact form of model~\eqref{prob:subdual}.
+In this formulation, \(\lambda_{H1}\) and \(\lambda_{H2}\) are the dual variables of tightened logic constraints~\eqref{cons:sFG1t} and~\eqref{cons:sFG2t}.
+We use \(\lambda_{F1}, \lambda_{F2}\) and \(\lambda_{F3}\) to represent the dual variables for the linearization constraints~\eqref{cons:sFGlin1t}-\eqref{cons:sFGlin3t} for the bilinear term \(\hat{y}_i^q G_i\), and \(\lambda_{z1}, \lambda_{z2}\) and \(\lambda_{z3}\) to represent the dual variables for the linearization constraints~\eqref{cons:sublinearize1}-\eqref{cons:sublinearize3} for the bilinear term \(G_{i} x_{ij}\).
+The dual variables for the \(G\)-tightening constraints~\eqref{cons:syG1t} and~\eqref{cons:syG2t} are denoted as \(\lambda_{y1}\) and \(\lambda_{y2}\).
+\\
+	\newline
+	We use the dual variables \(\lambda_{t1}, \lambda_{t2}\) and \(\lambda_{t3}\) to denote the dual variables for the constraints~\eqref{cons:stG1},~\eqref{cons:stG2} and~\eqref{cons:subH}, all related to the variable \(t\), while we use the dual variables \(\lambda_{x1}\) and \(\lambda_{x2}\) to denote the dual variables for the constraints~\eqref{cons:sxG1} and~\eqref{cons:sxG2}, both related to the variable \(x\).
+The duration constraint~\eqref{cons:subSep} has its dual variable denoted as \(\lambda_{d}\), the single activity crashing budget constraint~\eqref{cons:subBudget1} has its dual variable as \(\lambda_{xs}\), and the overall crashing budget constraint~\eqref{cons:subBudget} has its dual variable as \(\lambda_B\).
+Finally, we use \(\lambda_{\bar{x}}, \lambda_{\bar{G}}\) and \(\lambda_{\bar{F}}\) to represent the dual variables for the upper bound of variables \(x\), \(G\), and \(F\), respectively.\\
+	\newline
+	The constraints in the dual formulation corresponds to variables in the primal subproblem.
+Constraints~\eqref{cons:dualt1} and~\eqref{cons:dualt2} are for variable \(t\), and for the terminal activity \(i = T\) we need to include the primal objective function coefficient, 1.
+We establish constraints~\eqref{cons:dualx} for variable \(x\), constraints~\eqref{cons:dualG} for variable \(G\), constraints~\eqref{cons:dualF} for variable \(F\), and constraints~\eqref{cons:dualz} for variable \(z\).
+All dual variables have the correct signs matching the sense of corresponding primal constraints.
+
+	\section{Test Cases Data} \label{appen:data}
+	We present the detailed data of four test cases here.
+For all test cases we assume there is only one possible crashing option for each activity.
+The option consumes 1 unit of resource and has the effectiveness parameter of \(e_{i1} = 0.5\) for all \(i \in I\).
+The nominal scenario probability is \(p^0 = 0.1\) and \(p^\omega = \frac{1 - p^0}{|\Omega|}\).
+The timing of the disruption follows a lognormal distribution with parameters \(\mu\) and \(\sigma\) where the mode is \(e^{\mu - \sigma^2}\).
+We also assume that the duration is only dependent on the predecessor, i.e., \(D_{ik} = D_i\) and \(d_{ik}^\omega = d_i^\omega\).
+All \(d_i\) follow an exponential distribution with a mean of \(\mu_i\).
+The value of \(D_i\) and \(\mu_i\) are shown in the following tables.
+	\pagebreak
+	\begin{itemize}
+		\item Case 11: \(B = 3, \mu = \ln 6, \sigma = 0.5\)
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.9\textwidth]{case11}
+			\caption{Activity network of Case 11}
+			\label{fig:case11}
+		\end{figure}
 		\begin{table}[H]
 			\centering		
-		\begin{tabular}{ c | l l l l l l l l l l l l }
-			\hline
-			&10 & 20 & 50 & 100 & 200 & 300 & 400 & 500 & 750 & 1000 & 1500 & 2000 \\ \hline
-			Case 11& 118.35 & 112.33 & 114.91 & 98.82 & 98.82 \\
-			Case 14 & 114.44 & 108.04 & 110.346 & 98.75 & 98.75 \\
-			Case 19 & & & &  & -\\
-			\hline
+			\begin{tabular}{ c | l | l l c| l | l}
+				\cline{1-3}\cline{5-7}
+				Activity & \(D_{i}\) & \(\mu_i\) & \(\qquad\)& Activity & \(D_{i}\) & \(\mu_i\) \\
+				\cline{1-3}\cline{5-7}
+				1 & 10 & \(10^{-5}\) & & 7 & 7.3 & 1\\ 
+				2 & 2 & \(4\) & & 8 & 4.9 & 50\\ 
+				3 & 10 & \(2\) & & 9 & 11.1 & 40\\ 
+				4 & 12 & \(30\) & & 10 & 3.5 & 40\\ 
+				5 & 3 & \(1500\) & & 11 & 9.9 & 5\\ 
+				6 & 10 & \(1\) & &  &  & \\ 
+				\cline{1-3}\cline{5-7}
 			\end{tabular}
-		\caption{Computational performance for different sample sizes.}
-		\label{table:time}
+			\caption{Activity duration \(D_i\) and the mean of disruption magnitude \(\mu_i\) for Case 11}
+			\label{table:case11}
 		\end{table}
+		\pagebreak
+		\item Case 14: \(B = 4, \mu = \ln 35, \sigma = 0.5\)
 		\begin{figure}[H]
 			\centering
-		\includegraphics[width=0.8\textwidth]{case11_time}
-		\caption{Computational performance for different sample sizes.}
-		% \(|\Omega| \in \{100, 200, 300, 400, 500,1000\}\
-		\label{fig:time}
+			\includegraphics[width=0.9\textwidth]{case14}
+			\caption{Activity network of Case 14}
+			\label{fig:case14}
 		\end{figure}
-	\section{Conclusions} \label{sec:conclusions}
-	In this paper, we establish the concept of stochastic disruption and formulate a two-stage stochastic mixed integer program to model a project crashing optimization problem under the influence of single disruption.
-We use examples to illustrate the counterintuitive properties of our problem that it is possible to delay the start or crash a shorter activity to accelerate the whole project.
-Moreover, the computational results justify the need to use a two-stage stochastic mixed integer program to model this problem.
-It is computationally challenging to solve a two-stage stochastic mixed integer program with binary variables in the second stage.
-Therefore, we propose a decomposition method which uses the logic relationship to generate strong linear programming relaxation of recourse problems and sequentially partitions the master feasible regions to generate Benders' cuts.
-The proposed method can significantly improve the computational performance, especially for the large sample sizes, which we show is often required to obtain a good solution/estimation of bounds.\\
-	\newline
-	There are multiple possible extensions of the results in this paper.
-First, there is still room to improve the computational performance of the decomposition method.
-Currently, the refining process is to divide the partition element with fractional \(G\) values into three partitions evenly.
-This can be enhanced by learning the right partition points so that the lower bound can be tightened faster.
-In addition, we are working on exploiting the network structures to improve the quality of cuts or prune partitions.
-	\bibliographystyle{plainnat}
-	\bibliography{PERT_Bib}
+		\begin{table}[H]
+			\centering		
+			\begin{tabular}{ c | l | l l c| l | l}
+				\cline{1-3}\cline{5-7}
+				Activity & \(D_{i}\) & \(\mu_i\) & \(\qquad\)& Activity & \(D_{i}\) & \(\mu_i\) \\
+				\cline{1-3}\cline{5-7}
+				1 & 5 & \(10^{-5}\) & & 8 & 49 & 4000\\ 
+				2 & 30 & \(5\) & & 9 & 40 & 4000\\ 
+				3 & 25 & \(40000\) & & 10 & 30 & 3000\\ 
+				4 & 20 & \(40000\) & & 11 & 45 & 4000\\ 
+				5 & 15 & \(1500\) & & 12 & 25 & 5\\ 
+				6 & 24 & \(20000\) & & 13 & 21 & 5 \\ 
+				7 & 30 & \(20000\) & & 14 & 5 & 5 \\ 
+				\cline{1-3}\cline{5-7}
+			\end{tabular}
+			\caption{Activity duration \(D_i\) and the mean of disruption magnitude \(\mu_i\) for Case 14}
+			\label{table:case14}
+		\end{table}
+		\pagebreak
+		\item Case 19: \(B = 4, \mu = \ln 8, \sigma = 0.5\)
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=0.9\textwidth]{case19}
+			\caption{Activity network of Case 19}
+			\label{fig:case19}
+		\end{figure}
+		\begin{table}[H]
+			\centering		
+			\begin{tabular}{ c | l | l l c| l | l}
+				\cline{1-3}\cline{5-7}
+				Activity & \(D_{i}\) & \(\mu_i\) & \(\qquad\)& Activity & \(D_{i}\) & \(\mu_i\) \\
+				\cline{1-3}\cline{5-7}
+				1 & 5 & \(10\) & & 11 & 6 & 400\\ 
+				2 & 10 & \(100\) & & 12 & 4.5 & 300\\ 
+				3 & 18 & \(300\) & & 13 & 12 & 1000\\ 
+				4 & 35 & \(300\) & & 14 & 1.5 & 10\\ 
+				5 & 6 & \(50\) & & 15 & 2.1 & 200\\ 
+				6 & 6 & \(50\) & & 16 & 8.1 & 2 \\ 
+				7 & 2.5 & \(400\) & & 17 & 6.1 & 100 \\ 
+				8 & 8 & \(20\) & & 18 & 0.001 & 40 \\ 
+				9 & 10 & \(1000\) & & 19 & 0.001 & 300 \\ 
+				10 & 1 & \(50\) & & & & \\ 
+				\cline{1-3}\cline{5-7}
+			\end{tabular}
+			\caption{Activity duration \(D_i\) and the mean of disruption magnitude \(\mu_i\) for Case 19}
+			\label{table:case19}
+		\end{table}
+		\pagebreak
+		\item Case 35: \(B = 8, \mu = \ln 4, \sigma = 0.3\)
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=\textwidth]{case35}
+			\caption{Activity network of Case 35}
+			\label{fig:case35}
+		\end{figure}
+		\begin{table}[H]
+			\centering		
+			\begin{tabular}{ c | l | l l c| l | l}
+				\cline{1-3}\cline{5-7}
+				Activity & \(D_{i}\) & \(\mu_i\) & \(\qquad\)& Activity & \(D_{i}\) & \(\mu_i\) \\
+				\cline{1-3}\cline{5-7}
+				1 & 9 & \(10\) & & 19 & 8 & 10\\ 
+				2 & 7 & \(40\) & & 20 & 8 & 500\\ 
+				3 & 3 & \(30\) & & 21 & 1 & 500\\ 
+				4 & 4 & \(100\) & & 22 & 5 & 500\\ 
+				5 & 6 & \(50\) & & 23 & 2 & 10\\ 
+				6 & 3 & \(10\) & & 24 & 7 & 10 \\ 
+				7 & 10 & \(10\) & & 25 & 1 & 300 \\ 
+				8 & 4 & \(20\) & & 26 & 4 & 400 \\ 
+				9 & 3 & \(10\) & & 27 & 3 & 200 \\ 
+				10 & 6 & \(1000\) & & 28 & 4 & 1000 \\ 
+				11 & 9 & \(10\) & & 29 & 10 & 300\\ 
+				12 & 8 & \(500\) & & 30 & 7 & 500\\ 
+				13 & 5 & \(200\) & & 31 & 2 & 200\\ 
+				14 & 2 & \(10\) & & 32 & 9 & 100\\ 
+				15 & 5 & \(400\) & & 33 & 7 & 100\\ 
+				16 & 2 & \(10\) & & 34 & 1 & 100 \\ 
+				17 & 10 & \(10\) & & 35 & 7 & 200 \\ 
+				18 & 4 & \(2000\) & & & & \\ 
+				\cline{1-3}\cline{5-7}
+			\end{tabular}
+			\caption{Activity duration \(D_i\) and the mean of disruption magnitude \(\mu_i\) for Case 35}
+			\label{table:case35}
+		\end{table}
+	\end{itemize}
 

### 2019-07-10 src/test_branch_1.jl

@@ -1,0 +1,56 @@
+addprocs(30);
+global noThreads = 30;
+@everywhere using JuMP,Gurobi,CPLEX,Ipopt;
+@everywhere using Distributions,HDF5,JLD;
+# test sbb
+@everywhere include("header.jl");
+
+pathList = ["/home/haoxiang/PERT_tests/current/11/",
+            "/home/haoxiang/PERT_tests/current/14/",
+            "/home/haoxiang/PERT_tests/current/19/",
+            "/home/haoxiang/PERT_tests/current/35/",
+            "/home/haoxiang/PERT_tests/current/55/",
+            "/home/haoxiang/PERT_tests/current/75/"];
+
+# pathList = ["/home/haoxiang/scratch/PERT_tests/current/11/",
+#             "/home/haoxiang/scratch/PERT_tests/current/14/",
+#             "/home/haoxiang/scratch/PERT_tests/current/19/",
+#             "/home/haoxiang/scratch/PERT_tests/current/35/",
+#             "/home/haoxiang/scratch/PERT_tests/current/55/",
+#             "/home/haoxiang/scratch/PERT_tests/current/75/"];
+
+fileInd = 2;
+filePath = pathList[fileInd];
+Ωsize = 500;
+global Ω = 1:Ωsize;
+global ϵ = 1e-2;
+global pData;
+pData,disDataSet,nameD,nameH,dparams,Hparams = genData(filePath,Ωsize);
+global pData = pData;
+dataRaw = load("14_test1.jld");
+global disData = dataRaw["disData"];
+
+global allSucc = findSuccAll(pData);
+global distanceDict = Dict();
+for i in pData.II
+    for j in allSucc[i]
+        distanceDict[i,j] = detCal(pData,i,j);
+    end
+end
+
+global sN = 25;
+global MM = 20;
+global nSplit = 5;
+data = [];
+
+global bAlt = 1;
+tic();
+include("partSolve_Callback_tightened_sol.jl");
+timeFull = toc();
+gapFull = (ubCost - lbCost)/ubCost;
+ubFull = ubCost;
+lbFull = lbCost;
+xFull = deepcopy(xbest);
+tFull = deepcopy(tbest);
+push!(data,[ubFull,tFull,xFull,lbFull,timeFull]);
+save("14_test1_Results_1.jld","data",data);

### 2019-07-10 src/test_error.jl

@@ -1,0 +1,38 @@
+# test the crunch error for Gurobi
+addprocs(30);
+global noThreads = 30;
+@everywhere using JuMP,Gurobi,CPLEX,Ipopt;
+@everywhere using Distributions,HDF5,JLD;
+# test sbb
+@everywhere include("header.jl");
+
+pathList = ["/home/haoxiang/scratch/PERT_tests/current/11/",
+            "/home/haoxiang/scratch/PERT_tests/current/14/",
+            "/home/haoxiang/scratch/PERT_tests/current/19/",
+            "/home/haoxiang/scratch/PERT_tests/current/35/",
+            "/home/haoxiang/scratch/PERT_tests/current/55/",
+            "/home/haoxiang/scratch/PERT_tests/current/75/"];
+
+fileInd = 2;
+filePath = pathList[fileInd];
+Ωsize = [10,20,50,100,200,500,1000,2000];
+sNList = [0,0,0,0,20,25,20,40];
+MMList = [0,0,0,0,10,20,50,50];
+
+Ωl = 7;
+global Ω = 1:Ωsize[Ωl];
+randNo = 1;
+extBool = false;
+
+pData,disDataSet,nameD,nameH,dparams,Hparams = genData(filePath,1);
+global pData = pData;
+disDataRaw = load(pathList[fileInd]*"solData_$(Ωsize[Ωl]).jld");
+disData = disDataRaw["data"][randNo];
+
+global allSucc = findSuccAll(pData);
+global distanceDict = Dict();
+for i in pData.II
+    for j in allSucc[i]
+        distanceDict[i,j] = detCal(pData,i,j);
+    end
+end

### 2019-07-27 Writeup/PERT_Draft_DPM_7_27.tex
Changed test_alt for nova to run

--- 2019-07-10 Writeup/PERT_Paper_Draft3.tex
@@
 \usepackage{amsmath}
+\usepackage{scalefnt}
 \usepackage{graphicx}
@@
 \usepackage{color}
-\usepackage{scalefnt}
 \usepackage{amssymb}
@@
 In this setting, ``crashing" is an action that consumes a certain amount of one or more resources and shortens the duration of an activity accordingly~\citep{kuhl2008dynamic}.
-A deterministic optimization model for crashing an activity network was proposed in the 1960s \citep{fulkerson1961network, kelley1961criticalpath}, in which the goal is to complete the project in minimum time by allocating resources under one or more budget constraints.\\
-	\newline
+A deterministic optimization model for crashing an activity network was proposed in the 1960s \citep{fulkerson1961network, kelley1961criticalpath}, in which the goal is to complete the project in minimum time by allocating resources under one or more budget constraints.
+
 	When the program evaluation and review technique (PERT) was introduced~\citep{malcolm1959application}, activity durations were modeled as independent beta random variables, and the project duration approximated by a normal distribution.
@@
 \citet{ahipasaoglu2016distributionally} propose a distributionally robust optimization scheme applied to a PERT network, which reformulates the problem as a semidefinite program or a copositive program, depending on the description of uncertainty.
-The project crashing optimization problem finds application in project management~\citep{demeulemeester2006project, jaselskis1991allocation,tonchia2018industrial}, machine scheduling~\citep{blazewicz1983scheduling,hall1996machine}, health services scheduling~\citep{cardoen2010operating}, chemical processes~\citep{li2008process}, and digital circuit sizing~\citep{kim2007heuristic}.\\
-	\newline
+The project crashing optimization problem finds application in project management~\citep{demeulemeester2006project, jaselskis1991allocation,tonchia2018industrial}, machine scheduling~\citep{blazewicz1983scheduling,hall1996machine}, health services scheduling~\citep{cardoen2010operating}, chemical processes~\citep{li2008process}, and digital circuit sizing~\citep{kim2007heuristic}.
+
 	In this paper, we propose using the concept of stochastic disruptions to model uncertainty in the duration of activities, which differs from existing approaches in both stochastic programming and robust optimization.
@@
 Our setting inherits the philosophy of \citet{morton2009sealift}, but enhances the model by allowing the random disruption time to be continuous in the context of an activity network, instead of a prespecified set of fixed time periods.
-\\
-	\newline
+
 	Given a limited number of disruption scenarios, the problem of optimizing crashing decisions to minimize expected completion time can be formulated as a stochastic mixed-integer program, and we present the model in Section~\ref{sec:formulation}.
@@
 Constraint~\eqref{cons:dBudget} is the budget constraint and constraint~\eqref{cons:dSingleBudget} ensures that no more than one unit of crashing option can be applied to an activity.
-Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities.\\
-	\newline
+Constraint~\eqref{cons:dNonnegt} enforces nonnegativity for the start time of all activities.
+
 	For a project crashing problem under stochastic disruptions, we assume at most one stochastic disruption can occur at a random time in the project span.
@@
 For each scenario \(\omega\), the random realization of parameters, which we denote \(\xi^\omega\), consists of the timing of the disruption, \(H^\omega\), and the magnitude of the disruption via increases in the duration parameters, \(d^\omega_{ik}, \forall (i,k) \in \cA\).
-\\
-	\newline
-	Because we assume at most one disruption, we can model the problem as a two-stage stochastic mixed integer program, in which the timing of the second stage is random.
+
+	Because we assume at most one disruption, we can model the problem as a two-stage stochastic mixed-integer program, in which the timing of the second stage is random.
 That is, the definition of our stages differs from the usual stochastic programming setting.
@@
 And, the second stage characterizes the decisions for each realization of the disruption, which commence at the random time, $H^\omega$.
-The first stage decision variables are carried out until the disruption if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.\\
-	\newline
+The first stage decision variables are carried out until the disruption if it ever occurs, and after the disruption, the scenario-specific recourse decisions are executed.
+
 	The extensive formulation of the two-stage stochastic program is shown as formulation~\eqref{prob:extensive}:
@@
 	\end{subequations}
+
 	In model~\eqref{prob:extensive}, we minimize the expected project span, weighing the span under each scenario by its probability.
@@
 \citet{de1997complexity} use \verb|EOIT_3SAT| to prove that an activity network problem, in which there are a finite set of alternatives for each activity with different duration and cost, is NP-hard, and we use similar proof constructs.
-\\
-	\newline
+
 	Starting with an instance of \verb|EOIT_3SAT|, we formulate an activity network using three layers of nodes.
@@
 	%the procedure of constructing the network components corresponding to a variable and the negative complement of a variable. 
-	From now on we refer to the activities representing variables as \(u\)-activities and those representing clauses as \(c\)-activities.\\
-	\newline
+	From now on we refer to the activities representing variables as \(u\)-activities and those representing clauses as \(c\)-activities.
+
 	We make the following assignments:
@@
 	%\tcr{and which crashing option to select for the \tcr{$c$-activity} nodes}.
-	\\
-	\newline
+
     %	\tcb{We can prove the following lemmas.
@@
 	\end{proof}
-	\noi
+
 	As a result of Theorem~\ref{thm:npcomplete} we immediately obtain the following result.
@@
 If a disruption occurs, the nominal activity durations are lengthened by $d_1 = k$ and $d_2 = (k - 1)^2$.
-\\
-		\newline
+
 		If we start each activity without delay, then \(t_1 = 0,\ x_1=x_1^1\), and for any \(x_1 \leq 1\), \(t_2 \geq \frac{1}{2} \geq D_1(1 - e_1 x_1) \), which means activity \(2\) will start after the disruption.
@@
 
-	\noi In Example~\ref{eg:short} the intuition behind crashing the shorter activity is that it allows us to initiate activity~2 in time to avoid incurring delay~$d_2$.
+	In Example~\ref{eg:short} the intuition behind crashing the shorter activity is that it allows us to initiate activity~2 in time to avoid incurring delay~$d_2$.
 Both examples in this section suggest that the intuition associated with the deterministic version of the optimal crashing problem does not always apply in the stochastic setting, and provides further motivation for employing a model like that in formulation~\eqref{prob:extensive}.
@@
 	\section{A Decomposition Algorithm} \label{sec:decomposition}
-	%Model~\eqref{prob:extensive} is a two-stage stochastic mixed integer program XXX, which is can be large in scale and computationally expensive to solve.
+	%Model~\eqref{prob:extensive} is a two-stage stochastic mixed-integer program XXX, which is can be large in scale and computationally expensive to solve.
 	%in general~\cite{ahmed2011smip}. 
@@
 	\end{subequations}
+
 	A number of existing approches for stochastic mixed-integer programming assume a special structure not satisfied by our model.
@@
 Although this method suits our problem setting, preliminary computational results found that it was not competitive with the scheme we describe here, which makes use of the special structure of our problem.
-\\
-	\newline
+
 	A simple approach is to relax the integrality constraints~\eqref{cons:subInt} of {\em subproblem} ($S^\omega$), and execute a multi-cut L-shaped decomposition algorithm on this linear programming (LP) relaxation.
@@
 The topics in this section aim to tackle these two issues.
-\\
-	\newline
+
 	The combinatorial decision, $G_i \in \{0,1\}$,  $i \in I$, for each ($S^\omega$) is (almost fully) decided by the first-stage continuous variables, $t_i$.
@@
 We will be specific later regarding the value of $T_{\max}$, but for now we simply assume we have a value such that $t_i \in [0,T_{\max}]$ is a redundant constraint in model~\eqref{prob:extensive}.
-\\
-	\newline
+
 	We assume that $\Omega = \{1,2,\ldots,|\Omega|\}$ is such that $\omega < \omega^\prime$ implies $H^\omega \le H^{\omega^\prime}$ with strict inequality if the realizations of $H$ are distinct, and we let $H^0 \equiv 0 \le H^1$ and $H^{|\Omega|+1} \equiv T_{\max} \ge H^{|\Omega|}$.
@@
 	\end{definition}
-	\noi With the possible exceptions of $\underbar{H}^1$ and $\bar{H}^{|\cQ_i|}$, each \(\underbar{H}^q\) and \(\bar{H}^q\) corresponds to a disruption time of some scenario, and a simple example is illustrated in Figure~\ref{fig:simplePart} in which we have five scenarios, \(\Omega = \{1,2,3,4,5\}\).
+
+	With the possible exceptions of $\underbar{H}^1$ and $\bar{H}^{|\cQ_i|}$, each \(\underbar{H}^q\) and \(\bar{H}^q\) corresponds to a disruption time of some scenario, and a simple example is illustrated in Figure~\ref{fig:simplePart} in which we have five scenarios, \(\Omega = \{1,2,3,4,5\}\).
 The partition has three intervals as illustrated.
@@
 	\end{figure}
-	\noi For each activity \(i \in I\) the first-stage start time \(t_i\) lies an interval of \(\cP_i\), and we introduce a first-stage indicator variable:
+
+	For each activity \(i \in I\) the first-stage start time \(t_i\) lies an interval of \(\cP_i\), and we introduce a first-stage indicator variable:
 %	\begin{equation}
@@
 If we can fix the \(G_i\) for all \(i \in I\) to either 0 or 1 the resulting optimality cuts will be tight.
-\\
+
 %	\newline
@@
 	\begin{proof}
-			Constraint~\eqref{cons:nonnegt} enforces the lower bound of $0$. \\
+		Constraint~\eqref{cons:nonnegt} enforces the lower bound of $0$.
 		%under our assumption that $D_{ik} + d_{ik}^\omega \ge 0$ for all $(i,k) \in \cA$, $\omega \in \Omega$. \\
-			\newline 
 		By hypothesis \(t_k^0 - t_i^0 \geq D_{ik}, \forall (i,k) \in \cA\) since \(t_i^0\) is the longest \(S\)-\(i\) path of \(\mathcal{G}\) in which the arc length of \((i,k) \in \cA\) is \(D_{ik}\) and in which no crashing is allowed.
 We prove the upper bound on \(t_i^*\) by contradiction.
-\\
-			\newline
+
 		Suppose there does not exist a \(t^*\) such that \(t^*_i \in [0,H^{|\Omega|} + t_i^0],\ \forall i \in I\).
@@
 For validity, we check if constraints~\eqref{cons:newBoundsm} matches the logic when \(G_i\) is binary, while for effectiveness, we need to compare the feasible range of \(G\) in constraints~\eqref{cons:Grange} and that specified by constraints~\eqref{cons:newBoundsm}.
-\\
-	\newline
+
 	For a specific \(i \in I\), constraints~\eqref{cons:newBoundsm} can be rewritten using \(\hat{q}\):
@@
             \EndFor
-			\State Let \(\ell = \ell + 1\);
+            %\State Let \(\ell = \ell + 1\);
 			%\State For each \(\omega \in \Omega\), 
@@
 			\State Refine the partition and obtain the new partition \(\cP^{\ell + 1}\) and its indexed sets \(\cQ^{\ell + 1}\); \label{alg:refine_partition}
-			%			\State Let \(\ell = \ell + 1\);
-			\State Update previously generated cuts in \(\cP^\ell\) to the form of~\eqref{cons:updatedcut};
+			\State Update previously generated cuts to the form of~\eqref{cons:updatedcut};
 			\EndIf
+			\State Let \(\ell = \ell + 1\);
 			\vspace{0.1cm}
@@
 	\end{algorithm}
+
 %	\tcr{Do we need to make some assumption on $\delta$ relative to $\epsilon$? Suppose $\delta$ is huge; we'll never add a cut.}
-	\noi We prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
+	We prove Algorithm~\ref{alg:Cut} converges in finite number of iterations.
 Since every partition update is a refinement and we have a finite set of scenario \(\Omega\), we can prove the finite convergence of Algorithm~\ref{alg:Cut} as long as with the finest partition we reach the optimum of problem~\eqref{prob:extensive}.
-	%	We let $\cH=\{H^\omega \, | \, \omega \in \Omega \}$ denote the set of (distinct) disruption times.
-When a specific disruption time has scenarios with multiple magnitudes we have $|\cH| < |\Omega|$.
-
-	\newpage
+%	We let $\cH=\{H^\omega \, | \, \omega \in \Omega \}$ denote the set of (distinct) disruption times. When a specific disruption time has scenarios with multiple magnitudes we have $|\cH| < |\Omega|$.
 
@@
 	\subsection{Pruning Partitions Using Bound Tightening} \label{subsec:FBBT}
-	Feasibility-based and optimization-based bound tightening schemes have been proved powerful in mixed integer nonlinear programming to improve computational performance~\citep[e.g.,][]{belotti2012fbbt,coffrin2015strengthening,sundar2018OBBT}.
+	Feasibility-based and optimization-based bound tightening schemes have been proved powerful in mixed-integer nonlinear programming to improve computational performance~\citep[e.g.,][]{belotti2012fbbt,coffrin2015strengthening,sundar2018OBBT}.
 A feasibility-based bound tightening (FBBT) process is suitable for our problem because the precedence relationships limit the start times of  activities.
@@
 	The bound tightening process starts with a set of initial bounds \(\underbar{t}_i = 0\) and \(\bar{t}_i = T_{\max}\) for each \(i \in I\).
-We solve model~\eqref{prob:btminmax} iteratively and update \(\bar{t}_i\) and \(\underbar{t}_i\) until the bounds converge for every \(i \in I\).\\
-	\newline
-	We run FBBT at the beginning of our decomposition method to provide the initial partition \(\cP^0\) to start Algorithm~\ref{alg:Cut}.
+We solve model~\eqref{prob:btminmax} iteratively and update \(\bar{t}_i\) and \(\underbar{t}_i\) until the bounds converge for every \(i \in I\).
+
+	We run FBBT at the beginning of our decomposition method to provide the initial partition~\(\cP^0\) to start Algorithm~\ref{alg:Cut}.
 If we can tighten the bounds of some activities, for example, by branch-and-bound or heuristics, we can run FBBT to tighten the bounds for all activities, which leads to a tighter formulation of the subproblems, \((S^{\omega}_{\cP})\), as further detailed in Section~\ref{subsec:bbpartition}.
@@
 Solving such a model provides a feasible first-stage solution \((\hat{t},\hat{x})\), which can be used to generate an upper bound for the problem with the larger, original set of scenarios.
-Therefore, we can generate \(N\) small subsets of scenarios from the original scenario set, i.e., \(\Omega_n \subset \Omega,\ n = 1,2,\dots N\), and solve model~\eqref{prob:extensive} with each of those subsets to generate candidate upper bounds, and select the one with the smallest expected project span under $\Omega$.
-\\
-	\newline
+Therefore, we can generate \(N\) small subsets of scenarios from the original scenario set, i.e., \(\Omega_n \subset \Omega,\ n = 1,2,\dots,N\), and solve model~\eqref{prob:extensive} with each of those subsets to generate candidate upper bounds, and select the one with the smallest expected project span under $\Omega$.
+
 	In generating \(\Omega_n\), we observe that it is beneficial to have diverse scenarios within each subset.
 	%in a similar distribution as the original scenario set. 
-	As above, We sort the scenarios by disruption time so $H^\omega < H^{\omega+1}$.
+	As above, we sort the scenarios by disruption time so $H^\omega < H^{\omega+1}$.
 For simplicity, suppose each subset has equal size so that \(N \cdot |\Omega_n| = |\Omega|, \ \forall n\).
@@
 	In a Benders' decomposition algorithm, linear programming subproblems can have multiple optimal dual solutions, which means that at a specific incumbent solution, there are multiple valid cuts that could be generated.
-\citet{magnanti1981accelerating} provide a method to select Pareto-optimal cuts, which cannot be dominated by ordinary cuts,
+\citet{magnanti1981accelerating} provide a method to select Pareto-optimal cuts, which cannot be dominated,
 	%in the relative interior of the feasible region of the master problem. It means that the generated Pareto-optimal cuts have a higher value when the integrality is relaxed, 
-	and help tighten the linear programming relaxation of the master program.\\
-	\newline
+	and help tighten the LP relaxation of the master program.
+
 	We apply a technique that pursues the same goal as~\citeauthor{magnanti1981accelerating} in order to tighten cuts at interior points of \((M_\cP)\).
@@
 Next we need to find dual variables that ensure the dual objective value at \((\hat{t},\hat{x},\hat{y})\) is within a small tolerance of \(f^{\omega}_{\cP}(\hat{t},\hat{x},\hat{y})\) (e.g., \(\epsilon_{MW} = 10^{-5}\)), while maximizing the dual objective value at \((t^0,x^0,y^0)\).
-Let the following denote the dual of \((S^\omega_\cP)\) in compact form:
+Let the following denote the dual of \((S^\omega_\cP)\) in compact form, suppressing dependence on $\omega$:
 	\begin{subequations} \label{prob:subdual}
@@
 	\end{subequations}
-	We have suppressed the subproblem dependence on $\omega$; Appendix~\ref{appen:probdual} details the full version of model~\eqref{prob:subdual}.
+	%; Appendix~\ref{appen:probdual} details the full version of model~\eqref{prob:subdual}.
 	We solve the following to obtain Magnanti-Wong cut parameters, \({v}\), \(\pi\), \(\lambda\), and~\(\gamma\):
@@
 
-	\subsection{Cut Selection}
-	The Benders decomposition process within Algorithm~\ref{alg:Cut} takes a multicut approach.
-Many previous works have discussed the benefits and drawbacks of the multicut approach~\citep{birge2011introduction,trukhanov2010adaptive}.
-Although a multicut approach is able to obtain a good outer approximation of the recourse functions quickly, it is harder to solve the mixed integer master problem in later iterations since a large number of cuts are appended to the master problem.
-\\
-	\newline
-	We observe the similar phenomenon that keeping all cuts generated slows down solving the master problem.
-Therefore, we apply a simple cut selection process to only keep the tight cuts at the end of each Benders iteration.
-Refining partitions renders many cuts loose, and the cuts far from the optimal solution in the optimal solution may have a poor quality.
-Therefore, keeping only a limited number of cuts eliminates many redundant constraints, while it still provides a decent lower bound for the master problem.
-With this cut selection process, the number of cuts remaining in the master problem is moderate and a significant computational improvement is achieved.
-Detailed computational results showing this effectiveness of cut selection is presented in Table~\ref{table:time}.
+	\subsection{Cut Selection}\label{subsec:cut_selection}
+	Algorithm~\ref{alg:Cut} is a multi-cut version of Benders' decomposition procedure~\citep{birge1988multicut}.
+	%,trukhanov2010adaptive,birge2011introduction
+	A multi-cut scheme can converge in fewer iterations, but each iteration is typically more computationally expensive.
+The latter issue tends to exacerbate as the algorithm proceeds and cuts accumulate, particularly when the master problem is a mixed-integer program.
+
+	As we discuss in the next section, when naively keeping all cuts, we see that the time required to solve the master problem can grow quickly as the algorithm proceeds.
+Therefore, we limit the number of cuts and only keep those that have been tight most recently at the end of each Benders' iteration.
+Refining a partition can yield many loose cuts.
+Therefore, keeping only a limited number of cuts eliminates unnecessary constraints, while still providing a valuable lower bound and reducing computational effort.
+%Detailed computational results showing this effectiveness of cut selection is presented in Table~\ref{table:time}.
+
+	%\tcr{Saying that we only keep the tight cuts is probably not a good idea.
+This can (in simpler settings) provably lead to cycling, where you delete cuts, add the same cuts again, etc.
+So, I modified what we have above.}
 
 	\subsection{Refining Partitions}\label{subsec:refine} 
-	In this section we first discuss how a partition is refined in step~\ref{alg:refine_partition} of Algorithm~\ref{alg:Cut}. 
+	Here, we indicate how a partition is refined in step~\ref{alg:refine_partition} of Algorithm~\ref{alg:Cut}. 
 	%There could be many rules to refine the partition. 
 	The most significant contributor to the optimality gap is that variable \(G\) can take fractional values in the relaxed problem~\((S_{\cP}^\omega)\).
-For example, if \(d_{ik}^\omega \gg D_{ik}\) then \(G_i\) can take a fractional value far from an optimal value.
+For example, if \(d_{ik}^\omega \gg D_{ik}\) then \(G_i\) can take a fractional value far from optimal.
 	%For example, \(G_i\) should take value \(1\) when activity \(i\) starts after the disruption, but solving LP relaxation may output an optimal \(G_i\) as close to 0. 
 	This can significantly alter the duration between activity \(i\) and \(k\) (see constraint~\eqref{cons:subSep}) in the LP relaxation, and thus create a large gap between the relaxation and the original mixed-integer subproblem.
-Let \(N_p\) be a parameter that denotes the number of new partitions for each activity \(i \in I\); we use $N_p=5$ in our computation.
+Let \(N_p\) be a parameter that limits the number of new partitions for each activity \(i \in I\); we use $N_p=5$ in our subsequent computation, unless stated otherwise.
 Suppose subproblem \((S_\cP^\omega)\) has as part of its solution \({G}_i^\omega, i \in I \).
@@
 	\subsection{Branch-and-Cut Algorithm}\label{subsec:bbpartition}
-	In Algorithm~\ref{alg:Cut} we iteratively refine the partition defining the $y$-variables, and each time we solve master~\eqref{prob:masterTightened} we must solve a mixed integer linear program, which we do with a commercial integer programming solver.
+	In Algorithm~\ref{alg:Cut} we iteratively refine the partition defining the $y$-variables, and each time we solve master~\eqref{prob:masterTightened} we must solve a mixed-integer linear program, which we do with a commercial solver.
 	Algorithm~\ref{alg:Cut} is not a branch-and-cut~(B\&C) algorithm in that it does not adaptively generate different cuts at different parts of a branch-and-bound tree.
-As an improvement of Algorithm~\ref{alg:Cut}, here a B\&C algorithm is proposed, which involves a branch-and-bound (B\&B) tree with nodes that we manage.
-The root node in our B\&B tree involves the original partition, and we solve that node using the Benders' decomposition, which iteratively adds cuts to master~\eqref{prob:masterTightened} until the problem is solved for the fixed partition, as in Algorithm~\ref{alg:Cut}.
+As a potential improvement to Algorithm~\ref{alg:Cut}, we propose here a B\&C algorithm, which involves a branch-and-bound (B\&B) tree with nodes that we manage.
+The root node in our B\&B tree involves the original partition, and we solve that node using Benders' decomposition, which iteratively adds cuts to master~\eqref{prob:masterTightened} until the problem is solved for the fixed partition, as in Algorithm~\ref{alg:Cut}.
 In the B\&C algorithm we recursively branch on a continuous variable $t_i$ via $t_i \le H^\omega$ and $t_i \ge H^\omega$ for some $i$-$\omega$ pair.
@@
 Moreover, in our implementation we solve the nodes in our B\&B tree in parallel.
-\\
-	\newline
+
 	%Algorithm~\ref{alg:Cut} can be further enhanced by a branch-and-cut process, which helps reduce the number of binary variables added to the master and enables solving simpler integer programs in parallel.
@@
     	\begin{eqnarray}
-		&& \mbox{select} \ \omega \in \mbox{argmax}_{\omega \in \Omega}  \left [ f^{{\omega}}(\hat{t},\hat{x}) - f^{{\omega}}_{\cP}(\hat{t},\hat{x},\hat{y}) \right ] \label{branch:select_omega} \\
-		&& \mbox{select} \ i \in \mbox{argmax}_{i \in I} \left [ \rho_i^\omega \right ]. \label{branch:select_i}
+    	&& \mbox{select} \ \omega \in \mbox{argmax}_{\omega \in \Omega}  \left [ f^{{\omega}}(\hat{t},\hat{x}) - f^{{\omega}}_{\cP}(\hat{t},\hat{x},\hat{y}) \right ] \label{eqn:branchselo} \\
+    		&& \mbox{select} \ i \in \mbox{argmax}_{i \in I} \left [ \rho_i^\omega \right ]. \label{eqn:branchseli}
     	\end{eqnarray}
     \end{subequations}	
-	In~\eqref{branch:select_omega} we select the scenario~\({\omega}\) with the largest relaxation gap.
-Then in~\eqref{branch:select_i} we select the activity with the largest \(\rho_{i}^{{\omega}}\) from equation~\eqref{eqn:define_rho}.
+    In~\eqref{eqn:branchselo} we select the scenario~\({\omega}\) with the largest relaxation gap.
+Then in~\eqref{eqn:branchseli} we select the activity with the largest \(\rho_{i}^{{\omega}}\) from equation~\eqref{eqn:define_rho}.
 This defines the $i$-$\omega$ pair for branching on $t_i \le H^\omega$ versus $t_i \ge H^\omega$ using the $y$-variables in a form of SOS branching.
-\\
 	%subproblem of scenario \(\hat{\omega}\) has a fractional \(G_i\).
@@
 Correspondingly, the partition \(\cQ_{\hat{i}}\) will be refined because branching creates a natural partition at \(H^{\hat{\omega}}\), and some \(y_{\hat{i}}^{q}\) for the new partition will be forced to take value 0.\\
-	\newline
+
 	After a branch, for each child node we refine the partition on all activities \(i \in I\) according to Section~\ref{subsec:refine}.
@@
 	The children inherit the parent node's cuts, updated in a similar fashion as inequality~\eqref{cons:updatedcut}.
-To set up notation for Algorithm~\ref{alg:CutBB},  suppose for activity \(i \in I\), the current B\&B node, say node \(n\), has a partition \(\cP_i^n\) indexed by set \(\cQ_i^n\), and its parent node \(m\) has a partition \(\cP_i^m\) indexed by set \(\cQ_i^m\).
+To set up notation for Algorithm~\ref{alg:CutBB}, suppose that for activity \(i \in I\) the current B\&B node, say node \(n\), has a partition \(\cP_i^n\) indexed by set \(\cQ_i^n\), and its parent node \(m\) has a partition \(\cP_i^m\) indexed by set \(\cQ_i^m\).
 Then, the cuts inherited from node \(m\) are updated for node \(n\) as:
@@
 The parent node is marked as fathomed after a refinement, and we select the next available node with the smallest lower bound.
-\\
-	\newline
+
 	Putting all these pieces together, we summarize our partition-based branch-and-cut decomposition method in Algorithm~\ref{alg:CutBB}.
@@
 
-	\subsection{Numerical Example of the Partitioning Based Branch-and-Bound Decomposition Method} \label{subsec:numeg}
-	In this section, we use an example to illustrate Algorithm~\ref{alg:CutBB} with $\epsilon=0$.
-We consider the network with five activities, \(i \in I = \{1,2,3,4,5\}\), shown in Figure~\ref{fig:fiveAct}.
+	\subsection{Algorithm~\ref{alg:CutBB}: Numerical Example}\label{subsec:numeg}
+	We illustrate Algorithm~\ref{alg:CutBB} on an example with $\epsilon=0$. We consider the network with five activities that accompany the source and terminal, as shown in Figure~\ref{fig:fiveAct}. 
 	\begin{figure}[H]
@@
 	\end{figure}
-	\noi Each activity has a duration \(D_i = 1,\ \forall i \in I\), and can be crashed with a single option that decreases the duration by 90\% with one unit of resource consumption, i.e., \(e_{i1} = 0.9,\ \forall i \in I\), and we let \(B = 2\).
+	\noi Each of the five activities has unit duration, and can be crashed with a single option that decreases the duration by 90\% with one unit of resource consumption, i.e., \(e_{i1} = 0.9,\ \forall i \in I \setminus \{S, T\}\), and we let \(B = 2\).
 The probability of no disruption is \(p^0 = 0.2\), and the disruption can occur at four discrete time points, \(H^1 = 1,\ H^2 = 2,\ H^3 = 3,\ H^4 = 4\), with equal probability \(p^\omega = 0.2,\ \forall \omega \in \Omega = \{1,2,3,4\}\).
-The increase in duration is \(d_i^\omega = 10,\ \forall i \in I, \omega \in \Omega\).
-From this setup, we can bound the starting time of activity from above by \(T_{\max} = 9\).
-\\
-	\newline
-	\tcr{We first tighten the bound of starting time for each activity.
-Necessary?
-Seems like a stand-alone sentence.} We start Algorithm~\ref{alg:CutBB} with the initial node \(1\), and initial partition:
+The increase in duration under a disruption is \(d_i^\omega = 10\) for each activity-scenario pair.
+By Proposition~\ref{prop:bounds} we can bound the start time of each activity from above by \(T_{\max} = 9\).
+
+	Running the FBBT procedure of Section~\ref{subsec:FBBT} we obtain $\underbar{t}_1=0, \, \underbar{t}_2=0.1, \, \underbar{t}_3=0.2, \, \underbar{t}_4=1.2,\underbar{t}_5=2.2$, and $\underbar{t}_T=3.2$.
+Given these values, and the realizations of $H^\omega$, we initialize node 1 of Algorithm~\ref{alg:CutBB} with the following partition, which precludes certain intervals for activities 4, 5, and $T$:
 	\begin{align*}
-	&\cP_1^1 = \{(0,9)\} \qquad \qquad \;\; \cQ_1^1 = \{1\}\\
-	&\cP_2^1 = \{(0,9)\} \qquad \qquad \;\; \cQ_2^1 = \{1\}\\
-	&\cP_3^1 = \{(0,9)\} \qquad \qquad \;\; \cQ_3^1 = \{1\}\\
-	&\cP_4^1 = \{(0,1),(1,9)\} \qquad  \cQ_4^1 = \{1,2\} \qquad y_4^1 = 0\\
-	&\cP_5^1 = \{(0,2),(2,9)\} \qquad  \cQ_5^1 = \{1,2\} \qquad y_5^1 = 0\\
-	&\cP_T^1 = \{(0,3),(3,9)\} \qquad  \cQ_T^1 = \{1,2\} \qquad y_T^1 = 0.
+	    &\cP_1^1 = \{[0,9]\} \qquad \qquad \;\; \cQ_1^1 = \{1\}\\
+	    &\cP_2^1 = \{[0,9]\} \qquad \qquad \;\; \cQ_2^1 = \{1\}\\
+	    &\cP_3^1 = \{[0,9]\} \qquad \qquad \;\; \cQ_3^1 = \{1\}\\
+	    &\cP_4^1 = \{[0,1],[1,9]\} \qquad  \cQ_4^1 = \{1,2\} \qquad y_4^1 = 0\\
+	    &\cP_5^1 = \{[0,2],[2,9]\} \qquad  \cQ_5^1 = \{1,2\} \qquad y_5^1 = 0\\
+	    &\cP_T^1 = \{[0,3],[3,9]\} \qquad  \cQ_T^1 = \{1,2\} \qquad y_T^1 = 0.
 	\end{align*}
-	We can perform the Benders' decomposition on node \(1\).
-The process converges to an optimal value \(z^*_{\cP} = 4.072\).
-In the process, we update the upper bound with the best \(z^*\) found in the process, as \(UB = 6.607\).
+	Excecuting steps 6-18 of the algorithm, we solve node 1 with Benders' decomposition, converging to an optimal value of \(z^*_{\cP} = 4.072\), and in the process, we obtain an upper bound of \(UB = 6.607\).
 The optimal solution is:
@@
 	    & \hat{t}_3 = 1.899 \qquad \; \hat{x}_{31} = 0.1124\\
-	& \hat{t}_4 = 2.798 \qquad \; \hat{x}_{41} = 0.8860\\
-	& \hat{t}_5 = 2.997 \qquad \; \hat{x}_{51} = 0.8892\\
+	    & \hat{t}_4 = 2.798 \qquad \; \hat{x}_{41} = 0.8892\\
+	    & \hat{t}_5 = 2.997 \qquad \; \hat{x}_{51} = 0.8860 \\
 	    & \hat{t}_T = 3.2.
 	\end{align*}
-	At this solution, the largest relaxation gap is incurred at \(\hat{\omega} = 1\) with a value \(8.75\).
-The optimal solution to the subproblem \((S^1_\cP)\) has a fractional solution \(G_3 = 0.125\).
-Since the optimality gap at node 1 is larger than 0, we branch on scenario \(1\) and activity \(3\), creating two children nodes, node \(2\) and node \(3\).
+	 At this solution, by equation~\eqref{eqn:branchselo} the largest relaxation gap is incurred at \({\omega} = 1\), 
+	 %with a value \(8.75\). 
+	 and equation~\eqref{eqn:branchseli} corresponds to activity~3, which has a fractional solution of \(G_3 = 0.125\) in subproblem~\((S^1_\cP)\).
+We branch on $i$-$\omega$ pair 3-1, creating two children, node~\(2\) and node~\(3\).
 Node 2 has an additional constraint, \(t_3 \geq H^1 = 1\) and node 3 has an additional constraint \(t_3 \leq H^1 = 1\).
-For each activity \(i \in I\), we refine the partition by selecting the scenario with the largest nonzero \(\rho_i^\omega\) for \(\omega \in \Omega\).
-If for an activity \(i \in I\), there is no scenario with positive \(\rho_i^\omega\), we do not refine the partition for such activity.
-As stated in Section~\ref{subsec:FBBT}, we can solve a series of linear programs~\eqref{prob:btminmax} to tighten the bounds of starting times for node 2 and node 3, respectively with their additional constraint \(t_3 \geq 1\) and \(t_3 \leq 1\).
-After refinement and bound tightening, we obtain the partition for node 2 and node 3 as follows:
+For each activity \(i\), we refine the partition by selecting the scenario with the largest nonzero \(\rho_i^\omega\) for \(\omega \in \Omega\), i.e., for simplicity we use $N_p=1$; see Section~\ref{subsec:refine}.
+If the largest \(\rho_i^\omega\) is zero for activity $i$, we do not refine that activity's partition.
+We again apply the ideas of Section~\ref{subsec:FBBT}, and solve a series of linear programs~\eqref{prob:btminmax} to tighten the bounds of starting times for nodes~2 and~3, accounting for their respective additional constraints \(t_3 \geq 1\) and \(t_3 \leq 1\).
+This refinement and bound-tightening process yields:
  	\begin{align*}
  	    & \text{Node 2:}\\
-	&\cP_1^2 = \{(0,9)\} \qquad \qquad \qquad \quad \cQ_1^2 = \{1\}\\
-	&\cP_2^2 = \{(0,9)\} \qquad \qquad \qquad \quad \cQ_2^2 = \{1\}\\
-	&\cP_3^2 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_3^2 = \{1,2\} \qquad \quad  y_3^1 = 0\\
-	&\cP_4^2 = \{(0,1),(1,2),(2,9)\} \qquad  \cQ_4^2 = \{1,2,3\} \qquad y_4^1 = 0\\
-	&\cP_5^2 = \{(0,2),(2,3),(3,9)\} \qquad  \cQ_5^2 = \{1,2,3\} \qquad y_5^1 = 0\\
-	&\cP_T^2 = \{(0,3),(3,4),(4,9)\} \qquad  \cQ_T^2 = \{1,2,3\} \qquad y_T^1 = 0.
+	    &\cP_1^2 = \{[0,9]\} \qquad \qquad \qquad \quad \cQ_1^2 = \{1\}\\
+	    &\cP_2^2 = \{[0,9]\} \qquad \qquad \qquad \quad \cQ_2^2 = \{1\}\\
+	    &\cP_3^2 = \{[0,1],[1,9]\} \qquad \qquad \;\; \cQ_3^2 = \{1,2\} \qquad \quad  y_3^1 = 0\\
+	    &\cP_4^2 = \{[0,1],[1,2],[2,9]\} \qquad  \cQ_4^2 = \{1,2,3\} \qquad y_4^1 = 0\\
+	    &\cP_5^2 = \{[0,2],[2,3],[3,9]\} \qquad  \cQ_5^2 = \{1,2,3\} \qquad y_5^1 = 0\\
+	    &\cP_T^2 = \{[0,3],[3,4],[4,9]\} \qquad  \cQ_T^2 = \{1,2,3\} \qquad y_T^1 = 0
 	\end{align*}
@@
  	    & \text{Node 3:}\\
-	&\cP_1^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_1^3 = \{1,2\} \qquad \quad y_1^2 = 0\\
-	&\cP_2^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_2^3 = \{1,2\} \qquad \quad y_2^2 = 0\\
-	&\cP_3^3 = \{(0,1),(1,9)\} \qquad \qquad \;\; \cQ_3^3 = \{1,2\} \qquad \quad y_3^2 = 0\\
-	&\cP_4^3 = \{(0,1),(1,2),(2,9)\} \qquad  \cQ_4^3 = \{1,2,3\} \qquad y_4^1 = 0\\
-	&\cP_5^3 = \{(0,2),(2,3),(3,9)\} \qquad  \cQ_5^3 = \{1,2,3\} \qquad y_5^1 = 0\\
-	&\cP_T^3 = \{(0,3),(3,4),(4,9)\} \qquad  \cQ_T^3 = \{1,2,3\} \qquad y_T^1 = 0.
+	    &\cP_1^3 = \{[0,1],[1,9]\} \qquad \qquad \;\; \cQ_1^3 = \{1,2\} \qquad \quad y_1^2 = 0\\
+	    &\cP_2^3 = \{[0,1],[1,9]\} \qquad \qquad \;\; \cQ_2^3 = \{1,2\} \qquad \quad y_2^2 = 0\\
+	    &\cP_3^3 = \{[0,1],[1,9]\} \qquad \qquad \;\; \cQ_3^3 = \{1,2\} \qquad \quad y_3^2 = 0\\
+	    &\cP_4^3 = \{[0,1],[1,2],[2,9]\} \qquad  \cQ_4^3 = \{1,2,3\} \qquad y_4^1 = 0\\
+	    &\cP_5^3 = \{[0,2],[2,3],[3,9]\} \qquad  \cQ_5^3 = \{1,2,3\} \qquad y_5^1 = 0\\
+	    &\cP_T^3 = \{[0,3],[3,4],[4,9]\} \qquad  \cQ_T^3 = \{1,2,3\} \qquad y_T^1 = 0.
 	\end{align*}
-	We mark node 1 as complete and move on to node 2, which is the available node with the smallest lower bound.
-Processing node 2 with Benders' decomposition yields an optimal solution of 6.1111.
-The node 2 branches to node 4 and 5, which inherit the cuts and the lower bound from node 2.
-\\
-	\newline
-	The next available node with the smallest lower bound is node 3. Node 3 yields an optimal value of 6 and an optimal solution as: 
+	We fathom node 1 and nodes~2 and~3 inherit its cuts and lower bound.
+Breaking the tie arbitrarily, we select and then solve node~2 with Benders' decomposition and obtain an optimal value of $z^*_{\cP} = 6.111$.
+Node~2 then branches to nodes~4 and~5, which inherit the cuts and the lower bound from node~2.
+The upper bound value remains $UB=6.607$.
+
+	Node 3 now has the smallest lower bound, 4.072, among unfathomed nodes, and yields an optimal value of $z^*_{\cP} = 6$ and optimal solution: 
 	\begin{subequations} \label{eqn:optSol}
@@
     	\end{subequations}
-	The relaxation gap is zero, which means that the upper bound is updated to \(UB = 6\) as well.
-This leads to a zero optimality gap at node 3.
-Node 4 and node 5 will not be processed since their lower bounds are larger than the current upper bound.
-The algorithm terminates with the best solution in~\eqref{eqn:optSol}.
-The recorded best \(G\) variables indicate that activity 1,2 and 3 start before disruption scenario \(1\), activity 4 starts before disruption scenario \(2\), and activity 5 starts before disruption scenario \(3\).
-The optimal objective value is 6.
+    In the process of solving node 3, we also obtain a tighter global upper bound of $UB=6$ associated with solution~\eqref{eqn:optSol}, and hence the optimality gap at node~3 is zero.
+Nodes~4 and~5 can now be fathomed because their lower bound of 6.111 exceeds $UB$.
+The algorithm terminates with the optimal solution in equation~\eqref{eqn:optSol}, and the corresponding \(G\)-variables indicate that activities 1, 2, and 3 start before disruption scenario \(1\), activity 4 starts before disruption scenario \(2\), and activity 5 starts before disruption scenario \(3\).
+The optimal objective function value is $6= {0.6 \cdot \left [ 3.2 \right]  + 0.2 \cdot \left [ 2+ 11 \cdot (1-0.9 \cdot 8/9)+11 \right ]  + 0.2 \cdot \left [ 3 +11\cdot (1-0.9 \cdot 8/9) \right ]}$.
 
 \section{Experimental Results} \label{sec:results}
+\tcr{Read all the red comments to the end before doing anything.}
+
 %	\textcolor{blue}{Test results:
@@
 	\begin{enumerate}
-		\item What is the value of model~\eqref{prob:extensive} that takes account of randomness in both timing and magnitude of a disruption?
-In other words, what are other alternative solutions that are easier to obtain but possibly inferior?
-How does the quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
-		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
-		\item What is the time improvement of Algorithm~\ref{alg:CutBB} compared to solving extensive formulation~\eqref{prob:extensive} using a state-of-the-art MIP solver?
-How effective are the upper bound generation and Magnanti-Wong cuts?
+		\item What is the value of model~\eqref{prob:extensive}, which takes account of randomness in both the timing and magnitude of a disruption? In other words, 
+		%what are other alternative solutions that are easier to obtain but possibly inferior? 
+		how does the quality of the solution to model~\eqref{prob:extensive} compare to those of simpler alternatives?
+		\item How does the solution quality improve as the number of samples grows in a sample average approximation? 
+		\item How do Algorithms~\ref{alg:Cut} and~\ref{alg:CutBB} perform versus solving the extensive formulation~\eqref{prob:extensive} using a state-of-the-art MIP solver?
+How effective are the computational enhancements of upper-bound generation, Magnanti-Wong cuts, and the cut-selection procedure from Sections~\ref{subsec:HUB}-\ref{subsec:cut_selection}?
 	\end{enumerate}
-	We first introduce the test case PERT networks and distribution information used to characterize uncertainty in Section~\ref{subsec:testcases}.
-In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of the solution to model~\eqref{prob:extensive} compared to the alternative ones.
-We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}.
-Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:CutBB} compared to solving extensive formulation.
-\\
-	\newline
+	Section~\ref{subsec:testcases} introduces the PERT networks and probability distributions characterizing the disruptions for our test cases.
+In Section~\ref{subsec:value} we construct deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and compare the quality of the resulting solutions to those of model~\eqref{prob:extensive}.
+We test how the sample size affects solution quality and requisite computational effort in Section~\ref{subsec:budget}.
+Finally, in Section~\ref{subsec:time} we compare the performance of Algorithms~\ref{alg:Cut} and~\ref{alg:CutBB} to solving extensive formulation directly.
+
 	All tests are run on a server with 30 Intel Xeon cores at 3.1 GHz and 256 GB of RAM.
-For Algorithm~\ref{alg:CutBB}, each node is solved by 6 cores and we allow at most 5 nodes to be solved simultaneously so that the maximum number of cores used at any time is still 30.
+For Algorithm~\ref{alg:CutBB}, each node is solved by 6 cores and we allow at most 5 nodes to be solved simultaneously so that the maximum number of cores used at any time is again 30.
 All models are constructed using version 0.18.0 of the JuMP package~\citep{DunningHuchetteLubin2017} on the Julia platform.
-All linear programs and mixed integer programs are solved by Gurobi 8.01~\citep{gurobi2016} with default parameters.
+All linear programs and mixed-integer programs are solved by Gurobi 8.01~\citep{gurobi2016} with the integer feasibility tolerance and the primal feasibility tolerance both set to \(10^{-8}\).
+In addition, we solve all problems using an optimality-gap tolerance of $10^{-2}$, including Algorithm~\ref{alg:CutBB}'s $\epsilon=10^{-2}$ as well as $\delta=10^{-4}$.
 
@@
 	%	\end{itemize}}
-	\noi Although it is easy to construct an activity network with randomly distributed disruption time and magnitude, not all instances constructed can well illustrate properties of our problem.
-Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value.
-We use an activity network from~\citet{plambeck1996sample} with 11 activities, and % and the other with 110 activities.
+
+	%Although it is easy to construct an activity network with randomly distributed disruption time and magnitude, not all instances constructed can well illustrate properties of our problem. Therefore, 
+	We construct our test cases based on two activity networks from the literature, along with one we create from ``scratch'' and one we generate randomly.
+In particular, we use an activity network from~\citet{plambeck1996sample} with 11 activities, and % and the other with 110 activities.
 	one from~\citet{Elmaghraby77} with 19 activities. 
@@
 	 %and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}. 
-	In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities. Data of all test cases are detailed in Appendix~\ref{appen:data}.\\
-	\newline
-	For every test case, the timing of the disruption is randomly generated from a lognormal distribution since its value has to be nonnegative.
-The disruption magnitude of activities follows an exponential distribution of which the parameter differs among activities since the exponential distribution is widely used to model the service time~\citep{ross1996stochastic}.
+	 In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities. Data for all four test cases are detailed in Appendix~\ref{appen:data}.
+
+	For each test case, the timing of the disruption is a discrete random variable sampled from a lognormal distribution, which is commonly used to model failure times~\citep[e.g.,][]{crow1987lognormal,mullen1998lognormal}.
+The magnitude of the disruption for each activity follows an exponential distribution (which we again sample) whose parameter varies among the activities; the exponential distribution is widely used to model activity durations such as service times~\citep[e.g.,][]{ross1996stochastic}.
 	%. The exponential distribution can best model the drastic change caused by a disruption.
 	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
-	In this section, we compare the quality of five solutions obtained under alternative problem settings to show the value of modeling random timing and magnitude of the disruption.
-First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET").
-Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), timing is random but magnitude is at its expected value (denoted as ``\(H\)Only"), and magnitude is random but timing is at its expected value (denoted as ``\(d\)Only").
-Finally, we construct the fully stochastic model where both timing and magnitude are random (denoted as ``FULL").
-We sample \(500\) scenarios to solve for solutions of \(H\)Only, \(d\)Only and Full settings, and we generate 20 batches of samples of size \(5000\) to estimate an upper bound for each candidate solution.
-We present the upper bound estimation for those five candidate solutions in Figure~\ref{fig:value} and the \(95\%\) confidence interval in Table~\ref{table:value}.\\
+	We compare the quality of five solutions, one from solving model~\eqref{prob:extensive} and four from solving simpler alternatives, to investigate the value of modeling both the random timing and random magnitude of a disruption.
+First, we can obtain a solution by solving a deterministic model~\eqref{prob:static}, assuming no disruption occurs, i.e., $d^\omega=0$ (denoted ``DET").
+Three semi-stochastic alternative models can be solved assuming: both the timing and magnitude of the disruption are deterministic at their expected values (denoted ``EXP"); the timing is random but magnitude is fixed at its expected value (denoted ``\(H\)Only"); and, the magnitude is random but timing is fixed at its expected value (denoted ``\(d\)Only").
+Finally, we construct the fully stochastic model~\eqref{prob:extensive} in which both the timing and magnitude are random (denoted ``FULL").
+We sample \(500\) scenarios to solve \(H\)Only, \(d\)Only, and FULL.
+Twenty batches of samples of size 5,000 are used to estimate an upper bound for each candidate solution.
+The upper bound point estimate for those five candidate solutions is shown in Figure~\ref{fig:value}, and the \(95\%\) confidence interval is shown in Table~\ref{table:value}.
+\tcr{20 batches of size 5000 for the UB.
+This is the same as simply using a sample size of 100,000.
+The point estimates are identical.
+The sample variance is calculated slightly differently, but is the same in expectation.
+Right?} \tcb{Yes, the point estimates should have an identical mean no matter how large the sample size is.
+20 batches are used just to calculate the variance.} \tcr{But, the point is that the sample variance of the 100,000 points ought to be the same as the sample variance of the 20 batches of 5,000: $\mbox{var} \frac{1}{n} \sum_{i=1}^n X_i = \frac{1}{n} \mbox{var} X_1$.
+and $\mbox{var} \frac{1}{\ell} \sum_{j=1}^{\ell} \bar{X}^j_m = \frac{1}{\ell} \mbox{var}  \bar{X}_m = \frac{1}{\ell} \frac{1}{m} \mbox{var} X_1$.
+So, if $n=$100,000 and $\ell=20$ and $m=$5,000 then it should be the same.
+In other words, you can compute sample variance of 100,000 points or sample variance of 20 sample means, and it's the same.
+So, why batch at all?
+(Here, I've put aside the dividing by $n$ versus $n-1$ in the sample variance calculation, which does create small differences.) For the paper, let's just leave it as you have it.
+You can delete all these comments.}
+
 	%by plugging each of these solutions in the SAA problem with the original \(500\) samples, and we call this estimation, \(z^*\), as ``in-sample" since these samples are also used to obtain solutions.
@@
 		\includegraphics[width=0.8\textwidth]{graphValues}
-		\caption{Comparison of quality of alternative solutions to the problem~\eqref{prob:extensive}}
+		\caption{Comparison of quality of alternative solutions in which the optimal value of ``FULL'' is rescaled to 1.0}
 		\label{fig:value}
@@
 
-	\noi We align all test cases in the same scale and set the upper bound of FULL as 1 in Figure~\ref{fig:value}.
-It shows that the solution quality is poor without considering the uncertainty of disruption timing.
-The upper bound estimation of DET is at least \(30\%\) larger than that of FULL.
-The upper bound estimations of \(d\)Only and EXP are similar and at least \(10\%\) larger than that of FULL.
-For Case 14, the upper bound estimation of \(H\)Only is \(20\%\) larger than that of FULL.
-Although for other three cases, the upper bound estimation of \(H\)Only is close to that of FULL, the computational effort required to obtain \(H\)Only solution and the fully stochastic solution is on the same level, often much more.
-The test result justifies the value of having a fully stochastic model.
+	Figure~\ref{fig:value} scales the optimal value of each test problem, dividing by that of FULL, and shows that the solution quality can be poor without considering uncertainty in the timing of a disruption.
+DET's upper bound estimate is at least \(20\%\) larger than that of FULL for all test cases.
+The upper bound estimates of \(d\)Only and EXP are similar and at least \(10\%\) larger than that of FULL.
+For Case 14, the upper bound of \(H\)Only is \(20\%\) larger than that of FULL, and is closer to that of FULL for the other three cases.
+That said, given the sample sizes, the computational effort to solve \(H\)Only and FULL are comparable.
+These test results suggest that the solution to the fully stochastic model can outperform solutions to simpler variants.
+In the remainder of this section, we restrict attention to the FULL model.
+
 	%, since we need to include the same number of binary variables and same disruption magnitude brings symmetry issues. 
@@
 			& \thead{DET} & \thead{EXP} & \thead{\(d\)Only} & \thead{\(H\)Only} & \multicolumn{1}{c}{FULL}\\ \hline
-				Case 11	&	575.80 \(\pm\) 16.88	&	454.33\(\pm\) 18.34		&	454.33\(\pm\) 18.34	&	287.05\(\pm\) 14.91  &	287.29\(\pm\) 14.92	\\
-				Case 14	&	3309.27\(\pm\) 177.18	&	2878.65\(\pm\) 176.70 &	2876.42\(\pm\) 176.55	&	3098.05\(\pm\) 133.06	&	2602.97\(\pm\) 110.12	\\
-				Case 19	&	426.09\(\pm\) 10.09	&	389.61\(\pm\) 7.88	&	388.77\(\pm\) 8.43	&	355.29\(\pm\) 7.14	&	356.42\(\pm\) 5.86	\\
-				Case 35	&	1353.80\(\pm\) 21.11	&	1183.74\(\pm\) 18.52	&	1188.93\(\pm\) 19.53	&	1078.57\(\pm\) 17.31	&	1068.29\(\pm\) 17.47	\\
+			Case 11	&	575.80 \(\pm\) 16.88	&	454.33 \(\pm\) 18.34		&	454.33 \(\pm\) 18.34	&	287.05 \(\pm\) 14.91  &	287.29 \(\pm\) 14.92	\\
+            Case 14	&	3309.27 \(\pm\) 177.18	&	2878.65 \(\pm\) 176.70 &	2876.42 \(\pm\) 176.55	&	3098.05 \(\pm\) 133.06	&	2602.97 \(\pm\) 110.12	\\
+            Case 19	&	426.09 \(\pm\) 10.09	&	389.61 \(\pm\) 7.88	&	388.77 \(\pm\) 8.43	&	355.29 \(\pm\) 7.14	&	356.42 \(\pm\) 5.86	\\
+            Case 35	&	1353.80 \(\pm\) 21.11	&	1183.74 \(\pm\) 18.52	&	1188.93 \(\pm\) 19.53	&	1078.57 \(\pm\) 17.31	&	1068.29 \(\pm\) 17.47	\\
 			\hline
@@
 
-	\subsection{Simulation Budget} \label{subsec:budget}
-	We examine the quality of solutions generated from different sizes of samples.
-It is well known that the objective value obtained by SAA approaches the objective function of the original problem as the sample size grows to infinity, and the expected value of the SAA objective value improves as the sample size increases~\citep{shapiro2009lectures}.
-However, when the sample size increases, the computational cost increases as well.
-Understanding how the solution quality changes according to different sample sizes is important to help us decide a proper sample size while achieving a decent solution.
-For each test case, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(|\Omega| \in \{10, 20, 50, 100, 200, 500\}\).
-For each solution, we test against a set of \(5000\) samples and obtain the object value as a point estimation of the upper bound.
-We can also obtain the \(95\%\) confidence interval of the lower bound and the upper bound estimation for each sample size.
-We present the upper bound results in Table~\ref{table:budgetU}, the lower bound results in Table~\ref{table:budgetL} and visualization of the results with Figure~\ref{fig:budget}.
+	\subsection{Solution Quality versus Sample Size} \label{subsec:budget}
+	We examine the quality of solutions obtained by solving SAA problems with different sample sizes.
+In expectation, the optimal value of an SAA problem provides a lower bound on $z^*$, the optimal value of the population problem, and in expectation evaluating a sample-mean objective function of an SAA solution using an independent sample provides an upper bound on $z^* \,$\citep{mak_etal_1999}.
+Both estimates approach~$z^*$ as the sample size grows large~\citep[e.g.,][]{shapiro2009lectures}.
+Of course, the computational effort to solve the corresponding SAA problem grows with the sample size.
+Understanding how the solution quality improves with sample size helps us obtain a high-quality solution without excessive computational effort.
+For each test case, we first solve \(20\) SAA instances of model~\eqref{prob:extensive}, with sample sizes of 10, 20, 50, 100, 200, and 500.
+\tcr{I would not call $|\Omega|$ a sample size if you can avoid it.
+$\Omega$ is the sample space for the population problem as opposed to that of the SAA problem.
+(I removed $|\Omega|$.) You can delete this comment.} For each solution, we obtain a point estimate of the upper bound using the same 5,000 samples.
+We also obtain 95\% confidence intervals associated with both upper- and lower-bound estimators for each sample size.
+We present the upper bound results in Table~\ref{table:budgetU}, the lower bound results in Table~\ref{table:budgetL}, and a visualization of the estimators in Figure~\ref{fig:budget}.
 
@@
 			\hline
-				& \multicolumn{1}{c}{10} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{50} & \multicolumn{1}{c}{100} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{500}  \\ \hline
+	Sample size		& \multicolumn{1}{c}{10} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{50} & \multicolumn{1}{c}{100} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{500}  \\ \hline
 			Case 11	&	326.05	\(\pm\)	80.59	&	293.43	\(\pm\)	24.20	&	290.95	\(\pm\)	28.51	&	283.06	\(\pm\)	12.24	&	280.10	\(\pm\)	6.59	&	278.33	\(\pm\)	2.30	\\
@@
 		\end{tabular}}
-		\caption{Upper bound confidence interval for solutions generated by different budgets}
+		\caption{Upper bound point estimates, and 95\% confidence intervals, for SAA solutions with different sample sizes \tcr{I want to confirm: The confidence intervals are with respect to 20 replications.
+So, for a sample size of 10 you find 20 first-stage decisions.
+You compute the sample mean objective function value for 5000 samples.
+You use the same 5000 samples and compute the confidence interval over the 20 observations.}}
 		\label{table:budgetU}
@@
 			\hline
-				& \multicolumn{1}{c}{10} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{50} & \multicolumn{1}{c}{100} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{500}  \\ \hline
+	Sample size & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{50} & \multicolumn{1}{c}{100} & \multicolumn{1}{c}{200} & \multicolumn{1}{c}{500}  \\ \hline
 			Case 11	&	296.44	\(\pm\)	255.34	&	247.24	\(\pm\)	134.57	&	266.30	\(\pm\)	140.43	&	275.33	\(\pm\)	73.14	&	289.32	\(\pm\)	66.97	&	274.79	\(\pm\)	36.59	\\
@@
 		\end{tabular}}
-		\caption{Lower bound confidence interval for solutions generated by different budgets}
+		\caption{Lower bound point estimates, and 95\% confidence intervals, for SAA solutions with different sample sizes}
 		\label{table:budgetL}
@@
 		\includegraphics[width=\textwidth]{graphBudgets}
-		\caption{Confidence intervals of the lower/upper bound estimation for different sample sizes}
+		\caption{Confidence intervals, and point estimates, of the lower upper bounds for different sample sizes \tcr{Please edit the cropping of the plots so the $y$-axis label isn't cut-off.}}
 		\label{fig:budget}
 	\end{figure}
-	We can see the gap between the upper bound and the lower bound estimation decreases and both estimations become less variant as the sample size increases.
-A decent solution can be obtained by sampling a moderate number of samples, since the upper bound estimation stabilizes when the sample size is greater than \(100\).
-However, to achieve a good lower bound estimation requires a large number of samples.
-This comes from the nature of our uncertainty model, as we need to consider both timing and magnitude of the disruption.
+
+	From the two tables and Figure~\ref{fig:budget}, we can see the gap between the upper- and lower-bound estimators shrinks, and both estimators become less variable as the sample size grows.
+Improvements in the upper-bound estimators are small for sample sizes that exceed 100, and while improvements in lower-bound point estimates can appear larger (see Case 14) they are small relative to sampling error for such sample sizes.
 
 	\subsection{Computational Performance} \label{subsec:time}
-	In this section we present the computational result of our decomposition method.
-The results in this section reflect the effectiveness of the techniques introduced in Section~\ref{sec:decomposition}.
-We start with the comparison of the initial lower bound with and without the bounds on variable \(t\) tightened.
-	\newline
-	We show the quality of the heuristic upper bound obtained in Section~\ref{subsec:HUB}.
-We use the same 20 batches of samples as in Section~\eqref{subsec:budget}.
-For each batch we compare the true optimal value with the heuristic upper bounds.
-Table~\ref{table:hub} shows the smallest gap, the average gap and the largest gap, all in percentage, between the heuristic upper bound and the true optimal value.
-We split each sample into equal-sized subsamples to generate the heuristic upper bound.
-We use \(N = 10\) for \(|\Omega| = 100\), \(N = 10\) for \(|\Omega| = 200\), and \(N = 20\) for \(|\Omega| = 500\).
-We also report the average running time of obtaining the heuristic upper bound.
+	In this section we discuss the computational performance of our decomposition method with its various potential enhancements.
+As a benchmark, we compare the performance of Algorithms~\ref{alg:Cut} and~\ref{alg:CutBB} to direct solution of the extensive formulation~\eqref{prob:extensive} using a commercial solver.
+%We also present how effective the techniques introduced in Section~\ref{sec:decomposition} are in terms of accelerating the decomposition method.
+
+	We first show the quality of the heuristic upper bound described in Section~\ref{subsec:HUB}.
+We solve SAA instances with sample sizes of 100, 200, and 500, and in the notation of Section~\ref{subsec:HUB} we use $N= $ 10, 10, and 20 in these three instances, respectively.
+We compare the heuristic upper bound to the optimal value of the SAA instance.
+Moreover, for each case/sample-size pair, we replicate the procedure on 20 independent instances.
+These are the same 20 instances used for sample sizes of 100, 200, and 500 in Section~\ref{subsec:budget} for which Table~\ref{table:budgetL} reports average optimal values.
+Table~\ref{table:hub} shows the smallest gap, the average gap, and the largest gap, all as percentages, between the heuristic upper bound and the SAA optimal value across the 20 replications.
+The table also shows the average time required to compute the heuristic upper bound.
+
 	\begin{table}[H]
 		\centering		
-		\begin{tabular}{ c | c | l l l | r}
+		\begin{tabular}{ c | c | r r r | r}
 			\hline
-			\multirow{2}{*}{\(\quad\)} & \multirow{2}{*}{Sample size} & \multicolumn{3}{c |}{Gap (\%)} & \multirow{2}{*}{Average Time (Sec).} \\
+			\multirow{2}{*}{\(\quad\)} & \multirow{2}{*}{Sample size} & \multicolumn{3}{c |}{Gap (\%)} & \multirow{2}{*}{Average time (Sec).} \\
 		    & & Smallest & Average & Largest &\\
 			\hline
-			\multirow{3}{*}{Case 11} & 100 & 0.01	& 0.5	& 2.3	& 5.6\\
-			& 200 & 0	& 0.15	& 0.83	& 17.8\\
-			& 500 & 0	& 0.07	& 0.37	& 67.5\\
+			\multirow{3}{*}{Case 11} & 100 & 0.01	& 0.50 	& 2.30 	& 5.6\\
+			& 200 & 0.00	& 0.15	& 0.83	& 17.8\\
+			& 500 & 0.00	& 0.07	& 0.37	& 67.5\\
 			\hline
 			\multirow{3}{*}{Case 14} & 100 & 1.34	& 6.02	& 16.14	& 7.7\\
-			& 200 & 1.58	& 3.9	& 8.91	& 30.4\\
+			& 200 & 1.58	& 3.90 	& 8.91	& 30.4\\
 			& 500 & 0.75	& 2.35	& 3.96	& 104.4\\
@@
 			& 200 & 0.05	& 0.99	& 2.03	& 37.2\\
-			& 500 & 0	& 0.72	& 1.59	& 127.6\\
+			& 500 & 0.00	& 0.72	& 1.59	& 127.6\\
 			\hline
-			\multirow{3}{*}{Case 35} & 100 & 0	& 0.64	& 2.65	& 5.8\\
-			& 200 & 0.08	& 0.46	& 1.3	& 25.7\\
-			& 500 & 0	& 0.32	& 1.25	& 59.0\\
+			\multirow{3}{*}{Case 35} & 100 & 0.00	& 0.64	& 2.65	& 5.8\\
+			& 200 & 0.08	& 0.46	& 1.30	& 25.7\\
+			& 500 & 0.00	& 0.32	& 1.25	& 59.0\\
 			\hline
 		\end{tabular}
-		\caption{Gap information between the heuristic upper bound and optimal value for twenty random samples}
+		\caption{Gap between the heuristic upper bound and optimal value for 20 SAA replications}
 		\label{table:hub}
 	\end{table}
-	\noi We can see that the average upper bound gap is larger than 5\% only for Case 14 when the sample size equals to 100.
-Among all 240 samples, there are only 15 of which the heuristic upper bound is more than 5\% larger than the optimal value.
+
+	We see that the average upper bound gap exceeds 5\% only for Case 14 when the sample size is 100.
+Among all 240 SAA instances, there are only 15 for which the heuristic upper bound exceeds the optimal value by more than 5\%.
 We also observe that as the sample size grows, the heuristic upper bound's quality improves.
-\\
-	\newline
-	Next we show the effectiveness of finding a heuristic upper bound and generating Magnanti-Wong cuts.
-For all test cases, we use a sample size \(|\Omega| = 500\).
-In Table~\ref{table:heuristics}, ``UB" means that we only use heuristic upper bound in Section~\ref{subsec:HUB} and generate regular Benders' cuts, and ``MW" means that we generate Magnanti-Wong cuts in Section~\ref{subsec:MW} without a prespecified initial upper bound.
-We also test the time performance of using neither and using both techniques.
+
+	Table~\ref{table:heuristics} shows run-time results for finding a heuristic upper bound and generating Magnanti-Wong cuts \tcr{while using Algorithm~\ref{}}.
+For all test cases we use a sample size of 500.
+We use $N=20$ for the heuristic upper bound, and we retain all the generated cuts.
+In the table, ``UB" means that we only use the heuristic upper bound of Section~\ref{subsec:HUB} and generate regular Benders' cuts, and ``MW" means that we generate Magnanti-Wong cuts of Section~\ref{subsec:MW} without the benefit of the upper bound heuristic.
+We also show the computation time of using neither and using both techniques.
+
 	\begin{table}[H]
 		\centering		
-		\begin{tabular}{ c | l l l l }
+		\begin{tabular}{ c | r r r r }
 			\hline
-			Running Time (sec.) & Case 11 & Case 14 & Case 19 & Case 35 \\ \hline
-			Neither & 226.2 & 3573.8 & 4499.5 & 458.6 \\
-			UB & 153.8 & 3003.7 & 2899.9 & 110.7\\
-			MW & 290.4 & 2386.4 & 2002.1 & 451.0\\
-			Both & 222.3 & 2342.4 & 1411.5 & 170.2\\
+			Run time (sec.) & Case 11 & Case 14 & Case 19 & Case 35 \\ \hline
+			Neither & 178.9 & 3,573.8 & 4,499.5 & 160.2 \\
+			UB & 103.2 & 3,003.7 & 2,899.9 & 20.0\\
+			MW & 180.5 & 2,386.4 & 2,002.1 & 320.4\\
+			Both & 151.6 & 2,342.4 & 1,411.5 & 40.1\\
 			\hline
 		\end{tabular}
-		\caption{Computational improvement by utilizing heuristic upper bound generation and Magnanti-Wong heuristic cuts}
+		\caption{Run-time results for using the heuristic upper bound and Magnanti-Wong cuts \tcr{in Algorithm~\ref{}}}
 		\label{table:heuristics}
 	\end{table}
-	Table~\ref{table:heuristics} shows that obtaining a heuristic upper bound can significantly improve the computational time since many branches will be cut off by the heuristic upper bound when solving the master MIP.
-Magnanti-Wong cuts are effective for Case 14 and Case 19 but not for the other two cases.
-The effectiveness of such cuts may depend on the geometric nature of test cases, and it is valuable to investigate this phenomenon with more test cases in the future.\\
-	\newline
-	\noi Next we compare the running time of Algorithm~\ref{alg:Cut} (denoted as A\ref{alg:Cut}), Algorithm~\ref{alg:CutBB} (denoted as A\ref{alg:CutBB}), with and without the cut selection process (CS), and solving the extensive formulation~\eqref{prob:extensive} using Gurobi.
-The computational time is presented in Table~\ref{table:time}.
+
+	\tcr{Is Table~\ref{table:heuristics} based on 20 replications?
+(Either way, we should say.
+If not, we need to clarify because the first results use 20 replications.) As I indicate above, I'm not sure whether this is for Algorithm~1?
+In any case, I'm also not sure why the run-time values in Table~\ref{table:heuristics} don't appear somewhere in the 500 row of Table~\ref{table:time}?
+This section is unclear (to me) on whether FBBT is always being used?
+And, what is the effect of FBBT?}
+
+	Table~\ref{table:heuristics} shows that obtaining a heuristic upper bound can reduce computational effort; this occurs because the bound facilitates earlier fathoming of some nodes in the branch-and-bound tree when solving the master MIP.
+This outweighs the time required to compute the upper bound; see Table~\ref{table:hub}.
+Magnanti-Wong cuts are effective for Cases~14 and~19 but not for the other two cases, and the two techniques can have a synergistic effect (Case 14).
+%The effectiveness of such cuts may depend on the geometric nature of test cases, and it is valuable to investigate this phenomenon with more test cases in the future.
+
+	Table~\ref{table:time} compares the run time of Algorithm~\ref{alg:Cut} (denoted A\ref{alg:Cut}), Algorithm~\ref{alg:CutBB} (denoted A\ref{alg:CutBB}), with and without the cut selection procedure (CS); \tcr{these results use both the heuristic upper bound and Magnanti-Wong cuts.
+FBBT?}.
+The table also shows the run-time for solving the extensive formulation~\eqref{prob:extensive} using Gurobi, also to a relative optimality tolerance of 0.01.
+%The computational time is presented in Table~\ref{table:time}, assuming all techniques in Section~\ref{subsec:FBBT}-\ref{subsec:MW} are employed.
+
 	\begin{table}[ht]
 		\centering		
-		\begin{tabular}{ c | c | l l l l l}
+		\begin{tabular}{ c | c | r r r r r }
 			\hline
-			\multirow{2}{*}{Running Time (sec.)} & \multirow{2}{*}{Sample Size (\(|\Omega|\))} & \multicolumn{5}{c}{Methods} \\ \cline{3-7}
+			\multirow{2}{*}{Run time (sec.)} & \multirow{2}{*}{Sample size} & \multicolumn{5}{c}{Methods} \\ \cline{3-7}
 			& & A\ref{alg:Cut} & A\ref{alg:Cut}+CS & A\ref{alg:CutBB} & A\ref{alg:CutBB}+CS & Extensive  \\ \hline
@@
 			& 200 & 27.8 & 60.8 & 20.0 & 30.0 & 49.9\\
-			& 500 & 445.8 & 407.4 & 145.1 & 163.2 & 1634.3\\
-			& 1000 & 411.2 & 500.0 & 80.1 & 88.1 & 5622.7\\
+			& 500 & 445.8 & 407.4 & 145.1 & 163.2 & 1,634.3\\
+			& 1,000 & 411.2 & 500.0 & 80.1 & 88.1 & 5,622.7\\
 			\hline
@@
 			& 200 & 246.9 & 233.2 & 212.9 & 136.4 & 212.7 \\
-			& 500 & 2882.6 & 2635.8 & 1651.5 & 1122.1 & 1677.0 \\
-			& 1000 & 10388.4 & 12692.3 & 4777.6 & 2673.7 & 12027.1 \\
+			& 500 & 2,882.6 & 2,635.8 & 1,651.5 & 1,122.1 & 1,677.0 \\
+			& 1,000 & 10,388.4 & 12,692.3 & 4,777.6 & 2,673.7 & 12,027.1 \\
 			\hline
@@
 			& 200 & 412.2 & 337.0 & 552.6 & 270.4 & 383.8 \\
-			& 500 & 2732.1 & 2434.2 & 1008.4 & 830.8 & 3960.4 \\
-			& 1000 & 18251.8 & 14811.1 & 13995.4 & 3623.8 & 44537.3 \\
+			& 500 & 2,732.1 & 2,434.2 & 1,008.4 & 830.8 & 3,960.4 \\
+			& 1,000 & 18,251.8 & 14,811.1 & 13,995.4 & 3,623.8 & 44,537.3 \\
 			\hline
@@
 			& 500 & 81.9 & 80.5 & 30.0 & 30.0 & 346.9 \\
-			& 1000 & 313.0 & 303.9 & 50.1 & 50.1 & 690.5 \\
+			& 1,000 & 313.0 & 303.9 & 50.1 & 50.1 & 690.5 \\
 			\hline
 		\end{tabular}
-		\caption{Comparison of computational performance with different sample sizes for Algorithm~\ref{alg:CutBB} and solving extensive formulation using Gurobi}
+		\caption{Computational performance with different sample sizes for decomposition methods and directly solving the extensive formulation using Gurobi}
 		\label{table:time}
 	\end{table}
+
 	% decomposition works
-	Table~\ref{table:time} shows that although solving the extensive formulation may be faster when the sample size is small, the decomposition algorithms generally perform much better when the sample size is large.
-The only exception is in Case 14 where Algorithm~\ref{alg:Cut} has a longer running time than solving the extensive formulation, no matter whether we select cuts or not.
-In our decomposition methods, although we need to solve the master problem multiple times, the number of binary variables is significantly smaller than that in the extensive formulation.
-Therefore, when the sample size is large, our decomposition methods can still a better computational results than solving the extensive formulation.\\
-	\newline
+	Table~\ref{table:time} shows that although directly solving the extensive formulation may be faster when the sample size is small, our decomposition algorithms tend to perform better as the sample size grows; the table's one exception is Algorithm~\ref{alg:Cut} for Case 14.
+	%The only exception is in Case 14 where Algorithm~\ref{alg:Cut} has a longer running time than solving the extensive formulation, no matter whether we select cuts or not. 
+	The improved computational performance occurs because, while our decomposition methods must solve the master problem multiple times, the number of binary variables is significantly smaller than that of the extensive formulation.
+%Therefore, when the sample size is large, our decomposition methods can outperform direct solution.
+
 	% algorithm 2 is better, why
-	Algorithm~\ref{alg:CutBB} is faster than Algorithm~\ref{alg:Cut} when \(|\Omega| \geq 500\).
-When the sample size is large, Algorithm~\ref{alg:Cut} requires many master iterations to converge.
-In later iterations of Algorithm~\ref{alg:Cut}, solving the mixed integer master program becomes significantly harder.
+	Algorithm~\ref{alg:CutBB} outperforms Algorithm~\ref{alg:Cut} when the sample size exceeds 500.
+When the sample size is large, Algorithm~\ref{alg:Cut} requires many master iterations to converge, and solving the mixed-integer master program becomes significantly harder.
 For Algorithm~\ref{alg:CutBB}, the time saved by processing nodes in parallel outweighs the slightly longer solving time at each node due to using fewer cores.
-Moreover, because of branching, the master problems in the B\&B tree with a small number of binary variables in Algorithm~\ref{alg:CutBB}, which further accelerates solving the master problem.
+Moreover, because of branching, each master problem at a node in the B\&B tree has a small number of binary variables in Algorithm~\ref{alg:CutBB}, which further accelerates the B\&C algorithm.
 	% cut selection is useful, especially in algorithm 2
-	The results also show that selecting cuts can be helpful for the decomposition methods.
-Applying the cut selection process gains a larger improvement for Algorithm~\ref{alg:CutBB} than for Algorithm~\ref{alg:Cut}.
+    The results also show that selecting cuts can significantly improve the decomposition methods.
+On the most difficult instances, applying the cut selection scheme yields larger improvements for Algorithm~\ref{alg:CutBB} than for Algorithm~\ref{alg:Cut}.
 	%\begin{figure}
@@
 
+	\tcr{I'm a bit worried about the following in the computational results: 1.
+We argue that a sample size of about 100 is large enough to obtain good solutions.
+2.
+Then  we show that you don't need to decomposition algorithm in this case.
+We might be able to modify the first result by assessing solution quality using common random numbers.
+We'd do this by solving an SAA of sample size 10, 20, 50, 100, 200, 500, 1000.
+Then, we'd use 20 batches and compute the upper and lower bounds using a sample size of 10, 20, 50, 100, 200, 500, 1000.
+I suspect the sampling errors will be significantly smaller than what you present in the LB and UB tables and hence there may be an argument for needing the larger sample sizes.}
+
 \section{Conclusions} \label{sec:conclusions}
-	In this paper, we establish the concept of the stochastic disruption and formulate a two-stage stochastic mixed integer program to model a project crashing optimization problem under the influence of a single disruption.
-We use examples to illustrate the properties of our problem that it is possible to delay the start or crash a shorter activity to accelerate the whole project.
-Moreover, the computational results justify the need to use a two-stage stochastic mixed integer program to model this problem.
-It is computationally challenging to solve a two-stage stochastic mixed integer program with binary variables in the second stage, and we prove that it is NP-hard.
-Therefore, we propose a decomposition method which uses the logic relationship to sequentially partitions the continuous feasible regions of the master problem to generate tighter Benders' cuts.
-The proposed method can significantly improve the computational performance, especially for the large sample sizes, which we show is often required to obtain a good solution/estimation of bounds.\\
-	\newline
-	There are multiple possible extensions of the results in this paper.
+	We introduce the concept of a stochastic disruption in the context of a project crashing problem.
+We consider the case of a single disruption, and formulate the model as a two-stage stochastic mixed-integer program in which the timing of the stage, i.e., the disruption time, is random.
+We use examples to illustrate properties of our problem that deviate from its deterministic counterpart, including the fact that it can be optimal to delay the start of an activity or crash a shorter-duration activity, even under proportional reduction.
+While, conceptually, the underlying problem involves continuous decision variables, we argue that the problem is NP-hard.
+In our two-stage stochastic mixed-integer program, second-stage binary variables capture the logic of the start time of an activity, relative to the disruption time.
+The resulting model is computationally challenging, but we propose a decomposition method which exploits the logical temporal relationship just mentioned, and sequentially partitions the feasible region of continuous first-stage decision variables to generate tighter cuts in a Benders' decomposition algorithm.
+The proposed method can significantly improve computational performance, especially as sample sizes grow large.
+
+ The ideas in this paper can be extended in multiple ways.
+There may be opportunities to exploit network structure in tailoring the branch-and-cut algorithm that we have developed.
+The distribution governing the disruption time and, conditional on that time, the magnitude of the disruption may facilitate sampling strategies that reduce variance and improve solution quality.
+We have considered a model and algorithm that allow for at most one disruption, but handling a small number of disruptions	could be attractive.
+
+%\tcr{	There are multiple possible extensions of the results in this paper.
 First, there is still room to improve the computational performance of the decomposition method.
@@
 In addition, it is worthwhile to inspect the network structures so that we can improve the quality of cuts or prune partitions.
+}
+
+\section*{Acknowledgements}
+
+\tcr{To add}
+
+\tcr{In the references: Why does the Ross {\em Stochastic Processes} book have a huge number of authors? I changed it to just him but am leaving this note in case something else was intended.}
 
@@
 \appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 \section{Detailed Formulation of Model~\eqref{prob:subdual}} \label{appen:probdual}
@@
 All dual variables have the correct signs matching the sense of corresponding primal constraints.
+\end{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section{Test Cases Data} \label{appen:data}
-	We present the detailed data of four test cases here.
+    We present the data of four test cases here.
 For all test cases we assume there is only one possible crashing option for each activity.
@@
 The timing of the disruption follows a lognormal distribution with parameters \(\mu\) and \(\sigma\) where the mode is \(e^{\mu - \sigma^2}\).
-We also assume that the duration is only dependent on the predecessor, i.e., \(D_{ik} = D_i\) and \(d_{ik}^\omega = d_i^\omega\).
+We also assume that the duration only depends on the predecessor, i.e., \(D_{ik} = D_i\) and \(d_{ik}^\omega = d_i^\omega\).
 All \(d_i\) follow an exponential distribution with a mean of \(\mu_i\).

### 2019-07-27 src/test_alternatives.jl

@@ -59,9 +59,11 @@ tFull,xFull,ubFull,lbFull,timeIter,treeList,timedecomp = partSolve_BB_para_noUB(
 tFull,xFull,ubFull,lbFull,timeIter,treeList,timedecomp = partSolve_BB_para_share(pData,disData,Ω,sN,MM,noThreads,5,6,5,1e-2,5,10800);
 
 
-resultDict = Dict();
+#resultDict = Dict();
+data = load("test_alt.jld");
+resultDict = data["data"];
 
-for fileInd in 1:4
+for fileInd in 2:3
     Ωl = 6;
     filePath = pathList[fileInd];
     global Ω = 1:Ωsize[Ωl];

### 2019-07-28 Writeup/PERT_Draft_DPM_7_27.tex
Add the FBBT testing functionality

@@
 The upper bound point estimate for those five candidate solutions is shown in Figure~\ref{fig:value}, and the \(95\%\) confidence interval is shown in Table~\ref{table:value}.
-\tcr{20 batches of size 5000 for the UB.
+	%\tcr{20 batches of size 5000 for the UB.
 This is the same as simply using a sample size of 100,000.

### 2019-07-28 src/partSolve_BB_shared.jl

@@ -55,6 +55,7 @@ function solveMP_para_Share(data)
     nSplit = data[12];
     roundLimit = data[13];
     cutSelOpt = data[14];
+    BTOpt = data[15];
     Ω = 1:length(disData);
 
     Tmax1 =lDict[0];
@@ -411,11 +412,19 @@ function solveMP_para_Share(data)
         if lGFracInd != -1
             #locBreak = Int64(floor((GFrac[lGFracInd][1]*fracBreak + GFrac[lGFracInd][2]*(1 - fracBreak))));
             divSet1,divDet1,divSet2,divDet2 = breakDiv(pData,disData,H,divSet,divDet,lGFracInd,locBreakH,distanceDict);
-            divSet1,divDet1 = divExploit(pData,disData,H,divSet1,divDet1,distanceDict);
+            if BTOpt
+                divSet1,divDet1 = divExploit(pData,disData,H,divSet1,divDet1,distanceDict);
+            else
+                divSet1,divDet1 = divExploitSimple(pData,disData,H,divSet1,divDet1);
+            end
             divSet1,divDet1 = splitPrepld2(pData,disData,Ω,H,GCurrent,tCurrent,divSet1,divDet1,θCurrent,θIntCurrent,nSplit);
             #divSet1,divDet1 = splitPrepSmart2(pData,disData,Ω,H,GCurrent,tCurrent,divSet1,divDet1,θCurrent,θIntCurrent,nSplit)
 
-            divSet2,divDet2 = divExploit(pData,disData,H,divSet2,divDet2,distanceDict);
+            if BTOpt
+                divSet2,divDet2 = divExploit(pData,disData,H,divSet2,divDet2,distanceDict);
+            else
+                divSet2,divDet2 = divExploitSimple(pData,disData,H,divSet2,divDet2);
+            end
             divSet2,divDet2 = splitPrepld2(pData,disData,Ω,H,GCurrent,tCurrent,divSet2,divDet2,θCurrent,θIntCurrent,nSplit);
             #divSet2,divDet2 = splitPrepSmart2(pData,disData,Ω,H,GCurrent,tCurrent,divSet2,divDet2,θCurrent,θIntCurrent,nSplit)
             returnSet = [[divSet1,divDet1],[divSet2,divDet2]];
@@ -543,7 +552,7 @@ function solveMP_para_Share(data)
 end
 
 
[…]

### 2019-07-28 src/tighten.jl

@@ -360,6 +360,34 @@ function divExploit(pData,disData,H,PartSet,PartDet,distanceDict)
     return divSetNew,divDetNew;
 end
 
+function divExploitSimple(pData,disData,H,PartSet,PartDet)
+    PartSetNew = deepcopy(PartSet);
+    PartDetNew = deepcopy(PartDet);
+    for i in pData.II
+        # earlyT is the index of H that is right before the earliest possible starting time of i
+        # earlyT is the index of H that is right after the latest possible starting time of i
+        earlyT = 0;
+        lateT = maximum(keys(H));
+        for l in 1:length(PartSet[i])
+            if PartDet[i][l] == 1
+                earlyT = l;
+            end
+        end
+        for l in 1:earlyT
+            PartDetNew[i][l] = 1;
+        end
+        for l in length(PartSet[i]):-1:1
+            if PartDet[i][l] == -1
+                lateT = l;
+            end
+        end
+        for l in lateT:length(PartSet[i])
+            PartDetNew[i][l] = -1;
+        end
+    end
+    return PartSetNew,PartDetNew;
+end
+
 # break the divSet and get 2 updated divSets and divDets
 function breakDiv(pData,disData,H,divSet,divDet,iBreak,locBreak,distanceDict)
     # iBreak is the activity to branch on

### 2019-07-29 src/test_FBBT.jl
Fixed the simple FBBT procedure

@@ -1,4 +1,4 @@
-# script to test the alternative algorithms of decomposition
+# test the effectiveness of FBBT
 addprocs(30);
 global noThreads = 30;
 @everywhere using JuMP,Gurobi,CPLEX,Ipopt;
@@ -21,18 +21,13 @@ pathList = ["/scratch/haoxiang/current/11/",
                "/scratch/haoxiang/current/55/",
                "/scratch/haoxiang/current/75/"];
 
-# altOpt: 1: no UB, no MW
-#         2: UB, no MW
-#         3: MW, no UB
-#         4: both
-altOpt = 1
 Ωsize = [10,20,50,100,200,500,1000,2000];
 sNList = [10,0,0,0,20,25,20,40];
 MMList = [1,0,0,0,10,20,50,50];
 
+# precompile
 fileInd = 1;
 filePath = pathList[fileInd];
-# compile the functions
 Ωl = 1;
 global Ω = 1:Ωsize[Ωl];
 randNo = 1;
@@ -53,14 +48,9 @@ end
 
 global sN = sNList[Ωl];
 global MM = MMList[Ωl];
-
-tFull,xFull,ubFull,lbFull,timeIter,treeList,timedecomp = partSolve_BB_para_noMW(pData,disData,Ω,sN,MM,noThreads,5,6,5,1e-2,5,10800,true);
-tFull,xFull,ubFull,lbFull,timeIter,treeList,timedecomp = partSolve_BB_para_noUB(pData,disData,Ω,noThreads,5,6,5,1e-2,5,10800);
 tFull,xFull,ubFull,lbFull,timeIter,treeList,timedecomp = partSolve_BB_para_share(pData,disData,Ω,sN,MM,noThreads,5,6,5,1e-2,5,10800);
 
-
-resultDict = Dict();
-
+data = Dict();
 for fileInd in 1:4
     Ωl = 6;
     filePath = pathList[fileInd];
@@ -82,20 +72,13 @@ for fileInd in 1:4
 
     global sN = sNList[Ωl];
     global MM = MMList[Ωl];
-    resultDict[fileInd] = [];
 
-    for altOpt in 1:4
-        if altOpt == 1
-            tFull,xFull,ubFull,lbFull,timeIter,treeList,timedecomp = partSolve_BB_para_noMW(pData,disData,Ω,sN,MM,noThreads,5,6,5,1e-2,5,10800,false);
-        elseif altOpt == 2
[…]

### 2019-07-29 src/tighten.jl

@@ -389,7 +389,7 @@ function divExploitSimple(pData,disData,H,PartSet,PartDet)
 end
 
 # break the divSet and get 2 updated divSets and divDets
-function breakDiv(pData,disData,H,divSet,divDet,iBreak,locBreak,distanceDict)
+function breakDiv(pData,disData,H,divSet,divDet,iBreak,locBreak,distanceDict,BTOpt = true)
     # iBreak is the activity to branch on
     # locBreak is the point of H to break on
 
@@ -419,7 +419,11 @@ function breakDiv(pData,disData,H,divSet,divDet,iBreak,locBreak,distanceDict)
             push!(newPartDet1[iBreak],divDet[iBreak][l]);
         end
     end
-    divSet1,divDet1 = divExploit(pData,disData,H,newPartSet1,newPartDet1,distanceDict);
+    if BTOpt
+        divSet1,divDet1 = divExploit(pData,disData,H,newPartSet1,newPartDet1,distanceDict);
+    else
+        divSet1,divDet1 = divExploitSimple(pData,disData,H,newPartSet1,newPartDet1);
+    end
 
     newPartSet2 = deepcopy(divSet);
     newPartDet2 = deepcopy(divDet);
@@ -436,7 +440,11 @@ function breakDiv(pData,disData,H,divSet,divDet,iBreak,locBreak,distanceDict)
             push!(newPartDet2[iBreak],divDet[iBreak][l]);
         end
     end
-    divSet2,divDet2 = divExploit(pData,disData,H,newPartSet2,newPartDet2,distanceDict);
+    if BTOpt
+        divSet2,divDet2 = divExploit(pData,disData,H,newPartSet2,newPartDet2,distanceDict);
+    else
+        divSet2,divDet2 = divExploitSimple(pData,disData,H,newPartSet2,newPartDet2);
+    end
 
     return divSet1,divDet1,divSet2,divDet2;
 end
